### 2024-02-17 skripsi/abstract.tex
Layout & deriv deeponetsvm

%\chapter{ABSTRACT}
\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{ABSTRACT}
\begin{center}
\textbf{\large  ABSTRACT}\\[0.5cm]
\textbf{\large TITLE}\\[0.5cm]
\textbf{by}\\
\textbf{\penulis}\\
\textbf{NIM: \nim}\\[2em]
\end{center}

\noindent In general, Abstract is a translation of Abstrak. However, appropriate paraphrase may need some words or sentences whose meanings are close enough to those written in Abstrak.

\noindent Key words: \keywords

### 2024-02-17 skripsi/abstrak.tex
Layout & deriv deeponetsvm

%\chapter{ABSTRAK}
\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{ABSTRAK}
\begin{center}
\textbf{\large  ABSTRAK}\\[0.5cm]
\textbf{\large JUDUL ABSTRAK}\\[0.5cm]
\textbf{Oleh}\\
\textbf{\penulis}\\
\textbf{NIM: \nim}\\[2em]
\end{center}

\noindent Abstrak merupakan penjelasan singkat dan padat tentang pekerjaan dan hasil penelitian TA, yang dituliskan secara teknis. Abstrak memiliki karakter tegas dan komprehensif, dan hanya dapat dituliskan setelah pekerjaan penelitian telah mencapai tahap tertentu, dan karenanya ada hasil penelitian yang dapat dilaporkan. Abstrak ditulis menjelang akhir penyelesaian penulisan buku TA.

Secara umum, abstrak memuat beberapa komponen penting, yaitu: konteks atau cakupan pekerjaan penelitian, tujuan penelitian, metodologi yang digunakan selama penelitian, hasil-hasil penting yang dapat ditambahkan dengan implikasinya, dan simpulan dari penelitian. Dengan demikian, suatu abstrak tidak dapat dituliskan apabila penelitian belum mencapai hasil tertentu, apalagi kalau penelitiannya pun belum dilakukan.

Panjang abstrak sebaiknya dicukupkan dalam satu halaman, termasuk kata kunci. Tiga kata kunci dipandang cukup, yang masing-masingnya memuat paduan kata utama, yang dapat merepresentasikan isi Abstrak. Halaman Abstrak tidak memuat informasi judul dan penulis, sehingga tidak secara langsung dapat digunakan sebagai lembaran Abstrak Sidang TA yang disediakan untuk hadirin, yang memerlukan tambahan (sekurangnya) dua informasi tersebut.

\noindent Kata kunci: \katakunci

### 2024-02-17 skripsi/bab2.tex
Layout & deriv deeponetsvm

\chapter{KAJIAN PUSTAKA}

\noindent Bab ini mengulas secara rinci konsep-konsep dasar yang berkaitan dengn pekerjaan penelitian TA dan deskripsi studi pustaka yang dilakukan. Judul bab tidak harus seperti yang dituliskan, melainkan dapat lebih fleksibel yang mencerminkan isi paparan pada bab ini. Demikian halnya dengan judul sub bab.

\section{Sub Bab A} 
\noindent Teori dasar yang dituliskan pada sub bab ini dapat berupa konsep-konsep fundamental yang menjadi landasan pekerjaan penelitian, dan bisa saja sebagiannya terdapat pada buku teks atau artikel review. Pemahaman tentang teori dan konsep dasar ini, termasuk konsep pendukung seperti statistika atau numerik, harus tampak pada paparan yang diulas dalam sub bab ini.

\section{Sub Bab B}
\noindent Suatu penelitian tidak dapat lepas dari capaian pengetahuan dan pemahaman yang sudah dipublikasikan. Deskripsi tentang capaian ini menjadi penting karena selain menunjukkan tingkat pemahaman mahasiswa, juga mengetahui tempat pekerjaan penelitian TA dalam konstelasi capaian tersebut. Studi pustaka dan paparan hasilnya dapat memperkaya wawasan tentang topik yang diangkat pada penelitian TA.

\section{Membuat Persamaan}
\noindent Secara prinsip, suatu persamaan menyatu dalam kalimat. Letak persamaan dapat berada di awal, tengah, atau akhir kalimat. Dengan demikian, pada akhir persamaan harus diberikan tanda baca, misalnya koma, titik koma, atau titik, yang menekankan kehadiran persamaan dalam kalimat. Tidak semua persamaan harus diberi nomor. Persamaan yang dirujuk pada naskah TA saja yang harus diberi nomor. Kode awal penomoran ini adalah nomor urut bab, termasuk untuk persamaan pada Lampiran, dengan urutan alfabet kapital.

Setiap notasi harus unik atau tunggal, sehingga arti setiap notasi adalah unik atau tunggal juga. Arti satu notasi harus dituliskan segera ketika notasi tersebut muncul, dan tidak diulang lagi setelahnya.

\subsection{Contoh Persamaan Sederhana}
Persamaan (\ref{II.1}) mendeskripsikan dinamika fungsi gelombang $\psi(\vec{r},t)$ di bawah pengaruh potensial $V(\vec{r})$ dan dituliskan sebagai berikut:
\begin{equation}\label{II.1}
    i\hslash\frac{\partial \psi}{\partial t} = -\frac{\hslash^2}{2 m}\Vec{\nabla}^2 \psi + V(\vec{r})\psi,
\end{equation}
dengan $m$ adalah massa partikel dan $\hslash$ merupakan konstanta Planck tereduksi.

Di akhir persamaan (\ref{II.1}) diberi koma karena berada ditengah kalimat. Untuk merujuk ke persamaan yang telah ditulis, gunakan perintah \verb|\ref{}|.

Untuk menuliskan beberapa set persamaan yang masih terhubung, gunakan \verb|\subequations{}|. Misal kita punya persamaan diferensial terkopel, kita bisa tuliskan
\begin{subequations}
\begin{align}
    \frac{dy}{dt} &= -x ,\\
    \frac{dx}{dt} &= -y .
\end{align}
\end{subequations}
Kalau perlu matriks, kita bisa tulis seperti berikut.
\begin{equation}
    \sigma_x = \begin{pmatrix}
                0 & 1\\
                1 & 0
    \end{pmatrix},\quad
    \sigma_y = \begin{pmatrix}
                0 & -i\\
                i & 0
    \end{pmatrix}, \quad
    \sigma_z = \begin{pmatrix}
                1 & 0\\
                0 & -1
    \end{pmatrix}
\end{equation}

\section{Referensi dan Citation}
\noindent Sitasi dapat dimasukkan ke dalam Tugas Akhir seperti ini \cite{Fujita1996}. Untuk sitasi dengan beberapa sumber, dapat dituliskan juga \cite{hohen1964,Kim2006}. Atau untuk tiga sumber berarti \cite{kongkanand2006,kresse1999,Leibb1993}.

### 2024-02-17 skripsi/bab3.tex
Layout & deriv deeponetsvm

\chapter{METODOLOGI PENELITIAN}
\label{sec:metodologi_penelitian}

Secara umum, metode penelitian yang digunakan pada pekerjaan penelitian disampaikan pada bab ini. Judul bab tidak harus seperti yang dituliskan. Dalam kata lain bisa diubah sesuai kebutuhan.

\section{Model Komputasi}
\noindent The DeepONet architecture contains an element that is difficult to optimize.
% \begin{mini}
%   {W_b}{y=(W_b\cdot f+b_b)^\top\cdot(W_t\cdot v+b_t)+\xi
% \end{mini}

\begin{mini!}|s|
{\substack{W_b,b_b,W_t,b_t,\xi}}{\frac{1}{2}\Vert W_b\Vert_F^2 + \frac{1}{2}\Vert W_t\Vert_F^2 + \frac{c}{2}\sum_{i=1}^{l}\xi_i^2} {}{}
\addConstraint{y_i}{=(W_b f_i+b_b)^\top(W_t v_i+b_t)+\xi_i,\quad}{i=1,\ldots,l}
\end{mini!}

\begin{equation}
  \begin{aligned}
    L(W_b,b_b,W_t,b_t,\xi;\alpha)= {} & \frac{1}{2}\Vert W_b\Vert_F^2 + \frac{1}{2}\Vert W_t\Vert_F^2 +\frac{c}{2}\sum_{i=1}^{l}\xi_i^2 \\ &+ \sum_{i=1}^{l}\alpha_i(y_i-\xi_i-(W_b f_i+b_b)^\top(W_t v_i+b_t))
  \end{aligned}
\end{equation}
\begin{equation}
  \begin{aligned}
    \pdv{L(W_b,b_b,W_t,b_t,\xi;\alpha)}{W_b}                               & = 0                                                                                \\
    \frac{2}{2}W_b + 0 + 0 - \sum_{i=1}^{l}\alpha_i((W_t v_i+b_t)f_i^\top) & = 0                                                                                \\
    W_b - \sum_{i=1}^{l}\alpha_i((W_t v_i+b_t)f_i^\top)                    & = 0                                                                                \\
    W_b                                                                    & = \sum_{i=1}^{l}\alpha_i(W_t v_i f_i^\top+b_t f_i^\top)                            \\
    W_b                                                                    & = \sum_{i=1}^{l}(\alpha_i W_t v_i f_i^\top)+ \sum_{i=1}^{l}(\alpha_i b_t f_i^\top) \\
    W_b                                                                    & = W_t \sum_{i=1}^{l}(\alpha_i v_i f_i^\top)+ b_t \sum_{i=1}^{l}(\alpha_i f_i^\top) \\
    W_b                                                                    & = W_t \sum_{i=1}^{l}(\alpha_i v_i f_i^\top)+ b_t \sum_{i=1}^{l}(\alpha_i f_i^\top) \\
  \end{aligned}
\end{equation}
\begin{equation}
  \begin{aligned}
    \pdv{L(W_b,b_b,W_t,b_t,\xi;\alpha)}{W_t}                                        & = 0                                                                                                                                                                                    \\
    0 + \frac{2}{2}W_t + 0 - \sum_{i=1}^{l}\alpha_i((W_b f_i + b_b)v_i^\top)        & = 0                                                                                                                                                                                    \\
    W_t - \sum_{i=1}^{l}\alpha_i((W_b f_i + b_b)v_i^\top)                           & = 0                                                                                                                                                                                    \\
    W_t                                                                             & = \sum_{i=1}^{l}\alpha_i(W_b f_i v_i^\top + b_b v_i^\top)                                                                                                                              \\
    W_t                                                                             & = \sum_{i=1}^{l}\alpha_i((\sum_{j=1}^{l}\alpha_j(W_t v_j f_j^\top + b_t f_j^\top)) f_i v_i^\top+b_b v_i^\top)                                                                          \\
    W_t                                                                             & = \sum_{i=1}^{l}(\sum_{j=1}^{l}(\alpha_i\alpha_jW_t v_j f_j^\top f_i v_i^\top + \alpha_i\alpha_j b_t f_j^\top f_i v_i^\top) + \alpha_i b_b v_i^\top)                                   \\
    W_t                                                                             & = \sum_{i=1}^{l}(\sum_{j=1}^{l}(\alpha_i\alpha_jW_t v_j f_j^\top f_i v_i^\top) + \sum_{j=1}^{l}(\alpha_i\alpha_j b_t f_j^\top f_i v_i^\top) + \alpha_i b_b v_i^\top)                   \\
    W_t - \sum_{i=1}^{l}\sum_{j=1}^{l}\alpha_i\alpha_jW_t v_j f_j^\top f_i v_i^\top & = \sum_{i=1}^{l}(\sum_{j=1}^{l}(\alpha_i\alpha_j b_t f_j^\top f_i v_i^\top) + \alpha_i b_b v_i^\top)                                                                                   \\
    W_t(I - \sum_{i=1}^{l}\sum_{j=1}^{l}\alpha_i\alpha_j v_j f_j^\top f_i v_i^\top) & = \sum_{i=1}^{l}(\sum_{j=1}^{l}(\alpha_i\alpha_j b_t f_j^\top f_i v_i^\top) + \alpha_i b_b v_i^\top)                                                                                   \\
    W_t                                                                             & = \sum_{i=1}^{l}(\sum_{j=1}^{l}(\alpha_i\alpha_j b_t f_j^\top f_i v_i^\top) + \alpha_i b_b v_i^\top) (I - \sum_{i=1}^{l}\sum_{j=1}^{l}\alpha_i\alpha_j v_j f_j^\top f_i v_i^\top)^{-1} \\
    W_t                                                                             & = \sum_{i=1}^{l}(\alpha_i(\sum_{j=1}^{l}(\alpha_j b_t f_j^\top f_i) + b_b)v_i^\top ) (I - \sum_{i=1}^{l}\sum_{j=1}^{l}\alpha_i\alpha_j v_j f_j^\top f_i v_i^\top)^{-1}                 \\
  \end{aligned}
\end{equation}
\begin{equation}
  \begin{aligned}
    \pdv{L(W_b,b_b,W_t,b_t,\xi;\alpha)}{b_b}        & = 0 \\
    0 + 0 + 0 - \sum_{i=1}^{l}\alpha_i(W_t v_i+b_t) & = 0 \\
    \sum_{i=1}^{l}\alpha_i(W_t v_i+b_t)             & = 0
  \end{aligned}
\end{equation}
\begin{equation}
  \begin{aligned}
    \pdv{L(W_b,b_b,W_t,b_t,\xi;\alpha)}{b_t}        & = 0 \\
    0 + 0 + 0 - \sum_{i=1}^{l}\alpha_i(W_b f_i+b_b) & = 0 \\
    \sum_{i=1}^{l}\alpha_i(W_b f_i+b_b)             & = 0
  \end{aligned}
\end{equation}
\begin{equation}
  \begin{aligned}
    \pdv{L(W_b,b_b,W_t,b_t,\xi;\alpha)}{\xi}                         & = 0        \\
    0 + 0 + \frac{2c}{2}\sum_{i=1}^{l}\xi_i - \sum_{i=1}^{l}\alpha_i & = 0        \\
    \sum_{i=1}^{l}c\xi_i - \alpha_i                                  & = 0        \\
    c\xi_i                                                           & = \alpha_i \\
  \end{aligned}
\end{equation}
\begin{equation}
  \begin{aligned}
    \pdv{L(W_b,b_b,W_t,b_t,\xi;\alpha)}{\alpha}                         & = 0 \\
    0 + 0 + 0 + \sum_{i=1}^{l}y_i-\xi_i-(W_b f_i+b_b)^\top(W_t v_i+b_t) & = 0 \\
    \sum_{i=1}^{l}y_i-\xi_i-(W_b f_i+b_b)^\top(W_t v_i+b_t)             & = 0
  \end{aligned}
\end{equation}

\section{Sub Bab \texorpdfstring{$\alpha$}{α}}
\noindent Misal kita mau masukin tabel, kita bisa juga.
\begin{table}[H]
  \caption{Tabel Sederhana Pertama}
  \label{co:tabel1}
  \begin{center}
    \begin{tabular}{ |c|c|c| }
      \hline
      $G$     & $\text{dim }G$      & $\text{dim }F$ \\
      \hline
      $SU(N)$ & $N^2 -1$            & $N$            \\
      $SO(N)$ & $\frac{1}{2}N(N-1)$ & $N$            \\
      $Sp(N)$ & $N(2N+1)$           & $2N$           \\
      $E_6$   & $78$                & $27$           \\
      $E_7$   & $133$               & $56$           \\
      $E_8$   & $248$               & $248$          \\
      $F_4$   & $52$                & $6$            \\
      $G_2$   & $14$                & $7$            \\
      \hline
    \end{tabular}
  \end{center}
\end{table}

\section{Sub Bab \texorpdfstring{$\beta$}{ꞵ}}
\noindent Atau bisa juga seperti berikut.
\begin{table}[H]
  \caption{Tabel Sederhana Kedua}
  \label{co:tabel2}
  \begin{center}
    \begin{tabularx}{0.8\textwidth} {
      |>{\raggedright\arraybackslash}X
      |>{\raggedright\arraybackslash}X
      |>{\raggedright\arraybackslash}X
      |}
      \hline
      $G$     & $\text{dim }G$      & $\text{dim }F$ \\
      \hline
      $SU(N)$ & $N^2 -1$            & $N$            \\
      $SO(N)$ & $\frac{1}{2}N(N-1)$ & $N$            \\
      $Sp(N)$ & $N(2N+1)$           & $2N$           \\
      $E_6$   & $78$                & $27$           \\
      $E_7$   & $133$               & $56$           \\
      $E_8$   & $248$               & $248$          \\
      $F_4$   & $52$                & $6$            \\
      $G_2$   & $14$                & $7$            \\
      \hline
    \end{tabularx}
  \end{center}
\end{table}

### 2024-02-17 skripsi/bab4.tex
Layout & deriv deeponetsvm

\chapter{HASIL DAN ANALISIS}

\section{Sub Bab Hasil}
\noindent Bab ini memaparkan pekerjaan penelitian dan, terutama, hasil-hasilnya, untuk dianalisis. Secara komprehensif bab ini merepre-sentasikan curahan pemikiran dan kemampuan mahasiswa dalam menjalani pekerjaan penelitian, yang hasil-hasilnya dapat dipertanggungjawabkan. Banyak pendukung yang diperlukan dalam penulisan bab ini, seperti skema penting pengolahan data, penurunan model matematika, asumsi khusus, tabulasi hasil dan analisis, dan gambar atau grafik yang membantu dalam paparan analisis. Judul bab dan sub bab disesuaikan dengan isi paparan.

\section{Memasukkan Gambar}
\noindent Setiap gambar harus dirujuk pada naskah TA, termasuk gambar pada Lam- piran, menggunakan huruf pertama kapital (G) dan nomor gambar, tidak berdasarkan posisi relatifnya (misalnya di bawah ini atau sebelum ini). Format gambar yang umum adalah jpg, png, dan postscript (ps atau eps). Ukuran huruf pada nama sumbu dan label gambar/grafik harus cukup besar dan jelas, demikian halnya dengan angka pada sumbu. Gambar dan grafik dapat berwarna dengan pilihan warna yang tegas dan jelas.

\subsection{Contoh Gambar Sederhana}
Contoh menginput gambar pada buku TA pada
\begin{figure}[h] %h artinya here!
\centering
\includegraphics[width=0.3\linewidth]{gambar/Semiconductor-Fermi-Level-Band-Diagram-1.jpg}
\caption{Tingkatan Fermi pada\\Bahan Semikonduktor}
\label{fermilevel}
\end{figure}
Apabila ada dua gambar, kita juga bisa menaruh keduanya berdampingan.

\begin{figure}[H]
\centering
\subfigure[]{
 \includegraphics[width=0.4\linewidth]{gambar/Semiconductor-Fermi-Level-Band-Diagram-1.jpg}
 \label{surf-1}
 }\hspace{0.1\linewidth}
\subfigure[]{
 \includegraphics[width=0.4\linewidth]{gambar/Semiconductor-Fermi-Level-Band-Diagram-1.jpg}
 \label{surf-2}
}
\caption{Dengan menempatkan gambar \subref{surf-1} dan \subref{surf-2}, pembaca akan lebih mudah membandingkan keduanya.}
\label{surface}
\end{figure}

### 2024-02-17 skripsi/bab5.tex
Layout & deriv deeponetsvm

\chapter{SIMPULAN DAN SARAN}

\section{Simpulan}
\noindent Bab ini merupakan pamungkas berupa rincian rangkuman yang merupakan simpulan dari analisis yang telah dilakukan. Simpulan ini menyajikan sejumlah hal penting yang disampaikan secara ringkas, padat, dan utuh, yang menjawab tujuan penelitian yang dituliskan pada Bab Pendahuluan. Sangat mungkin   ada beberapa konsekuensi dan implikasi yang ditimbulkan dari simpulan yang dihasilkan, yang sepatutnya menjadi perhatian pada penelitian berikutnya. Judul bab dapat disesuaikan, namun umumnya ada \textit{Simpulan} yang memang mendominasi isi bab ini.

\section{Saran}
\noindent Sejumlah ide yang muncul ketika melaksanakan penelitian TA dapat menjadi bahan atau topik untuk pekerjaan selanjutnya. Hal ini dapat berupa perbaikan atau ragam lain dari apa yang telah dilakukan sepanjang penelitian. Sub bab ini menjadi sumber informasi penting bagi, utamanya mahasiswa, yang akan melakukan penelitian lanjutan.

### 2024-02-17 skripsi/identitas.tex
Layout & deriv deeponetsvm

%isi identitas diri di file ini......
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%JUDUL: 
\providecommand{\judul}{
    APROKSIMASI SOLUSI \textit{PARTIAL DIFFERENTIAL EQUATIONS} DENGAN \textit{PHYSICS-INFORMED SUPPORT VECTOR MACHINE}
}
%PENULIS:
\providecommand{\penulis}{
    Ahmad Izzuddin
}
%NIM:
\providecommand{\nim}{
    1908919
}

%Pembimbing1 dan pembimbing2, misalnya:
%Pembimbing 1
\providecommand{\pembimbingsatu}{
    Prof. Dr. Lala Septem Riza, M.T.
}
%NIP Pembimbing 1:
\providecommand{\NIPpbbsatu}{
    197809262008121001
}
%Pembimbing2
\providecommand{\pembimbingdua}{
    Nama Pembimbing 2
}
%NIP Pembimbing 2:
\providecommand{\NIPpbbdua}{
    314159265358979323
}

%untuk keywords yang ada di abstrak, di sini:
\providecommand{\katakunci}{
    Konsep Abstrak, Komponen Abstrak, Kata Kunci.
}
\providecommand{\keywords}{
    Abstract Concepts, Abstract Components, Key Words.
}

### 2024-02-17 skripsi/katapengantar.tex
Layout & deriv deeponetsvm

\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{KATA PENGANTAR}
\begin{center}
 \textbf{\large KATA PENGANTAR}\\[3em]
\end{center}
%-----------------------------------------

\noindent Kata pengantar berperan sebagai gerbang masuk bagi pembaca dan mendapat sajian ringkas tentang hal-hal terkait paparan pada buku Tugas Akhir (TA). Sajian ini sejatinya merupakan pengenalan umum bagi pembaca tentang isi tulisan. Hal ini berbeda dengan abstrak yang mendeskripsikan pekerjaan dan hasil penelitian secara lebih teknis.

Kata pengantar merupakan wadah penulis untuk mengenalkan dan mempromosikan pekerjaan dan hasil penelitian dengan bahasa yang sederhana, sehingga pembaca tertarik untuk menelusuri lebih jauh dengan mencermati seluruh paparan pada buku TA. Ini salah satu tujuan kata pengantar. Contoh paragraf yang mengantar pembaca pada isi Buku TA: \textit{Template} \LaTeX\ diberikan berikut ini.

Menuliskan pekerjaan dan hasil penelitian TA dalam suatu laporan buku TA memerlukan panduan standar. Panduan ini dibuat dalam beberapa dokumen, yang salah satunya adalah Buku TA: \textit{Template} \LaTeX. Suatu template adalah cetakan yang siap dituang oleh curahan buah pikiran yang keluar dari pengalaman dalam melakukan pekerjaan penelitian dan hasil-hasilnya. Mencermati cetakan yang memberikan sejumlah contoh dapat memperlancar penulisan laporan tersebut menjadi suatu produk, yaitu buku TA.

Tujuan lain dari Kata Pengantar adalah memberi tempat untuk menyampaikan rasa syukur dan terima kasih kepada banyak pihak, misalnya keluarga, staf akademik, staf tenaga kependidikan, teman, individu atau komunitas pemberi dukungan dan inspirasi, dan institusi pendukung pendanaan seperti pemberi beasiswa atau dana penelitian, atau pendukung akses fasilitas.

\textit{Pengorbanan, kegigihan, dedikasi, dan penuh tanggung jawab dari para pahlawan pekerja medis dalam perawatan pasien terpapar Covid-19 telah memberi inspirasi melalui nilai-nilai kejuangan tanpa pamrih. Inspirasi inilah yang membangkitkan spirit pamungkas pada penyelesaian Buku TA: Template} \LaTeX\ \textit{ini. Suatu inspirasi selalu bekerja dan mengena secara tidak langsung. Banyak berterima kasih atas inspirasi yang memantik spirit ini.}

\newpage
Tidak ada sub bab/bagian pada Kata Pengantar, namun daftar rincian diperkenankan. Pada bagian indentitas akhir, seperti berikut ini, dituliskan nama mahasiswa dan NIM, bukan \textit{penulis}, dan tidak perlu ditandatangani. Berikut adalah contoh penulisan rincian yang berisi ucapan terima kasih:
\begin{itemize}
 \item \pembimbingsatu dan \pembimbingdua selaku dosen pembimbing tugas akhir.
 \item Jyesta, sebagai teman bimbingan yang selalu bersedia untuk diajak berdiskusi selama penelitian.
 \item Rekan-rekan Spectranova, ............
\end{itemize}

\begin{flushright}
Bandung, \today\\[0.25cm]
\penulis \\
\nim
\end{flushright}

### 2024-02-17 skripsi/sampuldalam.tex
Layout & deriv deeponetsvm

\thispagestyle{empty}
\begin{center}
%bagian atas dari halaman
\begin{doublespace}
\textbf{\smaller\large{\MakeUppercase{\judul}}}\\[2.5cm]
\end{doublespace}

\textbf{\MakeUppercase{\large tugas akhir}}\\[0.5cm]
\begin{onehalfspace}
Diajukan untuk memenuhi syarat kelulusan tahap pendidikan strata-1 pada\\
Program Studi Fisika -- Institut Teknologi Bandung\\[1.8cm]
\end{onehalfspace}

\large Oleh: \\
\begin{onehalfspace}
\large{\penulis} \\
\large{\nim}\\[1.5cm]
\end{onehalfspace}
\vspace{1.5cm}

% EDIT PEMBIMBING, udah deh sampul2. :D
\large Pembimbing: \\
\begin{onehalfspace}
\large{\pembimbingsatu} \\
\large{\pembimbingdua}
\end{onehalfspace}

\vfill

% bagian bawah
\textbf{\large \MakeUppercase{program studi fisika}}\\
\textbf{\large \MakeUppercase{fakultas matematika dan ilmu pengetahuan alam}}\\
\textbf{\large \MakeUppercase{institut teknologi bandung}}\\
\textbf{\large 2021}\\
\end{center}

### 2024-05-06 skripsi/bab2.tex
remove ignored files

@@
 
-\section{Sub Bab A} 
-\noindent Teori dasar yang dituliskan pada sub bab ini dapat berupa konsep-konsep fundamental yang menjadi landasan pekerjaan penelitian, dan bisa saja sebagiannya terdapat pada buku teks atau artikel review.
-Pemahaman tentang teori dan konsep dasar ini, termasuk konsep pendukung seperti statistika atau numerik, harus tampak pada paparan yang diulas dalam sub bab ini.
+\section{Least Squares Support Vector Machine}
+\noindent An arguably fundamental model widely used whether in pedagogical settings or otherwise is the support vector machine.
+It dates back to works by Vapnik \& Lerner in 1963 (Recognition of Patterns with help of Generalized Portraits) and V.
+N.
+Vapnik \& A.
+Ya.
+Chervonenkis in 1964 (A note on one class of perceptrons/On a perceptron class).
+As the development on SVM continued, what originally was a model for classification of separable data generalized to regression tasks as well Vapnik (2000 The Nature of Statistical Learning Theory).
+
+To derive the least squares support vector regression (J.A. Suykens LSSVM Book) model we start with the linear expression:
+
+\begin{equation}
+        y=W^{\intercal}\vb{x}+b
+\end{equation}
+
+\begin{equation}
+        \min_{W,e} J(W,e) = \frac{1}{2}W^{\intercal}W + C\frac{1}{2}\sum_{k=1}^{n}e_{k}
+\end{equation}
+
+Such that
+\begin{equation}
+        y_{k}=W^{\intercal}\vb{x}_{k}+b+e_{k} \qquad k=1,\dots,n
+\end{equation}
+
+\begin{equation}
+        L(W,b,e;\vb{\alpha}) = \frac{1}{2}W^{\intercal}W + C\frac{1}{2}\sum_{k=1}^{n}e_{k} + \sum_{k=1}^{n}\alpha_{k} \left(W^{\intercal}\vb{x}_{k}+b+e_{k} - y_{k} \right)
+\end{equation}
+
+Derive the KKT system
+\begin{equation}
+        \begin{split}
+                \pdv{L}{W} = 0 \rightarrow & W = \sum_{k=1}^{n}\alpha_{k}x_{k} \\
+                \pdv{L}{b} = 0 \rightarrow & \sum_{k=1}^{n}\alpha_{k} = 0 \\
+                \pdv{L}{e_{k}} = 0 \rightarrow & \alpha_{k} = C e_{k} & \qquad k=1,\dots,n\\
+                \pdv{L}{\alpha_{k}} = 0 \rightarrow & W^{\intercal}\vb{x}_{k}+b+e_{k} - y_{k} = 0 & \qquad k=1,\dots,n\\
+        \end{split}
+\end{equation}
+
+After eliminating $W$ and $\vb*{e}$, with $\vb{1}_{n} = \langle 1,\dots,1\rangle$, $\vb{y} = \lbrack y_1, \dots, y_n \rbrack $, and ${\alpha} = \lbrack \alpha_1, \dots, \alpha_n \rbrack $ the solution is as follows in block matrix notation
+\begin{equation} \label{eq:lssvrSolution}
+        \begin{bmatrix}
+                0          & \vb{1}_{n}^{\intercal} \\
+                \vb{1}_{n} & \Omega + \frac{I}{C}
+        \end{bmatrix}
+        \begin{bmatrix}
+                b           \\
+                \vb{\alpha} \\
+        \end{bmatrix}
+        =
+        \begin{bmatrix}
+                0      \\
+                \vb{y} \\
+        \end{bmatrix}
+\end{equation}
+
+The solution in \cref{eq:lssvrSolution}
+
+\begin{algorithm}[H]
+        \caption{LSSVR Training}\label{alg1:cap}
+        \begin{algorithmic}[1]
+                \Require $\vb{X}, \vb{y}, \gamma$
+                \Ensure $\vb{\alpha}, b$
+                \State $\Omega \gets [[]]$ \Comment{Construct matrix of inner products in high dimensional space}
+
+                \For{$k=0 \to n$}
+                \For{$l=0 \to n$}
+                \State$\Omega_{k,l}\gets K(\vb{X}_k,\vb{X}_l)$
+                \EndFor
+                \EndFor
+                \State $\vb{H} \gets \Omega + \frac{\vb{I}}{\gamma}$
+                % \State $\vb{1} \gets [1,1,...,1]$
+                \State $\vb{A} \gets [[]]$ \Comment{Construct left hand side matrix}
+                \State $\vb{A}_{0,0} \gets 0$
+                \For{$k=0 \to n$}
+                \State $\vb{A}_{k+1,0} \gets 1$
+                \State $\vb{A}_{0,k+1} \gets 1$
+                \EndFor
+                \For{$k=0 \to n$}
+                \For{$l=0 \to n$}
+                \State $\vb{A}_{k+1,l+1} \gets \vb{H}_{k,l}$
+                \EndFor
+                \EndFor
+                \State $\vb{B}\gets []$ \Comment{Construct left hand side of the equation}
+                \State $\vb{B}_0 \gets 0$
+                \For{$k=0 \to n$}
+                \State $\vb{B}_{k+1} \gets \vb{y}_{k}$
+                \EndFor
+                \State $\vb{A}^{\dagger} \gets pseudoInverse(\vb{A})$ \Comment{Compute solution using pseudo inverse}
+                \State $\vb{S} \gets \vb{A}^{\dagger}\vb{B}$
+                \State $b \gets \vb{S}_{0}$
+                \For{$k=0 \to n$}
+                \State $\vb{\alpha}_{k} \gets \vb{S}_{k+1}$
+                \EndFor
+        \end{algorithmic}
+\end{algorithm}
+
+The basic psuedocode from the LSSVM Equation for function regression is defined in \nameref{alg1:cap} for a training set of length $n$, features $\vb{X}$, and labels $\vb{y}$.
+Training the LSSVM means computing the values of langrange multipliers $\vb{\alpha}$ and bias $b$.
+$K$ is the kernel function used to compute the inner products in high dimensional space, here we asume the RBF kernel.
+$\vb{A}$ is a matrix of size $n+1$ by $n+1$.
+$\vb{H}$ is a matrix of size $n$ by $n$.
+$\vb{I}$ is the identity.
+$\vb{B}$ is a vector of size $n+1$.
+$\vb{S}$ is a vector of size $n+1$.
+
+After training the model can be used for prediction of unseen points.
+The psuedocode for prediction is shown in \nameref{alg2:cap} for prediction features $\vb{U}$.
+The trained model uses the learned multipliers of training points $\vb{\alpha}$, the training points themselves $\vb{X}$, and the bias $b$.
+
+\begin{algorithm}[H]
+        \caption{LSSVR Prediction}\label{alg2:cap}
+        \begin{algorithmic}[1]
+                \Require $\vb{U}, \vb{\alpha}, \vb{X}, b$
+                \Ensure $\vb{v}$
+                \State $\Omega \gets [[]]$ \Comment{Construct matrix of inner products in high dimensional space}
+
+                \For{$k=0 \to m$}
+                \For{$l=0 \to n$}
+                \State$\Omega_{k,l}\gets K(\vb{U}_{k},\vb{X}_l)$
+                \EndFor
+                \EndFor
+                \State $\vb{v} \gets \Omega\vb{\alpha} + \vb{1}_{m}b$
+        \end{algorithmic}
+\end{algorithm}
+
+In this exmple we will be using the function $2x^2+4$. The values of this function can be seen in Table \ref{table:1}.
+
+\begin{table}[H]
+        \centering
+        \begin{tabular}{@{}lll@{}}
+                \toprule
+                No & x       & y       \\ \midrule
+                1  & 0.0     & 4.0     \\
+                2  & 0.33... & 4.22... \\
+                3  & 0.66... & 4.88... \\
+                4  & 1.0     & 6.0     \\
+                \bottomrule
+        \end{tabular}
+        \caption{Example data of function $2x^2+4$} \label{table:1}
+\end{table}
+For $\Omega_{i,j}=K(x_i,x_j)=exp \left(-\frac{\norm*{x_i-x_j}^2}{2\sigma^2}\right)$
+
+For example, with $\sigma=1$, $x_i=0.0$, \& $x_j = 0.33\dots$
+\begin{equation}
+        \begin{split}
+                K(0.0,0.33) & = exp\left(-\frac{\norm*{0.0-0.33}^2}{2(1)^2}\right) \\
+                & = exp\left(-\frac{0.33^2}{2}\right) \\
+                & = 0.9460
+        \end{split}
+\end{equation}
+
+\begin{equation}
+        \Omega\gets
+        \begin{bmatrix}
+                1.0000 & 0.9460 & 0.8007 & 0.6065 \\
+                0.9460 & 1.0000 & 0.9460 & 0.8007 \\
+                0.8007 & 0.9460 & 1.0000 & 0.9460 \\
+                0.6065 & 0.8007 & 0.9460 & 1.0000 \\
+        \end{bmatrix}
+\end{equation}
+
+\begin{equation}
+        \vb{I}\frac{1}{\gamma}\to\vb{I}\frac{1}{5}\to
+        \begin{bmatrix}
+                0.2000 & 0.0000 & 0.0000 & 0.0000 \\
+                0.0000 & 0.2000 & 0.0000 & 0.0000 \\
+                0.0000 & 0.0000 & 0.2000 & 0.0000 \\
+                0.0000 & 0.0000 & 0.0000 & 0.2000
+        \end{bmatrix}
+\end{equation}
+
+\begin{equation}
+        \Omega+\vb{I}\frac{1}{5}\to H\to \begin{bmatrix}
+                1.2000 & 0.9460 & 0.8007 & 0.6065 \\
+                0.9460 & 1.2000 & 0.9460 & 0.8007 \\
+                0.8007 & 0.9460 & 1.2000 & 0.9460 \\
+                0.6065 & 0.8007 & 0.9460 & 1.2000 \\
+        \end{bmatrix}
+\end{equation}
+
+\begin{equation}
+        A\to \begin{bmatrix}
+                0.0000 & 1.0000 & 1.0000 & 1.0000 & 1.0000 \\
+                1.0000 & 1.2000 & 0.9460 & 0.8007 & 0.6065 \\
+                1.0000 & 0.9460 & 1.2000 & 0.9460 & 0.8007 \\
+                1.0000 & 0.8007 & 0.9460 & 1.2000 & 0.9460 \\
+                1.0000 & 0.6065 & 0.8007 & 0.9460 & 1.2000 \\
+        \end{bmatrix}
+\end{equation}
+
+\begin{equation}
+        B\to \begin{bmatrix}
+                0.0000 \\
+                4.0000 \\
+                4.2222 \\
+                4.8889 \\
+                6.0000 \\
+        \end{bmatrix}
+\end{equation}
+
+\begin{equation}
+        A^{\dag}\to \begin{bmatrix}
+                -0.8994 & 0.4348  & 0.0652  & 0.0652  & 0.4348  \\
+                0.4348  & 2.0686  & -1.6490 & -0.5292 & 0.1096  \\
+                0.0652  & -1.6490 & 3.3774  & -1.1992 & -0.5292 \\
+                0.0652  & -0.5292 & -1.1992 & 3.3774  & -1.6490 \\
+                0.4348  & 0.1096  & -0.5292 & -1.6490 & 2.0686  \\
+        \end{bmatrix}
+\end{equation}
+
+\begin{equation}
+        A^{\dag}B\to S\to \begin{bmatrix}
+                4.9421  \\
+                -0.6177 \\
+                -1.3737 \\
+                -0.5625 \\
+                2.5538  \\
+        \end{bmatrix}
+\end{equation}
+
+\begin{equation}
+        b\to 4.9421
+\end{equation}
+
+\begin{equation}
+        \alpha \to \begin{bmatrix}
+                -0.6177 \\
+                -1.3737 \\
+                -0.5625 \\
+                2.5538  \\
+        \end{bmatrix}
+\end{equation}
+
+Prediction
+\begin{equation}
+        U\to \begin{bmatrix}
+                0.3 \\
+                0.2 \\
+                0.5
+        \end{bmatrix}
+\end{equation}
+
+\begin{equation}
+        \Omega\to \begin{bmatrix}
+                0.9560 & 0.9994 & 0.9350 & 0.7827 \\
+                0.9802 & 0.9912 & 0.8968 & 0.7261 \\
+                0.8825 & 0.9862 & 0.9862 & 0.8825 \\
+        \end{bmatrix}
+\end{equation}
+
+\begin{equation}
+        \Omega\alpha\to \begin{bmatrix}
+                -0.4904 \\
+                -0.6170 \\
+                -0.2008 \\
+        \end{bmatrix}
+\end{equation}
+
+\begin{equation}
+        \Omega\alpha+b\vb{1}_{m}\to v\to \begin{bmatrix}
+                4.4516 \\
+                4.3251 \\
+                4.7413 \\
+        \end{bmatrix}
+\end{equation}
+Where $\vb{1}_{m}$ is a vector of 1s with the length of $U$.
 
@@
         \begin{align}
-    \frac{dy}{dt} &= -x ,\\
-    \frac{dx}{dt} &= -y .
+                \frac{dy}{dt} & = -x , \\
+                \frac{dx}{dt} & = -y .
         \end{align}
@@
         \sigma_x = \begin{pmatrix}
-                0 & 1\\
+                0 & 1 \\
                 1 & 0
@@
         \sigma_y = \begin{pmatrix}
-                0 & -i\\
+                0 & -i \\
                 i & 0
@@
         \sigma_z = \begin{pmatrix}
-                1 & 0\\
+                1 & 0  \\
                 0 & -1

### 2024-06-04 skripsi/bab1.tex
change to biblatex, start background

\chapter{INTRODUCTION}
\section{Background}
\label{sec:background} %pelabelan ini opsional, biar bisa di klik kalo mengarahkan ke section tertentu.

\noindent Non-destructive testing (NDT) is critical process in the field of engineering and quality assurance that allows the evaluation of a subject without causing damage \autocite{howell2020nondestructive, maioUltrasoundPropagationComposite2022, bochudSparseDigitalSignal2015}. This makes NDT crucial in many cases like construction and manufacturing where testing needs to be done on products without damaging it. The use of NDT allows for early detection of flaws and anomalies ensuring the reliability, longevity, and safety of structures and machinery. A widely used form of NDT, ultrasonic testing, propagates mechanical waves into the material. The ultrasonic waves, typically in the kHz to MHz range, travel through the material and interact with inhomogeneities in the material ie. waves reflected by a cavity. This makes it possible to determine the location, size, and nature of deformities by analyzing the waves measured at predetermined locations. The measurements themselves result in a time series of wave amplitudes represented as displacement. The data can be presented as shown in \Cref{fig:us_presentation}. The amplitude time series by itself is referred as an A-Scan. B-Scans take measurements at multiple locations to show a cross section of the subject. C-Scans adds another dimension of measurements and presents a view of things that reflect the waves such as defects. Analysis of the ultrasonic data can then be carried out. When the material can be assumed homogeneous, ray based or time of flight based methods can be used. In pulse echo, the wave travels through the material and gets reflected by interfaces, whether the other side of the material, fractures within, or generally modulus/density discontinuities present in the material. This means the measurements would record a large amplitude initially from the impulse sent into the material. And then the reflected waves from the closest interface would arrive. This way, just by knowing the exact wave speed of the material, one could easily translate reflected wave arrival time into the positions of interfaces.

\begin{figure}[ht]
\centering
\includesvg[inkscapelatex=false, width=1.0\linewidth]{gambar/us scan presentations}
%\includegraphics[width=1.0\linewidth]{gambar/us scan presentations.png}
\caption{Different presentations of ultrasonic scan data. The subject is a box containing several anomalies indicated by the yellow oval and red triangle. The fist presentation is the A-Scan where the amplitude measured over time in one location. The second is B-Scan where the amplitudes over time is measured along a line. The results are then stacked with the vertical axis acting as time and the horizontal axis as position. The higher amplitudes correspond to lighter pixels. The third presentation is C-Scan which is a view of the amplitudes of reflected waves except the initial impulse and back wall reflection.}
\label{fig:us_presentation}
\end{figure}

Ultrasonic NDT has advantages that makes it one of the more widely used NDT methods \autocite{howell2020nondestructive, nivenFullWaveformInversion2020, feliceSizingFlawsUsing2018}. One advantage is that ultrasonic testing equipment is often portable making it suitable for cases where it is difficult or not possible to test in a controlled environment such as a laboratory. Inspections for infrastructure such as pipes or rail tracks are examples where it is costly and very disruptive to move the test subject to a testing location \autocite{}. Another advantage of ultrasonic testing is the low risk it poses in terms of safety. Unlike the ionizing radiation used in radiography, ultrasonic waves used in testing are harmless to humans. This means testing can be done with relatively less stringent safety precautions \autocite{}. Additionally, the technology is relatively mature with a variety of equipment and supplier options. Furthermore, affordable options for inexpensive ultrasonic equipment is also available \autocite{}. These advantages and the popularity of ultrasonic testing stemming from the aforementioned advantages highlights the important role ultrasonic testing plays in enabling affordable and reliable engineering.

%Talk about the process of A-scans, B-scans, C-scans. Talk about why its hard to analyze for more complex situations which are gaining popularity ie. composites.

The emergence of composites, sought after for their multi-functional properties, introduces challenges for inspection and analysis \autocites{inceOverviewEmergingHybrid2023, yangUltrasonicDetectionMethods2023, dwivediAdvancesResearchesNon2018, nivenFullWaveformInversion2020}. Different composites provide a range of benefits, from the strength to weight ratio of carbon fiber reinforced polymer composites to electromagnetic shielding materials. However, the anisotropic and complex characteristic of composites that give rise to the beneficial properties complicates wave propagation because of the location and directional dependence of material properties. For example wave speed can be faster in certain directions and locations. Reflections will happen not just because of anomalies, but also expected features in the material itself. Extraneous signals from inhomogeneities anticipated in the material makes it harder to extract useful information on unknown defects. In order to enable reliable use of ultrasonic NDT on composite materials and other complex situations, a method to quantify and characterize the complicated behavior is required \autocite{maioUltrasoundPropagationComposite2022}.

This is where model based methods come into play. Advances in computation over recent decades has enabled the use of computational tools to revolutionize many fields. Numerical modeling, in particular, has an almost symbiotic relationship with the rise of computing; with the likes of ENIAC, MANIAC, and a plethora of other early electronic digital computers \autocite{andersonScientificUsesMANIAC1986}. The ENIAC for example, promised to compute ballistic trajectories 10 times faster than the methods that were in used at the time. This progress allows the simulation and analysis of systems previously beyond reach. The effects range from prediction of weather systems and physics constrained problems like bleeding edge aerospace design to uncovering physical laws of nature.

Despite advances in computing power, numerical modeling of physical systems still remains an open problem with many challenges. Traditional methods such as Finite Element Method (FEM), Finite Difference Method (FDM), and Spectral Methods are limited to known operators and equations \autocite{karniadakisPhysicsinformedMachineLearning2021, du2024neural,fanaskovSpectralNeuralOperators2023,luLearningNonlinearOperators2021}. The modern data landscape further complicates traditional numerical modeling with its characteristic abundance of low quality, high quantity data, as some methods such as FDM are inherently sensitive to noise \autocite{dearagaoExplicitControlNumerical2021, huntulInverseProblemReconstructing2021}. Noisy data also presents a formidable challenge in general because gleaning any meaningful information from noisy and incomplete data requires further filtering and interpretation. This issue is particularly troubling for inverse problems. This is because some inverse problems are unstable in addition to their ill-posedness which necessitates advanced techniques \autocite{caubetInstabilityInverseProblem2013, mandacheExponentialInstabilityInverse2001}. The next layer of complexity is posed by the challenge of irregular domains. An example of this is fluid flow through materials such as gravel, sponges, even changing with time \autocite{liImmersedInterfaceMethod2006}. Due to the nature of irregular domains, mesh based methods struggle to adapt. Addressing these challenges is crucial for understanding a variety of problems in both scientific research and engineering.

%talk more about each challenge and the proposed solutions to it and how they do not fully cover the needs this work is trying to cover
The problem posed by model-based ultrasonic testing combines several of these challenges. First, visualizing properties of materials such as density from measurements of ultrasonic waves that interacted with the material is an inverse problem. This is because the effect is used to infer the cause. The challenge with inverse problems is that in many cases, the result is very sensitive to differences in the parameters \autocite{tarantolaInverseProblemTheory2005}; small variation in density distribution can result in very different measurements. As such, additional noise or inaccuracies in measurement can massively impact the predicted parameter. This very issue has been a long standing challenge in the geophysics community. The full waveform inversion (FWI) procedure used to determine properties of the earth, requires certain techniques such as a minimization criteria that mitigates this sensitivity \autocite{virieuxOverviewFullwaveformInversion2009}. Second, complex or irregular domains are a challenge for traditional mesh based methods as the domain may vary in time \autocite{liImmersedInterfaceMethod2006, burchnerImmersedBoundaryParametrizations2023}. Costly mesh generation hampers the performance of mesh based methods. In addition, some approaches like total focusing method (TFM), traveltime tomography (TT) and reverse time migration (RTM) are not able to provide more than a rough estimate of defects. Third, for some materials, there are little to no knowledge present in literature on how waves propagate through the material. Continued research has alleviated this issue by advanced our understanding of wave propagation and materials. \textcite{gordoaUltrasonicWavesBubbly2021} presented an analytic solution to ultrasonic wave propagation in bubbly liquids. \textcite{} . However, these solutions are not available for all situations and materials, as such is the case when a novel material is created. In some of these cases data collection may be easier to do compared to deriving from first principles.

%Talk about how composites, ndt, rapid prototyping, bigalow inflatable space habitat, etc is important to aerospace
Advances in computing technology and the integration of non-destructive testing have revolutionized the aerospace industry \autocite{guptaAdvancesApplicationsNonDestructive2022, jacobDataFusionEfficient2022}. This has had the effect of enabling rapid advancements in cutting-edge technologies such as vertical rocket landings, 3-D printed spacecraft, and in-space manufacturing to name a few \autocite{corradoSpaceExplorationEconomic2023}. These technologies addressed several key challenges with space exploration, namely cost, mission flexibility \& resilience, and environmental considerations. NDT plays a crucial role in ensuring the safety and quality of the innovations. The novelty of innovations means they do not have the luxury of being a proven solution.

%Talk about related works, using conventional methods, using nn, using other machine learning methods, using spectral methods.

Bagian ini mendeskripsikan gambaran umum, konteks, dan posisi penelitian TA dalam konstelasi perkembangan pengetahuan yang telah dicapai. Penjelasan yang dituliskan menjadi penting karena dengan landasan yang kuat, maka pekerjaan penelitian dapat terarah dilakukan. Hal ini lebih spesifik dan tegas disampaikan pada sub-sub bab berikutnya.

Beberapa pustaka utama yang berperan dominan dapat disampaikan di sini untuk memberi gambaran tentang letak penelitian TA dalam konstelasi keilmuan yang dicapai. Hasil-hasil dari pustaka terbaru dapat menopang Latar Belakang ini menjadi lebih kuat.

Sangat wajar apabila isi sub bab setelah Latar Belakang ini mengalami penyesuaian saat sejumlah hasil penelitian sudah diperoleh dan dianalisis. Pada dasarnya, hal ini dimungkinkan apabila ada penyesuaian kecil, karena fokus penelitian sejatinya sudah jelas sedari awal, namun hasil-hasil yang diperoleh dapat memperbaharui beberapa butir isi sub bab. Oleh karena itu, finalisasi isi Pendahuluan ini biasanya dilakukan menjelang akhir pembuatan laporan penelitian yang dituangkan dalam buku TA.

\section{Rumusan dan Batasan Masalah}
\noindent Bagian ini menjadi salah satu bagian penting dalam Pendahuluan. Setelah paparan Latar Belakang, maka masalah yang diangkat pada pekerjaan penelitian perlu dirumuskan dengan baik. Perumusan ini sebaiknya dibahasakan tidak dalam bentuk kalimat pertanyaan, melainkan kalimat aktif, dan dapat memuat lebih dari satu rumusan.

Sejalan dengan ini, setiap masalah yang diangkat selalu memiliki batas. Ada batasan, asumsi, atau kriteria yang menjadi pembatas atas masalah yang diangkat dalam penelitian TA, sehingga arah penelitian dapat fokus. Batasan ini perlu dituliskan secara tegas, dan dapat saja memuat lebih dari satu.

\section{Tujuan}
\label{sec:tujuan}
Bagian ini secara tegas menuliskan tujuan pekerjaan penelitian TA, yang dapat memuat lebih dari satu. Pemilihan kata kerja pada Tujuan ini sangat penting karena menggambarkan arah fokus dari jalinan upaya yang dilakukan.

\section{Metodologi}
Di sini disampaikan metodologi yang diterapkan pada pekerjaan penelitian TA. Beberpa di antaranya adalah pengamatan dan akuisisi data, eksperimen numerik, studi pustaka, teoretik atau analitik, dan semi analitik dengan komplemen numerik.

\section{Sistematika Penulisan}
\noindent Bagian ini adalah penutup Bab I yang menyampaikan  secara ringkas isi setiap  bab. Karena pembaca sudah sampai akhir Bab I, yang  berarti  sudah  mengetahui isinya, maka tidak perlu ditulis lagi rincian Bab I. Sebaiknya langsung dituliskan secara ringkas isi rincian bab-bab selanjutnya, misalnya, \textit{Setelah Pendahuluan pada Bab I ini, Bab II akan mengulas tentang ...}

Apabila diperlukan, dapat dituliskan konvensi khusus yang digunakan pada penulisan naskah buku TA ini, misalnya tanda titik menggantikan tanda desimal karena alasan kemudahan dan kejelasan dalam formulasi matematika.

### 2024-06-04 skripsi/bab3.tex
remove ignored files
change to biblatex, start background

@@
 
-\section{Model Komputasi}
-\noindent The DeepONet architecture contains an element that is difficult to optimize.
+\section{Computational Model}
+\noindent The proposed model derives inspiration from DeepONet, Neural Spectral methods, and Spectral Neural Operators.
+The method uses LSSVR to map between the input coefficients/functions and the solution coefficients.
+This mapping is the surrogate of the operator in the spectral domain.
+To exploit the nature of the problem, the kernel chosen has particular characteristics that makes it useful for the spectral/function domain.
+These are kernels such as the maximum distance between two functions or something that lies in the spectral domain favoring low/high frequencies depending on the particular problem.
 % \begin{mini}
@@
 \begin{mini!}|s|
-{\substack{W_b,b_b,W_t,b_t,\xi}}{\frac{1}{2}\Vert W_b\Vert_F^2 + \frac{1}{2}\Vert W_t\Vert_F^2 + \frac{c}{2}\sum_{i=1}^{l}\xi_i^2} {}{}
-\addConstraint{y_i}{=(W_b f_i+b_b)^\top(W_t v_i+b_t)+\xi_i,\quad}{i=1,\ldots,l}
+{\substack{\vb*{W_b},\vb*{W_t},\vb*{\xi}}}{\frac{1}{2}\Vert \vb*{W_b}\Vert_F^2 + \frac{1}{2}\Vert \vb*{W_t}\Vert_F^2 + \frac{c}{2}\sum_{i=1}^{N}\xi_i^2} {}{}
+\addConstraint{y_i}{=(\vb*{W_b} \vb*{f_i})^\top(\vb*{W_t} \vb*{v_i})+\xi_i,\quad}{i=1,\ldots,N}
 \end{mini!}
-
+Converting the optimization problem above to the lagrange formulation
 \begin{equation}
   \begin{aligned}
-    L(W_b,b_b,W_t,b_t,\xi;\alpha)= {} & \frac{1}{2}\Vert W_b\Vert_F^2 + \frac{1}{2}\Vert W_t\Vert_F^2 +\frac{c}{2}\sum_{i=1}^{l}\xi_i^2 \\ &+ \sum_{i=1}^{l}\alpha_i(y_i-\xi_i-(W_b f_i+b_b)^\top(W_t v_i+b_t))
+    L(\vb*{W_b},\vb*{W_t},\vb*{\xi};\vb*{\alpha})= {} & \frac{1}{2}\Vert \vb*{W_b}\Vert_F^2 + \frac{1}{2}\Vert \vb*{W_t}\Vert_F^2 +\frac{c}{2}\sum_{i=1}^{N}\xi_i^2 \\ &+ \sum_{i=1}^{N}\alpha_i(y_i-\xi_i-(\vb*{W_b} \vb*{f_i})^\top(\vb*{W_t} \vb*{v_i}))
   \end{aligned}
 \end{equation}
+Taking partial derivatives with respect to 
 \begin{equation}

### 2024-06-04 skripsi/sampuldalam.tex
change to biblatex, start background

@@
 
-\textbf{\MakeUppercase{\large tugas akhir}}\\[0.5cm]
+\textbf{\MakeUppercase{\large A Research Paper}}\\[0.5cm]
 \begin{onehalfspace}
-Diajukan untuk memenuhi syarat kelulusan tahap pendidikan strata-1 pada\\
-Program Studi Fisika -- Institut Teknologi Bandung\\[1.8cm]
+Submitted as partial fulfillment of the requirements for \textit{sarjana komputer} degree at\\
+Program Studi Ilmu Komputer -- Universitas Pendidikan Indonesia\\[1.8cm]
 \end{onehalfspace}
 
-\large Oleh: \\
+\large By: \\
 \begin{onehalfspace}
@@
 % EDIT PEMBIMBING, udah deh sampul2. :D
-\large Pembimbing: \\
+\large Supervisors: \\
 \begin{onehalfspace}
@@
 % bagian bawah
-\textbf{\large \MakeUppercase{program studi fisika}}\\
-\textbf{\large \MakeUppercase{fakultas matematika dan ilmu pengetahuan alam}}\\
-\textbf{\large \MakeUppercase{institut teknologi bandung}}\\
-\textbf{\large 2021}\\
+\textbf{\MakeUppercase{program studi ilmu komputer}}\\
+\textbf{ \MakeUppercase{fakultas pendidikan matematika dan ilmu pengetahuan alam}}\\
+\textbf{\MakeUppercase{UNIVERSITAS PENDIDIKAN INDONESIA}}\\
+\textbf{\the\year{}}\\
 \end{center}

### 2024-08-13 skripsi/bab1.tex
chapter 1 outline, WIP chapter 1: machine learning in physics history

@@
 \label{sec:background} %pelabelan ini opsional, biar bisa di klik kalo mengarahkan ke section tertentu.
+\noindent Partial differential equations (PDE) are a common tool widely used in the modern scientific understanding and many engineering processes.
+This is because many systems can be described by the way they change and often this can be more intuitive.
+As an example, when cooking with a frying pan on a stove top that is too small, notice that parts of the pan closer to the burner or heating element would heat up faster and stay hotter compared to the edge even after it stops heating up any further and reach a stable temperature.
+However, a more useful way to describe the system is using the heat equation.
+For a temperature function $u\left(\vb{x},t\right)$ of spatial coordinates vector $\vb{x}$ and time $t$, the heat equation is defined in \cref{eq:heat_equation}.
+\begin{equation} \label{eq:heat_equation}
+    \pdv{u}{t}=\alpha\laplacian u
+\end{equation}
+The Laplacian $\laplacian$ denotes sum of all second spatial derivatives.
+In three dimensions this is $\laplacian\cdot=\pdv{\cdot}{x_1}+\pdv{\cdot}{x_2}+\pdv{\cdot}{x_3}$.
+The constant $\alpha$ denotes how fast the heat spreads.
+Intuitively this equation says that the rate at which the temperature changes in time $\pdv{u}{t}$ is proportional to how different the temperature of a spot in the pan with its surroundings.
+One example of an insight this gives is that given the stove heat stays constant the temperature will no longer change for a particular point once the temperature difference is constant or in other words the function $u\left(\vb{x},t\right)$ approaches a linear function in space.
+Mathematically this is because of the Laplacian being second spatial derivatives.
+Intuitively, once the temperature distribution approaches linear, the current spot on the pan is outputting as much heat it is getting.
+
+Many other systems such as waves, quantum dynamics, fluid dynamics, elastics, and many more also define systems using PDEs.
+PDEs are also used outside of the physical sciences.
+In Finance, the Black-Scholes-Merton or Black-Scholes equation models the dynamics of the financial market.
+In ecology, PDEs are used to model population growth which is usefull for modelling location dependent carrying capacity.
+This is used to model species distribution which can help develop better conservation policies.
+In the social sciences, PDEs such as the cross-diffusion model is used to explore the evolution of the urban environment <https://doi.org/10.1038/s41598-023-38979-w>.
+Crowd dynamics is another field where researchers have found it useful to model using PDEs <https://doi.org/10.1016/S0378-4754(00)00228-7, https://doi.org/10.1109/TSMC.2015.2389763>.
+These are used to model dynamics such as shock-waves, pathing, and crowd flow as a whole.
+There are a variety of applications, ranging from brid flocks, pedestrian crowds, to robotic swarms <https://doi.org/10.1146/annurev-control-060822-123629>.
+
+Traditional numerical solvers used to solve PDEs have enjoyed many decades of development due to their long history.
+There are many general approaches to solve PDEs and many more very specific approaches.
+Some widely used approaches include Finite Element Methods (FEM), Finite Difference Methods (FDM), and Spectral Methods.
+FEM and FDM both are mesh based, meaning they rely on discretization of the computational domain <ADD DIAGRAM FOR THIS>.
+There are several challenges associated with this.
+First, irregular domains such as bone, spider silk, gravel, or other bio-inspired/aggregate materials,  pose a challenge due to the complexity of the domain geometry <https://doi.org/10.1016/0955-7997(91)90014-K, https://doi.org/10.1016/j.jcp.2007.03.025, https://doi.org/10.1038/s41467-024-47831-2>.
+Another issue is large deformations or mesh entanglement cause these methods to become ineffective <10.1061/(ASCE)EM.1943-7889.0001176>.
+While there are strategies to mitigate this, by deffinition they are an additional layer of difficulty to the process.
+Second, multi-scale applications where the micro and macro scales are both important require fine meshes such that the small scale structures are addequately simulated.
+This creates very large meshes that are very resource intensive <https://doi.org/10.1016/j.jcp.2007.03.025>.
+Therefore, in problems where these issues important, meshfree methods are prefered.
+One approach are Spectral methods which utilize basis functions to approaximate a global solution.
+A popular choice especially problems with known periodicity, are the Fourier Series.
+Another drawback of traditional methods are the requirement that PDEs and equations to solve be known analytically.
+This is because the solvers use the equations to formulate the solution.
+A dealbreaker like this makes traditional numerical approaches unsuited to data dominant problems.
+Third, a single evaluation of traditional solvers may not be very costly, multiple evaluations can add up.
+This is very apparent in inverse problems and other applications where multiple evaluations of the solver is required.
+
+With the increasing prevalance of machine learning methods and their use in more and more fields, research into their use for scientific computing has taken off in recent years.
+While statistical modeling has already been widely used in areas such as physical constants, stellar population studies, risk assesments of events such as earthquakes and coronal mass ejections <geophysics constants: 10.1029/2002JD002865, CME: https://doi.org/10.1016/j.asr.2005.04.089, asteroid: https://doi.org/10.1111/risa.12453, physics constants: https://doi.org/10.1103/RevModPhys.75.403, http://dx.doi.org/10.1214/074921706000000419, stellar population: https://doi.org/10.1093/mnras/stac3287>, the most widespread approach for forward modeling or inverse modeling are physics based numerical models.
+With the rise of machine learning methods research into their use for solving PDEs have also expanded.
+
+Another aproach to this starts by viewing PDEs as operators, which are generalized mappings between spaces.
+Familiar operators are functions which are mappings spaces of scalar values or vector values.
+PDEs on the other hand are operators that map between function spaces.
+A simple example is the derivative.
+It takes in a function and returns the derivative of said function.
+In other words it is an operator that maps between the space of all functions to the space of derivatives of those functions.
+Another way to view this is by imagining functions as infinite dimensional vectors.
+Where elements in the vector are the function's value evaluated at every point.
+The operator can be seen as vector functions mapping between these infinite dimensional vector spaces.
+Operators are important because a field of research has sprung up around this mathematical concept.
+Operator learning is the use of machine learning to learn operators from a data driven approach.
+As an analogy, regression traditionally has been used to approximate the mapping of functions.
+In the case of operator learning, a mapping between functions may be approximated.
 

### 2024-08-17 skripsi/bab1.tex
add related works in using ML in solving PDEs, limitations outline WIP

--- 2024-06-04 skripsi/bab1.tex
@@
 \chapter{INTRODUCTION}
-\section{Background}
-\label{sec:background} %pelabelan ini opsional, biar bisa di klik kalo mengarahkan ke section tertentu.
+\section{Background}\label{sec:background} %pelabelan ini opsional, biar bisa di klik kalo mengarahkan ke section tertentu.
+\noindent Partial differential equations (PDE) are a common tool widely used in the modern scientific understanding and many engineering processes.
+This is because many systems can be described by the way they change and often this can be more intuitive.
+As an example, think of someone heating up a large frying pan on a gas stove.
+To describe how the pan heats up when the center is right above the burner, one can say that the center would heat up first followed by its surroundings.
+Eventually the pan would not heat up any further.
+Also notice that the edges of the pan would always be cooler than the center.
+However, once a more complex setup is introduced such as an uneven heat source or more complex materials with different heat rates of transferring heat it becomes much harder to describe how the pan heats up.
+A more useful way to describe the system is using the heat equation.
+For a temperature function \(u\left(\vb{x},t\right)\) of spatial coordinates vector \(\vb{x}\) and time \(t\), the generalized heat equation is defined in \cref{eq:heat_equation}.
+\begin{equation} \label{eq:heat_equation}
+    \pdv{u}{t}=\divergence{\left(\alpha \gradient u\right)}
+\end{equation}
+The divergence operator \(\divergence \) denotes sum of all first spatial derivatives.
+In three dimensions this is \(\divergence=\pdv{\cdot}{x_1}+\pdv{\cdot}{x_2}+\pdv{\cdot}{x_3}\).
+And the gradient operator \(\gradient \) is the vector of all first spatial derivatives which in three dimensions is \(\gradient{f} = {\begin{bmatrix}\pdv{f}{x_1} & \pdv{f}{x_2} & \pdv{f}{x_3}\end{bmatrix}}^{\intercal}\).
+This equation says that the rate at which the temperature changes in time \(\pdv{u}{t}\) is proportional to how different the differences in temperature of a spot in the pan with its surroundings \(\laplacian{u}\) multiplied with thermal diffusivity parameter \(\alpha \).
+One example of an insight this gives is that given a homogeneous material (\(\alpha \) is constant) and the stove outputs heat at a constant rate the temperature will no longer change for a particular point once the temperature difference is constant.
+In other words once the function \(u\left(\vb{x},t\right)\) at some time \(t > 0 \) approaches a linear function in space, the temperature at all spots will no longer change in time.
+Mathematically this is because the time derivative is zero if the second spatial derivatives are also zero.
+Intuitively this is because once the temperature distribution approaches linear, the current spot on the pan is outputting as much heat it is getting.
+This insight is an example of why PDEs are usefull.
+
+Many other fields in physics such as waves, quantum dynamics, fluid dynamics, elastics, and many more also define systems using PDEs.
+PDEs are also used outside the physical sciences.
+In Finance, the Black-Scholes-Merton or Black-Scholes equation models the dynamics of the financial market.
+In ecology, PDEs are used to model population growth which is useful for modelling location dependent carrying capacity.
+This is used to model species distribution which can help develop better conservation policies.
+In the social sciences, PDEs such as the cross-diffusion model is used to explore the evolution of the urban environment \autocite{jinDetectingInteractionUrban2023}.
+Crowd dynamics is another field where researchers have found it useful to model using PDEs \autocite{mukherjeeLagrangianApproachModeling2015,hughesFlowLargeCrowds2000}.
+These are used to model dynamics such as shock-waves, pathing, and crowd flow as a whole.
+There are a variety of applications, ranging from bird flocks, pedestrian crowds, to robotic swarms \autocite{gongCrowdDynamicsModeling2023}.
+
+The scenario in which PDEs are used to simulate a system typically means computing an unknown quantity like the temperature field of an object over time from a set of known parameters such as initial conditions and material parameters such as thermal diffusivity in the case of the heat equation.
+This scenario is termed the forward problem.
+The inverse problem on the other hand solves for an unknown parameter using other known parameters and observations of the partial solution such as temperature field at the object's surface.
+Traditional methods used to solve these problems utilized knowledge of the exact equations to numerically solve PDEs.
+As an example, the Finite Difference Method (FDM) approximates the solution by substituting the partial derivatives with finite differences such as the first derivative approximation in \cref{eq:forward_finite_difference_1}.
+\begin{equation} \label{eq:forward_finite_difference_1}
+    \pdv{f\left(x\right)}{x} \approx \frac{f\left(x+h\right)-f\left(x\right)}{h}
+\end{equation}
+
+Traditional numerical solvers have enjoyed many decades of development due to their long history.
+There are many general approaches to solve PDEs and many more very specific approaches.
+Other than FDM, some widely used approaches include Finite Element Methods (FEM), Finite Volume Methods (FVM), Collocation Methods, and Spectral Methods.
+FEM and FDM are both mesh based approaches, meaning they rely on discretization of the computational domain <ADD DIAGRAM FOR THIS>.
+There are several challenges associated with this.
+First, irregular domains such as bone, spider silk, gravel, or other bio-inspired or aggregate materials pose a challenge due to the complexity of the domain geometry \autocite{gaulSimulationWavePropagation1991,buoniEfficientScalableNumerical2007,jiaModulateStressDistribution2024}.
+Also, irregular domains which create large deformations or mesh entanglement cause these methods to become ineffective \autocite{chenMeshfreeMethodsProgress2017}.
+While there are strategies to mitigate this, by definition they are an additional layer of difficulty to the process.
+Second, multiscale applications where the micro and macro scales are both important require fine meshes such that the small scale structures are adequately simulated.
+This creates meshes with very large number of points that are very resource intensive \autocite{buoniEfficientScalableNumerical2007}.
+Therefore, in problems where these issues important or resources are limited, mesh-free methods are preferred.
+Third, traditional methods require prior knowledge of analytic forms of PDEs.
+This is because the solvers use the equations to formulate the solution.
+A dealbreaker like this makes traditional numerical approaches unsuited to data dominant problems.
+Fourth, a single evaluation of traditional solvers may not be very costly, however multiple evaluations can add up.
+This is very apparent in inverse problems where the solver is evaluated multiple times to compute gradients in order to obtain parameter functions.
+These challenges altogether have motivated research into alternative methods that do not completely rely on prior knowledge, mesh free, and fast enough when computing solutions from parameters.
+
+With the increasing prevalence of machine learning methods and their use in more and more fields, research into their use for scientific computing has taken off in recent years.
+While statistical modeling has already been widely used in areas such as physical constants, stellar population studies, risk assessments of events such as earthquakes and coronal mass ejections \autocite{berlinerPhysicalStatisticalModeling2003,anselmoComputationalMethodsReentry2005,reinhardtAsteroidRiskAssessment2016,uzanFundamentalConstantsTheir2003,spanosWhereStatisticalModels2006,bernardiStellarPopulationAnalysis2022}, the dominant approach for forward modeling or inverse modeling has remained physics based numerical models.
+Machine learning has provided an alternative approach to model the solutions of PDEs.
+In their work, \textcite{aartsNeuralNetworkMethod2001} utilized neural networks to approximate each term of PDEs describing damped and undamped free vibrations and substituting them into the PDEs and associated initial conditions.
+The network parameters were then optimized to reduce the PDE residual and boundary condition loss using evolutionary algorithms.
+This approach was taken in order to make machine learning models more transparent which at the time was being pursued because of the high cost of optimizing uncertainties in water management numerical simulators.
+However, since this method approximates the mapping between coordinates and the values of a function and their derivatives, retraining would be necessary for changes to the function itself.
+This could become very costly as retraining costs accumulate.
+A more recent approach that also utilizes soft constrains from PDE residuals is termed physics informed neural network (PINN) \autocite{raissiPhysicsinformedNeuralNetworks2019}.
+The authors propose a framework that leverages advancements in computing, namely automatic differentiation (AD) techniques made readily available by modern machine learning libraries.
+In general, PINNs use AD to compute each term of the PDE from the output of the model and this is then substituted into the PDE to in order to compute the residuals and loss from boundary conditions.
+The network residual and boundary loss are then weighted and summed with the data loss.
+For a neural network \(\hat{u}\left(\vb{x},t\right)\) approximating the real solution \(u\left(\vb{x},t\right)\), the residual loss for the heat equation in \cref{eq:heat_equation} is \cref{eq:heat_pinn_loss}.
+One issue with using AD to compute the residual is that the network input needs to be the independent variable (i.e.\ coordinates, time, etc.).
+This once again means that if one wants to compute a different solution, the network needs to be retrained.
+\begin{equation}\label{eq:heat_pinn_loss}
+    \mathcal{L}_{PDE}={\left(\pdv{\hat{u}\left(\vb{x},t\right)}{t}-\divergence{\left(\alpha \gradient \hat{u}\left(\vb{x},t\right)\right)}\right)}^2
+\end{equation}
+Other works utilize convolutional neural networks (CNN) to compute the solution from input functions such as forcing terms or initial conditions.
+This approach generally means discretizing the functions on a grid and using these as training data.
+One study by \textcite{wangPhysicsinformedDeepLearning2020} predicts turbulent flow using spatial and temporal decomposition and a specialized U-Net, an architecture based on CNNs, to predict the velocity field from the decomposition of the previous velocity field.
+Part of the loss function is a regularization term for zero divergence in the velocity field to enforce incompressible fluid flow.
+This term was calculated using finite differences since auto differentiation is not applicable in this situation.
+Finite differences was also utilized in another CNN based fluid flow upscaling model by \textcite{gaoSuperresolutionDenoisingFluid2021} to compute the residual terms of the steady incompressible Navier-Stokes equation.
+This model also inferred unknown physical parameters such as boundary conditions.
+However, this approach would mean the model would need to scale as a quadratic in 2D, cubic in 3D, and much steeper in higher dimensions.
+Outside fluid dynamics, the combination of specialized CNNs and finite differences or another numerical differentiation method have been used for many other PDEs including Poisson's equation for temperature fields \autocite{zhaoPhysicsinformedConvolutionalNeural2023, gaoPhyGeoNetPhysicsinformedGeometryadaptive2021}, velocity models from seismic data \autocite{mullerDeepPretrainedFWI2023}, and seismic response of structures \autocite{zhangPhysicsguidedConvolutionalNeural2020,niMultiEndPhysicsInformedDeep2022}.
+While the use of CNNs mean that discretization is implied, solutions of different initial conditions or parameter functions can be computed by inference and no retraining is required.
+
+The mapping between discretized functions done by CNNs are related to an alternative approach that starts by viewing PDEs as operators, which are generalized mappings between spaces.
+One group of familiar operators are functions which maps between spaces of scalar values or vector values.
+PDEs on the other hand are operators that map between function spaces.
+A simple example is the derivative.
+The derivative takes in a function and returns the derivative of said function.
+In other words it is an operator that maps between the space of all functions to the space of derivatives of those functions.
+Another way to view operators starts by viewing functions as infinite dimensional vectors.
+Where elements in the vector are the function's value evaluated at every point in space.
+The operator can be seen as a vector function mapping between these infinite dimensional vector spaces.
+Operators are important because a field of research has sprung up around this mathematical concept.
+Operator learning is the use of machine learning to learn operators using data driven approaches.
+As an analogy, function regression traditionally has been used to approximate the mapping between input values such as coordinates and output values of functions evaluated at said coordinates.
+In the case of operator learning, the mapping between function spaces are approximated.
+The aforementioned approaches using CNNs does this directly using the values of functions at discrete points.
+There are other approaches like DeepONet that does not require the uniform grid like CNNs \autocite{luLearningNonlinearOperators2021}.
+This architecture instead uses both input functions and coordinates as inputs.
+The output is the output function evaluated at the coordinates provided.
+This architecture is based on an extension for deep learning of the universal operator approximation theory for neural networks first proposed almost three decades ago at the time of writing by \textcite{chenUniversalApproximationNonlinear1995}.
+The proposed architecture is composed of two sub-networks, where one termed the trunk \(\hat{\vb{T}}\left(\vb{x},t\right)\)learns the latent mapping for coordinates and the other network termed the branch \(\hat{\vb{B}}\left(\vb{f}\right)\) learns the latent mapping for the input function \(f \).
+The two latent mappings are combined through a dot product to obtain the approximated output function value \(u \left( \vb{x}, t \right)\).
+This is formulated in \cref{eq:universal_op_approx_nn}.
+\begin{equation}\label{eq:universal_op_approx_nn}
+    u\left( \vb{x}, t \right) \approx \hat{G}\left( \vb{f} \right)\left( \vb{x}, t \right) = \hat{\vb{B}}\left( \vb{f} \right) \cdot \hat{\vb{T}}\left( \vb{x}, t \right)
+\end{equation}
+Fourier Neural Operators is an alternative avenue for learning operators by utilizing the fact that functions can be decomposed into linear combinations of basis functions, namely trigonometric basis in this particular case \autocite{li2021fourier}.
+With this method the input function value is mapped to its corresponding output function value.
+This is done by first lifting the input function value to a higher dimension using a neural network and this is then passed through blocks composed of a Fourier transform, then a linear transform and filtering of higher modes, and finally the inverse Fourier transform.
+These blocks are stacked to a desired depth and finally another network projects the outputs to the target dimension.
+The reason a linear can be used is that differentiation is multiplication in the Fourier domain.
+One drawback with FNO is the requirement that output functions are not parameterized by coordinates and therefore is implicitly relative to the input function coordinates.
+To avoid this issue, \textcite{fanaskovSpectralNeuralOperators2023} reframes the problem by directly utilizing the coefficients of the input function computed using Fourier transform to predict the coefficients of the output function in terms of coefficients a Fourier series.
 
@@
 A widely used form of NDT, ultrasonic testing, propagates mechanical waves into the material.
-The ultrasonic waves, typically in the kHz to MHz range, travel through the material and interact with inhomogeneities in the material ie.
+The ultrasonic waves, typically in the kHz to MHz range, travel through the material and interact with inhomogeneities in the material i.e.
 waves reflected by a cavity.
@@
 The amplitude time series by itself is referred as an A-Scan.
-B-Scans take measurements at multiple locations to show a cross section of the subject.
+B-Scans take measurements at multiple locations to show a cross-section of the subject.
 C-Scans adds another dimension of measurements and presents a view of things that reflect the waves such as defects.
@@
 
-Ultrasonic NDT has advantages that makes it one of the more widely used NDT methods \autocite{howell2020nondestructive, nivenFullWaveformInversion2020, feliceSizingFlawsUsing2018}.
+Ultrasonic NDT has advantages that make it one of the more widely used NDT methods \autocite{howell2020nondestructive, nivenFullWaveformInversion2020, feliceSizingFlawsUsing2018}.
 One advantage is that ultrasonic testing equipment is often portable making it suitable for cases where it is difficult or not possible to test in a controlled environment such as a laboratory.

### 2024-08-22 skripsi/bab1.tex
finish Ch 1 draft, move figures

@@
 A more useful way to describe the system is using the heat equation.
-For a temperature function \(u\left(\vb{x},t\right)\) of spatial coordinates vector \(\vb{x}\) and time \(t\), the generalized heat equation is defined in \cref{eq:heat_equation}.
+For a temperature function \(u\left(\vb{x},t\right)\) of spatial coordinates vector \(\vb{x}\) and time \(t\), the generalized heat equation is defined in \lccref{eq:heat_equation}.
 \begin{equation} \label{eq:heat_equation}
@@
 Intuitively this is because once the temperature distribution approaches linear, the current spot on the pan is outputting as much heat it is getting.
-This insight is an example of why PDEs are usefull.
+This insight is an example of why PDEs are useful.
 
@@
 
-The scenario in which PDEs are used to simulate a system typically means computing an unknown quantity like the temperature field of an object over time from a set of known parameters such as initial conditions and material parameters such as thermal diffusivity in the case of the heat equation.
+An increasingly critical use of PDEs is in Numerical weather prediction (NWP).
+The information weather forecasts provide is an integral part of modern life.
+Many sectors rely on timely and accurate weather forecasts.
+Individuals, day to day rely on forecasts for a range of different decisions ranging from activities they can do to personal safety from extreme weather.
+The weather also affects retail as consumer behavior change with whether it is rain or shine \autocite{tianImpactWeatherConsumer2021,tianPredictingConsumerVarietyseeking2018,govindWeatherAffectPreference2020,moonWeatherSensitivityAnalysis2018}.
+Similarly, the types of transportation people use and operational decisions changes with the weather \autocite{lepageImpactWeatherActivities2021,nurmiExpectedImpactsValue2013}.
+Another critical sector is agriculture, where extreme weather events and changes in climate threatens the food supply \autocite{cogatoExtremeWeatherEvents2019,malhiImpactClimateChange2021,anwarAdaptingAgricultureClimate2013}.
+As the climate continues to warm and extreme weather events increase in frequency, the mitigation for these events become all the more important \autocite{ClimateChange20222023}.
+Because of this, forecasting is critical in making accurate decisions for policymakers and warnings of extreme weather events for civilians \autocite{astithaExtremeWeatherForecasting2023,stottAttributionExtremeWeather2016}.
+A major challenge is the fact that observations of weather can be sparse in the sense that observations are localized and do not cover entire areas \autocite{wilbyRainfallTemperatureEstimation2013,monmonierAirApparentHow1999,galkinAssimilationSparseContinuous2020}.
+This lack of spatially distributed meteorological information hampers decision-making on areas to be prioritized and what to prioritize based on location.
+For example, weather stations can only observe their immediate surroundings.
+And they are for the most part stationary.
+Even more mobile observation platforms like satellites only show the portion of the surface the satellite can see at any one time such as in \lccref{fig:satellite_image_coverage}.
+While accumulating observations through more satellite passes is possible, this, however, means short-lived features may not be observed.
+As impoverished regions often are the most data sparse, the effect compounds on the fact that for impoverished regions, scarce resources need to be effectively and efficiently applied.
+To this end, numerical models are employed to model a more representative view by using known physics such as the compressible Euler equations and statistical models \autocite{mengaldoCurrentEmergingTimeIntegration2019,kwasniokDatabasedStochasticSubgridscale2012}.
+The next step is in forecasting future weather which in itself is a challenge.
+The information this could provide is invaluable because it means planning for future weather is possible.
+
+\begin{figure}[h] %h means here!
+    \centering
+    \includegraphics[width=1.0\linewidth]{figures/snapshot_nasa_airs_aqua_2024_05_21T00_00_00Z.jpg}
+    \caption{Daytime and nighttime surface air temperature from observations by the AIRS instrument onboard the NASA AQUA satellite.
+This shows observations recorded through a whole day on the 21\textsuperscript{st} of May 2024.
+Notice that parts of the globe, especially near the equator have not been observed.
+This image was produced using NASA Worldview (\url{https://go.nasa.gov/46SaYyJ}).}\label{fig:satellite_image_coverage}
+\end{figure}
+
+Forecasting the weather or evolution of any other system is formulated as an initial value problem where past observations are used to predict an unknown future state of the system.
+A different formulation can be how heat spreads over time in different types of frying pans from known information of the pan's materials, their heat conduction properties, and that the stove gives off constant heat.
+In general the scenario is predicting the effect (future atmospheric temperature distribution, etc.) of some given causes (current and past weather, etc.).
 This scenario is termed the forward problem.
@@
 Traditional methods used to solve these problems utilized knowledge of the exact equations to numerically solve PDEs.
-As an example, the Finite Difference Method (FDM) approximates the solution by substituting the partial derivatives with finite differences such as the first derivative approximation in \cref{eq:forward_finite_difference_1}.
-\begin{equation} \label{eq:forward_finite_difference_1}
-    \pdv{f\left(x\right)}{x} \approx \frac{f\left(x+h\right)-f\left(x\right)}{h}
-\end{equation}
+As an example, the Finite Difference Method (FDM) approximates the solution by substituting the partial derivatives with finite differences and manipulating the equation such that the solution can be computed.
+% \begin{equation} \label{eq:forward_finite_difference_1}
+%     \pdv{f\left(x\right)}{x} \approx \frac{f\left(x+h\right)-f\left(x\right)}{h}
+% \end{equation}
 
@@
 There are several challenges associated with this.
-First, irregular domains such as bone, spider silk, gravel, or other bio-inspired or aggregate materials pose a challenge due to the complexity of the domain geometry \autocite{gaulSimulationWavePropagation1991,buoniEfficientScalableNumerical2007,jiaModulateStressDistribution2024}.
+First, irregular domains such as bio-inspired materials like bone, spider silk, or aggregate materials like gravel pose a challenge due to the complexity of the domain geometry \autocite{gaulSimulationWavePropagation1991,buoniEfficientScalableNumerical2007,jiaModulateStressDistribution2024}.
 Also, irregular domains which create large deformations or mesh entanglement cause these methods to become ineffective \autocite{chenMeshfreeMethodsProgress2017}.
@@
 This creates meshes with very large number of points that are very resource intensive \autocite{buoniEfficientScalableNumerical2007}.
-Therefore, in problems where these issues important or resources are limited, mesh-free methods are preferred.
-Third, traditional methods require prior knowledge of analytic forms of PDEs.
-This is because the solvers use the equations to formulate the solution.
-A dealbreaker like this makes traditional numerical approaches unsuited to data dominant problems.
-Fourth, a single evaluation of traditional solvers may not be very costly, however multiple evaluations can add up.
-This is very apparent in inverse problems where the solver is evaluated multiple times to compute gradients in order to obtain parameter functions.
-These challenges altogether have motivated research into alternative methods that do not completely rely on prior knowledge, mesh free, and fast enough when computing solutions from parameters.
+Third, a single evaluation of traditional mesh-based solvers may not be very costly, however multiple evaluations can add up.
+This is very apparent in inverse problems where the solver is queried multiple times to solve the forward problem in order to obtain parameter functions.
+Therefore, in problems where these issues important or resources are limited, mesh-free methods may be preferred.
+As an example, the spectral method solves PDEs by formulating the solution as a linear combination of global basis functions like the Fourier series.
+This can be likened to how music combines sound waves of different things to produce the overall sound.
+The complex formulation of the Fourier series is presented in \lccref{eq:fourier_series}.
+\begin{equation}\label{eq:fourier_series}
+    s = \sum_{k} c_k e^{2\pi ikx}
+\end{equation}
+The example differential equation we wish to solve is the simple derivative in \lccref{eq:derivative}.
+The aim is to find a function \(u* \) from a known function \(f* \).
+To do this we first formulate both into separate Fourier series approximations \(u \) and \(f \) in \lccrefs{eq:example_fourier_1,eq:example_fourier_2} respectively.
+\begin{align}
+    \dv{u\left( x \right)}{x} & = f\left( x \right) \label{eq:derivative}                      \\
+    u\left( x \right)         & = \sum_{k} \hat{u}_k e^{2\pi ikx} \label{eq:example_fourier_1} \\
+    f\left( x \right)         & = \sum_{k} \hat{f}_k e^{2\pi ikx} \label{eq:example_fourier_2}
+\end{align}
+Next we take the derivative of \lccref{eq:example_fourier_1} which result in \lccref{eq:fourier_series_derivative}.
+Using this we can substitute the terms in \lccref{eq:derivative} with \lccrefs{eq:fourier_series_derivative,eq:example_fourier_2} giving \lccref{eq:example_spectral_method_fourier_substituted}.
+Finally, after some algebraic manipulation we obtain \lccref{eq:derivative_coeff}.
+One also needs to choose \(\hat{u}_{0}\), which is the integration constant.
+Practically this would be done with a finite number of modes and the coefficients \(\hat{f}_k\) are obtained using a Discrete Fourier Transform (DFT) algorithm like the Fast Fourier Transform (FFT).
+\begin{align}
+    \dv{u\left( x \right)}{x}                                    & = \sum_{k} \hat{u}_k\times \left( 2\pi ik \right) e^{2\pi ikx} \label{eq:fourier_series_derivative} \\
+    \sum_{k} \hat{u}_k\times \left( 2\pi ik \right) e^{2\pi ikx} & = \sum_{k} \hat{f}_k e^{2\pi ikx} \label{eq:example_spectral_method_fourier_substituted}            \\
+    \hat{u}_k                                                    & = \hat{f}_k / \left( 2\pi ik \right) \label{eq:derivative_coeff}
+\end{align}
+The fourth challenge with traditional methods is that they require prior knowledge of analytic forms of PDEs.
+This is because the solvers use the equations to formulate solutions.
+This makes traditional numerical approaches unsuited to data dominant problems.
+These challenges altogether are some of what weather forecasting faces; NWP has the immense task of modeling multiple scales of the Earth's atmosphere while accounting for geographical features of physical systems that are still not fully understood.
+Many other fields also face these challenges which has motivated research into alternative methods that do not completely rely on prior knowledge, are mesh free, and fast enough when solving forward problems.
 
+\subsection*{Machine Learning for PDEs}
 With the increasing prevalence of machine learning methods and their use in more and more fields, research into their use for scientific computing has taken off in recent years.
@@
 The network residual and boundary loss are then weighted and summed with the data loss.
-For a neural network \(\hat{u}\left(\vb{x},t\right)\) approximating the real solution \(u\left(\vb{x},t\right)\), the residual loss for the heat equation in \cref{eq:heat_equation} is \cref{eq:heat_pinn_loss}.
+For a neural network \(\hat{u}\left(\vb{x},t\right)\) approximating the real solution \(u\left(\vb{x},t\right)\), the residual loss for the heat equation in \lccref{eq:heat_equation} is \lccref{eq:heat_pinn_loss}.
+There are several advantages of incorporating physics knowledge into the model including regularization of the model outputs to be more consistent with physics, faster convergence, and less to no data required depending on whether the network is trained in a manner that is supervised, self-supervised, or a combination of both.
 One issue with using AD to compute the residual is that the network input needs to be the independent variable (i.e.\ coordinates, time, etc.).
@@
 \end{equation}
+\subsection*{Learning PDEs with CNNs}
 Other works utilize convolutional neural networks (CNN) to compute the solution from input functions such as forcing terms or initial conditions.
@@
 While the use of CNNs mean that discretization is implied, solutions of different initial conditions or parameter functions can be computed by inference and no retraining is required.
+This property is especially useful for many-query problems such as computing gradients for inverse problems.
 
+\subsection*{Operator Learning}
 The mapping between discretized functions done by CNNs are related to an alternative approach that starts by viewing PDEs as operators, which are generalized mappings between spaces.
@@
 This architecture is based on an extension for deep learning of the universal operator approximation theory for neural networks first proposed almost three decades ago at the time of writing by \textcite{chenUniversalApproximationNonlinear1995}.
-The proposed architecture is composed of two sub-networks, where one termed the trunk \(\hat{\vb{T}}\left(\vb{x},t\right)\)learns the latent mapping for coordinates and the other network termed the branch \(\hat{\vb{B}}\left(\vb{f}\right)\) learns the latent mapping for the input function \(f \).
+The proposed architecture is composed of two subnetworks, where one termed the trunk \(\hat{\vb{T}}\left(\vb{x},t\right)\)learns the latent mapping for coordinates and the other network termed the branch \(\hat{\vb{B}}\left(\vb{f}\right)\) learns the latent mapping for the input function \(f \).
 The two latent mappings are combined through a dot product to obtain the approximated output function value \(u \left( \vb{x}, t \right)\).
-This is formulated in \cref{eq:universal_op_approx_nn}.
+This is formulated in \lccref{eq:universal_op_approx_nn}.
 \begin{equation}\label{eq:universal_op_approx_nn}
@@
 \end{equation}
-Fourier Neural Operators is an alternative avenue for learning operators by utilizing the fact that functions can be decomposed into linear combinations of basis functions, namely trigonometric basis in this particular case \autocite{li2021fourier}.
+Fourier Neural Operators (FNO) is an alternative avenue for learning operators by utilizing the fact that functions can be decomposed into linear combinations of basis functions, namely trigonometric basis in this particular case \autocite{li2021fourier}.
 With this method the input function value is mapped to its corresponding output function value.
@@
 One drawback with FNO is the requirement that output functions are not parameterized by coordinates and therefore is implicitly relative to the input function coordinates.
-To avoid this issue, \textcite{fanaskovSpectralNeuralOperators2023} reframes the problem by directly utilizing the coefficients of the input function computed using Fourier transform to predict the coefficients of the output function in terms of coefficients a Fourier series.
+To avoid this issue, \textcite{fanaskovSpectralNeuralOperators2023} reframes the problem by directly utilizing the coefficients of Fourier or Chebyshev basis.
+The model, termed Spectral Neural Operator (SNO) is trained on features of input function coefficients which are computed using Fourier or Chebyshev transforms and labels of output function coefficients using the same transforms.
+The authors point out one motivation for this approach which is that training neural networks on discretized data may not be ideal because unexpected outputs such as non-smooth interpolation may happen when the network is trained on one grid size and evaluated other grid sizes.
+With SNO, the interpolation of the function is smooth due to interpolation being done by Fourier basis functions which are sines and cosines for example.
+In a similar study, \textcite{du2024neural} extends the concept of mapping coefficients by proposing residuals in the spectral domain and leveraging Parseval's Identity to compute the spectral analog to the loss term in PINNs.
+This allows for self supervised learning in the spectral domain.
+The same benefits incorporating physics into PINNs also apply here without the pain points introduced by discretized model inputs and outputs.
+As a whole, operator learning creates an alternative approach that addresses the issue of retraining or recomputing the solution model.
+In addition, due to its data based approach, even systems with partially or fully unknown governing equations may be simulated.
 
-\noindent Non-destructive testing (NDT) is critical process in the field of engineering and quality assurance that allows the evaluation of a subject without causing damage \autocite{howell2020nondestructive, maioUltrasoundPropagationComposite2022, bochudSparseDigitalSignal2015}.
-This makes NDT crucial in many cases like construction and manufacturing where testing needs to be done on products without damaging it.
-The use of NDT allows for early detection of flaws and anomalies ensuring the reliability, longevity, and safety of structures and machinery.
-A widely used form of NDT, ultrasonic testing, propagates mechanical waves into the material.
-The ultrasonic waves, typically in the kHz to MHz range, travel through the material and interact with inhomogeneities in the material i.e.
-waves reflected by a cavity.
-This makes it possible to determine the location, size, and nature of deformities by analyzing the waves measured at predetermined locations.
-The measurements themselves result in a time series of wave amplitudes represented as displacement.
-The data can be presented as shown in \Cref{fig:us_presentation}.
-The amplitude time series by itself is referred as an A-Scan.
-B-Scans take measurements at multiple locations to show a cross-section of the subject.
-C-Scans adds another dimension of measurements and presents a view of things that reflect the waves such as defects.
-Analysis of the ultrasonic data can then be carried out.
-When the material can be assumed homogeneous, ray based or time of flight based methods can be used.
-In pulse echo, the wave travels through the material and gets reflected by interfaces, whether the other side of the material, fractures within, or generally modulus/density discontinuities present in the material.
-This means the measurements would record a large amplitude initially from the impulse sent into the material.
-And then the reflected waves from the closest interface would arrive.
-This way, just by knowing the exact wave speed of the material, one could easily translate reflected wave arrival time into the positions of interfaces.
+A persistent challenge with all these approaches is the issue of optimization.
+While neural networks are modular and expressive which is proven by the universal approximation theorem \autocite{cybenkoApproximationSuperpositionsSigmoidal1989,hornikMultilayerFeedforwardNetworks1989}, their loss function present many local minima meaning it is non-convex.
+This can be mitigated by using advanced optimization techniques that can find a local minima close enough to the global minima such as Adam \autocite{shresthaReviewDeepLearning2019,soydanerComparisonOptimizationAlgorithms2020}.
+However, the addition of PDE residuals into the loss function have worsened the highly non-convex loss landscape issue \autocite{rathoreChallengesTrainingPINNs2024,NEURIPS2021_df438e52,basirCriticalInvestigationFailure2022}.
+These problems range from the disparity in size of boundary and residual loss gradients to the fact that incorporation of residuals and boundary conditions themselves create a much more complex loss landscape.
+As a result, it is desirable to utilize a different machine learning algorithm that possesses a convex loss landscape.
+One family of such algorithms are Support Vector Machines (SVM) \autocite{vapnikNatureStatisticalLearning2000}.
+The appeal of SVMs are the fact that the model is formulated as a quadratic programming problem.
+This means there are strong guarantees for convergence, generalization, and complexity.
+Another formulation called Least Squares Support Vector Machines (LSSVM) reformulates the problem as a linear system \autocite{suykensLeastSquaresSupport2005}.
+This leads to an easier problem that can be computed faster by well established algorithms like the many implementations of least squares solvers.
+Another advantage of the linear formulation is that this can be easily parallelized to exploit hardware like graphics processing units more widely known as GPUs in contrast to the commonly used Sequential Minimal Optimization (SMO) used for SVMs with quadratic objective functions.
 
-\begin{figure}[ht]
-    \centering
-    \includesvg[inkscapelatex=false, width=1.0\linewidth]{gambar/us scan presentations}
-    %\includegraphics[width=1.0\linewidth]{gambar/us scan presentations.png}
-    \caption{Different presentations of ultrasonic scan data.
-The subject is a box containing several anomalies indicated by the yellow oval and red triangle.
-The fist presentation is the A-Scan where the amplitude measured over time in one location.
-The second is B-Scan where the amplitudes over time is measured along a line.
-The results are then stacked with the vertical axis acting as time and the horizontal axis as position.
-The higher amplitudes correspond to lighter pixels.
-The third presentation is C-Scan which is a view of the amplitudes of reflected waves except the initial impulse and back wall reflection.}
-    \label{fig:us_presentation}
-\end{figure}
+The advantageous properties of SVM based methods have attracted research into their use for solving PDEs.
+An early work using SVMs to solve PDEs by \textcite{youxiwuSVMSolvingForward2005} introduced a method for solving the forward problem of Electro-Impedance Tomography.
+This work solved for the mathematical model of EIT which is given by Maxwell's equations by modeling the trial function as using an \(\epsilon \)-SVR model.
+Another approach much more similar to PINNs was presented by \textcite{mehrkanoonLearningSolutionsPartial2015}.
+The residual and initial/boundary conditions are imposed as equality constraints on an LS-SVM objective function.
+A different study by \textcite{leakeAnalyticallyEmbeddingDifferential2019}, the incorporation of physics into the model is done slightly differently by utilizing the theory of functional connections to directly embed constraints into the solution.
+This means that the proposed method would satisfy the boundary condition exactly.
+However, the authors point out that for PDEs in higher dimensions deriving and implementing this method can become cumbersome.
+These approaches, however, do not learn the PDE operator itself.
+Meaning they are also not practical for many-query problems.
 
-Ultrasonic NDT has advantages that make it one of the more widely used NDT methods \autocite{howell2020nondestructive, nivenFullWaveformInversion2020, feliceSizingFlawsUsing2018}.
-One advantage is that ultrasonic testing equipment is often portable making it suitable for cases where it is difficult or not possible to test in a controlled environment such as a laboratory.
-Inspections for infrastructure such as pipes or rail tracks are examples where it is costly and very disruptive to move the test subject to a testing location \autocite{}.
-Another advantage of ultrasonic testing is the low risk it poses in terms of safety.
-Unlike the ionizing radiation used in radiography, ultrasonic waves used in testing are harmless to humans.
-This means testing can be done with relatively less stringent safety precautions \autocite{}.
-Additionally, the technology is relatively mature with a variety of equipment and supplier options.
-Furthermore, affordable options for inexpensive ultrasonic equipment is also available \autocite{}.
-These advantages and the popularity of ultrasonic testing stemming from the aforementioned advantages highlights the important role ultrasonic testing plays in enabling affordable and reliable engineering.
+\subsubsection*{Operator Learning for Weather Forecasting}
+In terms of weather forecasting, operator learning has been applied in terms of initial value problems.
+This problem formulation is reminiscent of time series prediction problems widely found in machine learning research.
+Researchers \textcite{kurthFourCastNetAcceleratingGlobal2023} developed FourCastNet which utilized Adaptive Fourier Neural Operator (AFNO), a transformer based model containing the previously mentioned FNO computational blocks by \textcite{li2021fourier}.
+This model was then able to be trained in a massively parallel manner.
+In a comparison with a traditional model called the Integrated Forecasting System from the European Center for Medium Range Weather Forecasts (ECMWF), FourCastNet is faster and much more efficient in terms of inference time, resulting in about 80,000 times speed up for a 100-member ensemble forecast.
+This is while performing much better than a previous deep learning approach.
+In another study, \textcite{bonevSphericalFourierNeural2023} proposed a variation on neural operators called Spherical Fourier Neural Operator (SFNO) which exploited the spherical nature of global forecasting by using Spherical Harmonic Transform (SHT) in place of Fourier Transform.
+This model when compared to AFNO and FNO, produced no visible artifacts in autoregressive rollouts for long range forecasting.
+In terms of forecasting, the model shows outcomes that matches the IFS which is a big leap forward in parity for traditional and machine learning based methods.
 
-%Talk about the process of A-scans, B-scans, C-scans. Talk about why its hard to analyze for more complex situations which are gaining popularity ie. composites.
-
-The emergence of composites, sought after for their multi-functional properties, introduces challenges for inspection and analysis \autocites{inceOverviewEmergingHybrid2023, yangUltrasonicDetectionMethods2023, dwivediAdvancesResearchesNon2018, nivenFullWaveformInversion2020}.
-Different composites provide a range of benefits, from the strength to weight ratio of carbon fiber reinforced polymer composites to electromagnetic shielding materials.
-However, the anisotropic and complex characteristic of composites that give rise to the beneficial properties complicates wave propagation because of the location and directional dependence of material properties.
-For example wave speed can be faster in certain directions and locations.
-Reflections will happen not just because of anomalies, but also expected features in the material itself.
-Extraneous signals from inhomogeneities anticipated in the material makes it harder to extract useful information on unknown defects.
-In order to enable reliable use of ultrasonic NDT on composite materials and other complex situations, a method to quantify and characterize the complicated behavior is required \autocite{maioUltrasoundPropagationComposite2022}.
-
-This is where model based methods come into play.
-Advances in computation over recent decades has enabled the use of computational tools to revolutionize many fields.
-Numerical modeling, in particular, has an almost symbiotic relationship with the rise of computing; with the likes of ENIAC, MANIAC, and a plethora of other early electronic digital computers \autocite{andersonScientificUsesMANIAC1986}.
-The ENIAC for example, promised to compute ballistic trajectories 10 times faster than the methods that were in used at the time.
-This progress allows the simulation and analysis of systems previously beyond reach.
-The effects range from prediction of weather systems and physics constrained problems like bleeding edge aerospace design to uncovering physical laws of nature.
-
-Despite advances in computing power, numerical modeling of physical systems still remains an open problem with many challenges.
-Traditional methods such as Finite Element Method (FEM), Finite Difference Method (FDM), and Spectral Methods are limited to known operators and equations \autocite{karniadakisPhysicsinformedMachineLearning2021, du2024neural,fanaskovSpectralNeuralOperators2023,luLearningNonlinearOperators2021}.
-The modern data landscape further complicates traditional numerical modeling with its characteristic abundance of low quality, high quantity data, as some methods such as FDM are inherently sensitive to noise \autocite{dearagaoExplicitControlNumerical2021, huntulInverseProblemReconstructing2021}.
-Noisy data also presents a formidable challenge in general because gleaning any meaningful information from noisy and incomplete data requires further filtering and interpretation.
-This issue is particularly troubling for inverse problems.
-This is because some inverse problems are unstable in addition to their ill-posedness which necessitates advanced techniques \autocite{caubetInstabilityInverseProblem2013, mandacheExponentialInstabilityInverse2001}.
-The next layer of complexity is posed by the challenge of irregular domains.
-An example of this is fluid flow through materials such as gravel, sponges, even changing with time \autocite{liImmersedInterfaceMethod2006}.
-Due to the nature of irregular domains, mesh based methods struggle to adapt.
-Addressing these challenges is crucial for understanding a variety of problems in both scientific research and engineering.
-
-%talk more about each challenge and the proposed solutions to it and how they do not fully cover the needs this work is trying to cover
-The problem posed by model-based ultrasonic testing combines several of these challenges.
-First, visualizing properties of materials such as density from measurements of ultrasonic waves that interacted with the material is an inverse problem.
-This is because the effect is used to infer the cause.
-The challenge with inverse problems is that in many cases, the result is very sensitive to differences in the parameters \autocite{tarantolaInverseProblemTheory2005}; small variation in density distribution can result in very different measurements.
-As such, additional noise or inaccuracies in measurement can massively impact the predicted parameter.
-This very issue has been a long standing challenge in the geophysics community.
-The full waveform inversion (FWI) procedure used to determine properties of the earth, requires certain techniques such as a minimization criteria that mitigates this sensitivity \autocite{virieuxOverviewFullwaveformInversion2009}.
-Second, complex or irregular domains are a challenge for traditional mesh based methods as the domain may vary in time \autocite{liImmersedInterfaceMethod2006, burchnerImmersedBoundaryParametrizations2023}.
-Costly mesh generation hampers the performance of mesh based methods.
-In addition, some approaches like total focusing method (TFM), traveltime tomography (TT) and reverse time migration (RTM) are not able to provide more than a rough estimate of defects.
-Third, for some materials, there are little to no knowledge present in literature on how waves propagate through the material.
-Continued research has alleviated this issue by advanced our understanding of wave propagation and materials.
-\textcite{gordoaUltrasonicWavesBubbly2021} presented an analytic solution to ultrasonic wave propagation in bubbly liquids.
-\textcite{} .
-However, these solutions are not available for all situations and materials, as such is the case when a novel material is created.
-In some of these cases data collection may be easier to do compared to deriving from first principles.
-
-%Talk about how composites, ndt, rapid prototyping, bigalow inflatable space habitat, etc is important to aerospace
-Advances in computing technology and the integration of non-destructive testing have revolutionized the aerospace industry \autocite{guptaAdvancesApplicationsNonDestructive2022, jacobDataFusionEfficient2022}.
-This has had the effect of enabling rapid advancements in cutting-edge technologies such as vertical rocket landings, 3-D printed spacecraft, and in-space manufacturing to name a few \autocite{corradoSpaceExplorationEconomic2023}.
-These technologies addressed several key challenges with space exploration, namely cost, mission flexibility \& resilience, and environmental considerations.
-NDT plays a crucial role in ensuring the safety and quality of the innovations.
-The novelty of innovations means they do not have the luxury of being a proven solution.
-
-%Talk about related works, using conventional methods, using nn, using other machine learning methods, using spectral methods.
-
-Bagian ini mendeskripsikan gambaran umum, konteks, dan posisi penelitian TA dalam konstelasi perkembangan pengetahuan yang telah dicapai.
+% Bagian ini mendeskripsikan gambaran umum, konteks, dan posisi penelitian TA dalam konstelasi perkembangan pengetahuan yang telah dicapai.
 Penjelasan yang dituliskan menjadi penting karena dengan landasan yang kuat, maka pekerjaan penelitian dapat terarah dilakukan.
@@
 
-Beberapa pustaka utama yang berperan dominan dapat disampaikan di sini untuk memberi gambaran tentang letak penelitian TA dalam konstelasi keilmuan yang dicapai.
+% Beberapa pustaka utama yang berperan dominan dapat disampaikan di sini untuk memberi gambaran tentang letak penelitian TA dalam konstelasi keilmuan yang dicapai.
 Hasil-hasil dari pustaka terbaru dapat menopang Latar Belakang ini menjadi lebih kuat.
 
-Sangat wajar apabila isi sub bab setelah Latar Belakang ini mengalami penyesuaian saat sejumlah hasil penelitian sudah diperoleh dan dianalisis.
+% Sangat wajar apabila isi sub bab setelah Latar Belakang ini mengalami penyesuaian saat sejumlah hasil penelitian sudah diperoleh dan dianalisis.
 Pada dasarnya, hal ini dimungkinkan apabila ada penyesuaian kecil, karena fokus penelitian sejatinya sudah jelas sedari awal, namun hasil-hasil yang diperoleh dapat memperbaharui beberapa butir isi sub bab.
@@
 
-\section{Rumusan dan Batasan Masalah}
-\noindent Bagian ini menjadi salah satu bagian penting dalam Pendahuluan.
+\section{Problem Statement}\label{sec:problem_statement}
+\noindent The problems this work sets out to solve based on \lccref{sec:background} are:
+\begin{enumerate}
+    \item What is the formulation a computational model for operator regression and therefore solving PDEs in the spectral domain using support vector machines?
+    \item How does the number of basis functions and model parameters impact the model performance?
+    \item How can one interpret the learned model?
+    \item Can the model learn to forecast the weather effectively? % TODO: how to integrate physics into the LSSVM formulation?
+\end{enumerate}
+
+% Bagian ini menjadi salah satu bagian penting dalam Pendahuluan.
 Setelah paparan Latar Belakang, maka masalah yang diangkat pada pekerjaan penelitian perlu dirumuskan dengan baik.
@@
 
-Sejalan dengan ini, setiap masalah yang diangkat selalu memiliki batas.
+% Sejalan dengan ini, setiap masalah yang diangkat selalu memiliki batas.
 Ada batasan, asumsi, atau kriteria yang menjadi pembatas atas masalah yang diangkat dalam penelitian TA, sehingga arah penelitian dapat fokus.
@@
 
-\section{Tujuan}
-\label{sec:tujuan}
-Bagian ini secara tegas menuliskan tujuan pekerjaan penelitian TA, yang dapat memuat lebih dari satu.
+\section{Aims}\label{sec:aims}
+\noindent Based on the stated problems in \lccref{sec:problem_statement}, this study aims to acomplish the following:
+\begin{enumerate}
+    \item The design and implementation of a computational model that maps coefficients in the spectral domain using Least Squares Support Vector Regression (LSSVR).
+    \item Hyperparameter optimization of the model.
+    \item Interpretation the model results and why some predictions turn out the way they do.
+    \item Comparison of SpectralSVR with SNO, DeepONet, FNO, and FDM on 4 problems
+\end{enumerate}
+% Bagian ini secara tegas menuliskan tujuan pekerjaan penelitian TA, yang dapat memuat lebih dari satu.
 Pemilihan kata kerja pada Tujuan ini sangat penting karena menggambarkan arah fokus dari jalinan upaya yang dilakukan.
 
-\section{Metodologi}
-Di sini disampaikan metodologi yang diterapkan pada pekerjaan penelitian TA.
-Beberpa di antaranya adalah pengamatan dan akuisisi data, eksperimen numerik, studi pustaka, teoretik atau analitik, dan semi analitik dengan komplemen numerik.
+\section{Contribution}
+\noindent In achieving the aims of this study the following contributions are made:
+\begin{enumerate}
+    \item A novel use LSSVR which has a convex objective to learn solution operators of partial differential equations and operators in general.
+    \item Comparison of non-uniform Fourier transform for arbitrary spatial sampling with interpolated grid point values.
+    \item Interpretation of trained model.
+\end{enumerate}
+
+\section{Limitations}
+\noindent This work is limited to the following:
+\begin{enumerate}
+    \item Functions the model works with are only continuous functions.
+    \item Hardware used in this project is limited to the standard offering on \url{kaggle.com} as of \today.
+    \item The basis functions are limited to Fourier basis.
+\end{enumerate}
 
 \section{Sistematika Penulisan}
-\noindent Bagian ini adalah penutup Bab I yang menyampaikan  secara ringkas isi setiap  bab.
+% \noindent Bagian ini adalah penutup Bab I yang menyampaikan  secara ringkas isi setiap  bab.
 Karena pembaca sudah sampai akhir Bab I, yang  berarti  sudah  mengetahui isinya, maka tidak perlu ditulis lagi rincian Bab I.
@@
 
-Apabila diperlukan, dapat dituliskan konvensi khusus yang digunakan pada penulisan naskah buku TA ini, misalnya tanda titik menggantikan tanda desimal karena alasan kemudahan dan kejelasan dalam formulasi matematika.
+% Apabila diperlukan, dapat dituliskan konvensi khusus yang digunakan pada penulisan naskah buku TA ini, misalnya tanda titik menggantikan tanda desimal karena alasan kemudahan dan kejelasan dalam formulasi matematika.

### 2024-08-22 skripsi/bab4.tex
finish Ch 1 draft, move figures

@@
 Format gambar yang umum adalah jpg, png, dan postscript (ps atau eps).
-Ukuran huruf pada nama sumbu dan label gambar/grafik harus cukup besar dan jelas, demikian halnya dengan angka pada sumbu.
+Ukuran huruf pada nama sumbu dan label figures/grafik harus cukup besar dan jelas, demikian halnya dengan angka pada sumbu.
 Gambar dan grafik dapat berwarna dengan pilihan warna yang tegas dan jelas.
@@
 \centering
-\includegraphics[width=0.3\linewidth]{gambar/Semiconductor-Fermi-Level-Band-Diagram-1.jpg}
+\includegraphics[width=0.3\linewidth]{figures/Semiconductor-Fermi-Level-Band-Diagram-1.jpg}
 \caption{Tingkatan Fermi pada\\Bahan Semikonduktor}
@@
 \subfigure[]{
- \includegraphics[width=0.4\linewidth]{gambar/Semiconductor-Fermi-Level-Band-Diagram-1.jpg}
+ \includegraphics[width=0.4\linewidth]{figures/Semiconductor-Fermi-Level-Band-Diagram-1.jpg}
  \label{surf-1}
@@
 \subfigure[]{
- \includegraphics[width=0.4\linewidth]{gambar/Semiconductor-Fermi-Level-Band-Diagram-1.jpg}
+ \includegraphics[width=0.4\linewidth]{figures/Semiconductor-Fermi-Level-Band-Diagram-1.jpg}
  \label{surf-2}

### 2024-08-22 skripsi/bab2.tex
wip ch 2 & 3

@@
 As the development on SVM continued, what originally was a model for classification of separable data generalized to regression tasks as well Vapnik (2000 The Nature of Statistical Learning Theory).
+\subsection{Disadvantages}
+However, the main disadvantage of LSSVMs are the fact that they do not have the sparse property of SVMs which can leave performance on the table.
+A simple mitigation can be done by filtering training samples with small absolute values of lagrangian multipliers \autocite{haifengwangComparisonSVMLSSVM2005}.
 

### 2024-09-06 skripsi/bab1.tex
research design and computational model, fix root file latex

@@
+% !TEX root = ./skripsi.tex
 \chapter{INTRODUCTION}
@@
     \item Functions the model works with are only continuous functions.
-    \item Hardware used in this project is limited to the standard offering on \url{kaggle.com} as of \today.
-    \item The basis functions are limited to Fourier basis.
+    \item Hardware used in this project is limited to the standard offering on \url{kaggle.com} as of \today{}.
+    \item The basis functions are limited to Fourier basis. % TODO: change this if more basis functions are added
+    \item Modeled fields are compact or dense meaning not sparse. Sparse observations or other data are assimilated using other methods.
 \end{enumerate}

### 2024-09-06 skripsi/bab3.tex
research design and computational model, fix root file latex

--- 2024-02-17 skripsi/bab3.tex
@@
-\chapter{METODOLOGI PENELITIAN}
-\label{sec:metodologi_penelitian}
+% !TEX root = ./skripsi.tex
+\chapter{Research Methodology}\label{sec:research_methodology}
 
-Secara umum, metode penelitian yang digunakan pada pekerjaan penelitian disampaikan pada bab ini. Judul bab tidak harus seperti yang dituliskan. Dalam kata lain bisa diubah sesuai kebutuhan.
+% Secara umum, metode penelitian yang digunakan pada pekerjaan penelitian disampaikan pada bab ini. Judul bab tidak harus seperti yang dituliskan. Dalam kata lain bisa diubah sesuai kebutuhan.
 
-\section{Model Komputasi}
-\noindent The DeepONet architecture contains an element that is difficult to optimize.
-% \begin{mini}
-%   {W_b}{y=(W_b\cdot f+b_b)^\top\cdot(W_t\cdot v+b_t)+\xi
-% \end{mini}
+\section{Research Design}
+\noindent This study is carried out under the framework of a research design.
+In this section, this design will be laid out and explained.
+The design includes the process from the beginning to the end of the overall study.
+The research design is visually depicted in \lccref{fig:research_design_diagram}.
 
-\begin{mini!}|s|
-{\substack{W_b,b_b,W_t,b_t,\xi}}{\frac{1}{2}\Vert W_b\Vert_F^2 + \frac{1}{2}\Vert W_t\Vert_F^2 + \frac{c}{2}\sum_{i=1}^{l}\xi_i^2} {}{}
-\addConstraint{y_i}{=(W_b f_i+b_b)^\top(W_t v_i+b_t)+\xi_i,\quad}{i=1,\ldots,l}
-\end{mini!}
+\begin{figure}[h]
+  \centering
+  \tikzfig{figures/research_design_diagram}
+  \caption{Research design diagram}\label{fig:research_design_diagram}
+\end{figure}
 
-\begin{equation}
-  \begin{aligned}
-    L(W_b,b_b,W_t,b_t,\xi;\alpha)= {} & \frac{1}{2}\Vert W_b\Vert_F^2 + \frac{1}{2}\Vert W_t\Vert_F^2 +\frac{c}{2}\sum_{i=1}^{l}\xi_i^2 \\ &+ \sum_{i=1}^{l}\alpha_i(y_i-\xi_i-(W_b f_i+b_b)^\top(W_t v_i+b_t))
-  \end{aligned}
-\end{equation}
-\begin{equation}
-  \begin{aligned}
-    \pdv{L(W_b,b_b,W_t,b_t,\xi;\alpha)}{W_b}                               & = 0                                                                                \\
-    \frac{2}{2}W_b + 0 + 0 - \sum_{i=1}^{l}\alpha_i((W_t v_i+b_t)f_i^\top) & = 0                                                                                \\
-    W_b - \sum_{i=1}^{l}\alpha_i((W_t v_i+b_t)f_i^\top)                    & = 0                                                                                \\
-    W_b                                                                    & = \sum_{i=1}^{l}\alpha_i(W_t v_i f_i^\top+b_t f_i^\top)                            \\
-    W_b                                                                    & = \sum_{i=1}^{l}(\alpha_i W_t v_i f_i^\top)+ \sum_{i=1}^{l}(\alpha_i b_t f_i^\top) \\
-    W_b                                                                    & = W_t \sum_{i=1}^{l}(\alpha_i v_i f_i^\top)+ b_t \sum_{i=1}^{l}(\alpha_i f_i^\top) \\
-    W_b                                                                    & = W_t \sum_{i=1}^{l}(\alpha_i v_i f_i^\top)+ b_t \sum_{i=1}^{l}(\alpha_i f_i^\top) \\
-  \end{aligned}
-\end{equation}
-\begin{equation}
-  \begin{aligned}
-    \pdv{L(W_b,b_b,W_t,b_t,\xi;\alpha)}{W_t}                                        & = 0                                                                                                                                                                                    \\
-    0 + \frac{2}{2}W_t + 0 - \sum_{i=1}^{l}\alpha_i((W_b f_i + b_b)v_i^\top)        & = 0                                                                                                                                                                                    \\
-    W_t - \sum_{i=1}^{l}\alpha_i((W_b f_i + b_b)v_i^\top)                           & = 0                                                                                                                                                                                    \\
-    W_t                                                                             & = \sum_{i=1}^{l}\alpha_i(W_b f_i v_i^\top + b_b v_i^\top)                                                                                                                              \\
-    W_t                                                                             & = \sum_{i=1}^{l}\alpha_i((\sum_{j=1}^{l}\alpha_j(W_t v_j f_j^\top + b_t f_j^\top)) f_i v_i^\top+b_b v_i^\top)                                                                          \\
-    W_t                                                                             & = \sum_{i=1}^{l}(\sum_{j=1}^{l}(\alpha_i\alpha_jW_t v_j f_j^\top f_i v_i^\top + \alpha_i\alpha_j b_t f_j^\top f_i v_i^\top) + \alpha_i b_b v_i^\top)                                   \\
-    W_t                                                                             & = \sum_{i=1}^{l}(\sum_{j=1}^{l}(\alpha_i\alpha_jW_t v_j f_j^\top f_i v_i^\top) + \sum_{j=1}^{l}(\alpha_i\alpha_j b_t f_j^\top f_i v_i^\top) + \alpha_i b_b v_i^\top)                   \\
-    W_t - \sum_{i=1}^{l}\sum_{j=1}^{l}\alpha_i\alpha_jW_t v_j f_j^\top f_i v_i^\top & = \sum_{i=1}^{l}(\sum_{j=1}^{l}(\alpha_i\alpha_j b_t f_j^\top f_i v_i^\top) + \alpha_i b_b v_i^\top)                                                                                   \\
-    W_t(I - \sum_{i=1}^{l}\sum_{j=1}^{l}\alpha_i\alpha_j v_j f_j^\top f_i v_i^\top) & = \sum_{i=1}^{l}(\sum_{j=1}^{l}(\alpha_i\alpha_j b_t f_j^\top f_i v_i^\top) + \alpha_i b_b v_i^\top)                                                                                   \\
-    W_t                                                                             & = \sum_{i=1}^{l}(\sum_{j=1}^{l}(\alpha_i\alpha_j b_t f_j^\top f_i v_i^\top) + \alpha_i b_b v_i^\top) (I - \sum_{i=1}^{l}\sum_{j=1}^{l}\alpha_i\alpha_j v_j f_j^\top f_i v_i^\top)^{-1} \\
-    W_t                                                                             & = \sum_{i=1}^{l}(\alpha_i(\sum_{j=1}^{l}(\alpha_j b_t f_j^\top f_i) + b_b)v_i^\top ) (I - \sum_{i=1}^{l}\sum_{j=1}^{l}\alpha_i\alpha_j v_j f_j^\top f_i v_i^\top)^{-1}                 \\
-  \end{aligned}
-\end{equation}
-\begin{equation}
-  \begin{aligned}
-    \pdv{L(W_b,b_b,W_t,b_t,\xi;\alpha)}{b_b}        & = 0 \\
-    0 + 0 + 0 - \sum_{i=1}^{l}\alpha_i(W_t v_i+b_t) & = 0 \\
-    \sum_{i=1}^{l}\alpha_i(W_t v_i+b_t)             & = 0
-  \end{aligned}
-\end{equation}
-\begin{equation}
-  \begin{aligned}
-    \pdv{L(W_b,b_b,W_t,b_t,\xi;\alpha)}{b_t}        & = 0 \\
-    0 + 0 + 0 - \sum_{i=1}^{l}\alpha_i(W_b f_i+b_b) & = 0 \\
-    \sum_{i=1}^{l}\alpha_i(W_b f_i+b_b)             & = 0
-  \end{aligned}
-\end{equation}
-\begin{equation}
-  \begin{aligned}
-    \pdv{L(W_b,b_b,W_t,b_t,\xi;\alpha)}{\xi}                         & = 0        \\
-    0 + 0 + \frac{2c}{2}\sum_{i=1}^{l}\xi_i - \sum_{i=1}^{l}\alpha_i & = 0        \\
-    \sum_{i=1}^{l}c\xi_i - \alpha_i                                  & = 0        \\
-    c\xi_i                                                           & = \alpha_i \\
-  \end{aligned}
-\end{equation}
-\begin{equation}
-  \begin{aligned}
-    \pdv{L(W_b,b_b,W_t,b_t,\xi;\alpha)}{\alpha}                         & = 0 \\
-    0 + 0 + 0 + \sum_{i=1}^{l}y_i-\xi_i-(W_b f_i+b_b)^\top(W_t v_i+b_t) & = 0 \\
-    \sum_{i=1}^{l}y_i-\xi_i-(W_b f_i+b_b)^\top(W_t v_i+b_t)             & = 0
-  \end{aligned}
-\end{equation}
+The study is carried out in 9 main phases. Each phase has a specific aim to accomplish such that the subsequent phases are able to proceed. Each phase is explained as follows:
+
+\begin{enumerate}
+  \item Problem Specification
+
+        The first phase of the study is dedicated to specifying and identifying the problem to be studied and will define the solution this study sets out to discover.
+
+  \item Literature Review
+
+  \item Design of Computational Model
+
+  \item Implementation of Computational Model
+
+  \item Planning of Experimental Scenarios
+
+  \item Data Generation and Retrieval
+
+  \item Data Preprocessing
+
+  \item Experiments
+
+  \item Analysis and Discussion
+
+\end{enumerate}
 

### 2024-09-11 skripsi/bab1.tex
finish chapter 3

@@
 As an example, the Finite Difference Method (FDM) approximates the solution by substituting the partial derivatives with finite differences and manipulating the equation such that the solution can be computed.
+The inverse problem on the other hand is determination of initial conditions or other parameters from observed state of the system.
+For example determining the heat source distribution given the temperature distribution at some point in time.
+One traditional approach to this would have meant solving the forward problem from an initial guess of the parameter and then evaluating some cost function such as how close the predicted solution is to the observed one.
+As expected, this would require many evaluations of the forward solver.
+This means that the cost of the solver would be greatly multiplied, emphasizing the importance of an efficient solver.
+% TODO: reword this because the explanation of the problem setup for forward and inverse problems is not layed out optimally.
+% TODO: perhaps the disadvantage of inverse problem in the paragraph above should be removed and only explanation of the inverse problem setup itself left by itself
 % \begin{equation} \label{eq:forward_finite_difference_1}
@@
 Other than FDM, some widely used approaches include Finite Element Methods (FEM), Finite Volume Methods (FVM), Collocation Methods, and Spectral Methods.
-FEM and FDM are both mesh based approaches, meaning they rely on discretization of the computational domain <ADD DIAGRAM FOR THIS>.
+FEM and FDM are both mesh based approaches, meaning they rely on discretization of the computational domain.
 There are several challenges associated with this.
@@
 The complex formulation of the Fourier series is presented in \lccref{eq:fourier_series}.
+% TODO: Add diagram example for discretization of the domain by FEM/FDM methods
 \begin{equation}\label{eq:fourier_series}
@@
 The example differential equation we wish to solve is the simple derivative in \lccref{eq:derivative}.
-The aim is to find a function \(u* \) from a known function \(f* \).
+In other words, the aim is to find a function \(u^{*} \) from a known function \(f^{*} \).
+This means we are learning the anti-derivative operator or more loosely known as the integral.
 To do this we first formulate both into separate Fourier series approximations \(u \) and \(f \) in \lccrefs{eq:example_fourier_1,eq:example_fourier_2} respectively.
 \begin{align}
-    \dv{u\left( x \right)}{x} & = f\left( x \right) \label{eq:derivative}                      \\
-    u\left( x \right)         & = \sum_{k} \hat{u}_k e^{2\pi ikx} \label{eq:example_fourier_1} \\
-    f\left( x \right)         & = \sum_{k} \hat{f}_k e^{2\pi ikx} \label{eq:example_fourier_2}
+    \dv{u^*\left( x \right)}{x} & = f^*\left( x \right) \label{eq:derivative}                                                      \\
+    u^*\left( x \right)         & \approx u\left( x \right)         = \sum_{k} \hat{u}_k e^{2\pi ikx} \label{eq:example_fourier_1} \\
+    f^*\left( x \right)         & \approx f\left( x \right)         = \sum_{k} \hat{f}_k e^{2\pi ikx} \label{eq:example_fourier_2}
 \end{align}

### 2024-09-11 skripsi/bab3.tex
finish chapter 3

@@
 
-        The first phase of the study is dedicated to specifying and identifying the problem to be studied and will define the solution this study sets out to discover.
-
-  \item Literature Review
+            In this phase, relevant literature of related works and other supporting materials will be reviewed to lay the groundwork of this study.
+Specifically, the literature review will encompass partial differential equations and their real world associations, traditional methods employed to solve them, systems with partially known or unknown governing equations, machine learning approaches to the problem, least squares support vector machines, performance metrics, and tools that will be used such as the PyTorch library.
 
@@
 
+            This phase of the study is allocated to the design of the computational model based on the literature that has been reviewed.
+The design of the overall process includes data retrieval, preprocessing, and the core spectral regression model itself.
+
       \item Implementation of Computational Model
+
+            After the computational model design is completed, the model is implemented in the Python Language using the Pytorch library as a core component.
+Implementation of the computational model is done using an iterative software development model.
+This development model was chosen due to its adaptability to unexpected challenges which is necessary because of the challenges and unknowns with developing a novel method.
 
@@
 
+            To properly gauge the performance of the proposed method at approximating operators, specifically the solution operator of partial differential equations, experimental scenarios are developed in this phase.
+Specifically, the scenarios serves three goals which are proof of concept or validation that the method is able to learn operators, a case study of a more complex system with real world data, and a using the model as a surrogate.
+Together, these experimental scenarios determine the applicability of the model to the problem.
+In addition, the model will be compared to a baseline model in order to put into context the proposed model's performance.
+In addition, kernel-input correlation matrices and input-Lagrangian multiplier inner product matrix will also be computed.
+
       \item Data Generation and Retrieval
+
+            This phase of the study is tied to the experimental scenarios that have been developed.
+After determination of the scenario specifics, the data that will be used for training, validation, and testing of the model in each scenario will be either generated or retrieved from an external source.
+In addition, in each scenario the hyperparameters of the model will be determined using Bayesian optimization as an alternative to the traditional grid search method.
 
@@
 
+            The next phase after data generation or retrieval is preprocessing.
+This is a crucial step in allowing the core LSSVR to learn the mappings in spectral space.
+In order to do this, the data will need to be reshaped, and important features selected for.
+Finally, inputs to the LSSVR will need to be normalized or scaled such that the LSSVR model can much more easily learn the data.
+
       \item Experiments
+
+            This phase of the study executes the experimental scenarios that was determined previously. The preprocessed data will be used in accordance to the preplanned scenarios.
 
@@
 
+            The final phase of the study is the analysis and discussion of the results.
+Analysis of each experimental scenario will assess the extent of the model's capabilities.
+Another component of the analysis is interpretation the trained model and how it comes to the predictions that it makes.
+The discussion will also touch on the hyperparameter optimization and comparisons with the baseline model.
+This will show how the model performs differently compared to the baseline.
 \end{enumerate}
 
-\section{Sub Bab \texorpdfstring{$\alpha$}{α}}
-\noindent Misal kita mau masukin tabel, kita bisa juga.
-\begin{table}[H]
-  \caption{Tabel Sederhana Pertama}
-  \label{co:tabel1}
-  \begin{center}
-    \begin{tabular}{ |c|c|c| }
-      \hline
-      $G$     & $\text{dim }G$      & $\text{dim }F$ \\
-      \hline
-      $SU(N)$ & $N^2 -1$            & $N$            \\
-      $SO(N)$ & $\frac{1}{2}N(N-1)$ & $N$            \\
-      $Sp(N)$ & $N(2N+1)$           & $2N$           \\
-      $E_6$   & $78$                & $27$           \\
-      $E_7$   & $133$               & $56$           \\
-      $E_8$   & $248$               & $248$          \\
-      $F_4$   & $52$                & $6$            \\
-      $G_2$   & $14$                & $7$            \\
-      \hline
-    \end{tabular}
-  \end{center}
-\end{table}
+\section{Literature Study Method}
+\noindent As a basis for this study, information surrounding the topic is collected from literature sources such as books, journal articles, and other academic works like dissertations.
+The tools that are used to find these sources include Google Scholar and Google Search.
+The search terms used start with two terms which are partial differential equations and machine learning.
+Based on reading the most relevant literature, further search terms are created from variants of previous search terms combined with terms from literature that has been found.
 
-\section{Sub Bab \texorpdfstring{$\beta$}{ꞵ}}
-\noindent Atau bisa juga seperti berikut.
-\begin{table}[H]
-  \caption{Tabel Sederhana Kedua}
-  \label{co:tabel2}
-  \begin{center}
-    \begin{tabularx}{0.8\textwidth} {
-      |>{\raggedright\arraybackslash}X
-      |>{\raggedright\arraybackslash}X
-      |>{\raggedright\arraybackslash}X
-      |}
-      \hline
-      $G$     & $\text{dim }G$      & $\text{dim }F$ \\
-      \hline
-      $SU(N)$ & $N^2 -1$            & $N$            \\
-      $SO(N)$ & $\frac{1}{2}N(N-1)$ & $N$            \\
-      $Sp(N)$ & $N(2N+1)$           & $2N$           \\
-      $E_6$   & $78$                & $27$           \\
-      $E_7$   & $133$               & $56$           \\
-      $E_8$   & $248$               & $248$          \\
-      $F_4$   & $52$                & $6$            \\
-      $G_2$   & $14$                & $7$            \\
-      \hline
-    \end{tabularx}
-  \end{center}
-\end{table}
+\section{Data Generation and Retrieval Method}
+\noindent Data to be used in this study are acquired in two different ways.
+The first method is data generation.
+This is motivated by the fact that some partial differential equations do not have much open and accessible real world data available.
+As such the systems are simulated using the equations themselves.
+In simple scenarios like computing the antiderivative \(u\) of some function \(f \), this can be done by randomly generating \(u\) and then taking their derivatives to compute \(f\).
+The random function generation itself is done by generating random coefficients for basis functions like the Fourier series.
+Once all functions are generated, random noise is added to ensure that the model is also robust towards inexact measurements.
+A diagram illustrating the process is shown in \lccref{fig:data_generation_diagram}.
+
+\begin{figure}[H]
+      \centering
+      \begin{adjustbox}{max width=\textwidth}
+            \tikzfig{figures/data_generation_diagram}
+      \end{adjustbox}
+      \caption{Data generation diagram}\label{fig:data_generation_diagram}
+\end{figure}
+
+Data retrieval is the other option which in this case is used to retrieve data for weather prediction.
+Based on the scenario the data is to be used for, relevant subsets of the dataset is retrieved to a working machine.
+This study specifically uses a dataset provided by the European Center for Medium Range Weather Forecast (ECMWF) named ERA5 hourly data on single levels from 1940 to present \autocite{c3sERA5HourlyData2018}.
+The first step is selecting a geographical area to study, time period, NetCDF4 data format, and variables such as temperature at 2 meters above the surface.
+Then the second step is specifications are then used to request the data through the climate data store application programming interface.
+The downloaded data is then parsed using the Xarray library and preprocessed.
+
+\section{Computational Model Implementation Method}
+\noindent Implementation of the computational model follows an iterative development model.
+This model basically consists of repeated cycles or iterations of software development.
+Each cycle is loosely based on the waterfall development model, namely the processes of requirement gathering, analysis \& design, implementation, and testing.
+This iterative property is crucial for this study because all the requirements cannot be known beforehand.
+This model minimizes the risk in developing complex software with partially known initial requirements.
+A diagram of the model can be seen in \lccref{fig:iterative_development_diagram}.
+
+\begin{figure}[H]
+      \centering
+      \begin{adjustbox}{max width=\textwidth}
+            \tikzfig{figures/iterative_development_diagram}
+      \end{adjustbox}
+      \caption{Iterative development model}\label{fig:iterative_development_diagram}
+\end{figure}
+
+This development model was adapted from \textcite{bittnerManagingIterativeSoftware2006}. Each process in the model is explained as follows:
+\begin{enumerate}
+      \item Initial Planning
+
+            The first process of the iterative development model sets up the parameters for the iterative development.
+These parameters are the broad scope of the project and initial requirements such as core components like LSSVR\@.
+The initial requirements are crucial in guiding the rest of the development as more requirements are gathered.
+The initial planning also determines technical choices like tooling and choice of language.
+The planning process also includes a rough architecture based in initial requirements.
+
+      \item Requirements
+
+            This process separates out the backlog of requirements into those that will be worked on in the current iteration.
+These requirements ideally share some functionality in order to allow the same context to be retained within the iteration which reduces the burden of context switching.
+
+      \item Analysis and Design
+
+            This process an analysis of the requirements of the current iteration is performed.
+This involves determining the constraints and goals for each requirement.
+Constraints also need to consider previous iterations such that the requirements can be fulfilled effectively and efficiently without regressing progress that has been made such as breaking existing functionality.
+From this analysis, the design is updated so that the requirement can be fulfilled.
+The design itself informs how the code should be structured.
+The interfaces used in the code are also specified.
+
+      \item Implementation
+
+            The implementation process applies the design that has been produced.
+In addition to implementing the program, this process also implements tests which validate and verify the produced code.
+In the case of complex pieces of the design, an approach of creating tests and assertions first is taken.
+This way, the code can be run quickly and fail immediately to allow a quicker convergence on the intended functionality.
+
+      \item Testing and Evaluation
+
+            Once the design is implemented, tests that have been created are run.
+Each feature is tested in an integrated manner to expedite the process while still providing enough confidence in the software.
+The results of the testing process are evaluated and any failed tests are resolved whether by reimplementation or reassessment of the correctness of the tests.
+Any missing functionality or feature discovered during evaluation are added to the backlog of requirements.
+
+      \item Release
+
+            After an iteration, the current version of the software is released.
+The iterative nature of this development model necessitates the use of a versioning system.
+As such each release can be identified by a version number loosely based on semantic versioning \autocite{preston-wernerSemanticVersioning200}.
+This version numbering system consists of major number that indicates breaking changes, minor numbers which indicate features and non-breaking changes, and lastly patch numbers are used for fixes.
+A version number is read as \verb|MAJOR.MINOR.PATCH|.
+During active development, only major version 0 will be used to prevent too many major versions.
+The released software is hosted in its own GitHub repository at \url{https://github.com/nidduzzi/SpectralSVR}.
+
+\end{enumerate}
+
+\section{Research Tools}
+\noindent The tools that are used in this study can be categorized into hardware and software. The following are hardware that are used in this study:
+\begin{itemize}
+      \item Kaggle CPU Kernel~\autocite{GettingStartedKaggle}
+            \begin{itemize}
+                  \item 4 Cores Intel Xeon
+                  \item 30 Gigabytes RAM
+                  \item 20 Gigabytes Working storage
+            \end{itemize}
+      \item Kaggle GPU Kernel~\autocite{GettingStartedKaggle}
+            \begin{itemize}
+                  \item 4 Cores Intel Xeon
+                  \item 29 Gigabytes RAM
+                  \item 1 Nvidia P100 GPU
+                  \item 20 Gigabytes Working storage
+            \end{itemize}
+      \item Personal Computer
+            \begin{itemize}
+                  \item Intel i5-8300H
+                  \item 16 Gigabytes RAM
+                  \item Nvidia GeForce GTX 1060 Mobile
+                  \item 1.5 Terabytes Storage
+            \end{itemize}
+\end{itemize}
+The software tools used in this study are the following:
+\begin{itemize}
+      \item Python
+      \item Jupyter Notebook
+      \item Git
+      \item Poetry Python package manager
+      \item Web Browser
+      \item \LaTeX{}
+\end{itemize}

### 2024-11-26 skripsi/chapter1.tex
rename files to english versions, add data figures for antiderivative, add content on data and computational model, edit parts of ch 1 & 3

--- 2024-09-11 skripsi/bab1.tex
@@
 
-\begin{figure}[h] %h means here!
+\begin{figure}[ht] %h means here!
     \centering
@@
 As an example, the spectral method solves PDEs by formulating the solution as a linear combination of global basis functions like the Fourier series.
-This can be likened to how music combines sound waves of different things to produce the overall sound.
+This can be likened to how music combines different sound waves to produce the overall sound.
+For some function \(s\), the approximation \(s^*\) gets closer to the original with more linear combinations of basis functions.
 The complex formulation of the Fourier series is presented in \lccref{eq:fourier_series}.
+With this approach, the approximated function is characterized completely by its coefficients \(c_k\).
+This fact is exploited by the spectral method to solve differential equations.
+The solution function can be approximated by finding the mapping between input function coefficients and solution function coefficients.
+The mapping between a function \(s\) and its derivative \(s^{\prime}\) can be found using the derivative equation from their coefficients leading to \(\hat{s}_k = \hat{s}^{\prime}_k/\left(2\pi ik\right)\).
+Practically this would be done with a finite number of coefficients (\(k < \infty \)) and the coefficients \(\hat{s}^{\prime}_k\) are obtained using a Discrete Fourier Transform (DFT) algorithm like the Fast Fourier Transform (FFT).
 % TODO: Add diagram example for discretization of the domain by FEM/FDM methods
-\begin{equation}\label{eq:fourier_series}
-    s = \sum_{k} c_k e^{2\pi ikx}
-\end{equation}
-The example differential equation we wish to solve is the simple derivative in \lccref{eq:derivative}.
-In other words, the aim is to find a function \(u^{*} \) from a known function \(f^{*} \).
-This means we are learning the anti-derivative operator or more loosely known as the integral.
-To do this we first formulate both into separate Fourier series approximations \(u \) and \(f \) in \lccrefs{eq:example_fourier_1,eq:example_fourier_2} respectively.
 \begin{align}
-    \dv{u^*\left( x \right)}{x} & = f^*\left( x \right) \label{eq:derivative}                                                      \\
-    u^*\left( x \right)         & \approx u\left( x \right)         = \sum_{k} \hat{u}_k e^{2\pi ikx} \label{eq:example_fourier_1} \\
-    f^*\left( x \right)         & \approx f\left( x \right)         = \sum_{k} \hat{f}_k e^{2\pi ikx} \label{eq:example_fourier_2}
+    s & \approx s^* = \sum_{k} \hat{s}_k e^{2\pi ikx}\label{eq:fourier_series}
 \end{align}
-Next we take the derivative of \lccref{eq:example_fourier_1} which result in \lccref{eq:fourier_series_derivative}.
-Using this we can substitute the terms in \lccref{eq:derivative} with \lccrefs{eq:fourier_series_derivative,eq:example_fourier_2} giving \lccref{eq:example_spectral_method_fourier_substituted}.
-Finally, after some algebraic manipulation we obtain \lccref{eq:derivative_coeff}.
-One also needs to choose \(\hat{u}_{0}\), which is the integration constant.
-Practically this would be done with a finite number of modes and the coefficients \(\hat{f}_k\) are obtained using a Discrete Fourier Transform (DFT) algorithm like the Fast Fourier Transform (FFT).
-\begin{align}
-    \dv{u\left( x \right)}{x}                                    & = \sum_{k} \hat{u}_k\times \left( 2\pi ik \right) e^{2\pi ikx} \label{eq:fourier_series_derivative} \\
-    \sum_{k} \hat{u}_k\times \left( 2\pi ik \right) e^{2\pi ikx} & = \sum_{k} \hat{f}_k e^{2\pi ikx} \label{eq:example_spectral_method_fourier_substituted}            \\
-    \hat{u}_k                                                    & = \hat{f}_k / \left( 2\pi ik \right) \label{eq:derivative_coeff}
-\end{align}
-The fourth challenge with traditional methods is that they require prior knowledge of analytic forms of PDEs.
-This is because the solvers use the equations to formulate solutions.
-This makes traditional numerical approaches unsuited to data dominant problems.
-These challenges altogether are some of what weather forecasting faces; NWP has the immense task of modeling multiple scales of the Earth's atmosphere while accounting for geographical features of physical systems that are still not fully understood.
-Many other fields also face these challenges which has motivated research into alternative methods that do not completely rely on prior knowledge, are mesh free, and fast enough when solving forward problems.
+This leads us to the fourth challenge with traditional methods which is that they require prior knowledge of analytic forms of PDEs.
+This is because traditional solvers use the equations to formulate solutions.
+This makes traditional numerical approaches unsuited to problems where the governing equations are unknown or partially known.
+These challenges altogether are some of what weather forecasting faces; NWP has the immense task of modeling multiple scales of the Earth's atmosphere while accounting for features of physical systems that are still not fully understood.
+Many other fields such as epidemiology \autocite{brauerMathematicalModelsEpidemiology2019} and ecology \autocite{holmesPartialDifferentialEquations1994,turchinDoesPopulationEcology2001} also face these challenges.
+As with many other fields, at some point in time the governing equations of many systems were not known.
+This has motivated research into alternative methods that do not completely rely on prior knowledge, are mesh free, and fast enough when solving forward problems.
 
@@
     \item Functions the model works with are only continuous functions.
-    \item Hardware used in this project is limited to the standard offering on \url{kaggle.com} as of \today{}.
     \item The basis functions are limited to Fourier basis. % TODO: change this if more basis functions are added

### 2024-11-26 skripsi/chapter2.tex
rename files to english versions, add data figures for antiderivative, add content on data and computational model, edit parts of ch 1 & 3

--- 2024-08-22 skripsi/bab2.tex
@@
+% !TEX root = ./skripsi.tex
 \chapter{KAJIAN PUSTAKA}
@@
 Demikian halnya dengan judul sub bab.
+
+\section{Fourier Transform and Series}
+\noindent
+
+Complex numbers are numbers consisting of real and imaginary components.
+Complex numbers are written as in \lccref{eq:complex_number} with \(a \) and \(b \) being the real and imaginary components respectively.
+The imaginary component is multiplied by the imaginary unit \(i=\sqrt{-1}\).
+\begin{align}
+  c = a + bi \label{eq:complex_number} \\
+\end{align}
 
@@
 \begin{equation}
-        \Omega+\vb{I}\frac{1}{5}\to H\to \begin{bmatrix}
+  \Omega+\vb{I}\frac{1}{5}\to H\to
+  \begin{bmatrix}
     1.2000 & 0.9460 & 0.8007 & 0.6065 \\
@@
 \begin{equation}
-        A\to \begin{bmatrix}
+  A\to
+  \begin{bmatrix}
     0.0000 & 1.0000 & 1.0000 & 1.0000 & 1.0000 \\
@@
 \begin{equation}
-        B\to \begin{bmatrix}
+  B\to
+  \begin{bmatrix}
     0.0000 \\
@@
 \begin{equation}
-        A^{\dag}\to \begin{bmatrix}
+  A^{\dag}\to
+  \begin{bmatrix}
     -0.8994 & 0.4348  & 0.0652  & 0.0652  & 0.4348  \\
@@
 \begin{equation}
-        A^{\dag}B\to S\to \begin{bmatrix}
+  A^{\dag}B\to S\to
+  \begin{bmatrix}
     4.9421  \\
@@
 \begin{equation}
-        \alpha \to \begin{bmatrix}
+  \alpha \to
+  \begin{bmatrix}
     -0.6177 \\
@@
 \begin{equation}
-        U\to \begin{bmatrix}
+  U\to
+  \begin{bmatrix}
     0.3 \\
@@
 \begin{equation}
-        \Omega\to \begin{bmatrix}
+  \Omega\to
+  \begin{bmatrix}
     0.9560 & 0.9994 & 0.9350 & 0.7827 \\
@@
 \begin{equation}
-        \Omega\alpha\to \begin{bmatrix}
+  \Omega\alpha\to
+  \begin{bmatrix}
     -0.4904 \\
@@
 \begin{equation}
-        \Omega\alpha+b\vb{1}_{m}\to v\to \begin{bmatrix}
+  \Omega\alpha+b\vb{1}_{m}\to v\to
+  \begin{bmatrix}
     4.4516 \\
@@
 \begin{equation}
-        \sigma_x = \begin{pmatrix}
+  \sigma_x =
+  \begin{pmatrix}
     0 & 1 \\
@@
   \end{pmatrix},\quad
-        \sigma_y = \begin{pmatrix}
+  \sigma_y =
+  \begin{pmatrix}
     0 & -i \\
@@
   \end{pmatrix}, \quad
-        \sigma_z = \begin{pmatrix}
+  \sigma_z =
+  \begin{pmatrix}
     1 & 0  \\
@@
 \section{Referensi dan Citation}
-\noindent Sitasi dapat dimasukkan ke dalam Tugas Akhir seperti ini \cite{Fujita1996}.
+% \noindent Sitasi dapat dimasukkan ke dalam Tugas Akhir seperti ini \cite{Fujita1996}.
 Untuk sitasi dengan beberapa sumber, dapat dituliskan juga \cite{hohen1964,Kim2006}.

### 2024-11-26 skripsi/chapter4.tex
rename files to english versions, add data figures for antiderivative, add content on data and computational model, edit parts of ch 1 & 3

% !TEX root = ./skripsi.tex
\chapter{RESULTS AND DISCUSSION}
\noindent This chapter will elaborate on the results of the study and relevant phases for analysis. This chapter is organized into five sections which are the results of data generation, data retrieval, design of computational model, implementation of computational model, experimental scenarios, and the experiments themselves.

\section{Data Generation}\label{sec:data_generation}
\noindent This study uses two data acquisition approaches. The first approach which is discussed in this section is data generation. This process involves manufacturing data randomly in such a way that they obey the PDEs to be modeled. The generated data consists of features and labels. These features and labels in the context of PDEs are parameters and the solution of the PDEs, respectively. The PDEs enforce a relationship between parameters and the solution. This relationship is implicitly encoded into the features and labels, which is what machine learning models can learn. Because the solution and parameters to PDEs are functions and there are many kinds with different properties, generating all the different kinds of functions is a difficult task. This is why this study focuses on Fourier functions. This means that out of the space of all functions \(F \) which include categories such as polynomials \(f\left(x\right)=a_{n}x^n+\cdots+a_1x+a_0\) where \(f\in F\), and \(a_n\) are constants; we only consider the subset of functions \(U \subset F\) which are of the form \(u\left(x\right)=\sum_{k}^{m}c_k e^{2\pi i k \frac{x}{P}}\).

Using the subset of Fourier functions has several benefits which has motivated the choice. First these functions are characterized purely by their coefficients \(c_k\), meaning there is no need to store discretized values which potentially saves space and computation. The second benefit is that other functions such as polynomials can be approximated by them using the Fourier transform. This means that despite limiting the set of functions to Fourier functions, the behavior of PDEs with other sets of functions can be approximated to a certain extent. The final benefit is the mature ecosystem around these functions which include fast algorithms for the Fourier transform and even numerical approaches for solving known PDEs like the previously mentioned spectral method. In summary the generated data consists of features and labels which are Fourier functions implicitly defining the relationship enforced by a PDE and scenario. After establishing the kind of functions to be used in dataset generation, the process can proceed. There are 4 steps involved in the data generation:% TODO: add reference to second chapter for spectral method, fourier transform, and other external concepts.
\begin{enumerate}
  \item Scenario and PDE Determination:
    The first step of data generation is determining the scenario related to the PDE or governing equations. First, the PDE to be modeled is determined based on the goals of the dataset. Then, one or more of the parameters is chosen to predict the solution. The chosen parameters will be called the input functions and the solution will be called output functions from here on. The second part of the scenario is the domain or more simply the physical space occupied by the system to be modeled. The domain will be used to compute the function values in relation to the physical space from coefficients of Fourier functions.
  \item Parameter Determination:
    The second step is determining all parameters other than that input parameter based on the scenario and governing equation. These parameters may be coefficients such as material properties like density or viscosity, or forcing terms which model external influence on the system like a heat source in the case of the heat equation. Depending on the parameters, solutions of PDEs may behave very differently, such as the appearance of discontinuities in the solution to low viscosity Burgers' equation. Because of this, the choice of parameters is guided by what the dataset seeks to do.
  \item Random Coefficient Generation:
    The third step of data generation is randomly generating the solutions for the chosen equation. Generating random functions in the space of Fourier functions exploits the fact that the coefficients characterize the function completely. By randomly assigning coefficients \(c_k\), many functions can be generated randomly with very little cost. Since the coefficients need to be complex numbers as in \lccref{eq:complex_number}, both real and imaginary components are generated independently by assigning a random value to each component for each wave number \(k\). They are then put together again into complex numbers.

    Since only real functions are of interest in this study, the generation cost can be approximately halved. This is because for real functions the coefficients for negative wave numbers \(k\) are complex conjugate of the positive wave numbers. This means that once the positive coefficients are generated, one only needs to compute their complex conjugate and concatenate the result with the coefficients of positive wave numbers. For dimensions higher than one, a simpler approach is used. The coefficients are generated for all wave numbers including the negative ones. The inverse Fourier transform is computed and this results in complex functions. The real components of these functions are kept and the Fourier transform is applied to get the coefficients of the real functions. Finally, these generated coefficients then be used with the basis functions as input functions.
    % TODO: add diagram for generating real functions, the mirroring process too
  \item Forcing Term Computation:
    Finally, in order to ensure that the generated solution and chosen parameters satisfy the equation, the forcing term is computed as the residual of the equation of interest with the parameters that was previously determined. This computation is done using the spectral method.
  \item Function Value and Noise Computation:
    The generated solution and forcing functions are labeled as input and output functions. The values of both functions in the domain can then be computed using the scenario determined in the first step. Once all coefficients are generated, the function values are computed with an inverse Fourier transform. The real component of the function values are retained, and the imaginary component are zeroed out. Noise is added to the function values here as needed. The processed function values are then converted back into coefficients using a Fourier transform. This processing is necessary to ensure that the coefficients are only describing the real function.

\end{enumerate}

These four steps are the general processes involved in generating datasets for this study. Further specifics of the generation process of each dataset is explained in their respective subsections.

\subsection{Data Generation: Anti-derivative}
\noindent The first dataset is a simple one dimensional derivative. This was chosen as a simple proof of concept of the ability to solve a differential equation. The equation is related to many real-world problems such as acceleration and speed. One can imagine a train in an ideal world where acceleration is directly translated into speed. When the train accelerates at time \(t \) by some amount \(a \), we can expect the train to have some speed \(u \). In this ideal world, the relationship between speed and acceleration can be modeled with a simple differential \lccref{eq:derivative}. This scenario is found in many real systems albeit often with many more details such as different components of acceleration from friction, drag, gravity, and other factors.
As previously mentioned in \lccref{sec:data_generation}, both velocity \(u \) and acceleration \(a \) are modeled with Fourier series in \lccrefs{eq:fourier_speed,eq:fourier_acceleration} respectively.
\begin{align}
  \dv{u\left( t \right)}{t} & = a\left( t \right) \label{eq:derivative}                                                           \\
  u\left( t \right)           & = \sum_{k} \hat{u}_k e^{2\pi ikt} \label{eq:fourier_speed}        \\
  a\left( t \right)           & = \sum_{k} \hat{a}_k e^{2\pi ikt} \label{eq:fourier_acceleration}
\end{align}
The domain of the scenario is a two-hour time window. This number was chosen because it is around the ideal length of travel time on high speed rail in comparison to air travel and car travel \autocite{givoniDevelopmentImpactModern2006,wangEfficiencySpatialEquity2019,wrro2236}. This is the first step in generating this dataset.

In the second step, as the derivative \lccref{eq:derivative} does not contain any parameters other than the acceleration which is the input parameter, there are no other parameters to determine. Therefore, the data generation process proceeds to generating coefficients for the speed functions \(\hat{u} \). The coefficients are assigned randomly from a Gaussian distribution with a mean of zero and standard deviation of one. This choice was made such that most wave numbers will have a coefficient of close to zero leaving a sparse set of wave numbers to mostly affect the resulting function. In total, 5000 unique functions are generated with 100 complex coefficients each.

In the third step, the output function coefficients are computed. To find the relation between \(\hat{u}_k \) and \(\hat{a}_k \), we need to find substitutes for each term in \lccref{eq:derivative}. To do this, we take the derivative of \lccref{eq:fourier_speed} which result in \lccref{eq:fourier_series_derivative}. Using this we can substitute the terms in \lccref{eq:derivative} with \lccrefs{eq:fourier_series_derivative,eq:fourier_acceleration} giving \lccref{eq:example_spectral_method_fourier_substituted}. Finally, after some algebraic manipulation we obtain the relationship between the input \(a^*\) and output function \(u^*\) in terms of their coefficients in \lccref{eq:derivative_coeff}. One also needs to choose the integration constant \(\hat{u}_{0}\) because at \(k=0\) \lccref{eq:derivative_coeff} becomes a division by zero.
\begin{align}
  \dv{u\left( x \right)}{x}                                    & = \sum_{k} \hat{u}_k\times \left( 2\pi ik \right) e^{2\pi ikx} \label{eq:fourier_series_derivative} \\
  \sum_{k} \hat{u}_k\times \left( 2\pi ik \right) e^{2\pi ikx} & = \sum_{k} \hat{a}_k e^{2\pi ikx} \label{eq:example_spectral_method_fourier_substituted}            \\
  \hat{u}_k                                                    & = \hat{a}_k / \left( 2\pi ik \right) \label{eq:derivative_coeff}
\end{align}

In the final step, using randomly generated values of \(\hat{a}_k\), the corresponding values of \(\hat{u}_k\) are computed with \lccref{eq:derivative_coeff}. These coefficients are then used to compute the function values inside the domain. The two-hour time window is represented by a grid of 500 discrete points. With the coefficients and evaluation points ready, the function values are computed using \lccrefs{eq:fourier_speed,eq:fourier_acceleration}. Next, noise is added to the function values in order to motivate models learning on the dataset to generalize on noise. To also allow evaluation of how well the model performs with different levels of noise, the samples are duplicated into three copies for each high, medium and low noise levels. The function values of each copy is perturbed with noise from a Gaussian distribution with zero mean and standard deviation of some percentage of the average function value standard deviation. The percentages of each high, medium, and low noise levels are 5, 10, and 50 percent. The perturbed function values are then transformed back into their coefficients. An example generated function and its different perturbed versions is shown in \lccref{fig:antiderivative_noise_levels}. The horizontal axis indicates time which is displayed in units of hours. The vertical axis indicates velocity in abstract units.

% TODO: add figures and tables of generated data and some intermediate steps.
\begin{figure}[H]
  \centering
  \begin{subfigure}{\linewidth}
    \begin{adjustbox}{width=\linewidth}
      \input{figures/clean_perturbed_solution_0.pgf}
    \end{adjustbox}
    \caption{}\label{fig:antiderivative_noise_levels}
  \end{subfigure}
  \begin{subfigure}{\linewidth}
    \begin{adjustbox}{width=\linewidth}
      \input{figures/antiderivative_clean_0.pgf}
    \end{adjustbox}
    \caption{}\label{fig:antiderivative}
  \end{subfigure}
  \begin{subfigure}{\linewidth}
    \begin{adjustbox}{width=\linewidth}
      \input{figures/derivative_clean_0.pgf}
    \end{adjustbox}
    \caption{}\label{fig:derivative}
  \end{subfigure}
  \caption{(\subref{fig:antiderivative_noise_levels}) A generated function with no noise (clean), low noise level (5\%), medium noise level (10\%), and high noise levels (50\%).\ (\subref{fig:antiderivative}) Antiderivative function with no noise.\ (\subref{fig:derivative}) Derivative function with no noise.}
\end{figure}
% TODO: interesting note that model trains better on function to coefficient task when the antiderivative is computed from the randomly generated derivative than if the derivative is computed from the randomly generated antiderivative. THIS NEEDS A REASON AND ANALYSIS SO MIGHT NOT BE NEEDED IN THIS WRITING. MAYBE A GOOD IDEA FOR A SEPARATE PIECE

\subsection{Data Generation: Burgers' Equation}
\noindent The second dataset generated in this study concerns the Burgers' equation. This equation has been used to model a variety of cases including fluid dynamics, traffic flow, and, shock waves \autocite{bonkileSystematicLiteratureReview2018,orlandiBurgersEquation2000,becBurgersTurbulence2007,jamesonEnergyEstimatesNonlinear2007}. This equation is also used as a base problem for testing the effectivity of numerical methods in solving non-linear PDEs \autocite{barterShockCapturingPDEbased2008,banksNumericalErrorEstimation2012, tabatabaeiImplicitMethodsNumerical2007,bonkileSystematicLiteratureReview2018}. The nonlinear term in the equation creates steep gradients and even shock waves which are discontinuous with low viscosity conditions. These challenges test the stability of numerical solvers. This is the scenario and reason for the choice of this PDE\@. To control the viscosity and therefore the steepness of gradients, the formulation of the Burgers' equation considered in this study is the forced viscous Burgers' equation in one dimension. For a velocity of \(u(x, t)\), viscosity of \(\nu \), and forcing term of \(f(x, t)\), the formulation of the forced Burgers' equation is shown in \lccref{eq:forced_viscous_burgers}.
\begin{align}
  \pdv{u}{t}+u\pdv{u}{x}-\nu\pdv[2]{u}{x} & = f \label{eq:forced_viscous_burgers}
\end{align}
The domain of we consider here is based on an exact solution of the equation. This is done so that the learned solver model can be tested on the exact solution. There are a number of sources in literature on the exact solution of the Burgers' equation \autocite{bentonTableSolutionsOnedimensional1972,wazwazPartialDifferentialEquations2010,woodExactSolutionBurgers2006}. In this study, we use a specific solution by \textcite{woodExactSolutionBurgers2006} which can be seen in \lccref{eq:burgers_exact_solution}. This solution is periodic in space but not in time. Therefore, the domain in space will be based on the spatial periodicity of the exact solution which is two. As such, the space domain spans from 0 to 2. The time domain, on the other hand, is chosen to span from 0 to 10 such that enough details of the solution is included.
\begin{equation}
  u(x,t) = \frac{2\nu\pi e^{-\pi^2\nu t}\sin(\pi x)}{a+e^{-\pi^2\nu t}\cos(\pi x)} \label{eq:burgers_exact_solution}
\end{equation}
Continuing to the second step, the parameters involved in \lccref{eq:forced_viscous_burgers} are the viscosity \(\nu \) and the forcing term \(f \). Since the forcing term is dependent on the solution in this step, the only parameter to determine is the viscosity. We choose three constant viscosity values which are 0.1, 0.01, and 0.0. These values are chosen so that a variety of behaviors are represented in the dataset from viscous to inviscid flow.

After this, in the third step, the solution functions \(u \) are generated with 20 modes in time and 20 in space and 500 unique function samples for each viscosity value. In total 1500 unique solution functions are generated.

As for the forcing term, it is computed using \lccref{eq:forced_viscous_burgers}. The solution field \(u\) and forcing term \(f\) are modeled with Fourier series in \lccrefs{eq:fourier_field,eq:fourier_force} where \(k\) is a vector of spatial and temporal wave number such that \(k_t\) is the temporal wave number and \(k_x\) is the spatial wave number.
\begin{align}
  u\left(x, t \right)           & = \sum_{k_{x}} \sum_{k_{t}} \hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)} \label{eq:fourier_field}        \\
  f\left(x, t \right)           & = \sum_{k_{x}}\sum_{k_{t}} \hat{f}_k e^{2\pi i(k_{x}x+k_{t}t)} \label{eq:fourier_force}
\end{align}
Substituting the terms in \lccref{eq:forced_viscous_burgers} with the respective Fourier series, we get the equation \lccref{eq:forced_viscous_burgers_fourier_substitution}. A problem one notices is the nonlinear term \(u\pdv{u}{x}\). A naive approach would multiply all wave numbers terms with each other.
\begin{align}
  u\pdv{u}{x} = \left(\sum_{k_{x}} \sum_{k_{t}} \hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)}\right) \times \left(\sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{x})\hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)}\right)
\end{align}
This is computationally expensive operation with \(N^2\) multiplications \autocite{lariosMATH934BURGERS2021,robertsDealiasedConvolutionsPseudospectral2011,shenSpectralMethodsAlgorithms2011,orszagComparisonPseudospectralSpectral1972}. To avoid this complexity, the term is first reformulated into \(\pdv{x}(u^2/2)\). Then to avoid aliasing, the coefficients are padded with 50\% zeros such that the padded coefficients are 3/2 times the size of the original \autocite{orszagEliminationAliasingFiniteDifference1971, lariosMATH934BURGERS2021}. Then we use the padded coefficients to compute the function values in the physical domain using the inverse transform. And then, the point wise squaring operation is performed and transform the results back to spectral domain. The resulting coefficients are then trimmed back to their original size before padding. Finally, we multiply the resulting coefficients \(\hat{uu}_k\) by the derivative constants. This operation is much more efficient with only \(1.5 N\) multiplications. This is still more efficient than the naive approach even after taking into account the transforms involved adds \(O(2\times 1.5Nln(1.5N))\) operations if using a Fast Fourier Transform algorithm. Putting all the above together, results in \lccref{eq:forced_viscous_burgers_fourier_substitution}.
\begin{equation}
  \begin{split}
    \sum_{k_{x}} \sum_{k_{t}} \hat{f}_k e^{2\pi i(k_{x}x+k_{t}t)} =
    & \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{t}) \hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)} \\
    & + \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{x})\hat{uu}_k e^{2\pi i(k_{x}x+k_{t}t)} \\
    & - \nu\sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{x})^2\hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)} \label{eq:forced_viscous_burgers_fourier_substitution}
  \end{split}
\end{equation}
\begin{align}
  \sum_{k_{x}} \sum_{k_{t}} \hat{f}_k & = \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{t}) \hat{u}_k + (2\pi i k_{x})\hat{uu}_k - \nu(2\pi i k_{x})^2\hat{u}_k \label{eq:forced_viscous_burgers_fourier} \\
  \hat{f}_k & = (2\pi i k_{t}) \hat{u}_k + (2\pi i k_{x})\hat{uu}_k - \nu(2\pi i k_{x})^2\hat{u}_k \label{eq:forced_viscous_burgers_coeff}
\end{align}
After simplifying the equation, we get the coefficients as in \lccref{eq:forced_viscous_burgers_coeff}. Using this equation, the exact forcing term corresponding to the randomly generated solution can be computed with relatively low cost. Finally, the function values of both the solutions and forcing terms are perturbed by adding Gaussian noise with a mean of zero and standard deviation of 10\% of the function value standard deviation to the values of the inverse transform. The perturbed coefficients are then recomputed from the sum and the final perturbed functions are obtained.

\section{Data Retrieval}
\noindent The second data acquisition approach retrieves data of a from an external source. This approach downloads the external data to a local machine. In this study, the specific dataset that will be used is the ERA5 dataset from the European Center for Medium-range Weather Forecast (ECMWF). Specifically, the ERA5 dataset is a reanalysis which means it combines observational data from all over the world in order to present a more complete picture of the weather system. This combination process, named 4D variational data assimilation, takes into account the physics known to be involved in the system. As an example weather station data which take measurements such as wind speed, humidity, and temperature of the immediate surroundings of the weather station is very limited in giving a broader picture of weather over a larger area. Even technologies like earth observations satellites are limited to what they can observe at any single point in time as most cannot see the entirety of the earth's surface at once. The ERA5 dataset specifically, assimilates previous forecasts with observational data every 12 hours. The ERA5 reanalysis is available at the following url (\url{https://cds.climate.copernicus.eu/datasets/reanalysis-era5-single-levels}).

The original dataset made available by ECMWF has a grid size of \ang{0.25} by \ang{0.25} in latitude and longitude for atmospheric data. Data of oceanic waves are also available at a coarser grid size of \ang{0.5} by \ang{0.5}. However, we will use a cloud optimized version called WeatherBench2 that is easier to retrieve \autocite{raspWeatherBench2Benchmark2023}. This is because the data is available in several more grid sizes such as \ang{1.5}. In addition, the data can be readily downloaded to a local machine without waiting for further processing on the server. The guide for working with the dataset is available at (\url{https://weatherbench2.readthedocs.io/en/latest/data-guide.html}). In our specific case, we use the version labeled \verb|1959-2023_01_10-6h-64x32_equiangular_conservative.zarr|. This dataset spans from year 1959 to 2023 with a grid size of \ang{5.625} or resolution of 64 by 32 which spans from \ang{-87.19} to \ang{87.19} in latitude and \ang{0.0} to \ang{354.4} in longitude. The dataset is also downsampled to 6 hour intervals that starts at midnight UTC January 1959 1\textsuperscript{st} and ends at 18:00 UTC January 10\textsuperscript{th} 2023.

While the original data provided by ECMWF is available in NetCDF or GRIB, the WeatherBench2 version is provided using the Zarr format in a Google Cloud Storage Bucket. This setup allows the use of libraries that support the Zarr format to access the dataset remotely. The particular library we use is called \emph{Xarray} version \verb|2024.9.0| \autocite{hoyer2017xarray,hoyerXarray2024}. Accessing the remote dataset is done as shown in \lccref{fig:access_remote_zarr}. In order to ensure access is granted, the storage option token is set to anon so that the method uses the anonymous only public access mode of authentication \autocite{GCSFSGCSFs2023122post1+1g8e500c6dirty}.

\begin{figure}[H]
  \centering
  \begin{lstlisting}[language=Python]
  import xarray as xr
  xr.open_zarr(
      "DATASET_ADDRESS",
      storage_options = {"token": "anon"},
  )
  \end{lstlisting}
  \caption{Example of using Xarray to access a publicly accessible Zarr dataset hosted on Google Cloud Storage Bucket.} \label{fig:access_remote_zarr}
\end{figure}

The dataset includes 62 variables with some variables also spanning 13 discrete vertical levels in the atmosphere. For our use, we will only be using the 2-meter temperature of the atmosphere. This is the air temperature 2 meters above the surface be it land, sea, or inland water. This variable is in units of kelvin. The values of this variable is obtained by interpolating between the model values at the surface and the lowest model vertical level. We also limit the time range to .... An example of the data that was retrieved can be seen in .
% TODO: talk about selecting the time here
% ECMWF description
% - Role
% - legitimacy
% - Weatherbench2
% data description
% - data assimilation, maybe reference a general description
% - variables
% - dimensions/coordinates (time, spatial) and resolution in each
% - climatology

\section{Design of Computational Model}
\noindent In this section, we will discuss the design of the computational model that is proposed in this work. An illustration of the computational model is show in \lccref{fig:computational_model}.

\begin{figure}[H]
  \centering
  \begin{adjustbox}{max width=\textwidth}
    \tikzfig{figures/computational_model}
  \end{adjustbox}
  \caption{Computational Model of SpectralSVR}\label{fig:computational_model}
\end{figure}

The computational is divided into four large phases. The processes within these phases are based on the broad outcomes of the phase. The phases themselves are data preparation, data transformation, model training, and model evaluation. Each phase is composed of processes that together works toward the output of the larger process.

\subsection{Data Preparation}
\noindent The data preparation phase starts off the computation by preparing the data that is to be used in this study. This phase starts with specifying the problem to be solved. This translates to the dataset that will be used to represent these problems. The first type of dataset is generated based on a known governing equation or PDE\@. Using said equation, the goal is to generate pairs of functions that are related to each other by the equation. In the next process, generally, the solution function is first generated randomly. This is done by generating random numbers to use as coefficients of a set of basis functions. Then parameters of the equation is determined, such as term coefficients. Using the generated solution and predetermined parameters, a forcing term can generally be computed to satisfy the equation. Augmentations such as noise can then be added in the final process which is evaluating the function values. These processes result in a generated dataset. To verify the generation method and any models trained on the generated data one can use exact analytical solutions of the governing equations.

The second type of dataset is retrieved from an external source. The data source is first identified, in our case it is the WeatherBench 2 collection of datasets. The specific dataset from the collection of different dataset versions is first determined. And then, we determine the filters for the portions of the dataset we are interested in. Once the dataset and filters are determined, the retrieval process starts by accessing the dataset using the \emph{Xarray} library \autocite{hoyer2017xarray,hoyerXarray2024}. The filters are applied as in . % TODO: add figure for filtering process and local save process
The filtered version is then stored locally. Using the stored dataset, the basis coefficients of the data is computed using a discrete Fourier transform.

\subsection{Data Transformation}

\subsection{Model Training}

\subsection{Model Evaluation}

\section{Implementation of Computational Model}
\noindent

\section{Experimental Scenarios}
\noindent

\section{Experimental Results}
\noindent

% \section{Sub Bab Hasil}
% \noindent Bab ini memaparkan pekerjaan penelitian dan, terutama, hasil-hasilnya, untuk dianalisis. Secara komprehensif bab ini merepre-sentasikan curahan pemikiran dan kemampuan mahasiswa dalam menjalani pekerjaan penelitian, yang hasil-hasilnya dapat dipertanggungjawabkan. Banyak pendukung yang diperlukan dalam penulisan bab ini, seperti skema penting pengolahan data, penurunan model matematika, asumsi khusus, tabulasi hasil dan analisis, dan gambar atau grafik yang membantu dalam paparan analisis. Judul bab dan sub bab disesuaikan dengan isi paparan.

% \section{Memasukkan Gambar}
% \noindent Setiap gambar harus dirujuk pada naskah TA, termasuk gambar pada Lam- piran, menggunakan huruf pertama kapital (G) dan nomor gambar, tidak berdasarkan posisi relatifnya (misalnya di bawah ini atau sebelum ini). Format gambar yang umum adalah jpg, png, dan postscript (ps atau eps). Ukuran huruf pada nama sumbu dan label figures/grafik harus cukup besar dan jelas, demikian halnya dengan angka pada sumbu. Gambar dan grafik dapat berwarna dengan pilihan warna yang tegas dan jelas.

% \subsection{Contoh Gambar Sederhana}
% Contoh menginput gambar pada buku TA pada
% \begin{figure}[ht] %h artinya here!
%     \centering
%     \includegraphics[width=0.3\linewidth]{figures/Semiconductor-Fermi-Level-Band-Diagram-1.jpg}
%     \caption{Tingkatan Fermi pada\\Bahan Semikonduktor}\label{fermilevel}
% \end{figure}
% Apabila ada dua gambar, kita juga bisa menaruh keduanya berdampingan.

% \begin{figure}[H]
%     \centering
%     \subfigure[]{
%         \includegraphics[width=0.4\linewidth]{figures/Semiconductor-Fermi-Level-Band-Diagram-1.jpg}\label{surf-1}
%     }\hspace{0.1\linewidth}
%     \subfigure[]{
%         \includegraphics[width=0.4\linewidth]{figures/Semiconductor-Fermi-Level-Band-Diagram-1.jpg}\label{surf-2}
%     }
%     \caption{Dengan menempatkan gambar \subref{surf-1} dan \subref{surf-2}, pembaca akan lebih mudah membandingkan keduanya.}\label{surface}
% \end{figure}

### 2024-12-07 skripsi/chapter2.tex
finish ch4 computational model, start implementation

@@
 After eliminating $W$ and $\vb*{e}$, with $\vb{1}_{n} = \langle 1,\dots,1\rangle$, $\vb{y} = \lbrack y_1, \dots, y_n \rbrack $, and ${\alpha} = \lbrack \alpha_1, \dots, \alpha_n \rbrack $ the solution is as follows in block matrix notation
-\begin{equation} \label{eq:lssvrSolution}
+\begin{equation} \label{eq:lssvr_solution}
   \begin{bmatrix}
@@
 
-The solution in \cref{eq:lssvrSolution}
+The solution in \cref{eq:lssvr_solution}
 
 \begin{algorithm}[H]
-  \caption{LSSVR Training}\label{alg1:cap}
+  \caption{LSSVR Training}\label{alg:lssvr_training}
   \begin{algorithmic}[1]
-    \Require $\vb{X}, \vb{y}, \gamma$
-    \Ensure $\vb{\alpha}, b$
-    \State $\Omega \gets [[]]$ \Comment{Construct matrix of inner products in high dimensional space}
+    \Procedure{SolveLSSVR}{$\vb{X}, \vb{y}, \gamma $}
+    \State{\(\Omega \gets [[]]\)}
+    \Comment{Construct matrix of inner products in high dimensional space}
 
-    \For{$k=0 \to n$}
-    \For{$l=0 \to n$}
-    \State$\Omega_{k,l}\gets K(\vb{X}_k,\vb{X}_l)$
-    \EndFor
-    \EndFor
-    \State $\vb{H} \gets \Omega + \frac{\vb{I}}{\gamma}$
+    \For{\(k=0 \to n\)}
+    \For{\(l=0 \to n\)}
+    \State{\(\Omega_{k,l}\gets K(\vb{X}_k,\vb{X}_l)\)}
+    \EndFor{}
+    \EndFor{}
+    \State{\(\vb{H} \gets \Omega + \frac{\vb{I}}{\gamma}\)}
     % \State $\vb{1} \gets [1,1,...,1]$
-    \State $\vb{A} \gets [[]]$ \Comment{Construct left hand side matrix}
-    \State $\vb{A}_{0,0} \gets 0$
-    \For{$k=0 \to n$}
-    \State $\vb{A}_{k+1,0} \gets 1$
-    \State $\vb{A}_{0,k+1} \gets 1$
-    \EndFor
-    \For{$k=0 \to n$}
-    \For{$l=0 \to n$}
-    \State $\vb{A}_{k+1,l+1} \gets \vb{H}_{k,l}$
-    \EndFor
-    \EndFor
-    \State $\vb{B}\gets []$ \Comment{Construct left hand side of the equation}
-    \State $\vb{B}_0 \gets 0$
-    \For{$k=0 \to n$}
-    \State $\vb{B}_{k+1} \gets \vb{y}_{k}$
-    \EndFor
-    \State $\vb{A}^{\dagger} \gets pseudoInverse(\vb{A})$ \Comment{Compute solution using pseudo inverse}
-    \State $\vb{S} \gets \vb{A}^{\dagger}\vb{B}$
-    \State $b \gets \vb{S}_{0}$
-    \For{$k=0 \to n$}
-    \State $\vb{\alpha}_{k} \gets \vb{S}_{k+1}$
-    \EndFor
+    \State{\(\vb{A} \gets [[]]\)}
+    \Comment{Construct left-hand side matrix}
+    \State{\(\vb{A}_{0,0} \gets 0\)}
+    \For{\(k=0 \to n\)}
+    \State{\(\vb{A}_{k+1,0} \gets 1\)}
+    \State{\(\vb{A}_{0,k+1} \gets 1\)}
+    \EndFor{}
+    \For{\(k=0 \to n\)}
+    \For{\(l=0 \to n\)}
+    \State{\(\vb{A}_{k+1,l+1} \gets \vb{H}_{k,l}\)}
+    \EndFor{}
+    \EndFor{}
+    \State{\(\vb{B}\gets []\)}
+    \Comment{Construct left-hand side of the equation}
+    \State{\(\vb{B}_0 \gets 0\)}
+    \For{\(k=0 \to n\)}
+    \State{\(\vb{B}_{k+1} \gets \vb{y}_{k}\)}
+    \EndFor{}
+    \State{\(\vb{A}^{\dagger} \gets pseudoInverse(\vb{A})\)}
+    \Comment{Compute solution using pseudo inverse}
+    \State{\(\vb{S} \gets \vb{A}^{\dagger}\vb{B}\)}
+    \State{\(b \gets \vb{S}_{0}\)}
+    \For{\(k=0 \to n\)}
+    \State{\(\vb{\alpha}_{k} \gets \vb{S}_{k+1}\)}
+    \EndFor{}
+    \State{\textbf{return}\(\vb{\alpha}, b\)}
+    \EndProcedure{}
   \end{algorithmic}
@@
 
-The basic psuedocode from the LSSVM Equation for function regression is defined in \nameref{alg1:cap} for a training set of length $n$, features $\vb{X}$, and labels $\vb{y}$.
+The basic pseudocode from the LSSVM Equation for function regression is defined in \lccref{alg:lssvr_training} for a training set of length $n$, features $\vb{X}$, and labels $\vb{y}$.
 Training the LSSVM means computing the values of langrange multipliers $\vb{\alpha}$ and bias $b$.
-$K$ is the kernel function used to compute the inner products in high dimensional space, here we asume the RBF kernel.
+$K$ is the kernel function used to compute the inner products in high dimensional space, here we assume the RBF kernel.
 $\vb{A}$ is a matrix of size $n+1$ by $n+1$.
@@
 
-After training the model can be used for prediction of unseen points.
-The psuedocode for prediction is shown in \nameref{alg2:cap} for prediction features $\vb{U}$.
-The trained model uses the learned multipliers of training points $\vb{\alpha}$, the training points themselves $\vb{X}$, and the bias $b$.
+After training the model can be used for prediction of unseen features.
+The pseudocode for prediction is shown in \lccref{alg:lssvr_prediction} for prediction features $\vb{U}$ with \(p \) samples.
+The trained model uses the training features themselves $\vb{X}$ with \(n \) samples, the learned multipliers of training points $\vb{\alpha}$, and the bias $b$.
 
 \begin{algorithm}[H]
-  \caption{LSSVR Prediction}\label{alg2:cap}
+  \caption{LSSVR Prediction}\label{alg:lssvr_prediction}
   \begin{algorithmic}[1]
@@
 
-    \For{$k=0 \to m$}
+    \For{$k=0 \to p$}
     \For{$l=0 \to n$}

### 2024-12-07 skripsi/chapter4.tex
finish ch4 computational model, start implementation

@@
 
-\section{Data Retrieval}
+\section{Data Retrieval}\label{sec:data_retrieval}
 \noindent The second data acquisition approach retrieves data of a from an external source.
@@
 
-\section{Design of Computational Model}
+\section{Design of Computational Model}\label{sec:computational_model_design}
 \noindent In this section, we will discuss the design of the computational model that is proposed in this work. An illustration of the computational model is show in \lccref{fig:computational_model}.
@@
 
-The computational is divided into four large phases.
+The computational model is divided into four large phases.
 The processes within these phases are based on the broad outcomes of the phase.
@@
 The specific dataset from the collection of different dataset versions is first determined.
+The dataset is available in the \emph{Zarr} format.
 And then, we determine the filters for the portions of the dataset we are interested in.
 Once the dataset and filters are determined, the retrieval process starts by accessing the dataset using the \emph{Xarray} library \autocite{hoyer2017xarray,hoyerXarray2024}.
-The filters are applied as in .
-% TODO: add figure for filtering process and local save process
-The filtered version is then stored locally. Using the stored dataset, the basis coefficients of the data is computed using a discrete Fourier transform.
+The filters are applied as in ....
+% TODO: add figure for code of the filtering process and local save process
+Finally, the filtered version is stored locally. The local dataset is also stored in the \emph{Zarr} format.
 
 \subsection{Data Transformation}
+\noindent The second phase of the computational model transforms the data that has been prepared into a form that can be used with the proposed model.
+In this study, there are two ways a dataset can be used.
+The first and simplest way is to predict the solution function from the forcing term for a given set of PDE parameters.
+In this case, the input function is the forcing term.
+In other words, the input function is the predictor or independent variable that will be used to predict the solution function.
+As such, the output function is the solution function.
+The antiderivative dataset is used in this way.
+The derivative, which represents the acceleration function, is used to predict the velocity function.
+Which means that the input function is the acceleration function and the output function is the velocity function.
+The second use of a dataset depends on whether it can be interpreted as a mapping of a previous function to the next function.
+In other words, a series of functions related to the previous function as a sum of the previous function and a perturbation.
+A commonly used form of this are time series.
+Generally, a time series can be represented as \lccref{eq:time_step_function}.
+This function describes the evolution of function \(f\) as a sum of some initial state \(f^0\) and perturbation which is its rate of change \(\dv{f}{t}\) at a point in time close to the current time multiplied by the time step \(\delta t\).
+\begin{equation}
+  f^{t+1} = f^{t} + \delta t \times \dv{f}{t} \label{eq:time_step_function}
+\end{equation}
+In this case the previous function and any other independent variables like the forcing term involved in the time derivative \(\dv{f}{t}\) is used to predict the perturbation which is the time derivative itself.
+It would mean that each sample function in the data would need to at least have two dimensions.
+This is because one dimension represents the evolution of the function over time, while the other dimensions define the spatial domain where the function's values are computed at each time step.
+This condition is true for both the Burgers' equation dataset and the WeatherBench 2 collection of ERA5 datasets.
+First, the Burgers' equation dataset, while is also able to be used in the first way as a mapping between the forcing term and the solution, one of the traditional ways of solving it is using the method of lines in conjunction with another method such as the finite differences method or the spectral method.
+In both of these, the Burgers' equation is formulated as an initial value problem, using the finite differences to computing the time derivative.
+% TODO: add figures and citation for this, or if this is avaliable in a different place in the thesis a refference to that.
+The method of lines approach in one of its forms is equal to \lccref{eq:time_step_function} \autocite{schiesserNumericalMethodLines2012,sadikuSimpleIntroductionMethod2000}.
+As such the Burgers' equation dataset can also be used in this way.
+In this case, algebraic manipulation of \lccref{eq:forced_viscous_burgers} results in the time derivative of the solution as in \lccref{eq:forced_viscous_burgers_time_derivative}.
+\begin{align}
+  \pdv{u}{t} = f - u\pdv{u}{x} + \nu\pdv[2]{u}{x} \label{eq:forced_viscous_burgers_time_derivative}
+\end{align}
+As can be seen, the time derivative is expressed in terms of the solution function, the forcing term and any other partial derivatives.
+Because of this, it means we can train the model to learn the relationship between the solution function combined with the forcing term and the time derivative.
+Putting this together with \lccref{eq:time_step_function}, it is possible to predict the solution function in a future time based on the current solution function and forcing term.
+The input functions in this case are both the value of the solution function and the forcing term at the current time step.
+The output function is the time derivative which is computed by rearranging \lccref{eq:time_step_function} resulting in \lccref{eq:time_derivative_time_step_function}.
+\begin{equation}
+  \dv{f}{t} = \frac{f^{t+1} - f^{t}}{\delta t} \label{eq:time_derivative_time_step_function}
+\end{equation}
+Perhaps in a more obvious manner, the same is also applied to the WeatherBench 2 collection of ERA5 datasets.
+The 2-meter temperature is a series of snapshots in time of the distribution of temperature all over the world at 2 meters above the surface.
+The input function in this case is the temperature distribution at the current time step.
+The output function is the time derivative of the temperature distribution computed using \lccref{eq:time_derivative_time_step_function}.
+
+The input and output functions are then transformed into basis coefficients using the Fourier transform. % TODO: add reference to fourier transform in chapter 2
+Once the coefficients are computed, the input and output sample pairs are split into train, test, and validation subsets.
+For the first type of input and output function pair, since the samples are independent of each other, a random sampling of the dataset without replacement is done to select the samples for each subset.
+For the second type of input and output function pairs, if there are multiple samples of functions as in the Burgers' equation dataset, the same process with random sampling is followed.
+On the other hand, if only one function sample is available, such as the WeatherBench 2 dataset, an issue that arises is the fact that the samples are dependent on one another.
+This is because a previous time step influences the next time step.
+This is a problem for generalizing the learned model, since random sampling would lead to the model learning information in the future of the testing subset \autocite{kapoorLeakageReproducibilityCrisis2023,kaufmanLeakageDataMining2012}.
+As such, the portioning of the dataset is done by dividing the sample into different sections of the function in time.
+
+Finally, the data is scaled.
+This is done because of how support vector machines require scaling for inputs in order to perform well with certain hyperparameters such as the RBF kernel \autocite{ben-hurUsersGuideSupport2010}.
+For our case we use standard scaling based on the inputs of the training subset.
+This approach transforms the dataset by manipulating the distribution characteristics of the dataset \autocite{ahsanEffectDataScaling2021}.
+Specifically, the standard deviation \(\sigma \) and mean \(x_0\) of the dataset values \(x\) are processed such that the resulting values have a mean of 0 and standard deviation of 1.
+The function shown in \lccref{eq:standard_scaler} represents how each sample is processed with respect to the standard deviation \(\sigma \) and mean \(x_0\) of each feature.
+\begin{equation}
+  z(x;\sigma,x_0)=\frac{x-x_0}{\sigma} \label{eq:standard_scaler}
+\end{equation}
+The scaling is important for the RBF kernel specifically due to the fact that the kernel utilize a scale parameter.
+This parameter affects how scale of values influence the kernel.
+Another and perhaps more general benefit of scaling is the uniformity it enforces across features.
+This is useful because all feature weigh the outcome equally.
+In our use case, this equality is a reflection of what the data actually represents.
+Each feature which is a discretized value or its coefficient representation has equal value to any other feature.
+No point or coefficient is any more or less value compared to another point or coefficient.
+
+The scaling is applied to input functions only because scaling of the outputs does not affect the performance of the model \autocite{ben-hurUsersGuideSupport2010}.
+To also prevent information leakage across training and testing sets, the mean and standard deviation of each feature is computed using the training subset only.
+Once the parameter values are obtained, all input function samples in the dataset are transformed into their scaled versions.
+This means that the distribution for the testing and validation sets may be outside the target standard deviation and mean.
+% TODO: add graphs and tables of the resulting preprocessed data
 
 \subsection{Model Training}
+\noindent Once the data has been preprocessed, the model is trained using pairs of training features and labels.
+The training phase is separated into four processes.
+First, the preprocessed input and output function representation need to be real numbers.
+This is because the LSSVR model was made to work with real numbers.
+Any complex values such as Fourier coefficients are represented as flattened pairs of the real and imaginary components of complex values.
+% TODO: add figure of flattened complex values
+
+The training can proceed to solve \lccref{eq:lssvr_solution}.
+As the original LSSVR equation was made for regression of a single value of \(\vb{y} \), we constructed an extended the original equation in order to train multiple regression models to predict each coefficient in an output function sample.
+The assumption of this extension is that the inputs and model hyperparameters such as kernels and the regularization constant \(C \) are the same across individual regressors.
+Therefore, it follows that the solution vector and target vector can both be transformed into their matrix form with each column representing the individual regressor which results in \lccref{eq:lssvr_solution_vectorized}.
+This vectorized version is equal to \(m \) separate instances of \lccref{eq:lssvr_solution}.
+In essence, instead of a vector of scalar sample output values and a vector of model parameters, the extended equation consists of a matrix of rows of vector output values and a matrix of model parameters with each column representing the separate model for each output and row representing the Lagrange multipliers for each sample.
+The procedure to solve \lccref{eq:lssvr_solution_vectorized} adjusts \lccref{alg:lssvr_training} for the extra dimension spanning the multiple outputs of size \(m\).
+\begin{equation} \label{eq:lssvr_solution_vectorized}
+  \begin{bmatrix}
+    0          & \vb{1}_{n}^{\intercal} \\
+    \vb{1}_{n} & \Omega + \frac{I}{C}
+  \end{bmatrix}
+  \begin{bmatrix}
+    b_0           & \cdots & b_m \\
+    \vb{\alpha}_0 & \cdots & \vb{\alpha}_m\\
+  \end{bmatrix}
+  =
+  \begin{bmatrix}
+    0        & \cdots & 0 \\
+    \vb{y}_0 & \cdots & \vb{y}_m \\
+  \end{bmatrix}
+\end{equation}
+
+Second, as the training process of an LSSVR described in requires constructing the first matrix on the left-hand side and the matrix on the right-hand side, each component of the matrices themselves will also need to be constructed.
+The kernel matrix \(\Omega \) is first constructed by computing the kernel values between each sample input with every other sample input.
+If the training set has \(n \) samples, then the resulting kernel matrix would be of size \(n \) by \(n \).
+% Assemble lssvr optimality equation matrices
+Third, using the inputs \(\vb{X}\), outputs \(\vb{y}\), predetermined regularization constant \(C \), and the obtained kernel matrix \(\Omega \), \lccref{eq:lssvr_solution_vectorized} is assembled.
+Finally, the matrix of learned parameters \(\vb{\alpha}\) and \(\vb{b}\), which are the Lagrange multipliers and bias respectively, are solved for using a linear equation solver such as a matrix Moore-Penrose inverse or linear least squares solver.
+
+% TODO: decide if hyperparameter selection is needed and explain why or why not.
+Maybe hyperparameter selection is done in a phase after the model evaluation with a decision between repeating model training with different hyperparameters or keeping the trained model.
+Next, the selection of hyperparameters is done to optimize the model further.
+As previously mentioned, the hyperparameters are the regularization constant \(C \) and kernel functions including the kernel function parameters.
 
 \subsection{Model Evaluation}
+\noindent The fourth phase of the computational model is the evaluation of the learned model.
+This phase starts with formatting the inputs.
+If the inputs aren't scaled yet, then it is scaled using the scaler fitted on the training set.
+This is the case for new data such as new measurements or an analytical solution of the learned PDE\@.
+Once the inputs that is to be evaluated is scaled in the same way as the training inputs, the model can predict the corresponding outputs.
+
+The procedure to compute the predicted outputs follows \lccref{alg:lssvr_prediction}.
+This leads to the second process which is computing the kernel matrix between the training input features \(\vb{X}\) and the evaluation input features \(\vb{U}\).
+The matrix is constructed as the kernel value between each evaluation sample feature and every training sample feature.
+For \(p \) evaluation samples and \(n \) training samples, this results in a kernel matrix \(\Omega \) with a shape of \(p \) rows and \(n \) columns.
+
+In the third process, the constructed kernel matrix is then multiplied with the matrix of learned Lagrange multipliers \(\vb{\alpha}\).
+The multiplication is the matrix multiplication process.
+Then, the bias vector is added to each row to produce the final predicted outputs \(\vb{v}\).
+This process is represented by \lccref{eq:lssvr_prediction_vectorized}.
+\begin{equation}
+  \vb{v} = \Omega\vb{\alpha}+\vb{1}\vb{b} \label{eq:lssvr_prediction_vectorized}
+\end{equation}
+
+The fourth process is concerned with the fact that the predicted output \(\vb{v}\) is a matrix of real numbers.
+The LSSVR output needs to be formatted before it can be used in the proposed model.
+This is done by converting the outputs into the same format as the training labels.
+As we use the Fourier basis, the model output is converted back into a matrix of complex numbers using the inverse of the first process during training.
+Finally, these predicted Fourier basis coefficients can be used to evaluate the predicted functions themselves.
 
 \section{Implementation of Computational Model}
-\noindent
+\noindent This section discusses the implementation of modeling and approximation of PDEs using LSSVR\@.
+Using the computational model design in \lccref{sec:computational_model_design}, the computational model is implemented as a library using the Python programming language.
+The development process itself is based on the iterative development model as mentioned in \lccref{sec:development method}.
+In this section, the output iterative processes are consolidated and explained together.
+
+\subsection{Analysis}
+\noindent The aim of any program that is developed in this study is to model the relationship between functions defined by a partial differential equation or other operators and governing equations.
+Since the potential subject of modeling can be wide-ranging, the software product that will be developed is a library.
+This is done so that the tools and proposed model that is developed will be able to be used with a variety of PDEs.
+With this in mind, the software must also be performant and compatible with the larger machine learning and scientific computing community.
+
+To demonstrate the use and capability of the software, three case studies are chosen to represent the variety of PDEs.
+The first case study is the antiderivative equation.
+This simple case is chosen as a proof of concept to show that the proposed model works in the most simple case.
+The second case study, which is the Burgers' equation, adds a level of complexity because of the nonlinearity involved with the solution function.
+The third case study, which is the ERA5 weather dataset, was chosen to show how the model performs on data with real world observations incorporated into it.
+This dataset also presents a challenge because of the uncertainties involved with weather simulation \autocite{herreraReviewCurrentFuture2017}.
+These datasets are discussed in \lccrefs{sec:data_generation,sec:data_retrieval}.
+
+In addition, the software product is developed within certain limitations. The limitations are:
+\begin{enumerate}
+  \item The operating and implementation language of the library is Python.
+  \item The library is to be used in user code
+  \item The library depends on other libraries including the following core dependencies Pytorch, Numpy, Xarray, Zarr, Pandas, and tqdm.
+\end{enumerate}
+
+\subsection{Design}
+\noindent In this subsection, the architectural design of the software product is explained.
+The architecture consists of modules with similar concerns.
+This was chosen because of the intuition built by the use of other libraries with a similar architecture.
+The broad aim of modeling PDEs with LSSVR and basis functions coefficients can be separated into smaller concerns of data, model, basis functions, and utilities.
+
+\subsection{Implementation}
+
+\subsection{Testing}
 

### 2024-12-18 skripsi/chapter1.tex
modify ch1 aims, add ch4 implementation & scenarios, start ch4 experimental results

@@
     \item What is the formulation a computational model for operator regression and therefore solving PDEs in the spectral domain using support vector machines?
-    \item How does the number of basis functions and model parameters impact the model performance?
+    \item Can the model learn the relationships represented by PDEs? And how does it perform on different problems?
     \item How can one interpret the learned model?
-    \item Can the model learn to forecast the weather effectively? % TODO: how to integrate physics into the LSSVM formulation?
 \end{enumerate}
@@
     \item The design and implementation of a computational model that maps coefficients in the spectral domain using Least Squares Support Vector Regression (LSSVR).
-    \item Hyperparameter optimization of the model.
+    \item Proof of the model's learning ability using three different problems.
     \item Interpretation the model results and why some predictions turn out the way they do.
-    \item Comparison of SpectralSVR with SNO, DeepONet, FNO, and FDM on 4 problems
 \end{enumerate}
@@
     \item A novel use LSSVR which has a convex objective to learn solution operators of partial differential equations and operators in general.
-    \item Comparison of non-uniform Fourier transform for arbitrary spatial sampling with interpolated grid point values.
-    \item Interpretation of trained model.
+    \item Interpretation of machine learning model trained on operator data.
 \end{enumerate}
@@
     \item Functions the model works with are only continuous functions.
-    \item The basis functions are limited to Fourier basis. % TODO: change this if more basis functions are added
+    \item The basis functions are limited to Fourier basis.
     \item Modeled fields are compact or dense meaning not sparse. Sparse observations or other data are assimilated using other methods.

### 2024-12-18 skripsi/chapter2.tex
modify ch1 aims, add ch4 implementation & scenarios, start ch4 experimental results

@@
 
-\section{Fourier Transform and Series}
+\section{Fourier Transform and Series}\label{sec:fourier_discussion}
 \noindent
@@
   c = a + bi \label{eq:complex_number} \\
+\end{align}
+\autocite{DiscreteFourierTransform}
+\begin{align}
+  c_k=\sum_{n=0}^{N-1} f_n e^{-i2\pi kn/N} \label{eq:discrete_fourier_transform}\\
+  f_n=\sum_{k=0}^{N-1} c_k e^{i2\pi kn/N} \label{eq:inverse_discrete_fourier_transform}
 \end{align}
@@
 
-\section{Sub Bab B}
-\noindent Suatu penelitian tidak dapat lepas dari capaian pengetahuan dan pemahaman yang sudah dipublikasikan.
+% \section{Sub Bab B}
+% \noindent Suatu penelitian tidak dapat lepas dari capaian pengetahuan dan pemahaman yang sudah dipublikasikan.
 Deskripsi tentang capaian ini menjadi penting karena selain menunjukkan tingkat pemahaman mahasiswa, juga mengetahui tempat pekerjaan penelitian TA dalam konstelasi capaian tersebut.
@@
 
-\section{Membuat Persamaan}
-\noindent Secara prinsip, suatu persamaan menyatu dalam kalimat.
+% \section{Membuat Persamaan}
+% \noindent Secara prinsip, suatu persamaan menyatu dalam kalimat.
 Letak persamaan dapat berada di awal, tengah, atau akhir kalimat.
@@
 
-Setiap notasi harus unik atau tunggal, sehingga arti setiap notasi adalah unik atau tunggal juga.
+% Setiap notasi harus unik atau tunggal, sehingga arti setiap notasi adalah unik atau tunggal juga.
 Arti satu notasi harus dituliskan segera ketika notasi tersebut muncul, dan tidak diulang lagi setelahnya.
 
-\subsection{Contoh Persamaan Sederhana}
-Persamaan (\ref{II.1}) mendeskripsikan dinamika fungsi gelombang $\psi(\vec{r},t)$ di bawah pengaruh potensial $V(\vec{r})$ dan dituliskan sebagai berikut:
-\begin{equation}\label{II.1}
-  i\hslash\frac{\partial \psi}{\partial t} = -\frac{\hslash^2}{2 m}\Vec{\nabla}^2 \psi + V(\vec{r})\psi,
-\end{equation}
-dengan $m$ adalah massa partikel dan $\hslash$ merupakan konstanta Planck tereduksi.
+% \subsection{Contoh Persamaan Sederhana}
+% Persamaan (\ref{II.1}) mendeskripsikan dinamika fungsi gelombang $\psi(\vec{r},t)$ di bawah pengaruh potensial $V(\vec{r})$ dan dituliskan sebagai berikut:
+% \begin{equation}\label{II.1}
+%   i\hslash\frac{\partial \psi}{\partial t} = -\frac{\hslash^2}{2 m}\Vec{\nabla}^2 \psi + V(\vec{r})\psi,
+% \end{equation}
+% dengan $m$ adalah massa partikel dan $\hslash$ merupakan konstanta Planck tereduksi.
 
-Di akhir persamaan (\ref{II.1}) diberi koma karena berada ditengah kalimat. Untuk merujuk ke persamaan yang telah ditulis, gunakan perintah \verb|\ref{}|.
+% Di akhir persamaan (\ref{II.1}) diberi koma karena berada ditengah kalimat. Untuk merujuk ke persamaan yang telah ditulis, gunakan perintah \verb|\ref{}|.
 
-Untuk menuliskan beberapa set persamaan yang masih terhubung, gunakan \verb|\subequations{}|. Misal kita punya persamaan diferensial terkopel, kita bisa tuliskan
-\begin{subequations}
-  \begin{align}
-    \frac{dy}{dt} & = -x , \\
-    \frac{dx}{dt} & = -y .
-  \end{align}
-\end{subequations}
-Kalau perlu matriks, kita bisa tulis seperti berikut.
-\begin{equation}
-  \sigma_x =
-  \begin{pmatrix}
-    0 & 1 \\
-    1 & 0
-  \end{pmatrix},\quad
-  \sigma_y =
-  \begin{pmatrix}
-    0 & -i \\
-    i & 0
-  \end{pmatrix}, \quad
-  \sigma_z =
-  \begin{pmatrix}
-    1 & 0  \\
-    0 & -1
-  \end{pmatrix}
-\end{equation}
+% Untuk menuliskan beberapa set persamaan yang masih terhubung, gunakan \verb|\subequations{}|. Misal kita punya persamaan diferensial terkopel, kita bisa tuliskan
+% \begin{subequations}
+%   \begin{align}
+%     \frac{dy}{dt} & = -x , \\
+%     \frac{dx}{dt} & = -y .
+%   \end{align}
+% \end{subequations}
+% Kalau perlu matriks, kita bisa tulis seperti berikut.
+% \begin{equation}
+%   \sigma_x =
+%   \begin{pmatrix}
+%     0 & 1 \\
+%     1 & 0
+%   \end{pmatrix},\quad
+%   \sigma_y =
+%   \begin{pmatrix}
+%     0 & -i \\
+%     i & 0
+%   \end{pmatrix}, \quad
+%   \sigma_z =
+%   \begin{pmatrix}
+%     1 & 0  \\
+%     0 & -1
+%   \end{pmatrix}
+% \end{equation}
 
-\section{Referensi dan Citation}
+% \section{Referensi dan Citation}
 % \noindent Sitasi dapat dimasukkan ke dalam Tugas Akhir seperti ini \cite{Fujita1996}.

### 2024-12-18 skripsi/chapter4.tex
modify ch1 aims, add ch4 implementation & scenarios, start ch4 experimental results

@@
 Each phase is composed of processes that together works toward the output of the larger process.
+At the end, a final process of analysis and interpretation is carried out.
 
@@
 
-\subsection{Design}
+\subsection{Design} \label{sec:implementation_design}
 \noindent In this subsection, the architectural design of the software product is explained.
@@
 This was chosen because of the intuition built by the use of other libraries with a similar architecture.
-The broad aim of modeling PDEs with LSSVR and basis functions coefficients can be separated into smaller concerns of data, model, basis functions, and utilities.
+The broad aim of modeling PDEs with LSSVR and basis functions coefficients can be separated into smaller concerns of data, model, and basis functions.
+Each of these concerns are addressed by a corresponding module.
+The explanation of each module are as follows:
+\begin{enumerate}
+  \item Utilities
+
+    \noindent This module provides basic tools that are used across the entire library.
+The utilities this module needs to provide include scaling, conversion between real and complex representations of matrices, resizing coefficient tensors, and adaptors for or the traditional ordinary differential equation solvers.
+Scaling functionality is used for inputs into the support vector machines.
+And as previously mentioned, since LSSVR only works with real numbers, the tools for converting between complex and their real number representations is also necessary.
+Another useful tool for working with basis coefficients is a way to resize the coefficients in terms of how many basis functions is desired.
+An example of the usage is downsizing Fourier coefficients from 12 to 8 modes.
+The last utility mentioned here provides the ability to solve ordinary differential equations.
+This utility is useful for generating data for certain types of PDEs such as the Burgers' equation.
+
+  \item Basis Functions
+
+    \noindent As the proposed model will learn the relationships defined by PDEs within the spectral domain, a large proportion of the computation will also concern the use of the basis functions themselves.
+The module will define the functionality and data structure that is expected to be used when working with basis functions in this library.
+First and foremost, the central function of this module is to store and facilitate the connection between the coefficients in the spectral domain and their values in the physical domain.
+This is dependent on the basis functions used.
+For the Fourier basis that we use in this study, this means that the transformations are the discrete Fourier transform and the discrete inverse Fourier transform.
+Other than this core functionality, information on the characteristics of the coefficients such as the number of modes, in other words basis functions, should also be provided by this module.
+In addition, other functionality included in this module are visualization of coefficients in physical space, generation of random functions, time dependent \& complex/real coefficients, noise perturbation of functions, and differential operators.
+
+  \item Model
+
+    \noindent The proposed SpectralSVR model is implemented in this module.
+As the proposed model essentially wraps a support vector regression model in such a way that it can process coefficients, this module will house the SpectralSVR wrapper itself and the LSSVR variant of support vector regression that is used in this study.
+The SpectralSVR wrapper must provide three core pieces of functionality.
+First, it must translate complex input and output samples into their real representations.
+This applies to both training and evaluation.
+Second, in addition to predicting the coefficients during evaluation, the wrapper should also be able to predict the function values themselves for any given set of point coordinates.
+This is important for quick evaluations of a predicted function at an arbitrary point.
+The third functionality is inverse input function search for a given output.
+This is useful for inverse problems where the parameters are unknown, but the solution is partially known.
+Aside from the core functionality, a complementary functionality is testing for the learned model.
+
+    The model module also implements the LSSVR model.
+This implementation provides two main functionalities.
+The first is training the LSSVR model with some given model hyperparameters such as the regularization constant and kernel.
+The second functionality is the evaluation of the learned model.
+Both functionalities allow for multiple output regression.
+This is required to learn the mappings for many coefficients at once.
+Other functionality provided by the implementation include interpretability functions and model serialization for saving and loading the learned model to disk.
+
+  \item Problems
+
+    \noindent This module provides the functionality concerned with generating data.
+Two out of the three datasets in this study are generated with this module.
+In general this module provides two pieces of functionality.
+The first is generation of the data itself.
+This functionality generates at least two sets of functions that are related to each other by the chosen PDE\@.
+The generation is based on at least two parameters which are the number of samples to generate and the number of modes or basis functions to generate the coefficients for.
+The second functionality provided by this module is the residual based on the chosen PDE\@.
+This is useful to verify if any set of functions comply with the PDE\@.
+For example, the residual may be used to verify the generated data.
+Another use is to grade the predictions by the learned model.
+
+\end{enumerate}
+
+The design presented here is the product of multiple iterations that started with building the core model and then the basis functions and finally the data.
+Throughout the iterations, the utilities were also added to alleviate the need for general tools.
 
@@
 
+\noindent The design in \lccref{sec:implementation_design} is implemented within the same iterative loop.
+As such, the feedback from tests is immediate, and any fixes can be implemented quickly.
+The implementation is done using the Python language and a number of Python libraries.
+To facilitate the management of dependencies, the implementation makes use of the package management tool Poetry \autocite{eustacePoetryPythonPackaging2024}.
+In addition, the Python version is managed using the tool pyenv.
+The implementation process starts with installation of the required dependencies.
+The dependencies are specified in the \verb|pyproject.toml| as shown in \lccref{fig:poetry_add_deps}.
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Toml]
+...
+[tool.poetry.dependencies]
+python = "^3.10.6"
+numpy = "^1.24.0"
+tqdm = "^4.65.0"
+jaxtyping = "^0.2.20"
+pandas = "^2.2.2"
+torchmetrics = "^1.4.2"
+scikit-learn = "^1.5.0"
+matplotlib = "^3.9.0"
+torch = {version = "^2.4.1+cu124", source = "pytorch-gpu"}
+torchvision = {version = "^0.19.1+cu124", source = "pytorch-gpu"}
+torchaudio = {version = "^2.4.1+cu124", source = "pytorch-gpu"}
+ray = {extras = ["tune"], version = "^2.37.0"}
+hyperopt = "^0.2.7"
+ipywidgets = "^8.1.5"
+torchdiffeq = "^0.2.4"
+xarray = "^2024.10.0"
+zarr = "^2.18.3"
+gcsfs = "^2024.10.0"
+
+[[tool.poetry.source]]
+name = "pytorch-gpu"
+url = "https://download.pytorch.org/whl/cu124"
+priority = "explicit"
+
+[build-system]
+requires = ["poetry-core"]
+build-backend = "poetry.core.masonry.api"
+  \end{lstlisting}
+  \caption{Contents of pyproject.toml configuration file that define the dependencies using Poetry}\label{fig:poetry_add_deps}
+\end{figure}
+
+After ensuring that the correct version of python is being used with pyenv, the dependencies specified in the \verb|pyproject.toml| file can be installed using the shell command \verb|poetry install|.
+At the end of each iteration, the dependencies are subject to change depending on whether any new ones are needed or old dependencies can be removed.
+
+In the following, we will discuss the implementation of each module and how the phases of computational model relates to each implemented functionality.
+The base data structure that is used in the implementation is the Pytorch Tensor \autocite{Ansel_PyTorch_2_Faster_2024}.
+Tensors are a generalization of scalars and array-like structures such as vectors and matrices.
+This is essential since many computations that is done in the proposed model are based on matrices and higher dimensional arrays.
+Pytorch Tensors allow the elements to be of different data types such as floating point numbers of different precision or even complex numbers.
+In addition to basic operations for working with the Tensors such as matrix multiplications, Pytorch also provides many algorithms for use when working with Tensors such as linear equation solvers or the Fast Fourier Transform.
+Another reason for choosing to use Pytorch is the ability to parallelize computation using specialized processors such as GPUs.
+Lastly, Pytorch is widely used in the machine learning community which reflects on its reliability, wealth of community knowledge and support, and active development.
+
+\subsubsection{Utilities}
+
+\noindent The utilities module provide common tools that are used when working with the developed software.
+First, because the basis function used in this study is the Fourier basis, a large proportion of concern is the storage of Fourier basis coefficients.
+The Fourier series representation that is used in this study is the complex representation as show in \lccref{eq:fourier_series}.
+However, as previously mentioned, least squares support vector machines is constructed to work with real numbers.
+In order for LSSVR to learn the relationship between complex numbers, a representation of complex numbers in terms of real numbers is necessary.
+Since sample features and labels for LSSVR need to be flattened into one dimension which result in a matrix with rows of samples, the representation of complex numbers using real numbers can be done after features and labels have been flattened.
+An example of such a matrix of two samples with four features each can be seen in \lccref{eq:complex_matrix}.
+To represent the complex number features as real numbers, once can simply split a single complex number into two real numbers.
+When this is done to the entire matrix of complex numbers, the result is \lccref{eq:complex_matrix_real_rep}.
+\begin{align}
+  \begin{bmatrix}
+    -1.03+0i & -0.52+0.39i & -0.54+0i & -0.52-0.39i\\
+    -0.85+0i & -0.39+0.19i &  0.87+0i & -0.39-0.19i
+  \end{bmatrix}\label{eq:complex_matrix}\\
+  \begin{bmatrix}
+    -1.03 & 0 & -0.52 & 0.39 & -0.54 & 0 & -0.52 & -0.39\\
+    -0.85 & 0 & -0.39 & 0.19 &  0.87 & 0 & -0.39 & -0.19
+  \end{bmatrix}\label{eq:complex_matrix_real_rep}
+\end{align}
+There are several ways to do this in Pytorch, such as extracting the real and imaginary element components into separate matrices and then interleaving the columns to create the real representation.
+However, a more performant version can be made by using built-in functions of the library that directly allows views of complex valued tensors as real tensors and vice versa.
+The \verb|view_as_real| and \verb|view_as_complex| functions allow the conversion between real and complex representations by representing complex valued tensors by adding a dimension of size two for each component of complex numbers.
+The resulting implementation can be seen in \lccref{fig:complex_matrix_conversion_implementation}.
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+def to_real_coeff(x: torch.Tensor) -> torch.Tensor:
+    return torch.view_as_real(x).flatten(-2)
+
+def to_complex_coeff(x: torch.Tensor) -> torch.Tensor:
+  return torch.view_as_complex(
+    x.reshape((*x.shape[:-1], -1, 2))
+  )
+  \end{lstlisting}
+  \caption{Utility function to convert between complex matrices and the real representations}\label{fig:complex_matrix_conversion_implementation}
+\end{figure}
+
+Another important utility used on inputs for the proposed SpectralSVR is a scaler.
+This utility has been implemented in a variety of ways and using different tools.
+However, as the standard scaling is not provided by Pytorch, we have also implemented our own version.
+The scaler accepts Pytorch tensors or tuples of tensors of real or complex elements.
+First, the scaler is implemented as a class that is instantiated.
+The scaler is then fitted onto the reference data to obtain the standard deviation and mean of each feature.
+This information is stored as properties of the class.
+Any complex tensors are converted into their real representations using the functions in \lccref{fig:complex_matrix_conversion_implementation}.
+Once the scaler instance is fitted, any set of tensors with the same number of features (columns) and element type (complex or real) can be roughly transformed into a standard deviation of one and mean of zero for every feature.
+This is done by subtracting the fitted mean of each feature from the elements in the column and then dividing with the feature's standard deviation.
+The implementation also provides a method to retrieve a scaler fitted on a subset of the original tuple of tensors.
+Serialization for saving to and loading from disk is also implemented.
+This is done simply by using the Pytorch save and load functions on the scaler instance itself.
+For some use cases, an inverse scaling operation to the original standard deviation and mean is also essential.
+The implementation is simply the reverse of the transformation process where the elements are multiplied by the standard deviation and the mean is the added.
+
+Another group of utility in the module is concerned with managing the number of modes a tensor of coefficients has.
+First, a function called \verb|resize_modes| accepts a tensor of coefficients and the target number of modes in each dimension.
+The first dimension is always assumed to represent the different samples.
+Because of this the target modes will only affect the dimensions after the first.
+The wave numbers are also assumed to be symmetric about zero such that the highest absolute values of the wave number is in the middle of each dimension.
+The wave number decreases symmetrically as you move towards the edges of the dimension and reaching the lowest absolute wave number at the edges.
+This is done to ensure compatibility with the way existing libraries such as Pytorch works with tensors of Fourier coefficients.
+Because of this, shrinking a tensor of coefficients along a dimension means removing the center of the tensor along that dimension.
+And expanding to a target number of modes that is larger means that the tensor is padded with zeros in the center along the desired dimension.
+In addition, the remaining coefficients may be rescaled in order to balance the effect of adding or removing coefficients.
+The implementation is presented in \lccrefs{fig:coefficient_shrink_impl,fig:coefficient_expand_impl}.
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+for dim, (target_mode, current_mode) in enumerate(
+    zip(target_modes, current_modes), 1
+):
+    device = x.device
+    start_range = torch.tensor(
+        range((target_mode - 1) // 2 + 1), dtype=torch.int
+    ).to(device=device)
+    end_range = torch.tensor(
+        range(current_mode - target_mode // 2,
+          current_mode
+        ),
+        dtype=torch.int,
+    ).to(device=device)
+
+    x_resized = torch.concat(
+        (
+            x_resized.index_select(dim, start_range),
+            x_resized.index_select(dim, end_range),
+        ),
+        dim,
+    )
+  \end{lstlisting}
+  \caption{Example of shrinking a tensor of samples' coefficients to a target number of modes}\label{fig:coefficient_shrink_impl}
+\end{figure}
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+for dim, (target_mode, current_mode) in enumerate(
+    zip(target_modes, current_modes), 1
+):
+    device = x.device
+    start_range = torch.tensor(
+        range((current_mode - 1) // 2 + 1), dtype=torch.int
+    ).to(device=device)
+    # make sure that end range is empty if
+    # the coefficient is only size 1
+    end_range = torch.tensor(
+        range(current_mode // 2, current_mode)
+        if current_mode > 1
+        else range(0),
+        dtype=torch.int,
+    ).to(device=device)
+    padding_size = target_mode - current_mode
+    modes = list(x_resized.shape)
+    modes[dim] = padding_size
+    padding = torch.zeros(modes).to(x_resized)
+
+    x_resized = torch.concat(
+        (
+            x_resized.index_select(dim, start_range),
+            padding,
+            x_resized.index_select(dim, end_range),
+        ),
+        dim,
+    )
+  \end{lstlisting}
+  \caption{Example of expanding a tensor of samples' coefficients to a target number of modes}\label{fig:coefficient_expand_impl}
+\end{figure}
+Next, the second way to manage the size of a tensor along a dimension is to interpolate the current values.
+The implementation uses simple linear interpolation.
+This is especially useful for situations such as coefficients that are themselves functions of time.
+This is a common application such as when solving the initial condition problem of a function in space and time.
+One might represent the function as a Fourier series with basis as functions of space and coefficients as functions of time.
+In this case, the coefficients for time values that are not available can be interpolated.
+The implementation of this is shown in \lccref{fig:coefficient_interpolation_impl}.
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+    index_floor = index_float.floor().to(torch.int)
+    index_ceil = index_float.ceil().to(torch.int)
+    x_ceil = x.index_select(dim, index_ceil)
+    x_floor = x.index_select(dim, index_floor)
+    # interpolate coefficients
+    index_shape = [1 for _ in range(x_floor.ndim)]
+    index_shape[1] = -1
+    index_scaler = (
+        ((index_float - index_floor) / (
+          index_ceil - index_floor
+        ))
+        .reshape(index_shape)
+        .nan_to_num()
+    )
+    # ynt + scaler * (ynt1 - ynt)
+    # (1 - scaler) * ynt + scaler * ynt1
+    x_interp = torch.lerp(x_floor, x_ceil, index_scaler.to(x))
+  \end{lstlisting}
+  \caption{Example of interpolating for indices (floating point indices) between the available ones (intiger indices)}\label{fig:coefficient_interpolation_impl}
+\end{figure}
+
+Finally, this module also provides the types and reexports implementations of ordinary differential equation solvers from the torchdiffeq library \autocite{Chen_torchdiffeq_2021}.
+The implementation can be seen in \lccref{fig:solver_impl}.
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+RHSFuncType = Callable[[torch.Tensor, torch.Tensor],
+  torch.Tensor
+]
+SolverSignatureType = Callable[[
+        RHSFuncType, torch.Tensor, torch.Tensor,
+    ],
+    torch.Tensor
+]
+MixedRHSFuncType = Callable[[
+        torch.Tensor, torch.Tensor, torch.Tensor,
+    ],
+    torch.Tensor,
+]
+MixedSolverSignatureType = Callable[
+    [MixedRHSFuncType, torch.Tensor, torch.Tensor],
+    torch.Tensor,
+]
+
+def euler_solver(
+    rhs_func: RHSFuncType,
+    y0: torch.Tensor,
+    t: torch.Tensor,
+):
+    solution = torch.zeros((len(t), *y0.shape)).to(y0)
+
+    j = 1
+    solution[j - 1] = y0
+    for t0, t1 in zip(t[:-1], t[1:]):
+        dt = t1 - t0
+        y = solution[j - 1]
+        solution[j] = y + dt * rhs_func(t0, y)
+        assert (
+            solution.isnan().sum() == 0
+        ), f"solver encountered nan at timestep {j} (t={t0})"
+        j = j + 1
+    return solution
+
+implicit_adams_solver: SolverSignatureType = partial(
+    odeint, method="implicit_adams", options={"max_iters": 4}
+)  # type: ignore
+
+lsoda_solver: SolverSignatureType = partial(
+    odeint, method="scipy_solver", options={"solver": "LSODA"}
+)  # type: ignore
+  \end{lstlisting}
+  \caption{Implementation of ODE solvers and the types}\label{fig:solver_impl}
+\end{figure}
+
+\subsubsection{Basis Functions}
+
+\noindent This module implements two classes.
+The first is the base Basis class.
+The second is a subclass implementing the Fourier basis specifically.
+These classes provide the functionality needed to have an easier time when working with basis functions and their coefficients.
+First, the core function of these classes is to provide a way to transition between the spectral domain and the physical domain.
+This is implemented in the base class by storing the coefficients of sample functions as a class property.
+The coefficients are assumed to be at least of one function.
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+...
+    @staticmethod
+    def transform(
+        f: torch.Tensor,
+        res: TransformResType | None = None,
+        periodic: bool = True,
+        periods: PeriodsInputType = None,
+        allow_fft: bool = True,
+    ) -> torch.Tensor:
+        if not torch.is_complex(f):
+            f = f * (1 + 0j)
+        res = transformResType_to_tuple(res, tuple(f.shape[1:]))
+        periods = periodsInputType_to_tuple(periods, f.shape[1:])
+        # perform 1d transform over every dimension
+        F = f
+        for cdim in range(1, ndims):
+            F = FourierBasis._ndim_transform(
+                F,
+                dim=cdim,
+                func="forward",
+                res=res[cdim - 1],
+                periodic=periodic,
+                period=periods[cdim - 1],
+                allow_fft=allow_fft,
+            )
+
+        return F
+...
+  \end{lstlisting}
+  \caption{Implementation of forward Fourier transform}\label{fig:fourier_transform_impl}
+\end{figure}
+
+The transitions between the coefficients and functions values are implemented as a function to transform function values to coefficients and an inverse transform function to compute function values from coefficients.
+The base class enforces this by defining abstract methods which any subclass will need to implement.
+The FourierBasis subclass then implements the transform and inverse transform functions specific for transitioning between function values and Fourier basis coefficients.
+As before, the implementation assumes that the first dimension indexes the samples and the rest represent the coefficient wave numbers.
+This means that the implementation must allow for multidimensional functions.
+For the Fourier transform and inverse transform, the multidimensional version is relatively simple to implement.
+The multidimensional Fourier transform essentially performs the one dimensional Fourier transform along one dimension.
+And then, using the result to perform the one dimensional Fourier transform along the next dimension.
+This process is repeated until the last dimension.
+The implementation of the forward transform is presented in \lccref{fig:fourier_transform_impl}.
+The inverse transform simply changes the \verb|func| parameter to \enquote{inverse}.
+
+The Fourier transform along each dimension is done by flattening every other dimension into the sample dimension.
+This essentially means that the function values are \enquote{sliced} along the dimension currently being transformed, and that each \enquote{slice} is its own \enquote{sample}.
+Mathematically, this is simply due to the matrix multiplication of basis functions along one dimension with every other dimension.
+The implementation of this is shown in \lccref{fig:ndim_fourier_transform_impl}.
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+...
+    @staticmethod
+    def _ndim_transform(
+        f: torch.Tensor,
+        dim: int,
+        func: Literal["forward", "inverse"],
+        res: slice,
+        periodic: bool,
+        period: float,
+        allow_fft: bool,
+    ) -> torch.Tensor:
+        # flatten so that each extra dimension is
+        # treated as a separate "sample"
+        # move dimension to transform to the end
+        # so that it can stay intact after f is flatened
+        f_transposed = f.moveaxis(dim, -1)
+        # flatten so that the last dimension is intact
+        f_flatened = f_transposed.flatten(0, -2)
+
+        F_flattened = FourierBasis._raw_transform(
+            f_flatened,
+            func=func,
+            res=res,
+            periodic=periodic,
+            period=period,
+            allow_fft=allow_fft,
+        )
+        # unflatten so that the correct shape is returned
+        F_transposed = F_flattened.reshape(
+          (*f_transposed.shape[:-1], res.step)
+        )
+        F = F_transposed.moveaxis(-1, dim)
+
+        return F
+...
+  \end{lstlisting}
+  \caption{Implementation of n-dimensional Fourier transform for a specific dimension}\label{fig:ndim_fourier_transform_impl}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+...
+    @staticmethod
+    def _raw_transform(
+        f: torch.Tensor,
+        func: Literal["forward", "inverse"],
+        res: slice,
+        periodic: bool,
+        period: float,
+        allow_fft: bool,
+    ) -> torch.Tensor:
+        match func:
+            case "forward":
+                sign = -1
+            case "inverse":
+                sign = 1
+        mode = f.shape[1]
+        domain_starts_at_0 = res.start == 0
+        domain_end_equal_to_period = res.stop == period
+        can_use_fft = (
+            domain_starts_at_0
+            and domain_end_equal_to_period
+            and periodic
+            and allow_fft
+        )
+        if can_use_fft:
+            if func == "forward":
+                F = torch.fft.fft(
+                  f, dim=1, n=res.step, norm="backward"
+                )
+            elif func == "inverse":
+                F = torch.fft.ifft(
+                  f, dim=1, n=res.step, norm="forward"
+                )
+        else:
+            if periodic:
+                n = res.start + torch.arange(res.step).to(f)
+                n = n / res.step * period
+            else:
+                n = torch.linspace(
+                    res.start, res.stop, res.step
+                ).to(f)
+            e = FourierBasis.fn(
+                n.view(-1, 1),
+                mode,
+                periods=period,
+                constant=sign * 2j * torch.pi,
+            )
+
+            F = torch.mm(f, e.T)
+        return F
+...
+  \end{lstlisting}
+  \caption{Implementation of the one dimensional Fourier Transform}\label{fig:1d_fourier_transform_impl}
+\end{figure}
+
+The one dimensional Fourier transform itself is implemented as a raw transform function.
+This function accepts input of a matrix of values to transform, a parameter to indicate the type of transformation (inverse transform or forward transform), the evaluation boundary and number of grid points, whether the evaluation should assume the function is periodic, the size of the function domain, and if the Fast Fourier Transform is allowed to be used.
+The evaluation boundaries, actual function domain size, whether the function can be assumed to be periodic, and if FFTs is allowed to be used together determine the Discrete Fourier Transform algorithm that is used.
+The FFT algorithm is used if the folowing are all true: the evaluation starts at zero and ends with the same value as the period, the function can be assumed to be periodic, and FFT is allowed.
+Otherwise, the transform is computed naively using \lccrefs{eq:discrete_fourier_transform,eq:inverse_discrete_fourier_transform}.
+The naive approach allows for evaluating function values of coefficients at various grid sizes and evaluation boundaries.
+This is useful for being able to evaluate at resolutions other than that of the original discretized function or coefficients.
+One use for this is plotting the function at different parts or resolutions.
+The relationship with the physical domain means that the boundaries of the domain is important.
+This is because the function values that will be used may only be valid within certain boundaries.
+Because of this, the information of physical domain bounds must also be stored.
+This is done by storing the span of the function in each dimension.
+The implementation we have gone with doesn't store any other information than the span in each dimension.
+Because of this, the information would need to be stored outside the Basis class instance and any outputs or operations with the classes will need to take this into account.
+The implementation of the one dimensional Fourier transform is presented in \lccref{fig:1d_fourier_transform_impl}.
+
+The secondary set of functionality provided by the basis classes are mathematical operators on the functions the coefficients represent.
+There are four operators implemented, which are the addition, subtraction, derivative, and antiderivative operators.
+These four operations can be further categorized into arithmetic and calculus operations.
+The arithmetic operations, which are addition and subtraction, are implemented by following how the actual mathematical operations would be carried out on two functions which are Fourier series as shown in \lccref{eq:fourier_series_addition}.
+For subtraction, the plus sign is simply replaced with the minues sign.
+\begin{align}
+  \sum_{k} \hat{u}_k e^{2\pi ikx} + \sum_{k} \hat{f}_k e^{2\pi ikx} =
+  \sum_{k} \left(\hat{u}_k + \hat{f}_k\right) e^{2\pi ikx} \label{eq:fourier_series_addition}
+\end{align}
+The implementation leverages the operator overloading in Python classes.
+For addition, the overload should be done to the \verb|__add__| function.
+This function adds the current instance to another object which is the other basis instance for our use case.
+We also want the operation to return an independent instance without any references to the previous instances.
+To do this, all properties are coppied into a new instance.
+This is then used to perform the arithmetic operation.
+The implementation in \lccref{fig:basis_addition_impl} demonstrates the addition operation.
+For subtraction, a similar implementation is done using the \verb|__sub__| function and switching the plus sign with the minus sign.
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+...
+    def __add__(self, other: Self):
+        if isinstance(other, self.__class__):
+            if other.coeff is None:
+                return self.copy()
+            elif self.coeff is None:
+                return other.copy()
+            else:
+                result = self.resize_modes(other)
+                result.coeff = result.coeff + other.coeff
+                return result
+        else:
+            raise TypeError(
+                f"unsupported operand type(s) for +: '{
+                    self.__class__
+                }' and '{type(other)}'"
+            )
+...
+  \end{lstlisting}
+  \caption{Implementation of basis addition function}\label{fig:basis_addition_impl}
+\end{figure}
+
+The calculus operations for Fourier basis take advantage of the properties of the Fourier series.
+As discussed in \lccref{sec:fourier_discussion}, derivatives and integration become multiplication and division in the spectral space of Fourier series.
+Our implementation takes advantage of this as shown in \lccref{fig:basis_grad_impl}.
+Similar to how subtraction is just a modification of the addition operation, the integral or antiderivative operator is also implemented simply by changing the operation with the term multiplier from multiplication to division.
+% TODO: change the reference to specific equations for calculus in spectral domain
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+...
+    def grad(self, dim: int = 0, ord: int = 1) -> Self:
+        copy = self.copy()
+        if dim == 0 and self.time_dependent:
+            # time dependent use finite differences
+            dt = self.periods[0] / (self.time_size - 1)
+            coeff = copy.coeff
+            for o in range(ord):
+                coeff = torch.gradient(coeff, spacing=dt, dim=1)[0]
+            copy.coeff = coeff
+        else:
+            if self.time_dependent:
+                # disregard time dimension
+                dim = dim - 1
+            k = copy.wave_number(copy.modes[dim])
+            multiplier_dims = [1 for _ in range(copy.ndim)]
+            multiplier_dims[dim] = copy.modes[dim]
+            if self.time_dependent:
+                multiplier_dims = (1, *multiplier_dims)
+            multiplier = (
+                2
+                * torch.pi
+                * 1j
+                * k.reshape(multiplier_dims).to(copy.coeff)
+                / self.periods[dim]
+            )
+            multiplier = multiplier.pow(ord)
+            coeff = copy.coeff.mul(multiplier)
+            coeff[:, ..., 0] = torch.tensor(0 + 0j)
+            copy.coeff = coeff
+        return copy
+...
+  \end{lstlisting}
+  \caption{Implementation of basis grad function}\label{fig:basis_grad_impl}
+\end{figure}
+
+The last group of functionality implemented in the Basis and FourierBasis classes provides convenience and often used procedures when working with basis functions.
+First, random coefficient generation for the Fourier basis is implemented.
+This is done as discussed in step 3 of the data generation process discussed in \lccref{sec:data_generation}.
+The implemented function shown in \lccref{fig:generate_coeff_impl} is then wrapped in another function that creates a new FourierBasis instance with the generated coefficients.
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+...
+    @classmethod
+    def generate_coeff(
+        cls,
+        n: int,
+        modes: int | tuple[int, ...],
+        generator: torch.Generator | None = None,
+        random_func: Callable[..., torch.Tensor] = torch.randn,
+        complex_funcs: bool = False,
+        scale: bool = True,
+    ) -> torch.Tensor:
+        if isinstance(modes, int):
+            modes = (modes,)
+        n_modes = len(modes)
+        assert n_modes > 0, "modes should have at least one element"
+        random_func = partial(random_func, generator=generator)
+        if complex_funcs:
+            coeff = random_func((n, *modes), dtype=torch.complex64)
+        else:
+            coeff = random_func((n, *modes), dtype=torch.complex64)
+
+            vals = cls.inv_transform(coeff)
+            coeff = cls.transform(vals.real + 0j)
+        if scale:
+            scaler = torch.tensor(modes).sum() * 0.2
+            coeff = coeff.mul(scaler)
+        return coeff
+...
+  \end{lstlisting}
+  \caption{Implementation of Fourier Basis coefficient generation function}\label{fig:generate_coeff_impl}
+\end{figure}
+
+Other convenience functionality also provided include plotting, function value perturbation, and function value evaluation based on domain span information that has been stored in the class instance.
+The function value evaluation is especially useful for experimenting and for the plotting functionality itself.
+This is because, the span was given to the constructor and does not need to be composed again with the inverse transform function.
+
+\subsubsection{Model}
+
+\noindent The SpectralSVR model is implemented in this module.
+There are two components in this module.
+First, there is the implementation of least-squares support vector regression (LSSVR) using Pytorch.
+This implementation is a reimplementation and modification of an LSSVR implementation using scikit-learn by \textcite{florencioLssvr2020}.
+The modifications are mainly concerned with using Pytorch in place of scikit-learn.
+Other modifications are concerned with the performance side of things, which are computing the kernel matrix in batches to avoid memory spikes and the ability to compute on hardware accelerators supported by Pytorch such as GPUs.
+The LSSVR implementation starts with the constructor which accepts model hyperparameters which include the regularization parameter, kernel function and any kernel parameters, verbosity level, kernel matrix computation batch size, and device to perform computations on.
+The recieved parameters are then stored as properties of the class instance.
+For the kernel specifically, it will be initialized with the correct default parameters when the fitting function is called.
+This is because if the kernel of choice is the radial basis function, the default scaling parameter needs to be computed from the training features as the square root of the sum of feature variance values.
+
+The optimization function that fits the model to the training data solves \lccref{eq:lssvr_solution}.
+This function is shown in \lccref{fig:lssvr_fit_function_impl}.
+The first half of the function sets up the left and right hand side matrices.
+The left hand side matrix is constructed in part with the kernel matrix.
+The kernel function used is batched to reduce the peak memory footprint.
+These matrices are then used in the second half to compute the solution using the least squares solver function from Pytorch called lstq.
+Finally, the result is split into the biases and Lagrange multipliers which are then returned as a tuple.
+The optimizing function is wrapped in a more user-friendly function which allows the use of numpy arrays in addition to the Pytorch Tensor used in the optimizing function.
+The wrapper function is named fit.
+It conforms the inputs provided by the user into the expected types and matrix shapes of rows for samples and columns for input features or output targets.
+The processed inputs and outputs are also stored as support vectors for use during prediction.
+The fit function returns the class instance once training is done.
+This is for method chaining purposes for ease of use when using the fit function in a chain with other functions we will discuss next, such as the prediction function.
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+...
+    def _optimize_parameters(
+      self,
+      X: torch.Tensor,
+      y_values: torch.Tensor,
+    ):
+
+        A = torch.empty(
+          (X.shape[0] + 1,) * 2,
+          device=self.device,
+          dtype=self.dtype,
+        )
+        A[1:, 1:] = self._batched_K(X, X)
+        A[1:, 1:].diagonal().copy_(
+            A[1:, 1:].diagonal()
+            + torch.ones(
+                (A[1:, 1:].shape[0],),
+                device=self.device,
+                dtype=self.dtype,
+            ).to()
+            / self.C
+        )
+        A[0, 0] = 0
+        A[0, 1:] = 1
+        A[1:, 0] = 1
+        shape = np.array(y_values.shape)
+        shape[0] += 1
+        B = torch.empty(
+          list(shape), device=self.device, dtype=self.dtype
+        )
+        B[0] = 0
+        B[1:] = y_values
+
+        solution: torch.Tensor = torch.linalg.lstsq(
+            A.to(dtype=torch.float), B.to(dtype=torch.float)
+        ).solution.to(dtype=self.dtype)
+
+        b = solution[0, :]
+        alpha = solution[1:, :]
+
+        return (b, alpha)
+...
+  \end{lstlisting}
+  \caption{Implementation of Least-squares Support Vector Regression fitting function}\label{fig:lssvr_fit_function_impl}
+\end{figure}
+
+The learned multipliers and bias parameters are then used for predicting outputs from unseen sample features.
+\Cref{eq:lssvr_prediction_vectorized} shows the computation that needs to be done to compute the predicted output.
+The prediction process first constructs both matrices on the left-hand side of the equation.
+This is done by computing the kernel matrix between the prediction features and the training features, otherwise known as support vectors.
+The prediction function therefore is very straight forward with an input of unseen features and the learned parameters.
+The function output is simply the predicted outputs.
+The implementation of this function is shown in \lccref{fig:lssvr_predict_function_impl}.
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+...
+NumpyArrayorTensor = (
+    np.ndarray[typing.Any, np.dtype[np.float_]] |
+    torch.Tensor
+)
+...
+    def predict(
+        self,
+        X: NumpyArrayorTensor,
+    ) -> NumpyArrayorTensor:
+        """Predicts the labels of data X given a trained model.
+        - X: ndarray of shape (n_samples, n_attributes)
+        """
+        is_torch = isinstance(X, torch.Tensor)
+        if is_torch:
+            if X.ndim == 1:
+                X_reshaped_torch = X.reshape(-1, 1)
+            else:
+                X_reshaped_torch = X
+            X_= X_reshaped_torch.clone().to(
+                self.device, dtype=self.dtype
+            )
+        else:
+            if X.ndim == 1:
+                X_reshaped_np = X.reshape(-1, 1)
+            else:
+                X_reshaped_np = X
+            X_ = torch.from_numpy(X_reshaped_np).to(
+                self.device, dtype=self.dtype
+            )
+
+        KxX = self._batched_K(X_, self.sv_x)
+
+        y_pred = KxX @ self.alpha + self.b
+        predictions: NumpyArrayorTensor
+        if is_torch:
+            predictions = y_pred.to(X)
+        else:
+            predictions = y_pred.cpu().numpy()
+
+        if X.ndim == 1:
+            return predictions.reshape(-1)
+        else:
+            return predictions
+...
+  \end{lstlisting}
+  \caption{Implementation of Least-squares Support Vector Regression prediction function}\label{fig:lssvr_predict_function_impl}
+\end{figure}
+
+Aside from these core functions, interpretation of the model using the methods introduced by \textcite{ustunVisualisationInterpretationSupport2007} are also implemented in the LSSVR class.
+First, using the support vectors and the kernel matrix computed between each support vectors, the correlation image is computed.
+This image, which is a correlation matrix, is intended to visualize the importance of features within kernel functions.
+This is simply computed with matrix multiplication between the kernel matrix and the support vectors.
+The implementation is shown in \lccref{fig:lssvr_correlation_image_function_impl}.
+The batched kernel function is used in this case to mitigate the memory footprint.
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+...
+    def get_correlation_image(self):
+        return self._batched_K(
+            self.sv_x, self.sv_x
+        ).mm(self.sv_x)
+...
+  \end{lstlisting}
+  \caption{Implementation of Least-squares Support Vector Regression correlation image function}\label{fig:lssvr_correlation_image_function_impl}
+\end{figure}
+
+The other interpretation method introduced by \textcite{ustunVisualisationInterpretationSupport2007} visualizes the relationship learned between the input features and the outputs.
+This visualization is computed as the matrix multiplication between the support vectors and the learned Lagrange multipliers.
+The support vector matrix is transposed so that the multiplication is done on the dimension that indexes each sample.
+This computation is implemented as shown in \lccref{fig:lssvr_p_matrix_function_impl}.
+The resulting matrix is termed the p-matrix.
+The columns of this matrix represents the outputs and the rows represents the input features.
+The p-matrix values show how each feature contribute to the output learned by the model.
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+...
+    def get_p_matrix(self):
+        return self.sv_x.T.mm(self.alpha)
+...
+  \end{lstlisting}
+  \caption{Implementation of Least-squares Support Vector Regression p-matrix function}\label{fig:lssvr_p_matrix_function_impl}
+\end{figure}
+
+The second component of the model modules is the SpectralSVR implementation that uses a multi-output support vector regression (SVR) model to learn in the spectral domain, such as the LSSVR implementation in the first component.
+The SpectralSVR is implemented as a class that extends the LSSVR to be able to learn from features and labels which are complex valued, which is the case for Fourier series coefficients.
+First, the constructor used to initialize each SpectralSVR instance accepts a Basis instance, an SVR instance which is the implemented LSSVR by default, and the verbosity of the model.
+These parameters are then used when the training function shown in \lccref{fig:spectralsvr_train_impl} is called.
+Training the SpectralSVR model begins by calling the train function with parameters of the input function representation, output function representation, and an indicator of whether the output function is time dependent.
+Then, the function ensures that the features and labels are matrices.
+And then, if the input or output function representations are complex, they are transformed into the real representation.
+These formatted training data features and labels are then used to train the LSSVR model itself.
+Finally, to again allow for chaining methods, the function returns the current class instance.
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+...
+    def train(
+        self,
+        f: torch.Tensor,
+        u_coeff: torch.Tensor,
+        u_time_dependent: bool = False,
+    ):
+        self.basis.time_dependent = u_time_dependent
+        if self.basis.coeff_dtype.is_complex:
+            u_coeff = to_complex_coeff(u_coeff)
+
+        if f.ndim > 2:
+            f = f.flatten(1)
+        if u_coeff.ndim > 2:
+            u_coeff = u_coeff.flatten(1)
+
+        if torch.is_complex(u_coeff):
+            u_coeff = to_real_coeff(u_coeff)
+        if torch.is_complex(f):
+            f = to_real_coeff(f)
+        self.svr.fit(f, u_coeff)
+        return self
+...
+  \end{lstlisting}
+  \caption{Implementation of SpectralSVR training function}\label{fig:spectralsvr_train_impl}
+\end{figure}
+
+Using the learned data to predict other output function representations from unseen input functions can be done by directly calling the predict function of the LSSVR\@.
+This results in the real representation which needs to be converted into the complex representation for the FourierBasis.
+Once the conversion is done, the coefficients can be used to construct a new FourerBasis instance of the predictions.
+From there, the predicted functions can be evaluated and  plotted.
+However, if one simply wants to evaluate the value of the predicted function at arbitrary points, another function is implemented to provide ease of use for this exact case.
+The implemented function is called forward as displayed in \lccref{fig:spectralsvr_forward_impl}.
+The arguments to this function are the input functions, the evaluation points, and the domain span.
+The function first predicts the output function coefficients.
+Then, the predicted coefficients are multiplied with the basis function values at each point to compute the final predicted point values.
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+...
+    def forward(
+        self,
+        f: torch.Tensor,
+        x: torch.Tensor,
+        periods: tuple[float, ...]
+        | None = None,
+    ) -> torch.Tensor:
+        if len(x.shape) == 1:
+            x = x.unsqueeze(-1)
+
+        # compute coefficients
+        if torch.is_complex(f):
+            f = to_real_coeff(f)
+        coeff = self.svr.predict(f)
+        # convert to complex if basis needs complex values so that the reshaping is correct
+        if self.basis.coeff_dtype.is_complex:
+            coeff = to_complex_coeff(coeff)
+
+        return self.basis.evaluate(
+            coeff=coeff.reshape((f.shape[0], *self.modes)),
+            x=x,
+            periods=periods,
+            time_dependent=self.basis.time_dependent,
+        )
+...
+  \end{lstlisting}
+  \caption{Implementation of SpectralSVR forward function (pointwise prediction)}\label{fig:spectralsvr_forward_impl}
+\end{figure}
+
+The final core piece of functionality the SpectralSVR class provides is the inverse parameter estimation.
+This is implemented to solve inverse problems such as predicting the initial conditions for the Burgers' equation or heat equation.
+This function essentially does the gradient descent on a loss function in such a way that the output function matches some expected output.
+The loss function can simply be the coefficients of the expected output function.
+The loss function is formulated as the mean squared error of the difference between the predicted output and expected output.
+Using some randomly initialized values as the inputs, the predicted output is then used to compute the loss.
+The gradient of the loss with respect to the inputs are then computed and then used to perform optimization of the inputs using the ADAM optimizer.
+This is implemented as the inverse function shown in \lccref{fig:spectralsvr_inverse_impl}.
+The function arguments are the expected output function coefficients, evaluation points, the loss function used, how many optimization loops are done, the random number generator, and the gain which is used in generating the random initial input functions.
+The function returns the estimated input function coefficients in the real representation.
+For Fourier coefficients this means that the predicted input coefficients need to first be converted to complex valued tensors and then used to construct a FourierBasis instace.
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+...
+    def inverse(
+        self,
+        u: torch.Tensor,
+        points: torch.Tensor,
+        loss_fn: Callable[
+            [torch.Tensor, torch.Tensor], torch.Tensor
+        ] = mean_squared_error,
+        epochs=100,
+        generator=torch.Generator().manual_seed(42),
+        gain=0.2,
+        **optimizer_params,
+    ):
+        f_shape = (u.shape[0], self.svr.sv_x.shape[1])
+        # inverse problem
+        f_pred = torch.randn(f_shape, generator=generator) * gain
+        f_pred.requires_grad_()
+
+        optim = torch.optim.Adam([f_pred], **optimizer_params)
+        for epoch in range(epochs):
+            optim.zero_grad()
+            u_pred = self.forward(f_pred, points).real
+            loss = loss_fn(u_pred, u)
+            loss.backward()
+            optim.step()
+        optim.zero_grad()
+        return f_pred
+...
+  \end{lstlisting}
+  \caption{Implementation of SpectralSVR inverse function (parameter estimation)}\label{fig:spectralsvr_inverse_impl}
+\end{figure}
+
+The last piece of the SpectralSVR class provides a convenience function for testing the performance of the learned model.
+This function is shown in \lccref{fig:spectralsvr_test_impl}.
+The function arguments are the testing inputs, testing outputs, and a resolution for evaluation of function values.
+The first step is to convert the testing input into real representations and then predicting the output function.
+The predicted output are then compared to the testing outputs using many metrics including RMSE, MSE, MAE, R2, SMAPE, RSE, RRSE, and the number of Nan values present in the predicted output.
+The same comparison process is carried out again for the function values which are evaluated at the specified resolution.
+Finally, the function returns the metric values as a nested tuple for both the coefficients predictions and the function value predictions.
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+...
+    def test(
+        self,
+        f: torch.Tensor,
+        u_coeff_targets: torch.Tensor,
+        res: ResType = 200,
+    ):
+        if torch.is_complex(f):
+            logger.debug("transform f to real")
+            f = to_real_coeff(f)
+        u_coeff_preds = self.svr.predict(f)
+        if torch.is_complex(u_coeff_targets):
+            logger.debug("transform u_coeff to real")
+            u_coeff_targets = to_real_coeff(u_coeff_targets)
+
+        grid = self.basis.grid(res).flatten(0, -2)
+        u_preds = self.basis.evaluate(
+            coeff=to_complex_coeff(u_coeff_preds),
+            x=grid,
+            time_dependent=self.basis.time_dependent,
+        ).real
+        u_targets = self.basis.evaluate(
+            coeff=to_complex_coeff(u_coeff_targets),
+            x=grid,
+            time_dependent=self.basis.time_dependent,
+        ).real
+        return {
+            "spectral": get_metrics(
+                u_coeff_preds, u_coeff_targets
+            ),
+            "function value": get_metrics(u_preds, u_targets),
+        }
+...
+  \end{lstlisting}
+  \caption{Implementation of SpectralSVR test function}\label{fig:spectralsvr_test_impl}
+\end{figure}
+
+\subsubsection{Problems}
+
+\noindent The final module implements the PDEs that will serve as problems the proposed modules will solve.
+The implementation is mainly responsible for generating datasets from the PDEs and computing the PDE residuals.
+This implementation is focused on the two synthetic datasets which are the antiderivative problem and the Burgers' equation problem.
+The problem base class is implemented as an abstract class that the specific problems will subclass.
+The base class requires any subclass to implement three methods.
+First, the data generation method which receives specifications such as what basis functions to use, how many function samples to create, how many modes are needed for each sample, and a Pytorch generator that will be used in generating the random basis coefficients.
+Other arguments more specific to each problem will be implemented by the specific subclass.
+This function is then expected to return a tuple of Basis instances.
+The second and third functions are the spectral and function value residuals for the PDE of each subclass, respectively.
+These three functions make up the functionality that is offered by all Problem subclasses.
+The implementation of the Problem subclass can be seen in \lccref{fig:problem_impl}.
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+import abc
+import torch
+from ..basis import BasisSubType
+
+class Problem(abc.ABC):
+    def __init__(self) -> None:
+        super().__init__()
+
+    @abc.abstractmethod
+    def generate(
+        self,
+        basis: type[BasisSubType],
+        n: int,
+        modes: int | tuple[int, ...],
+        *args,
+        generator: torch.Generator | None = None,
+        **kwargs,
+    ) -> tuple[BasisSubType, ...]:
+        pass
+
+    @abc.abstractmethod
+    def spectral_residual(
+        self, u: BasisSubType, *args, **kwargs
+    ) -> BasisSubType:
+        pass
+
+    @abc.abstractmethod
+    def residual(
+        self, u: BasisSubType, *args, **kwargs
+    ) -> BasisSubType:
+        pass
+  \end{lstlisting}
+  \caption{Implementation of Problem base class}\label{fig:problem_impl}
+\end{figure}
+
+The antiderivative problem is relatively simple to implement.
+The generation function takes advantage of the gradient operation and generate function provided by the Basis subclasses.
+The arguments to this function are the same as the base class with the addition of an integration constant parameter.
+By default, the value of the integration constant is zero.
+The function then returns the tuple of basis subclass instances representing the derivative and antiderivative functions.
+This function can be seen in \lccref{fig:antiderivative_generate_impl}.
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+...
+    def generate(
+        self,
+        basis: Type[BasisSubType],
+        n: int,
+        modes: int | tuple[int, ...],
+        u0: float | int | complex,
+        *args,
+        generator: torch.Generator | None = None,
+        **kwargs,
+    ) -> tuple[BasisSubType, BasisSubType]:
+        if isinstance(modes, int):
+            modes = (modes,)
+        # generate solution functions
+        u = basis.generate(
+            n, modes, generator=generator, *args, **kwargs
+        )
+        # compute derivative functions
+        ut = u.grad()
+        # set the integration coefficient
+        if isinstance(u0, complex):
+            if u.coeff.is_complex():
+                u.coeff[:, 0] = torch.tensor(u0)
+            else:
+                u.coeff[:, 0] = torch.tensor(u0).real
+        elif isinstance(u0, float) or isinstance(u0, int):
+            if u.coeff.is_complex():
+                u.coeff[:, 0] = torch.tensor(u0 + 0j)
+            else:
+                u.coeff[:, 0] = torch.tensor(u0)
+        else:
+            u.coeff[:, 0] = u0
+
+        return (u, ut)
+...
+  \end{lstlisting}
+  \caption{Implementation of Antiderivative generate function}\label{fig:antiderivative_generate_impl}
+\end{figure}
+
+The residual functions are similarly easy to implement as shown in \lccref{fig:antiderivative_residual_impl}.
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+...
+    def spectral_residual(
+        self, u: BasisSubType, ut: BasisSubType
+    ) -> BasisSubType:
+        residual = u.grad() - ut
+        if residual.coeff is not None:
+            residual.coeff[:, 0].mul_(0)
+
+        return residual
+
+    def residual(
+        self, u: BasisSubType, ut: BasisSubType
+    ) -> BasisSubType:
+        u_val, grid = u.get_values_and_grid()
+        ut_val = ut.get_values()
+        dt = grid[1, 0] - grid[0, 0]
+        u_grad = torch.gradient(
+            u_val, spacing=dt.item(), dim=1
+        )[0]
+        residual_val = u_grad - ut_val
+        residual = u.copy()
+        residual.coeff = u.transform(residual_val)
+        return residual
+...
+  \end{lstlisting}
+  \caption{Implementation of Antiderivative residual functions}\label{fig:antiderivative_residual_impl}
+\end{figure}
+
+For the Burgers' equation, the problem subclass for this PDE implemented a generate function with two generation paths.
+But before discussing the specifics of the two paths, the function has some extra arguments and preprocessing of those arguments.
+This time the function asks for the kind of functions the initial condition and the forcing term needs to be, whether they are random or constant.
+The combination of the kind of functions the initial conditions and forcing terms are will determine the path of generation that the function will take.
+The function also requires the viscosity parameter nu which is 0.01 by default.
+The domain also needs to be specified with a default value of 0 to 1 with 200 grid points for both space and time.
+The solver which is used for one of the generation procedures is also an argument with a default of the implicit adams solver from torchdiffeq \autocite{Chen_torchdiffeq_2021}.
+Finally, whether the output basis coefficients are time dependent or not is passed in as an argument alongside with the Pytorch generator.
+The implementation of this portion of the function can be seen in \lccref{fig:burgers_generate_impl}.
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+...
+    def generate(
+        self,
+        basis: Type[BasisSubType],
+        n: int,
+        modes: int | tuple[int, ...],
+        u0: ParamInput | BasisSubType = "random",
+        f: ParamInput | BasisSubType = 0,
+        nu: float = 0.01,
+        space_domain=slice(0, 1, 200),
+        time_domain=slice(0, 1, 200),
+        solver: SolverSignatureType = implicit_adams_solver,
+        time_dependent_coeff: bool = True,
+        *args,
+        generator: torch.Generator | None = None,
+        **kwargs,
+    ) -> tuple[BasisSubType, BasisSubType]:
+        if isinstance(modes, int):
+            modes = (modes,)
+
+        device = "cuda:0" if torch.cuda.is_available() else "cpu"
+
+        L = space_domain.stop - space_domain.start
+        x = (
+            basis.grid(slice(
+                space_domain.start, space_domain.stop, modes[0]
+            )).flatten(0, -2)
+            .to(device=device)
+        )
+        T: float = time_domain.stop - time_domain.start
+        nt = int(time_domain.step)
+        # nt = int(T / (0.01 * nu) + 2)
+        dt = T / (nt - 1)
+        t = basis.grid(time_domain).flatten().to(device=device)
+        periods = (T, L)
+...
+  \end{lstlisting}
+  \caption{Implementation of Burgers generate function}\label{fig:burgers_generate_impl}
+\end{figure}
+
+The first generation path and most similar to the antiderivative case is when both the initial condition and forcing terms are random.
+This branch of the generate function utilizes the residual function to compute the forcing term from the randomly generated solution function.
+This method of generating the solution and forcing term is stable and relatively straightforward.
+The implementation of this branch is shown in \lccref{fig:burgers_generate_manufactured_impl}.
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+...
+        if u0 == "random" and f == "random":
+            # use method of manufactured solution
+            time_mode = modes[0]
+            if len(modes) > 1:
+                modes = modes[1:]
+            u = basis.generate(
+                n,
+                (time_mode, *modes),
+                periods=periods,
+                generator=generator,
+            )
+            res_modes = tuple(slice(0, L, mode) for mode in modes)
+            fst = self.spectral_residual(
+                u,
+                basis(
+                    basis.generate_empty(n, (time_mode, *modes))
+                ),
+                nu,
+            )
+            u_gen = u
+            f_gen = fst
+            # convert to timed dependent coeffs
+            if time_dependent_coeff:
+                u_val = u.get_values(res=(time_domain, *res_modes))
+                u_coeff = basis.transform(
+                    u_val.flatten(0, 1)
+                ).reshape((n, nt, *modes))
+                u_gen = basis(
+                    coeff=u_coeff,
+                    time_dependent=True,
+                    periods=periods
+                )
+
+                f_val = fst.get_values(
+                    res=(time_domain, *res_modes)
+                )
+                f_coeff = basis.transform(
+                    f_val.flatten(0, 1)
+                ).reshape((n, nt, *modes))
+                f_gen = basis(
+                    coeff=f_coeff,
+                    time_dependent=True,
+                    periods=periods
+                )
+...
+  \end{lstlisting}
+  \caption{Implementation of Burgers generate function manufactured method}\label{fig:burgers_generate_manufactured_impl}
+\end{figure}
+
+The second case is when at least one of the initial condition or forcing term is not random.
+This second case requires solving the Burgers' equation using traditional numerical methods.
+The generate function calls a function that has the responsibility of setting up the constant initial conditions or constant forcing terms and then calls the ODE solver specified in the generate function arguments.
+The right-hand side function computes the time derivative based on \lccref{eq:time_derivative_time_step_function}.
+The implementation of this is show in \lccref{fig:burgers_generate_dt_impl}.
+Putting the above together gives us the implementation of the method of lines generation of Burgers' equation solution and forcing term as show in \lccref{fig:burgers_generate_mol_impl}.
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+...
+    @staticmethod
+    def rhs(
+        basis: type[Basis],
+        nu: float,
+        u_hat: torch.Tensor,
+        f_hat: torch.Tensor,
+    ) -> torch.Tensor:
+        u = basis(u_hat)
+        dealias_modes = tuple(
+            int(mode * 1.5) for mode in u.modes
+        )
+        u_dealiased = u.resize_modes(
+            dealias_modes, rescale=False
+        )
+        u_val = basis.inv_transform(u_dealiased.coeff)
+        uu_x_hat_dealiased = 0.5 * basis.transform(u_val**2)
+        uu_x = basis(
+            uu_x_hat_dealiased
+        ).resize_modes(u.modes, rescale=False).grad()
+
+        u_u_x_hat = uu_x.coeff
+        u_xx_hat = u.grad().grad().coeff
+        u_t_hat = nu * u_xx_hat + f_hat - u_u_x_hat
+        return u_t_hat
+...
+  \end{lstlisting}
+  \caption{Implementation of Burgers generate function time derivative}\label{fig:burgers_generate_dt_impl}
+\end{figure}
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+...
+        u0.coeff = u0.coeff.to(device=device)
+        fst.coeff = fst.coeff.to(device=device)
+        print(f"generating with {len(t)} time steps")
+
+        def f_func(t: torch.Tensor, x: torch.Tensor = x):
+            x = x.tile((1, 2))
+            x[:, 0] = t
+            return basis.transform(
+                fst(x).reshape((-1, modes[0]))
+            )
+
+        def rhs_func(t: torch.Tensor, y0: torch.Tensor):
+            y0 = to_complex_coeff(y0)
+            return to_real_coeff(
+                cls.rhs(basis, nu, y0, f_func(t))
+            )
+
+        u_hat = solver(rhs_func, to_real_coeff(u0.coeff), t)
+        if basis.coeff_dtype.is_complex:
+            u_shape = u_hat.shape
+            u_hat = to_complex_coeff(
+                u_hat.flatten(0, 1)
+            ).reshape(
+                (*u_shape[:2], *u0.coeff.shape[1:])
+            )
+
+        u_hat = u_hat.movedim(0, 1)
+        if timedependent_solution:
+            u = basis(u_hat, **kwargs, time_dependent=True)
+        else:
+            u_hat = u_hat.reshape((n * nt, modes[0]))
+            u = basis(
+                basis.transform(
+                    basis.inv_transform(u_hat).reshape(
+                        (n, nt, modes[0])
+                    )
+                ),
+                **kwargs,
+            )
+        u.coeff = u.coeff.cpu()
+        fst.coeff = fst.coeff.cpu()
+        return (u, fst)
+...
+  \end{lstlisting}
+  \caption{Implementation of Burgers generate function method of lines}\label{fig:burgers_generate_mol_impl}
+\end{figure}
+
+The spectral residual of the Burgers' equation which is used in the method of manufactured solution generation approach is implemented as shown in \lccref{fig:burgers_spectral_residual_impl}.
+As with the right hand side function, we use the psuedospectral approach for computing the convolution term to avoid large computational expenses for higher number of modes.
+The function value residual is also implemented in a similar manner to the antiderivative version.
+The derivatives are computed with the Pytorch gradient function.
+And then using \lccref{eq:forced_viscous_burgers}, the residual is computed by subtracting the forcing term from both sides.
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+...
+    def spectral_residual(
+        self, u: BasisSubType, f: BasisSubType, nu: float
+    ) -> BasisSubType:
+        u_t = u.grad(dim=0, ord=1)
+
+        dealias_modes = tuple(
+            int(mode * 1.5) for mode in u.modes
+        )
+        u_dealiased = u.resize_modes(
+            dealias_modes, rescale=False
+        )
+        u_val = u.inv_transform(u_dealiased.coeff)
+        uu_dealiased = u.copy()
+        uu_dealiased.coeff = u.transform(u_val.pow(2).mul(0.5))
+        uu_x = uu_dealiased.resize_modes(
+            u.modes, rescale=False
+        ).grad(dim=1)
+
+        u_xx = u.grad(dim=1, ord=2)
+        nu_u_xx = u_xx
+        nu_u_xx.coeff = nu_u_xx.coeff * nu
+
+        residual = u_t + uu_x - nu_u_xx - f
+        return residual
+...
+  \end{lstlisting}
+  \caption{Implementation of Burgers spectral residual function}\label{fig:burgers_spectral_residual_impl}
+\end{figure}
+
 \subsection{Testing}
-
-\section{Experimental Scenarios}
+\noindent The implementation is followed by tests of the functionality core to this study.
+The testing is done using the pytest library.
+The testing method used is a black box approach.
+The tests are written in a separate \verb|tests| directory.
+Each module is tested by a separate file.
+The tests are done to ensure compliance of the implementation to the requirements of the software.
+The results are presented in \lccref{table:impl_test_result}.
+
+\begin{table}[H]
+  \centering
+  \begin{tabular}{lm{0.2\linewidth}m{0.5\linewidth}l}
+    % \toprule
+    \toprule
+    No & Process & Test Target & Test Result       \\
+    \midrule
+    1  & Transform & Transform invertible with inverse transform & Achieved     \\\addlinespace[0.5em]
+    2  & Evaluation & Transform coefficient evaluation close to original values & Achieved \\\addlinespace[0.5em]
+    3  & Plot & Plotting function is run successfully & Achieved  \\\addlinespace[0.5em]
+    4  & Perturb & Perturb function is run successfully & Achieved     \\\addlinespace[0.5em]
+    5  & Operations & Operation functions is run successfully & Achieved     \\\addlinespace[0.5em]
+    6  & Complex Coefficients Conversion & Conversion between real and complex coefficient representation is invertible for odd and even number of modes & Achieved     \\\addlinespace[0.5em]
+    7  & SpectralSVR Train & Training function is run successfully & Achieved     \\\addlinespace[0.5em]
+    8  & SpectralSVR Prediction & Coefficient prediction error within tolerable range & Achieved     \\\addlinespace[0.5em]
+    9  & SpectralSVR Prediction & Function value prediction error within tolerable range & Achieved     \\
+    \bottomrule
+  \end{tabular}
+  \caption{Testing results of the SpectralSVR Library implementation using black box method} \label{table:impl_test_result}
+\end{table}
+
+\section{Experimental Scenarios}\label{sec:experimental_scenarios}
+\noindent To achieve the goals of this study, as outlined in \lccref{sec:aims}, we lay out three experimental scenarios.
+These scenarios represent different experimental configurations that will be applied to our implementation of the SpectralSVR library.
+A table of the configurations for each scenario can be seen in \lccref{table:experimental_scenarios}.
+
+\begin{table}[H]
+  \centering
+  \begin{tabularx}{\textwidth}{ L{0.75} *{3}{L{1.09}} } % compute these using approx barycentric coords (x + 3y = 4, x = 0.8y)
+    \toprule
+    Configuration & Scenario 1 & Scenario 2 & Scenario 3       \\
+    \midrule
+    Data Source & Synthetic (computed from equations) & Synthetic (computed from equations) with three viscosity values & ERA5 dataset \\\addlinespace[0.5em]
+    Data Augmentations & Perturbations of three different noise levels & Perturbation of 10\% the mean standard deviation of function values &  \\\addlinespace[0.5em]
+    Data Sample Size & 5000 unique functions for each noise level & 500 unique functions for each viscosity value & 7000 time steps \\\addlinespace[0.5em]
+    Regularization Parameter (\(C\)) & 1.0 & 1.0 & 1.0 \\\addlinespace[0.5em]
+    Kernel & RBF (\(\sigma = features \times X.var()\)) & RBF (\(\sigma = features \times X.var()\)) & RBF (\(\sigma = features \times X.var()\)) \\\addlinespace[0.5em]
+    Additional Tests & Exact solutions & Exact solutions &  \\\addlinespace[0.5em]
+    Interpretation & p-matrix and correlation image & p-matrix and correlation image & p-matrix and correlation image \\
+    \bottomrule
+  \end{tabularx}
+  \caption{The configuration of experimental scenarios in this study} \label{table:experimental_scenarios}
+\end{table}
+
+Each scenario serves a different purpose.
+The first scenario is constructed to establish whether the model can learn any relationships at all in data that implicitly defines differential equations.
+This scenario is a proof of concept of whether the model is capable of accurately learning the relationship between derivatives and their anti-derivatives.
+As the simplest case, it provides a foundation for understanding the model and its behavior.
+The second goal of this scenario is to determine how noise affects the model's predictions.
+This is especially important for the inverse problem because of how sensitive the derivative is to changes in the antiderivative.
+
+The second scenario extends the goal of the first scenario by examining the model and its behavior when learning a nonlinear PDE\@.
+The data subsets with different viscosity values are intended to allow us to learn more about how this will affect the performance on the exact solutions which may contain discontinuities for lower viscosity numbers.
+The model will learn to predict future states of systems governed by the Burgers' equation from past states.
+
+The third scenario is designed to demonstrate the modeling capability of SpectralSVR on a more practical problem of weather prediction.
+The earth weather system is a complex collection of processes.
+Using the ERA5 dataset, the model will be used to predict future states of the atmosphere from previous states.
+Specifically, the model will learn to predict the temperature 2 meters above the surface.
+That means that other than the time and spatial resolution not being the highest, the model will also learn from partial information of the relationships defined by the equation since no other variables will be included.
+This choice was made as an analog for situation with unknown PDEs and therefore unknown variables.
+With these situations, there is no guarantee that the variables measured have any relation with the system.
+These three scenarios together address the last two aims of this study.
+
+\section{Experimental Results}\label{sec:experimental_results}
+\noindent In this section, the results of each experimental scenario is presented and analyzed. The results come in the form of testing metrics mentioned in . %TODO: add reference to the metrics used.
+The model interpretations are displays of the correlation image and the p-matrix. The function values and coefficients themselves will also be plotted depending on the number of dimensions.
+
+\subsection{Scenario 1}
+\noindent The first scenario
+
+\subsection{Scenario 2}
 \noindent
 
-\section{Experimental Results}
+\subsection{Scenario 3}
 \noindent
-
-% \section{Sub Bab Hasil}
-% \noindent Bab ini memaparkan pekerjaan penelitian dan, terutama, hasil-hasilnya, untuk dianalisis.
-Secara komprehensif bab ini merepre-sentasikan curahan pemikiran dan kemampuan mahasiswa dalam menjalani pekerjaan penelitian, yang hasil-hasilnya dapat dipertanggungjawabkan.
-Banyak pendukung yang diperlukan dalam penulisan bab ini, seperti skema penting pengolahan data, penurunan model matematika, asumsi khusus, tabulasi hasil dan analisis, dan gambar atau grafik yang membantu dalam paparan analisis.
-Judul bab dan sub bab disesuaikan dengan isi paparan.
-
-% \section{Memasukkan Gambar}
-% \noindent Setiap gambar harus dirujuk pada naskah TA, termasuk gambar pada Lam- piran, menggunakan huruf pertama kapital (G) dan nomor gambar, tidak berdasarkan posisi relatifnya (misalnya di bawah ini atau sebelum ini).
-Format gambar yang umum adalah jpg, png, dan postscript (ps atau eps).
-Ukuran huruf pada nama sumbu dan label figures/grafik harus cukup besar dan jelas, demikian halnya dengan angka pada sumbu.
-Gambar dan grafik dapat berwarna dengan pilihan warna yang tegas dan jelas.
-
-% \subsection{Contoh Gambar Sederhana}
-% Contoh menginput gambar pada buku TA pada
-% \begin{figure}[ht] %h artinya here!
-%     \centering
-%     \includegraphics[width=0.3\linewidth]{figures/Semiconductor-Fermi-Level-Band-Diagram-1.jpg}
-%     \caption{Tingkatan Fermi pada\\Bahan Semikonduktor}\label{fermilevel}
-% \end{figure}
-% Apabila ada dua gambar, kita juga bisa menaruh keduanya berdampingan.
-
-% \begin{figure}[H]
-%     \centering
-%     \subfigure[]{
-%         \includegraphics[width=0.4\linewidth]{figures/Semiconductor-Fermi-Level-Band-Diagram-1.jpg}\label{surf-1}
-%     }\hspace{0.1\linewidth}
-%     \subfigure[]{
-%         \includegraphics[width=0.4\linewidth]{figures/Semiconductor-Fermi-Level-Band-Diagram-1.jpg}\label{surf-2}
-%     }
-%     \caption{Dengan menempatkan gambar \subref{surf-1} dan \subref{surf-2}, pembaca akan lebih mudah membandingkan keduanya.}\label{surface}
-% \end{figure}

### 2024-12-26 skripsi/chapter4.tex
finish ch4 scenaro 1 results

@@
   \end{adjustbox}
-  \caption{Computational Model of SpectralSVR}\label{fig:computational_model}
+  \caption{Computational Model of SpectralSVR.}\label{fig:computational_model}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Contents of pyproject.toml configuration file that define the dependencies using Poetry}\label{fig:poetry_add_deps}
+  \caption{Contents of pyproject.toml configuration file that define the dependencies using Poetry.}\label{fig:poetry_add_deps}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Utility function to convert between complex matrices and the real representations}\label{fig:complex_matrix_conversion_implementation}
+  \caption{Utility function to convert between complex matrices and the real representations.}\label{fig:complex_matrix_conversion_implementation}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Example of shrinking a tensor of samples' coefficients to a target number of modes}\label{fig:coefficient_shrink_impl}
+  \caption{Example of shrinking a tensor of samples' coefficients to a target number of modes.}\label{fig:coefficient_shrink_impl}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Example of expanding a tensor of samples' coefficients to a target number of modes}\label{fig:coefficient_expand_impl}
+  \caption{Example of expanding a tensor of samples' coefficients to a target number of modes.}\label{fig:coefficient_expand_impl}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Example of interpolating for indices (floating point indices) between the available ones (intiger indices)}\label{fig:coefficient_interpolation_impl}
+  \caption{Example of interpolating for indices (floating point indices) between the available ones (intiger indices).}\label{fig:coefficient_interpolation_impl}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Implementation of ODE solvers and the types}\label{fig:solver_impl}
+  \caption{Implementation of ODE solvers and the types.}\label{fig:solver_impl}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Implementation of forward Fourier transform}\label{fig:fourier_transform_impl}
+  \caption{Implementation of forward Fourier transform.}\label{fig:fourier_transform_impl}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Implementation of n-dimensional Fourier transform for a specific dimension}\label{fig:ndim_fourier_transform_impl}
+  \caption{Implementation of n-dimensional Fourier transform for a specific dimension.}\label{fig:ndim_fourier_transform_impl}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Implementation of the one dimensional Fourier Transform}\label{fig:1d_fourier_transform_impl}
+  \caption{Implementation of the one dimensional Fourier Transform.}\label{fig:1d_fourier_transform_impl}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Implementation of basis addition function}\label{fig:basis_addition_impl}
+  \caption{Implementation of basis addition function.}\label{fig:basis_addition_impl}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Implementation of basis grad function}\label{fig:basis_grad_impl}
+  \caption{Implementation of basis grad function.}\label{fig:basis_grad_impl}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Implementation of Fourier Basis coefficient generation function}\label{fig:generate_coeff_impl}
+  \caption{Implementation of Fourier Basis coefficient generation function.}\label{fig:generate_coeff_impl}
 \end{figure}
@@
 
-\subsubsection{Model}
+\subsubsection{Model}\label{sec:impl_model}
 
@@
   \end{lstlisting}
-  \caption{Implementation of Least-squares Support Vector Regression fitting function}\label{fig:lssvr_fit_function_impl}
+  \caption{Implementation of Least-squares Support Vector Regression fitting function.}\label{fig:lssvr_fit_function_impl}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Implementation of Least-squares Support Vector Regression prediction function}\label{fig:lssvr_predict_function_impl}
+  \caption{Implementation of Least-squares Support Vector Regression prediction function.}\label{fig:lssvr_predict_function_impl}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Implementation of Least-squares Support Vector Regression correlation image function}\label{fig:lssvr_correlation_image_function_impl}
+  \caption{Implementation of Least-squares Support Vector Regression correlation image function.}\label{fig:lssvr_correlation_image_function_impl}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Implementation of Least-squares Support Vector Regression p-matrix function}\label{fig:lssvr_p_matrix_function_impl}
+  \caption{Implementation of Least-squares Support Vector Regression p-matrix function.}\label{fig:lssvr_p_matrix_function_impl}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Implementation of SpectralSVR training function}\label{fig:spectralsvr_train_impl}
+  \caption{Implementation of SpectralSVR training function.}\label{fig:spectralsvr_train_impl}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Implementation of SpectralSVR forward function (pointwise prediction)}\label{fig:spectralsvr_forward_impl}
+  \caption{Implementation of SpectralSVR forward function (pointwise prediction).}\label{fig:spectralsvr_forward_impl}
 \end{figure}
@@
 This function essentially does the gradient descent on a loss function in such a way that the output function matches some expected output.
-The loss function can simply be the coefficients of the expected output function.
+The loss function is simply a measure of how far the outputs of the current predicted inputs are from the target outputs.
 The loss function is formulated as the mean squared error of the difference between the predicted output and expected output.
@@
 The function returns the estimated input function coefficients in the real representation.
-For Fourier coefficients this means that the predicted input coefficients need to first be converted to complex valued tensors and then used to construct a FourierBasis instace.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def inverse(
+For Fourier coefficients this means that the predicted input coefficients need to first be converted to complex valued tensors and then used to construct a FourierBasis instance.
+For convenience, a wrapper like the forward function is also implemented for evaluating the function values of the predicted input coefficients.
+
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+...
+    def inverse_coeff(
         self,
-        u: torch.Tensor,
-        points: torch.Tensor,
+        u_coeff: torch.Tensor,
         loss_fn: Callable[
@@
         generator=torch.Generator().manual_seed(42),
-        gain=0.2,
+        gain=0.05,
         **optimizer_params,
     ):
-        f_shape = (u.shape[0], self.svr.sv_x.shape[1])
+        f_shape = (u_coeff.shape[0], self.svr.sv_x.shape[1])
+        complex_coeff = u_coeff.is_complex()
+        original_device = u_coeff.device
+        u_coeff = to_real_coeff(u_coeff.flatten(1)).to(self.svr.device)
+
         # inverse problem
-        f_pred = torch.randn(f_shape, generator=generator) * gain
-        f_pred.requires_grad_()
-
-        optim = torch.optim.Adam([f_pred], **optimizer_params)
+        f_coeff_pred = (
+            torch.randn(f_shape, generator=generator).to(self.svr.device) * gain
+        )
+        f_coeff_pred.requires_grad_()
+        optim = torch.optim.Adam([f_coeff_pred], **optimizer_params)
+
         for epoch in range(epochs):
             optim.zero_grad()
-            u_pred = self.forward(f_pred, points).real
-            loss = loss_fn(u_pred, u)
+            u_coeff_pred = self.svr.predict(f_coeff_pred)
+            loss = loss_fn(u_coeff_pred, u_coeff)
             loss.backward()
@@
         optim.zero_grad()
-        return f_pred
-...
-  \end{lstlisting}
-  \caption{Implementation of SpectralSVR inverse function (parameter estimation)}\label{fig:spectralsvr_inverse_impl}
-\end{figure}
-
-The last piece of the SpectralSVR class provides a convenience function for testing the performance of the learned model.
+        f_coeff_pred.requires_grad_(False)
+        if complex_coeff:
+            f_coeff_pred = to_complex_coeff(f_coeff_pred)
+        return f_coeff_pred.to(original_device)
+...
+  \end{lstlisting}
+  \caption{Implementation of SpectralSVR inverse coeff function (parameter estimation).}\label{fig:spectralsvr_inverse_impl}
+\end{figure}
+
+The SpectralSVR class also provides a convenience function for testing the performance of the learned model.
 This function is shown in \lccref{fig:spectralsvr_test_impl}.
-The function arguments are the testing inputs, testing outputs, and a resolution for evaluation of function values.
+The function arguments are the testing inputs, expected testing outputs, and a resolution for evaluation of function values.
 The first step is to convert the testing input into real representations and then predicting the output function.
@@
   \end{lstlisting}
-  \caption{Implementation of SpectralSVR test function}\label{fig:spectralsvr_test_impl}
+  \caption{Implementation of SpectralSVR test function.}\label{fig:spectralsvr_test_impl}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Implementation of Problem base class}\label{fig:problem_impl}
+  \caption{Implementation of Problem base class.}\label{fig:problem_impl}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Implementation of Antiderivative generate function}\label{fig:antiderivative_generate_impl}
+  \caption{Implementation of Antiderivative generate function.}\label{fig:antiderivative_generate_impl}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Implementation of Antiderivative residual functions}\label{fig:antiderivative_residual_impl}
+  \caption{Implementation of Antiderivative residual functions.}\label{fig:antiderivative_residual_impl}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Implementation of Burgers generate function}\label{fig:burgers_generate_impl}
+  \caption{Implementation of Burgers generate function.}\label{fig:burgers_generate_impl}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Implementation of Burgers generate function manufactured method}\label{fig:burgers_generate_manufactured_impl}
+  \caption{Implementation of Burgers generate function manufactured method.}\label{fig:burgers_generate_manufactured_impl}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Implementation of Burgers generate function time derivative}\label{fig:burgers_generate_dt_impl}
+  \caption{Implementation of Burgers generate function time derivative.}\label{fig:burgers_generate_dt_impl}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Implementation of Burgers generate function method of lines}\label{fig:burgers_generate_mol_impl}
+  \caption{Implementation of Burgers generate function method of lines.}\label{fig:burgers_generate_mol_impl}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Implementation of Burgers spectral residual function}\label{fig:burgers_spectral_residual_impl}
+  \caption{Implementation of Burgers spectral residual function.}\label{fig:burgers_spectral_residual_impl}
 \end{figure}
@@
 The tests are done to ensure compliance of the implementation to the requirements of the software.
-The results are presented in \lccref{table:impl_test_result}.
+The final results are presented in \lccref{table:impl_test_result}.
+Each version and iteration of the development must ensure that the tests are passed before any changes are committed to the Github repository.
 
@@
   \end{tabular}
-  \caption{Testing results of the SpectralSVR Library implementation using black box method} \label{table:impl_test_result}
+  \caption{Testing results of the SpectralSVR Library implementation using black box method.} \label{table:impl_test_result}
 \end{table}
@@
 \begin{table}[H]
+  \caption{The configuration of experimental scenarios in this study.} \label{table:experimental_scenarios}
   \centering
@@
     Data Sample Size & 5000 unique functions for each noise level & 500 unique functions for each viscosity value & 7000 time steps \\\addlinespace[0.5em]
+    Number of Modes &  &  &  \\\addlinespace[0.5em]
+    Scaling & Standard scaling & Standard scaling & Standard scaling\\\addlinespace[0.5em]
+    Dataset Split & 80\% Training and 20\% Testing for each noise level & 80\% Training and 20\% Testing for each viscosity value & 80\% Training and 20\% Testing \\\addlinespace[0.5em]
     Regularization Parameter (\(C\)) & 1.0 & 1.0 & 1.0 \\\addlinespace[0.5em]
@@
   \end{tabularx}
-  \caption{The configuration of experimental scenarios in this study} \label{table:experimental_scenarios}
 \end{table}
@@
 As the simplest case, it provides a foundation for understanding the model and its behavior.
+The 5\% noise model is then used to predict the antiderivative of a cosine function with a period of one as shown in \lccref{eq:sine_derivative}.
+The exact solution is known as \lccref{eq:sine_function} \autocite{abramowitzHandbookMathematicalFunctions1972}.
 The second goal of this scenario is to determine how noise affects the model's predictions.
 This is especially important for the inverse problem because of how sensitive the derivative is to changes in the antiderivative.
+To further solidify how the model fares for inverse problems, this scenario will also assess the performance of a trained model for a very simple inverse problem setup to determine the derivatives of the testing subset from the antiderivatives.
+This setup will utilize the model as a surrogate forward solver and optimize for a loss function using the inverse function of the SpectralSVR class as described in \lccref{sec:impl_model}.
+\begin{align}
+  f(x) &= 2\pi cos\left(2\pi x\right)\label{eq:sine_derivative}\\
+  f(x) &= sin\left(2\pi x\right)\label{eq:sine_function}
+\end{align}
 
@@
 The model will learn to predict future states of systems governed by the Burgers' equation from past states.
+The model trained for a viscosity value of 0.01 will be used to predict \lccref{eq:burgers_exact_solution} from initial conditions at time equals zero and the corresponding forcing term of a constant value of zero.
 
@@
 \subsection{Scenario 1}
-\noindent The first scenario
+\noindent The first scenario results are presented in four parts.
+The first is the coefficient prediction metrics which is shown in \lccref{table:scenario_1_spectral_metrics}.
+The table shows the noise level, the corresponding kernel scaling factor sigma, and the performance metrics themselves.
+\begin{table}[H]
+  \caption{Performance metrics of coefficient prediction in scenario 1 by noise level.}\label{table:scenario_1_spectral_metrics}
+  \centering
+  \begin{tabular}{lrrrrrrrrr}
+    \toprule
+    Noise level & Sigma & MSE & RMSE & MAE & R2 & sMAPE \\
+    \midrule
+    5\% & 10.00 & 0.85 & 0.92 & 0.56 & 0.96 & 0.31 \\
+    10\% & 10.00 & 2.07 & 1.44 & 0.93 & 0.91 & 0.46 \\
+    50\% & 10.00 & 15.56 & 3.94 & 3.04 & 0.50 & 1.04 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+The scenario is implemented as a Jupyter notebook which imports relevant libraries and our SpectralSVR library.
+The notebook starts with creating the data with the Antiderivative problem subclass.
+All random processes use the same Pytorch Generator instance with a seed of 42.
+The data is then augmented by perturbing the function values to create three versions with the noise levels mentioned in the scenario.
+Looping through each version, the training and testing subsets are randomly sampled to result in 80\% and 20\% of the original dataset respectively.
+Then the scaler is fitted on the training subset inputs.
+And then, both the training and testing inputs are transformed using the fitted scaler.
+Next, an instance of SpectralSVR is trained and tested.
+Finally, the metrics are stored and the next noise level is processed.
+Next the 5\% noise model is used to predict the antiderivative of a sine function.
+
+\Cref{table:scenario_1_spectral_metrics} shows that the model is able to generalize from the training data and learn the simple linear antiderivative operator.
+Focusing on the coefficient of determination (R2) scores, we can see that the model is off by 0.04 to the perfect score of 1.0 for the lowest noise level.
+While increasing noise levels does degrade the performance, this is partly due to the target values also having been perturbed.
+This fact can be seen if we look at how predictions from the very same trained models on noisy inputs are compared to the noise-free versions of the antiderivative functions which is shown in \lccref{table:scenario_1_clean_spectral_metrics}.
+The metrics show that the model predictions are slightly closer to the unperturbed function coefficients compared to the perturbed versions.
+This can be seen as the influence of the independent synthetic measurement noise in the perturbed targets being removed from the testing metrics.
+
+The higher noise levels shows that the model is still relatively accurate.
+Looking at the R2 score for the 50\% noise level, the model is more accurate than a baseline mean value model.
+The R2 score of 0.5 means that the model predictions has roughly half the error the baseline would produce.
+Another observation is that the kernel scaling hyperparameter sigma has the same value the same for all noise levels since the inputs are all scaled to approximately have a standard deviation of one.
+The value itself is from the number of features which comes out to 100 total inputs to the LSSVR\@.
+
+\begin{table}[H]
+  \caption{Performance metrics of coefficient prediction compared to unperturbed targets in scenario 1 by noise level.}\label{table:scenario_1_clean_spectral_metrics}
+  \centering
+  \begin{tabular}{lrrrrrrrr}
+    \toprule
+    Noise level & MSE & RMSE & MAE & R2 & sMAPE \\
+    \midrule
+    5\% & 0.78 & 0.89 & 0.51 & 0.96 & 0.28 \\
+    10\% & 1.82 & 1.35 & 0.81 & 0.92 & 0.41 \\
+    50\% & 9.34 & 3.06 & 2.25 & 0.62 & 0.91 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+The function values are also evaluated and the values of the metrics between the noisy targets and predictions are shown in \lccref{table:scenario_1_function_metrics}.
+While the relative metrics R2 and sMAPE stay close to the values we obtained for the coefficients themselves, since the metrics are now being computed in the physical domain, the scales have changed and because of that the values of the absolute metrics now reflect the change in scale.
+For reference, the scale of the target coefficient values for the 50\% noise level dataset in their real representation can range on average from -13.54 to 13.6 across the entire dataset.
+Therefore, an RMSE value of 3.94 for the predictions compared to the noisy targets mean that the error ratio is roughly 0.148 or just above 1 to 7.
+For the function values of the 50\% noise dataset the values range on average from -2.5 to 2.49.
+This was more difficult to compute since there is no direct way to compute the amplitude of the function from just the coefficients.
+Here we used the inverse transform and extracted the maximum and minimum values of each function from the discrete values.
+Since the RMSE in \lccref{table:scenario_1_function_metrics} for the 50\% noise dataset is 0.63, the error ratio comes to 0.126.
+One side note about \lccref{table:scenario_1_function_metrics} is that since the model instances are the same as the ones used in the coefficient evaluations, the hyperparameters are still the same including the kernel scaling factor sigma.
+\begin{table}[H]
+  \caption{Performance metrics of function value from evaluated coefficient prediction in scenario 1 by noise level.}\label{table:scenario_1_function_metrics}
+  \centering
+  \begin{tabular}{lrrrrrrrr}
+    \toprule
+    Noise level & MSE & RMSE & MAE & R2 & sMAPE \\
+    \midrule
+    5\% & 0.03 & 0.18 & 0.15 & 0.97 & 0.39 \\
+    10\% & 0.08 & 0.29 & 0.23 & 0.92 & 0.55 \\
+    50\% & 0.62 & 0.79 & 0.63 & 0.49 & 1.04 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+For the metrics between the predictions and the noise-free version of the target function values, the results parallel the outcomes of the coefficient predictions.
+The metrics show that the model performs slightly better with more pronounced differences for the higher noise levels.
+This echoes our previous statement on the effect of independent \enquote{measurement} noise in the target values on the evaluation metrics.
+\begin{table}[H]
+  \caption{Performance metrics of function value from evaluated coefficient prediction compared to unperturbed targets in scenario 1 by noise level.}\label{table:scenario_1_clean_function_metrics}
+  \centering
+  \begin{tabular}{lrrrrrrr}
+    \toprule
+    Noise level  & MSE & RMSE & MAE & R2 & sMAPE \\
+    \midrule
+    5\% & 0.03 & 0.18 & 0.14 & 0.97 & 0.38 \\
+    10\% & 0.07 & 0.27 & 0.22 & 0.92 & 0.53 \\
+    50\% & 0.37 & 0.61 & 0.49 & 0.62 & 0.94 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+The next part of this scenario is the results from predicting the exact solution of \lccref{eq:sine_derivative} which is \lccref{eq:sine_function}.
+The function values will be computed with the same discretization as the number of modes we used in the training set.
+Once the values are obtained for both functions, the coefficients are computed.
+Then instancing the FourierBasis class with the coefficients of the derivative function, we can create perturbed versions according to the noise levels of the training set.
+Finally, the derivative is used to predict the noise-free antiderivative.
+The results are presented in \lccrefs{table:scenario_1_exact_spectral_metrics,table:scenario_1_exact_function_metrics}.
+For 5\% and 10\% noise levels, the model shows that it has learned the relation.
+However, the 50\% noise level, the model has been unable to predict the results well enough.
+The marked difference in error across all metrics between the 50\% and the lower noise levels is more apparent for this specific exact problem compared to the test sets.
+A clear picture of this can be seen when we compare the sMAPE metric.
+For the test set, the predictions on average results in a value of 1, however, for this exact problem the sMAPE value is 1.4 to 1.7.
+
+\begin{table}[H]
+  \caption{Performance metrics of coefficient prediction of exact antiderivative in scenario 1 by noise level.}\label{table:scenario_1_exact_spectral_metrics}
+  \centering
+  \begin{tabular}{lrrrr}
+    \toprule
+    Noise level & MSE & RMSE & MAE & sMAPE \\
+    \midrule
+    5\% & 0.12 & 0.35 & 0.20 & 1.26 \\
+    10\% & 0.75 & 0.87 & 0.30 & 1.26 \\
+    50\% & 10.35 & 3.22 & 0.82 & 1.39 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\begin{table}[H]
+  \caption{Performance metrics of evaluated function values of coefficient prediction of exact antiderivative in scenario 1 by noise level.}\label{table:scenario_1_exact_function_metrics}
+  \centering
+  \begin{tabular}{lrrrr}
+    \toprule
+    Noise level & MSE & RMSE & MAE & sMAPE \\
+    \midrule
+    5\% & 0.01 & 0.07 & 0.06 & 0.24 \\
+    10\% & 0.03 & 0.17 & 0.15 & 0.37 \\
+    50\% & 0.41 & 0.64 & 0.57 & 1.66 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+The predictions of the exact equation is shown in \lccref{fig:exact_antiderivative}.
+Visually, we can see that as the noise level increases, the model predictions become worse.
+Another observation is how the higher the noise level, the more the predicted functions become closer to zero.
+This is explained by the double penalty phenomenon \autocite{lledoScaledependentVerificationPrecipitation2023}.
+The loss function used for LSSVR penalizes the model for predicting a non-zero value that turns out to be wrong compared to predicting a zero value.
+This results in a model with predictions that are close to the mean of the training data.
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/exact_antiderivative_label.pgf}
+    \end{adjustbox}
+    \caption{}\label{fig:exact_antiderivative_label}
+  \end{subfigure}
+  \begin{subfigure}{\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/exact_antiderivative_prediction.pgf}
+    \end{adjustbox}
+    \caption{}\label{fig:exact_antiderivative_prediction}
+  \end{subfigure}
+  \caption{(\subref{fig:exact_antiderivative_label}) The perturbed exact input function values from \lccref{eq:sine_derivative}.
+(\subref{fig:exact_antiderivative_prediction}) Prediction of antiderivative from the input function that was perturbed.}\label{fig:exact_antiderivative}
+\end{figure}
+
+For inverse problems, we simply use the same testing set with the labels now used to predict the features.
+The model instances are still the same as before.
+With the implementation shown in \lccref{fig:spectralsvr_inverse_impl}, we run the inverse function for predicting coefficients with 2000 epochs, a learning rate of 0.02, and randomized starting point from a normal distribution multiplied by a factor of 0.05.
+The results of inverse prediction for all three noise levels are shown in \lccref{table:scenario_1_inv_spectral_metrics}.
+These metrics were computed after both the target and predicted input functions are scaled back using the same scalers they were scaled down with.
+Because the scales of the input and output functions are different, the absolute metrics are much larger in these results compared to the forward problem results.
+For reference, the target input coefficents on average range from -695.65 to 694.9.
+The relative metrics show that for the lower noise levels, the accuracy is still relatively good.
+However, the values are lower than the values for the forward test.
+The difference with the antiderivative prediction becomes more pronounced with the higher noise levels.
+For the highest noise level, the performance has degraded so far that the predictions are worse than a baseline model from the mean of the target input functions.
+One must also note that despite the much worse results of the other metrics for the highest noise level, at this time we're unable to explain why sMAPE results in roughly the same performance as in the forward problem.
+
+\begin{table}[H]
+  \caption{Performance metrics of coefficient inverse prediction of derivative in scenario 1 by noise level.}\label{table:scenario_1_inv_spectral_metrics}
+  \centering
+  \begin{tabular}{lrrrrr}
+    \toprule
+    Noise level & MSE & RMSE & MAE & R2 & sMAPE \\
+    \midrule
+    5\% & 1739.56 & 41.71 & 26.44 & 0.91 & 0.36 \\
+    10\% & 3485.10 & 59.03 & 42.19 & 0.76 & 0.52 \\
+    50\% & 49319.73 & 222.08 & 174.48 & -0.19 & 1.05 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+Next, we have the correlation image and p-matrix for the model of each noise level.
+The results are shown in \lccref{fig:scenario_1_interpretation}.
+Each row in the figure represent the results of a model trained on a different noise level.
+The correlation image for 5\% and 10\% noise show clear lines on the coefficient corresponding to the output coefficient that was sorted.
+We can also see that the negative wave number reflection also being sorted.
+This is because of the reflection that occurs with complex Fourier coefficients for real-valued functions.
+There are other faint vertical lines you are able to see for other input coefficients.
+These faint lines are not sorted like the corresponding coefficients we mentioned before.
+Meaning, while they don't affect the particular output coefficients that were sorted, they do show that there is information embedded in the kernel matrix for these input coefficients.
+However, if we look at the 50\% noise correlation image, even the corresponding coefficient does not show a clear line or gradient.
+The lines are more noisy compared to the other noise levels.
+But the kernel still manages to embed some information.
+The p-matrices show that The model itself is able to still learn some relationship between the input coefficients and the output coefficients.
+For the 5\% and 10\% noise levels, the p-matrices show very clearly the contributions of input coefficients to the output coefficients.
+However, looking at the p-matrix for 50\% noise level, the lower wave numbers show lower contribution of input coefficients to the output coefficients.
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=1.2\linewidth}
+      \input{figures/antiderivative_ci_5.pgf}
+    \end{adjustbox}
+    \caption{Correlation image 5\% noise.}\label{fig:sc1_ci_5}
+  \end{subfigure}
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=1.2\linewidth}
+      \input{figures/antiderivative_pm_5.pgf}
+    \end{adjustbox}
+    \caption{The p-matrix for 5\% noise.}\label{fig:sc1_pm_5}
+  \end{subfigure}
+  \\[-0.7\baselineskip]
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=1.2\linewidth}
+      \input{figures/antiderivative_ci_10.pgf}
+    \end{adjustbox}
+    \caption{Correlation image 10\% noise.}\label{fig:sc1_ci_10}
+  \end{subfigure}
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=1.2\linewidth}
+      \input{figures/antiderivative_pm_10.pgf}
+    \end{adjustbox}
+    \caption{The p-matrix for 10\% noise.}\label{fig:sc1_pm_10}
+  \end{subfigure}
+  \\[-0.7\baselineskip]
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=1.2\linewidth}
+      \input{figures/antiderivative_ci_50.pgf}
+    \end{adjustbox}
+    \caption{Correlation image 50\% noise.}\label{fig:sc1_ci_50}
+  \end{subfigure}
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=1.2\linewidth}
+      \input{figures/antiderivative_pm_50.pgf}
+    \end{adjustbox}
+    \caption{The p-matrix for 50\% noise.}\label{fig:sc1_pm_50}
+  \end{subfigure}
+  \caption{Correlation image (left column) and p-matrix (right column) for each model trained on a different noise level (row).
+The correlation image was sorted same order the values of the real component of wave number \(k=2\) were sorted in descending order.}\label{fig:scenario_1_interpretation}
+\end{figure}
+
+The final observation we make is how for all the p-matrices the pronounced contribution of the input wave number to their corresponding output wave number.
+This means that the majority of contributions to each output coefficients come from the corresponding input coefficients of the same wave number.
+Our knowledge on how the simple derivative equation for Fourier series relate the coefficients of the derivative function and the antiderivative function aligns with the contributions shown by the p-matrices.
+This confirms that the model is indeed learning the relations that is defined by the derivative equation.
 
 \subsection{Scenario 2}
-\noindent
+\noindent The second scenario results are presented in two parts which are the coefficient predictions and function value predictions.
 

### 2024-12-29 skripsi/chapter4.tex
ch4 add scenario 2, todo: predictions for exact burgers

@@
 
-After this, in the third step, the solution functions \(u \) are generated with 20 modes in time and 20 in space and 500 unique function samples for each viscosity value.
-In total 1500 unique solution functions are generated.
+After this, in the third step, the solution functions \(u \) are generated with 25 modes in time and 25 in space and 40 unique function samples for each viscosity value.
+In total 120 unique solution functions are generated.
+To ensure the same solutions are generated every time, the random number generator uses a new instance of the generator with the same seed number.
+This results in the solutions being the same for all viscosity and other parameters of the equation are adapted to this.
 
@@
 Using this equation, the exact forcing term corresponding to the randomly generated solution can be computed with relatively low cost.
-Finally, the function values of both the solutions and forcing terms are perturbed by adding Gaussian noise with a mean of zero and standard deviation of 10\% of the function value standard deviation to the values of the inverse transform.
+Finally, the function values of both the solutions and forcing terms are perturbed by adding Gaussian noise with a mean of zero and standard deviation of 5\% of the function value standard deviation to the values of the inverse transform.
 The perturbed coefficients are then recomputed from the sum and the final perturbed functions are obtained.
+
+An example of the solution and forcing term pairs that has been generated is shown in \lccref{fig:burgers_data}.
+Using the same seed we can see that the solution functions of the same sample are the same for the most part.
+However, with the forcing terms, we see much larger amplitudes for higher frequencies for larger viscosity values.
+This is inline with \lccref{eq:forced_viscous_burgers_coeff}.
+The squared multiplier gets large much more quickly for higher frequencies due to the squaring operation.
+The since this effect is controlled by the viscosity via multiplication, the higher the viscosity, the larger the high frequency amplitudes of the forcing term.
+This in other words mean that more viscous fluids require quadratically more force to affect the solution in the same way with lower viscosities.
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/burgers_solution_0.0.pgf}
+    \end{adjustbox}
+    \caption{Solution function for \(\nu=0\).}\label{fig:burgers_solution_0.0}
+  \end{subfigure}
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/burgers_forcing_0.0.pgf}
+    \end{adjustbox}
+    \caption{Forcing function for \(\nu=0\).}\label{fig:burgers_forcing_0.0}
+  \end{subfigure}
+  % \\[-0.7\baselineskip]
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/burgers_solution_0.01.pgf}
+    \end{adjustbox}
+    \caption{Solution function for \(\nu=0.01\).}\label{fig:burgers_solution_0.01}
+  \end{subfigure}
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/burgers_forcing_0.01.pgf}
+    \end{adjustbox}
+    \caption{Forcing function for \(\nu=0.01\).}\label{fig:burgers_forcing_0.01}
+  \end{subfigure}
+  % \\[-0.7\baselineskip]
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/burgers_solution_0.1.pgf}
+    \end{adjustbox}
+    \caption{Solution function for \(\nu=0.1\).}\label{fig:burgers_solution_0.1}
+  \end{subfigure}
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/burgers_forcing_0.1.pgf}
+    \end{adjustbox}
+    \caption{Forcing function for \(\nu=0.1\).}\label{fig:burgers_forcing_0.1}
+  \end{subfigure}
+  \caption{Example sample pairs of solution and forcing terms for the Burgers' equation dataset.}\label{fig:burgers_data}
+\end{figure}
 
@@
 
-\subsection{Data Transformation}
+\subsection{Data Transformation}\label{sec:data_transformation}
 \noindent The second phase of the computational model transforms the data that has been prepared into a form that can be used with the proposed model.
@@
 Which means that the input function is the acceleration function and the output function is the velocity function.
+
 The second use of a dataset depends on whether it can be interpreted as a mapping of a previous function to the next function.
@@
 This function describes the evolution of function \(f\) as a sum of some initial state \(f^0\) and perturbation which is its rate of change \(\dv{f}{t}\) at a point in time close to the current time multiplied by the time step \(\delta t\).
+This is the first order Taylor polynomial.
+Adding more terms with higher order derivatives can be done to increase the accuracy.
+This describes the same process that is used in the finite differences method.
 \begin{equation}
-  f^{t+1} = f^{t} + \delta t \times \dv{f}{t} \label{eq:time_step_function}
+  f^{t+1} = f^{t} + \delta t \times \dv{f}{t} + \dots \label{eq:time_step_function}
 \end{equation}
-In this case the previous function and any other independent variables like the forcing term involved in the time derivative \(\dv{f}{t}\) is used to predict the perturbation which is the time derivative itself.
+In this case the previous function and any other independent variables like the forcing term involved in the right-hand side of the equation is used to predict the difference between the future state and the current state.
 It would mean that each sample function in the data would need to at least have two dimensions.
@@
 This condition is true for both the Burgers' equation dataset and the WeatherBench 2 collection of ERA5 datasets.
-First, the Burgers' equation dataset, while is also able to be used in the first way as a mapping between the forcing term and the solution, one of the traditional ways of solving it is using the method of lines in conjunction with another method such as the finite differences method or the spectral method.
-In both of these, the Burgers' equation is formulated as an initial value problem, using the finite differences to computing the time derivative.
-% TODO: add figures and citation for this, or if this is avaliable in a different place in the thesis a refference to that.
-The method of lines approach in one of its forms is equal to \lccref{eq:time_step_function} \autocite{schiesserNumericalMethodLines2012,sadikuSimpleIntroductionMethod2000}.
-As such the Burgers' equation dataset can also be used in this way.
+First, the Burgers' equation dataset, while is also able to be used in the first way as a mapping between the forcing term and the solution, one of the traditional ways of solving it is using the method of lines.
+This entails solving the dimensions other that time with methods such as the finite differences method or the spectral method.
+The time dimension is then separately solved using the finite differences method such as the form shown in \lccref{eq:time_step_function} \autocite{schiesserNumericalMethodLines2012,sadikuSimpleIntroductionMethod2000}.
+This is the form that the Burgers' equation dataset will be used in.
 In this case, algebraic manipulation of \lccref{eq:forced_viscous_burgers} results in the time derivative of the solution as in \lccref{eq:forced_viscous_burgers_time_derivative}.
@@
 \end{align}
-As can be seen, the time derivative is expressed in terms of the solution function, the forcing term and any other partial derivatives.
+The most important component of the right-hand side of the equation, the time derivative, is expressed in terms of the solution function, the forcing term and any other partial derivatives.
 Because of this, it means we can train the model to learn the relationship between the solution function combined with the forcing term and the time derivative.
@@
     b_0           & \cdots & b_m           \\
-    \vb{\alpha}_0 & \cdots & \vb{\alpha}_m\\
+    \vb{\alpha}_0 & \cdots & \vb{\alpha}_m \\
   \end{bmatrix}
@@
   \begin{bmatrix}
-    -1.03+0i & -0.52+0.39i & -0.54+0i & -0.52-0.39i\\
+    -1.03+0i & -0.52+0.39i & -0.54+0i & -0.52-0.39i \\
     -0.85+0i & -0.39+0.19i & 0.87+0i  & -0.39-0.19i
-  \end{bmatrix}\label{eq:complex_matrix}\\
+  \end{bmatrix}\label{eq:complex_matrix} \\
   \begin{bmatrix}
-    -1.03 & 0 & -0.52 & 0.39 & -0.54 & 0 & -0.52 & -0.39\\
+    -1.03 & 0 & -0.52 & 0.39 & -0.54 & 0 & -0.52 & -0.39 \\
     -0.85 & 0 & -0.39 & 0.19 & 0.87  & 0 & -0.39 & -0.19
@@
     Number of Modes                  &                                                     &                                                                     &                                            \\\addlinespace[0.5em]
-    Scaling & Standard scaling & Standard scaling & Standard scaling\\\addlinespace[0.5em]
+    Scaling                          & Standard scaling                                    & Standard scaling                                                    & Standard scaling                           \\\addlinespace[0.5em]
     Dataset Split                    & 80\% Training and 20\% Testing for each noise level & 80\% Training and 20\% Testing for each viscosity value             & 80\% Training and 20\% Testing             \\\addlinespace[0.5em]
@@
 \begin{align}
-  f(x) &= 2\pi cos\left(2\pi x\right)\label{eq:sine_derivative}\\
-  f(x) &= sin\left(2\pi x\right)\label{eq:sine_function}
+  f(x) & = 2\pi cos\left(2\pi x\right)\label{eq:sine_derivative} \\
+  f(x) & = sin\left(2\pi x\right)\label{eq:sine_function}
 \end{align}
@@
 \noindent The second scenario results are presented in two parts which are the coefficient predictions and function value predictions.
+The functions are first preprocessed in order to format them into current and next values in time as discussed in \lccref{sec:data_transformation}.
+The coefficient value predictions are shown in \lccref{table:scenario_2_spectral_metrics}.
+The RBF kernel parameter computed from the data is once again the same for all versions of the dataset with a value of 10.
+The testing metrics show that the performance of the model vary with the viscosity value \(\nu \).
+Starting with the inviscid Burgers' equation, with \(\nu=0\), the model performs relatively well and close to the best result with \(\nu=0.01\).
+The function value evaluated from the predictions is shown in \lccref{table:scenario_2_function_metrics}.
+The metrics across the board shows that the function value relative metrics are worse compared to the coefficients.
+Comparing the absolute metrics for the same table, we see the same general trend that the higher viscosity show the model performing worse.
+
+\begin{table}[H]
+  \caption{Performance metrics of coefficient prediction of next time step in scenario 2 by noise level.}\label{table:scenario_2_spectral_metrics}
+  \centering
+  \begin{tabular}{lrrrrr}
+    \toprule
+    \(\nu\) & MSE  & RMSE & MAE  & R2   & sMAPE \\
+    \midrule
+    0.0     & 0.01 & 0.09 & 0.06 & 0.87 & 0.60  \\
+    0.01    & 0.01 & 0.08 & 0.06 & 0.90 & 0.56  \\
+    0.1     & 0.03 & 0.17 & 0.13 & 0.49 & 1.09  \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\begin{table}[H]
+  \caption{Performance metrics of function values evaluated from coefficient prediction of next time step in scenario 2 by noise level.}\label{table:scenario_2_function_metrics}
+  \centering
+  \begin{tabular}{lrrrrr}
+    \toprule
+    \(\nu\) & MSE      & RMSE & MAE  & R2   & sMAPE \\
+    \midrule
+    0.0     & 6.36e-04 & 0.03 & 0.02 & 0.85 & 0.66  \\
+    0.01    & 5.19e-04 & 0.02 & 0.02 & 0.88 & 0.62  \\
+    0.1     & 2.28e-03 & 0.05 & 0.04 & 0.45 & 1.13  \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+The correlation image and p-matrix for each viscosity can be seen in \lccref{fig:scenario_2_interpretation}.
+Analyzing the correlation images first, we see that some columns are sorted in correlation to how the samples are sorted based on the real component of the 4th output wave number.
+For the inviscid equation, this correlation is the strongest with multiple columns exhibiting the correlation.
+The highest and visually most sorted values are from the forcing term portion of the inputs.
+A weaker correlation is still present of the viscosity of \(\nu=0.01\).
+However, once we get to the highest viscosity case, we see a seemingly random arrangement of the correlation image values.
+This observation and the lower scores can both be explained by the level of temporal discretization.
+This is the same issue we encounter when we use some traditional methods for higher viscosity values with the same time step for lower viscosity values \autocite{kassamFourthOrderTimeSteppingStiff2005,seydaogluNumericalSolutionBurgers2016}.
+The issue arises in stiff differential equations.
+This term describes the presence of a rapidly varying component.
+We can see that the larger amplitudes of high frequency components in the forcing term to represent the rapidly varying components as shown in \lccrefs{fig:burgers_forcing_0.0,fig:burgers_forcing_0.01,fig:burgers_forcing_0.1}.
+Traditionally, stiff equations would require specific solvers purpose built to efficiently solve the problem.
+Otherwise, as with our method, the solving process would require much finer time steps.
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/burgers_ci_0.0.pgf}
+    \end{adjustbox}
+    \caption{Correlation image \(\nu=0.0\).}\label{fig:sc2_ci_0.0}
+  \end{subfigure}
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/burgers_pm_0.0.pgf}
+    \end{adjustbox}
+    \caption{The p-matrix for \(\nu=0.0\).}\label{fig:sc2_pm_0.0}
+  \end{subfigure}
+  % \\[-0.7\baselineskip]
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/burgers_ci_0.01.pgf}
+    \end{adjustbox}
+    \caption{Correlation image \(\nu=0.01\).}\label{fig:sc2_ci_0.01}
+  \end{subfigure}
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/burgers_pm_0.01.pgf}
+    \end{adjustbox}
+    \caption{The p-matrix for \(\nu=0.01\).}\label{fig:sc2_pm_0.01}
+  \end{subfigure}
+  % \\[-0.7\baselineskip]
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/burgers_ci_0.1.pgf}
+    \end{adjustbox}
+    \caption{Correlation image \(\nu=0.1\).}\label{fig:sc2_ci_0.1}
+  \end{subfigure}
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/burgers_pm_0.1.pgf}
+    \end{adjustbox}
+    \caption{The p-matrix for \(\nu=0.1\).}\label{fig:sc2_pm_0.1}
+  \end{subfigure}
+  \caption{Correlation image (left column) and p-matrix (right column) for each model trained on a different noise level (row).
+The correlation image was sorted same order the values of the real component of wave number \(k=4\) were sorted in descending order.}\label{fig:scenario_2_interpretation}
+\end{figure}
+
+The p-matrix shows the difference in contributions of both input functions.
+For the inviscid equation, the contributions mainly come from the forcing term.
+The current solution contributes a smaller amount in comparison.
+There is similarity with the antiderivative p-matrices in this case.
+The contributions to each output wave number mainly come from input coefficients with the same wave number.
+However, there is a noticeable contribution from other wave numbers too unlike the antiderivative case.
+For higher viscosity values, notice that the contribution of the previous solution increases.
+The increase is more pronounced for higher frequencies.
+This aligns with the quadratic scaling from the wave number on the coefficients \autocite{canutoSpectralMethodsEvolution2007}.
+The p-matrix for lower viscosity values show more structured contribution of other wave numbers in comparison to the higher wave numbers.
+This structure comes in the form of a grid pattern.
+For the real components of the output, the contribution of other wave numbers oscillate between higher and lower values depending on whether the input component is real or not.
+The imaginary output components on the other hand have a more constant contribution across the input components.
+The contribution once again become more pronounced the higher the absolute value of the wave number.
 

### 2025-01-02 skripsi/chapter4.tex
finish second scenario, fix figures and spelling ch4, start third scenario

@@
     \begin{adjustbox}{width=\linewidth}
-      \input{figures/clean_perturbed_solution_0.pgf}
+      \input{figures/antiderivative_clean_perturbed_solution.pgf}
     \end{adjustbox}
@@
     \begin{adjustbox}{width=\linewidth}
-      \input{figures/antiderivative_clean_0.pgf}
+      \input{figures/antiderivative_clean.pgf}
     \end{adjustbox}
@@
     \begin{adjustbox}{width=\linewidth}
-      \input{figures/derivative_clean_0.pgf}
+      \input{figures/antiderivative_derivative_clean.pgf}
     \end{adjustbox}
@@
 
-After this, in the third step, the solution functions \(u \) are generated with 25 modes in time and 25 in space and 40 unique function samples for each viscosity value.
-In total 120 unique solution functions are generated.
-To ensure the same solutions are generated every time, the random number generator uses a new instance of the generator with the same seed number.
+After this, in the third step, the solution functions \(u \) are generated with 8 modes in time and 8 in space and 500 unique function samples for each viscosity value.
+Since we don't factor the viscosity in at this point, for ease of comparison, we ensure the same solutions are generated every time by using a new instance of the generator with the same seed number each time.
 This results in the solutions being the same for all viscosity and other parameters of the equation are adapted to this.
 
-As for the forcing term, it is computed using \lccref{eq:forced_viscous_burgers}.
+Next we account for the different viscosity values in this stage.
+The forcing term is computed using \lccref{eq:forced_viscous_burgers}.
 The solution field \(u\) and forcing term \(f\) are modeled with Fourier series in \lccrefs{eq:fourier_field,eq:fourier_force} where \(k\) is a vector of spatial and temporal wave number such that \(k_t\) is the temporal wave number and \(k_x\) is the spatial wave number.
@@
      & + \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{x})\hat{uu}_k e^{2\pi i(k_{x}x+k_{t}t)}                                                              \\
-     & - \nu\sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{x})^2\hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)} \label{eq:forced_viscous_burgers_fourier_substitution}
+     & - \nu\sum_{k_{x}} \sum_{k_{t}} {(2\pi i k_{x})}^2\hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)} \label{eq:forced_viscous_burgers_fourier_substitution}
   \end{split}
@@
 \begin{align}
-  \sum_{k_{x}} \sum_{k_{t}} \hat{f}_k & = \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{t}) \hat{u}_k + (2\pi i k_{x})\hat{uu}_k - \nu(2\pi i k_{x})^2\hat{u}_k \label{eq:forced_viscous_burgers_fourier} \\
-  \hat{f}_k                           & = (2\pi i k_{t}) \hat{u}_k + (2\pi i k_{x})\hat{uu}_k - \nu(2\pi i k_{x})^2\hat{u}_k \label{eq:forced_viscous_burgers_coeff}
+  \sum_{k_{x}} \sum_{k_{t}} \hat{f}_k & = \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{t}) \hat{u}_k + (2\pi i k_{x})\hat{uu}_k - \nu{(2\pi i k_{x})}^2\hat{u}_k \label{eq:forced_viscous_burgers_fourier} \\
+  \hat{f}_k                           & = (2\pi i k_{t}) \hat{u}_k + (2\pi i k_{x})\hat{uu}_k - \nu{(2\pi i k_{x})}^2\hat{u}_k \label{eq:forced_viscous_burgers_coeff}
 \end{align}
@@
 Using this equation, the exact forcing term corresponding to the randomly generated solution can be computed with relatively low cost.
-Finally, the function values of both the solutions and forcing terms are perturbed by adding Gaussian noise with a mean of zero and standard deviation of 5\% of the function value standard deviation to the values of the inverse transform.
+Finally, the function values of both the solutions and forcing terms are perturbed by adding Gaussian noise with a mean of zero and standard deviation of 10\% of the function value standard deviation to the values of the inverse transform.
 The perturbed coefficients are then recomputed from the sum and the final perturbed functions are obtained.
@@
 An example of the solution and forcing term pairs that has been generated is shown in \lccref{fig:burgers_data}.
-Using the same seed we can see that the solution functions of the same sample are the same for the most part.
+Using the same seed we can see that the solution functions of the same sample are the same.
 However, with the forcing terms, we see much larger amplitudes for higher frequencies for larger viscosity values.
@@
 The since this effect is controlled by the viscosity via multiplication, the higher the viscosity, the larger the high frequency amplitudes of the forcing term.
-This in other words mean that more viscous fluids require quadratically more force to affect the solution in the same way with lower viscosities.
+This, in other words, means that more viscous fluids require a stronger forcing term to affect the solution in the same way with as fluids with a lower viscosity.
 
@@
 The ERA5 dataset specifically, assimilates previous forecasts with observational data every 12 hours.
-The ERA5 reanalysis is available at the following url (\url{https://cds.climate.copernicus.eu/datasets/reanalysis-era5-single-levels}).
+The ERA5 reanalysis is available at the following URL (\url{https://cds.climate.copernicus.eu/datasets/reanalysis-era5-single-levels}).
 
@@
 This dataset spans from year 1959 to 2023 with a grid size of \ang{5.625} or resolution of 64 by 32 which spans from \ang{-87.19} to \ang{87.19} in latitude and \ang{0.0} to \ang{354.4} in longitude.
-The dataset is also downsampled to 6 hour intervals that starts at midnight UTC January 1959 1\textsuperscript{st} and ends at 18:00 UTC January 10\textsuperscript{th} 2023.
+The dataset is also resampled down to 6-hour intervals that starts at midnight UTC January 1959 1\textsuperscript{st} and ends at 18:00 UTC January 10\textsuperscript{th} 2023.
 
@@
   \end{lstlisting}
-  \caption{Example of using Xarray to access a publicly accessible Zarr dataset hosted on Google Cloud Storage Bucket.} \label{fig:access_remote_zarr}
+  \caption{Example of using Xarray to access a publicly accessible Zarr dataset hosted on Google Cloud Storage Bucket.}\label{fig:access_remote_zarr}
 \end{figure}
@@
 The values of this variable is obtained by interpolating between the model values at the surface and the lowest model vertical level.
-We also limit the time range to ....
+We also limit the time range to ...
 An example of the data that was retrieved can be seen in .
@@
 Adding more terms with higher order derivatives can be done to increase the accuracy.
-This describes the same process that is used in the finite differences method.
+This describes the same process that is used in the finite difference method.
 \begin{equation}
@@
 This phase starts with formatting the inputs.
-If the inputs aren't scaled yet, then it is scaled using the scaler fitted on the training set.
+If the inputs aren't scaled yet, then it is scaled using the scaling function fitted on the training set.
 This is the case for new data such as new measurements or an analytical solution of the learned PDE\@.
@@
   \item The library is to be used in user code
-  \item The library depends on other libraries including the following core dependencies Pytorch, Numpy, Xarray, Zarr, Pandas, and tqdm.
+  \item The library depends on other libraries including the following core dependencies PyTorch, NumPy, Xarray, Zarr, Pandas, and tqdm.
 \end{enumerate}
 
-\subsection{Design} \label{sec:implementation_design}
+\subsection{Design}\label{sec:implementation_design}
 \noindent In this subsection, the architectural design of the software product is explained.
@@
 To facilitate the management of dependencies, the implementation makes use of the package management tool Poetry \autocite{eustacePoetryPythonPackaging2024}.
-In addition, the Python version is managed using the tool pyenv.
+In addition, the Python version is managed using the tool PyEnv.
 The implementation process starts with installation of the required dependencies.
@@
 In the following, we will discuss the implementation of each module and how the phases of computational model relates to each implemented functionality.
-The base data structure that is used in the implementation is the Pytorch Tensor \autocite{Ansel_PyTorch_2_Faster_2024}.
+The base data structure that is used in the implementation is the PyTorch Tensor \autocite{Ansel_PyTorch_2_Faster_2024}.
 Tensors are a generalization of scalars and array-like structures such as vectors and matrices.
 This is essential since many computations that is done in the proposed model are based on matrices and higher dimensional arrays.
-Pytorch Tensors allow the elements to be of different data types such as floating point numbers of different precision or even complex numbers.
-In addition to basic operations for working with the Tensors such as matrix multiplications, Pytorch also provides many algorithms for use when working with Tensors such as linear equation solvers or the Fast Fourier Transform.
-Another reason for choosing to use Pytorch is the ability to parallelize computation using specialized processors such as GPUs.
-Lastly, Pytorch is widely used in the machine learning community which reflects on its reliability, wealth of community knowledge and support, and active development.
+PyTorch Tensors allow the elements to be of different data types such as floating point numbers of different precision or even complex numbers.
+In addition to basic operations for working with the Tensors such as matrix multiplications, PyTorch also provides many algorithms for use when working with Tensors such as linear equation solvers or the Fast Fourier Transform.
+Another reason for choosing to use PyTorch is the ability to parallelize computation using specialized processors such as GPUs.
+Lastly, PyTorch is widely used in the machine learning community which reflects on its reliability, wealth of community knowledge and support, and active development.
 
@@
 \end{align}
-There are several ways to do this in Pytorch, such as extracting the real and imaginary element components into separate matrices and then interleaving the columns to create the real representation.
+There are several ways to do this in PyTorch, such as extracting the real and imaginary element components into separate matrices and then interleaving the columns to create the real representation.
 However, a more performant version can be made by using built-in functions of the library that directly allows views of complex valued tensors as real tensors and vice versa.
@@
 
-Another important utility used on inputs for the proposed SpectralSVR is a scaler.
+Another important utility used on inputs for the proposed SpectralSVR is a scaling function.
 This utility has been implemented in a variety of ways and using different tools.
-However, as the standard scaling is not provided by Pytorch, we have also implemented our own version.
-The scaler accepts Pytorch tensors or tuples of tensors of real or complex elements.
-First, the scaler is implemented as a class that is instantiated.
-The scaler is then fitted onto the reference data to obtain the standard deviation and mean of each feature.
+However, as the standard scaling is not provided by PyTorch, we have also implemented our own version.
+The scaling function accepts PyTorch tensors or tuples of tensors of real or complex elements.
+First, the scaling function is implemented as a class that is instantiated.
+The scaling function is then fitted onto the reference data to obtain the standard deviation and mean of each feature.
 This information is stored as properties of the class.
 Any complex tensors are converted into their real representations using the functions in \lccref{fig:complex_matrix_conversion_implementation}.
-Once the scaler instance is fitted, any set of tensors with the same number of features (columns) and element type (complex or real) can be roughly transformed into a standard deviation of one and mean of zero for every feature.
+Once the scaling function instance is fitted, any set of tensors with the same number of features (columns) and element type (complex or real) can be roughly transformed into a standard deviation of one and mean of zero for every feature.
 This is done by subtracting the fitted mean of each feature from the elements in the column and then dividing with the feature's standard deviation.
-The implementation also provides a method to retrieve a scaler fitted on a subset of the original tuple of tensors.
+The implementation also provides a method to retrieve a scaling function fitted on a subset of the original tuple of tensors.
 Serialization for saving to and loading from disk is also implemented.
-This is done simply by using the Pytorch save and load functions on the scaler instance itself.
+This is done simply by using the PyTorch save and load functions on the scaling function instance itself.
 For some use cases, an inverse scaling operation to the original standard deviation and mean is also essential.
@@
 The wave number decreases symmetrically as you move towards the edges of the dimension and reaching the lowest absolute wave number at the edges.
-This is done to ensure compatibility with the way existing libraries such as Pytorch works with tensors of Fourier coefficients.
+This is done to ensure compatibility with the way existing libraries such as PyTorch works with tensors of Fourier coefficients.
 Because of this, shrinking a tensor of coefficients along a dimension means removing the center of the tensor along that dimension.
@@
   \end{lstlisting}
-  \caption{Example of interpolating for indices (floating point indices) between the available ones (intiger indices).}\label{fig:coefficient_interpolation_impl}
+  \caption{Example of interpolating for indices (floating point indices) between the available ones (integer indices).}\label{fig:coefficient_interpolation_impl}
 \end{figure}
@@
 The evaluation boundaries, actual function domain size, whether the function can be assumed to be periodic, and if FFTs is allowed to be used together determine the Discrete Fourier Transform algorithm that is used.
-The FFT algorithm is used if the folowing are all true: the evaluation starts at zero and ends with the same value as the period, the function can be assumed to be periodic, and FFT is allowed.
+The FFT algorithm is used if the following are all true: the evaluation starts at zero and ends with the same value as the period, the function can be assumed to be periodic, and FFT is allowed.
 Otherwise, the transform is computed naively using \lccrefs{eq:discrete_fourier_transform,eq:inverse_discrete_fourier_transform}.
@@
 The arithmetic operations, which are addition and subtraction, are implemented by following how the actual mathematical operations would be carried out on two functions which are Fourier series as shown in \lccref{eq:fourier_series_addition}.
-For subtraction, the plus sign is simply replaced with the minues sign.
+For subtraction, the plus sign is simply replaced with the minus sign.
 \begin{align}
@@
 The implementation leverages the operator overloading in Python classes.
-For addition, the overload should be done to the \verb|__add__| function.
+In addition, the overload should be done to the \verb|__add__| function.
 This function adds the current instance to another object which is the other basis instance for our use case.
 We also want the operation to return an independent instance without any references to the previous instances.
-To do this, all properties are coppied into a new instance.
+To do this, all properties are copied into a new instance.
 This is then used to perform the arithmetic operation.
@@
 There are two components in this module.
-First, there is the implementation of least-squares support vector regression (LSSVR) using Pytorch.
+First, there is the implementation of least-squares support vector regression (LSSVR) using PyTorch.
 This implementation is a reimplementation and modification of an LSSVR implementation using scikit-learn by \textcite{florencioLssvr2020}.
-The modifications are mainly concerned with using Pytorch in place of scikit-learn.
-Other modifications are concerned with the performance side of things, which are computing the kernel matrix in batches to avoid memory spikes and the ability to compute on hardware accelerators supported by Pytorch such as GPUs.
+The modifications are mainly concerned with using PyTorch in place of scikit-learn.
+Other modifications are concerned with the performance side of things, which are computing the kernel matrix in batches to avoid memory spikes and the ability to compute on hardware accelerators supported by PyTorch such as GPUs.
 The LSSVR implementation starts with the constructor which accepts model hyperparameters which include the regularization parameter, kernel function and any kernel parameters, verbosity level, kernel matrix computation batch size, and device to perform computations on.
-The recieved parameters are then stored as properties of the class instance.
+The received parameters are then stored as properties of the class instance.
 For the kernel specifically, it will be initialized with the correct default parameters when the fitting function is called.
@@
 The kernel function used is batched to reduce the peak memory footprint.
-These matrices are then used in the second half to compute the solution using the least squares solver function from Pytorch called lstq.
+These matrices are then used in the second half to compute the solution using the least squares solver function from PyTorch called lstq.
 Finally, the result is split into the biases and Lagrange multipliers which are then returned as a tuple.
-The optimizing function is wrapped in a more user-friendly function which allows the use of numpy arrays in addition to the Pytorch Tensor used in the optimizing function.
+The optimizing function is wrapped in a more user-friendly function which allows the use of NumPy arrays in addition to the PyTorch Tensor used in the optimizing function.
 The wrapper function is named fit.
@@
 The first step is to convert the testing input into real representations and then predicting the output function.
-The predicted output are then compared to the testing outputs using many metrics including RMSE, MSE, MAE, R2, SMAPE, RSE, RRSE, and the number of Nan values present in the predicted output.
+The predicted output are then compared to the testing outputs using many metrics including RMSE, MSE, MAE, R2, SMAPE, RRSE, and the number of Nan values present in the predicted output.
 The same comparison process is carried out again for the function values which are evaluated at the specified resolution.
@@
 The base class requires any subclass to implement three methods.
-First, the data generation method which receives specifications such as what basis functions to use, how many function samples to create, how many modes are needed for each sample, and a Pytorch generator that will be used in generating the random basis coefficients.
+First, the data generation method which receives specifications such as what basis functions to use, how many function samples to create, how many modes are needed for each sample, and a PyTorch generator that will be used in generating the random basis coefficients.
 Other arguments more specific to each problem will be implemented by the specific subclass.
@@
 The domain also needs to be specified with a default value of 0 to 1 with 200 grid points for both space and time.
-The solver which is used for one of the generation procedures is also an argument with a default of the implicit adams solver from torchdiffeq \autocite{Chen_torchdiffeq_2021}.
-Finally, whether the output basis coefficients are time dependent or not is passed in as an argument alongside with the Pytorch generator.
+The solver which is used for one of the generation procedures is also an argument with a default of the implicit Adams solver from torchdiffeq \autocite{Chen_torchdiffeq_2021}.
+Finally, whether the output basis coefficients are time dependent or not is passed in as an argument alongside with the PyTorch generator.
 The implementation of this portion of the function can be seen in \lccref{fig:burgers_generate_impl}.
@@
 The spectral residual of the Burgers' equation which is used in the method of manufactured solution generation approach is implemented as shown in \lccref{fig:burgers_spectral_residual_impl}.
-As with the right hand side function, we use the psuedospectral approach for computing the convolution term to avoid large computational expenses for higher number of modes.
-The function value residual is also implemented in a similar manner to the antiderivative version.
-The derivatives are computed with the Pytorch gradient function.
+As with the right-hand side function, we use the psuedospectral approach for computing the convolution term to avoid large computational expenses for higher number of modes.
+The function value residual is also implemented similarly to the antiderivative version.
+The derivatives are computed with the PyTorch gradient function.
 And then using \lccref{eq:forced_viscous_burgers}, the residual is computed by subtracting the forcing term from both sides.
@@
 \noindent The implementation is followed by tests of the functionality core to this study.
-The testing is done using the pytest library.
+The testing is done using the PyTest library.
 The testing method used is a black box approach.
@@
 The final results are presented in \lccref{table:impl_test_result}.
-Each version and iteration of the development must ensure that the tests are passed before any changes are committed to the Github repository.
+Each version and iteration of the development must ensure that the tests are passed before any changes are committed to the GitHub repository.
 
@@
   \end{tabular}
-  \caption{Testing results of the SpectralSVR Library implementation using black box method.} \label{table:impl_test_result}
+  \caption{Testing results of the SpectralSVR Library implementation using black box method.}\label{table:impl_test_result}
 \end{table}
@@
 \section{Experimental Scenarios}\label{sec:experimental_scenarios}
-\noindent To achieve the goals of this study, as outlined in \lccref{sec:aims}, we lay out three experimental scenarios.
+\noindent To achieve the goals of this study, as outlined in \lccref{sec:aims}, we present three experimental scenarios.
 These scenarios represent different experimental configurations that will be applied to our implementation of the SpectralSVR library.
@@
 \begin{table}[H]
-  \caption{The configuration of experimental scenarios in this study.} \label{table:experimental_scenarios}
-  \centering
-  \begin{tabularx}{\textwidth}{ L{0.75} *{3}{L{1.09}} } % compute these using approx barycentric coords (x + 3y = 4, x = 0.8y)
+  \caption{The configuration of experimental scenarios in this study.}\label{table:experimental_scenarios}
+  \centering
+  \begin{tabularx}{\textwidth}{L{0.75}*{3}{L{1.09}}} % compute these using approx barycentric coords (x + 3y = 4, x = 0.8y)
     \toprule
@@
 \begin{align}
-  f(x) & = 2\pi cos\left(2\pi x\right)\label{eq:sine_derivative} \\
-  f(x) & = sin\left(2\pi x\right)\label{eq:sine_function}
+  f(x) & = 2\pi \cos\left(2\pi x\right)\label{eq:sine_derivative} \\
+  f(x) & = \sin\left(2\pi x\right)\label{eq:sine_function}
 \end{align}
@@
 The second scenario extends the goal of the first scenario by examining the model and its behavior when learning a nonlinear PDE\@.
-The data subsets with different viscosity values are intended to allow us to learn more about how this will affect the performance on the exact solutions which may contain discontinuities for lower viscosity numbers.
+The data subsets with different viscosity values are intended to allow us to learn more about how this will affect the performance on the exact solutions for lower viscosity numbers.
 The model will learn to predict future states of systems governed by the Burgers' equation from past states.
-The model trained for a viscosity value of 0.01 will be used to predict \lccref{eq:burgers_exact_solution} from initial conditions at time equals zero and the corresponding forcing term of a constant value of zero.
+The model for each viscosity will be used to predict \lccref{eq:burgers_exact_solution} from initial conditions at time equals zero and the corresponding forcing term of a constant value of zero.
+The exact equation prediction will be done using a rollout method.
+The initial condition along with the initial forcing term will be given to the model to predict the solution at the first time step.
+The model will then use the predicted solution with the forcing term at the first time step to predict the solution at the second time step.
+This is repeated until the stopping condition of time \(t=10\).
+The forcing term for the exact solution is a constant zero.
+Along with the rollout of the exact solution, we also perform roll out on one of the test solution.
 
@@
 The first is the coefficient prediction metrics which is shown in \lccref{table:scenario_1_spectral_metrics}.
-The table shows the noise level, the corresponding kernel scaling factor sigma, and the performance metrics themselves.
+The table shows the noise level and the performance metrics.
 \begin{table}[H]
@@
     \toprule
-    Noise level & Sigma & MSE   & RMSE & MAE  & R2   & sMAPE \\
+    Noise level & MSE   & RMSE & MAE  & R2   & sMAPE \\
     \midrule
-    5\%         & 10.00 & 0.85  & 0.92 & 0.56 & 0.96 & 0.31  \\
-    10\%        & 10.00 & 2.07  & 1.44 & 0.93 & 0.91 & 0.46  \\
-    50\%        & 10.00 & 15.56 & 3.94 & 3.04 & 0.50 & 1.04  \\
+    5\%         & 0.86  & 0.93 & 0.57 & 0.96 & 0.31  \\
+    10\%        & 2.06  & 1.43 & 0.93 & 0.91 & 0.46  \\
+    50\%        & 15.59 & 3.95 & 3.04 & 0.50 & 1.04  \\
     \bottomrule
@@
 The notebook starts with creating the data with the Antiderivative problem subclass.
-All random processes use the same Pytorch Generator instance with a seed of 42.
+All random processes use the same PyTorch Generator instance with a seed of 42.
 The data is then augmented by perturbing the function values to create three versions with the noise levels mentioned in the scenario.
 Looping through each version, the training and testing subsets are randomly sampled to result in 80\% and 20\% of the original dataset respectively.
-Then the scaler is fitted on the training subset inputs.
-And then, both the training and testing inputs are transformed using the fitted scaler.
+Then the scaling function is fitted on the training subset inputs.
+And then, both the training and testing inputs are transformed using the fitted scaling function.
 Next, an instance of SpectralSVR is trained and tested.
@@
 Next the 5\% noise model is used to predict the antiderivative of a sine function.
+
+The kernel scaling hyperparameter sigma has the same value of 10 for all noise levels.
+This is because the inputs are all scaled to approximately have a standard deviation of one.
+The value itself is from the number of features which comes out to 100 total inputs to the LSSVR\@.
 
@@
 The R2 score of 0.5 means that the model predictions has roughly half the error the baseline would produce.
-Another observation is that the kernel scaling hyperparameter sigma has the same value the same for all noise levels since the inputs are all scaled to approximately have a standard deviation of one.
-The value itself is from the number of features which comes out to 100 total inputs to the LSSVR\@.
 
@@
     \midrule
-    5\%         & 0.78 & 0.89 & 0.51 & 0.96 & 0.28  \\
-    10\%        & 1.82 & 1.35 & 0.81 & 0.92 & 0.41  \\
-    50\%        & 9.34 & 3.06 & 2.25 & 0.62 & 0.91  \\
+    5\%         & 0.79 & 0.89 & 0.51 & 0.96 & 0.28  \\
+    10\%        & 1.80 & 1.34 & 0.80 & 0.92 & 0.40  \\
+    50\%        & 9.30 & 3.05 & 2.23 & 0.62 & 0.90  \\
     \bottomrule
@@
     10\%        & 0.08 & 0.29 & 0.23 & 0.92 & 0.55  \\
-    50\%        & 0.62 & 0.79 & 0.63 & 0.49 & 1.04  \\
+    50\%        & 0.62 & 0.79 & 0.63 & 0.49 & 1.05  \\
     \bottomrule
@@
     5\%         & 0.03 & 0.18 & 0.14 & 0.97 & 0.38  \\
-    10\%        & 0.07 & 0.27 & 0.22 & 0.92 & 0.53  \\
+    10\%        & 0.07 & 0.27 & 0.21 & 0.93 & 0.53  \\
     50\%        & 0.37 & 0.61 & 0.49 & 0.62 & 0.94  \\
@@
     \midrule
-    5\%         & 0.12  & 0.35 & 0.20 & 1.26  \\
-    10\%        & 0.75  & 0.87 & 0.30 & 1.26  \\
-    50\%        & 10.35 & 3.22 & 0.82 & 1.39  \\
+    5\%         & 0.09  & 0.29 & 0.16 & 1.18  \\
+    10\%        & 0.80  & 0.89 & 0.31 & 1.23  \\
+    50\%        & 10.33 & 3.21 & 0.83 & 1.44  \\
     \bottomrule
@@
     \midrule
-    5\%         & 0.01 & 0.07 & 0.06 & 0.24  \\
-    10\%        & 0.03 & 0.17 & 0.15 & 0.37  \\
-    50\%        & 0.41 & 0.64 & 0.57 & 1.66  \\
+    5\%         & 0.00 & 0.06 & 0.05 & 0.23  \\
+    10\%        & 0.03 & 0.18 & 0.15 & 0.36  \\
+    50\%        & 0.41 & 0.64 & 0.58 & 1.65  \\
     \bottomrule
@@
 
-The predictions of the exact equation is shown in \lccref{fig:exact_antiderivative}.
+The predictions of the exact equation is shown in \lccref{fig:antiderivative_exact}.
 Visually, we can see that as the noise level increases, the model predictions become worse.
@@
     \begin{adjustbox}{width=\linewidth}
-      \input{figures/exact_antiderivative_label.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:exact_antiderivative_label}
+      \input{figures/antiderivative_exact_input.pgf}
+    \end{adjustbox}
+    \caption{}\label{fig:antiderivative_exact_input}
   \end{subfigure}
@@
     \begin{adjustbox}{width=\linewidth}
-      \input{figures/exact_antiderivative_prediction.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:exact_antiderivative_prediction}
-  \end{subfigure}
-  \caption{(\subref{fig:exact_antiderivative_label}) The perturbed exact input function values from \lccref{eq:sine_derivative}.
-(\subref{fig:exact_antiderivative_prediction}) Prediction of antiderivative from the input function that was perturbed.}\label{fig:exact_antiderivative}
+      \input{figures/antiderivative_exact_prediction.pgf}
+    \end{adjustbox}
+    \caption{}\label{fig:antiderivative_exact_prediction}
+  \end{subfigure}
+  \caption{(\subref{fig:antiderivative_exact_label}) The perturbed exact input function values from \lccref{eq:sine_derivative}.\ (\subref{fig:antiderivative_exact_prediction}) Prediction of antiderivative from the input function that was perturbed.}\label{fig:antiderivative_exact}
 \end{figure}
@@
 The results of inverse prediction for all three noise levels are shown in \lccref{table:scenario_1_inv_spectral_metrics}.
-These metrics were computed after both the target and predicted input functions are scaled back using the same scalers they were scaled down with.
+These metrics were computed after both the target and predicted input functions are scaled back using the same scaling functions they were scaled down with.
 Because the scales of the input and output functions are different, the absolute metrics are much larger in these results compared to the forward problem results.
-For reference, the target input coefficents on average range from -695.65 to 694.9.
+For reference, the target input coefficients on average range from -695.65 to 694.9.
 The relative metrics show that for the lower noise levels, the accuracy is still relatively good.
@@
 \begin{figure}[H]
+  \begin{adjustwidth}{-0.1\linewidth}{-0.1\linewidth}
     \centering
     \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=1.2\linewidth}
+      \begin{adjustbox}{width=\linewidth}
         \input{figures/antiderivative_ci_5.pgf}
@@
     \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=1.2\linewidth}
+      \begin{adjustbox}{width=\linewidth}
         \input{figures/antiderivative_pm_5.pgf}
@@
     \end{subfigure}
-  \\[-0.7\baselineskip]
+    % \\[\baselineskip]
     \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=1.2\linewidth}
+      \begin{adjustbox}{width=\linewidth}
         \input{figures/antiderivative_ci_10.pgf}
@@
     \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=1.2\linewidth}
+      \begin{adjustbox}{width=\linewidth}
         \input{figures/antiderivative_pm_10.pgf}
@@
     \end{subfigure}
-  \\[-0.7\baselineskip]
+    \\[\baselineskip]
     \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=1.2\linewidth}
+      \begin{adjustbox}{width=\linewidth}
         \input{figures/antiderivative_ci_50.pgf}
@@
     \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=1.2\linewidth}
+      \begin{adjustbox}{width=\linewidth}
         \input{figures/antiderivative_pm_50.pgf}
@@
     \end{subfigure}
+  \end{adjustwidth}
   \caption{Correlation image (left column) and p-matrix (right column) for each model trained on a different noise level (row).
@@
 This means that the majority of contributions to each output coefficients come from the corresponding input coefficients of the same wave number.
-Our knowledge on how the simple derivative equation for Fourier series relate the coefficients of the derivative function and the antiderivative function aligns with the contributions shown by the p-matrices.
+Our knowledge on how the simple derivative equation for Fourier series relate the coefficients of the derivative function and the antiderivative function is shown in \lccref{eq:derivative_coeff}.
+This aligns with the contributions shown by the p-matrices.
 This confirms that the model is indeed learning the relations that is defined by the derivative equation.
+
+In summary, the model is able to learn the linear relationship defined by the derivative equation.
+This is true even for high noise levels.
+The model also learns the actual relationship between each wave number which is shown in the p-matrix.
+Inverse prediction of the input function is also successfully done for lower noise levels.
+At high noise levels, the noise overwhelms the model.
 
@@
 The functions are first preprocessed in order to format them into current and next values in time as discussed in \lccref{sec:data_transformation}.
+The sample pairs are first divided into two for the training and testing sets.
+Each function is then discretized into 200 time steps.
+Then, the features are put together as the coefficients of the solution and forcing term at the current time step.
+The labels are the solution at the next time step.
+Since there is too much data to fit into memory all at once at the end of this process, we randomly sample the feature and label pairs.
+This result in a maximum of 8000 samples for the training set and 2000 samples for the testing set.
+As mentioned in \lccref{sec:data_transformation}, the training features are used to fit a scaling function.
+And then, all features are scaled using the fitted scaling function.
+
 The coefficient value predictions are shown in \lccref{table:scenario_2_spectral_metrics}.
-The RBF kernel parameter computed from the data is once again the same for all versions of the dataset with a value of 10.
+The RBF kernel parameter computed from the data is once again the same for all versions of the dataset with a value of 5.66.
 The testing metrics show that the performance of the model vary with the viscosity value \(\nu \).
-Starting with the inviscid Burgers' equation, with \(\nu=0\), the model performs relatively well and close to the best result with \(\nu=0.01\).
+Starting with the inviscid Burgers' equation, with \(\nu=0\), the model performs the best with a close second from the model for the \(\nu = 0.01 \) dataset version.
 The function value evaluated from the predictions is shown in \lccref{table:scenario_2_function_metrics}.
-The metrics across the board shows that the function value relative metrics are worse compared to the coefficients.
+The metrics across the board shows that the function value relative metrics are slightly better compared to the coefficients.
 Comparing the absolute metrics for the same table, we see the same general trend that the higher viscosity show the model performing worse.
@@
 \begin{table}[H]
-  \caption{Performance metrics of coefficient prediction of next time step in scenario 2 by noise level.}\label{table:scenario_2_spectral_metrics}
+  \caption{Performance metrics of coefficient prediction of next time step in scenario 2 by viscosity.}\label{table:scenario_2_spectral_metrics}
   \centering
@@
     \toprule
-    \(\nu\) & MSE  & RMSE & MAE  & R2   & sMAPE \\
+    \(\nu \) & MSE      & RMSE     & MAE      & R2   & sMAPE \\
     \midrule
-    0.0     & 0.01 & 0.09 & 0.06 & 0.87 & 0.60  \\
-    0.01    & 0.01 & 0.08 & 0.06 & 0.90 & 0.56  \\
-    0.1     & 0.03 & 0.17 & 0.13 & 0.49 & 1.09  \\
+    0.0      & 3.46e-04 & 1.86e-02 & 1.24e-02 & 0.79 & 0.65  \\
+    0.01     & 3.56e-04 & 1.89e-02 & 1.27e-02 & 0.78 & 0.67  \\
+    0.1      & 9.17e-04 & 3.03e-02 & 2.32e-02 & 0.46 & 1.08  \\
     \bottomrule
@@
 \begin{table}[H]
-  \caption{Performance metrics of function values evaluated from coefficient prediction of next time step in scenario 2 by noise level.}\label{table:scenario_2_function_metrics}
+  \caption{Performance metrics of function values evaluated from coefficient prediction of next time step in scenario 2 by viscosity.}\label{table:scenario_2_function_metrics}
   \centering
@@
     \toprule
-    \(\nu\) & MSE      & RMSE & MAE  & R2   & sMAPE \\
+    \(\nu \) & MSE      & RMSE     & MAE      & R2   & sMAPE \\
     \midrule
-    0.0     & 6.36e-04 & 0.03 & 0.02 & 0.85 & 0.66  \\
-    0.01    & 5.19e-04 & 0.02 & 0.02 & 0.88 & 0.62  \\
-    0.1     & 2.28e-03 & 0.05 & 0.04 & 0.45 & 1.13  \\
+    0.0      & 5.58e-05 & 7.47e-03 & 5.89e-03 & 0.82 & 0.70  \\
+    0.01     & 5.74e-05 & 7.58e-03 & 6.01e-03 & 0.81 & 0.71  \\
+    0.1      & 1.58e-04 & 1.26e-02 & 9.98e-03 & 0.51 & 1.04  \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+The testing results are complimented with a rollout experiment.
+The results from the rollout are shown in \lccref{fig:scenario_2_rollout}.
+The rollout starts from time \(t=0\).
+In all the plots, this is at the bottom.
+We have included this initial condition in the plots.
+From this initial condition in combination with the forcing term at the initial time step, the model predicts the first time step solution.
+The model then uses the predicted solution combined with the corresponding forcing term to predict the second time step.
+To see how well the model is performing relative to the actual target values, we compute the difference between the two as shown in \lccrefs{fig:sc2_rollout_diff_0.0,fig:sc2_rollout_diff_0.01,fig:sc2_rollout_diff_0.1}.
+Observe that errors are introduced relatively early around time \(t=1\).
+However, the model rollout stays stable until the end despite this error.
+This results in the model being able to finish the rollout for this sample.
+\begin{figure}[H]
+  \centering
+  \begin{adjustwidth}{-0.1\linewidth}{-0.1\linewidth}
+    \begin{subfigure}{0.33\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/burgers_rollout_target_0.0.pgf}
+      \end{adjustbox}
+      \caption{The target for \(\nu=0.0\)}\label{fig:sc2_rollout_target_0.0}
+    \end{subfigure}
+    \begin{subfigure}{0.33\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/burgers_rollout_pred_0.0.pgf}
+      \end{adjustbox}
+      \caption{The prediction for \(\nu=0.0\)}\label{fig:sc2_rollout_pred_0.0}
+    \end{subfigure}
+    \begin{subfigure}{0.32\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/burgers_rollout_diff_0.0.pgf}
+      \end{adjustbox}
+      \caption{The difference for \(\nu=0.0\)}\label{fig:sc2_rollout_diff_0.0}
+    \end{subfigure}
+    \\[0.7\baselineskip]
+    \begin{subfigure}{0.33\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/burgers_rollout_target_0.01.pgf}
+      \end{adjustbox}
+      \caption{The target for \(\nu=0.01\)}\label{fig:sc2_rollout_target_0.01}
+    \end{subfigure}
+    \begin{subfigure}{0.33\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/burgers_rollout_pred_0.01.pgf}
+      \end{adjustbox}
+      \caption{The prediction for \(\nu=0.01\)}\label{fig:sc2_rollout_pred_0.01}
+    \end{subfigure}
+    \begin{subfigure}{0.32\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/burgers_rollout_diff_0.01.pgf}
+      \end{adjustbox}
+      \caption{The difference for \(\nu=0.01\)}\label{fig:sc2_rollout_diff_0.01}
+    \end{subfigure}
+    \\[0.7\baselineskip]
+    \begin{subfigure}{0.33\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/burgers_rollout_target_0.1.pgf}
+      \end{adjustbox}
+      \caption{The target for \(\nu=0.1\)}\label{fig:sc2_rollout_target_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.33\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/burgers_rollout_pred_0.1.pgf}
+      \end{adjustbox}
+      \caption{The prediction for \(\nu=0.1\)}\label{fig:sc2_rollout_pred_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.32\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/burgers_rollout_diff_0.1.pgf}
+      \end{adjustbox}
+      \caption{The difference for \(\nu=0.1\)}\label{fig:sc2_rollout_diff_0.1}
+    \end{subfigure}
+    % \\[0.7\baselineskip]
+  \end{adjustwidth}
+  \caption{The rollout predictions for one of the test function. The difference is calculated as the targets subtracted by the predictions.}\label{fig:scenario_2_rollout}
+\end{figure}
+
+Another observation we can see is that the difference between the target and rollout predictions is much more pronounced for lower viscosity values.
+This result is aligned with metrics shown in \lccrefs{table:scenario_2_rollout_spectral_metrics,table:scenario_2_rollout_function_metrics}.
+The absolute metrics show that the models are performing several times worse in rollout compared to the single time step tests shown in \lccrefs{table:scenario_2_spectral_metrics,table:scenario_2_function_metrics}.
+This seems to be the same challenge that traditional solvers also face with the shocks that may be present with lower viscosity values.
+This means that for rollout scenarios, the model has a much harder time with lower viscosity values.
+\begin{table}[H]
+  \caption{Performance metrics of coefficient rollout in scenario 2 by viscosity.}\label{table:scenario_2_rollout_spectral_metrics}
+  \centering
+  \begin{tabular}{lrrrr}
+    \toprule
+    \(\nu \) & MSE      & RMSE     & MAE      & sMAPE \\
+    \midrule
+    0.0      & 2.91e-01 & 5.40e-01 & 4.07e-01 & 0.90  \\
+    0.01     & 1.61e-01 & 4.01e-01 & 2.86e-01 & 0.75  \\
+    0.1      & 1.70e-01 & 4.12e-01 & 3.02e-01 & 0.81  \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+\begin{table}[H]
+  \caption{Performance metrics of function values evaluated from coefficient rollout in scenario 2 by viscosity.}\label{table:scenario_2_rollout_function_metrics}
+  \centering
+  \begin{tabular}{lrrrr}
+    \toprule
+    \(\nu \) & MSE      & RMSE     & MAE      & sMAPE \\
+    \midrule
+    0.0      & 5.81e-02 & 2.41e-01 & 1.89e-01 & 1.04  \\
+    0.01     & 3.17e-02 & 1.78e-01 & 1.40e-01 & 0.94  \\
+    0.1      & 2.91e-02 & 1.71e-01 & 1.33e-01 & 0.92  \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+The exact function \cref{eq:burgers_exact_solution} is computed for each viscosity value.
+The discrete Fourier transform of the values are then used for doing rollout with the model.
+For the forcing term, we just use a constant function with a value of zero.
+The rollout predictions are shown in \lccref{fig:scenario_2_interpretation}.
+The model is not successful in the rollout for the inviscid equation and for the viscosity of \(\nu=0.01\).
+Both of these cases, the model produces too much error that the original function is no longer recognizable in the predictions.
+For the higher viscosity value of \(\nu=0.1\) the rollout produces a recognizable prediction.
+The error stays to about half the maximum function value.
+We do see some more noticeable error in the flatter parts of the function.
+The error also take a very similar shape across the different viscosity values.
+Since we essentially used the same solutions for training the model for each viscosity, the similarity in error means that it can be alleviated with more diverse training samples.
+The error for the flatter functions may also be alleviated by including similar flatter functions during training.
+\begin{figure}[H]
+  \centering
+  \begin{adjustwidth}{-0.1\linewidth}{-0.1\linewidth}
+    \begin{subfigure}{0.33\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/burgers_exact_target_0.0.pgf}
+      \end{adjustbox}
+      \caption{The target for \(\nu=0.0\)}\label{fig:sc2_exact_target_0.0}
+    \end{subfigure}
+    \begin{subfigure}{0.33\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/burgers_exact_pred_0.0.pgf}
+      \end{adjustbox}
+      \caption{The prediction for \(\nu=0.0\)}\label{fig:sc2_exact_pred_0.0}
+    \end{subfigure}
+    \begin{subfigure}{0.32\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/burgers_exact_diff_0.0.pgf}
+      \end{adjustbox}
+      \caption{The difference for \(\nu=0.0\)}\label{fig:sc2_exact_diff_0.0}
+    \end{subfigure}
+    \\[0.7\baselineskip]
+    \begin{subfigure}{0.33\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/burgers_exact_target_0.01.pgf}
+      \end{adjustbox}
+      \caption{The target for \(\nu=0.01\)}\label{fig:sc2_exact_target_0.01}
+    \end{subfigure}
+    \begin{subfigure}{0.33\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/burgers_exact_pred_0.01.pgf}
+      \end{adjustbox}
+      \caption{The prediction for \(\nu=0.01\)}\label{fig:sc2_exact_pred_0.01}
+    \end{subfigure}
+    \begin{subfigure}{0.32\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/burgers_exact_diff_0.01.pgf}
+      \end{adjustbox}
+      \caption{The difference for \(\nu=0.01\)}\label{fig:sc2_exact_diff_0.01}
+    \end{subfigure}
+    \\[0.7\baselineskip]
+    \begin{subfigure}{0.33\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/burgers_exact_target_0.1.pgf}
+      \end{adjustbox}
+      \caption{The target for \(\nu=0.1\)}\label{fig:sc2_exact_target_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.33\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/burgers_exact_pred_0.1.pgf}
+      \end{adjustbox}
+      \caption{The prediction for \(\nu=0.1\)}\label{fig:sc2_exact_pred_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.32\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/burgers_exact_diff_0.1.pgf}
+      \end{adjustbox}
+      \caption{The difference for \(\nu=0.1\)}\label{fig:sc2_exact_diff_0.1}
+    \end{subfigure}
+    % \\[0.7\baselineskip]
+  \end{adjustwidth}
+  \caption{The rollout predictions for one of the exact function in \lccref{eq:burgers_exact_solution}.
+The difference is calculated as the targets subtracted by the predictions.}\label{fig:scenario_2_exact}
+\end{figure}
+
+The metrics for the exact rollout further solidifies our observations from the plots.
+The metrics are shown in \lccrefs{table:scenario_2_exact_spectral_metrics,table:scenario_2_exact_function_metrics}.
+While the absolute metrics are low, this is mostly due to the maximum function values of the exact function also being pretty low.
+The relative metric sMAPE shows a much clearer picture.
+As expected, the inviscid prediction is pretty much just error.
+The next result, for viscosity \(\nu=0.01\), is better.
+This seems to be from the slight conformance to the target.
+The plots for this viscosity show that the prediction contains \enquote{shapes} similar to the target despite the scale not being close to the target.
+Finally, the highest viscosity level results show the best performance.
+Despite the good performance in the higher detail areas of the function, the error from the flatter areas overwhelm the metrics due to its larger portion of the function.
+\begin{table}[H]
+  \caption{Performance metrics of coefficient rollout of exact solution in scenario 2 by viscosity.}\label{table:scenario_2_exact_spectral_metrics}
+  \centering
+  \begin{tabular}{lrrrr}
+    \toprule
+    \(\nu \) & MSE      & RMSE     & MAE      & sMAPE \\
+    \midrule
+    0.0      & 2.16e-02 & 1.47e-01 & 1.08e-01 & 2.00  \\
+    0.01     & 1.32e-02 & 1.15e-01 & 6.37e-02 & 1.58  \\
+    0.1      & 2.83e-03 & 5.32e-02 & 4.00e-02 & 1.50  \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+\begin{table}[H]
+  \caption{Performance metrics of function values evaluated from coefficient rollout of exact solution in scenario 2 by viscosity.}\label{table:scenario_2_exact_function_metrics}
+  \centering
+  \begin{tabular}{lrrrr}
+    \toprule
+    \(\nu \) & MSE      & RMSE     & MAE      & sMAPE \\
+    \midrule
+    0.0      & 4.16e-03 & 6.45e-02 & 4.56e-02 & 2.00  \\
+    0.01     & 3.23e-03 & 5.68e-02 & 4.94e-02 & 1.73  \\
+    0.1      & 3.86e-04 & 1.97e-02 & 1.62e-02 & 1.47  \\
     \bottomrule
@@
 The highest and visually most sorted values are from the forcing term portion of the inputs.
-A weaker correlation is still present of the viscosity of \(\nu=0.01\).
-However, once we get to the highest viscosity case, we see a seemingly random arrangement of the correlation image values.
+Different wave numbers in the inputs are also sorted differently, this indicates an inverse correlation.
+For a higher viscosity of \(\nu=0.01\), a weaker correlation is still present.
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/burgers_ci_0.0.pgf}
+    \end{adjustbox}
+    \caption{Correlation image \(\nu=0.0\).}\label{fig:sc2_ci_0.0}
+  \end{subfigure}
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/burgers_pm_0.0.pgf}
+    \end{adjustbox}
+    \caption{The p-matrix for \(\nu=0.0\).}\label{fig:sc2_pm_0.0}
+  \end{subfigure}
+  % \\[-0.7\baselineskip]
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/burgers_ci_0.01.pgf}
+    \end{adjustbox}
+    \caption{Correlation image \(\nu=0.01\).}\label{fig:sc2_ci_0.01}
+  \end{subfigure}
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/burgers_pm_0.01.pgf}
+    \end{adjustbox}
+    \caption{The p-matrix for \(\nu=0.01\).}\label{fig:sc2_pm_0.01}
+  \end{subfigure}
+  % \\[-0.7\baselineskip]
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/burgers_ci_0.1.pgf}
+    \end{adjustbox}
+    \caption{Correlation image \(\nu=0.1\).}\label{fig:sc2_ci_0.1}
+  \end{subfigure}
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/burgers_pm_0.1.pgf}
+    \end{adjustbox}
+    \caption{The p-matrix for \(\nu=0.1\).}\label{fig:sc2_pm_0.1}
+  \end{subfigure}
+  \caption{Correlation image (left column) and p-matrix (right column) for each model trained on a different viscosity (row).
+The correlation image was sorted same order the values of the real component of wave number \(k=4\) were sorted in descending order.}\label{fig:scenario_2_interpretation}
+\end{figure}
+
+Once we get to the highest viscosity, while the order is still present, we see a more random arrangement of the correlation image values.
 This observation and the lower scores can both be explained by the level of temporal discretization.
@@
 The issue arises in stiff differential equations.
-This term describes the presence of a rapidly varying component.
+Stiff differential equations refer to the presence of a rapidly varying component.
 We can see that the larger amplitudes of high frequency components in the forcing term to represent the rapidly varying components as shown in \lccrefs{fig:burgers_forcing_0.0,fig:burgers_forcing_0.01,fig:burgers_forcing_0.1}.
-Traditionally, stiff equations would require specific solvers purpose built to efficiently solve the problem.
-Otherwise, as with our method, the solving process would require much finer time steps.
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_ci_0.0.pgf}
-    \end{adjustbox}
-    \caption{Correlation image \(\nu=0.0\).}\label{fig:sc2_ci_0.0}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_pm_0.0.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix for \(\nu=0.0\).}\label{fig:sc2_pm_0.0}
-  \end{subfigure}
-  % \\[-0.7\baselineskip]
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_ci_0.01.pgf}
-    \end{adjustbox}
-    \caption{Correlation image \(\nu=0.01\).}\label{fig:sc2_ci_0.01}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_pm_0.01.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix for \(\nu=0.01\).}\label{fig:sc2_pm_0.01}
-  \end{subfigure}
-  % \\[-0.7\baselineskip]
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_ci_0.1.pgf}
-    \end{adjustbox}
-    \caption{Correlation image \(\nu=0.1\).}\label{fig:sc2_ci_0.1}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_pm_0.1.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix for \(\nu=0.1\).}\label{fig:sc2_pm_0.1}
-  \end{subfigure}
-  \caption{Correlation image (left column) and p-matrix (right column) for each model trained on a different noise level (row).
-The correlation image was sorted same order the values of the real component of wave number \(k=4\) were sorted in descending order.}\label{fig:scenario_2_interpretation}
-\end{figure}
+Traditionally, stiff equations would require specific numerical methods purpose built to efficiently solve the problem.
+Otherwise, the using a solver like FDM would require much finer time steps than the one we are using here.
 
@@
 However, there is a noticeable contribution from other wave numbers too unlike the antiderivative case.
+The biggest contribution from the current solution is the constant/bias term.
 For higher viscosity values, notice that the contribution of the previous solution increases.
@@
 
+To summarize, Low viscosity values are a challenge to the model as with traditional methods.
+Despite that, this scenario confirms the model's ability to learn the nonlinear relationship defined by the Burgers' equation.
+The model is also able to stay stable with a relatively large time step.
+This concludes the synthetic data portion of the study.
+
 \subsection{Scenario 3}
-\noindent
+\noindent This final scenario tests the model on a much more complex dataset with much more immediate implications for the real world.

### 2025-01-06 skripsi/chapter1.tex
Finish ch4, fix some problems with

@@
 Crowd dynamics is another field where researchers have found it useful to model using PDEs \autocite{mukherjeeLagrangianApproachModeling2015,hughesFlowLargeCrowds2000}.
-These are used to model dynamics such as shock-waves, pathing, and crowd flow as a whole.
-There are a variety of applications, ranging from bird flocks, pedestrian crowds, to robotic swarms \autocite{gongCrowdDynamicsModeling2023}.
+PDEs have a variety of applications, ranging from bird flocks, pedestrian crowds, to robotic swarms \autocite{gongCrowdDynamicsModeling2023}.
 
@@
 This means there are strong guarantees for convergence, generalization, and complexity.
-Another formulation called Least Squares Support Vector Machines (LSSVM) reformulates the problem as a linear system \autocite{suykensLeastSquaresSupport2005}.
+Another formulation called Least-Squares Support Vector Machines (LSSVM) reformulates the problem as a linear system \autocite{suykensLeastSquaresSupport2005}.
 This leads to an easier problem that can be computed faster by well established algorithms like the many implementations of least squares solvers.
@@
 \section{Aims}\label{sec:aims}
-\noindent Based on the stated problems in \lccref{sec:problem_statement}, this study aims to acomplish the following:
+\noindent Based on the stated problems in \lccref{sec:problem_statement}, this study aims to accomplish the following:
 \begin{enumerate}
-    \item The design and implementation of a computational model that maps coefficients in the spectral domain using Least Squares Support Vector Regression (LSSVR).
+    \item The design and implementation of a computational model that maps coefficients in the spectral domain using Least-Squares Support Vector Regression (LSSVR).
     \item Proof of the model's learning ability using three different problems.
@@
     \item The basis functions are limited to Fourier basis.
-    \item Modeled fields are compact or dense meaning not sparse. Sparse observations or other data are assimilated using other methods.
+    \item Modeled fields are compact or dense meaning not sparse. If this is not true, such as sparse observations, the data would need to be assimilated to create a dense field.
 \end{enumerate}
 
-\section{Sistematika Penulisan}
+% \section{Sistematika Penulisan}
 % \noindent Bagian ini adalah penutup Bab I yang menyampaikan  secara ringkas isi setiap  bab.

### 2025-01-06 skripsi/chapter2.tex
Finish ch4, fix some problems with

@@
 \begin{align}
-  c_k=\sum_{n=0}^{N-1} f_n e^{-i2\pi kn/N} \label{eq:discrete_fourier_transform}\\
+  c_k=\sum_{n=0}^{N-1} f_n e^{-i2\pi kn/N} \label{eq:discrete_fourier_transform} \\
   f_n=\sum_{k=0}^{N-1} c_k e^{i2\pi kn/N} \label{eq:inverse_discrete_fourier_transform}
@@
     \pdv{L}{b} = 0 \rightarrow          & \sum_{k=1}^{n}\alpha_{k} = 0                                     \\
-    \pdv{L}{e_{k}} = 0 \rightarrow & \alpha_{k} = C e_{k} & \qquad k=1,\dots,n\\
-    \pdv{L}{\alpha_{k}} = 0 \rightarrow & W^{\intercal}\vb{x}_{k}+b+e_{k} - y_{k} = 0 & \qquad k=1,\dots,n\\
+    \pdv{L}{e_{k}} = 0 \rightarrow      & \alpha_{k} = C e_{k}                        & \qquad k=1,\dots,n \\
+    \pdv{L}{\alpha_{k}} = 0 \rightarrow & W^{\intercal}\vb{x}_{k}+b+e_{k} - y_{k} = 0 & \qquad k=1,\dots,n \\
   \end{split}
@@
 
-In this exmple we will be using the function $2x^2+4$. The values of this function can be seen in Table \ref{table:1}.
+In this example we will be using the function \(2x^2+4\). The values of this function can be seen in \lccref{table:1}.
 

### 2025-01-06 skripsi/chapter3.tex
rename files to english versions, add data figures for antiderivative, add content on data and computational model, edit parts of ch 1 & 3
finish ch4 computational model, start implementation
finish second scenario, fix figures and spelling ch4, start third scenario
Finish ch4, fix some problems with

--- 2024-09-11 skripsi/bab3.tex
@@
 % !TEX root = ./skripsi.tex
-\chapter{Research Methodology}\label{sec:research_methodology}
+\chapter{RESEARCH METHODOLOGY}\label{sec:research_methodology}
 
@@
             In this phase, relevant literature of related works and other supporting materials will be reviewed to lay the groundwork of this study.
-Specifically, the literature review will encompass partial differential equations and their real world associations, traditional methods employed to solve them, systems with partially known or unknown governing equations, machine learning approaches to the problem, least squares support vector machines, performance metrics, and tools that will be used such as the PyTorch library.
+Specifically, the literature review will encompass partial differential equations and their real world associations, traditional methods employed to solve them, systems with partially known or unknown governing equations, machine learning approaches to the problem, least-squares support vector machines, performance metrics and tools that will be used such as the PyTorch library.
 
@@
 
-            After the computational model design is completed, the model is implemented in the Python Language using the Pytorch library as a core component.
+            After the computational model design is completed, the model is implemented in the Python Language using the PyTorch library as a core component.
 Implementation of the computational model is done using an iterative software development model.
@@
 
-\section{Computational Model Implementation Method}
+\section{Computational Model Implementation Method}\label{sec:development_method}
 \noindent Implementation of the computational model follows an iterative development model.
@@
             \begin{itemize}
-                  \item Intel i5-8300H
+                  \item Intel i5{-}8300H
                   \item 16 Gigabytes RAM

### 2025-01-06 skripsi/chapter4.tex
Finish ch4, fix some problems with

@@
 
-% TODO: add figures and tables of generated data and some intermediate steps.
 \begin{figure}[H]
@@
   import xarray as xr
-  xr.open_zarr(
+  ds = xr.open_zarr(
       "DATASET_ADDRESS",
@@
   \caption{Example of using Xarray to access a publicly accessible Zarr dataset hosted on Google Cloud Storage Bucket.}\label{fig:access_remote_zarr}
+\end{figure}
+
+The specific dataset resolution we use is 64 by 32 representing longitude and latitude respectively.
+The ERA5 reanalysis dataset is hosted at the following URL\@: \url{gs://weatherbench2/datasets/era5/1959-2023_01_10-6h-64x32_equiangular_conservative.zarr}.
+The corresponding climatology is hosted at \url{gs://weatherbench2/datasets/era5-hourly-climatology/1990-2019_6h_64x32_equiangular_conservative.zarr}.
+The climatology is the average for hours 0, 6, 12, and 18 for each day of the year from 1990 until 2019.
+This average helps in defining the expected state of the weather at specific points in time based on the historical averages for that time of day and year.
+
+For the reanalysis dataset, we limit the time range to the years 1995{-}2013 for training and 2020{-}2022 for testing.
+The specific time ranges for training are chosen to balance the diversity within the data and capacity of the machine the processing will be done on.
+The testing set time range was chosen to be as close to those shown on the WeatherBench 2 website.
+The filter for time and variables is shown in \lccref{fig:wb2_retrieval}.
+The reason for the different time ranges between training and testing is to reduce the risk of information leakage accross the training and testing sets.
+This ensures that the testing scores we measure will be for the most part from the generalization that model learned during training.
+The filter is an array the length of the number of samples.
+The array values are all the datetime values that the year ranges are true for.
+This results in an array of boolean values.
+Using this boolean filter we can index the data so that we get the filtered data.
+Then, the filtered data is saved locally so that we can access it in a more performant way.
+The encoding chunks may need to be removed in order to evade the Xarray library from mistakenly persisting the remote encoding after slicing data \autocite{ianZarrEncodingAttributes}.
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+  years_idx = ds['time.year']
+  data_idx = (years_idx > START_YEAR) & (years_idx < END_YEAR)
+  da_orig = ds['2m_temperature'][data_idx]
+  # save locally
+  da_orig.encoding.pop('chunks',None)
+  da_orig.to_zarr(DATA_FILENAME, mode='w')
+  # open local version
+  da = xr.open_zarr(DATA_FILENAME)
+  \end{lstlisting}
+  \caption{Example of filtering of Xarray dataset by year and variable. The data is saved and then loaded locally.}\label{fig:wb2_retrieval}
 \end{figure}
@@
 This is the air temperature 2 meters above the surface be it land, sea, or inland water.
-This variable is in units of kelvin.
-The values of this variable is obtained by interpolating between the model values at the surface and the lowest model vertical level.
-We also limit the time range to ...
-An example of the data that was retrieved can be seen in .
-% TODO: talk about selecting the time here
-% ECMWF description
-% - Role
-% - legitimacy
-% - Weatherbench2
-% data description
-% - data assimilation, maybe reference a general description
-% - variables
-% - dimensions/coordinates (time, spatial) and resolution in each
-% - climatology
+This variable is in units of kelvin (K).
+Vertically, the values of this variable is obtained by interpolating between the model values at the surface and the lowest model vertical level.
+An example of the data that was retrieved can be seen in \lccref{fig:wb2_data}.
+The data shown is in the equiangular projection.
+This means that towards the poles, the shapes become more distorted.
+While this is not the most ideal way to represent the data, using the data in this way adds to the challenge of how the model can adapt to the use of suboptimal configurations in the data.
+To compute the anomaly, we can simply subtract the current state in \lccref{fig:wb2_train_data} by the climatology in \lccref{fig:wb2_clim_data} resulting in \lccref{fig:wb2_train_anomaly}.
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/wb2_train_data.pgf}
+    \end{adjustbox}
+    \caption{}\label{fig:wb2_train_data}
+  \end{subfigure}
+  \begin{subfigure}{\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/wb2_clim_data.pgf}
+    \end{adjustbox}
+    \caption{}\label{fig:wb2_clim_data}
+  \end{subfigure}
+  \begin{subfigure}{\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/wb2_train_anomaly.pgf}
+    \end{adjustbox}
+    \caption{}\label{fig:wb2_train_anomaly}
+  \end{subfigure}
+  \caption{Data retrieved:(\subref{fig:wb2_train_data}) 2-meter temperature at January 1, 1995 6:00 UTC\@.
+(\subref{fig:wb2_train_anomaly}) Anomaly for 2-meter temperature at January 1, 1995 6:00 UTC\@.
+(\subref{fig:wb2_clim_data}) 2-meter temperature climatology for the first day of the year at hour 6 UTC\@.}\label{fig:wb2_data}
+\end{figure}
+
+After filtering, our training set has the dimensions of 27760 time steps, 64 longitude, and 32 latitude.
+The testing set on the other hand has 4384 time steps and the same values for the other two dimensions.
+For uses, such as a validation set during hyperparameter optimization, one can use a subset of the training set.
+The dimensions of the climatology are 4 for hour (0, 6, 12,\& 18), 366 for day of year, 64 for longitude, and 32 for latitude.
 
@@
 Once the dataset and filters are determined, the retrieval process starts by accessing the dataset using the \emph{Xarray} library \autocite{hoyer2017xarray,hoyerXarray2024}.
-The filters are applied as in ....
-% TODO: add figure for code of the filtering process and local save process
-Finally, the filtered version is stored locally. The local dataset is also stored in the \emph{Zarr} format.
+The filters are applied as in \lccref{fig:wb2_retrieval}.
+Finally, the filtered version is stored locally.
+The local dataset is also stored in the \emph{Zarr} format.
 
@@
 
-% TODO: decide if hyperparameter selection is needed and explain why or why not.
-Maybe hyperparameter selection is done in a phase after the model evaluation with a decision between repeating model training with different hyperparameters or keeping the trained model.
-Next, the selection of hyperparameters is done to optimize the model further.
-As previously mentioned, the hyperparameters are the regularization constant \(C \) and kernel functions including the kernel function parameters.
+For our study, we choose to not optimize the hyperparameters to focus on the broad performance with default hyperparameter values.
+The scaling parameter of the RBF kernel is computed from the training features.
+This is computed as the square root of the sum of feature variances.
+The regularization parameter used will be a default value of 1.
+Using the same values allow for easier comparisons for comparable results.
 
@@
 Similar to how subtraction is just a modification of the addition operation, the integral or antiderivative operator is also implemented simply by changing the operation with the term multiplier from multiplication to division.
-% TODO: change the reference to specific equations for calculus in spectral domain
+% TODO: change the reference to specific equations for calculus in spectral domain in ch2
 
@@
 The first step is to convert the testing input into real representations and then predicting the output function.
-The predicted output are then compared to the testing outputs using many metrics including RMSE, MSE, MAE, R2, SMAPE, RRSE, and the number of Nan values present in the predicted output.
+The predicted output are then compared to the testing outputs using many metrics including RMSE, MSE, MAE, R\textsuperscript{2}, SMAPE, RRSE, and the number of Nan values present in the predicted output.
 The same comparison process is carried out again for the function values which are evaluated at the specified resolution.
@@
     \toprule
-    Noise level & MSE   & RMSE & MAE  & R2   & sMAPE \\
+    Noise level & MSE   & RMSE & MAE  & R\textsuperscript{2}   & sMAPE \\
     \midrule
@@
 \Cref{table:scenario_1_spectral_metrics} shows that the model is able to generalize from the training data and learn the simple linear antiderivative operator.
-Focusing on the coefficient of determination (R2) scores, we can see that the model is off by 0.04 to the perfect score of 1.0 for the lowest noise level.
+Focusing on the coefficient of determination (R\textsuperscript{2}) scores, we can see that the model is off by 0.04 to the perfect score of 1.0 for the lowest noise level.
 While increasing noise levels does degrade the performance, this is partly due to the target values also having been perturbed.
@@
 The higher noise levels shows that the model is still relatively accurate.
-Looking at the R2 score for the 50\% noise level, the model is more accurate than a baseline mean value model.
-The R2 score of 0.5 means that the model predictions has roughly half the error the baseline would produce.
+Looking at the R\textsuperscript{2} score for the 50\% noise level, the model is more accurate than a baseline mean value model.
+The R\textsuperscript{2} score of 0.5 means that the model predictions has roughly half the error the baseline would produce.
 
@@
     \toprule
-    Noise level & MSE  & RMSE & MAE  & R2   & sMAPE \\
+    Noise level & MSE  & RMSE & MAE  & R\textsuperscript{2}   & sMAPE \\
     \midrule
@@
 The function values are also evaluated and the values of the metrics between the noisy targets and predictions are shown in \lccref{table:scenario_1_function_metrics}.
-While the relative metrics R2 and sMAPE stay close to the values we obtained for the coefficients themselves, since the metrics are now being computed in the physical domain, the scales have changed and because of that the values of the absolute metrics now reflect the change in scale.
+While the relative metrics R\textsuperscript{2} and sMAPE stay close to the values we obtained for the coefficients themselves, since the metrics are now being computed in the physical domain, the scales have changed and because of that the values of the absolute metrics now reflect the change in scale.
 For reference, the scale of the target coefficient values for the 50\% noise level dataset in their real representation can range on average from -13.54 to 13.6 across the entire dataset.
@@
   \end{subfigure}
-  \caption{(\subref{fig:antiderivative_exact_label}) The perturbed exact input function values from \lccref{eq:sine_derivative}.\ (\subref{fig:antiderivative_exact_prediction}) Prediction of antiderivative from the input function that was perturbed.}\label{fig:antiderivative_exact}
+  \caption{(\subref{fig:antiderivative_exact_input}) The perturbed exact input function values from \lccref{eq:sine_derivative}.\ (\subref{fig:antiderivative_exact_prediction}) Prediction of antiderivative from the input function that was perturbed.}\label{fig:antiderivative_exact}
 \end{figure}
@@
     \toprule
-    Noise level & MSE      & RMSE   & MAE    & R2    & sMAPE \\
+    Noise level & MSE      & RMSE   & MAE    & R\textsuperscript{2}    & sMAPE \\
     \midrule
@@
 \begin{figure}[H]
-  \begin{adjustwidth}{-0.1\linewidth}{-0.1\linewidth}
+  \begin{adjustwidth}{-0.05\linewidth}{-0.05\linewidth}
     \centering
@@
     \end{subfigure}
-    \\[\baselineskip]
+    % \\[\baselineskip]
     \begin{subfigure}{0.49\linewidth}
@@
     \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & R2   & sMAPE \\
+    \(\nu \) & MSE      & RMSE     & MAE      & R\textsuperscript{2}   & sMAPE \\
     \midrule
@@
   \caption{Correlation image (left column) and p-matrix (right column) for each model trained on a different viscosity (row).
-The correlation image was sorted same order the values of the real component of wave number \(k=4\) were sorted in descending order.}\label{fig:scenario_2_interpretation}
+The correlation image was sorted same order the values of the real component of wave number \(k=2\) were sorted in descending order.}\label{fig:scenario_2_interpretation}
 \end{figure}
@@
 \subsection{Scenario 3}
-\noindent This final scenario tests the model on a much more complex dataset with much more immediate implications for the real world.
+\noindent This final scenario tests the model on a much more complex dataset.
+As said previously, this dataset, which is computed using real observations of Earth's weather system, will be used to represent the model learning a very complex system with many unknown contributing variables.
+For our case, this means the data used will be limited to the 2-meter temperature.
+The anomaly is computed by subtracting the climatology from the corresponding day of years and hours of the atmospheric state.
+For example, the temperature on the 6\textsuperscript{th} of January 1998 at 18:00 UTC is subtracted with the average temperature for the 6\textsuperscript{th} day of the year at 18:00 hour UTC\@.
+For any anomaly predictions, the corresponding atmospheric state can simply be computed as the inverse process described before by adding the climatology to the predicted anomaly.
+
+The preprocessing of the data is carried out in the same manner as the Burgers' equation experiments.
+The difference being that for the features we only include the current anomaly of the atmosphere and there are no forcing terms.
+The targets are the future anomaly of the atmosphere.
+The reason for choosing to train and predict the anomaly instead of the state valued themselves is to avoid the model from just learning the obvious periodicity that exists in weather such as the day-night cycle or the seasons.
+Next, Both the current anomaly and future anomaly are Fourier transformed to their 2-dimensional coefficients.
+This process is done for both the training and testing set.
+Once the features for both are processed, we fit the standard scaling function on the training features.
+Using this fitted scaling function, both the training and testing features are scaled to a mean of 0 and standard deviation of approximately 1.
+
+The testing results are shown in \lccrefs{table:sc3_test_anomaly_metrics,table:sc3_test_state_metrics}.
+To put the absolute metrics into context, the median test state coefficient' maximum absolute value is \num{569364.25}.
+With this information, an RMSE value of 64.72 is relatively low error.
+The relative metric sMAPE also agrees with this, with a value of 0.76.
+The function values show that the model on average has an error of around 2 degrees kelvin or Celsius.
+This is again relatively small for the range of temperatures on Earth which span roughly 120 degrees kelvin across the historical maxima and minima.
+From existing knowledge of the problem, we know these values for the metrics are mainly due to the periodicity of atmospheric states.
+When we look at the anomaly metrics, the model is still able to learn some things and perform slightly better than a model of anomaly averages.
+However, since the median maximum absolute value for the state coefficients is \num{1155.14}, the error rate is not as good as the state predictions.
+\begin{table}[H]
+  \caption{Performance metrics of anomaly coefficient prediction for scenario 3.}\label{table:sc3_test_anomaly_metrics}
+  \centering
+  \begin{tabular}{lrrrrr}
+    \toprule
+                   & MSE     & RMSE  & MAE   & R\textsuperscript{2}   & sMAPE \\
+    \midrule
+    spectral       & 4189.16 & 64.72 & 32.47 & 0.35 & 1.19  \\
+    function value & 4.09    & 2.02  & 1.44  & 0.09 & 1.24  \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\begin{table}[H]
+  \caption{Performance metrics of state coefficient prediction for scenario 3.}\label{table:sc3_test_state_metrics}
+  \centering
+  \begin{tabular}{lrrrrr}
+    \toprule
+                   & MSE     & RMSE  & MAE   & R\textsuperscript{2}   & sMAPE \\
+    \midrule
+    spectral       & 4189.16 & 64.72 & 32.47 & 0.56 & 0.74  \\
+    function value & 4.09    & 2.02  & 1.44  & 0.75 & 0.01  \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+The p-matrix and correlation image is shown in \lccref{fig:sc3_interpretation}.
+For the correlation image, we see that most wave numbers are correlated or inversely correlated with the outputs.
+The strongest correlation is shown by the features of the same wave number as the sorted target.
+This is an indication that the equations involved may be nonlinear.
+If we look at the p-matrix however, it seems very flat save a faint diagonal line from the top left to the bottom right.
+The values of the p-matrix are also extremely high.
+With the \enquote{flatness} we see, this is indicative of strong contributions by a few inputs.
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/wb2_ci.pgf}
+    \end{adjustbox}
+    \caption{The correlation image.}\label{fig:sc3_ci}
+  \end{subfigure}
+  \begin{subfigure}{0.49\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/wb2_pm.pgf}
+    \end{adjustbox}
+    \caption{The p-matrix.}\label{fig:sc3_pm}
+  \end{subfigure}
+  % \\[-0.7\baselineskip]
+  \caption{Correlation image and p-matrix for WeatherBench 2 model.
+The correlation image was sorted same order the values of the real component of wave number \((k_{longitude}=0, k_{latitude}=2)\) were sorted in descending order.}\label{fig:sc3_interpretation}
+\end{figure}
+
+To see more details of the p-matrix, we show a zoomed in version in \lccrefs{fig:sc3_pm_zoom1,fig:sc3_pm_zoom2}.
+The relationships are much more clear between features and outputs that do not share the same wave number.
+The coefficients with the same longitude wave numbers appear in the same \enquote{square} shape.
+Within the \enquote{square}, coefficients close to the same latitude wave number show much stronger contribution.
+For low wave numbers, shown in \lccref{fig:sc3_pm_zoom1}, the contribution is spread over more latitude wave numbers.
+The higher wave numbers, on the other hand, has the contributions much more concentrated on the coefficients with the same latitude wave numbers.
+In addition, the value of contribution differ by an order of magnitude with lower longitude wave numbers having higher maximum contribution.
+This observation suggests that the nonlinearity and magnitude are inversely proportional to the absolute value of the longitude wave number.
+This is in contrast to when we discussed the forcing term for our Burgers' equation scenario.
+The low frequencies in longitude may indicate that the model has learned some feature of the anomaly that is specific to different times of day.
+This is because the lowest longitudinal wave number would correspond to when different parts of the world is in nighttime or in daytime.
+Other possible explanations may be due to the fact that the earth more closely resemble a sphere compared to the toroidal shape that the 2-dimensional Fourier transform assumes.
+This would result in the representation latitude-wise being distorted.
+For this issue, the use of spherical harmonics may be a better fit to rule out the possibility of any distortions the Fourier transform may introduce.
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/wb2_pm_zoom1.pgf}
+    \end{adjustbox}
+    \caption{The p-matrix zoomed in to \((k_{longitude}=\{0, 1, 2\}, k_{latitude}=[-16, 16))\).}\label{fig:sc3_pm_zoom1}
+  \end{subfigure}
+  \begin{subfigure}{\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/wb2_pm_zoom2.pgf}
+    \end{adjustbox}
+    \caption{The p-matrix zoomed in to \((k_{longitude}=\{\phantom{-}31,-32,\phantom{-}32\}, k_{latitude}=[-16, 16))\).}\label{fig:sc3_pm_zoom2}
+  \end{subfigure}
+  \caption{The p-matrix of the WeatherBench 2 models zoomed in to specific wave numbers.}\label{fig:sc3_pm_zoomed}
+\end{figure}
+
+The predictions from test features are processed through the Fourier inverse transform to evaluate the function values.
+The direct predictions, which is the anomaly, is shown in \lccref{fig:sc3_anomaly_predictions}.
+The model seem to be predicting less extreme values that are noticeable in the target.
+Specifically areas over North America, Central Asia, and parts of Antarctica show lower temperature anomaly than expected.
+We also loose detail in areas which should have a lower anomaly such as northern areas of Africa, Greenland, and South Asia.
+The lack of detail seems to be a problem of underestimation.
+We believe this is caused by the so-called \enquote{double penalty} issue caused by the loss function used for the LSSVR \autocite{lledoScaledependentVerificationPrecipitation2023}.
+The predictions tend to be closer to the mean of the data to avoid the extra penalty from a wrong prediction with a high value.
+One way to allow for finer details that are less accurate is to penalize the higher frequency wave numbers less compared to the lower frequency wave numbers.
+For our case this means the LSSVR for each output will have their regularization parameter decreased to allow the model to focus less on the errors for higher frequencies.
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{\linewidth}
+    % \centering
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/wb2_anom_pred.pgf}
+    \end{adjustbox}
+    \caption{Predicted 2-meter temperature anomaly.}\label{fig:sc3_anomaly_pred}
+  \end{subfigure}
+  \begin{subfigure}{\linewidth}
+    % \centering
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/wb2_anom_target.pgf}
+    \end{adjustbox}
+    \caption{Target 2-meter temperature anomaly.}\label{fig:sc3_anomaly_target}
+  \end{subfigure}
+  \caption{2-meter temperature anomaly prediction for the 1\textsuperscript{st} of January 2020 at 6:00 UTC based on the previous anomaly at 0:00 UTC.}\label{fig:sc3_anomaly_predictions}
+\end{figure}
+
+The state predictions which is obtained by adding the climatology to the predicted anomaly is shown in \lccref{fig:sc3_state_predictions}.
+This further shows areas of discrepancy between the prediction and the target.
+The area in the South Pacific show that the target has a higher difference temperature compared to the prediction.
+This smoothness in the prediction is easier to see for areas in the ocean.
+Many sharp features are lost and the state prediction start to resemble averaged view of the climatology.
+We must also take into account that the model only used temperature distribution data.
+Other pieces of information we know to be crucial to weather prediction such as wind speed or pressure was not included in the inputs.
+With this in consideration the model was still able to learn some relationships defined by governing equations of weather.
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{\linewidth}
+    % \centering
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/wb2_state_pred.pgf}
+    \end{adjustbox}
+    \caption{Predicted 2-meter temperature.}\label{fig:sc3_state_pred}
+  \end{subfigure}
+  \begin{subfigure}{\linewidth}
+    % \centering
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/wb2_state_target.pgf}
+    \end{adjustbox}
+    \caption{Target 2-meter temperature.}\label{fig:sc3_state_target}
+  \end{subfigure}
+  \caption{2-meter temperature prediction for the 1\textsuperscript{st} of January 2020 at 6:00 UTC based on the previous anomaly at 0:00 UTC.}\label{fig:sc3_state_predictions}
+\end{figure}
+
+The results of our experiments show that the proposed model has the ability to learn the relationships that PDEs and other governing equations define.
+The interpretation methods for support vector regression that we used, namely the correlation image and p-matrix developed by \textcite{ustunVisualisationInterpretationSupport2007}, allows us to confirm what the model has learned.
+In the case of the WeatherBench2 model, it has also allowed us to glean some insight into some mechanisms that the model has learned.
+This information was used to verify the learned relationships for the simple derivative equation.
+Together with the performance metrics on three different problems, we have shown the proposed model to be a viable tool for situations with limited knowledge and a need for some level of interpretability of the model.

### 2025-01-06 skripsi/chapter5.tex
Finish ch4, fix some problems with

% !TEX root = ./skripsi.tex
\chapter{CONCLUSIONS AND FUTURE WORK}

\section{Conclusion}
% \noindent Bab ini merupakan pamungkas berupa rincian rangkuman yang merupakan simpulan dari analisis yang telah dilakukan. Simpulan ini menyajikan sejumlah hal penting yang disampaikan secara ringkas, padat, dan utuh, yang menjawab tujuan penelitian yang dituliskan pada Bab Pendahuluan. Sangat mungkin   ada beberapa konsekuensi dan implikasi yang ditimbulkan dari simpulan yang dihasilkan, yang sepatutnya menjadi perhatian pada penelitian berikutnya. Judul bab dapat disesuaikan, namun umumnya ada \textit{Simpulan} yang memang mendominasi isi bab ini.

\section{Future Work}
% \noindent Sejumlah ide yang muncul ketika melaksanakan penelitian TA dapat menjadi bahan atau topik untuk pekerjaan selanjutnya. Hal ini dapat berupa perbaikan atau ragam lain dari apa yang telah dilakukan sepanjang penelitian. Sub bab ini menjadi sumber informasi penting bagi, utamanya mahasiswa, yang akan melakukan penelitian lanjutan.

### 2025-01-09 skripsi/apendix.tex
finish ch2 and start ch5

--- 2024-12-07 skripsi/chapter2.tex
@@
 % !TEX root = ./skripsi.tex
-\chapter{KAJIAN PUSTAKA}
+\appendix
 
-\noindent Bab ini mengulas secara rinci konsep-konsep dasar yang berkaitan dengn pekerjaan penelitian TA dan deskripsi studi pustaka yang dilakukan.
-Judul bab tidak harus seperti yang dituliskan, melainkan dapat lebih fleksibel yang mencerminkan isi paparan pada bab ini.
-Demikian halnya dengan judul sub bab.
-
-\section{Fourier Transform and Series}
-\noindent
-
-Complex numbers are numbers consisting of real and imaginary components.
-Complex numbers are written as in \lccref{eq:complex_number} with \(a \) and \(b \) being the real and imaginary components respectively.
-The imaginary component is multiplied by the imaginary unit \(i=\sqrt{-1}\).
-\begin{align}
-  c = a + bi \label{eq:complex_number} \\
-\end{align}
-
-\section{Least Squares Support Vector Machine}
-\noindent An arguably fundamental model widely used whether in pedagogical settings or otherwise is the support vector machine.
-It dates back to works by Vapnik \& Lerner in 1963 (Recognition of Patterns with help of Generalized Portraits) and V.
-N.
-Vapnik \& A.
-Ya.
-Chervonenkis in 1964 (A note on one class of perceptrons/On a perceptron class).
-As the development on SVM continued, what originally was a model for classification of separable data generalized to regression tasks as well Vapnik (2000 The Nature of Statistical Learning Theory).
-\subsection{Disadvantages}
-However, the main disadvantage of LSSVMs are the fact that they do not have the sparse property of SVMs which can leave performance on the table.
-A simple mitigation can be done by filtering training samples with small absolute values of lagrangian multipliers \autocite{haifengwangComparisonSVMLSSVM2005}.
-
-To derive the least squares support vector regression (J.A. Suykens LSSVM Book) model we start with the linear expression:
-
-\begin{equation}
-  y=W^{\intercal}\vb{x}+b
-\end{equation}
-
-\begin{equation}
-  \min_{W,e} J(W,e) = \frac{1}{2}W^{\intercal}W + C\frac{1}{2}\sum_{k=1}^{n}e_{k}
-\end{equation}
-
-Such that
-\begin{equation}
-  y_{k}=W^{\intercal}\vb{x}_{k}+b+e_{k} \qquad k=1,\dots,n
-\end{equation}
-
-\begin{equation}
-  L(W,b,e;\vb{\alpha}) = \frac{1}{2}W^{\intercal}W + C\frac{1}{2}\sum_{k=1}^{n}e_{k} + \sum_{k=1}^{n}\alpha_{k} \left(W^{\intercal}\vb{x}_{k}+b+e_{k} - y_{k} \right)
-\end{equation}
-
-Derive the KKT system
-\begin{equation}
-  \begin{split}
-    \pdv{L}{W} = 0 \rightarrow & W = \sum_{k=1}^{n}\alpha_{k}x_{k} \\
-    \pdv{L}{b} = 0 \rightarrow & \sum_{k=1}^{n}\alpha_{k} = 0 \\
-    \pdv{L}{e_{k}} = 0 \rightarrow & \alpha_{k} = C e_{k} & \qquad k=1,\dots,n\\
-    \pdv{L}{\alpha_{k}} = 0 \rightarrow & W^{\intercal}\vb{x}_{k}+b+e_{k} - y_{k} = 0 & \qquad k=1,\dots,n\\
-  \end{split}
-\end{equation}
-
-After eliminating $W$ and $\vb*{e}$, with $\vb{1}_{n} = \langle 1,\dots,1\rangle$, $\vb{y} = \lbrack y_1, \dots, y_n \rbrack $, and ${\alpha} = \lbrack \alpha_1, \dots, \alpha_n \rbrack $ the solution is as follows in block matrix notation
-\begin{equation} \label{eq:lssvr_solution}
-  \begin{bmatrix}
-    0          & \vb{1}_{n}^{\intercal} \\
-    \vb{1}_{n} & \Omega + \frac{I}{C}
-  \end{bmatrix}
-  \begin{bmatrix}
-    b           \\
-    \vb{\alpha} \\
-  \end{bmatrix}
-  =
-  \begin{bmatrix}
-    0      \\
-    \vb{y} \\
-  \end{bmatrix}
-\end{equation}
-
-The solution in \cref{eq:lssvr_solution}
-
-\begin{algorithm}[H]
-  \caption{LSSVR Training}\label{alg:lssvr_training}
-  \begin{algorithmic}[1]
-    \Procedure{SolveLSSVR}{$\vb{X}, \vb{y}, \gamma $}
-    \State{\(\Omega \gets [[]]\)}
-    \Comment{Construct matrix of inner products in high dimensional space}
-
-    \For{\(k=0 \to n\)}
-    \For{\(l=0 \to n\)}
-    \State{\(\Omega_{k,l}\gets K(\vb{X}_k,\vb{X}_l)\)}
-    \EndFor{}
-    \EndFor{}
-    \State{\(\vb{H} \gets \Omega + \frac{\vb{I}}{\gamma}\)}
-    % \State $\vb{1} \gets [1,1,...,1]$
-    \State{\(\vb{A} \gets [[]]\)}
-    \Comment{Construct left-hand side matrix}
-    \State{\(\vb{A}_{0,0} \gets 0\)}
-    \For{\(k=0 \to n\)}
-    \State{\(\vb{A}_{k+1,0} \gets 1\)}
-    \State{\(\vb{A}_{0,k+1} \gets 1\)}
-    \EndFor{}
-    \For{\(k=0 \to n\)}
-    \For{\(l=0 \to n\)}
-    \State{\(\vb{A}_{k+1,l+1} \gets \vb{H}_{k,l}\)}
-    \EndFor{}
-    \EndFor{}
-    \State{\(\vb{B}\gets []\)}
-    \Comment{Construct left-hand side of the equation}
-    \State{\(\vb{B}_0 \gets 0\)}
-    \For{\(k=0 \to n\)}
-    \State{\(\vb{B}_{k+1} \gets \vb{y}_{k}\)}
-    \EndFor{}
-    \State{\(\vb{A}^{\dagger} \gets pseudoInverse(\vb{A})\)}
-    \Comment{Compute solution using pseudo inverse}
-    \State{\(\vb{S} \gets \vb{A}^{\dagger}\vb{B}\)}
-    \State{\(b \gets \vb{S}_{0}\)}
-    \For{\(k=0 \to n\)}
-    \State{\(\vb{\alpha}_{k} \gets \vb{S}_{k+1}\)}
-    \EndFor{}
-    \State{\textbf{return}\(\vb{\alpha}, b\)}
-    \EndProcedure{}
-  \end{algorithmic}
-\end{algorithm}
-
-The basic pseudocode from the LSSVM Equation for function regression is defined in \lccref{alg:lssvr_training} for a training set of length $n$, features $\vb{X}$, and labels $\vb{y}$.
-Training the LSSVM means computing the values of langrange multipliers $\vb{\alpha}$ and bias $b$.
-$K$ is the kernel function used to compute the inner products in high dimensional space, here we assume the RBF kernel.
-$\vb{A}$ is a matrix of size $n+1$ by $n+1$.
-$\vb{H}$ is a matrix of size $n$ by $n$.
-$\vb{I}$ is the identity.
-$\vb{B}$ is a vector of size $n+1$.
-$\vb{S}$ is a vector of size $n+1$.
-
-After training the model can be used for prediction of unseen features.
-The pseudocode for prediction is shown in \lccref{alg:lssvr_prediction} for prediction features $\vb{U}$ with \(p \) samples.
-The trained model uses the training features themselves $\vb{X}$ with \(n \) samples, the learned multipliers of training points $\vb{\alpha}$, and the bias $b$.
-
-\begin{algorithm}[H]
-  \caption{LSSVR Prediction}\label{alg:lssvr_prediction}
-  \begin{algorithmic}[1]
-    \Require $\vb{U}, \vb{\alpha}, \vb{X}, b$
-    \Ensure $\vb{v}$
-    \State $\Omega \gets [[]]$ \Comment{Construct matrix of inner products in high dimensional space}
-
-    \For{$k=0 \to p$}
-    \For{$l=0 \to n$}
-    \State$\Omega_{k,l}\gets K(\vb{U}_{k},\vb{X}_l)$
-    \EndFor
-    \EndFor
-    \State $\vb{v} \gets \Omega\vb{\alpha} + \vb{1}_{m}b$
-  \end{algorithmic}
-\end{algorithm}
-
-In this exmple we will be using the function $2x^2+4$. The values of this function can be seen in Table \ref{table:1}.
+\chapter{EXAMPLE COMPUTATION OF LSSVR}
+% Example computation
+In this example we will be using the function \(2x^2+4\). The values of this function can be seen in \lccref{table:1}.
 
@@
     1  & 0.0        & 4.0        \\
-    2  & 0.33... & 4.22... \\
-    3  & 0.66... & 4.88... \\
+    2  & 0.33\ldots & 4.22\ldots \\
+    3  & 0.66\ldots & 4.88\ldots \\
     4  & 1.0        & 6.0        \\
@@
   \end{tabular}
-  \caption{Example data of function $2x^2+4$} \label{table:1}
+  \caption{Example data of function \(2x^2+4\)}\label{table:lssvr_example_function_values}
 \end{table}
-For $\Omega_{i,j}=K(x_i,x_j)=exp \left(-\frac{\norm*{x_i-x_j}^2}{2\sigma^2}\right)$
+For \(\Omega_{i,j}=K(x_i,x_j)=exp \left(-\frac{\norm*{x_i-x_j}^2}{2\sigma^2}\right)\)
 
-For example, with $\sigma=1$, $x_i=0.0$, \& $x_j = 0.33\dots$
+For example, with \(\sigma=1\), \(x_i=0.0\), \& \(x_j = 0.33\dots\)
 \begin{equation}
   \begin{split}
-    K(0.0,0.33) & = exp\left(-\frac{\norm*{0.0-0.33}^2}{2(1)^2}\right) \\
-    & = exp\left(-\frac{0.33^2}{2}\right) \\
+    K(0.0,0.33) & = \exp\left(-\frac{\norm*{0.0-0.33}^2}{2(1)^2}\right) \\
+                & = \exp\left(-\frac{0.33^2}{2}\right)                  \\
                 & = 0.9460
@@
 \begin{equation}
-  \vb{I}\frac{1}{\gamma}\to\vb{I}\frac{1}{5}\to
+  \vb{I}\frac{1}{C}\to\vb{I}\frac{1}{5}\to
   \begin{bmatrix}
@@
 \end{equation}
-Where $\vb{1}_{m}$ is a vector of 1s with the length of $U$.
+Where \(\vb{1}_{m}\) is a vector of 1s with the length of \(U\).
 
-\section{Sub Bab B}
-\noindent Suatu penelitian tidak dapat lepas dari capaian pengetahuan dan pemahaman yang sudah dipublikasikan.
-Deskripsi tentang capaian ini menjadi penting karena selain menunjukkan tingkat pemahaman mahasiswa, juga mengetahui tempat pekerjaan penelitian TA dalam konstelasi capaian tersebut.
-Studi pustaka dan paparan hasilnya dapat memperkaya wawasan tentang topik yang diangkat pada penelitian TA.
+% \section{PROGRAM SATU}
+% \section{PROGRAM DUA}
 
-\section{Membuat Persamaan}
-\noindent Secara prinsip, suatu persamaan menyatu dalam kalimat.
-Letak persamaan dapat berada di awal, tengah, atau akhir kalimat.
-Dengan demikian, pada akhir persamaan harus diberikan tanda baca, misalnya koma, titik koma, atau titik, yang menekankan kehadiran persamaan dalam kalimat.
-Tidak semua persamaan harus diberi nomor.
-Persamaan yang dirujuk pada naskah TA saja yang harus diberi nomor.
-Kode awal penomoran ini adalah nomor urut bab, termasuk untuk persamaan pada Lampiran, dengan urutan alfabet kapital.
-
-Setiap notasi harus unik atau tunggal, sehingga arti setiap notasi adalah unik atau tunggal juga.
-Arti satu notasi harus dituliskan segera ketika notasi tersebut muncul, dan tidak diulang lagi setelahnya.
-
-\subsection{Contoh Persamaan Sederhana}
-Persamaan (\ref{II.1}) mendeskripsikan dinamika fungsi gelombang $\psi(\vec{r},t)$ di bawah pengaruh potensial $V(\vec{r})$ dan dituliskan sebagai berikut:
-\begin{equation}\label{II.1}
-  i\hslash\frac{\partial \psi}{\partial t} = -\frac{\hslash^2}{2 m}\Vec{\nabla}^2 \psi + V(\vec{r})\psi,
-\end{equation}
-dengan $m$ adalah massa partikel dan $\hslash$ merupakan konstanta Planck tereduksi.
-
-Di akhir persamaan (\ref{II.1}) diberi koma karena berada ditengah kalimat. Untuk merujuk ke persamaan yang telah ditulis, gunakan perintah \verb|\ref{}|.
-
-Untuk menuliskan beberapa set persamaan yang masih terhubung, gunakan \verb|\subequations{}|. Misal kita punya persamaan diferensial terkopel, kita bisa tuliskan
-\begin{subequations}
-  \begin{align}
-    \frac{dy}{dt} & = -x , \\
-    \frac{dx}{dt} & = -y .
-  \end{align}
-\end{subequations}
-Kalau perlu matriks, kita bisa tulis seperti berikut.
-\begin{equation}
-  \sigma_x =
-  \begin{pmatrix}
-    0 & 1 \\
-    1 & 0
-  \end{pmatrix},\quad
-  \sigma_y =
-  \begin{pmatrix}
-    0 & -i \\
-    i & 0
-  \end{pmatrix}, \quad
-  \sigma_z =
-  \begin{pmatrix}
-    1 & 0  \\
-    0 & -1
-  \end{pmatrix}
-\end{equation}
-
-\section{Referensi dan Citation}
-% \noindent Sitasi dapat dimasukkan ke dalam Tugas Akhir seperti ini \cite{Fujita1996}.
-Untuk sitasi dengan beberapa sumber, dapat dituliskan juga \cite{hohen1964,Kim2006}.
-Atau untuk tiga sumber berarti \cite{kongkanand2006,kresse1999,Leibb1993}.
+% \chapter{GAMBAR-GAMBAR}

### 2025-01-09 skripsi/chapter1.tex
finish ch2 and start ch5

@@
 % TODO: reword this because the explanation of the problem setup for forward and inverse problems is not layed out optimally.
-% TODO: perhaps the disadvantage of inverse problem in the paragraph above should be removed and only explanation of the inverse problem setup itself left by itself
 % \begin{equation} \label{eq:forward_finite_difference_1}
@@
 This model was then able to be trained in a massively parallel manner.
-In a comparison with a traditional model called the Integrated Forecasting System from the European Center for Medium Range Weather Forecasts (ECMWF), FourCastNet is faster and much more efficient in terms of inference time, resulting in about 80,000 times speed up for a 100-member ensemble forecast.
+In a comparison with a traditional model called the Integrated Forecasting System from the European Center for Medium Range Weather Forecasts (ECMWF), FourCastNet is faster and much more efficient in terms of inference time, resulting in about \num{80000} times speed up for a \num{100}-member ensemble forecast.
 This is while performing much better than a previous deep learning approach.

### 2025-01-09 skripsi/chapter2.tex
finish ch2 and start ch5

--- 2024-12-18 skripsi/chapter2.tex
@@
 % !TEX root = ./skripsi.tex
-\chapter{KAJIAN PUSTAKA}
-
-\noindent Bab ini mengulas secara rinci konsep-konsep dasar yang berkaitan dengn pekerjaan penelitian TA dan deskripsi studi pustaka yang dilakukan.
+\chapter{LITERATURE REVIEW}
+\noindent This chapter will discuss and summarize the literature related to this study.
+The context of the study will be explained in terms of the state of the art (SoTA), the literature involved, and how this problem fits within the larger computing and physical sciences field.
+% \noindent Bab ini mengulas secara rinci konsep-konsep dasar yang berkaitan dengn pekerjaan penelitian TA dan deskripsi studi pustaka yang dilakukan.
 Judul bab tidak harus seperti yang dituliskan, melainkan dapat lebih fleksibel yang mencerminkan isi paparan pada bab ini.
@@
 
+\section{Governing Equations}
+\noindent Mathematical expressions that describe the behavior of a system are called governing equations.
+Typically, governing equations are in the form of Differential Equations (DE).
+For some systems with several variables, the governing equations are Partial Differential Equations (PDE).
+These equations are the foundation of many engineering and scientific models \autocite{olverIntroductionPartialDifferential2014,andersonGoverningEquationsFluid1992}.
+In the physical sciences, the use of PDEs as governing equations is widespread.
+Many fields, including those outside the physical sciences, use these equations to model systems and solve problems whose solutions we take for granted today, ranging from fluid mechanics to ecology.
+
+In recorded history, the early work of differential equations can be traced to the independent works of Gottfried Wilhelm Leibniz and Isaac Newton.
+The formulation of calculus and its associated notation paved the groundwork for further study into the mathematical description of change.
+PDEs as a subject of study was started in the 18\textsuperscript{th} century with the works of Euler, d'Alembert, Lagrange, and Laplace \autocite{brezisPartialDifferentialEquations1998}.
+Near the end of the 19\textsuperscript{th} century, Poincar\'e stated that a variety of physical system share a similarity.
+This is followed by the statement that they should be treated in a similar fashion.
+He expressed his motivation for mathematical proofs that approximate physical phenomena.
+Meanwhile, through the 18\textsuperscript{th} and 19\textsuperscript{th} century, many equations such as the Euler equation of incompressible flow, Maxwell's equation in electromagnetic theory, and the Navier-Stokes equations for fluid flow.
+These are just some examples of the equations that were developed during that period of time.
+In the 20\textsuperscript{th} century, what is known today as the Burgers' equation was introduced with the interest of modeling turbulent flow.
+Today, there are many more equations that have been introduced to solve many more different problems.
+The Poisson equation, for example, is used to model many problems including electric potential, steady-state temperature distribution, and Newtonian gravity \autocite{selvaduraiPartialDifferentialEquations2000}.
+
+% Derivative Equation
+Governing equations in the form of PDEs describe the behavior of systems by quantifying changes.
+These changes, naturally, are represented as partial derivatives.
+We will discuss three situations where systems can be described in this way.
+First, in its simplest form, a derivative equation models the relationship between the rate of change and the total change.
+In more relatable terms, the example for this is the relationship between speed and acceleration.
+Acceleration is the rate of change for speed.
+The function that describes speed will complement the acceleration depending on the kind of function that describes acceleration and vice versa.
+The mathematical formulation for the derivative equation is shown in \lccref{eq:derivative}.
+Because of the ubiquity of the relationship defined by this equation, it is perhaps the one with the most uses.
+Some applications for differential equations include radioactive decay \autocite{grochRadioactiveDecay1998,huestisUnderstandingOriginMeaning2002}, population dynamics \autocite{gopalsamyStabilityOscillationsDelay1992}, and other dynamical systems \autocite{katokIntroductionModernTheory2009}.
+\begin{align}
+  \dv{u\left( t \right)}{t} & = a\left( t \right) \label{eq:derivative}
+\end{align}
+
+Solving the derivative equation can be analytically if the exact form is known.
+This involves common techniques in calculus such as separation of variables \autocite{braunDifferentialEquationsTheir1993}.
+In other cases, the solution can be computed using numerical methods such as Euler's method and the Runge-Kutta method among others.
+These numerical methods use the knowledge about the differential equations to compute the solutions.
+Both the Euler's method and Runge-Kutta method compute the solution by adding the current value of the solution with the estimated difference with the next value of the solution to produce the next value of the solution.
+The estimated difference is typically computed by with some combination the derivative and step size.
+This is where the knowledge of the derivative equation to be solved is used.
+By storing each predicted solution value and using it as the current solution value, the entire solution is computed.
+
+% Burgers' Equation
+The second situation we discuss is the Burgers' equation.
+This equation was initially used for describing the distribution of speed in a fluid.
+Although not entirely physically accurate, this equation describes how differences in speed observed within a fluid can emerge.
+These differences in speed can lead to shocks where the gradient approach infinity \autocite{orlandiBurgersEquation2000}.
+The forced-viscous equation can be seen in \lccref{eq:forced_viscous_burgers}.
+The equation is made up of four terms including the forcing term.
+The first is the time derivative.
+The second term is the convection term which makes this equation nonlinear because the solution is multiplied by another form of the solution, which in this case is the first derivative in space.
+The third term is the advection term.
+Finally, we have the forcing term that encompasses all external influence on the solution.
+\begin{align}
+  \pdv{u}{t}+u\pdv{u}{x}-\nu\pdv[2]{u}{x} & = f \label{eq:forced_viscous_burgers}
+\end{align}
+
+An intuitive way to understand how the solution would evolve in time is to think of the time derivative in terms of all the other components.
+This way we can see how the solution would change from one time to the next at all points.
+The viscosity \(\nu \) modulates the advection term.
+The larger the viscosity value, the more the solution resists forming shocks.
+This is because, the second derivative makes the time derivative have higher values for areas of rapid change.
+Specifically, it makes areas that change rapidly in space to lower solution values have lower time derivative values.
+For areas with rapid change in space to higher solution values, it makes those areas have higher time derivative values.
+The result is that it spreads out the rapid changes in space or \enquote{curves} over time.
+
+The convolution term behaves in an amplifying manner.
+For areas that have the same signs for their solution value and the space derivative, it would attract it to lower values.
+For areas with differing signs for the solution value and space derivative, it would attract it to a higher value.
+As a whole this would make the solution tend toward large negative gradients and discourage large positive gradients.
+As the negative gradient grows, if unimpeded by the advection term, it would eventually lead to the formation of a shock wave moving to the positive x direction.
+Finally, the forcing term affects the time derivative directly and attract the solution toward which ever direction defined by the forcing term.
+%add discussion about turbulence here.
+% TODO: add figure for the effects of each term on the time derivative and how the solution evolves
+Solutions to the Burgers' equation can be obtained analytically.
+One of the most straightforward ways is the Cole-Hopf transform.
+Using this method, the solution to the Burgers' equation \(u\) is computed from any valid solutions of the heat equation \(\phi \).
+The solution of the Burgers' equation is obtained by using the Cole-Hopf transform written in \lccref{eq:cole_hopf}.
+However, this limits the range of possible solutions because of the requirement of a valid heat equation solution.
+For a wider range of solutions, numerical methods are predominantly used to solve the initial value problem for the Burgers' equation.
+This can be done by computing the time derivative term from the other terms.
+However, both the convection and advection terms create a challenge in solving the equation numerically.
+For small viscosity values, the equation is dominated by the convection term.
+And as previously mentioned this means the development of sharp gradients and possibly shock waves.
+As the gradient become sharper, the solution would require finer and finer time steps in order to stay at a consistent error for each step, otherwise the solution can become unstable.
+\begin{align}
+  u = -2\nu\frac{\phi_x}{\phi}\label{eq:cole_hopf}
+\end{align}
+
+High viscosity values introduce a similar issue.
+The problem comes from rapidly varying large values introduced by the second derivative.
+This is a product of the \enquote{amplification} caused by derivatives which is compounded by higher orders.
+The rapid variation also mean that smaller time steps would need to be used by standard numerical solvers.
+For numerical solvers, such as the forward Euler method we discussed earlier, insufficiently fine time steps can lead to numerical instability.
+This imposes a constraint on how large the time steps and or on how the numerical solvers can treat these equations.
+The differential equations that cause this issue are called stiff PDEs.
+To overcome these challenges, specialized numerical solvers for stiff PDEs have been developed \autocite{kassamFourthOrderTimeSteppingStiff2005}.
+
+% The Weather
+The third situation we discuss here is the weather system.
+Today, we have much better understanding of the governing equations of the weather system.
+The governing equations of the weather include the momentum equations (for example wind), gravitational force, friction, centrifugal force, Coriolis force, the hydrostatic equation, and thermodynamic equations \autocite{martinIntroductionWeatherClimate2014}.
+These components each describe how different variables change and the interaction between those variables, such as wind and temperature.
+
+The interplay between the governing equations of weather are very complex.
+In addition, some constituting equations like the Navier-Stokes, can be very nonlinear.
+These are some reasons why analytical solutions for the governing equation are not feasible for realistic scenarios.
+Today, the weather is modeled by numerical methods.
+Initially, many numerical models that were in use were based on the Finite Differences Method (FDM).
+After 1972, other approaches regained interest, namely the spectral methods \autocite{puNumericalWeatherPrediction2018,mengaldoCurrentEmergingTimeIntegration2019}.
+Much more recently, other advances include ensemble forecasting where multiple models represent the probabilistic distribution that needs to be accounted for.
+Another development is advanced data assimilation methods for various observational data sources \autocite{parkDataAssimilationAtmospheric2013}.
+Due to the size differences involved with simulating the weather, some parts such as turbulence or the presence of aerosols adds further challenges.
+Many operational models, use approximations such as turbulence closure because the unknowns outnumber the equations.
+Due to these challenges, there has been research into the use of machine learning and other statistical methods for this specific area \autocite{langAIFSECMWFDatadriven2024,bonevSphericalFourierNeural2023}.
+Machine learning-based approaches provide the ability to predict the weather with increasing accuracy and speed using a black box model which complements the physics-based models \autocite{biAccurateMediumrangeGlobal2023}.
+Ongoing research and technological developments continue to refine these models, aiming for more precise and reliable weather forecasts.
+% TODO: talk about inverse and forward problems
+
+\section{Machine Learning}
+\noindent Machine Learning (ML) has experienced a surge of interest in the past two decades.
+A major contributor to this is the increase in computing power.
+Specifically Neural Networks (NN), found renewed interest with parallel algorithms being able to run on hardware accelerators like Graphics Processing Units (GPU).
+Machine Learning can be categorized into two major paradigms which are supervised learning and unsupervised learning \autocite{alpaydinIntroductionMachineLearning2020}.
+In unsupervised learning, the model is usually asked to find the structures within the data.
+For example, the different groups that share a similar structure or how often such structures appear.
+On the other hand, supervised learning involves training models with pairs of features and labels.
+The labeled dataset gives a certain direction the for the model to learn.
+For example, labels that indicate whether a cat is present or not in an image.
+Other labels might instead indicate the number of cats in the image.
+These labels essentially asks the model to look for certain structures in the features that are shared between common labels.
+
+Supervised learning is further categorized into the type of prediction task.
+The first task is classification.
+In this task, models are trained to group samples into different categories.
+Samples within the same category would share a common structure within its features.
+For example, a regulatory body of the government wants to detect fraudulent activities.
+A model could be trained to classify whether a bank account is involved in fraudulent activity or not.
+This is done by training on a collection of both fraudulent and normal transaction data.
+By processing the data into more meaningful features such as average transactions or the rate of transactions and incorporating other information about the account a pair of features and labels are created.
+This can then be used to train the model to distinguish between fraudulent and legitimate activities.
+
+% Regression
+The second task we will discuss is regression, which we will focus on for the rest of this section.
+In regression the model is tasked to predict continuous values based on the features it receives \autocite{alpaydinIntroductionMachineLearning2020,matloffStatisticalRegressionClassification2017}.
+This is in contrast to the discrete values used as labels in the classification task.
+Applying machine learning to the problem of modeling systems, like traditional numerical methods, is a regression task.
+For example, if we want a model to learn the relationship between the coefficients of two different functions in place of the spectral method, this would be a case of regression.
+As more concrete example, the prediction of weather variables is a regression task.
+Typically, the features are based on the current and previous states of the atmosphere.
+The model is then trained to predict the future atmospheric state.
+The variables that represent atmospheric state such as temperature and wind speed are continuous variables.
+Specifically, if the task is to predict from features outside the range of the training data, such as predicting future weather, this is called extrapolation.
+On the other hand, if the features exists within the range of the training data, such as approximating the wind speed between weather station, the action is called interpolation.
+Regardless, for both, the model learns to approximate the continuous labels from the features.
+
+% Autoregression
+On the subject of weather prediction, the goal is sometimes to predict several time steps ahead of the reference input features.
+The term lead time is used in this scenario to refer to the amount of time ahead of the reference time.
+Weather predictions for several time steps ahead is particularly useful in order to allow for longer term planning.
+For example, management of the power grid and renewable power sources rely on weather forecasts to manage supply.
+For these cases, the model is usually trained to predict the state at the next time step based on the current time step.
+To achieve the predictions for several time steps ahead, the model would need to predict using its previous predictions.
+This is repeated until the target lead time is reached.
+This use of the model is called autoregression \autocite{maccarroneGDPForecastingMachine2021}.
+An important property of the model for this task is stability.
+This is because errors will compound very quickly if the model is unstable.
+For ML models that has flexible loss functions like NNs, the model can be made more accurate by including the autogression during training and incorporating the autoregression error into the loss function \autocite{pmlr-v32-gregor14}.
+Together, autoregression and regression, form an essential tool for solving many problems involving the prediction of continuous values.
+
+\section{Operator Learning}
+\noindent Machine learning, as with many other fields, has found its foothold in scientific computing.
+The term that has become popular for this field is Scientific Machine Learning (SciML) \autocite{bakerWorkshopReportBasic2019}.
+This field, just like scientific computing, is interdisciplinary with mathematics, physics, computer science, and other disciplines contributing to solve the specific challenges involved with datasets specific to these individual disciplines.
+The field seeks to extract insights from scientific datasets by building new methods that are scalable, interpretable, and reliable.
+This is partly driven by the advances in computing, specifically machine learning, and the potential for and accumulation of scientific data.
+The motivations for developing domain-specific machine learning tools include the difficulty in using and interpreting general purpose ML algorithms for the problems researchers seek to solve with scientific datasets.
+
+A set of tools called Operator Learning has been attracting interest within SciML\@.
+These tools learn the mappings between functions defined by an operator \autocite{JMLR:v24:21-1524,boulleMathematicalGuideOperator2024}.
+Mathematically, an operator is a mapping between function spaces.
+For example, the derivative operator \(\dv{x}\) maps the space of all differentiable functions with the space of derivative functions.
+For this example, the model would learn the relationship between the derivative function and the antiderivative function.
+More generally, a model \(\hat{\mathcal{A}}\) is used to approximate an unknown operator \(\mathcal{A}\).
+Given data that represent two functions \((f,u)\) with \(f\in\mathcal{F}\) and \(u\in\mathcal{U}\) on a domain \(\Omega{}\) which is a subset of the \(n\)-dimensional real number line, and an operator \(\mathcal{A}:\mathcal{F}\mapsto\mathcal{U}\) such that \(\mathcal{A}(f)=u\), the objective is to find the approximation \(\hat{\mathcal{A}}\).
+The search for the approximation is due such that for any new data \(f'\in\mathcal{F}\) and \(u'\in\mathcal{U}\), we get \(\hat{\mathcal{A}}(f')\approx\mathcal{A}(f')\).
+
+The model \(\hat{\mathcal{A}}\) is optimized by minimizing the loss function shown in \lccref{eq:operator_learning_loss}, with model parameters \(\theta{}\).
+\begin{align}
+  \min_{\theta} L\left(\hat{\mathcal{A}}\left(f;\theta\right),u\right)\label{eq:operator_learning_loss}
+\end{align}
+
+There are currently different model architectures for the learning operators.
+Most of these are implemented as Neural Networks (NN).
+The Neural Operator proposes a method to generalize NNs to learning mappings between function spaces \autocite{li2021fourier}.
+The Fourier Neural Operator (FNO) variant adds Fourier transforms to the composition of layers within the NN\@.
+Another NN layer is added to learn the mapping within the Fourier domain.
+The outputs of this layer is then Inverse transformed and passed on.
+This entire process is called the FNO block.
+Adding multiple of these blocks allow for learning more complex relationships.
+Another approach called Spectral Neural Operators, instead maps the coefficients of inputs to the coefficients of output functions \autocite{fanaskovSpectralNeuralOperators2023}.
+For coefficients obtained from Fourier transforms, the model is approximating the standard spectral method by taking advantage of the properties of the Fourier coefficients we discuss in \lccref{sec:fourier_discussion}.
+Essentially, derivatives are multiplication in the Fourier domain.
+A similar work extended the idea by leveraging the known PDE to be part of the loss function \autocite{du2024neural}.
+The model is penalized for the residual computed using the PDE\@.
+This allows the NN to be trained in a self-supervised setting.
+Another major model is the so called DeepONet architecture proposed by \textcite{luLearningNonlinearOperators2021}.
+This model can be seen as foregoing the basis function the Fourier Transform enforces and instead learns the basis functions from the data \autocite{meurisMachinelearningbasedSpectralMethods2023}.
+Because of this, the model has two components.
+The first, named the trunk network acts as the learned basis functions.
+This network is given evaluation coordinates and computes the values of the \enquote{basis functions}.
+The second network, called the branch network, learns the mapping between the input function representation and the coefficients for the output function.
+The dot product of the outputs of both trunk and branch networks are evaluated to obtain the value of the predicted function at the specified coordinate.
+The final proposed approach we will discuss here doesn't use Deep Learning.
+The approach proposed by \textcite{nelsenOperatorLearningUsing2024} uses Random Feature Models (RFM) to learn operators.
+This model enjoys the advantage of using one of the simplest forms of machine learning.
+
 \section{Fourier Transform and Series}\label{sec:fourier_discussion}
-\noindent
+\noindent The Fourier transform and its associated series is a well known topic in both computing and the physical sciences \autocite{smithMathematicsDiscreteFourier2007}.
+The Fourier transform is used extensively both in theoretical and practical scenarios.
+In mathematics and physics, the Fourier transform is used widely for many subjects such as harmonic analysis, quantum mechanics, and of course in solving PDEs.
+More practical uses of the transform include signal processing, communication systems, data compression such as JPEG and MP3, and cryptography.
+For solving PDEs, the Fourier transform is used to simplify the equations involved.
+This is due to the unique properties associated with the Fourier transform.
 
+The Fourier series can be represented in two ways, the first is the real representation by using sine and cosines as the basis functions in the series shown in \lccref{eq:fourier_series_sine_cosine}.
+The second representation is the complex representation which uses Euler's formula as the basis functions shown in \lccref{eq:fourier_series_complex}.
+Both of these are equivalent and are just the different representations.
+The relationship between the two representations is defined in \lccref{eq:fourier_coefficient_equivalency}.
+\begin{align}
+  f(x)=       & \hat{a}_0 + \sum_{k=0}^{\infty} \hat{a}_k\cos(2\pi kx) + \hat{b}_k\sin(2\pi kx)\label{eq:fourier_series_sine_cosine} \\
+  f(x)=       & \sum_{k=-\infty}^{\infty} \hat{c}_k e^{2\pi ikx}\label{eq:fourier_series_complex}                                    \\
+  \hat{c}_k = & \begin{cases}
+                  \hat{a}_0,               & k = 0 \\
+                  (\hat{a}_k-\hat{b}_k)/2, & k > 0 \\
+                  (\hat{a}_k+\hat{b}_k)/2, & k < 0 \\
+                \end{cases}\label{eq:fourier_coefficient_equivalency}
+\end{align}
+
+To understand the complex coefficients better, we will do a brief summary of complex numbers.
 Complex numbers are numbers consisting of real and imaginary components.
@@
 \end{align}
-\autocite{DiscreteFourierTransform}
+The Discrete Fourier Transform (DFT) is shown in \lccref{eq:discrete_fourier_transform}.
+The DFT is used for discrete function values, which is the case for most practical applications \autocite{smithMathematicsDiscreteFourier2007,mathworksDiscreteFourierTransform2024}.
+This transform takes the discretized values and performs point wise multiplication between the values of the function and the basis function for a specific wave number.
+This is equivalent to the dot product between vectors which measures how large the projection of one vector on the other.
+Intuitively, this process \enquote{measures} how much of the discretized function is aligned with the basis function of that specific wave number.
+This measure is the coefficient for that wave number.
+The computation is repeated for all wave numbers.
+The inverse DFT calculates the function values from the computed coefficients as shown in \lccref{eq:inverse_discrete_fourier_transform}.
 \begin{align}
-  c_k=\sum_{n=0}^{N-1} f_n e^{-i2\pi kn/N} \label{eq:discrete_fourier_transform}\\
-  f_n=\sum_{k=0}^{N-1} c_k e^{i2\pi kn/N} \label{eq:inverse_discrete_fourier_transform}
+  \hat{c}_k= & \sum_{n=0}^{N-1} f_n e^{-2\pi ikn/N} \label{eq:discrete_fourier_transform}                   \\
+  f_n=       & \sum_{k=-N/2}^{N/2-1} \hat{c}_k e^{2\pi ikn/N} \label{eq:inverse_discrete_fourier_transform}
 \end{align}
 
+The implementation of the DFT and inverse DFT can affect the performance of the operation.
+The naive approach of implementing the equations exactly, while flexible in ways such as the wave numbers to compute coefficients for, is not the most efficient way.
+For faster computation, the aptly named Fast Fourier Transform (FFT) algorithm is used \autocite{chuFFTBlackBox2000}.
+This algorithm computes the DFT efficiently by exploiting symmetries that exist in and properties of the DFT\@.
+The Cooley-Tukey algorithm, arguably one of the most well known variation, uses a divide and conquer strategy by dividing the DFT into two at each step.
+This means that the discretized function would need to have discretization that is of the power of two.
+Methods have been developed to get around this, such as padding the data with zeroes to the next power of two and scaling the results accordingly.
+FFT algorithms can achieve a computational complexity of \(O(n\log(n))\) in comparison to \(O(n^2)\) complexity of the naive DFT algorithm.
+
+% Derivatives and antiderivatives of fourier series
+The Fourier series has an important property that is very important to this study.
+Taking the derivative of the Fourier series in \lccref{eq:fourier_series_complex} with respect to \(x\) results in \lccref{eq:fourier_series_complex_derivative}.
+Assuming we represent the derivative function is represented as another Fourier series with coefficients \(\hat{f'}_k\), the derivative coefficients can be computed from the coefficients of the original function \(f\) as shown in \lccref{eq:fourier_coeff_derivative}.
+This shows that the derivative of a Fourier series can be obtained trivially by simply multiplying the coefficients with the coefficients of the basis function exponents.
+The antiderivative can similarly be obtained by using the same relation and dividing the coefficients of the original function with the same scaling factor.
+Notice that the wave number is included in the scaling factor.
+This means that higher frequency coefficients get scaled more.
+For derivatives this amplifies the higher frequencies more and the antiderivative will smooth out the function by suppressing the higher frequencies.
+\begin{align}
+  \dv{x}f(x)=  & \sum_{k=-N/2}^{N/2-1} \hat{c}_k (2\pi ik) e^{2\pi ikx} \label{eq:fourier_series_complex_derivative} \\
+  =            & \sum_{k=-N/2}^{N/2-1} \hat{f'}_k e^{2\pi ikx}\nonumber                                              \\
+  \hat{f'}_k = & (2\pi ik)\hat{c}_k\label{eq:fourier_coeff_derivative}
+\end{align}
+
+This property of Fourier series is used in the spectral method \autocite{shenSpectralMethodsAlgorithms2011,boydChebyshevFourierSpectral2001}.
+The ability to compute derivatives as a simple multiplication motivates its use to solve PDEs.
+By using Fourier series to represent the solution to PDEs, one can isolate the solution coefficients in terms of the other values.
+This is a powerful tool for linear PDEs.
+For nonlinear PDEs like the Burgers' equation, the solution coefficients are not able to be obtained as easily.
+This is due to the multiplication between the solution and its derivatives.
+The solution is to iteratively compute the value of the solution coefficient until it converges.
+For problems in domains with more than one dimension, such as space and time for the Burgers' equation, one of the dimensions can be integrated separately using a different method like Euler's method.
+This hybrid approach is called the Method of Lines.
+Using the Fourier series, the spectral method is able to solve PDEs to a high degree of accuracy and efficiency for smooth functions.
+
+\section{Method of Manufactured Solutions}
+\noindent A method commonly used for testing PDE solvers is the Method of Manufactured Solutions (MMS).
+This is to verify that the program runs but also is accurate in its solutions.
+The concern of this method is not the physical realism of the solutions, rather it is a purely mathematical concern.
+This is because verification of a method means making sure the code accurately implements the mathematical equation.
+This very specific goal, places no requirement on the realism of any solutions used in the verification of the method \autocite{roacheCodeVerificationMethod2002,salariCodeVerificationMethod2000,vedovotoApplicationMethodManufactured2011}.
+
+The method solves PDEs by simply utilizing the equations involved.
+This method requires that the form of the PDE used must account for a forcing term.
+This is typically done by adding the forcing term as the residual.
+The residual is simply the right-hand side after moving all terms to the left-hand side.
+Without a forcing term, which translate to a forcing term of zero, the residual is the discrepancy between the right-hand side and left-hand side of the equation.
+By encapsulating the residual in the forcing term, any solution can be chosen because the discrepancy is now accounted as the outside forces the forcing term represent.
+This is the principle behind MMS\@.
+Combining this approach with the spectral method and Fourier series with arbitrary coefficients, the forcing term can be computed as a Fourier series given the solution as another Fourier series and other parameters.
+For verification purposes of numerical methods, using the solutions and other parameters generated with MMS require the implemented method to admit forcing terms.
+An example of MMS can be seen in \lccref{sec:data_generation_burgers}.
+
+% other properties we use such as Parseval's identity
+
 \section{Least Squares Support Vector Machine}
-\noindent An arguably fundamental model widely used whether in pedagogical settings or otherwise is the support vector machine.
-It dates back to works by Vapnik \& Lerner in 1963 (Recognition of Patterns with help of Generalized Portraits) and V.
-N.
-Vapnik \& A.
-Ya.
-Chervonenkis in 1964 (A note on one class of perceptrons/On a perceptron class).
-As the development on SVM continued, what originally was a model for classification of separable data generalized to regression tasks as well Vapnik (2000 The Nature of Statistical Learning Theory).
-\subsection{Disadvantages}
-However, the main disadvantage of LSSVMs are the fact that they do not have the sparse property of SVMs which can leave performance on the table.
-A simple mitigation can be done by filtering training samples with small absolute values of lagrangian multipliers \autocite{haifengwangComparisonSVMLSSVM2005}.
+\noindent An arguably fundamental model widely used both in pedagogical settings or otherwise is the Support Vector Machine (SVM).
+It dates back to works by \textcite{vapnik1963recognition} and \textcite{vapnik1964perceptron}.
+As the development on SVM continued, what originally was a model for classification of separable data generalized to regression tasks as well \autocite{vapnikNatureStatisticalLearning2000}.
+The support vector machine is essentially a straight line fitting model.
+We will refer to the line as a hyperplane for a more general term in multiple dimensions.
+For classification, this hyperplane divides the samples into two sides.
+One side being of one class and the other for samples not in that class.
+The optimization is done such that the line is at the maximum distance from the nearest points.
+This formulation still has a major weakness, which is that the model many not find a line that perfectly separates all the points.
+To allow for some error, slack terms are added to the constraints of the model.
+For regression, SVMs follow a similar approach with classification.
+However, rather than separating the inputs, the line is optimized to best fit the samples.
 
-To derive the least squares support vector regression (J.A. Suykens LSSVM Book) model we start with the linear expression:
-
+% Derivation of LSSVR
+The quadratic nature of the SVM objective function means that it is guaranteed to have an optimum point.
+However, with the motivation to further simplify the SVM, the Least-Squares Support Vector Machine (LSSVM) was introduced by \textcite{suykensLeastSquaresSupport2005}.
+The aim of this proposed method was to have a simpler formulation of the SVM while retaining the majority of benefits it provided.
+Here, we will focus on the regression problem and as such the LSSVM for regression.
+Given a pair of features \(\vb{x}\in\mathcal{X}\) and labels \(y\in\mathcal{Y}\), the approximate linear model is given by \lccref{eq:lssvr_primal_linear_model} where \(W\) is the model weights and \(b\) is the bias which are both parameters of the model.
 \begin{equation}
-  y=W^{\intercal}\vb{x}+b
+  y=W^{\intercal}\vb{x}+b\label{eq:lssvr_primal_linear_model}
+\end{equation}
+Training the model means optimizing the model by adjusting its parameters to minimize the objective function in \lccref{eq:lssvr_primal_objective} where \(e_k\) is the difference between the prediction \(W^{\intercal}\vb{x}+b\) and the label \(y\).
+\begin{equation}
+  \min_{W,b,e} J(W,e) = \frac{1}{2}W^{\intercal}W + C\frac{1}{2}\sum_{k=1}^{n}e_{k}^{2}\label{eq:lssvr_primal_objective}
+\end{equation}
+Such that
+\begin{equation}
+  y_{k}=W^{\intercal}\vb{x}_{k}+b+e_{k} \qquad k=1,\dots,n\label{eq:lssvr_primal_constraint}
+\end{equation}
+To find the optimal point for the objective function given the constraint \lccref{eq:lssvr_primal_constraint}, we must construct the Lagrangian which combines the objective function with the constraint.
+The Lagrangian is shown in \lccref{eq:lssvr_primal_lagrangian} where \(\alpha_{k}\) is the Lagrange multiplier for the \(k\)\textsuperscript{th} sample constraint.
+\begin{equation}
+  L(W,b,e;\vb{\alpha}) = \frac{1}{2}W^{\intercal}W + C\frac{1}{2}\sum_{k=1}^{n}e_{k}^{2} - \sum_{k=1}^{n}\alpha_{k} \left(W^{\intercal}\vb{x}_{k}+b+e_{k} - y_{k} \right)\label{eq:lssvr_primal_lagrangian}
 \end{equation}
 
+To compute the optimal parameters, first the point at which the gradient is zero for each parameter must be found.
+This is simply by equating to zero the derivative of the Lagrangian with respect to each parameter.
+This is called the Karush-Khun-Tucker optimality condition.
+Computing this for our Lagrangian results in \lccref{eq:lssvr_KKT}.
 \begin{equation}
-  \min_{W,e} J(W,e) = \frac{1}{2}W^{\intercal}W + C\frac{1}{2}\sum_{k=1}^{n}e_{k}
+  \begin{split}
+    \pdv{L}{W} = 0 \rightarrow          & W           = & \sum_{k=1}^{n}\alpha_{k}\vb{x}_{k}                      \\
+    \pdv{L}{b} = 0 \rightarrow          & 0           = & \sum_{k=1}^{n}\alpha_{k}                                \\
+    \pdv{L}{e_{k}} = 0 \rightarrow      & \alpha_{k}  = & C e_{k}                            & \qquad k=1,\dots,n \\
+    \pdv{L}{\alpha_{k}} = 0 \rightarrow & y_{k}       = & W^{\intercal}\vb{x}_{k}+b+e_{k}    & \qquad k=1,\dots,n \\
+  \end{split}\label{eq:lssvr_KKT}
 \end{equation}
 
-Such that
+Substituting the relationships for the optimal parameters, we can rewrite the Lagrangian in terms of the Lagrangian multipliers and the bias.
+The reasoning for this choice will be explained later.
+The substitution yields \lccref{eq:lssvr_dual}.
+\begin{align}
+   & \begin{aligned}
+       L(W,b,e;\vb{\alpha}) & =  \frac{1}{2}\left(\sum_{k=1}^{n}\alpha_{k}\vb{x}_{k}^{\intercal}\right)\left(\sum_{l=1}^{n}\alpha_{l}\vb{x}_{l}\right) + \frac{1}{2C}\sum_{k=1}^{n}\alpha_{k}^{2} \\
+                            & \qquad - \sum_{k=1}^{n}\alpha_{k} \left(\sum_{l=1}^{n}\alpha_{l}\vb{x}_{l}^{\intercal}\vb{x}_{k}+b+\frac{\alpha_{k}}{C} - y_{k} \right)
+     \end{aligned}        \\
+   & \begin{aligned}
+       \phantom{L(W,b,e;\vb{\alpha})} & =  \frac{1}{2}\sum_{k=1}^{n}\sum_{l=1}^{n}\alpha_{k}\alpha_{l}\vb{x}_{k}^{\intercal}\vb{x}_{l} + \frac{1}{2C}\vb{\alpha}^{\intercal}\vb{\alpha}                                      \\
+                                      & \qquad - \sum_{k=1}^{n}\sum_{l=1}^{n}\alpha_{k}\alpha_{l}\vb{x}_{l}^{\intercal}\vb{x}_{k} -b\times 0 - \frac{1}{C}\vb{\alpha}^{\intercal}\vb{\alpha} + \sum_{k=1}^{n}\alpha_{k}y_{k}
+     \end{aligned} \nonumber \\
+   & \begin{aligned}
+       \phantom{L(W,b,e;\vb{\alpha})} & =  -\frac{1}{2}\sum_{k=1}^{n}\sum_{l=1}^{n}\alpha_{k}\alpha_{l}\vb{x}_{k}^{\intercal}\vb{x}_{l} - \frac{1}{2C}\vb{\alpha}^{\intercal}\vb{\alpha} + \vb{\alpha}^{\intercal}\vb{y} \\
+     \end{aligned}\label{eq:lssvr_dual}
+\end{align}
+subject to
 \begin{equation}
-  y_{k}=W^{\intercal}\vb{x}_{k}+b+e_{k} \qquad k=1,\dots,n
+  \sum_{k=1}^{n}\alpha_{k} = 0
 \end{equation}
 
-\begin{equation}
-  L(W,b,e;\vb{\alpha}) = \frac{1}{2}W^{\intercal}W + C\frac{1}{2}\sum_{k=1}^{n}e_{k} + \sum_{k=1}^{n}\alpha_{k} \left(W^{\intercal}\vb{x}_{k}+b+e_{k} - y_{k} \right)
-\end{equation}
-
-Derive the KKT system
-\begin{equation}
-  \begin{split}
-    \pdv{L}{W} = 0 \rightarrow & W = \sum_{k=1}^{n}\alpha_{k}x_{k} \\
-    \pdv{L}{b} = 0 \rightarrow & \sum_{k=1}^{n}\alpha_{k} = 0 \\
-    \pdv{L}{e_{k}} = 0 \rightarrow & \alpha_{k} = C e_{k} & \qquad k=1,\dots,n\\
-    \pdv{L}{\alpha_{k}} = 0 \rightarrow & W^{\intercal}\vb{x}_{k}+b+e_{k} - y_{k} = 0 & \qquad k=1,\dots,n\\
-  \end{split}
-\end{equation}
-
-After eliminating $W$ and $\vb*{e}$, with $\vb{1}_{n} = \langle 1,\dots,1\rangle$, $\vb{y} = \lbrack y_1, \dots, y_n \rbrack $, and ${\alpha} = \lbrack \alpha_1, \dots, \alpha_n \rbrack $ the solution is as follows in block matrix notation
+To extend the model further, the kernel trick was introduced by \textcite{vapnikNatureStatisticalLearning2000}.
+This allows SVMs to learn nonlinear problems.
+In order to achieve, the input data is mapped to a higher dimension.
+For example, a set of points along one dimension can be lifted to two dimension by adding another coordinate that is the square of the first.
+This operation leads to the line being able to separate the samples in the middle from the samples towards both edges by intersecting the now parabolic line of samples in two points instead of the original one.
+Doing this with more dimensions mean that the model can add more nonlinearity.
+This is done by simply replacing the features \(\vb{x}_{k}\) with the mapped features \(\phi(\vb{x}_{k})\).
+However, for high dimensional mappings this causes the size of the weights \(W\) to increase accordingly.
+This is especially concerning when we use mappings to infinite dimensions.
+Fortunately, the dual formulation only contains inner products (dot products for Euclidean spaces) for all operations with the features.
+This means that a kernel function \(K\) can be used to compute these inner products in the higher dimensions without having to deal with the actual high dimensional mappings directly.
+The first term of the dual can be reformulated as a matrix of the kernel values multiplied by the vectors of Lagrange multipliers \(\alpha \).
+The kernel matrix \(\Omega \) has elements of \(K(\vb{x}_{k},\vb{x}_{l})\).
+In addition, the minimization of the derived dual in \lccref{eq:lssvr_dual} is equivalent to the maximization of the equation multiplied by \(-1\).
+Putting all the above together we can construct the block matrix notation for the LSSVR optimal parameters shown in \lccref{eq:lssvr_solution} with \(\vb{1}_{n} = \langle 1,\dots,1\rangle \), \(\vb{y} = \lbrack y_1, \dots, y_n \rbrack \), and \({\alpha} = \lbrack \alpha_1, \dots, \alpha_n \rbrack \).
+Solving for the parameters which are the Lagrangian multipliers \(\vb{\alpha}\) and bias \(b\) can be done by doing least-squares.
 \begin{equation} \label{eq:lssvr_solution}
@@
 
-The solution in \cref{eq:lssvr_solution}
-
+The construction of matrices in \lccref{eq:lssvr_solution} and the solving procedure is presented by the pseudocode in \lccref{alg:lssvr_training}.
+Given a training set of length \(n\), features \(\vb{X}\), and labels \(\vb{y}\).
+Training the LSSVM means computing the values of Lagrange multipliers \(\vb{\alpha}\) and bias \(b\) where \(K\) is the kernel function, \(\vb{A}\) is the right-hand side matrix of size \(n+1\) by \(n+1\), \(\vb{H}\) is sum of the kernel matrix and the diagonal matrix of reciprocals of the regularization parameter \(C\) of size \(n\) by \(n\), \(\vb{I}\) is the identity matrix, \(\vb{B}\) is the right-hand side vector of size \(n+1\), and \(\vb{S}\) is the solution parameter vector of size \(n+1\).
 \begin{algorithm}[H]
@@
   \begin{algorithmic}[1]
-    \Procedure{SolveLSSVR}{$\vb{X}, \vb{y}, \gamma $}
+    \Procedure{SolveLSSVR}{$\vb{X}, \vb{y}, C $}
     \State{\(\Omega \gets [[]]\)}
@@
     \EndFor{}
-    \State{\(\vb{H} \gets \Omega + \frac{\vb{I}}{\gamma}\)}
+    \State{\(\vb{H} \gets \Omega + \frac{\vb{I}}{C}\)}
     % \State $\vb{1} \gets [1,1,...,1]$
@@
     \EndFor{}
-    \State{\(\vb{A}^{\dagger} \gets pseudoInverse(\vb{A})\)}
-    \Comment{Compute solution using pseudo inverse}
+    \State{\(\vb{A}^{\dagger} \gets leastSquares(\vb{A})\)}
+    \Comment{Compute solution using least-squares}
     \State{\(\vb{S} \gets \vb{A}^{\dagger}\vb{B}\)}
@@
 
-The basic pseudocode from the LSSVM Equation for function regression is defined in \lccref{alg:lssvr_training} for a training set of length $n$, features $\vb{X}$, and labels $\vb{y}$.
-Training the LSSVM means computing the values of langrange multipliers $\vb{\alpha}$ and bias $b$.
-$K$ is the kernel function used to compute the inner products in high dimensional space, here we assume the RBF kernel.
-$\vb{A}$ is a matrix of size $n+1$ by $n+1$.
-$\vb{H}$ is a matrix of size $n$ by $n$.
-$\vb{I}$ is the identity.
-$\vb{B}$ is a vector of size $n+1$.
-$\vb{S}$ is a vector of size $n+1$.
-
 After training the model can be used for prediction of unseen features.
-The pseudocode for prediction is shown in \lccref{alg:lssvr_prediction} for prediction features $\vb{U}$ with \(p \) samples.
-The trained model uses the training features themselves $\vb{X}$ with \(n \) samples, the learned multipliers of training points $\vb{\alpha}$, and the bias $b$.
-
+The pseudocode for prediction is shown in \lccref{alg:lssvr_prediction} for prediction features \(\vb{U}\) with \(p \) samples.
+The trained model uses the training features themselves \(\vb{X}\) with \(n \) samples, the learned multipliers of training points \(\vb{\alpha}\), and the bias \(b\).
 \begin{algorithm}[H]
@@
   \begin{algorithmic}[1]
-    \Require $\vb{U}, \vb{\alpha}, \vb{X}, b$
-    \Ensure $\vb{v}$
-    \State $\Omega \gets [[]]$ \Comment{Construct matrix of inner products in high dimensional space}
+    \Require{\(\vb{U}, \vb{\alpha}, \vb{X}, b\)}
+    \Ensure{\(\vb{v}\)}
+    \State{\(\Omega \gets [[]]\)} \Comment{Construct matrix of inner products in high dimensional space}
 
-    \For{$k=0 \to p$}
-    \For{$l=0 \to n$}
-    \State$\Omega_{k,l}\gets K(\vb{U}_{k},\vb{X}_l)$
-    \EndFor
-    \EndFor
-    \State $\vb{v} \gets \Omega\vb{\alpha} + \vb{1}_{m}b$
+    \For{\(k=0 \to p\)}
+    \For{\(l=0 \to n\)}
+    \State{\(\Omega_{k,l}\gets K(\vb{U}_{k},\vb{X}_l)\)}
+    \EndFor{}
+    \EndFor{}
+    \State{\(\vb{v} \gets \Omega\vb{\alpha} + \vb{1}_{m}b\)}
   \end{algorithmic}
@@
 
-In this exmple we will be using the function $2x^2+4$. The values of this function can be seen in Table \ref{table:1}.
+The choice of kernel used to construct the kernel matrix is problem specific. Three kernels are most commonly used in SVMs. These kernels are:
+\begin{enumerate}
+  \item Linear Kernel
 
-\begin{table}[H]
-  \centering
-  \begin{tabular}{@{}lll@{}}
-    \toprule
-    No & x       & y       \\ \midrule
-    1  & 0.0     & 4.0     \\
-    2  & 0.33... & 4.22... \\
-    3  & 0.66... & 4.88... \\
-    4  & 1.0     & 6.0     \\
-    \bottomrule
-  \end{tabular}
-  \caption{Example data of function $2x^2+4$} \label{table:1}
-\end{table}
-For $\Omega_{i,j}=K(x_i,x_j)=exp \left(-\frac{\norm*{x_i-x_j}^2}{2\sigma^2}\right)$
+        This kernel is the simplest with it being the dot product.
+It is recommended for cases where the number of features overwhelm the number of samples.
+The kernel is shown in \lccref{eq:linear_kernel}.
+Because this kernel operates in the original feature space, it is effective for linear problems.
+        \begin{equation}
+          K(\vb{x}_k,\vb{x}_l) = \vb{x}_k\cdot\vb{x}_l\label{eq:linear_kernel}
+        \end{equation}
+  \item Polynomial Kernel
 
-For example, with $\sigma=1$, $x_i=0.0$, \& $x_j = 0.33\dots$
+        The polynomial kernel is shown in \lccref{eq:poly_kernel}.
+This kernel allows the model to learn more complex nonlinear decision boundaries.
+The parameter \(c\) is a constant and \(d\) is the degree of the polynomial.
+The degree of the polynomial need to be monitored closely in order to avoid overfitting.
         \begin{equation}
-  \begin{split}
-    K(0.0,0.33) & = exp\left(-\frac{\norm*{0.0-0.33}^2}{2(1)^2}\right) \\
-    & = exp\left(-\frac{0.33^2}{2}\right) \\
-    & = 0.9460
-  \end{split}
+          K\left(\vb{x}_k,\vb{x}_l\right) = \left(\vb{x}_k\cdot\vb{x}_l+c\right)^{d} \label{eq:poly_kernel}
+        \end{equation}
+  \item Radial Basis Function Kernel
+
+        The RBF kernel is presented in \lccref{eq:rbf_kernel}.
+This kernel maps the inputs to infinite dimensional space.
+This enables the SVM to create decision boundaries which are not rigid.
+The RBF kernel is especially effective for nonlinear relationships between features and labels.
+The kernel has a parameter \(\sigma \) which is the scale parameter.
+This parameter affects how the kernel treats structures of different scales in the features.
+This parameter can be approximated roughly from the average variance of across all features multiplied by the number of features.
+        \begin{equation}
+          K(\vb{x}_k,\vb{x}_l) = \exp\left(-\frac{\lVert\vb{x}_k,\vb{x}_l\rVert^2}{2\sigma^2}\right) \label{eq:rbf_kernel}
+        \end{equation}
+\end{enumerate}
+
+% SVR Interpretation
+After an SVM model is trained, it can be dissected and analyzed to interpret the decisions the model came up with using the work of \textcite{ustunVisualisationInterpretationSupport2007}.
+There are two tools that \autocite{ustunVisualisationInterpretationSupport2007} introduced, which are the Correlation Image (CI) and the p-vector.
+First, the correlation image is aimed to present the contribution of each input feature to the kernel matrix.
+This is because of the loss of input feature information after computing the inner product using the kernel function.
+Given \(N\) training samples and \(m\) input features, the correlation image matrix can be computed as the matrix multiplication between the kernel matrix of the training input features with a shape of \((N,N)\) and the matrix of all training input features with a shape of \((N,m)\).
+The matrix multiplication results in a matrix with the same shape as the matrix of training samples.
+To show the correlation, the rows of the result matrix will need to be sorted according to the output values.
+
+The second tool is the p-vector.
+This tool seeks to inform the learned contributions of each input feature towards the output.
+The Lagrangian multipliers contain information on the contribution of each training sample towards the output.
+To link this with the input features, the multipliers are multiplied against the matrix of training inputs.
+This is done by transposing the matrix of training inputs and performing a matrix multiplication against the Lagrange multipliers.
+The result shows how much contribution each input contributes to the output.
+If we generalize to multiple outputs, the result is a matrix with the rows representing input features and columns representing each output.
+
+Both of these tools allow the user to analyze which inputs are important.
+In addition, the relationships learned can also be seen albeit with the caveat that the contributions are basically sums different contribution terms.
+And, there is method to separate each contribution term currently.
+Despite the shortcomings, these tools are invaluable in interpreting and understanding the learned model.
+
+% Advantages and Disadvantages
+LSSVMs have many benefits but also its own trade-offs.
+The main disadvantage of LSSVMs is the fact that they do not have the sparse property of SVMs.
+This can result in more computation during training and prediction since every single sample would need to be included in the computations.
+A simple mitigation can be done by filtering training samples with small absolute values of Lagrangian multipliers \autocite{haifengwangComparisonSVMLSSVM2005}.
+However, the benefits of simple matrix operations outweigh the disadvantages.
+This is because of the parallelization benefits of algorithms for simple matrix operations.
+With access to parallel hardware accelerators, the speedup for both training and inference can be very large.
+
+\section{Regression Metrics}\label{sec:evaluation_metrics}
+\noindent In order to evaluate the prediction of the model, four metrics are used.
+The metrics are divided into absolute metrics and relative metrics.
+Absolute metrics require context of scale to interpret their meaning \autocite{botchkarevNewTypologyDesign2019,alpaydinIntroductionMachineLearning2020}.
+Meanwhile, relative metrics often have a set range of values that it can have.
+This allows for quick interpretation of the severity of prediction errors.
+The metrics we discuss here are:
+\begin{enumerate}
+  \item MSE and RMSE
+
+        The Mean Squared Error (MSE) and its root RMSE, are both very popular metrics.
+Given target values \(y_i\) and predictions \(y'_i\) such that the difference is \(e_{i} = y'_i-y_i\), the MSE is shown in \lccref{eq:mse}.
+        \begin{equation}
+          MSE = \frac{1}{n}\sum_{i=1}^{n}e_{i}^{2}\label{eq:mse}
         \end{equation}
 
+        For The RMSE is simply the square root of the MSE\@.
+The MSE has the property of inflating large errors.
+The squaring also makes it so that the values are positive.
+This means that the absolute lowest error value is zero.
+However, the squaring does complicate the interpretation because the units are no longer the same as the predictions.
+Here the RMSE comes into play, because of the root square, the units are back to the original target units.
+This makes the MSE and RMSE very useful.
+  \item MAE
+
+        The second metric is the MAE\@. This metric is calculated as the mean of the absolute differences between the prediction and the target. The MAE is calculated as shown in \lccref{eq:mae}.
         \begin{equation}
-  \Omega\gets
-  \begin{bmatrix}
-    1.0000 & 0.9460 & 0.8007 & 0.6065 \\
-    0.9460 & 1.0000 & 0.9460 & 0.8007 \\
-    0.8007 & 0.9460 & 1.0000 & 0.9460 \\
-    0.6065 & 0.8007 & 0.9460 & 1.0000 \\
-  \end{bmatrix}
+          MAE = \frac{1}{n}\sum_{i=1}^{n}\abs{e_{i}}\label{eq:mae}
         \end{equation}
 
+        This metric is good at representing the errors without any distortions.
+Because there is no nonlinear components, the metric is very straightforward to interpret.
+Due to the use of the absolute value, the minimum value of the metric is also zero.
+  \item R\textsuperscript{2}
+
+        The third metric is the coefficient of determination.
+This metric can be seen as the ratio between the model's accuracy and a baseline model of mean values.
+Mathematically, this metric is calculated using \lccref{eq:r2} given target values \(y_i\) and predictions \(y'_i\).
         \begin{equation}
-  \vb{I}\frac{1}{\gamma}\to\vb{I}\frac{1}{5}\to
-  \begin{bmatrix}
-    0.2000 & 0.0000 & 0.0000 & 0.0000 \\
-    0.0000 & 0.2000 & 0.0000 & 0.0000 \\
-    0.0000 & 0.0000 & 0.2000 & 0.0000 \\
-    0.0000 & 0.0000 & 0.0000 & 0.2000
-  \end{bmatrix}
+          r2 = 1 - \frac{\sum_{i=1}^{n}(y_{i} - y'_{i})^{2}}{\sum_{i=1}^{n}(y_{i} - \bar{y})^{2}}\label{eq:r2}
         \end{equation}
 
+        Because the R\textsuperscript{2} is a relative metric, there is a range of possible values.
+First, the highest value possible is one.
+This happens when the predictions are exactly the same as the targets.
+For predictions that are no better than the average value, the score is zero.
+Scores below zero mean that the predictions are worse than the average value.
+  \item sMAPE
+
+        The final metric is the symmetric Mean Absolute Percentage Error.
+This metric has a range of values between zero for no error and two for high error.
+The values can be scaled by multiplying by 100 to obtain the percentages.
+Given target values \(y_i\) and predictions \(y'_i\) such that the difference is \(e_{i} = y'_i-y_i\), the sMAPE is calculated using \lccref{eq:smape} where \(\epsilon \) is a small value to prevent divisions by zero.
         \begin{equation}
-  \Omega+\vb{I}\frac{1}{5}\to H\to
-  \begin{bmatrix}
-    1.2000 & 0.9460 & 0.8007 & 0.6065 \\
-    0.9460 & 1.2000 & 0.9460 & 0.8007 \\
-    0.8007 & 0.9460 & 1.2000 & 0.9460 \\
-    0.6065 & 0.8007 & 0.9460 & 1.2000 \\
-  \end{bmatrix}
+          sMAPE = \frac{2}{N} \sum_{i=1}^{N}\frac{\abs{e_{i}}}{\max(\abs{y_{i}} + \abs{y'_{i}},\epsilon)}
         \end{equation}
 
-\begin{equation}
-  A\to
-  \begin{bmatrix}
-    0.0000 & 1.0000 & 1.0000 & 1.0000 & 1.0000 \\
-    1.0000 & 1.2000 & 0.9460 & 0.8007 & 0.6065 \\
-    1.0000 & 0.9460 & 1.2000 & 0.9460 & 0.8007 \\
-    1.0000 & 0.8007 & 0.9460 & 1.2000 & 0.9460 \\
-    1.0000 & 0.6065 & 0.8007 & 0.9460 & 1.2000 \\
-  \end{bmatrix}
-\end{equation}
+        Despite the name, sMAPE does have issues with asymmetry arising from the denominator.
+For cases where the prediction overpredicts and underpredicts by the same amount, depending on the value of the target, the metric may penalize the prediction closer to zero more than the one that is further.
+This is despite both predictions being the same absolute difference away from the target value.
 
-\begin{equation}
-  B\to
-  \begin{bmatrix}
-    0.0000 \\
-    4.0000 \\
-    4.2222 \\
-    4.8889 \\
-    6.0000 \\
-  \end{bmatrix}
-\end{equation}
+\end{enumerate}
 
-\begin{equation}
-  A^{\dag}\to
-  \begin{bmatrix}
-    -0.8994 & 0.4348  & 0.0652  & 0.0652  & 0.4348  \\
-    0.4348  & 2.0686  & -1.6490 & -0.5292 & 0.1096  \\
-    0.0652  & -1.6490 & 3.3774  & -1.1992 & -0.5292 \\
-    0.0652  & -0.5292 & -1.1992 & 3.3774  & -1.6490 \\
-    0.4348  & 0.1096  & -0.5292 & -1.6490 & 2.0686  \\
-  \end{bmatrix}
-\end{equation}
+\section{Python Language and PyTorch Library}
+\noindent The origins of the Python programming language began in the late 1980s as with its designer Guido van Rossum \autocite{rossumHistoryPythonBrief2009}.
+The language began with internal releases at the designer's workplace.
+Over thirty years later, today, the language has reached the stable version of \num{3.14}.
+Many today use Python as a high level language with very convenient features.
+Python is a multi-paradigm language with support for many styles of programs from standalone scripts to entire applications that use paradigms like object-oriented programming.
+Python also acts as a bridge for using software components written in other languages \autocite{rossumGlueItAll1998}.
+The language has a syntax that is relatively easy to understand.
+This has brought many people to the ecosystem and has consistently ranked the language as one of the most used programming languages in the world \autocite{stackoverflowTechnology2024Stack2024}.
+Specifically for the field of machine learning, Python enjoys a wide following \autocite{jetbrainsLanguagesStateDeveloper2023}.
+The machine learning ecosystem within python leverages Python's capability to interact with other languages to provide performant code that is still easy to use.
+This can be seen across different Machine Learning libraries in Python, such as Tensorflow, PyTorch, and Jax.
 
-\begin{equation}
-  A^{\dag}B\to S\to
-  \begin{bmatrix}
-    4.9421  \\
-    -0.6177 \\
-    -1.3737 \\
-    -0.5625 \\
-    2.5538  \\
-  \end{bmatrix}
-\end{equation}
-
-\begin{equation}
-  b\to 4.9421
-\end{equation}
-
-\begin{equation}
-  \alpha \to
-  \begin{bmatrix}
-    -0.6177 \\
-    -1.3737 \\
-    -0.5625 \\
-    2.5538  \\
-  \end{bmatrix}
-\end{equation}
-
-Prediction
-\begin{equation}
-  U\to
-  \begin{bmatrix}
-    0.3 \\
-    0.2 \\
-    0.5
-  \end{bmatrix}
-\end{equation}
-
-\begin{equation}
-  \Omega\to
-  \begin{bmatrix}
-    0.9560 & 0.9994 & 0.9350 & 0.7827 \\
-    0.9802 & 0.9912 & 0.8968 & 0.7261 \\
-    0.8825 & 0.9862 & 0.9862 & 0.8825 \\
-  \end{bmatrix}
-\end{equation}
-
-\begin{equation}
-  \Omega\alpha\to
-  \begin{bmatrix}
-    -0.4904 \\
-    -0.6170 \\
-    -0.2008 \\
-  \end{bmatrix}
-\end{equation}
-
-\begin{equation}
-  \Omega\alpha+b\vb{1}_{m}\to v\to
-  \begin{bmatrix}
-    4.4516 \\
-    4.3251 \\
-    4.7413 \\
-  \end{bmatrix}
-\end{equation}
-Where $\vb{1}_{m}$ is a vector of 1s with the length of $U$.
+PyTorch specifically, was originally developed by Meta AI as an open source project.
+Today it is part of the Linux Foundation \autocite{jimzemlinWelcomingPyTorchLinux2022}.
+As one of the most successful and important machine learning software project, PyTorch has a big community which provides support.
+The PyTorch ecosystem of other projects built around PyTorch, such as torchdiffeq \autocite{Chen_torchdiffeq_2021}, are part of what makes PyTorch an appealing choice when undertaking a Machine Learning project.
+At its core, PyTorch provides an implementation of tensors which are generalizations of matrices for arbitrary dimensions.
+The tensors are surrounded by operations that are related to its manipulation and use, such as matrix multiplications or even linear solvers.
+In addition, PyTorch also provides many of the tools for working with Neural Networks.
+Other parts of PyTorch deal with the data and preprocessing, such as a way to randomly sample data or the family of operations surrounding FFTs.
+The features and all other benefits of both Python and PyTorch, allow for rapid prototyping and is conducive to research projects.
+The community means help is also not far away.
+% Mean Squared Error (MSE & RMSE)
+% Mean Absolute Error (MAE)
+% Coefficient of Determination (R\textsuperscript{2})
+% Symmetric Mean Absolute Percentage Error (sMAPE)
 

### 2025-01-09 skripsi/chapter4.tex
finish ch2 and start ch5

@@
 This means that despite limiting the set of functions to Fourier functions, the behavior of PDEs with other sets of functions can be approximated to a certain extent.
-The final benefit is the mature ecosystem around these functions which include fast algorithms for the Fourier transform and even numerical approaches for solving known PDEs like the previously mentioned spectral method.
-In summary the generated data consists of features and labels which are Fourier functions implicitly defining the relationship enforced by a PDE and scenario.
-After establishing the kind of functions to be used in dataset generation, the process can proceed.
-There are 4 steps involved in the data generation:% TODO: add reference to second chapter for spectral method, fourier transform, and other external concepts.
+The final benefit is the mature ecosystem around these functions which include fast algorithms for the Fourier transform and even numerical approaches for solving known PDEs like the previously mentioned spectral method which we discussed in \lccref{sec:fourier_discussion}.
+In summary, the generated data consists of features and labels which are Fourier coefficients implicitly defining the relationship enforced by a PDE and scenario.
+To proceed with the data generation, there are 4 steps involved:
 \begin{enumerate}
@@
 \begin{align}
-  \dv{u\left( t \right)}{t} & = a\left( t \right) \label{eq:derivative}                         \\
   u\left( t \right)         & = \sum_{k} \hat{u}_k e^{2\pi ikt} \label{eq:fourier_speed}        \\
@@
 This choice was made such that most wave numbers will have a coefficient of close to zero leaving a sparse set of wave numbers to mostly affect the resulting function.
-In total, 5000 unique functions are generated with 100 complex coefficients each.
+In total, \num{5000} unique functions are generated with \num{100} complex coefficients each.
 
@@
 These coefficients are then used to compute the function values inside the domain.
-The two-hour time window is represented by a grid of 500 discrete points.
+The two-hour time window is represented by a grid of \num{500} discrete points.
 With the coefficients and evaluation points ready, the function values are computed using \lccrefs{eq:fourier_speed,eq:fourier_acceleration}.
@@
 \end{figure}
-% TODO: interesting note that model trains better on function to coefficient task when the antiderivative is computed from the randomly generated derivative than if the derivative is computed from the randomly generated antiderivative.
+% TODO: interesting note that the model trains better on function to coefficient task when the antiderivative is computed from the randomly generated derivative than if the derivative is computed from the randomly generated antiderivative.
 THIS NEEDS A REASON AND ANALYSIS SO MIGHT NOT BE NEEDED IN THIS WRITING.
@@
 
-\subsection{Data Generation: Burgers' Equation}
+\subsection{Data Generation: Burgers' Equation}\label{sec:data_generation_burgers}
 \noindent The second dataset generated in this study concerns the Burgers' equation.
@@
 For a velocity of \(u(x, t)\), viscosity of \(\nu \), and forcing term of \(f(x, t)\), the formulation of the forced Burgers' equation is shown in \lccref{eq:forced_viscous_burgers}.
-\begin{align}
-  \pdv{u}{t}+u\pdv{u}{x}-\nu\pdv[2]{u}{x} & = f \label{eq:forced_viscous_burgers}
-\end{align}
+
 The domain of we consider here is based on an exact solution of the equation.
@@
 Since the forcing term is dependent on the solution in this step, the only parameter to determine is the viscosity.
-We choose three constant viscosity values which are 0.1, 0.01, and 0.0.
+We choose three constant viscosity values which are \num{0.1}, \num{0.01}, and \num{0.0}.
 These values are chosen so that a variety of behaviors are represented in the dataset from viscous to inviscid flow.
 
-After this, in the third step, the solution functions \(u \) are generated with 8 modes in time and 8 in space and 500 unique function samples for each viscosity value.
+After this, in the third step, the solution functions \(u \) are generated with 8 modes in time and 8 in space and \num{500} unique function samples for each viscosity value.
 Since we don't factor the viscosity in at this point, for ease of comparison, we ensure the same solutions are generated every time by using a new instance of the generator with the same seed number each time.
@@
 The filter for time and variables is shown in \lccref{fig:wb2_retrieval}.
-The reason for the different time ranges between training and testing is to reduce the risk of information leakage accross the training and testing sets.
+The reason for the different time ranges between training and testing is to reduce the risk of information leakage across the training and testing sets.
 This ensures that the testing scores we measure will be for the most part from the generalization that model learned during training.
@@
     \end{adjustbox}
-    \caption{}\label{fig:wb2_train_data}
+    \caption{2-meter temperature}\label{fig:wb2_train_data}
   \end{subfigure}
@@
     \end{adjustbox}
-    \caption{}\label{fig:wb2_clim_data}
+    \caption{Climatology}\label{fig:wb2_clim_data}
   \end{subfigure}
@@
     \end{adjustbox}
-    \caption{}\label{fig:wb2_train_anomaly}
+    \caption{2-meter temperature anomaly}\label{fig:wb2_train_anomaly}
   \end{subfigure}
   \caption{Data retrieved:(\subref{fig:wb2_train_data}) 2-meter temperature at January 1, 1995 6:00 UTC\@.
-(\subref{fig:wb2_train_anomaly}) Anomaly for 2-meter temperature at January 1, 1995 6:00 UTC\@.
-(\subref{fig:wb2_clim_data}) 2-meter temperature climatology for the first day of the year at hour 6 UTC\@.}\label{fig:wb2_data}
-\end{figure}
-
-After filtering, our training set has the dimensions of 27760 time steps, 64 longitude, and 32 latitude.
-The testing set on the other hand has 4384 time steps and the same values for the other two dimensions.
+(\subref{fig:wb2_clim_data}) 2-meter temperature climatology for the first day of the year at hour 6 UTC\@.
+(\subref{fig:wb2_train_anomaly}) Anomaly for 2-meter temperature at January 1, 1995 6:00 UTC\@.}\label{fig:wb2_data}
+\end{figure}
+
+After filtering, our training set has the dimensions of \num{27760} time steps, \num{64} longitude, and \num{32} latitude.
+The testing set on the other hand has \num{4384} time steps and the same values for the other two dimensions.
 For uses, such as a validation set during hyperparameter optimization, one can use a subset of the training set.
-The dimensions of the climatology are 4 for hour (0, 6, 12,\& 18), 366 for day of year, 64 for longitude, and 32 for latitude.
+The dimensions of the climatology are 4 for hour (0, 6, 12,\& 18), \num{366} for day of year, \num{64} for longitude, and 32 for latitude.
 
@@
 This entails solving the dimensions other that time with methods such as the finite differences method or the spectral method.
-The time dimension is then separately solved using the finite differences method such as the form shown in \lccref{eq:time_step_function} \autocite{schiesserNumericalMethodLines2012,sadikuSimpleIntroductionMethod2000}.
+The time dimension is then separately solved using FDM such as the form shown in \lccref{eq:time_step_function} \autocite{schiesserNumericalMethodLines2012,sadikuSimpleIntroductionMethod2000}.
 This is the form that the Burgers' equation dataset will be used in.
@@
 
-The input and output functions are then transformed into basis coefficients using the Fourier transform. % TODO: add reference to fourier transform in chapter 2
+The input and output functions are then transformed into basis coefficients using the Fourier transform we discussed in \lccref{sec:fourier_discussion}.
 Once the coefficients are computed, the input and output sample pairs are split into train, test, and validation subsets.
@@
 Using the computational model design in \lccref{sec:computational_model_design}, the computational model is implemented as a library using the Python programming language.
-The development process itself is based on the iterative development model as mentioned in \lccref{sec:development method}.
+The development process itself is based on the iterative development model as mentioned in \lccref{sec:development_method}.
 In this section, the output iterative processes are consolidated and explained together.
@@
 Similar to how subtraction is just a modification of the addition operation, the integral or antiderivative operator is also implemented simply by changing the operation with the term multiplier from multiplication to division.
-% TODO: change the reference to specific equations for calculus in spectral domain in ch2
 
@@
 The first step is to convert the testing input into real representations and then predicting the output function.
-The predicted output are then compared to the testing outputs using many metrics including RMSE, MSE, MAE, R\textsuperscript{2}, SMAPE, RRSE, and the number of Nan values present in the predicted output.
+The predicted output are then compared to the testing outputs using many metrics including RMSE, MSE, MAE, R\textsuperscript{2}, sMAPE, RRSE, and the number of Nan values present in the predicted output.
 The same comparison process is carried out again for the function values which are evaluated at the specified resolution.
@@
 The spectral residual of the Burgers' equation which is used in the method of manufactured solution generation approach is implemented as shown in \lccref{fig:burgers_spectral_residual_impl}.
-As with the right-hand side function, we use the psuedospectral approach for computing the convolution term to avoid large computational expenses for higher number of modes.
+As with the right-hand side function, we use the pseudospectral approach for computing the convolution term to avoid large computational expenses for higher number of modes.
 The function value residual is also implemented similarly to the antiderivative version.
@@
 \section{Experimental Results}\label{sec:experimental_results}
-\noindent In this section, the results of each experimental scenario is presented and analyzed. The results come in the form of testing metrics mentioned in . %TODO: add reference to the metrics used.
-The model interpretations are displays of the correlation image and the p-matrix. The function values and coefficients themselves will also be plotted depending on the number of dimensions.
+\noindent In this section, the results of each experimental scenario is presented and analyzed.
+The results come in the form of testing metrics mentioned in \lccref{sec:evaluation_metrics}.
+The model interpretations are displays of the correlation image and the p-matrix.
+The function values and coefficients themselves will also be plotted depending on the number of dimensions.
 
@@
 Comparing the absolute metrics for the same table, we see the same general trend that the higher viscosity show the model performing worse.
+For reference, the maximum amplitude of the functions on average are \num{2.56e-02}.
+This puts the error in an order of magnitude less than the average maximum amplitude.
+For the coefficients, on average, the maximum absolute value at each time step is \num{9.29e-02}.
+This means for the viscosity of 0.0 and \num{0.01}, the error is roughly 1 to 9 of the maximum absolute value.
 
@@
 \end{table}
+
+The predictions from test features are processed through the Fourier inverse transform to evaluate the function values.
+The direct predictions, which is the anomaly, is shown in \lccref{fig:sc3_anomaly_predictions}.
+The model seem to be predicting less extreme values that are noticeable in the target.
+Specifically areas over North America, Central Asia, and parts of Antarctica show lower temperature anomaly than expected.
+We also loose detail in areas which should have a lower anomaly such as northern areas of Africa, Greenland, and South Asia.
+The lack of detail seems to be a problem of underestimation.
+We believe this is caused by the so-called \enquote{double penalty} issue caused by the loss function used for the LSSVR \autocite{lledoScaledependentVerificationPrecipitation2023}.
+The predictions tend to be closer to the mean of the data to avoid the extra penalty from a wrong prediction with a high value.
+One way to allow for finer details that are less accurate is to penalize the higher frequency wave numbers less compared to the lower frequency wave numbers.
+For our case this means the LSSVR for each output will have their regularization parameter decreased to allow the model to focus less on the errors for higher frequencies.
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{\linewidth}
+    % \centering
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/wb2_anom_pred.pgf}
+    \end{adjustbox}
+    \caption{Predicted 2-meter temperature anomaly.}\label{fig:sc3_anomaly_pred}
+  \end{subfigure}
+  \begin{subfigure}{\linewidth}
+    % \centering
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/wb2_anom_target.pgf}
+    \end{adjustbox}
+    \caption{Target 2-meter temperature anomaly.}\label{fig:sc3_anomaly_target}
+  \end{subfigure}
+  \caption{2-meter temperature anomaly prediction for the 1\textsuperscript{st} of January 2020 at 6:00 UTC based on the previous anomaly at 0:00 UTC.}\label{fig:sc3_anomaly_predictions}
+\end{figure}
+
+The state predictions which is obtained by adding the climatology to the predicted anomaly is shown in \lccref{fig:sc3_state_predictions}.
+This further shows areas of discrepancy between the prediction and the target.
+The area in the South Pacific show that the target has a higher difference temperature compared to the prediction.
+This smoothness in the prediction is easier to see for areas in the ocean.
+Many sharp features are lost and the state prediction start to resemble averaged view of the climatology.
+We must also take into account that the model only used temperature distribution data.
+Other pieces of information we know to be crucial to weather prediction such as wind speed or pressure was not included in the inputs.
+With this in consideration the model was still able to learn some relationships defined by governing equations of weather.
+%TODO: decide to mention the results of this or not (https://sites.research.google/weatherbench/deterministic-scores/)
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{\linewidth}
+    % \centering
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/wb2_state_pred.pgf}
+    \end{adjustbox}
+    \caption{Predicted 2-meter temperature.}\label{fig:sc3_state_pred}
+  \end{subfigure}
+  \begin{subfigure}{\linewidth}
+    % \centering
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/wb2_state_target.pgf}
+    \end{adjustbox}
+    \caption{Target 2-meter temperature.}\label{fig:sc3_state_target}
+  \end{subfigure}
+  \caption{2-meter temperature prediction for the 1\textsuperscript{st} of January 2020 at 6:00 UTC based on the previous anomaly at 0:00 UTC.}\label{fig:sc3_state_predictions}
+\end{figure}
+
 The p-matrix and correlation image is shown in \lccref{fig:sc3_interpretation}.
@@
 
-The predictions from test features are processed through the Fourier inverse transform to evaluate the function values.
-The direct predictions, which is the anomaly, is shown in \lccref{fig:sc3_anomaly_predictions}.
-The model seem to be predicting less extreme values that are noticeable in the target.
-Specifically areas over North America, Central Asia, and parts of Antarctica show lower temperature anomaly than expected.
-We also loose detail in areas which should have a lower anomaly such as northern areas of Africa, Greenland, and South Asia.
-The lack of detail seems to be a problem of underestimation.
-We believe this is caused by the so-called \enquote{double penalty} issue caused by the loss function used for the LSSVR \autocite{lledoScaledependentVerificationPrecipitation2023}.
-The predictions tend to be closer to the mean of the data to avoid the extra penalty from a wrong prediction with a high value.
-One way to allow for finer details that are less accurate is to penalize the higher frequency wave numbers less compared to the lower frequency wave numbers.
-For our case this means the LSSVR for each output will have their regularization parameter decreased to allow the model to focus less on the errors for higher frequencies.
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    % \centering
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_anom_pred.pgf}
-    \end{adjustbox}
-    \caption{Predicted 2-meter temperature anomaly.}\label{fig:sc3_anomaly_pred}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    % \centering
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_anom_target.pgf}
-    \end{adjustbox}
-    \caption{Target 2-meter temperature anomaly.}\label{fig:sc3_anomaly_target}
-  \end{subfigure}
-  \caption{2-meter temperature anomaly prediction for the 1\textsuperscript{st} of January 2020 at 6:00 UTC based on the previous anomaly at 0:00 UTC.}\label{fig:sc3_anomaly_predictions}
-\end{figure}
-
-The state predictions which is obtained by adding the climatology to the predicted anomaly is shown in \lccref{fig:sc3_state_predictions}.
-This further shows areas of discrepancy between the prediction and the target.
-The area in the South Pacific show that the target has a higher difference temperature compared to the prediction.
-This smoothness in the prediction is easier to see for areas in the ocean.
-Many sharp features are lost and the state prediction start to resemble averaged view of the climatology.
-We must also take into account that the model only used temperature distribution data.
-Other pieces of information we know to be crucial to weather prediction such as wind speed or pressure was not included in the inputs.
-With this in consideration the model was still able to learn some relationships defined by governing equations of weather.
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    % \centering
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_state_pred.pgf}
-    \end{adjustbox}
-    \caption{Predicted 2-meter temperature.}\label{fig:sc3_state_pred}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    % \centering
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_state_target.pgf}
-    \end{adjustbox}
-    \caption{Target 2-meter temperature.}\label{fig:sc3_state_target}
-  \end{subfigure}
-  \caption{2-meter temperature prediction for the 1\textsuperscript{st} of January 2020 at 6:00 UTC based on the previous anomaly at 0:00 UTC.}\label{fig:sc3_state_predictions}
-\end{figure}
-
 The results of our experiments show that the proposed model has the ability to learn the relationships that PDEs and other governing equations define.

### 2025-01-09 skripsi/chapter5.tex
finish ch2 and start ch5

@@
 \section{Conclusion}
+\noindent Based on the results of the research into \lower{\judul}, several conclusions can be drawn.
+\begin{enumerate}
+    \item The proposed SpectralSVR model is able to learn the relationships defined by PDEs.
+This is done with a computational model that with four phases which are data preparation, data transformation, model training, and finally model evaluation.
+    \item Interpretation of the proposed model can be done to a certain extent using two tools which are the correlation image and p-matrix developed by \textcite{ustunVisualisationInterpretationSupport2007}.
+    \item The proposed model is also capable in dealing with noise and partial data as shown in scenario 1 and 3.
+    \item The model's capabilities are also verified using exact solution. This revealed that for some configurations the model is able to successfully generalize to exact solutions.
+\end{enumerate}
 % \noindent Bab ini merupakan pamungkas berupa rincian rangkuman yang merupakan simpulan dari analisis yang telah dilakukan.
@@
 \section{Future Work}
+During the work on this study, some limitations were imposed, and many new questions also went unanswered. Here, we would like to list some potential avenues for future work:
+\begin{itemize}
+    % TODO: reword these points
+    \item Most of the synthetic data used to in scenario 1 and 2 were not realistic as they were generated using MMS.
+The addition of more realistic data generated by traditional numerical methods or other sources could improve the model's performance and .
+    \item Test how auto regression of weather is compared to the target data
+    \item Compare inverse prediction results with traditional derivatives such as the spectral method or FDM
+    \item Compare the proposed method to other methods in comparable situations
+    \item Measure and compare the efficiency (time) of computing solutions compared to traditional and machine learning-based methods
+    \item Add more basis functions like spherical harmonics or wavelet basis
+    \item Add more regression models, specifically more support vector regression models to continue being able to use the correlation image and p-matrix
+    \item Use better metrics for measuring performance such as the \enquote{standard error of regression}
+    \item Analyze the performance with different hyperparameters or data sizes and plot the result in charts.
+    \item Analysis of the error by wave number.
+    \item Solve the problem of double penalty that causes the model to tend towards smooth solutions \autocite{brownForecastsSpatialFields2011,NIPS2017_44a2e080}.
+Try to use more regularization (higher regularization parameter) for higher wave numbers.
+    \item Add support for sparse data by using data assimilation techniques like the Lomb-Scargale Periodogram \autocite{vanderplasUnderstandingLombScargle2018}, and 4d-var data assimilation \autocite{puNumericalWeatherPrediction2018,parkDataAssimilationAtmospheric2013}.
+    \item A study of the contribution patterns for different terms in a PDE shown by the p-matrix or other methods.
+\end{itemize}
 % \noindent Sejumlah ide yang muncul ketika melaksanakan penelitian TA dapat menjadi bahan atau topik untuk pekerjaan selanjutnya.

### 2025-01-13 skripsi/abstract.tex
fix fourier derivatives with periods, fix typos in cover, change judul to lower case and add title case variant, add toc, tof, tot, toa to table of contents, fix font issue with mathptmx, add statement of originality, remove list of notation (for now), fix incorrect statement about burgers eq in ch2, fix sattelite coverage image caption too long, move burgers eq exact solution to ch2, fix figure positioning H not h, reword future work

@@
-%\chapter{ABSTRACT}
+% !TEX root = ./skripsi.tex
 \clearpage
@@
 \textbf{\large  ABSTRACT}\\[0.5cm]
-\textbf{\large TITLE}\\[0.5cm]
+\textbf{\large \judulcapitalized}\\[0.5cm]
 \textbf{by}\\
 \textbf{\penulis}\\
-\textbf{NIM: \nim}\\[2em]
+\textbf{NIM:\@\nim}\\[2em]
 \end{center}
 
-\noindent In general, Abstract is a translation of Abstrak. However, appropriate paraphrase may need some words or sentences whose meanings are close enough to those written in Abstrak.
+\noindent Numerical models of systems are a crucial part of science and engineering.
+The use of machine learning in this space for operator learning provides an alternative as data-driven surrogates.
+The Fourier Transform provides a key component for learning the relationship between a function and its derivatives.
+Building on Spectral Neural Operators (SNO), we propose a Support Vector Machine (SVM) based framework to learn the underlying governing equations of a system based on data.
+We study the viability and interpretability of the proposed framework on the derivative equation and the Burgers' equation.
+The model is able to learn from mathematically correct random data and is able to partially generalize to an exact solution of the Burgers' equation.
+The learned model is interpreted and verified to have learned the correct contributions of the input function coefficients to the output function coefficients.
 
-\noindent Key words: \keywords
+\noindent Keywords: \keywords{}

### 2025-01-13 skripsi/abstrak.tex
fix fourier derivatives with periods, fix typos in cover, change judul to lower case and add title case variant, add toc, tof, tot, toa to table of contents, fix font issue with mathptmx, add statement of originality, remove list of notation (for now), fix incorrect statement about burgers eq in ch2, fix sattelite coverage image caption too long, move burgers eq exact solution to ch2, fix figure positioning H not h, reword future work

@@
-%\chapter{ABSTRAK}
+% !TEX root = ./skripsi.tex
 \clearpage
@@
 \textbf{\large  ABSTRAK}\\[0.5cm]
-\textbf{\large JUDUL ABSTRAK}\\[0.5cm]
+\textbf{\large Aproksimasi Solusi \textit{Govering Equations} dengan \emph{Fourier Transform} dan \textit{Support Vector Machine}}\\[0.5cm]
 \textbf{Oleh}\\
@@
 
-\noindent Abstrak merupakan penjelasan singkat dan padat tentang pekerjaan dan hasil penelitian TA, yang dituliskan secara teknis.
+\noindent Model numerik sebuah sistem merupakan bagian penting dari ilmu pengetahuan dan \textit{engineering}.
+Penggunaan \textit{Machine Learning} (ML) dalam ruang ini untuk pembelajaran operator menyediakan alternatif sebagai \textit{data-driven surrogates}.
+\textit{Fourier Transform} menyediakan komponen kunci untuk mempelajari hubungan antara suatu fungsi dan turunannya.
+Berdasarkan \textit{Spectral Neural Operators (SNO)}, kami mengusulkan kerangka kerja berbasis \textit{Support Vector Machine (SVM)} untuk mempelajari persamaan dasar yang mengatur suatu sistem berdasarkan data.
+Kami mempelajari kelayakan dan interpretabilitas kerangka kerja yang diusulkan pada persamaan turunan dan persamaan Burgers.
+Model ini mampu belajar dari data acak yang secara matematis benar dan sebagian mampu melakukan generalisasi ke solusi eksak dari persamaan Burgers.
+Model yang dipelajari diinterpretasikan dan diverifikasi untuk mempelajari kontribusi yang benar dari koefisien fungsi masukan terhadap koefisien fungsi keluaran.
+% \noindent Abstrak merupakan penjelasan singkat dan padat tentang pekerjaan dan hasil penelitian TA, yang dituliskan secara teknis.
 Abstrak memiliki karakter tegas dan komprehensif, dan hanya dapat dituliskan setelah pekerjaan penelitian telah mencapai tahap tertentu, dan karenanya ada hasil penelitian yang dapat dilaporkan.
@@
 
-Secara umum, abstrak memuat beberapa komponen penting, yaitu: konteks atau cakupan pekerjaan penelitian, tujuan penelitian, metodologi yang digunakan selama penelitian, hasil-hasil penting yang dapat ditambahkan dengan implikasinya, dan simpulan dari penelitian.
+% Secara umum, abstrak memuat beberapa komponen penting, yaitu: konteks atau cakupan pekerjaan penelitian, tujuan penelitian, metodologi yang digunakan selama penelitian, hasil-hasil penting yang dapat ditambahkan dengan implikasinya, dan simpulan dari penelitian.
 Dengan demikian, suatu abstrak tidak dapat dituliskan apabila penelitian belum mencapai hasil tertentu, apalagi kalau penelitiannya pun belum dilakukan.
 
-Panjang abstrak sebaiknya dicukupkan dalam satu halaman, termasuk kata kunci.
+% Panjang abstrak sebaiknya dicukupkan dalam satu halaman, termasuk kata kunci.
 Tiga kata kunci dipandang cukup, yang masing-masingnya memuat paduan kata utama, yang dapat merepresentasikan isi Abstrak.
@@
 
-\noindent Kata kunci: \katakunci
+\noindent Kata kunci: \katakunci{}

### 2025-01-13 skripsi/acknowledgments.tex
fix fourier derivatives with periods, fix typos in cover, change judul to lower case and add title case variant, add toc, tof, tot, toa to table of contents, fix font issue with mathptmx, add statement of originality, remove list of notation (for now), fix incorrect statement about burgers eq in ch2, fix sattelite coverage image caption too long, move burgers eq exact solution to ch2, fix figure positioning H not h, reword future work

% !TEX root = ./skripsi.tex
\clearpage
\phantomsection{}
\addcontentsline{toc}{chapter}{ACKNOWLEDGMENTS}
\begin{center}
 \textbf{\large ACKNOWLEDGMENTS}\\[3em]
\end{center}
%-----------------------------------------
\noindent I would like to take the time to acknowledge my friends, family, and everyone who have taken the time to support and encourage me through the completion process of my degree.
% \noindent Kata pengantar berperan sebagai gerbang masuk bagi pembaca dan mendapat sajian ringkas tentang hal-hal terkait paparan pada buku Tugas Akhir (TA). Sajian ini sejatinya merupakan pengenalan umum bagi pembaca tentang isi tulisan. Hal ini berbeda dengan abstrak yang mendeskripsikan pekerjaan dan hasil penelitian secara lebih teknis.

% Kata pengantar merupakan wadah penulis untuk mengenalkan dan mempromosikan pekerjaan dan hasil penelitian dengan bahasa yang sederhana, sehingga pembaca tertarik untuk menelusuri lebih jauh dengan mencermati seluruh paparan pada buku TA. Ini salah satu tujuan kata pengantar. Contoh paragraf yang mengantar pembaca pada isi Buku TA: \textit{Template} \LaTeX\ diberikan berikut ini.

% Menuliskan pekerjaan dan hasil penelitian TA dalam suatu laporan buku TA memerlukan panduan standar. Panduan ini dibuat dalam beberapa dokumen, yang salah satunya adalah Buku TA: \textit{Template} \LaTeX. Suatu template adalah cetakan yang siap dituang oleh curahan buah pikiran yang keluar dari pengalaman dalam melakukan pekerjaan penelitian dan hasil-hasilnya. Mencermati cetakan yang memberikan sejumlah contoh dapat memperlancar penulisan laporan tersebut menjadi suatu produk, yaitu buku TA.

% Tujuan lain dari Kata Pengantar adalah memberi tempat untuk menyampaikan rasa syukur dan terima kasih kepada banyak pihak, misalnya keluarga, staf akademik, staf tenaga kependidikan, teman, individu atau komunitas pemberi dukungan dan inspirasi, dan institusi pendukung pendanaan seperti pemberi beasiswa atau dana penelitian, atau pendukung akses fasilitas.

% \textit{Pengorbanan, kegigihan, dedikasi, dan penuh tanggung jawab dari para pahlawan pekerja medis dalam perawatan pasien terpapar Covid-19 telah memberi inspirasi melalui nilai-nilai kejuangan tanpa pamrih. Inspirasi inilah yang membangkitkan spirit pamungkas pada penyelesaian Buku TA: Template} \LaTeX\ \textit{ini. Suatu inspirasi selalu bekerja dan mengena secara tidak langsung. Banyak berterima kasih atas inspirasi yang memantik spirit ini.}

% \newpage
% Tidak ada sub bab/bagian pada Kata Pengantar, namun daftar rincian diperkenankan. Pada bagian indentitas akhir, seperti berikut ini, dituliskan nama mahasiswa dan NIM, bukan \textit{penulis}, dan tidak perlu ditandatangani. Berikut adalah contoh penulisan rincian yang berisi ucapan terima kasih:
% \begin{itemize}
%  \item \pembimbingsatu dan \pembimbingdua selaku dosen pembimbing tugas akhir.
%  \item Jyesta, sebagai teman bimbingan yang selalu bersedia untuk diajak berdiskusi selama penelitian.
%  \item Rekan-rekan Spectranova, ............
% \end{itemize}

\begin{flushright}
Bandung, \today{}\\[0.25cm]
\penulis{}\\
\nim{}
\end{flushright}

### 2025-01-13 skripsi/chapter1.tex
fix fourier derivatives with periods, fix typos in cover, change judul to lower case and add title case variant, add toc, tof, tot, toa to table of contents, fix font issue with mathptmx, add statement of originality, remove list of notation (for now), fix incorrect statement about burgers eq in ch2, fix sattelite coverage image caption too long, move burgers eq exact solution to ch2, fix figure positioning H not h, reword future work

@@
 \chapter{INTRODUCTION}
-\section{Background}\label{sec:background} %pelabelan ini opsional, biar bisa di klik kalo mengarahkan ke section tertentu.
+\section{Background}\label{sec:background}
+% TODO:talk about mathematical models and governing equations here instead. PDEs can be talked later as a subset of governing equations
 \noindent Partial differential equations (PDE) are a common tool widely used in the modern scientific understanding and many engineering processes.
@@
 
-Many other fields in physics such as waves, quantum dynamics, fluid dynamics, elastics, and many more also define systems using PDEs.
+Many other fields in physics such as waves, quantum dynamics, fluid dynamics, elastics, and many more also model systems using PDEs.
 PDEs are also used outside the physical sciences.
@@
 Because of this, forecasting is critical in making accurate decisions for policymakers and warnings of extreme weather events for civilians \autocite{astithaExtremeWeatherForecasting2023,stottAttributionExtremeWeather2016}.
+% TODO: do i need this? because my project doesn't address this. at least not directly. I can mention this as context for where other ML research in weather has gone.
 A major challenge is the fact that observations of weather can be sparse in the sense that observations are localized and do not cover entire areas \autocite{wilbyRainfallTemperatureEstimation2013,monmonierAirApparentHow1999,galkinAssimilationSparseContinuous2020}.
@@
 Even more mobile observation platforms like satellites only show the portion of the surface the satellite can see at any one time such as in \lccref{fig:satellite_image_coverage}.
+Notice that parts of the globe, especially near the equator have not been observed.
 While accumulating observations through more satellite passes is possible, this, however, means short-lived features may not be observed.
@@
 The information this could provide is invaluable because it means planning for future weather is possible.
-
-\begin{figure}[ht] %h means here!
+\begin{figure}[H] 
     \centering
@@
 This shows observations recorded through a whole day on the 21\textsuperscript{st} of May 2024.
-Notice that parts of the globe, especially near the equator have not been observed.
 This image was produced using NASA Worldview (\url{https://go.nasa.gov/46SaYyJ}).}\label{fig:satellite_image_coverage}

### 2025-01-13 skripsi/chapter2.tex
fix fourier derivatives with periods, fix typos in cover, change judul to lower case and add title case variant, add toc, tof, tot, toa to table of contents, fix font issue with mathptmx, add statement of originality, remove list of notation (for now), fix incorrect statement about burgers eq in ch2, fix sattelite coverage image caption too long, move burgers eq exact solution to ch2, fix figure positioning H not h, reword future work

@@
 As a whole this would make the solution tend toward large negative gradients and discourage large positive gradients.
-As the negative gradient grows, if unimpeded by the advection term, it would eventually lead to the formation of a shock wave moving to the positive x direction.
+As the negative gradient grows, if unimpeded by the advection term, it would eventually lead to the formation of a shock wave.
 Finally, the forcing term affects the time derivative directly and attract the solution toward which ever direction defined by the forcing term.
@@
 Solutions to the Burgers' equation can be obtained analytically.
-One of the most straightforward ways is the Cole-Hopf transform.
-Using this method, the solution to the Burgers' equation \(u\) is computed from any valid solutions of the heat equation \(\phi \).
+One of the most straightforward ways is the Cole-Hopf transform \autocite{wazwazPartialDifferentialEquations2010}.
+Using this method, the solution to the Burgers' equation \(u\) can be computed from any valid solutions of the heat equation \(\phi \).
 The solution of the Burgers' equation is obtained by using the Cole-Hopf transform written in \lccref{eq:cole_hopf}.
-However, this limits the range of possible solutions because of the requirement of a valid heat equation solution.
+For example, one solution from this transform is shown in \lccref{eq:burgers_exact_solution} was specifically mentioned by \textcite{woodExactSolutionBurgers2006} to be complex enough to test how well numerical methods solving the Burgers' equation can handle the nonlinearity.
+Similar solutions and other solutions using also exists in other literature \autocite{bentonTableSolutionsOnedimensional1972,wazwazPartialDifferentialEquations2010}.
+\begin{align}
+  u = -2\nu\frac{\phi_x}{\phi}\label{eq:cole_hopf}
+\end{align}
+\begin{equation}
+  u(x,t) = \frac{2\nu\pi e^{-\pi^2\nu t}\sin(\pi x)}{a+e^{-\pi^2\nu t}\cos(\pi x)} \label{eq:burgers_exact_solution}
+\end{equation}
+
+The use of the Cole-Hopf transform, however, limits the range of possible solutions because of the requirement of a valid heat equation solution.
 For a wider range of solutions, numerical methods are predominantly used to solve the initial value problem for the Burgers' equation.
@@
 As the gradient become sharper, the solution would require finer and finer time steps in order to stay at a consistent error for each step, otherwise the solution can become unstable.
-\begin{align}
-  u = -2\nu\frac{\phi_x}{\phi}\label{eq:cole_hopf}
-\end{align}
-
 High viscosity values introduce a similar issue.
@@
 % TODO: talk about inverse and forward problems
+% There are categories of problems when solving PDEs, The forward problem (IVP, BVP, IVBP) and the inverse problem (parameter estimation)
 
@@
 
-The Fourier series can be represented in two ways, the first is the real representation by using sine and cosines as the basis functions in the series shown in \lccref{eq:fourier_series_sine_cosine}.
-The second representation is the complex representation which uses Euler's formula as the basis functions shown in \lccref{eq:fourier_series_complex}.
+The Fourier series can be represented in two ways, the first is the real representation by using sine and cosines as the basis functions in the series shown in \lccref{eq:fourier_series_sine_cosine}, where \(k\) is the wave number, \(L\) is the period, and \(\hat{a}_{k}\) and \(\hat{b}_{k}\) are the coefficients for the \(k\)-th wave number.
+The second representation is the complex representation which uses Euler's formula as the basis functions shown in \lccref{eq:fourier_series_complex} with complex valued coefficients \(\hat{c}_{k}\).
 Both of these are equivalent and are just the different representations.
@@
 \begin{align}
-  f(x)=       & \hat{a}_0 + \sum_{k=0}^{\infty} \hat{a}_k\cos(2\pi kx) + \hat{b}_k\sin(2\pi kx)\label{eq:fourier_series_sine_cosine} \\
-  f(x)=       & \sum_{k=-\infty}^{\infty} \hat{c}_k e^{2\pi ikx}\label{eq:fourier_series_complex}                                    \\
+  f(x)=       & \hat{a}_0 + \sum_{k=0}^{\infty} \hat{a}_k\cos(2\pi kx/L) + \hat{b}_k\sin(2\pi kx/L)\label{eq:fourier_series_sine_cosine} \\
+  f(x)=       & \sum_{k=-\infty}^{\infty} \hat{c}_k e^{2\pi ikx/L}\label{eq:fourier_series_complex}                                    \\
   \hat{c}_k = & \begin{cases}
@@
 \begin{align}
-  \dv{x}f(x)=  & \sum_{k=-N/2}^{N/2-1} \hat{c}_k (2\pi ik) e^{2\pi ikx} \label{eq:fourier_series_complex_derivative} \\
-  =            & \sum_{k=-N/2}^{N/2-1} \hat{f'}_k e^{2\pi ikx}\nonumber                                              \\
-  \hat{f'}_k = & (2\pi ik)\hat{c}_k\label{eq:fourier_coeff_derivative}
+  \dv{x}f(x)=  & \sum_{k=-N/2}^{N/2-1} \hat{c}_k (2\pi ik/L) e^{2\pi ikx/L} \label{eq:fourier_series_complex_derivative} \\
+  =            & \sum_{k=-N/2}^{N/2-1} \hat{f'}_k e^{2\pi ikx/L}\nonumber                                              \\
+  \hat{f'}_k = & (2\pi ik/L)\hat{c}_k\label{eq:fourier_coeff_derivative}
 \end{align}
@@
 % \section{Referensi dan Citation}
-% \noindent Sitasi dapat dimasukkan ke dalam Tugas Akhir seperti ini \cite{Fujita1996}.
-Untuk sitasi dengan beberapa sumber, dapat dituliskan juga \cite{hohen1964,Kim2006}.
-Atau untuk tiga sumber berarti \cite{kongkanand2006,kresse1999,Leibb1993}.
+% \noindent Sitasi dapat dimasukkan ke dalam Tugas Akhir seperti ini \autocite{Fujita1996}.
+Untuk sitasi dengan beberapa sumber, dapat dituliskan juga \autocite{hohen1964,Kim2006}.
+Atau untuk tiga sumber berarti \autocite{kongkanand2006,kresse1999,Leibb1993}.

### 2025-01-13 skripsi/chapter4.tex
fix fourier derivatives with periods, fix typos in cover, change judul to lower case and add title case variant, add toc, tof, tot, toa to table of contents, fix font issue with mathptmx, add statement of originality, remove list of notation (for now), fix incorrect statement about burgers eq in ch2, fix sattelite coverage image caption too long, move burgers eq exact solution to ch2, fix figure positioning H not h, reword future work

@@
 This scenario is found in many real systems albeit often with many more details such as different components of acceleration from friction, drag, gravity, and other factors.
-As previously mentioned in \lccref{sec:data_generation}, both velocity \(u \) and acceleration \(a \) are modeled with Fourier series in \lccrefs{eq:fourier_speed,eq:fourier_acceleration} respectively.
+As previously mentioned in \lccref{sec:data_generation}, both velocity \(u \) and acceleration \(a \) are modeled with Fourier series in \lccrefs{eq:fourier_speed,eq:fourier_acceleration} respectively, where \(T\) is the period representing the length of the domain.
 \begin{align}
-  u\left( t \right)         & = \sum_{k} \hat{u}_k e^{2\pi ikt} \label{eq:fourier_speed}        \\
-  a\left( t \right)         & = \sum_{k} \hat{a}_k e^{2\pi ikt} \label{eq:fourier_acceleration}
+  u\left( t \right) & = \sum_{k} \hat{u}_k e^{2\pi ikt/T} \label{eq:fourier_speed}        \\
+  a\left( t \right) & = \sum_{k} \hat{a}_k e^{2\pi ikt/T} \label{eq:fourier_acceleration}
 \end{align}
@@
 This choice was made such that most wave numbers will have a coefficient of close to zero leaving a sparse set of wave numbers to mostly affect the resulting function.
-In total, \num{5000} unique functions are generated with \num{100} complex coefficients each.
+In total, \num{5000} unique functions are generated with \num{50} complex coefficients each.
 
@@
 \begin{align}
-  \dv{u\left( x \right)}{x}                                    & = \sum_{k} \hat{u}_k\times \left( 2\pi ik \right) e^{2\pi ikx} \label{eq:fourier_series_derivative} \\
-  \sum_{k} \hat{u}_k\times \left( 2\pi ik \right) e^{2\pi ikx} & = \sum_{k} \hat{a}_k e^{2\pi ikx} \label{eq:example_spectral_method_fourier_substituted}            \\
-  \hat{u}_k                                                    & = \hat{a}_k / \left( 2\pi ik \right) \label{eq:derivative_coeff}
+  \dv{u\left( t \right)}{t}                                        & = a\left(t\right) \label{eq:fourier_series_derivative}                                                             \\
+  \sum_{k} \hat{u}_k\times \left( 2\pi ik/T \right) e^{2\pi ikt/T} & = \sum_{k} \hat{a}_k e^{2\pi ikt/T} \label{eq:example_spectral_method_fourier_substituted}                         \\
+  \hat{a}_k                                                        & = \hat{u}_k\left( 2\pi ik/T \right)                                                    \label{eq:derivative_coeff}
 \end{align}
@@
 The domain of we consider here is based on an exact solution of the equation.
-This is done so that the learned solver model can be tested on the exact solution.
-There are a number of sources in literature on the exact solution of the Burgers' equation \autocite{bentonTableSolutionsOnedimensional1972,wazwazPartialDifferentialEquations2010,woodExactSolutionBurgers2006}.
+This is done so that the learned model can be tested on an exact solution and capture enough of the details within the solution within the domain.
 In this study, we use a specific solution by \textcite{woodExactSolutionBurgers2006} which can be seen in \lccref{eq:burgers_exact_solution}.
@@
 The time domain, on the other hand, is chosen to span from 0 to 10 such that enough details of the solution is included.
-\begin{equation}
-  u(x,t) = \frac{2\nu\pi e^{-\pi^2\nu t}\sin(\pi x)}{a+e^{-\pi^2\nu t}\cos(\pi x)} \label{eq:burgers_exact_solution}
-\end{equation}
+
 Continuing to the second step, the parameters involved in \lccref{eq:forced_viscous_burgers} are the viscosity \(\nu \) and the forcing term \(f \).
@@
 The solution field \(u\) and forcing term \(f\) are modeled with Fourier series in \lccrefs{eq:fourier_field,eq:fourier_force} where \(k\) is a vector of spatial and temporal wave number such that \(k_t\) is the temporal wave number and \(k_x\) is the spatial wave number.
+The period in time is represented by \(T\) and in space it is \(L\).
 \begin{align}
-  u\left(x, t \right) & = \sum_{k_{x}} \sum_{k_{t}} \hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)} \label{eq:fourier_field} \\
-  f\left(x, t \right) & = \sum_{k_{x}}\sum_{k_{t}} \hat{f}_k e^{2\pi i(k_{x}x+k_{t}t)} \label{eq:fourier_force}
+  u\left(x, t \right) & = \sum_{k_{x}} \sum_{k_{t}} \hat{u}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)} \label{eq:fourier_field} \\
+  f\left(x, t \right) & = \sum_{k_{x}}\sum_{k_{t}} \hat{f}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)} \label{eq:fourier_force}
 \end{align}
@@
 A problem one notices is the nonlinear term \(u\pdv{u}{x}\).
-A naive approach would multiply all wave numbers terms with each other.
+A naive approach would multiply all wave numbers terms with each other as shown in \lccref{eq:burgers_convolution}.
 \begin{align}
-  u\pdv{u}{x} = \left(\sum_{k_{x}} \sum_{k_{t}} \hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)}\right) \times \left(\sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{x})\hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)}\right)
+  u\pdv{u}{x} = \left(\sum_{k_{x}} \sum_{k_{t}} \hat{u}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)}\right) \times \left(\sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{x}/L)\hat{u}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)}\right)\label{eq:burgers_convolution}
 \end{align}
@@
   \begin{split}
-    \sum_{k_{x}} \sum_{k_{t}} \hat{f}_k e^{2\pi i(k_{x}x+k_{t}t)} =
-     & \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{t}) \hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)}                                                                \\
-     & + \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{x})\hat{uu}_k e^{2\pi i(k_{x}x+k_{t}t)}                                                              \\
-     & - \nu\sum_{k_{x}} \sum_{k_{t}} {(2\pi i k_{x})}^2\hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)} \label{eq:forced_viscous_burgers_fourier_substitution}
+    \sum_{k_{x}} \sum_{k_{t}} \hat{f}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)} =
+     & \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{t}/T) \hat{u}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)}                                                                \\
+     & + \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{x}/L)\hat{uu}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)}                                                              \\
+     & - \nu\sum_{k_{x}} \sum_{k_{t}} {(2\pi i k_{x}/L)}^2\hat{u}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)} \label{eq:forced_viscous_burgers_fourier_substitution}
   \end{split}
@@
 \begin{align}
-  \sum_{k_{x}} \sum_{k_{t}} \hat{f}_k & = \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{t}) \hat{u}_k + (2\pi i k_{x})\hat{uu}_k - \nu{(2\pi i k_{x})}^2\hat{u}_k \label{eq:forced_viscous_burgers_fourier} \\
-  \hat{f}_k                           & = (2\pi i k_{t}) \hat{u}_k + (2\pi i k_{x})\hat{uu}_k - \nu{(2\pi i k_{x})}^2\hat{u}_k \label{eq:forced_viscous_burgers_coeff}
+  \sum_{k_{x}} \sum_{k_{t}} \hat{f}_k & = \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{t}/T) \hat{u}_k + (2\pi i k_{x}/L)\hat{uu}_k - \nu{(2\pi i k_{x}/L)}^2\hat{u}_k \label{eq:forced_viscous_burgers_fourier} \\
+  \hat{f}_k                           & = (2\pi i k_{t}/T) \hat{u}_k + (2\pi i k_{x}/L)\hat{uu}_k - \nu{(2\pi i k_{x}/L)}^2\hat{u}_k \label{eq:forced_viscous_burgers_coeff}
 \end{align}
@@
 For the forcing term, we just use a constant function with a value of zero.
-The rollout predictions are shown in \lccref{fig:scenario_2_interpretation}.
+The rollout predictions are shown in \lccref{fig:scenario_2_exact}.
 The model is not successful in the rollout for the inviscid equation and for the viscosity of \(\nu=0.01\).

### 2025-01-13 skripsi/chapter5.tex
fix fourier derivatives with periods, fix typos in cover, change judul to lower case and add title case variant, add toc, tof, tot, toa to table of contents, fix font issue with mathptmx, add statement of originality, remove list of notation (for now), fix incorrect statement about burgers eq in ch2, fix sattelite coverage image caption too long, move burgers eq exact solution to ch2, fix figure positioning H not h, reword future work

--- 2025-01-06 skripsi/chapter5.tex
@@
 \section{Conclusion}
+\noindent Based on the results of the research into \MakeLowercase{\judul}, several conclusions can be drawn.
+\begin{enumerate}
+    \item The proposed SpectralSVR model is able to learn the relationships defined by PDEs.
+This is done with a computational model that with four phases which are data preparation, data transformation, model training, and finally model evaluation.
+    \item Interpretation of the proposed model can be done to a certain extent using two tools which are the correlation image and p-matrix developed by \textcite{ustunVisualisationInterpretationSupport2007}.
+    \item The proposed model is also capable in dealing with noise and partial data as shown in scenario 1 and 3.
+    \item The model's capabilities are also verified using exact solution. This revealed that for some configurations the model is able to successfully generalize to exact solutions.
+\end{enumerate}
 % \noindent Bab ini merupakan pamungkas berupa rincian rangkuman yang merupakan simpulan dari analisis yang telah dilakukan.
@@
 \section{Future Work}
+During the work on this study, some limitations were imposed, and many new questions also went unanswered. Here, we would like to list some potential avenues for future work:
+\begin{itemize}
+    % TODO: reword these points
+    \item The synthetic data used in scenarios 1 and 2 were generated using MMS\@.
+While mathematically correct, this data is not realistic.
+Incorporating more realistic data from traditional numerical methods or other sources could enhance the model's ability to predict more realistic solutions.
+    \item Test how the auto-regression of weather compares to the target data.
+    \item Compare inverse prediction results with traditional derivatives, such as the spectral method or FDM\@.
+    \item Compare the proposed method with other methods in comparable situations.
+    \item Measure and compare the efficiency (time) of computing solutions against traditional and machine learning-based methods.
+    \item Add more basis functions, such as spherical harmonics or wavelet bases.
+    \item Incorporate more regression models, specifically more support vector regression models, to continue utilizing the correlation image and p-matrix.
+    \item Use better metrics for measuring performance, such as the \enquote{standard error of regression}.
+    \item Analyze the performance with different hyperparameters or data sizes and present the results in charts.
+    \item Perform an analysis of the error by wave number.
+    \item Solve the problem of double penalties that cause the model to favor smooth solutions \autocite{brownForecastsSpatialFields2011,NIPS2017_44a2e080}.
+Try using stronger regularization (a higher regularization parameter) for higher wave numbers.
+    \item Add support for sparse data by employing data assimilation techniques, such as the Lomb-Scargle periodogram \autocite{vanderplasUnderstandingLombScargle2018}, and 4D-Var data assimilation \autocite{puNumericalWeatherPrediction2018,parkDataAssimilationAtmospheric2013}.
+    \item Study the contribution patterns for different terms in a PDE using the p-matrix or other methods.
+\end{itemize}
 % \noindent Sejumlah ide yang muncul ketika melaksanakan penelitian TA dapat menjadi bahan atau topik untuk pekerjaan selanjutnya.

### 2025-01-13 skripsi/identitas.tex
change to biblatex, start background
research design and computational model, fix root file latex
Finish ch4, fix some problems with
finish ch2 and start ch5
fix fourier derivatives with periods, fix typos in cover, change judul to lower case and add title case variant, add toc, tof, tot, toa to table of contents, fix font issue with mathptmx, add statement of originality, remove list of notation (for now), fix incorrect statement about burgers eq in ch2, fix sattelite coverage image caption too long, move burgers eq exact solution to ch2, fix figure positioning H not h, reword future work

@@
+% !TEX root = ./skripsi.tex
 %isi identitas diri di file ini......
@@
 %JUDUL: 
-\providecommand{\judul}{
-    APROKSIMASI SOLUSI \textit{PARTIAL DIFFERENTIAL EQUATIONS} DENGAN \textit{PHYSICS-INFORMED SUPPORT VECTOR MACHINE}
-}
+\providecommand{\judul}{approximating solutions of governing equations with Fourier transform and support vector machine}
+\providecommand{\judulcapitalized}{Approximating Solutions of Governing Equations With Fourier Transform and Support Vector Machine}
 %PENULIS:
-\providecommand{\penulis}{
-    Ahmad Izzuddin
-}
+\providecommand{\penulis}{Ahmad Izzuddin}
 %NIM:
-\providecommand{\nim}{
-    1908919
-}
+\providecommand{\nim}{1908919}
 
@@
 %Pembimbing 1
-\providecommand{\pembimbingsatu}{
-    Prof. Dr. Lala Septem Riza, M.T.
-}
+\providecommand{\pembimbingsatu}{Prof.\ Dr.\ Lala Septem Riza, M.T.}
 %NIP Pembimbing 1:
-\providecommand{\NIPpbbsatu}{
-    197809262008121001
-}
+\providecommand{\NIPpbbsatu}{197809262008121001}
 %Pembimbing2
-\providecommand{\pembimbingdua}{
-    Nama Pembimbing 2
-}
+\providecommand{\pembimbingdua}{Dr.\ Muhammad Nursalman, M.T.}
 %NIP Pembimbing 2:
-\providecommand{\NIPpbbdua}{
-    314159265358979323
-}
+\providecommand{\NIPpbbdua}{197909292006041002}
 
 %untuk keywords yang ada di abstrak, di sini:
-\providecommand{\katakunci}{
-    Konsep Abstrak, Komponen Abstrak, Kata Kunci.
-}
-\providecommand{\keywords}{
-    Abstract Concepts, Abstract Components, Key Words.
-}
+\providecommand{\katakunci}{\textit{Operator Learning}, PDE, LSSVM.}
+\providecommand{\keywords}{Operator Learning, PDE, LSSVM.}

### 2025-01-13 skripsi/statementoforiginality.tex
fix fourier derivatives with periods, fix typos in cover, change judul to lower case and add title case variant, add toc, tof, tot, toa to table of contents, fix font issue with mathptmx, add statement of originality, remove list of notation (for now), fix incorrect statement about burgers eq in ch2, fix sattelite coverage image caption too long, move burgers eq exact solution to ch2, fix figure positioning H not h, reword future work

% !TEX root = ./skripsi.tex
\clearpage
\phantomsection{}
\addcontentsline{toc}{chapter}{STATEMENT OF ORIGINALITY}
\begin{center}
 \textbf{\large STATEMENT OF ORIGINALITY}\\[3em]
\end{center}
%-----------------------------------------
\noindent Hereby, I declare that the thesis titled  
\enquote{\judulcapitalized} and all its contents are entirely my own work. I have not engaged in plagiarism or citation practices that contravene the ethical standards of academic conduct upheld within the scholarly community. By making this declaration, I accept full responsibility and am prepared to face any consequences or sanctions should any violation of academic ethics or claims regarding the originality of this work arise in the future.

\begin{flushright}
Bandung, \today{}\\[2cm]
\penulis{}\\
\nim{}
\end{flushright}

### 2025-01-13 article/article.tex
finish article draft

% !TEX root = ./article.tex
\documentclass[preprint,12pt,times,authoryear]{elsarticle}
\input{preamble}
\begin{document}
\begin{frontmatter}
  \title{\judul}
  % \author{
  %   Lala Septem Riza\\
  %   \texttt{lala.s.riza@upi.edu}
  %   \and
  %   Ahmad Izzuddin\\
  %   \texttt{ahmadizzuddin@upi.edu}
  \author[upi]{Lala Septem Riza}
  \ead{lala.s.riza@upi.edu}
  \author[upi]{Ahmad Izzuddin}
  \ead{ahmadizzuddin@upi.edu}

  \affiliation[upi]{organization={Department of Computer Science Education Universitas Pendidikan Indonesia},%Department and Organization
    addressline={Jl. Dr. Setiabudi No.229},
    postcode={40154},
    city={Bandung},
    country={Indonesia}}
  \begin{abstract}
    Numerical models of systems are a crucial part of science and engineering. The use of machine learning in this space for operator learning provides an alternative as data-driven surrogates. The Fourier Transform provides a key component for learning the relationship between a function and its derivatives. Building on Spectral Neural Operators (SNO), we propose a Support Vector Machine (SVM) based framework to learn the underlying governing equations of a system based on data. We study the viability and interpretability of the proposed framework on the derivative equation and the Burgers' equation. The model is able to learn from mathematically correct random data and is able to partially generalize to an exact solution of the Burgers' equation. The learned model is interpreted and verified to have learned the correct contributions of the input function coefficients to the output function coefficients.
  \end{abstract}
  \begin{keyword}
    %% keywords here, in the form: keyword \sep keyword
    Operator Learning \sep LSSVR \sep PDE
    % keyword one \sep keyword two
    %% PACS codes here, in the form: \PACS code \sep code
    % \PACS 0000 \sep 1111
    %% MSC codes here, in the form: \MSC code \sep code
    %% or \MSC[2008] code \sep code (2000 is the default)
    \MSC 35-04 \sep 68T99
  \end{keyword}

\end{frontmatter}
\section{Introduction}
Governing equations have been a critical part of the technological revolution. They help us understand better the systems that exist in our world \citep{braunDifferentialEquationsTheir1993}. Typically, governing equations are differential equations. For systems with many variables, they are described by Partial Differential Equations (PDE). For example, the spread of heat on a cooking surface is described by the heat equation, with the temperature as a function of time and space. Differential equations are used because often, the behavior systems are easier to describe in the way they change.

Typically, when modeling a system with PDEs, there are different problem types based on the conditions that are imposed on the solution. The main problem types are where the solutions are constrained by its boundaries. For equations with a temporal component, an initial value can be imposed as a restriction on solution's value at that initial point in time. This problem is called the Initial Value Problem (IVP). The Boundary Value Problem (BVP) on the other hand, defines the restrictions on the solution at the spatial boundary of the system being simulated, such as values or derivatives the solution must have at the boundary. The Initial-Boundary Value Problem (IBVP) combines both conditions imposed on the solution. These problems are considered part of the larger group of forward problems. This is because, the objective is to determine the system's response in terms of the solution towards causal factors, namely parameters and imposed conditions \citep{groetschInverseProblemsMathematical1993, vogelComputationalMethodsInverse2002}. The inverse problem, on the other hand, is the reverse process where parameters or conditions such as the initial value is the objective. Simply put, in inverse problems, the effects are used to compute the cause that led to it.

While some PDEs have analytical solutions, they are restrictive in ways such as the initial condition, or other parameters \citep{selvaduraiPartialDifferentialEquations2000,koprivaImplementingSpectralMethods2009, olverIntroductionPartialDifferential2014, schiesserNumericalMethodLines2012, wazwazPartialDifferentialEquations2010}. Because of this, modeling a system with differential equations usually involve the use of numerical methods. With their long history, there are now several well established general methods such as Finite Difference Method (FDM), Finite Element Method (FEM), and the Spectral Method. With mesh based methods such as FDM, evaluating the solutions at higher resolutions means either recomputing the solution with a higher resolution which increases the computational cost, or interpolation which can depend on the problem. For multiscale problems like Numerical Weather Prediction (NWP), the complex interactions are very difficult to model due to the vast differences in scale \citep{frankCharacterizingDynamicsMultiscale2024}. Also, the user needs to know the equations involved before modeling the system. Which may not be available in some fields like ecology \citep{holmesPartialDifferentialEquations1994,turchinDoesPopulationEcology2001} and epidemiology \citep{brauerMathematicalModelsEpidemiology2019}.

These challenges have spurred interest in modeling systems with the use of Machine Learning (ML) as surrogates. There are two types of modeling with ML models. The first kind is akin to function regression, where the model predicts solution values from coordinates and parameters. An example, \citet{raissiPhysicsinformedNeuralNetworks2019} proposed Physics-Informed Neural Networks (PINN). The specific implementation they used is a Feedforward Neural Network (FNN) as an approximation for the solution.  To enforce the PDE, the loss is computed with PDE residuals and other constraints. The partial derivatives for the residual are computed with ease using the automatic differentiation with respect to the input coordinates. Other works utilize convolutional neural networks (CNN) to compute the solution from input functions such as forcing terms or initial conditions. This approach generally means discretizing the functions on a grid and using these as training data. One study by \citet{wangPhysicsinformedDeepLearning2020} predicts turbulent flow using spatial and temporal decomposition and a specialized U-Net, an architecture based on CNNs, to predict the velocity field from the decomposition of the previous velocity field. Part of the loss function is a regularization term for zero divergence in the velocity field to enforce incompressible fluid flow. This term was calculated using finite differences since auto differentiation cannot be used without the coordinates in the model inputs. While the use of CNNs mean that discretization is implied, solutions of different initial conditions or parameter functions can be computed by inference and no retraining is required. This property is especially useful for many-query problems such as computing gradients for inverse problems.

% TODO: talk about the relationship of derivatives in the fourier domain with an example equation
This is where operator learning models that predicts basis function coefficients come in. Basis functions are collections of functions that share common properties and can be used to represent other functions in a linear combination. For example, the sine and cosines in the real Fourier series. This is the concept used by \citet{fanaskovSpectralNeuralOperators2023} for their proposed model, termed Spectral Neural Operator (SNO). The model Neural Network (NN) is trained on features of input function coefficients which are computed using Fourier or Chebyshev transforms and labels of output function coefficients using the same transforms. This separates the concern of discretization from the problem of learning the relationships enforced by some system between functions.\ \citet{du2024neural} extends the concept of mapping coefficients by proposing residuals in the spectral domain and leveraging Parseval's Identity to compute the spectral analog to the loss term in PINNs. This allows for self supervised learning in the spectral domain. The same benefits incorporating physics into PINNs also apply here without the pain points introduced by discretized model inputs and outputs. Another approach by \citet{luLearningNonlinearOperators2021}, essentially uses learned basis functions in the form of NNs. This has the benefit of the basis functions being custom-made to fit the problem and equations being modeled \citep{meurisMachinelearningbasedSpectralMethods2023}. These methods show promise and provide solutions to parameters via the relatively fast process of inference.

The use of NNs does come with its own downsides. First, the loss functions used in their optimization represents a landscape with many local minima. This problem becomes worse with the addition of PDE residual terms that cause disparities in the gradients of each individual loss term and \citep{rathoreChallengesTrainingPINNs2024,NEURIPS2021_df438e52,basirCriticalInvestigationFailure2022}. This has motivated the use of ML algorithms with a convex loss landscape for modeling. Support Vector Machines (SVM) are one such family of algorithms \citep{vapnikNatureStatisticalLearning2000}. The appeal of SVMs is the fact that the model is formulated as a quadratic programming problem. This means there are strong guarantees for convergence, generalization, and complexity. Another formulation called Least-Squares Support Vector Machines (LSSVM) reformulates the problem as a linear system \citep{suykensLeastSquaresSupport2005}. This leads to an easier problem that can be computed faster by well established algorithms like the many implementations of least squares solvers. Another advantage of the linear formulation is that this can be easily parallelized to exploit hardware like graphics processing units more widely known as GPUs in contrast to the commonly used Sequential Minimal Optimization (SMO) used for SVMs with quadratic objective functions.

An early work using SVMs to solve PDEs by \citet{youxiwuSVMSolvingForward2005} introduced a method for solving the forward problem of Electro-Impedance Tomography. This work solved for the mathematical model of EIT which is given by Maxwell's equations by modeling the trial function as using an \(\epsilon \)-SVR model. Another approach much more similar to PINNs was presented by \citet{mehrkanoonLearningSolutionsPartial2015}. The residual and initial/boundary conditions are imposed as equality constraints on an LSSVM objective function. A different study by \citet{leakeAnalyticallyEmbeddingDifferential2019}, the incorporation of physics into the model is done slightly differently by utilizing the theory of functional connections to directly embed constraints into the solution. This means that the proposed method would satisfy the boundary condition exactly. These approaches, however, only learn a function regression problem constrained by the PDE\@. Meaning they are also not practical for many-query problems.

In this paper, we propose an operator learning model based on basis functions and LSSVM for regression, named SpectralSVR\@. Here we will focus on demonstrating the model's capability, starting with a proof of concept with the simple derivative equation. And then, the nonlinear PDE solving capabilities will be shown by approximating solutions to the Burgers' equation.% Finally, we will also use the ERA5 dataset, specifically the could optimized version provided by WeatherBench 2 \citep{raspWeatherBench2Benchmark2023}. %TODO: determine if the inverse problem need to be included

\section{Methods}
This section describes the proposed method and the case studies we used.
\subsection{SpectralSVR}
% Model design
The design of the proposed model is built upon performing regression in the Fourier domain. This means that any function values that will be used by the model, should be transformed into their coefficients. And, any predictions from the model, which are coefficients, should be transformed back into function values. The training process is shown in \lccref{fig:spectralsvr_training}. The process starts with determining the feature and label functions. Typically, the feature functions would include the forcing term and other parameter functions such as the solution at the current time step. The label functions typically is the solution function or the solution function at the next time step. The Fourier coefficients are then computed using the DFT\@. The coefficients are then flattened for each sample. A scaling function is fitted on the flattened feature coefficients and the feature coefficients are then scaled using the fitted scaling function. Finally, Using the scaled feature and label coefficients, the training function computes the parameters of the model.

\begin{figure}[H]
  \centering
  \tikzfig{figures/training_spectralsvr}
  \caption{SpectralSVR training diagram}\label{fig:spectralsvr_training}
\end{figure}

The prediction process is shown in \lccref{fig:spectralsvr_prediction}. The process starts by transforming the feature functions into their coefficients with the DFT\@. These coefficients are then scaled with the scaling function fitted during training. The scaled feature coefficients are then used with the learned parameters to produce the predicted coefficients using the LSSVR prediction function. Finally, the inverse DFT is computed on the predicted coefficients to obtain the predicted function value.
\begin{figure}[H]
  \centering
  \tikzfig{figures/prediction_spectralsvr}
  \caption{SpectralSVR prediction diagram}\label{fig:spectralsvr_prediction}
\end{figure}

To interpret the relationship learned by the LSSVR between the feature and label coefficients, we use two tools called the correlation image and p-matrix introduced by \citet{ustunVisualisationInterpretationSupport2007}.

\subsection{Case Studies}
% case studies
% antiderivative
The model's ability will be verified and demonstrated using two equations. The data will be generated using the method of manufactured solutions \citep{roacheCodeVerificationMethod2002,salariCodeVerificationMethod2000,vedovotoApplicationMethodManufactured2011}. First, the model will be tasked to learn the basic relationship defined by the simple derivative \lccref{eq:fourier_series_derivative}. The solution functions are generated as Fourier polynomials with random coefficients sampled from a normal distribution. The generated solution function takes the form shown in \lccref{eq:fourier_speed}. The coefficients of the derivative function in \lccref{eq:fourier_acceleration} is computed using \lccref{eq:derivative_coeff}.

\begin{align}
  \dv{u\left( t \right)}{t}                                        & = a\left(t\right) \label{eq:fourier_series_derivative}                                                            \\
  u\left( t \right)                                                & = \sum_{k} \hat{u}_k e^{2\pi ikt/T} \label{eq:fourier_speed}                                                      \\
  a\left( t \right)                                                & = \sum_{k} \hat{a}_k e^{2\pi ikt/T} \label{eq:fourier_acceleration}                                               \\
  \sum_{k} \hat{u}_k\times \left( 2\pi ik/T \right) e^{2\pi ikt/T} & = \sum_{k} \hat{a}_k e^{2\pi ikt/T} \label{eq:example_spectral_method_fourier_substituted}                        \\
  \hat{a}_k                                                        & = \hat{u}_k\left(2\pi ik/T \right)                                                    \label{eq:derivative_coeff}
\end{align}

In total, we generate \num{5000} unique functions with \num{50} complex coefficients each. We also add noise to the function values at three levels of the average function standard deviation. The entire set has three versions with different levels of noise which are 5\%, 10\% and 50\%.

% burgers
The second problem the model will be presented with is solving the Burgers' equation by stepping through time. Because of the nonlinearity of this equation, it is often used to test the capability of numerical solvers \citep{woodExactSolutionBurgers2006,wazwazPartialDifferentialEquations2010,koprivaImplementingSpectralMethods2009}. The formulation of the Burgers' equation we use is the forced viscous Burgers' equation in 1-dimension as shown in \lccref{eq:forced_viscous_burgers} where the viscosity is \(\nu{}\).
\begin{align}
  \pdv{u}{t}+u\pdv{u}{x}-\nu\pdv[2]{u}{x} & = f \label{eq:forced_viscous_burgers}
\end{align}

Data generation is done similarly to the derivative equation. With the solution as in \lccref{eq:fourier_field} and the forcing term \lccref{eq:fourier_force}, the equation for the forcing term is shown in \lccref{eq:forced_viscous_burgers_coeff}. The nonlinear term is approximated, for efficiency, in the physical domain and the coefficients subsequently computed as \(\hat{uu}_k\).
\begin{align}
  u\left(x, t \right) & = \sum_{k_{x}} \sum_{k_{t}} \hat{u}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)} \label{eq:fourier_field}                                         \\
  f\left(x, t \right) & = \sum_{k_{x}}\sum_{k_{t}} \hat{f}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)} \label{eq:fourier_force}                                          \\
  \hat{f}_k           & = (2\pi i k_{t}/T) \hat{u}_k + (2\pi i k_{x}/L)\hat{uu}_k - \nu{(2\pi i k_{x}/L)}^2\hat{u}_k \label{eq:forced_viscous_burgers_coeff}
\end{align}

The functions generated for the Burgers' equation will use three different values of \(\nu{}\) to in order to be able to analyze how the model behaves with varying levels of stiffness and nonlinearity. The values for viscosity are \num{0.0} for the inviscid equation, \num{0.01}, and \num{0.1} for a more stiff PDE\@. For each viscosity level, we generate \num{500} unique solution functions and compute the corresponding forcing term using \lccref{eq:forced_viscous_burgers_coeff}. Each function has 8 modes in space and 8 in time.

% WeatherBench 2
% The final dataset we use is the ERA5 dataset. The cloud optimized version from WeatherBench 2 we use will have a grid size of 64 in longitude by 32 in latitude. The model will attempt to partially model the complex weather data using only the 2-meter temperature variable. For the reanalysis dataset, we limit the time range to the years 1995{-}2013 for training and 2020{-}2022 for testing. The specific time ranges for training are chosen to balance the diversity within the data and capacity of the machine the processing will be done on. We also use the climatology provided by WeatherBench 2 which is the averages for hours 0, 6, 12, and 18 for each day of the year from 1990 until 2019.

\section{Results and Discussion}
In this section, we will present the results of the experiments on each equation and the ERA5 dataset. The metrics we will show in this section are evaluated between the function values evaluated from the predicted coefficients and the function values of the test label coefficients.

\subsection{Scenario 1: Derivative Equation}
For the derivative equation, metrics between the noisy targets and predictions are shown in \lccref{table:scenario_1_function_metrics}. The metrics shows that the model is able to generalize from the training data and learn the simple linear antiderivative operator. Focusing on the R\textsuperscript{2} scores, we can see that the model is off by 0.04 to the perfect score of 1.0 for the lowest noise level. While increasing noise levels does degrade the performance, this is partly due to the target values also having been perturbed.

For the function values of the 50\% noise dataset, the values range on average from \num{-2.5} to \num{2.49}. This was approximated since there is no direct way to compute the amplitude of the function from just the coefficients. Here we used the inverse transform and extracted the maximum and minimum values of each function from the discrete values. Since the RMSE in \lccref{table:scenario_1_function_metrics} for the 50\% noise dataset is \num{0.63}, the error ratio comes to \num{0.126}. One side note about \lccref{table:scenario_1_function_metrics} is that the kernel scaling hyperparameter is the same for all noise levels because of the scaling which is 10.
\begin{table}[H]
  \caption{Performance metrics of function value from evaluated coefficient prediction in scenario 1 by noise level.}\label{table:scenario_1_function_metrics}
  \centering
  \begin{tabular}{lrrrrrrrr}
    \toprule
    Noise level & MSE  & RMSE & MAE  & R\textsuperscript{2} & sMAPE \\
    \midrule
    5\%         & 0.03 & 0.18 & 0.15 & 0.97                 & 0.39  \\
    10\%        & 0.08 & 0.29 & 0.23 & 0.92                 & 0.55  \\
    50\%        & 0.62 & 0.79 & 0.63 & 0.49                 & 1.05  \\
    \bottomrule
  \end{tabular}
\end{table}

The metrics between the predictions and the noise-free version of the target function values can be seen in \lccref{table:scenario_1_clean_function_metrics}. The metrics show that the model predictions are slightly closer to the unperturbed functions compared to the perturbed versions. This can be seen as the influence of the independent measurement noise in the perturbed targets being removed from the testing metrics. The metrics show that the model performs slightly better with more pronounced differences for the higher noise levels.
\begin{table}[H]
  \caption{Performance metrics of function value from evaluated coefficient prediction compared to unperturbed targets in scenario 1 by noise level.}\label{table:scenario_1_clean_function_metrics}
  \centering
  \begin{tabular}{lrrrrrrr}
    \toprule
    Noise level & MSE  & RMSE & MAE  & R\textsuperscript{2} & sMAPE \\
    \midrule
    5\%         & 0.03 & 0.18 & 0.14 & 0.97                 & 0.38  \\
    10\%        & 0.07 & 0.27 & 0.21 & 0.93                 & 0.53  \\
    50\%        & 0.37 & 0.61 & 0.49 & 0.62                 & 0.94  \\
    \bottomrule
  \end{tabular}
\end{table}

The next part of this scenario is the results from predicting the exact solution of \(f(t)=2\pi\cos(2\pi t)\) which is \(u(t)=\sin(2\pi t)\). The function values will be computed, and the values put through the preprocessing steps as all other function values. The results are presented in \lccrefs{table:scenario_1_exact_function_metrics}. For 5\% and 10\% noise levels, the model shows that it has learned the relation. However, the 50\% noise level, the model has been unable to predict the results well enough. The marked difference in error across all metrics between the 50\% and the lower noise levels is more apparent for this specific exact problem compared to the test sets. A clear picture of this can be seen when we compare the sMAPE metric. For the test set, the predictions on average results in a value of 1, however, for this exact problem the sMAPE value is 0.23 to 1.65.
\begin{table}[H]
  \caption{Performance metrics of evaluated function values of coefficient prediction of exact antiderivative in scenario 1 by noise level.}\label{table:scenario_1_exact_function_metrics}
  \centering
  \begin{tabular}{lrrrr}
    \toprule
    Noise level & MSE  & RMSE & MAE  & sMAPE \\
    \midrule
    5\%         & 0.00 & 0.06 & 0.05 & 0.23  \\
    10\%        & 0.03 & 0.18 & 0.15 & 0.36  \\
    50\%        & 0.41 & 0.64 & 0.58 & 1.65  \\
    \bottomrule
  \end{tabular}
\end{table}

The predictions of the exact equation is shown in \lccref{fig:antiderivative_exact}. Visually, we can see that as the noise level increases, the model predictions become worse. Another observation is how the higher the noise level, the more the predicted functions become closer to zero. This is explained by the double penalty phenomenon \citep{lledoScaledependentVerificationPrecipitation2023}. The loss function used for LSSVR penalizes the model for predicting a non-zero value that turns out to be wrong compared to predicting a zero value. This results in a model with predictions that are close to the mean of the training data.
\begin{figure}[H]
  \centering
  \begin{subfigure}{\linewidth}
    \begin{adjustbox}{width=\linewidth}
      \input{figures/antiderivative_exact_input.pgf}
    \end{adjustbox}
    \caption{}\label{fig:antiderivative_exact_input}
  \end{subfigure}
  \begin{subfigure}{\linewidth}
    \begin{adjustbox}{width=\linewidth}
      \input{figures/antiderivative_exact_prediction.pgf}
    \end{adjustbox}
    \caption{}\label{fig:antiderivative_exact_prediction}
  \end{subfigure}
  \caption{(\subref{fig:antiderivative_exact_input}) The perturbed exact input function values from \lccref{eq:sine_derivative}.\ (\subref{fig:antiderivative_exact_prediction}) Prediction of antiderivative from the input function that was perturbed.}\label{fig:antiderivative_exact}
\end{figure}

Next, we have the correlation image and p-matrix for the model of each noise level. The results are shown in \lccref{fig:scenario_1_interpretation}. Each row in the figure represent the results of a model trained on a different noise level. The correlation image for 5\% and 10\% noise show clear lines on the coefficient corresponding to the output coefficient that was sorted. We can also see that the negative wave number reflection also being sorted. This is because of the reflection that occurs with complex Fourier coefficients for real-valued functions. There are other faint vertical lines you are able to see for other input coefficients. These faint lines are not sorted like the corresponding coefficients we mentioned before. Meaning, while they don't affect the particular output coefficients that were sorted, they do show that there is information embedded in the kernel matrix for these input coefficients. However, if we look at the 50\% noise correlation image, even the corresponding coefficient does not show a clear line or gradient. The lines are more noisy compared to the other noise levels. But the kernel still manages to embed some information. The p-matrices show that The model itself is able to still learn some relationship between the input coefficients and the output coefficients. For the 5\% and 10\% noise levels, the p-matrices show very clearly the contributions of input coefficients to the output coefficients. However, looking at the p-matrix for 50\% noise level, the lower wave numbers show lower contribution of input coefficients to the output coefficients.
\begin{figure}[H]
  \begin{adjustwidth}{-0.05\linewidth}{-0.05\linewidth}
    \centering
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/antiderivative_ci_5.pgf}
      \end{adjustbox}
      \caption{Correlation image 5\% noise.}\label{fig:sc1_ci_5}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/antiderivative_pm_5.pgf}
      \end{adjustbox}
      \caption{The p-matrix for 5\% noise.}\label{fig:sc1_pm_5}
    \end{subfigure}
    % \\[\baselineskip]
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/antiderivative_ci_10.pgf}
      \end{adjustbox}
      \caption{Correlation image 10\% noise.}\label{fig:sc1_ci_10}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/antiderivative_pm_10.pgf}
      \end{adjustbox}
      \caption{The p-matrix for 10\% noise.}\label{fig:sc1_pm_10}
    \end{subfigure}
    % \\[\baselineskip]
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/antiderivative_ci_50.pgf}
      \end{adjustbox}
      \caption{Correlation image 50\% noise.}\label{fig:sc1_ci_50}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/antiderivative_pm_50.pgf}
      \end{adjustbox}
      \caption{The p-matrix for 50\% noise.}\label{fig:sc1_pm_50}
    \end{subfigure}
  \end{adjustwidth}
  \caption{Correlation image (left column) and p-matrix (right column) for each model trained on a different noise level (row). The correlation image was sorted same order the values of the real component of wave number \(k=2\) were sorted in descending order.}\label{fig:scenario_1_interpretation}
\end{figure}

The final observation we make is how for all the p-matrices the pronounced contribution of the input wave number to their corresponding output wave number. This means that the majority of contributions to each output coefficients come from the corresponding input coefficients of the same wave number. Our knowledge on how the simple derivative equation for Fourier series relate the coefficients of the derivative function and the antiderivative function is shown in \lccref{eq:derivative_coeff}. This aligns with the contributions shown by the p-matrices. This confirms that the model is indeed learning the relations that is defined by the derivative equation.

\subsection{Scenario 2: Burgers' Equation}
The function value evaluated from the predictions is shown in \lccref{table:scenario_2_function_metrics}. The metrics across the board shows that the function value relative metrics are slightly better compared to the coefficients. Comparing the absolute metrics for the same table, we see the same general trend that the higher viscosity show the model performing worse. For reference, the maximum amplitude of the functions on average are \num{2.56e-02}. This puts the error in an order of magnitude less than the average maximum amplitude.
\begin{table}[H]
  \caption{Performance metrics of function values evaluated from coefficient prediction of next time step in scenario 2 by viscosity.}\label{table:scenario_2_function_metrics}
  \centering
  \begin{tabular}{lrrrrr}
    \toprule
    \(\nu \) & MSE      & RMSE     & MAE      & R\textsuperscript{2} & sMAPE \\
    \midrule
    0.0      & 5.58e-05 & 7.47e-03 & 5.89e-03 & 0.82                 & 0.70  \\
    0.01     & 5.74e-05 & 7.58e-03 & 6.01e-03 & 0.81                 & 0.71  \\
    0.1      & 1.58e-04 & 1.26e-02 & 9.98e-03 & 0.51                 & 1.04  \\
    \bottomrule
  \end{tabular}
\end{table}

The testing results are complimented with a rollout experiment. The results from the rollout are shown in \lccref{fig:scenario_2_rollout}. The rollout starts from time \(t=0\). In all the plots, this is at the bottom. We have included this initial condition in the plots. From this initial condition in combination with the forcing term at the initial time step, the model predicts the first time step solution. The model then uses the predicted solution combined with the corresponding forcing term to predict the second time step. To see how well the model is performing relative to the actual target values, we compute the difference between the two as shown in \lccrefs{fig:sc2_rollout_diff_0.0,fig:sc2_rollout_diff_0.01,fig:sc2_rollout_diff_0.1}. Observe that errors are introduced relatively early around time \(t=1\). However, the model rollout stays stable until the end despite this error. This results in the model being able to finish the rollout for this sample.
\begin{figure}[H]
  \centering
  \begin{adjustwidth}{-0.1\linewidth}{-0.1\linewidth}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_target_0.0.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.0\)}\label{fig:sc2_rollout_target_0.0}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_pred_0.0.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.0\)}\label{fig:sc2_rollout_pred_0.0}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_diff_0.0.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.0\)}\label{fig:sc2_rollout_diff_0.0}
    \end{subfigure}
    \\[0.7\baselineskip]
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_target_0.01.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.01\)}\label{fig:sc2_rollout_target_0.01}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_pred_0.01.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.01\)}\label{fig:sc2_rollout_pred_0.01}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_diff_0.01.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.01\)}\label{fig:sc2_rollout_diff_0.01}
    \end{subfigure}
    \\[0.7\baselineskip]
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_target_0.1.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.1\)}\label{fig:sc2_rollout_target_0.1}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_pred_0.1.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.1\)}\label{fig:sc2_rollout_pred_0.1}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_diff_0.1.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.1\)}\label{fig:sc2_rollout_diff_0.1}
    \end{subfigure}
    % \\[0.7\baselineskip]
  \end{adjustwidth}
  \caption{The rollout predictions for one of the test function. The difference is calculated as the targets subtracted by the predictions.}\label{fig:scenario_2_rollout}
\end{figure}

Another observation we can see is that the difference between the target and rollout predictions is much more pronounced for lower viscosity values. This result is aligned with metrics shown in \lccrefs{table:scenario_2_rollout_function_metrics}. The absolute metrics show that the models are performing several times worse in rollout compared to the single time step tests shown in \lccrefs{table:scenario_2_function_metrics}. This seems to be the same challenge that traditional solvers also face with the shocks that may be present with lower viscosity values. This means that for rollout scenarios, the model has a much harder time with lower viscosity values. The observation here is that for higher viscosity values, the error is dominated by the global error, and the lower viscosity value, the error is dominated by local errors and as such accumulates.
\begin{table}[H]
  \caption{Performance metrics of function values evaluated from coefficient rollout in scenario 2 by viscosity.}\label{table:scenario_2_rollout_function_metrics}
  \centering
  \begin{tabular}{lrrrr}
    \toprule
    \(\nu \) & MSE      & RMSE     & MAE      & sMAPE \\
    \midrule
    0.0      & 5.81e-02 & 2.41e-01 & 1.89e-01 & 1.04  \\
    0.01     & 3.17e-02 & 1.78e-01 & 1.40e-01 & 0.94  \\
    0.1      & 2.91e-02 & 1.71e-01 & 1.33e-01 & 0.92  \\
    \bottomrule
  \end{tabular}
\end{table}

The exact function \cref{eq:burgers_exact_solution} is computed for each viscosity value. The discrete Fourier transform of the values are then used for doing rollout with the model. For the forcing term, we just use a constant function with a value of zero. The rollout predictions are shown in \lccref{fig:scenario_2_exact}. The model is not successful in the rollout for the inviscid equation and for the viscosity of \(\nu=0.01\). Both of these cases, the model produces too much error that the original function is no longer recognizable in the predictions. For the higher viscosity value of \(\nu=0.1\) the rollout produces a recognizable prediction. The error stays to about half the maximum function value. We do see some more noticeable error in the flatter parts of the function. The error also take a very similar shape across the different viscosity values. Since we essentially used the same solutions for training the model for each viscosity, the similarity in error means that it can be alleviated with more diverse training samples. The error for the flatter functions may also be alleviated by including similar flatter functions during training.
\begin{figure}[H]
  \centering
  \begin{adjustwidth}{-0.1\linewidth}{-0.1\linewidth}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_target_0.0.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.0\)}\label{fig:sc2_exact_target_0.0}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_pred_0.0.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.0\)}\label{fig:sc2_exact_pred_0.0}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_diff_0.0.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.0\)}\label{fig:sc2_exact_diff_0.0}
    \end{subfigure}
    \\[0.7\baselineskip]
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_target_0.01.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.01\)}\label{fig:sc2_exact_target_0.01}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_pred_0.01.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.01\)}\label{fig:sc2_exact_pred_0.01}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_diff_0.01.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.01\)}\label{fig:sc2_exact_diff_0.01}
    \end{subfigure}
    \\[0.7\baselineskip]
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_target_0.1.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.1\)}\label{fig:sc2_exact_target_0.1}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_pred_0.1.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.1\)}\label{fig:sc2_exact_pred_0.1}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_diff_0.1.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.1\)}\label{fig:sc2_exact_diff_0.1}
    \end{subfigure}
    % \\[0.7\baselineskip]
  \end{adjustwidth}
  \caption{The rollout predictions for one of the exact function in \lccref{eq:burgers_exact_solution}. The difference is calculated as the targets subtracted by the predictions.}\label{fig:scenario_2_exact}
\end{figure}

The correlation image and p-matrix for each viscosity can be seen in \lccref{fig:scenario_2_interpretation}. Analyzing the correlation images first, we see that some columns are sorted in correlation to how the samples are sorted based on the real component of the 4th output wave number. For the inviscid equation, this correlation is the strongest with multiple columns exhibiting the correlation. The highest and visually most sorted values are from the forcing term portion of the inputs. Different wave numbers in the inputs are also sorted differently, this indicates an inverse correlation. For a higher viscosity of \(\nu=0.01\), a weaker correlation is still present.
\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\linewidth}
    \begin{adjustbox}{width=\linewidth}
      \input{figures/burgers_ci_0.0.pgf}
    \end{adjustbox}
    \caption{Correlation image \(\nu=0.0\).}\label{fig:sc2_ci_0.0}
  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
    \begin{adjustbox}{width=\linewidth}
      \input{figures/burgers_pm_0.0.pgf}
    \end{adjustbox}
    \caption{The p-matrix for \(\nu=0.0\).}\label{fig:sc2_pm_0.0}
  \end{subfigure}
  % \\[-0.7\baselineskip]
  \begin{subfigure}{0.49\linewidth}
    \begin{adjustbox}{width=\linewidth}
      \input{figures/burgers_ci_0.01.pgf}
    \end{adjustbox}
    \caption{Correlation image \(\nu=0.01\).}\label{fig:sc2_ci_0.01}
  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
    \begin{adjustbox}{width=\linewidth}
      \input{figures/burgers_pm_0.01.pgf}
    \end{adjustbox}
    \caption{The p-matrix for \(\nu=0.01\).}\label{fig:sc2_pm_0.01}
  \end{subfigure}
  % \\[-0.7\baselineskip]
  \begin{subfigure}{0.49\linewidth}
    \begin{adjustbox}{width=\linewidth}
      \input{figures/burgers_ci_0.1.pgf}
    \end{adjustbox}
    \caption{Correlation image \(\nu=0.1\).}\label{fig:sc2_ci_0.1}
  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
    \begin{adjustbox}{width=\linewidth}
      \input{figures/burgers_pm_0.1.pgf}
    \end{adjustbox}
    \caption{The p-matrix for \(\nu=0.1\).}\label{fig:sc2_pm_0.1}
  \end{subfigure}
  \caption{Correlation image (left column) and p-matrix (right column) for each model trained on a different viscosity (row). The correlation image was sorted same order the values of the real component of wave number \(k=2\) were sorted in descending order.}\label{fig:scenario_2_interpretation}
\end{figure}

Once we get to the highest viscosity, while the order is still present, we see a more random arrangement of the correlation image values. This observation and the lower scores can both be explained by the level of temporal discretization. This is the same issue we encounter when we use some traditional methods for higher viscosity values with the same time step for lower viscosity values \citep{kassamFourthOrderTimeSteppingStiff2005,seydaogluNumericalSolutionBurgers2016}. The issue arises in stiff differential equations. Stiff differential equations refer to the presence of a rapidly varying component. We can see that the larger amplitudes of high frequency components in the forcing term to represent the rapidly varying components as shown in \lccrefs{fig:burgers_forcing_0.0,fig:burgers_forcing_0.01,fig:burgers_forcing_0.1}. Traditionally, stiff equations would require specific numerical methods purpose built to efficiently solve the problem. Otherwise, the using a solver like FDM would require much finer time steps than the one we are using here.%TODO: add the data figures to the appendix

The p-matrix shows the difference in contributions of both input functions. For the inviscid equation, the contributions mainly come from the forcing term. The current solution contributes a smaller amount in comparison. There is similarity with the antiderivative p-matrices in this case. The contributions to each output wave number mainly come from input coefficients with the same wave number. However, there is a noticeable contribution from other wave numbers too unlike the antiderivative case. The biggest contribution from the current solution is the constant/bias term. For higher viscosity values, notice that the contribution of the previous solution increases. The increase is more pronounced for higher frequencies. This aligns with the quadratic scaling from the wave number on the coefficients \citep{canutoSpectralMethodsEvolution2007}. The p-matrix for lower viscosity values show more structured contribution of other wave numbers in comparison to the higher wave numbers. This structure comes in the form of a grid pattern. For the real components of the output, the contribution of other wave numbers oscillate between higher and lower values depending on whether the input component is real or not. The imaginary output components on the other hand have a more constant contribution across the input components. The contribution once again become more pronounced the higher the absolute value of the wave number.
\section{Conclusion}
\noindent Based on the results of the research into \MakeLowercase{\judul}, several conclusions can be drawn.
\begin{enumerate}
  \item The proposed SpectralSVR model is able to learn the relationships defined by PDEs. This is done using a model that learns in the Fourier domain with Fourier Transforms and Inverse Transform bridging the Fourier domain and the physical domain.
  \item Interpretation of the proposed model can be done to a certain extent using two tools which are the correlation image and p-matrix developed by \citet{alisationInterpretationSupport2007}. This interpretation shows that the model correctly attributes the relationship of the input coefficients to the output coefficients.
  \item The proposed model is also capable in dealing with noise and partial data as shown in scenario 1.
        % \item The model's capabilities are also verified using exact solution. This revealed that for some configurations the model is able to successfully generalize to exact solutions.
\end{enumerate}

To improve the model's predictive capabilities, several key areas of enhancement have been identified for future works. First, the synthetic data used in scenarios 1 and 2 lack realism, even though they are mathematically correct when generated using the method of manufactured solutions. Incorporating data derived from traditional numerical methods or other reliable sources could help the model produce more accurate and realistic predictions. Evaluating the performance of auto-regression in weather data compared to target data is another critical step. Additionally, the inverse prediction results should be compared with traditional methods, such as the spectral method or finite difference method (FDM), to assess accuracy and reliability.

Further improvements include benchmarking the proposed method against comparable approaches and measuring computational efficiency in terms of time, relative to both traditional and machine learning-based methods. Expanding the range of basis functions, such as spherical harmonics or wavelet bases, and incorporating additional regression models, specifically support vector regression models, could enhance the utility of tools like the correlation image and p-matrix. The use of better performance metrics, such as the standard error of regression, is recommended, along with a detailed analysis of performance across varying hyperparameters, data sizes, and error trends by wave number. Addressing the issue of double penalties, which lead to overly smooth solutions \citep{brownForecastsSpatialFields2011,NIPS2017_44a2e080}, requires exploring stronger regularization for higher wave numbers. Finally, incorporating data assimilation techniques, such as the Lomb-Scargle periodogram \citep{vanderplasUnderstandingLombScargle2018} and 4D-Var assimilation \citep{puNumericalWeatherPrediction2018,parkDataAssimilationAtmospheric2013}, could enable support for sparse data. Finally, a study of contribution patterns for different terms in partial differential equations (PDEs) using methods like the p-matrix would provide deeper insights into model dynamics.

These future directions build on the strengths of the proposed SpectralSVR model, which has demonstrated its ability to learn relationships defined by PDEs, interpret results using tools like the correlation image and p-matrix, and handle noise and partial data effectively. By addressing these identified areas of improvement, the model's robustness, accuracy, and applicability could be further enhanced, especially in real-world scenarios.

Through these developments, the SpectralSVR model has the potential to not only refine its generalization capabilities, as evidenced by its partial success with exact solutions, but also to expand its utility across diverse and complex problems. These steps will contribute to advancing computational approaches for SciML-based modelling and establish the proposed framework as a versatile tool in this domain.
\bibliographystyle{elsarticle-harv}
\bibliography{references.bib}
\end{document}

### 2025-01-14 article/apendix.tex
fix labels, fix problem with graphics path and suround with curly braces, start technical document

--- 2025-01-06 skripsi/chapter4.tex
@@
-% !TEX root = ./skripsi.tex
-\chapter{RESULTS AND DISCUSSION}
-\noindent This chapter will elaborate on the results of the study and relevant phases for analysis.
-This chapter is organized into five sections which are the results of data generation, data retrieval, design of computational model, implementation of computational model, experimental scenarios, and the experiments themselves.
-
-\section{Data Generation}\label{sec:data_generation}
-\noindent This study uses two data acquisition approaches.
-The first approach which is discussed in this section is data generation.
-This process involves manufacturing data randomly in such a way that they obey the PDEs to be modeled.
-The generated data consists of features and labels.
-These features and labels in the context of PDEs are parameters and the solution of the PDEs, respectively.
-The PDEs enforce a relationship between parameters and the solution.
-This relationship is implicitly encoded into the features and labels, which is what machine learning models can learn.
-Because the solution and parameters to PDEs are functions and there are many kinds with different properties, generating all the different kinds of functions is a difficult task.
-This is why this study focuses on Fourier functions.
-This means that out of the space of all functions \(F \) which include categories such as polynomials \(f\left(x\right)=a_{n}x^n+\cdots+a_1x+a_0\) where \(f\in F\), and \(a_n\) are constants; we only consider the subset of functions \(U \subset F\) which are of the form \(u\left(x\right)=\sum_{k}^{m}c_k e^{2\pi i k \frac{x}{P}}\).
-
-Using the subset of Fourier functions has several benefits which has motivated the choice.
-First these functions are characterized purely by their coefficients \(c_k\), meaning there is no need to store discretized values which potentially saves space and computation.
-The second benefit is that other functions such as polynomials can be approximated by them using the Fourier transform.
-This means that despite limiting the set of functions to Fourier functions, the behavior of PDEs with other sets of functions can be approximated to a certain extent.
-The final benefit is the mature ecosystem around these functions which include fast algorithms for the Fourier transform and even numerical approaches for solving known PDEs like the previously mentioned spectral method.
-In summary the generated data consists of features and labels which are Fourier functions implicitly defining the relationship enforced by a PDE and scenario.
-After establishing the kind of functions to be used in dataset generation, the process can proceed.
-There are 4 steps involved in the data generation:% TODO: add reference to second chapter for spectral method, fourier transform, and other external concepts.
-\begin{enumerate}
-  \item Scenario and PDE Determination:
-        The first step of data generation is determining the scenario related to the PDE or governing equations.
-First, the PDE to be modeled is determined based on the goals of the dataset.
-Then, one or more of the parameters is chosen to predict the solution.
-The chosen parameters will be called the input functions and the solution will be called output functions from here on.
-The second part of the scenario is the domain or more simply the physical space occupied by the system to be modeled.
-The domain will be used to compute the function values in relation to the physical space from coefficients of Fourier functions.
-  \item Parameter Determination:
-        The second step is determining all parameters other than that input parameter based on the scenario and governing equation.
-These parameters may be coefficients such as material properties like density or viscosity, or forcing terms which model external influence on the system like a heat source in the case of the heat equation.
-Depending on the parameters, solutions of PDEs may behave very differently, such as the appearance of discontinuities in the solution to low viscosity Burgers' equation.
-Because of this, the choice of parameters is guided by what the dataset seeks to do.
-  \item Random Coefficient Generation:
-        The third step of data generation is randomly generating the solutions for the chosen equation.
-Generating random functions in the space of Fourier functions exploits the fact that the coefficients characterize the function completely.
-By randomly assigning coefficients \(c_k\), many functions can be generated randomly with very little cost.
-Since the coefficients need to be complex numbers as in \lccref{eq:complex_number}, both real and imaginary components are generated independently by assigning a random value to each component for each wave number \(k\).
-They are then put together again into complex numbers.
-
-        Since only real functions are of interest in this study, the generation cost can be approximately halved.
-This is because for real functions the coefficients for negative wave numbers \(k\) are complex conjugate of the positive wave numbers.
-This means that once the positive coefficients are generated, one only needs to compute their complex conjugate and concatenate the result with the coefficients of positive wave numbers.
-For dimensions higher than one, a simpler approach is used.
-The coefficients are generated for all wave numbers including the negative ones.
-The inverse Fourier transform is computed and this results in complex functions.
-The real components of these functions are kept and the Fourier transform is applied to get the coefficients of the real functions.
-Finally, these generated coefficients then be used with the basis functions as input functions.
-        % TODO: add diagram for generating real functions, the mirroring process too
-  \item Forcing Term Computation:
-        Finally, in order to ensure that the generated solution and chosen parameters satisfy the equation, the forcing term is computed as the residual of the equation of interest with the parameters that was previously determined.
-This computation is done using the spectral method.
-  \item Function Value and Noise Computation:
-        The generated solution and forcing functions are labeled as input and output functions.
-The values of both functions in the domain can then be computed using the scenario determined in the first step.
-Once all coefficients are generated, the function values are computed with an inverse Fourier transform.
-The real component of the function values are retained, and the imaginary component are zeroed out.
-Noise is added to the function values here as needed.
-The processed function values are then converted back into coefficients using a Fourier transform.
-This processing is necessary to ensure that the coefficients are only describing the real function.
-
-\end{enumerate}
-
-These four steps are the general processes involved in generating datasets for this study. Further specifics of the generation process of each dataset is explained in their respective subsections.
-
-\subsection{Data Generation: Anti-derivative}
-\noindent The first dataset is a simple one dimensional derivative.
-This was chosen as a simple proof of concept of the ability to solve a differential equation.
-The equation is related to many real-world problems such as acceleration and speed.
-One can imagine a train in an ideal world where acceleration is directly translated into speed.
-When the train accelerates at time \(t \) by some amount \(a \), we can expect the train to have some speed \(u \).
-In this ideal world, the relationship between speed and acceleration can be modeled with a simple differential \lccref{eq:derivative}.
-This scenario is found in many real systems albeit often with many more details such as different components of acceleration from friction, drag, gravity, and other factors.
-As previously mentioned in \lccref{sec:data_generation}, both velocity \(u \) and acceleration \(a \) are modeled with Fourier series in \lccrefs{eq:fourier_speed,eq:fourier_acceleration} respectively.
-\begin{align}
-  \dv{u\left( t \right)}{t} & = a\left( t \right) \label{eq:derivative}                         \\
-  u\left( t \right)         & = \sum_{k} \hat{u}_k e^{2\pi ikt} \label{eq:fourier_speed}        \\
-  a\left( t \right)         & = \sum_{k} \hat{a}_k e^{2\pi ikt} \label{eq:fourier_acceleration}
-\end{align}
-The domain of the scenario is a two-hour time window.
-This number was chosen because it is around the ideal length of travel time on high speed rail in comparison to air travel and car travel \autocite{givoniDevelopmentImpactModern2006,wangEfficiencySpatialEquity2019,wrro2236}.
-This is the first step in generating this dataset.
-
-In the second step, as the derivative \lccref{eq:derivative} does not contain any parameters other than the acceleration which is the input parameter, there are no other parameters to determine.
-Therefore, the data generation process proceeds to generating coefficients for the speed functions \(\hat{u} \).
-The coefficients are assigned randomly from a Gaussian distribution with a mean of zero and standard deviation of one.
-This choice was made such that most wave numbers will have a coefficient of close to zero leaving a sparse set of wave numbers to mostly affect the resulting function.
-In total, 5000 unique functions are generated with 100 complex coefficients each.
-
-In the third step, the output function coefficients are computed.
-To find the relation between \(\hat{u}_k \) and \(\hat{a}_k \), we need to find substitutes for each term in \lccref{eq:derivative}.
-To do this, we take the derivative of \lccref{eq:fourier_speed} which result in \lccref{eq:fourier_series_derivative}.
-Using this we can substitute the terms in \lccref{eq:derivative} with \lccrefs{eq:fourier_series_derivative,eq:fourier_acceleration} giving \lccref{eq:example_spectral_method_fourier_substituted}.
-Finally, after some algebraic manipulation we obtain the relationship between the input \(a^*\) and output function \(u^*\) in terms of their coefficients in \lccref{eq:derivative_coeff}.
-One also needs to choose the integration constant \(\hat{u}_{0}\) because at \(k=0\) \lccref{eq:derivative_coeff} becomes a division by zero.
-\begin{align}
-  \dv{u\left( x \right)}{x}                                    & = \sum_{k} \hat{u}_k\times \left( 2\pi ik \right) e^{2\pi ikx} \label{eq:fourier_series_derivative} \\
-  \sum_{k} \hat{u}_k\times \left( 2\pi ik \right) e^{2\pi ikx} & = \sum_{k} \hat{a}_k e^{2\pi ikx} \label{eq:example_spectral_method_fourier_substituted}            \\
-  \hat{u}_k                                                    & = \hat{a}_k / \left( 2\pi ik \right) \label{eq:derivative_coeff}
-\end{align}
-
-In the final step, using randomly generated values of \(\hat{a}_k\), the corresponding values of \(\hat{u}_k\) are computed with \lccref{eq:derivative_coeff}.
-These coefficients are then used to compute the function values inside the domain.
-The two-hour time window is represented by a grid of 500 discrete points.
-With the coefficients and evaluation points ready, the function values are computed using \lccrefs{eq:fourier_speed,eq:fourier_acceleration}.
-Next, noise is added to the function values in order to motivate models learning on the dataset to generalize on noise.
-To also allow evaluation of how well the model performs with different levels of noise, the samples are duplicated into three copies for each high, medium and low noise levels.
-The function values of each copy is perturbed with noise from a Gaussian distribution with zero mean and standard deviation of some percentage of the average function value standard deviation.
-The percentages of each high, medium, and low noise levels are 5, 10, and 50 percent.
-The perturbed function values are then transformed back into their coefficients.
-An example generated function and its different perturbed versions is shown in \lccref{fig:antiderivative_noise_levels}.
-The horizontal axis indicates time which is displayed in units of hours.
-The vertical axis indicates velocity in abstract units.
-
+% !TEX root = ./article.tex
+\appendix
+\section{Derivative Equation Generated Data Example}
 \begin{figure}[H]
@@
 \end{figure}
-% TODO: interesting note that model trains better on function to coefficient task when the antiderivative is computed from the randomly generated derivative than if the derivative is computed from the randomly generated antiderivative.
-THIS NEEDS A REASON AND ANALYSIS SO MIGHT NOT BE NEEDED IN THIS WRITING.
-MAYBE A GOOD IDEA FOR A SEPARATE PIECE
 
-\subsection{Data Generation: Burgers' Equation}
-\noindent The second dataset generated in this study concerns the Burgers' equation.
-This equation has been used to model a variety of cases including fluid dynamics, traffic flow, and, shock waves \autocite{bonkileSystematicLiteratureReview2018,orlandiBurgersEquation2000,becBurgersTurbulence2007,jamesonEnergyEstimatesNonlinear2007}.
-This equation is also used as a base problem for testing the effectivity of numerical methods in solving non-linear PDEs \autocite{barterShockCapturingPDEbased2008,banksNumericalErrorEstimation2012, tabatabaeiImplicitMethodsNumerical2007,bonkileSystematicLiteratureReview2018}.
-The nonlinear term in the equation creates steep gradients and even shock waves which are discontinuous with low viscosity conditions.
-These challenges test the stability of numerical solvers.
-This is the scenario and reason for the choice of this PDE\@.
-To control the viscosity and therefore the steepness of gradients, the formulation of the Burgers' equation considered in this study is the forced viscous Burgers' equation in one dimension.
-For a velocity of \(u(x, t)\), viscosity of \(\nu \), and forcing term of \(f(x, t)\), the formulation of the forced Burgers' equation is shown in \lccref{eq:forced_viscous_burgers}.
-\begin{align}
-  \pdv{u}{t}+u\pdv{u}{x}-\nu\pdv[2]{u}{x} & = f \label{eq:forced_viscous_burgers}
-\end{align}
-The domain of we consider here is based on an exact solution of the equation.
-This is done so that the learned solver model can be tested on the exact solution.
-There are a number of sources in literature on the exact solution of the Burgers' equation \autocite{bentonTableSolutionsOnedimensional1972,wazwazPartialDifferentialEquations2010,woodExactSolutionBurgers2006}.
-In this study, we use a specific solution by \textcite{woodExactSolutionBurgers2006} which can be seen in \lccref{eq:burgers_exact_solution}.
-This solution is periodic in space but not in time.
-Therefore, the domain in space will be based on the spatial periodicity of the exact solution which is two.
-As such, the space domain spans from 0 to 2.
-The time domain, on the other hand, is chosen to span from 0 to 10 such that enough details of the solution is included.
-\begin{equation}
-  u(x,t) = \frac{2\nu\pi e^{-\pi^2\nu t}\sin(\pi x)}{a+e^{-\pi^2\nu t}\cos(\pi x)} \label{eq:burgers_exact_solution}
-\end{equation}
-Continuing to the second step, the parameters involved in \lccref{eq:forced_viscous_burgers} are the viscosity \(\nu \) and the forcing term \(f \).
-Since the forcing term is dependent on the solution in this step, the only parameter to determine is the viscosity.
-We choose three constant viscosity values which are 0.1, 0.01, and 0.0.
-These values are chosen so that a variety of behaviors are represented in the dataset from viscous to inviscid flow.
-
-After this, in the third step, the solution functions \(u \) are generated with 8 modes in time and 8 in space and 500 unique function samples for each viscosity value.
-Since we don't factor the viscosity in at this point, for ease of comparison, we ensure the same solutions are generated every time by using a new instance of the generator with the same seed number each time.
-This results in the solutions being the same for all viscosity and other parameters of the equation are adapted to this.
-
-Next we account for the different viscosity values in this stage.
-The forcing term is computed using \lccref{eq:forced_viscous_burgers}.
-The solution field \(u\) and forcing term \(f\) are modeled with Fourier series in \lccrefs{eq:fourier_field,eq:fourier_force} where \(k\) is a vector of spatial and temporal wave number such that \(k_t\) is the temporal wave number and \(k_x\) is the spatial wave number.
-\begin{align}
-  u\left(x, t \right) & = \sum_{k_{x}} \sum_{k_{t}} \hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)} \label{eq:fourier_field} \\
-  f\left(x, t \right) & = \sum_{k_{x}}\sum_{k_{t}} \hat{f}_k e^{2\pi i(k_{x}x+k_{t}t)} \label{eq:fourier_force}
-\end{align}
-Substituting the terms in \lccref{eq:forced_viscous_burgers} with the respective Fourier series, we get the equation \lccref{eq:forced_viscous_burgers_fourier_substitution}.
-A problem one notices is the nonlinear term \(u\pdv{u}{x}\).
-A naive approach would multiply all wave numbers terms with each other.
-\begin{align}
-  u\pdv{u}{x} = \left(\sum_{k_{x}} \sum_{k_{t}} \hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)}\right) \times \left(\sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{x})\hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)}\right)
-\end{align}
-This is computationally expensive operation with \(N^2\) multiplications \autocite{lariosMATH934BURGERS2021,robertsDealiasedConvolutionsPseudospectral2011,shenSpectralMethodsAlgorithms2011,orszagComparisonPseudospectralSpectral1972}.
-To avoid this complexity, the term is first reformulated into \(\pdv{x}(u^2/2)\).
-Then to avoid aliasing, the coefficients are padded with 50\% zeros such that the padded coefficients are 3/2 times the size of the original \autocite{orszagEliminationAliasingFiniteDifference1971, lariosMATH934BURGERS2021}.
-Then we use the padded coefficients to compute the function values in the physical domain using the inverse transform.
-And then, the point wise squaring operation is performed and transform the results back to spectral domain.
-The resulting coefficients are then trimmed back to their original size before padding.
-Finally, we multiply the resulting coefficients \(\hat{uu}_k\) by the derivative constants.
-This operation is much more efficient with only \(1.5 N\) multiplications.
-This is still more efficient than the naive approach even after taking into account the transforms involved adds \(O(2\times 1.5Nln(1.5N))\) operations if using a Fast Fourier Transform algorithm.
-Putting all the above together, results in \lccref{eq:forced_viscous_burgers_fourier_substitution}.
-\begin{equation}
-  \begin{split}
-    \sum_{k_{x}} \sum_{k_{t}} \hat{f}_k e^{2\pi i(k_{x}x+k_{t}t)} =
-     & \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{t}) \hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)}                                                                \\
-     & + \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{x})\hat{uu}_k e^{2\pi i(k_{x}x+k_{t}t)}                                                              \\
-     & - \nu\sum_{k_{x}} \sum_{k_{t}} {(2\pi i k_{x})}^2\hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)} \label{eq:forced_viscous_burgers_fourier_substitution}
-  \end{split}
-\end{equation}
-\begin{align}
-  \sum_{k_{x}} \sum_{k_{t}} \hat{f}_k & = \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{t}) \hat{u}_k + (2\pi i k_{x})\hat{uu}_k - \nu{(2\pi i k_{x})}^2\hat{u}_k \label{eq:forced_viscous_burgers_fourier} \\
-  \hat{f}_k                           & = (2\pi i k_{t}) \hat{u}_k + (2\pi i k_{x})\hat{uu}_k - \nu{(2\pi i k_{x})}^2\hat{u}_k \label{eq:forced_viscous_burgers_coeff}
-\end{align}
-After simplifying the equation, we get the coefficients as in \lccref{eq:forced_viscous_burgers_coeff}.
-Using this equation, the exact forcing term corresponding to the randomly generated solution can be computed with relatively low cost.
-Finally, the function values of both the solutions and forcing terms are perturbed by adding Gaussian noise with a mean of zero and standard deviation of 10\% of the function value standard deviation to the values of the inverse transform.
-The perturbed coefficients are then recomputed from the sum and the final perturbed functions are obtained.
-
-An example of the solution and forcing term pairs that has been generated is shown in \lccref{fig:burgers_data}.
-Using the same seed we can see that the solution functions of the same sample are the same.
-However, with the forcing terms, we see much larger amplitudes for higher frequencies for larger viscosity values.
-This is inline with \lccref{eq:forced_viscous_burgers_coeff}.
-The squared multiplier gets large much more quickly for higher frequencies due to the squaring operation.
-The since this effect is controlled by the viscosity via multiplication, the higher the viscosity, the larger the high frequency amplitudes of the forcing term.
-This, in other words, means that more viscous fluids require a stronger forcing term to affect the solution in the same way with as fluids with a lower viscosity.
-
+\section{Burgers' Equation Generated Data Example}
 \begin{figure}[H]
@@
 \end{figure}
-
-\section{Data Retrieval}\label{sec:data_retrieval}
-\noindent The second data acquisition approach retrieves data of a from an external source.
-This approach downloads the external data to a local machine.
-In this study, the specific dataset that will be used is the ERA5 dataset from the European Center for Medium-range Weather Forecast (ECMWF).
-Specifically, the ERA5 dataset is a reanalysis which means it combines observational data from all over the world in order to present a more complete picture of the weather system.
-This combination process, named 4D variational data assimilation, takes into account the physics known to be involved in the system.
-As an example weather station data which take measurements such as wind speed, humidity, and temperature of the immediate surroundings of the weather station is very limited in giving a broader picture of weather over a larger area.
-Even technologies like earth observations satellites are limited to what they can observe at any single point in time as most cannot see the entirety of the earth's surface at once.
-The ERA5 dataset specifically, assimilates previous forecasts with observational data every 12 hours.
-The ERA5 reanalysis is available at the following URL (\url{https://cds.climate.copernicus.eu/datasets/reanalysis-era5-single-levels}).
-
-The original dataset made available by ECMWF has a grid size of \ang{0.25} by \ang{0.25} in latitude and longitude for atmospheric data.
-Data of oceanic waves are also available at a coarser grid size of \ang{0.5} by \ang{0.5}.
-However, we will use a cloud optimized version called WeatherBench2 that is easier to retrieve \autocite{raspWeatherBench2Benchmark2023}.
-This is because the data is available in several more grid sizes such as \ang{1.5}.
-In addition, the data can be readily downloaded to a local machine without waiting for further processing on the server.
-The guide for working with the dataset is available at (\url{https://weatherbench2.readthedocs.io/en/latest/data-guide.html}).
-In our specific case, we use the version labeled \verb|1959-2023_01_10-6h-64x32_equiangular_conservative.zarr|.
-This dataset spans from year 1959 to 2023 with a grid size of \ang{5.625} or resolution of 64 by 32 which spans from \ang{-87.19} to \ang{87.19} in latitude and \ang{0.0} to \ang{354.4} in longitude.
-The dataset is also resampled down to 6-hour intervals that starts at midnight UTC January 1959 1\textsuperscript{st} and ends at 18:00 UTC January 10\textsuperscript{th} 2023.
-
-While the original data provided by ECMWF is available in NetCDF or GRIB, the WeatherBench2 version is provided using the Zarr format in a Google Cloud Storage Bucket.
-This setup allows the use of libraries that support the Zarr format to access the dataset remotely.
-The particular library we use is called \emph{Xarray} version \verb|2024.9.0| \autocite{hoyer2017xarray,hoyerXarray2024}.
-Accessing the remote dataset is done as shown in \lccref{fig:access_remote_zarr}.
-In order to ensure access is granted, the storage option token is set to anon so that the method uses the anonymous only public access mode of authentication \autocite{GCSFSGCSFs2023122post1+1g8e500c6dirty}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-  import xarray as xr
-  ds = xr.open_zarr(
-      "DATASET_ADDRESS",
-      storage_options = {"token": "anon"},
-  )
-  \end{lstlisting}
-  \caption{Example of using Xarray to access a publicly accessible Zarr dataset hosted on Google Cloud Storage Bucket.}\label{fig:access_remote_zarr}
-\end{figure}
-
-The specific dataset resolution we use is 64 by 32 representing longitude and latitude respectively.
-The ERA5 reanalysis dataset is hosted at the following URL\@: \url{gs://weatherbench2/datasets/era5/1959-2023_01_10-6h-64x32_equiangular_conservative.zarr}.
-The corresponding climatology is hosted at \url{gs://weatherbench2/datasets/era5-hourly-climatology/1990-2019_6h_64x32_equiangular_conservative.zarr}.
-The climatology is the average for hours 0, 6, 12, and 18 for each day of the year from 1990 until 2019.
-This average helps in defining the expected state of the weather at specific points in time based on the historical averages for that time of day and year.
-
-For the reanalysis dataset, we limit the time range to the years 1995{-}2013 for training and 2020{-}2022 for testing.
-The specific time ranges for training are chosen to balance the diversity within the data and capacity of the machine the processing will be done on.
-The testing set time range was chosen to be as close to those shown on the WeatherBench 2 website.
-The filter for time and variables is shown in \lccref{fig:wb2_retrieval}.
-The reason for the different time ranges between training and testing is to reduce the risk of information leakage accross the training and testing sets.
-This ensures that the testing scores we measure will be for the most part from the generalization that model learned during training.
-The filter is an array the length of the number of samples.
-The array values are all the datetime values that the year ranges are true for.
-This results in an array of boolean values.
-Using this boolean filter we can index the data so that we get the filtered data.
-Then, the filtered data is saved locally so that we can access it in a more performant way.
-The encoding chunks may need to be removed in order to evade the Xarray library from mistakenly persisting the remote encoding after slicing data \autocite{ianZarrEncodingAttributes}.
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-  years_idx = ds['time.year']
-  data_idx = (years_idx > START_YEAR) & (years_idx < END_YEAR)
-  da_orig = ds['2m_temperature'][data_idx]
-  # save locally
-  da_orig.encoding.pop('chunks',None)
-  da_orig.to_zarr(DATA_FILENAME, mode='w')
-  # open local version
-  da = xr.open_zarr(DATA_FILENAME)
-  \end{lstlisting}
-  \caption{Example of filtering of Xarray dataset by year and variable. The data is saved and then loaded locally.}\label{fig:wb2_retrieval}
-\end{figure}
-
-The dataset includes 62 variables with some variables also spanning 13 discrete vertical levels in the atmosphere.
-For our use, we will only be using the 2-meter temperature of the atmosphere.
-This is the air temperature 2 meters above the surface be it land, sea, or inland water.
-This variable is in units of kelvin (K).
-Vertically, the values of this variable is obtained by interpolating between the model values at the surface and the lowest model vertical level.
-An example of the data that was retrieved can be seen in \lccref{fig:wb2_data}.
-The data shown is in the equiangular projection.
-This means that towards the poles, the shapes become more distorted.
-While this is not the most ideal way to represent the data, using the data in this way adds to the challenge of how the model can adapt to the use of suboptimal configurations in the data.
-To compute the anomaly, we can simply subtract the current state in \lccref{fig:wb2_train_data} by the climatology in \lccref{fig:wb2_clim_data} resulting in \lccref{fig:wb2_train_anomaly}.
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_train_data.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:wb2_train_data}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_clim_data.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:wb2_clim_data}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_train_anomaly.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:wb2_train_anomaly}
-  \end{subfigure}
-  \caption{Data retrieved:(\subref{fig:wb2_train_data}) 2-meter temperature at January 1, 1995 6:00 UTC\@.
-(\subref{fig:wb2_train_anomaly}) Anomaly for 2-meter temperature at January 1, 1995 6:00 UTC\@.
-(\subref{fig:wb2_clim_data}) 2-meter temperature climatology for the first day of the year at hour 6 UTC\@.}\label{fig:wb2_data}
-\end{figure}
-
-After filtering, our training set has the dimensions of 27760 time steps, 64 longitude, and 32 latitude.
-The testing set on the other hand has 4384 time steps and the same values for the other two dimensions.
-For uses, such as a validation set during hyperparameter optimization, one can use a subset of the training set.
-The dimensions of the climatology are 4 for hour (0, 6, 12,\& 18), 366 for day of year, 64 for longitude, and 32 for latitude.
-
-\section{Design of Computational Model}\label{sec:computational_model_design}
-\noindent In this section, we will discuss the design of the computational model that is proposed in this work. An illustration of the computational model is show in \lccref{fig:computational_model}.
-
-\begin{figure}[H]
-  \centering
-  \begin{adjustbox}{max width=\textwidth}
-    \tikzfig{figures/computational_model}
-  \end{adjustbox}
-  \caption{Computational Model of SpectralSVR.}\label{fig:computational_model}
-\end{figure}
-
-The computational model is divided into four large phases.
-The processes within these phases are based on the broad outcomes of the phase.
-The phases themselves are data preparation, data transformation, model training, and model evaluation.
-Each phase is composed of processes that together works toward the output of the larger process.
-At the end, a final process of analysis and interpretation is carried out.
-
-\subsection{Data Preparation}
-\noindent The data preparation phase starts off the computation by preparing the data that is to be used in this study.
-This phase starts with specifying the problem to be solved.
-This translates to the dataset that will be used to represent these problems.
-The first type of dataset is generated based on a known governing equation or PDE\@.
-Using said equation, the goal is to generate pairs of functions that are related to each other by the equation.
-In the next process, generally, the solution function is first generated randomly.
-This is done by generating random numbers to use as coefficients of a set of basis functions.
-Then parameters of the equation is determined, such as term coefficients.
-Using the generated solution and predetermined parameters, a forcing term can generally be computed to satisfy the equation.
-Augmentations such as noise can then be added in the final process which is evaluating the function values.
-These processes result in a generated dataset.
-To verify the generation method and any models trained on the generated data one can use exact analytical solutions of the governing equations.
-
-The second type of dataset is retrieved from an external source.
-The data source is first identified, in our case it is the WeatherBench 2 collection of datasets.
-The specific dataset from the collection of different dataset versions is first determined.
-The dataset is available in the \emph{Zarr} format.
-And then, we determine the filters for the portions of the dataset we are interested in.
-Once the dataset and filters are determined, the retrieval process starts by accessing the dataset using the \emph{Xarray} library \autocite{hoyer2017xarray,hoyerXarray2024}.
-The filters are applied as in \lccref{fig:wb2_retrieval}.
-Finally, the filtered version is stored locally.
-The local dataset is also stored in the \emph{Zarr} format.
-
-\subsection{Data Transformation}\label{sec:data_transformation}
-\noindent The second phase of the computational model transforms the data that has been prepared into a form that can be used with the proposed model.
-In this study, there are two ways a dataset can be used.
-The first and simplest way is to predict the solution function from the forcing term for a given set of PDE parameters.
-In this case, the input function is the forcing term.
-In other words, the input function is the predictor or independent variable that will be used to predict the solution function.
-As such, the output function is the solution function.
-The antiderivative dataset is used in this way.
-The derivative, which represents the acceleration function, is used to predict the velocity function.
-Which means that the input function is the acceleration function and the output function is the velocity function.
-
-The second use of a dataset depends on whether it can be interpreted as a mapping of a previous function to the next function.
-In other words, a series of functions related to the previous function as a sum of the previous function and a perturbation.
-A commonly used form of this are time series.
-Generally, a time series can be represented as \lccref{eq:time_step_function}.
-This function describes the evolution of function \(f\) as a sum of some initial state \(f^0\) and perturbation which is its rate of change \(\dv{f}{t}\) at a point in time close to the current time multiplied by the time step \(\delta t\).
-This is the first order Taylor polynomial.
-Adding more terms with higher order derivatives can be done to increase the accuracy.
-This describes the same process that is used in the finite difference method.
-\begin{equation}
-  f^{t+1} = f^{t} + \delta t \times \dv{f}{t} + \dots \label{eq:time_step_function}
-\end{equation}
-In this case the previous function and any other independent variables like the forcing term involved in the right-hand side of the equation is used to predict the difference between the future state and the current state.
-It would mean that each sample function in the data would need to at least have two dimensions.
-This is because one dimension represents the evolution of the function over time, while the other dimensions define the spatial domain where the function's values are computed at each time step.
-This condition is true for both the Burgers' equation dataset and the WeatherBench 2 collection of ERA5 datasets.
-First, the Burgers' equation dataset, while is also able to be used in the first way as a mapping between the forcing term and the solution, one of the traditional ways of solving it is using the method of lines.
-This entails solving the dimensions other that time with methods such as the finite differences method or the spectral method.
-The time dimension is then separately solved using the finite differences method such as the form shown in \lccref{eq:time_step_function} \autocite{schiesserNumericalMethodLines2012,sadikuSimpleIntroductionMethod2000}.
-This is the form that the Burgers' equation dataset will be used in.
-In this case, algebraic manipulation of \lccref{eq:forced_viscous_burgers} results in the time derivative of the solution as in \lccref{eq:forced_viscous_burgers_time_derivative}.
-\begin{align}
-  \pdv{u}{t} = f - u\pdv{u}{x} + \nu\pdv[2]{u}{x} \label{eq:forced_viscous_burgers_time_derivative}
-\end{align}
-The most important component of the right-hand side of the equation, the time derivative, is expressed in terms of the solution function, the forcing term and any other partial derivatives.
-Because of this, it means we can train the model to learn the relationship between the solution function combined with the forcing term and the time derivative.
-Putting this together with \lccref{eq:time_step_function}, it is possible to predict the solution function in a future time based on the current solution function and forcing term.
-The input functions in this case are both the value of the solution function and the forcing term at the current time step.
-The output function is the time derivative which is computed by rearranging \lccref{eq:time_step_function} resulting in \lccref{eq:time_derivative_time_step_function}.
-\begin{equation}
-  \dv{f}{t} = \frac{f^{t+1} - f^{t}}{\delta t} \label{eq:time_derivative_time_step_function}
-\end{equation}
-Perhaps in a more obvious manner, the same is also applied to the WeatherBench 2 collection of ERA5 datasets.
-The 2-meter temperature is a series of snapshots in time of the distribution of temperature all over the world at 2 meters above the surface.
-The input function in this case is the temperature distribution at the current time step.
-The output function is the time derivative of the temperature distribution computed using \lccref{eq:time_derivative_time_step_function}.
-
-The input and output functions are then transformed into basis coefficients using the Fourier transform. % TODO: add reference to fourier transform in chapter 2
-Once the coefficients are computed, the input and output sample pairs are split into train, test, and validation subsets.
-For the first type of input and output function pair, since the samples are independent of each other, a random sampling of the dataset without replacement is done to select the samples for each subset.
-For the second type of input and output function pairs, if there are multiple samples of functions as in the Burgers' equation dataset, the same process with random sampling is followed.
-On the other hand, if only one function sample is available, such as the WeatherBench 2 dataset, an issue that arises is the fact that the samples are dependent on one another.
-This is because a previous time step influences the next time step.
-This is a problem for generalizing the learned model, since random sampling would lead to the model learning information in the future of the testing subset \autocite{kapoorLeakageReproducibilityCrisis2023,kaufmanLeakageDataMining2012}.
-As such, the portioning of the dataset is done by dividing the sample into different sections of the function in time.
-
-Finally, the data is scaled.
-This is done because of how support vector machines require scaling for inputs in order to perform well with certain hyperparameters such as the RBF kernel \autocite{ben-hurUsersGuideSupport2010}.
-For our case we use standard scaling based on the inputs of the training subset.
-This approach transforms the dataset by manipulating the distribution characteristics of the dataset \autocite{ahsanEffectDataScaling2021}.
-Specifically, the standard deviation \(\sigma \) and mean \(x_0\) of the dataset values \(x\) are processed such that the resulting values have a mean of 0 and standard deviation of 1.
-The function shown in \lccref{eq:standard_scaler} represents how each sample is processed with respect to the standard deviation \(\sigma \) and mean \(x_0\) of each feature.
-\begin{equation}
-  z(x;\sigma,x_0)=\frac{x-x_0}{\sigma} \label{eq:standard_scaler}
-\end{equation}
-The scaling is important for the RBF kernel specifically due to the fact that the kernel utilize a scale parameter.
-This parameter affects how scale of values influence the kernel.
-Another and perhaps more general benefit of scaling is the uniformity it enforces across features.
-This is useful because all feature weigh the outcome equally.
-In our use case, this equality is a reflection of what the data actually represents.
-Each feature which is a discretized value or its coefficient representation has equal value to any other feature.
-No point or coefficient is any more or less value compared to another point or coefficient.
-
-The scaling is applied to input functions only because scaling of the outputs does not affect the performance of the model \autocite{ben-hurUsersGuideSupport2010}.
-To also prevent information leakage across training and testing sets, the mean and standard deviation of each feature is computed using the training subset only.
-Once the parameter values are obtained, all input function samples in the dataset are transformed into their scaled versions.
-This means that the distribution for the testing and validation sets may be outside the target standard deviation and mean.
-% TODO: add graphs and tables of the resulting preprocessed data
-
-\subsection{Model Training}
-\noindent Once the data has been preprocessed, the model is trained using pairs of training features and labels.
-The training phase is separated into four processes.
-First, the preprocessed input and output function representation need to be real numbers.
-This is because the LSSVR model was made to work with real numbers.
-Any complex values such as Fourier coefficients are represented as flattened pairs of the real and imaginary components of complex values.
-% TODO: add figure of flattened complex values
-
-The training can proceed to solve \lccref{eq:lssvr_solution}.
-As the original LSSVR equation was made for regression of a single value of \(\vb{y} \), we constructed an extended the original equation in order to train multiple regression models to predict each coefficient in an output function sample.
-The assumption of this extension is that the inputs and model hyperparameters such as kernels and the regularization constant \(C \) are the same across individual regressors.
-Therefore, it follows that the solution vector and target vector can both be transformed into their matrix form with each column representing the individual regressor which results in \lccref{eq:lssvr_solution_vectorized}.
-This vectorized version is equal to \(m \) separate instances of \lccref{eq:lssvr_solution}.
-In essence, instead of a vector of scalar sample output values and a vector of model parameters, the extended equation consists of a matrix of rows of vector output values and a matrix of model parameters with each column representing the separate model for each output and row representing the Lagrange multipliers for each sample.
-The procedure to solve \lccref{eq:lssvr_solution_vectorized} adjusts \lccref{alg:lssvr_training} for the extra dimension spanning the multiple outputs of size \(m\).
-\begin{equation} \label{eq:lssvr_solution_vectorized}
-  \begin{bmatrix}
-    0          & \vb{1}_{n}^{\intercal} \\
-    \vb{1}_{n} & \Omega + \frac{I}{C}
-  \end{bmatrix}
-  \begin{bmatrix}
-    b_0           & \cdots & b_m           \\
-    \vb{\alpha}_0 & \cdots & \vb{\alpha}_m \\
-  \end{bmatrix}
-  =
-  \begin{bmatrix}
-    0        & \cdots & 0        \\
-    \vb{y}_0 & \cdots & \vb{y}_m \\
-  \end{bmatrix}
-\end{equation}
-
-Second, as the training process of an LSSVR described in requires constructing the first matrix on the left-hand side and the matrix on the right-hand side, each component of the matrices themselves will also need to be constructed.
-The kernel matrix \(\Omega \) is first constructed by computing the kernel values between each sample input with every other sample input.
-If the training set has \(n \) samples, then the resulting kernel matrix would be of size \(n \) by \(n \).
-% Assemble lssvr optimality equation matrices
-Third, using the inputs \(\vb{X}\), outputs \(\vb{y}\), predetermined regularization constant \(C \), and the obtained kernel matrix \(\Omega \), \lccref{eq:lssvr_solution_vectorized} is assembled.
-Finally, the matrix of learned parameters \(\vb{\alpha}\) and \(\vb{b}\), which are the Lagrange multipliers and bias respectively, are solved for using a linear equation solver such as a matrix Moore-Penrose inverse or linear least squares solver.
-
-For our study, we choose to not optimize the hyperparameters to focus on the broad performance with default hyperparameter values.
-The scaling parameter of the RBF kernel is computed from the training features.
-This is computed as the square root of the sum of feature variances.
-The regularization parameter used will be a default value of 1.
-Using the same values allow for easier comparisons for comparable results.
-
-\subsection{Model Evaluation}
-\noindent The fourth phase of the computational model is the evaluation of the learned model.
-This phase starts with formatting the inputs.
-If the inputs aren't scaled yet, then it is scaled using the scaling function fitted on the training set.
-This is the case for new data such as new measurements or an analytical solution of the learned PDE\@.
-Once the inputs that is to be evaluated is scaled in the same way as the training inputs, the model can predict the corresponding outputs.
-
-The procedure to compute the predicted outputs follows \lccref{alg:lssvr_prediction}.
-This leads to the second process which is computing the kernel matrix between the training input features \(\vb{X}\) and the evaluation input features \(\vb{U}\).
-The matrix is constructed as the kernel value between each evaluation sample feature and every training sample feature.
-For \(p \) evaluation samples and \(n \) training samples, this results in a kernel matrix \(\Omega \) with a shape of \(p \) rows and \(n \) columns.
-
-In the third process, the constructed kernel matrix is then multiplied with the matrix of learned Lagrange multipliers \(\vb{\alpha}\).
-The multiplication is the matrix multiplication process.
-Then, the bias vector is added to each row to produce the final predicted outputs \(\vb{v}\).
-This process is represented by \lccref{eq:lssvr_prediction_vectorized}.
-\begin{equation}
-  \vb{v} = \Omega\vb{\alpha}+\vb{1}\vb{b} \label{eq:lssvr_prediction_vectorized}
-\end{equation}
-
-The fourth process is concerned with the fact that the predicted output \(\vb{v}\) is a matrix of real numbers.
-The LSSVR output needs to be formatted before it can be used in the proposed model.
-This is done by converting the outputs into the same format as the training labels.
-As we use the Fourier basis, the model output is converted back into a matrix of complex numbers using the inverse of the first process during training.
-Finally, these predicted Fourier basis coefficients can be used to evaluate the predicted functions themselves.
-
-\section{Implementation of Computational Model}
-\noindent This section discusses the implementation of modeling and approximation of PDEs using LSSVR\@.
-Using the computational model design in \lccref{sec:computational_model_design}, the computational model is implemented as a library using the Python programming language.
-The development process itself is based on the iterative development model as mentioned in \lccref{sec:development method}.
-In this section, the output iterative processes are consolidated and explained together.
-
-\subsection{Analysis}
-\noindent The aim of any program that is developed in this study is to model the relationship between functions defined by a partial differential equation or other operators and governing equations.
-Since the potential subject of modeling can be wide-ranging, the software product that will be developed is a library.
-This is done so that the tools and proposed model that is developed will be able to be used with a variety of PDEs.
-With this in mind, the software must also be performant and compatible with the larger machine learning and scientific computing community.
-
-To demonstrate the use and capability of the software, three case studies are chosen to represent the variety of PDEs.
-The first case study is the antiderivative equation.
-This simple case is chosen as a proof of concept to show that the proposed model works in the most simple case.
-The second case study, which is the Burgers' equation, adds a level of complexity because of the nonlinearity involved with the solution function.
-The third case study, which is the ERA5 weather dataset, was chosen to show how the model performs on data with real world observations incorporated into it.
-This dataset also presents a challenge because of the uncertainties involved with weather simulation \autocite{herreraReviewCurrentFuture2017}.
-These datasets are discussed in \lccrefs{sec:data_generation,sec:data_retrieval}.
-
-In addition, the software product is developed within certain limitations. The limitations are:
-\begin{enumerate}
-  \item The operating and implementation language of the library is Python.
-  \item The library is to be used in user code
-  \item The library depends on other libraries including the following core dependencies PyTorch, NumPy, Xarray, Zarr, Pandas, and tqdm.
-\end{enumerate}
-
-\subsection{Design}\label{sec:implementation_design}
-\noindent In this subsection, the architectural design of the software product is explained.
-The architecture consists of modules with similar concerns.
-This was chosen because of the intuition built by the use of other libraries with a similar architecture.
-The broad aim of modeling PDEs with LSSVR and basis functions coefficients can be separated into smaller concerns of data, model, and basis functions.
-Each of these concerns are addressed by a corresponding module.
-The explanation of each module are as follows:
-\begin{enumerate}
-  \item Utilities
-
-        \noindent This module provides basic tools that are used across the entire library.
-The utilities this module needs to provide include scaling, conversion between real and complex representations of matrices, resizing coefficient tensors, and adaptors for or the traditional ordinary differential equation solvers.
-Scaling functionality is used for inputs into the support vector machines.
-And as previously mentioned, since LSSVR only works with real numbers, the tools for converting between complex and their real number representations is also necessary.
-Another useful tool for working with basis coefficients is a way to resize the coefficients in terms of how many basis functions is desired.
-An example of the usage is downsizing Fourier coefficients from 12 to 8 modes.
-The last utility mentioned here provides the ability to solve ordinary differential equations.
-This utility is useful for generating data for certain types of PDEs such as the Burgers' equation.
-
-  \item Basis Functions
-
-        \noindent As the proposed model will learn the relationships defined by PDEs within the spectral domain, a large proportion of the computation will also concern the use of the basis functions themselves.
-The module will define the functionality and data structure that is expected to be used when working with basis functions in this library.
-First and foremost, the central function of this module is to store and facilitate the connection between the coefficients in the spectral domain and their values in the physical domain.
-This is dependent on the basis functions used.
-For the Fourier basis that we use in this study, this means that the transformations are the discrete Fourier transform and the discrete inverse Fourier transform.
-Other than this core functionality, information on the characteristics of the coefficients such as the number of modes, in other words basis functions, should also be provided by this module.
-In addition, other functionality included in this module are visualization of coefficients in physical space, generation of random functions, time dependent \& complex/real coefficients, noise perturbation of functions, and differential operators.
-
-  \item Model
-
-        \noindent The proposed SpectralSVR model is implemented in this module.
-As the proposed model essentially wraps a support vector regression model in such a way that it can process coefficients, this module will house the SpectralSVR wrapper itself and the LSSVR variant of support vector regression that is used in this study.
-The SpectralSVR wrapper must provide three core pieces of functionality.
-First, it must translate complex input and output samples into their real representations.
-This applies to both training and evaluation.
-Second, in addition to predicting the coefficients during evaluation, the wrapper should also be able to predict the function values themselves for any given set of point coordinates.
-This is important for quick evaluations of a predicted function at an arbitrary point.
-The third functionality is inverse input function search for a given output.
-This is useful for inverse problems where the parameters are unknown, but the solution is partially known.
-Aside from the core functionality, a complementary functionality is testing for the learned model.
-
-        The model module also implements the LSSVR model.
-This implementation provides two main functionalities.
-The first is training the LSSVR model with some given model hyperparameters such as the regularization constant and kernel.
-The second functionality is the evaluation of the learned model.
-Both functionalities allow for multiple output regression.
-This is required to learn the mappings for many coefficients at once.
-Other functionality provided by the implementation include interpretability functions and model serialization for saving and loading the learned model to disk.
-
-  \item Problems
-
-        \noindent This module provides the functionality concerned with generating data.
-Two out of the three datasets in this study are generated with this module.
-In general this module provides two pieces of functionality.
-The first is generation of the data itself.
-This functionality generates at least two sets of functions that are related to each other by the chosen PDE\@.
-The generation is based on at least two parameters which are the number of samples to generate and the number of modes or basis functions to generate the coefficients for.
-The second functionality provided by this module is the residual based on the chosen PDE\@.
-This is useful to verify if any set of functions comply with the PDE\@.
-For example, the residual may be used to verify the generated data.
-Another use is to grade the predictions by the learned model.
-
-\end{enumerate}
-
-The design presented here is the product of multiple iterations that started with building the core model and then the basis functions and finally the data.
-Throughout the iterations, the utilities were also added to alleviate the need for general tools.
-
-\subsection{Implementation}
-
-\noindent The design in \lccref{sec:implementation_design} is implemented within the same iterative loop.
-As such, the feedback from tests is immediate, and any fixes can be implemented quickly.
-The implementation is done using the Python language and a number of Python libraries.
-To facilitate the management of dependencies, the implementation makes use of the package management tool Poetry \autocite{eustacePoetryPythonPackaging2024}.
-In addition, the Python version is managed using the tool PyEnv.
-The implementation process starts with installation of the required dependencies.
-The dependencies are specified in the \verb|pyproject.toml| as shown in \lccref{fig:poetry_add_deps}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Toml]
-...
-[tool.poetry.dependencies]
-python = "^3.10.6"
-numpy = "^1.24.0"
-tqdm = "^4.65.0"
-jaxtyping = "^0.2.20"
-pandas = "^2.2.2"
-torchmetrics = "^1.4.2"
-scikit-learn = "^1.5.0"
-matplotlib = "^3.9.0"
-torch = {version = "^2.4.1+cu124", source = "pytorch-gpu"}
-torchvision = {version = "^0.19.1+cu124", source = "pytorch-gpu"}
-torchaudio = {version = "^2.4.1+cu124", source = "pytorch-gpu"}
-ray = {extras = ["tune"], version = "^2.37.0"}
-hyperopt = "^0.2.7"
-ipywidgets = "^8.1.5"
-torchdiffeq = "^0.2.4"
-xarray = "^2024.10.0"
-zarr = "^2.18.3"
-gcsfs = "^2024.10.0"
-
-[[tool.poetry.source]]
-name = "pytorch-gpu"
-url = "https://download.pytorch.org/whl/cu124"
-priority = "explicit"
-
-[build-system]
-requires = ["poetry-core"]
-build-backend = "poetry.core.masonry.api"
-  \end{lstlisting}
-  \caption{Contents of pyproject.toml configuration file that define the dependencies using Poetry.}\label{fig:poetry_add_deps}
-\end{figure}
-
-After ensuring that the correct version of python is being used with pyenv, the dependencies specified in the \verb|pyproject.toml| file can be installed using the shell command \verb|poetry install|.
-At the end of each iteration, the dependencies are subject to change depending on whether any new ones are needed or old dependencies can be removed.
-
-In the following, we will discuss the implementation of each module and how the phases of computational model relates to each implemented functionality.
-The base data structure that is used in the implementation is the PyTorch Tensor \autocite{Ansel_PyTorch_2_Faster_2024}.
-Tensors are a generalization of scalars and array-like structures such as vectors and matrices.
-This is essential since many computations that is done in the proposed model are based on matrices and higher dimensional arrays.
-PyTorch Tensors allow the elements to be of different data types such as floating point numbers of different precision or even complex numbers.
-In addition to basic operations for working with the Tensors such as matrix multiplications, PyTorch also provides many algorithms for use when working with Tensors such as linear equation solvers or the Fast Fourier Transform.
-Another reason for choosing to use PyTorch is the ability to parallelize computation using specialized processors such as GPUs.
-Lastly, PyTorch is widely used in the machine learning community which reflects on its reliability, wealth of community knowledge and support, and active development.
-
-\subsubsection{Utilities}
-
-\noindent The utilities module provide common tools that are used when working with the developed software.
-First, because the basis function used in this study is the Fourier basis, a large proportion of concern is the storage of Fourier basis coefficients.
-The Fourier series representation that is used in this study is the complex representation as show in \lccref{eq:fourier_series}.
-However, as previously mentioned, least squares support vector machines is constructed to work with real numbers.
-In order for LSSVR to learn the relationship between complex numbers, a representation of complex numbers in terms of real numbers is necessary.
-Since sample features and labels for LSSVR need to be flattened into one dimension which result in a matrix with rows of samples, the representation of complex numbers using real numbers can be done after features and labels have been flattened.
-An example of such a matrix of two samples with four features each can be seen in \lccref{eq:complex_matrix}.
-To represent the complex number features as real numbers, once can simply split a single complex number into two real numbers.
-When this is done to the entire matrix of complex numbers, the result is \lccref{eq:complex_matrix_real_rep}.
-\begin{align}
-  \begin{bmatrix}
-    -1.03+0i & -0.52+0.39i & -0.54+0i & -0.52-0.39i \\
-    -0.85+0i & -0.39+0.19i & 0.87+0i  & -0.39-0.19i
-  \end{bmatrix}\label{eq:complex_matrix} \\
-  \begin{bmatrix}
-    -1.03 & 0 & -0.52 & 0.39 & -0.54 & 0 & -0.52 & -0.39 \\
-    -0.85 & 0 & -0.39 & 0.19 & 0.87  & 0 & -0.39 & -0.19
-  \end{bmatrix}\label{eq:complex_matrix_real_rep}
-\end{align}
-There are several ways to do this in PyTorch, such as extracting the real and imaginary element components into separate matrices and then interleaving the columns to create the real representation.
-However, a more performant version can be made by using built-in functions of the library that directly allows views of complex valued tensors as real tensors and vice versa.
-The \verb|view_as_real| and \verb|view_as_complex| functions allow the conversion between real and complex representations by representing complex valued tensors by adding a dimension of size two for each component of complex numbers.
-The resulting implementation can be seen in \lccref{fig:complex_matrix_conversion_implementation}.
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-def to_real_coeff(x: torch.Tensor) -> torch.Tensor:
-    return torch.view_as_real(x).flatten(-2)
-
-def to_complex_coeff(x: torch.Tensor) -> torch.Tensor:
-  return torch.view_as_complex(
-    x.reshape((*x.shape[:-1], -1, 2))
-  )
-  \end{lstlisting}
-  \caption{Utility function to convert between complex matrices and the real representations.}\label{fig:complex_matrix_conversion_implementation}
-\end{figure}
-
-Another important utility used on inputs for the proposed SpectralSVR is a scaling function.
-This utility has been implemented in a variety of ways and using different tools.
-However, as the standard scaling is not provided by PyTorch, we have also implemented our own version.
-The scaling function accepts PyTorch tensors or tuples of tensors of real or complex elements.
-First, the scaling function is implemented as a class that is instantiated.
-The scaling function is then fitted onto the reference data to obtain the standard deviation and mean of each feature.
-This information is stored as properties of the class.
-Any complex tensors are converted into their real representations using the functions in \lccref{fig:complex_matrix_conversion_implementation}.
-Once the scaling function instance is fitted, any set of tensors with the same number of features (columns) and element type (complex or real) can be roughly transformed into a standard deviation of one and mean of zero for every feature.
-This is done by subtracting the fitted mean of each feature from the elements in the column and then dividing with the feature's standard deviation.
-The implementation also provides a method to retrieve a scaling function fitted on a subset of the original tuple of tensors.
-Serialization for saving to and loading from disk is also implemented.
-This is done simply by using the PyTorch save and load functions on the scaling function instance itself.
-For some use cases, an inverse scaling operation to the original standard deviation and mean is also essential.
-The implementation is simply the reverse of the transformation process where the elements are multiplied by the standard deviation and the mean is the added.
-
-Another group of utility in the module is concerned with managing the number of modes a tensor of coefficients has.
-First, a function called \verb|resize_modes| accepts a tensor of coefficients and the target number of modes in each dimension.
-The first dimension is always assumed to represent the different samples.
-Because of this the target modes will only affect the dimensions after the first.
-The wave numbers are also assumed to be symmetric about zero such that the highest absolute values of the wave number is in the middle of each dimension.
-The wave number decreases symmetrically as you move towards the edges of the dimension and reaching the lowest absolute wave number at the edges.
-This is done to ensure compatibility with the way existing libraries such as PyTorch works with tensors of Fourier coefficients.
-Because of this, shrinking a tensor of coefficients along a dimension means removing the center of the tensor along that dimension.
-And expanding to a target number of modes that is larger means that the tensor is padded with zeros in the center along the desired dimension.
-In addition, the remaining coefficients may be rescaled in order to balance the effect of adding or removing coefficients.
-The implementation is presented in \lccrefs{fig:coefficient_shrink_impl,fig:coefficient_expand_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-for dim, (target_mode, current_mode) in enumerate(
-    zip(target_modes, current_modes), 1
-):
-    device = x.device
-    start_range = torch.tensor(
-        range((target_mode - 1) // 2 + 1), dtype=torch.int
-    ).to(device=device)
-    end_range = torch.tensor(
-        range(current_mode - target_mode // 2,
-          current_mode
-        ),
-        dtype=torch.int,
-    ).to(device=device)
-
-    x_resized = torch.concat(
-        (
-            x_resized.index_select(dim, start_range),
-            x_resized.index_select(dim, end_range),
-        ),
-        dim,
-    )
-  \end{lstlisting}
-  \caption{Example of shrinking a tensor of samples' coefficients to a target number of modes.}\label{fig:coefficient_shrink_impl}
-\end{figure}
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-for dim, (target_mode, current_mode) in enumerate(
-    zip(target_modes, current_modes), 1
-):
-    device = x.device
-    start_range = torch.tensor(
-        range((current_mode - 1) // 2 + 1), dtype=torch.int
-    ).to(device=device)
-    # make sure that end range is empty if
-    # the coefficient is only size 1
-    end_range = torch.tensor(
-        range(current_mode // 2, current_mode)
-        if current_mode > 1
-        else range(0),
-        dtype=torch.int,
-    ).to(device=device)
-    padding_size = target_mode - current_mode
-    modes = list(x_resized.shape)
-    modes[dim] = padding_size
-    padding = torch.zeros(modes).to(x_resized)
-
-    x_resized = torch.concat(
-        (
-            x_resized.index_select(dim, start_range),
-            padding,
-            x_resized.index_select(dim, end_range),
-        ),
-        dim,
-    )
-  \end{lstlisting}
-  \caption{Example of expanding a tensor of samples' coefficients to a target number of modes.}\label{fig:coefficient_expand_impl}
-\end{figure}
-Next, the second way to manage the size of a tensor along a dimension is to interpolate the current values.
-The implementation uses simple linear interpolation.
-This is especially useful for situations such as coefficients that are themselves functions of time.
-This is a common application such as when solving the initial condition problem of a function in space and time.
-One might represent the function as a Fourier series with basis as functions of space and coefficients as functions of time.
-In this case, the coefficients for time values that are not available can be interpolated.
-The implementation of this is shown in \lccref{fig:coefficient_interpolation_impl}.
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-    index_floor = index_float.floor().to(torch.int)
-    index_ceil = index_float.ceil().to(torch.int)
-    x_ceil = x.index_select(dim, index_ceil)
-    x_floor = x.index_select(dim, index_floor)
-    # interpolate coefficients
-    index_shape = [1 for _ in range(x_floor.ndim)]
-    index_shape[1] = -1
-    index_scaler = (
-        ((index_float - index_floor) / (
-          index_ceil - index_floor
-        ))
-        .reshape(index_shape)
-        .nan_to_num()
-    )
-    # ynt + scaler * (ynt1 - ynt)
-    # (1 - scaler) * ynt + scaler * ynt1
-    x_interp = torch.lerp(x_floor, x_ceil, index_scaler.to(x))
-  \end{lstlisting}
-  \caption{Example of interpolating for indices (floating point indices) between the available ones (integer indices).}\label{fig:coefficient_interpolation_impl}
-\end{figure}
-
-Finally, this module also provides the types and reexports implementations of ordinary differential equation solvers from the torchdiffeq library \autocite{Chen_torchdiffeq_2021}.
-The implementation can be seen in \lccref{fig:solver_impl}.
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-RHSFuncType = Callable[[torch.Tensor, torch.Tensor],
-  torch.Tensor
-]
-SolverSignatureType = Callable[[
-        RHSFuncType, torch.Tensor, torch.Tensor,
-    ],
-    torch.Tensor
-]
-MixedRHSFuncType = Callable[[
-        torch.Tensor, torch.Tensor, torch.Tensor,
-    ],
-    torch.Tensor,
-]
-MixedSolverSignatureType = Callable[
-    [MixedRHSFuncType, torch.Tensor, torch.Tensor],
-    torch.Tensor,
-]
-
-def euler_solver(
-    rhs_func: RHSFuncType,
-    y0: torch.Tensor,
-    t: torch.Tensor,
-):
-    solution = torch.zeros((len(t), *y0.shape)).to(y0)
-
-    j = 1
-    solution[j - 1] = y0
-    for t0, t1 in zip(t[:-1], t[1:]):
-        dt = t1 - t0
-        y = solution[j - 1]
-        solution[j] = y + dt * rhs_func(t0, y)
-        assert (
-            solution.isnan().sum() == 0
-        ), f"solver encountered nan at timestep {j} (t={t0})"
-        j = j + 1
-    return solution
-
-implicit_adams_solver: SolverSignatureType = partial(
-    odeint, method="implicit_adams", options={"max_iters": 4}
-)  # type: ignore
-
-lsoda_solver: SolverSignatureType = partial(
-    odeint, method="scipy_solver", options={"solver": "LSODA"}
-)  # type: ignore
-  \end{lstlisting}
-  \caption{Implementation of ODE solvers and the types.}\label{fig:solver_impl}
-\end{figure}
-
-\subsubsection{Basis Functions}
-
-\noindent This module implements two classes.
-The first is the base Basis class.
-The second is a subclass implementing the Fourier basis specifically.
-These classes provide the functionality needed to have an easier time when working with basis functions and their coefficients.
-First, the core function of these classes is to provide a way to transition between the spectral domain and the physical domain.
-This is implemented in the base class by storing the coefficients of sample functions as a class property.
-The coefficients are assumed to be at least of one function.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    @staticmethod
-    def transform(
-        f: torch.Tensor,
-        res: TransformResType | None = None,
-        periodic: bool = True,
-        periods: PeriodsInputType = None,
-        allow_fft: bool = True,
-    ) -> torch.Tensor:
-        if not torch.is_complex(f):
-            f = f * (1 + 0j)
-        res = transformResType_to_tuple(res, tuple(f.shape[1:]))
-        periods = periodsInputType_to_tuple(periods, f.shape[1:])
-        # perform 1d transform over every dimension
-        F = f
-        for cdim in range(1, ndims):
-            F = FourierBasis._ndim_transform(
-                F,
-                dim=cdim,
-                func="forward",
-                res=res[cdim - 1],
-                periodic=periodic,
-                period=periods[cdim - 1],
-                allow_fft=allow_fft,
-            )
-
-        return F
-...
-  \end{lstlisting}
-  \caption{Implementation of forward Fourier transform.}\label{fig:fourier_transform_impl}
-\end{figure}
-
-The transitions between the coefficients and functions values are implemented as a function to transform function values to coefficients and an inverse transform function to compute function values from coefficients.
-The base class enforces this by defining abstract methods which any subclass will need to implement.
-The FourierBasis subclass then implements the transform and inverse transform functions specific for transitioning between function values and Fourier basis coefficients.
-As before, the implementation assumes that the first dimension indexes the samples and the rest represent the coefficient wave numbers.
-This means that the implementation must allow for multidimensional functions.
-For the Fourier transform and inverse transform, the multidimensional version is relatively simple to implement.
-The multidimensional Fourier transform essentially performs the one dimensional Fourier transform along one dimension.
-And then, using the result to perform the one dimensional Fourier transform along the next dimension.
-This process is repeated until the last dimension.
-The implementation of the forward transform is presented in \lccref{fig:fourier_transform_impl}.
-The inverse transform simply changes the \verb|func| parameter to \enquote{inverse}.
-
-The Fourier transform along each dimension is done by flattening every other dimension into the sample dimension.
-This essentially means that the function values are \enquote{sliced} along the dimension currently being transformed, and that each \enquote{slice} is its own \enquote{sample}.
-Mathematically, this is simply due to the matrix multiplication of basis functions along one dimension with every other dimension.
-The implementation of this is shown in \lccref{fig:ndim_fourier_transform_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    @staticmethod
-    def _ndim_transform(
-        f: torch.Tensor,
-        dim: int,
-        func: Literal["forward", "inverse"],
-        res: slice,
-        periodic: bool,
-        period: float,
-        allow_fft: bool,
-    ) -> torch.Tensor:
-        # flatten so that each extra dimension is
-        # treated as a separate "sample"
-        # move dimension to transform to the end
-        # so that it can stay intact after f is flatened
-        f_transposed = f.moveaxis(dim, -1)
-        # flatten so that the last dimension is intact
-        f_flatened = f_transposed.flatten(0, -2)
-
-        F_flattened = FourierBasis._raw_transform(
-            f_flatened,
-            func=func,
-            res=res,
-            periodic=periodic,
-            period=period,
-            allow_fft=allow_fft,
-        )
-        # unflatten so that the correct shape is returned
-        F_transposed = F_flattened.reshape(
-          (*f_transposed.shape[:-1], res.step)
-        )
-        F = F_transposed.moveaxis(-1, dim)
-
-        return F
-...
-  \end{lstlisting}
-  \caption{Implementation of n-dimensional Fourier transform for a specific dimension.}\label{fig:ndim_fourier_transform_impl}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    @staticmethod
-    def _raw_transform(
-        f: torch.Tensor,
-        func: Literal["forward", "inverse"],
-        res: slice,
-        periodic: bool,
-        period: float,
-        allow_fft: bool,
-    ) -> torch.Tensor:
-        match func:
-            case "forward":
-                sign = -1
-            case "inverse":
-                sign = 1
-        mode = f.shape[1]
-        domain_starts_at_0 = res.start == 0
-        domain_end_equal_to_period = res.stop == period
-        can_use_fft = (
-            domain_starts_at_0
-            and domain_end_equal_to_period
-            and periodic
-            and allow_fft
-        )
-        if can_use_fft:
-            if func == "forward":
-                F = torch.fft.fft(
-                  f, dim=1, n=res.step, norm="backward"
-                )
-            elif func == "inverse":
-                F = torch.fft.ifft(
-                  f, dim=1, n=res.step, norm="forward"
-                )
-        else:
-            if periodic:
-                n = res.start + torch.arange(res.step).to(f)
-                n = n / res.step * period
-            else:
-                n = torch.linspace(
-                    res.start, res.stop, res.step
-                ).to(f)
-            e = FourierBasis.fn(
-                n.view(-1, 1),
-                mode,
-                periods=period,
-                constant=sign * 2j * torch.pi,
-            )
-
-            F = torch.mm(f, e.T)
-        return F
-...
-  \end{lstlisting}
-  \caption{Implementation of the one dimensional Fourier Transform.}\label{fig:1d_fourier_transform_impl}
-\end{figure}
-
-The one dimensional Fourier transform itself is implemented as a raw transform function.
-This function accepts input of a matrix of values to transform, a parameter to indicate the type of transformation (inverse transform or forward transform), the evaluation boundary and number of grid points, whether the evaluation should assume the function is periodic, the size of the function domain, and if the Fast Fourier Transform is allowed to be used.
-The evaluation boundaries, actual function domain size, whether the function can be assumed to be periodic, and if FFTs is allowed to be used together determine the Discrete Fourier Transform algorithm that is used.
-The FFT algorithm is used if the following are all true: the evaluation starts at zero and ends with the same value as the period, the function can be assumed to be periodic, and FFT is allowed.
-Otherwise, the transform is computed naively using \lccrefs{eq:discrete_fourier_transform,eq:inverse_discrete_fourier_transform}.
-The naive approach allows for evaluating function values of coefficients at various grid sizes and evaluation boundaries.
-This is useful for being able to evaluate at resolutions other than that of the original discretized function or coefficients.
-One use for this is plotting the function at different parts or resolutions.
-The relationship with the physical domain means that the boundaries of the domain is important.
-This is because the function values that will be used may only be valid within certain boundaries.
-Because of this, the information of physical domain bounds must also be stored.
-This is done by storing the span of the function in each dimension.
-The implementation we have gone with doesn't store any other information than the span in each dimension.
-Because of this, the information would need to be stored outside the Basis class instance and any outputs or operations with the classes will need to take this into account.
-The implementation of the one dimensional Fourier transform is presented in \lccref{fig:1d_fourier_transform_impl}.
-
-The secondary set of functionality provided by the basis classes are mathematical operators on the functions the coefficients represent.
-There are four operators implemented, which are the addition, subtraction, derivative, and antiderivative operators.
-These four operations can be further categorized into arithmetic and calculus operations.
-The arithmetic operations, which are addition and subtraction, are implemented by following how the actual mathematical operations would be carried out on two functions which are Fourier series as shown in \lccref{eq:fourier_series_addition}.
-For subtraction, the plus sign is simply replaced with the minus sign.
-\begin{align}
-  \sum_{k} \hat{u}_k e^{2\pi ikx} + \sum_{k} \hat{f}_k e^{2\pi ikx} =
-  \sum_{k} \left(\hat{u}_k + \hat{f}_k\right) e^{2\pi ikx} \label{eq:fourier_series_addition}
-\end{align}
-The implementation leverages the operator overloading in Python classes.
-In addition, the overload should be done to the \verb|__add__| function.
-This function adds the current instance to another object which is the other basis instance for our use case.
-We also want the operation to return an independent instance without any references to the previous instances.
-To do this, all properties are copied into a new instance.
-This is then used to perform the arithmetic operation.
-The implementation in \lccref{fig:basis_addition_impl} demonstrates the addition operation.
-For subtraction, a similar implementation is done using the \verb|__sub__| function and switching the plus sign with the minus sign.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def __add__(self, other: Self):
-        if isinstance(other, self.__class__):
-            if other.coeff is None:
-                return self.copy()
-            elif self.coeff is None:
-                return other.copy()
-            else:
-                result = self.resize_modes(other)
-                result.coeff = result.coeff + other.coeff
-                return result
-        else:
-            raise TypeError(
-                f"unsupported operand type(s) for +: '{
-                    self.__class__
-                }' and '{type(other)}'"
-            )
-...
-  \end{lstlisting}
-  \caption{Implementation of basis addition function.}\label{fig:basis_addition_impl}
-\end{figure}
-
-The calculus operations for Fourier basis take advantage of the properties of the Fourier series.
-As discussed in \lccref{sec:fourier_discussion}, derivatives and integration become multiplication and division in the spectral space of Fourier series.
-Our implementation takes advantage of this as shown in \lccref{fig:basis_grad_impl}.
-Similar to how subtraction is just a modification of the addition operation, the integral or antiderivative operator is also implemented simply by changing the operation with the term multiplier from multiplication to division.
-% TODO: change the reference to specific equations for calculus in spectral domain in ch2
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def grad(self, dim: int = 0, ord: int = 1) -> Self:
-        copy = self.copy()
-        if dim == 0 and self.time_dependent:
-            # time dependent use finite differences
-            dt = self.periods[0] / (self.time_size - 1)
-            coeff = copy.coeff
-            for o in range(ord):
-                coeff = torch.gradient(coeff, spacing=dt, dim=1)[0]
-            copy.coeff = coeff
-        else:
-            if self.time_dependent:
-                # disregard time dimension
-                dim = dim - 1
-            k = copy.wave_number(copy.modes[dim])
-            multiplier_dims = [1 for _ in range(copy.ndim)]
-            multiplier_dims[dim] = copy.modes[dim]
-            if self.time_dependent:
-                multiplier_dims = (1, *multiplier_dims)
-            multiplier = (
-                2
-                * torch.pi
-                * 1j
-                * k.reshape(multiplier_dims).to(copy.coeff)
-                / self.periods[dim]
-            )
-            multiplier = multiplier.pow(ord)
-            coeff = copy.coeff.mul(multiplier)
-            coeff[:, ..., 0] = torch.tensor(0 + 0j)
-            copy.coeff = coeff
-        return copy
-...
-  \end{lstlisting}
-  \caption{Implementation of basis grad function.}\label{fig:basis_grad_impl}
-\end{figure}
-
-The last group of functionality implemented in the Basis and FourierBasis classes provides convenience and often used procedures when working with basis functions.
-First, random coefficient generation for the Fourier basis is implemented.
-This is done as discussed in step 3 of the data generation process discussed in \lccref{sec:data_generation}.
-The implemented function shown in \lccref{fig:generate_coeff_impl} is then wrapped in another function that creates a new FourierBasis instance with the generated coefficients.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    @classmethod
-    def generate_coeff(
-        cls,
-        n: int,
-        modes: int | tuple[int, ...],
-        generator: torch.Generator | None = None,
-        random_func: Callable[..., torch.Tensor] = torch.randn,
-        complex_funcs: bool = False,
-        scale: bool = True,
-    ) -> torch.Tensor:
-        if isinstance(modes, int):
-            modes = (modes,)
-        n_modes = len(modes)
-        assert n_modes > 0, "modes should have at least one element"
-        random_func = partial(random_func, generator=generator)
-        if complex_funcs:
-            coeff = random_func((n, *modes), dtype=torch.complex64)
-        else:
-            coeff = random_func((n, *modes), dtype=torch.complex64)
-
-            vals = cls.inv_transform(coeff)
-            coeff = cls.transform(vals.real + 0j)
-        if scale:
-            scaler = torch.tensor(modes).sum() * 0.2
-            coeff = coeff.mul(scaler)
-        return coeff
-...
-  \end{lstlisting}
-  \caption{Implementation of Fourier Basis coefficient generation function.}\label{fig:generate_coeff_impl}
-\end{figure}
-
-Other convenience functionality also provided include plotting, function value perturbation, and function value evaluation based on domain span information that has been stored in the class instance.
-The function value evaluation is especially useful for experimenting and for the plotting functionality itself.
-This is because, the span was given to the constructor and does not need to be composed again with the inverse transform function.
-
-\subsubsection{Model}\label{sec:impl_model}
-
-\noindent The SpectralSVR model is implemented in this module.
-There are two components in this module.
-First, there is the implementation of least-squares support vector regression (LSSVR) using PyTorch.
-This implementation is a reimplementation and modification of an LSSVR implementation using scikit-learn by \textcite{florencioLssvr2020}.
-The modifications are mainly concerned with using PyTorch in place of scikit-learn.
-Other modifications are concerned with the performance side of things, which are computing the kernel matrix in batches to avoid memory spikes and the ability to compute on hardware accelerators supported by PyTorch such as GPUs.
-The LSSVR implementation starts with the constructor which accepts model hyperparameters which include the regularization parameter, kernel function and any kernel parameters, verbosity level, kernel matrix computation batch size, and device to perform computations on.
-The received parameters are then stored as properties of the class instance.
-For the kernel specifically, it will be initialized with the correct default parameters when the fitting function is called.
-This is because if the kernel of choice is the radial basis function, the default scaling parameter needs to be computed from the training features as the square root of the sum of feature variance values.
-
-The optimization function that fits the model to the training data solves \lccref{eq:lssvr_solution}.
-This function is shown in \lccref{fig:lssvr_fit_function_impl}.
-The first half of the function sets up the left and right hand side matrices.
-The left hand side matrix is constructed in part with the kernel matrix.
-The kernel function used is batched to reduce the peak memory footprint.
-These matrices are then used in the second half to compute the solution using the least squares solver function from PyTorch called lstq.
-Finally, the result is split into the biases and Lagrange multipliers which are then returned as a tuple.
-The optimizing function is wrapped in a more user-friendly function which allows the use of NumPy arrays in addition to the PyTorch Tensor used in the optimizing function.
-The wrapper function is named fit.
-It conforms the inputs provided by the user into the expected types and matrix shapes of rows for samples and columns for input features or output targets.
-The processed inputs and outputs are also stored as support vectors for use during prediction.
-The fit function returns the class instance once training is done.
-This is for method chaining purposes for ease of use when using the fit function in a chain with other functions we will discuss next, such as the prediction function.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def _optimize_parameters(
-      self,
-      X: torch.Tensor,
-      y_values: torch.Tensor,
-    ):
-
-        A = torch.empty(
-          (X.shape[0] + 1,) * 2,
-          device=self.device,
-          dtype=self.dtype,
-        )
-        A[1:, 1:] = self._batched_K(X, X)
-        A[1:, 1:].diagonal().copy_(
-            A[1:, 1:].diagonal()
-            + torch.ones(
-                (A[1:, 1:].shape[0],),
-                device=self.device,
-                dtype=self.dtype,
-            ).to()
-            / self.C
-        )
-        A[0, 0] = 0
-        A[0, 1:] = 1
-        A[1:, 0] = 1
-        shape = np.array(y_values.shape)
-        shape[0] += 1
-        B = torch.empty(
-          list(shape), device=self.device, dtype=self.dtype
-        )
-        B[0] = 0
-        B[1:] = y_values
-
-        solution: torch.Tensor = torch.linalg.lstsq(
-            A.to(dtype=torch.float), B.to(dtype=torch.float)
-        ).solution.to(dtype=self.dtype)
-
-        b = solution[0, :]
-        alpha = solution[1:, :]
-
-        return (b, alpha)
-...
-  \end{lstlisting}
-  \caption{Implementation of Least-squares Support Vector Regression fitting function.}\label{fig:lssvr_fit_function_impl}
-\end{figure}
-
-The learned multipliers and bias parameters are then used for predicting outputs from unseen sample features.
-\Cref{eq:lssvr_prediction_vectorized} shows the computation that needs to be done to compute the predicted output.
-The prediction process first constructs both matrices on the left-hand side of the equation.
-This is done by computing the kernel matrix between the prediction features and the training features, otherwise known as support vectors.
-The prediction function therefore is very straight forward with an input of unseen features and the learned parameters.
-The function output is simply the predicted outputs.
-The implementation of this function is shown in \lccref{fig:lssvr_predict_function_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-NumpyArrayorTensor = (
-    np.ndarray[typing.Any, np.dtype[np.float_]] |
-    torch.Tensor
-)
-...
-    def predict(
-        self,
-        X: NumpyArrayorTensor,
-    ) -> NumpyArrayorTensor:
-        """Predicts the labels of data X given a trained model.
-        - X: ndarray of shape (n_samples, n_attributes)
-        """
-        is_torch = isinstance(X, torch.Tensor)
-        if is_torch:
-            if X.ndim == 1:
-                X_reshaped_torch = X.reshape(-1, 1)
-            else:
-                X_reshaped_torch = X
-            X_= X_reshaped_torch.clone().to(
-                self.device, dtype=self.dtype
-            )
-        else:
-            if X.ndim == 1:
-                X_reshaped_np = X.reshape(-1, 1)
-            else:
-                X_reshaped_np = X
-            X_ = torch.from_numpy(X_reshaped_np).to(
-                self.device, dtype=self.dtype
-            )
-
-        KxX = self._batched_K(X_, self.sv_x)
-
-        y_pred = KxX @ self.alpha + self.b
-        predictions: NumpyArrayorTensor
-        if is_torch:
-            predictions = y_pred.to(X)
-        else:
-            predictions = y_pred.cpu().numpy()
-
-        if X.ndim == 1:
-            return predictions.reshape(-1)
-        else:
-            return predictions
-...
-  \end{lstlisting}
-  \caption{Implementation of Least-squares Support Vector Regression prediction function.}\label{fig:lssvr_predict_function_impl}
-\end{figure}
-
-Aside from these core functions, interpretation of the model using the methods introduced by \textcite{ustunVisualisationInterpretationSupport2007} are also implemented in the LSSVR class.
-First, using the support vectors and the kernel matrix computed between each support vectors, the correlation image is computed.
-This image, which is a correlation matrix, is intended to visualize the importance of features within kernel functions.
-This is simply computed with matrix multiplication between the kernel matrix and the support vectors.
-The implementation is shown in \lccref{fig:lssvr_correlation_image_function_impl}.
-The batched kernel function is used in this case to mitigate the memory footprint.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def get_correlation_image(self):
-        return self._batched_K(
-            self.sv_x, self.sv_x
-        ).mm(self.sv_x)
-...
-  \end{lstlisting}
-  \caption{Implementation of Least-squares Support Vector Regression correlation image function.}\label{fig:lssvr_correlation_image_function_impl}
-\end{figure}
-
-The other interpretation method introduced by \textcite{ustunVisualisationInterpretationSupport2007} visualizes the relationship learned between the input features and the outputs.
-This visualization is computed as the matrix multiplication between the support vectors and the learned Lagrange multipliers.
-The support vector matrix is transposed so that the multiplication is done on the dimension that indexes each sample.
-This computation is implemented as shown in \lccref{fig:lssvr_p_matrix_function_impl}.
-The resulting matrix is termed the p-matrix.
-The columns of this matrix represents the outputs and the rows represents the input features.
-The p-matrix values show how each feature contribute to the output learned by the model.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def get_p_matrix(self):
-        return self.sv_x.T.mm(self.alpha)
-...
-  \end{lstlisting}
-  \caption{Implementation of Least-squares Support Vector Regression p-matrix function.}\label{fig:lssvr_p_matrix_function_impl}
-\end{figure}
-
-The second component of the model modules is the SpectralSVR implementation that uses a multi-output support vector regression (SVR) model to learn in the spectral domain, such as the LSSVR implementation in the first component.
-The SpectralSVR is implemented as a class that extends the LSSVR to be able to learn from features and labels which are complex valued, which is the case for Fourier series coefficients.
-First, the constructor used to initialize each SpectralSVR instance accepts a Basis instance, an SVR instance which is the implemented LSSVR by default, and the verbosity of the model.
-These parameters are then used when the training function shown in \lccref{fig:spectralsvr_train_impl} is called.
-Training the SpectralSVR model begins by calling the train function with parameters of the input function representation, output function representation, and an indicator of whether the output function is time dependent.
-Then, the function ensures that the features and labels are matrices.
-And then, if the input or output function representations are complex, they are transformed into the real representation.
-These formatted training data features and labels are then used to train the LSSVR model itself.
-Finally, to again allow for chaining methods, the function returns the current class instance.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def train(
-        self,
-        f: torch.Tensor,
-        u_coeff: torch.Tensor,
-        u_time_dependent: bool = False,
-    ):
-        self.basis.time_dependent = u_time_dependent
-        if self.basis.coeff_dtype.is_complex:
-            u_coeff = to_complex_coeff(u_coeff)
-
-        if f.ndim > 2:
-            f = f.flatten(1)
-        if u_coeff.ndim > 2:
-            u_coeff = u_coeff.flatten(1)
-
-        if torch.is_complex(u_coeff):
-            u_coeff = to_real_coeff(u_coeff)
-        if torch.is_complex(f):
-            f = to_real_coeff(f)
-        self.svr.fit(f, u_coeff)
-        return self
-...
-  \end{lstlisting}
-  \caption{Implementation of SpectralSVR training function.}\label{fig:spectralsvr_train_impl}
-\end{figure}
-
-Using the learned data to predict other output function representations from unseen input functions can be done by directly calling the predict function of the LSSVR\@.
-This results in the real representation which needs to be converted into the complex representation for the FourierBasis.
-Once the conversion is done, the coefficients can be used to construct a new FourerBasis instance of the predictions.
-From there, the predicted functions can be evaluated and  plotted.
-However, if one simply wants to evaluate the value of the predicted function at arbitrary points, another function is implemented to provide ease of use for this exact case.
-The implemented function is called forward as displayed in \lccref{fig:spectralsvr_forward_impl}.
-The arguments to this function are the input functions, the evaluation points, and the domain span.
-The function first predicts the output function coefficients.
-Then, the predicted coefficients are multiplied with the basis function values at each point to compute the final predicted point values.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def forward(
-        self,
-        f: torch.Tensor,
-        x: torch.Tensor,
-        periods: tuple[float, ...]
-        | None = None,
-    ) -> torch.Tensor:
-        if len(x.shape) == 1:
-            x = x.unsqueeze(-1)
-
-        # compute coefficients
-        if torch.is_complex(f):
-            f = to_real_coeff(f)
-        coeff = self.svr.predict(f)
-        # convert to complex if basis needs complex values so that the reshaping is correct
-        if self.basis.coeff_dtype.is_complex:
-            coeff = to_complex_coeff(coeff)
-
-        return self.basis.evaluate(
-            coeff=coeff.reshape((f.shape[0], *self.modes)),
-            x=x,
-            periods=periods,
-            time_dependent=self.basis.time_dependent,
-        )
-...
-  \end{lstlisting}
-  \caption{Implementation of SpectralSVR forward function (pointwise prediction).}\label{fig:spectralsvr_forward_impl}
-\end{figure}
-
-The final core piece of functionality the SpectralSVR class provides is the inverse parameter estimation.
-This is implemented to solve inverse problems such as predicting the initial conditions for the Burgers' equation or heat equation.
-This function essentially does the gradient descent on a loss function in such a way that the output function matches some expected output.
-The loss function is simply a measure of how far the outputs of the current predicted inputs are from the target outputs.
-The loss function is formulated as the mean squared error of the difference between the predicted output and expected output.
-Using some randomly initialized values as the inputs, the predicted output is then used to compute the loss.
-The gradient of the loss with respect to the inputs are then computed and then used to perform optimization of the inputs using the ADAM optimizer.
-This is implemented as the inverse function shown in \lccref{fig:spectralsvr_inverse_impl}.
-The function arguments are the expected output function coefficients, evaluation points, the loss function used, how many optimization loops are done, the random number generator, and the gain which is used in generating the random initial input functions.
-The function returns the estimated input function coefficients in the real representation.
-For Fourier coefficients this means that the predicted input coefficients need to first be converted to complex valued tensors and then used to construct a FourierBasis instance.
-For convenience, a wrapper like the forward function is also implemented for evaluating the function values of the predicted input coefficients.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def inverse_coeff(
-        self,
-        u_coeff: torch.Tensor,
-        loss_fn: Callable[
-            [torch.Tensor, torch.Tensor], torch.Tensor
-        ] = mean_squared_error,
-        epochs=100,
-        generator=torch.Generator().manual_seed(42),
-        gain=0.05,
-        **optimizer_params,
-    ):
-        f_shape = (u_coeff.shape[0], self.svr.sv_x.shape[1])
-        complex_coeff = u_coeff.is_complex()
-        original_device = u_coeff.device
-        u_coeff = to_real_coeff(u_coeff.flatten(1)).to(self.svr.device)
-
-        # inverse problem
-        f_coeff_pred = (
-            torch.randn(f_shape, generator=generator).to(self.svr.device) * gain
-        )
-        f_coeff_pred.requires_grad_()
-        optim = torch.optim.Adam([f_coeff_pred], **optimizer_params)
-
-        for epoch in range(epochs):
-            optim.zero_grad()
-            u_coeff_pred = self.svr.predict(f_coeff_pred)
-            loss = loss_fn(u_coeff_pred, u_coeff)
-            loss.backward()
-            optim.step()
-        optim.zero_grad()
-        f_coeff_pred.requires_grad_(False)
-        if complex_coeff:
-            f_coeff_pred = to_complex_coeff(f_coeff_pred)
-        return f_coeff_pred.to(original_device)
-...
-  \end{lstlisting}
-  \caption{Implementation of SpectralSVR inverse coeff function (parameter estimation).}\label{fig:spectralsvr_inverse_impl}
-\end{figure}
-
-The SpectralSVR class also provides a convenience function for testing the performance of the learned model.
-This function is shown in \lccref{fig:spectralsvr_test_impl}.
-The function arguments are the testing inputs, expected testing outputs, and a resolution for evaluation of function values.
-The first step is to convert the testing input into real representations and then predicting the output function.
-The predicted output are then compared to the testing outputs using many metrics including RMSE, MSE, MAE, R\textsuperscript{2}, SMAPE, RRSE, and the number of Nan values present in the predicted output.
-The same comparison process is carried out again for the function values which are evaluated at the specified resolution.
-Finally, the function returns the metric values as a nested tuple for both the coefficients predictions and the function value predictions.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def test(
-        self,
-        f: torch.Tensor,
-        u_coeff_targets: torch.Tensor,
-        res: ResType = 200,
-    ):
-        if torch.is_complex(f):
-            logger.debug("transform f to real")
-            f = to_real_coeff(f)
-        u_coeff_preds = self.svr.predict(f)
-        if torch.is_complex(u_coeff_targets):
-            logger.debug("transform u_coeff to real")
-            u_coeff_targets = to_real_coeff(u_coeff_targets)
-
-        grid = self.basis.grid(res).flatten(0, -2)
-        u_preds = self.basis.evaluate(
-            coeff=to_complex_coeff(u_coeff_preds),
-            x=grid,
-            time_dependent=self.basis.time_dependent,
-        ).real
-        u_targets = self.basis.evaluate(
-            coeff=to_complex_coeff(u_coeff_targets),
-            x=grid,
-            time_dependent=self.basis.time_dependent,
-        ).real
-        return {
-            "spectral": get_metrics(
-                u_coeff_preds, u_coeff_targets
-            ),
-            "function value": get_metrics(u_preds, u_targets),
-        }
-...
-  \end{lstlisting}
-  \caption{Implementation of SpectralSVR test function.}\label{fig:spectralsvr_test_impl}
-\end{figure}
-
-\subsubsection{Problems}
-
-\noindent The final module implements the PDEs that will serve as problems the proposed modules will solve.
-The implementation is mainly responsible for generating datasets from the PDEs and computing the PDE residuals.
-This implementation is focused on the two synthetic datasets which are the antiderivative problem and the Burgers' equation problem.
-The problem base class is implemented as an abstract class that the specific problems will subclass.
-The base class requires any subclass to implement three methods.
-First, the data generation method which receives specifications such as what basis functions to use, how many function samples to create, how many modes are needed for each sample, and a PyTorch generator that will be used in generating the random basis coefficients.
-Other arguments more specific to each problem will be implemented by the specific subclass.
-This function is then expected to return a tuple of Basis instances.
-The second and third functions are the spectral and function value residuals for the PDE of each subclass, respectively.
-These three functions make up the functionality that is offered by all Problem subclasses.
-The implementation of the Problem subclass can be seen in \lccref{fig:problem_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-import abc
-import torch
-from ..basis import BasisSubType
-
-class Problem(abc.ABC):
-    def __init__(self) -> None:
-        super().__init__()
-
-    @abc.abstractmethod
-    def generate(
-        self,
-        basis: type[BasisSubType],
-        n: int,
-        modes: int | tuple[int, ...],
-        *args,
-        generator: torch.Generator | None = None,
-        **kwargs,
-    ) -> tuple[BasisSubType, ...]:
-        pass
-
-    @abc.abstractmethod
-    def spectral_residual(
-        self, u: BasisSubType, *args, **kwargs
-    ) -> BasisSubType:
-        pass
-
-    @abc.abstractmethod
-    def residual(
-        self, u: BasisSubType, *args, **kwargs
-    ) -> BasisSubType:
-        pass
-  \end{lstlisting}
-  \caption{Implementation of Problem base class.}\label{fig:problem_impl}
-\end{figure}
-
-The antiderivative problem is relatively simple to implement.
-The generation function takes advantage of the gradient operation and generate function provided by the Basis subclasses.
-The arguments to this function are the same as the base class with the addition of an integration constant parameter.
-By default, the value of the integration constant is zero.
-The function then returns the tuple of basis subclass instances representing the derivative and antiderivative functions.
-This function can be seen in \lccref{fig:antiderivative_generate_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def generate(
-        self,
-        basis: Type[BasisSubType],
-        n: int,
-        modes: int | tuple[int, ...],
-        u0: float | int | complex,
-        *args,
-        generator: torch.Generator | None = None,
-        **kwargs,
-    ) -> tuple[BasisSubType, BasisSubType]:
-        if isinstance(modes, int):
-            modes = (modes,)
-        # generate solution functions
-        u = basis.generate(
-            n, modes, generator=generator, *args, **kwargs
-        )
-        # compute derivative functions
-        ut = u.grad()
-        # set the integration coefficient
-        if isinstance(u0, complex):
-            if u.coeff.is_complex():
-                u.coeff[:, 0] = torch.tensor(u0)
-            else:
-                u.coeff[:, 0] = torch.tensor(u0).real
-        elif isinstance(u0, float) or isinstance(u0, int):
-            if u.coeff.is_complex():
-                u.coeff[:, 0] = torch.tensor(u0 + 0j)
-            else:
-                u.coeff[:, 0] = torch.tensor(u0)
-        else:
-            u.coeff[:, 0] = u0
-
-        return (u, ut)
-...
-  \end{lstlisting}
-  \caption{Implementation of Antiderivative generate function.}\label{fig:antiderivative_generate_impl}
-\end{figure}
-
-The residual functions are similarly easy to implement as shown in \lccref{fig:antiderivative_residual_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def spectral_residual(
-        self, u: BasisSubType, ut: BasisSubType
-    ) -> BasisSubType:
-        residual = u.grad() - ut
-        if residual.coeff is not None:
-            residual.coeff[:, 0].mul_(0)
-
-        return residual
-
-    def residual(
-        self, u: BasisSubType, ut: BasisSubType
-    ) -> BasisSubType:
-        u_val, grid = u.get_values_and_grid()
-        ut_val = ut.get_values()
-        dt = grid[1, 0] - grid[0, 0]
-        u_grad = torch.gradient(
-            u_val, spacing=dt.item(), dim=1
-        )[0]
-        residual_val = u_grad - ut_val
-        residual = u.copy()
-        residual.coeff = u.transform(residual_val)
-        return residual
-...
-  \end{lstlisting}
-  \caption{Implementation of Antiderivative residual functions.}\label{fig:antiderivative_residual_impl}
-\end{figure}
-
-For the Burgers' equation, the problem subclass for this PDE implemented a generate function with two generation paths.
-But before discussing the specifics of the two paths, the function has some extra arguments and preprocessing of those arguments.
-This time the function asks for the kind of functions the initial condition and the forcing term needs to be, whether they are random or constant.
-The combination of the kind of functions the initial conditions and forcing terms are will determine the path of generation that the function will take.
-The function also requires the viscosity parameter nu which is 0.01 by default.
-The domain also needs to be specified with a default value of 0 to 1 with 200 grid points for both space and time.
-The solver which is used for one of the generation procedures is also an argument with a default of the implicit Adams solver from torchdiffeq \autocite{Chen_torchdiffeq_2021}.
-Finally, whether the output basis coefficients are time dependent or not is passed in as an argument alongside with the PyTorch generator.
-The implementation of this portion of the function can be seen in \lccref{fig:burgers_generate_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def generate(
-        self,
-        basis: Type[BasisSubType],
-        n: int,
-        modes: int | tuple[int, ...],
-        u0: ParamInput | BasisSubType = "random",
-        f: ParamInput | BasisSubType = 0,
-        nu: float = 0.01,
-        space_domain=slice(0, 1, 200),
-        time_domain=slice(0, 1, 200),
-        solver: SolverSignatureType = implicit_adams_solver,
-        time_dependent_coeff: bool = True,
-        *args,
-        generator: torch.Generator | None = None,
-        **kwargs,
-    ) -> tuple[BasisSubType, BasisSubType]:
-        if isinstance(modes, int):
-            modes = (modes,)
-
-        device = "cuda:0" if torch.cuda.is_available() else "cpu"
-
-        L = space_domain.stop - space_domain.start
-        x = (
-            basis.grid(slice(
-                space_domain.start, space_domain.stop, modes[0]
-            )).flatten(0, -2)
-            .to(device=device)
-        )
-        T: float = time_domain.stop - time_domain.start
-        nt = int(time_domain.step)
-        # nt = int(T / (0.01 * nu) + 2)
-        dt = T / (nt - 1)
-        t = basis.grid(time_domain).flatten().to(device=device)
-        periods = (T, L)
-...
-  \end{lstlisting}
-  \caption{Implementation of Burgers generate function.}\label{fig:burgers_generate_impl}
-\end{figure}
-
-The first generation path and most similar to the antiderivative case is when both the initial condition and forcing terms are random.
-This branch of the generate function utilizes the residual function to compute the forcing term from the randomly generated solution function.
-This method of generating the solution and forcing term is stable and relatively straightforward.
-The implementation of this branch is shown in \lccref{fig:burgers_generate_manufactured_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-        if u0 == "random" and f == "random":
-            # use method of manufactured solution
-            time_mode = modes[0]
-            if len(modes) > 1:
-                modes = modes[1:]
-            u = basis.generate(
-                n,
-                (time_mode, *modes),
-                periods=periods,
-                generator=generator,
-            )
-            res_modes = tuple(slice(0, L, mode) for mode in modes)
-            fst = self.spectral_residual(
-                u,
-                basis(
-                    basis.generate_empty(n, (time_mode, *modes))
-                ),
-                nu,
-            )
-            u_gen = u
-            f_gen = fst
-            # convert to timed dependent coeffs
-            if time_dependent_coeff:
-                u_val = u.get_values(res=(time_domain, *res_modes))
-                u_coeff = basis.transform(
-                    u_val.flatten(0, 1)
-                ).reshape((n, nt, *modes))
-                u_gen = basis(
-                    coeff=u_coeff,
-                    time_dependent=True,
-                    periods=periods
-                )
-
-                f_val = fst.get_values(
-                    res=(time_domain, *res_modes)
-                )
-                f_coeff = basis.transform(
-                    f_val.flatten(0, 1)
-                ).reshape((n, nt, *modes))
-                f_gen = basis(
-                    coeff=f_coeff,
-                    time_dependent=True,
-                    periods=periods
-                )
-...
-  \end{lstlisting}
-  \caption{Implementation of Burgers generate function manufactured method.}\label{fig:burgers_generate_manufactured_impl}
-\end{figure}
-
-The second case is when at least one of the initial condition or forcing term is not random.
-This second case requires solving the Burgers' equation using traditional numerical methods.
-The generate function calls a function that has the responsibility of setting up the constant initial conditions or constant forcing terms and then calls the ODE solver specified in the generate function arguments.
-The right-hand side function computes the time derivative based on \lccref{eq:time_derivative_time_step_function}.
-The implementation of this is show in \lccref{fig:burgers_generate_dt_impl}.
-Putting the above together gives us the implementation of the method of lines generation of Burgers' equation solution and forcing term as show in \lccref{fig:burgers_generate_mol_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    @staticmethod
-    def rhs(
-        basis: type[Basis],
-        nu: float,
-        u_hat: torch.Tensor,
-        f_hat: torch.Tensor,
-    ) -> torch.Tensor:
-        u = basis(u_hat)
-        dealias_modes = tuple(
-            int(mode * 1.5) for mode in u.modes
-        )
-        u_dealiased = u.resize_modes(
-            dealias_modes, rescale=False
-        )
-        u_val = basis.inv_transform(u_dealiased.coeff)
-        uu_x_hat_dealiased = 0.5 * basis.transform(u_val**2)
-        uu_x = basis(
-            uu_x_hat_dealiased
-        ).resize_modes(u.modes, rescale=False).grad()
-
-        u_u_x_hat = uu_x.coeff
-        u_xx_hat = u.grad().grad().coeff
-        u_t_hat = nu * u_xx_hat + f_hat - u_u_x_hat
-        return u_t_hat
-...
-  \end{lstlisting}
-  \caption{Implementation of Burgers generate function time derivative.}\label{fig:burgers_generate_dt_impl}
-\end{figure}
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-        u0.coeff = u0.coeff.to(device=device)
-        fst.coeff = fst.coeff.to(device=device)
-        print(f"generating with {len(t)} time steps")
-
-        def f_func(t: torch.Tensor, x: torch.Tensor = x):
-            x = x.tile((1, 2))
-            x[:, 0] = t
-            return basis.transform(
-                fst(x).reshape((-1, modes[0]))
-            )
-
-        def rhs_func(t: torch.Tensor, y0: torch.Tensor):
-            y0 = to_complex_coeff(y0)
-            return to_real_coeff(
-                cls.rhs(basis, nu, y0, f_func(t))
-            )
-
-        u_hat = solver(rhs_func, to_real_coeff(u0.coeff), t)
-        if basis.coeff_dtype.is_complex:
-            u_shape = u_hat.shape
-            u_hat = to_complex_coeff(
-                u_hat.flatten(0, 1)
-            ).reshape(
-                (*u_shape[:2], *u0.coeff.shape[1:])
-            )
-
-        u_hat = u_hat.movedim(0, 1)
-        if timedependent_solution:
-            u = basis(u_hat, **kwargs, time_dependent=True)
-        else:
-            u_hat = u_hat.reshape((n * nt, modes[0]))
-            u = basis(
-                basis.transform(
-                    basis.inv_transform(u_hat).reshape(
-                        (n, nt, modes[0])
-                    )
-                ),
-                **kwargs,
-            )
-        u.coeff = u.coeff.cpu()
-        fst.coeff = fst.coeff.cpu()
-        return (u, fst)
-...
-  \end{lstlisting}
-  \caption{Implementation of Burgers generate function method of lines.}\label{fig:burgers_generate_mol_impl}
-\end{figure}
-
-The spectral residual of the Burgers' equation which is used in the method of manufactured solution generation approach is implemented as shown in \lccref{fig:burgers_spectral_residual_impl}.
-As with the right-hand side function, we use the psuedospectral approach for computing the convolution term to avoid large computational expenses for higher number of modes.
-The function value residual is also implemented similarly to the antiderivative version.
-The derivatives are computed with the PyTorch gradient function.
-And then using \lccref{eq:forced_viscous_burgers}, the residual is computed by subtracting the forcing term from both sides.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def spectral_residual(
-        self, u: BasisSubType, f: BasisSubType, nu: float
-    ) -> BasisSubType:
-        u_t = u.grad(dim=0, ord=1)
-
-        dealias_modes = tuple(
-            int(mode * 1.5) for mode in u.modes
-        )
-        u_dealiased = u.resize_modes(
-            dealias_modes, rescale=False
-        )
-        u_val = u.inv_transform(u_dealiased.coeff)
-        uu_dealiased = u.copy()
-        uu_dealiased.coeff = u.transform(u_val.pow(2).mul(0.5))
-        uu_x = uu_dealiased.resize_modes(
-            u.modes, rescale=False
-        ).grad(dim=1)
-
-        u_xx = u.grad(dim=1, ord=2)
-        nu_u_xx = u_xx
-        nu_u_xx.coeff = nu_u_xx.coeff * nu
-
-        residual = u_t + uu_x - nu_u_xx - f
-        return residual
-...
-  \end{lstlisting}
-  \caption{Implementation of Burgers spectral residual function.}\label{fig:burgers_spectral_residual_impl}
-\end{figure}
-
-\subsection{Testing}
-\noindent The implementation is followed by tests of the functionality core to this study.
-The testing is done using the PyTest library.
-The testing method used is a black box approach.
-The tests are written in a separate \verb|tests| directory.
-Each module is tested by a separate file.
-The tests are done to ensure compliance of the implementation to the requirements of the software.
-The final results are presented in \lccref{table:impl_test_result}.
-Each version and iteration of the development must ensure that the tests are passed before any changes are committed to the GitHub repository.
-
-\begin{table}[H]
-  \centering
-  \begin{tabular}{lm{0.2\linewidth}m{0.5\linewidth}l}
-    % \toprule
-    \toprule
-    No & Process                         & Test Target                                                                                                   & Test Result \\
-    \midrule
-    1  & Transform                       & Transform invertible with inverse transform                                                                   & Achieved    \\\addlinespace[0.5em]
-    2  & Evaluation                      & Transform coefficient evaluation close to original values                                                     & Achieved    \\\addlinespace[0.5em]
-    3  & Plot                            & Plotting function is run successfully                                                                         & Achieved    \\\addlinespace[0.5em]
-    4  & Perturb                         & Perturb function is run successfully                                                                          & Achieved    \\\addlinespace[0.5em]
-    5  & Operations                      & Operation functions is run successfully                                                                       & Achieved    \\\addlinespace[0.5em]
-    6  & Complex Coefficients Conversion & Conversion between real and complex coefficient representation is invertible for odd and even number of modes & Achieved    \\\addlinespace[0.5em]
-    7  & SpectralSVR Train               & Training function is run successfully                                                                         & Achieved    \\\addlinespace[0.5em]
-    8  & SpectralSVR Prediction          & Coefficient prediction error within tolerable range                                                           & Achieved    \\\addlinespace[0.5em]
-    9  & SpectralSVR Prediction          & Function value prediction error within tolerable range                                                        & Achieved    \\
-    \bottomrule
-  \end{tabular}
-  \caption{Testing results of the SpectralSVR Library implementation using black box method.}\label{table:impl_test_result}
-\end{table}
-
-\section{Experimental Scenarios}\label{sec:experimental_scenarios}
-\noindent To achieve the goals of this study, as outlined in \lccref{sec:aims}, we present three experimental scenarios.
-These scenarios represent different experimental configurations that will be applied to our implementation of the SpectralSVR library.
-A table of the configurations for each scenario can be seen in \lccref{table:experimental_scenarios}.
-
-\begin{table}[H]
-  \caption{The configuration of experimental scenarios in this study.}\label{table:experimental_scenarios}
-  \centering
-  \begin{tabularx}{\textwidth}{L{0.75}*{3}{L{1.09}}} % compute these using approx barycentric coords (x + 3y = 4, x = 0.8y)
-    \toprule
-    Configuration                    & Scenario 1                                          & Scenario 2                                                          & Scenario 3                                 \\
-    \midrule
-    Data Source                      & Synthetic (computed from equations)                 & Synthetic (computed from equations) with three viscosity values     & ERA5 dataset                               \\\addlinespace[0.5em]
-    Data Augmentations               & Perturbations of three different noise levels       & Perturbation of 10\% the mean standard deviation of function values &                                            \\\addlinespace[0.5em]
-    Data Sample Size                 & 5000 unique functions for each noise level          & 500 unique functions for each viscosity value                       & 7000 time steps                            \\\addlinespace[0.5em]
-    Number of Modes                  &                                                     &                                                                     &                                            \\\addlinespace[0.5em]
-    Scaling                          & Standard scaling                                    & Standard scaling                                                    & Standard scaling                           \\\addlinespace[0.5em]
-    Dataset Split                    & 80\% Training and 20\% Testing for each noise level & 80\% Training and 20\% Testing for each viscosity value             & 80\% Training and 20\% Testing             \\\addlinespace[0.5em]
-    Regularization Parameter (\(C\)) & 1.0                                                 & 1.0                                                                 & 1.0                                        \\\addlinespace[0.5em]
-    Kernel                           & RBF (\(\sigma = features \times X.var()\))          & RBF (\(\sigma = features \times X.var()\))                          & RBF (\(\sigma = features \times X.var()\)) \\\addlinespace[0.5em]
-    Additional Tests                 & Exact solutions                                     & Exact solutions                                                     &                                            \\\addlinespace[0.5em]
-    Interpretation                   & p-matrix and correlation image                      & p-matrix and correlation image                                      & p-matrix and correlation image             \\
-    \bottomrule
-  \end{tabularx}
-\end{table}
-
-Each scenario serves a different purpose.
-The first scenario is constructed to establish whether the model can learn any relationships at all in data that implicitly defines differential equations.
-This scenario is a proof of concept of whether the model is capable of accurately learning the relationship between derivatives and their anti-derivatives.
-As the simplest case, it provides a foundation for understanding the model and its behavior.
-The 5\% noise model is then used to predict the antiderivative of a cosine function with a period of one as shown in \lccref{eq:sine_derivative}.
-The exact solution is known as \lccref{eq:sine_function} \autocite{abramowitzHandbookMathematicalFunctions1972}.
-The second goal of this scenario is to determine how noise affects the model's predictions.
-This is especially important for the inverse problem because of how sensitive the derivative is to changes in the antiderivative.
-To further solidify how the model fares for inverse problems, this scenario will also assess the performance of a trained model for a very simple inverse problem setup to determine the derivatives of the testing subset from the antiderivatives.
-This setup will utilize the model as a surrogate forward solver and optimize for a loss function using the inverse function of the SpectralSVR class as described in \lccref{sec:impl_model}.
-\begin{align}
-  f(x) & = 2\pi \cos\left(2\pi x\right)\label{eq:sine_derivative} \\
-  f(x) & = \sin\left(2\pi x\right)\label{eq:sine_function}
-\end{align}
-
-The second scenario extends the goal of the first scenario by examining the model and its behavior when learning a nonlinear PDE\@.
-The data subsets with different viscosity values are intended to allow us to learn more about how this will affect the performance on the exact solutions for lower viscosity numbers.
-The model will learn to predict future states of systems governed by the Burgers' equation from past states.
-The model for each viscosity will be used to predict \lccref{eq:burgers_exact_solution} from initial conditions at time equals zero and the corresponding forcing term of a constant value of zero.
-The exact equation prediction will be done using a rollout method.
-The initial condition along with the initial forcing term will be given to the model to predict the solution at the first time step.
-The model will then use the predicted solution with the forcing term at the first time step to predict the solution at the second time step.
-This is repeated until the stopping condition of time \(t=10\).
-The forcing term for the exact solution is a constant zero.
-Along with the rollout of the exact solution, we also perform roll out on one of the test solution.
-
-The third scenario is designed to demonstrate the modeling capability of SpectralSVR on a more practical problem of weather prediction.
-The earth weather system is a complex collection of processes.
-Using the ERA5 dataset, the model will be used to predict future states of the atmosphere from previous states.
-Specifically, the model will learn to predict the temperature 2 meters above the surface.
-That means that other than the time and spatial resolution not being the highest, the model will also learn from partial information of the relationships defined by the equation since no other variables will be included.
-This choice was made as an analog for situation with unknown PDEs and therefore unknown variables.
-With these situations, there is no guarantee that the variables measured have any relation with the system.
-These three scenarios together address the last two aims of this study.
-
-\section{Experimental Results}\label{sec:experimental_results}
-\noindent In this section, the results of each experimental scenario is presented and analyzed. The results come in the form of testing metrics mentioned in . %TODO: add reference to the metrics used.
-The model interpretations are displays of the correlation image and the p-matrix. The function values and coefficients themselves will also be plotted depending on the number of dimensions.
-
-\subsection{Scenario 1}
-\noindent The first scenario results are presented in four parts.
-The first is the coefficient prediction metrics which is shown in \lccref{table:scenario_1_spectral_metrics}.
-The table shows the noise level and the performance metrics.
-\begin{table}[H]
-  \caption{Performance metrics of coefficient prediction in scenario 1 by noise level.}\label{table:scenario_1_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrrrrrrr}
-    \toprule
-    Noise level & MSE   & RMSE & MAE  & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    5\%         & 0.86  & 0.93 & 0.57 & 0.96 & 0.31  \\
-    10\%        & 2.06  & 1.43 & 0.93 & 0.91 & 0.46  \\
-    50\%        & 15.59 & 3.95 & 3.04 & 0.50 & 1.04  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The scenario is implemented as a Jupyter notebook which imports relevant libraries and our SpectralSVR library.
-The notebook starts with creating the data with the Antiderivative problem subclass.
-All random processes use the same PyTorch Generator instance with a seed of 42.
-The data is then augmented by perturbing the function values to create three versions with the noise levels mentioned in the scenario.
-Looping through each version, the training and testing subsets are randomly sampled to result in 80\% and 20\% of the original dataset respectively.
-Then the scaling function is fitted on the training subset inputs.
-And then, both the training and testing inputs are transformed using the fitted scaling function.
-Next, an instance of SpectralSVR is trained and tested.
-Finally, the metrics are stored and the next noise level is processed.
-Next the 5\% noise model is used to predict the antiderivative of a sine function.
-
-The kernel scaling hyperparameter sigma has the same value of 10 for all noise levels.
-This is because the inputs are all scaled to approximately have a standard deviation of one.
-The value itself is from the number of features which comes out to 100 total inputs to the LSSVR\@.
-
-\Cref{table:scenario_1_spectral_metrics} shows that the model is able to generalize from the training data and learn the simple linear antiderivative operator.
-Focusing on the coefficient of determination (R\textsuperscript{2}) scores, we can see that the model is off by 0.04 to the perfect score of 1.0 for the lowest noise level.
-While increasing noise levels does degrade the performance, this is partly due to the target values also having been perturbed.
-This fact can be seen if we look at how predictions from the very same trained models on noisy inputs are compared to the noise-free versions of the antiderivative functions which is shown in \lccref{table:scenario_1_clean_spectral_metrics}.
-The metrics show that the model predictions are slightly closer to the unperturbed function coefficients compared to the perturbed versions.
-This can be seen as the influence of the independent synthetic measurement noise in the perturbed targets being removed from the testing metrics.
-
-The higher noise levels shows that the model is still relatively accurate.
-Looking at the R\textsuperscript{2} score for the 50\% noise level, the model is more accurate than a baseline mean value model.
-The R\textsuperscript{2} score of 0.5 means that the model predictions has roughly half the error the baseline would produce.
-
-\begin{table}[H]
-  \caption{Performance metrics of coefficient prediction compared to unperturbed targets in scenario 1 by noise level.}\label{table:scenario_1_clean_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrrrrrr}
-    \toprule
-    Noise level & MSE  & RMSE & MAE  & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    5\%         & 0.79 & 0.89 & 0.51 & 0.96 & 0.28  \\
-    10\%        & 1.80 & 1.34 & 0.80 & 0.92 & 0.40  \\
-    50\%        & 9.30 & 3.05 & 2.23 & 0.62 & 0.90  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The function values are also evaluated and the values of the metrics between the noisy targets and predictions are shown in \lccref{table:scenario_1_function_metrics}.
-While the relative metrics R\textsuperscript{2} and sMAPE stay close to the values we obtained for the coefficients themselves, since the metrics are now being computed in the physical domain, the scales have changed and because of that the values of the absolute metrics now reflect the change in scale.
-For reference, the scale of the target coefficient values for the 50\% noise level dataset in their real representation can range on average from -13.54 to 13.6 across the entire dataset.
-Therefore, an RMSE value of 3.94 for the predictions compared to the noisy targets mean that the error ratio is roughly 0.148 or just above 1 to 7.
-For the function values of the 50\% noise dataset the values range on average from -2.5 to 2.49.
-This was more difficult to compute since there is no direct way to compute the amplitude of the function from just the coefficients.
-Here we used the inverse transform and extracted the maximum and minimum values of each function from the discrete values.
-Since the RMSE in \lccref{table:scenario_1_function_metrics} for the 50\% noise dataset is 0.63, the error ratio comes to 0.126.
-One side note about \lccref{table:scenario_1_function_metrics} is that since the model instances are the same as the ones used in the coefficient evaluations, the hyperparameters are still the same including the kernel scaling factor sigma.
-\begin{table}[H]
-  \caption{Performance metrics of function value from evaluated coefficient prediction in scenario 1 by noise level.}\label{table:scenario_1_function_metrics}
-  \centering
-  \begin{tabular}{lrrrrrrrr}
-    \toprule
-    Noise level & MSE  & RMSE & MAE  & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    5\%         & 0.03 & 0.18 & 0.15 & 0.97 & 0.39  \\
-    10\%        & 0.08 & 0.29 & 0.23 & 0.92 & 0.55  \\
-    50\%        & 0.62 & 0.79 & 0.63 & 0.49 & 1.05  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-For the metrics between the predictions and the noise-free version of the target function values, the results parallel the outcomes of the coefficient predictions.
-The metrics show that the model performs slightly better with more pronounced differences for the higher noise levels.
-This echoes our previous statement on the effect of independent \enquote{measurement} noise in the target values on the evaluation metrics.
-\begin{table}[H]
-  \caption{Performance metrics of function value from evaluated coefficient prediction compared to unperturbed targets in scenario 1 by noise level.}\label{table:scenario_1_clean_function_metrics}
-  \centering
-  \begin{tabular}{lrrrrrrr}
-    \toprule
-    Noise level & MSE  & RMSE & MAE  & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    5\%         & 0.03 & 0.18 & 0.14 & 0.97 & 0.38  \\
-    10\%        & 0.07 & 0.27 & 0.21 & 0.93 & 0.53  \\
-    50\%        & 0.37 & 0.61 & 0.49 & 0.62 & 0.94  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The next part of this scenario is the results from predicting the exact solution of \lccref{eq:sine_derivative} which is \lccref{eq:sine_function}.
-The function values will be computed with the same discretization as the number of modes we used in the training set.
-Once the values are obtained for both functions, the coefficients are computed.
-Then instancing the FourierBasis class with the coefficients of the derivative function, we can create perturbed versions according to the noise levels of the training set.
-Finally, the derivative is used to predict the noise-free antiderivative.
-The results are presented in \lccrefs{table:scenario_1_exact_spectral_metrics,table:scenario_1_exact_function_metrics}.
-For 5\% and 10\% noise levels, the model shows that it has learned the relation.
-However, the 50\% noise level, the model has been unable to predict the results well enough.
-The marked difference in error across all metrics between the 50\% and the lower noise levels is more apparent for this specific exact problem compared to the test sets.
-A clear picture of this can be seen when we compare the sMAPE metric.
-For the test set, the predictions on average results in a value of 1, however, for this exact problem the sMAPE value is 1.4 to 1.7.
-
-\begin{table}[H]
-  \caption{Performance metrics of coefficient prediction of exact antiderivative in scenario 1 by noise level.}\label{table:scenario_1_exact_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    Noise level & MSE   & RMSE & MAE  & sMAPE \\
-    \midrule
-    5\%         & 0.09  & 0.29 & 0.16 & 1.18  \\
-    10\%        & 0.80  & 0.89 & 0.31 & 1.23  \\
-    50\%        & 10.33 & 3.21 & 0.83 & 1.44  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\begin{table}[H]
-  \caption{Performance metrics of evaluated function values of coefficient prediction of exact antiderivative in scenario 1 by noise level.}\label{table:scenario_1_exact_function_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    Noise level & MSE  & RMSE & MAE  & sMAPE \\
-    \midrule
-    5\%         & 0.00 & 0.06 & 0.05 & 0.23  \\
-    10\%        & 0.03 & 0.18 & 0.15 & 0.36  \\
-    50\%        & 0.41 & 0.64 & 0.58 & 1.65  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The predictions of the exact equation is shown in \lccref{fig:antiderivative_exact}.
-Visually, we can see that as the noise level increases, the model predictions become worse.
-Another observation is how the higher the noise level, the more the predicted functions become closer to zero.
-This is explained by the double penalty phenomenon \autocite{lledoScaledependentVerificationPrecipitation2023}.
-The loss function used for LSSVR penalizes the model for predicting a non-zero value that turns out to be wrong compared to predicting a zero value.
-This results in a model with predictions that are close to the mean of the training data.
-
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/antiderivative_exact_input.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:antiderivative_exact_input}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/antiderivative_exact_prediction.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:antiderivative_exact_prediction}
-  \end{subfigure}
-  \caption{(\subref{fig:antiderivative_exact_input}) The perturbed exact input function values from \lccref{eq:sine_derivative}.\ (\subref{fig:antiderivative_exact_prediction}) Prediction of antiderivative from the input function that was perturbed.}\label{fig:antiderivative_exact}
-\end{figure}
-
-For inverse problems, we simply use the same testing set with the labels now used to predict the features.
-The model instances are still the same as before.
-With the implementation shown in \lccref{fig:spectralsvr_inverse_impl}, we run the inverse function for predicting coefficients with 2000 epochs, a learning rate of 0.02, and randomized starting point from a normal distribution multiplied by a factor of 0.05.
-The results of inverse prediction for all three noise levels are shown in \lccref{table:scenario_1_inv_spectral_metrics}.
-These metrics were computed after both the target and predicted input functions are scaled back using the same scaling functions they were scaled down with.
-Because the scales of the input and output functions are different, the absolute metrics are much larger in these results compared to the forward problem results.
-For reference, the target input coefficients on average range from -695.65 to 694.9.
-The relative metrics show that for the lower noise levels, the accuracy is still relatively good.
-However, the values are lower than the values for the forward test.
-The difference with the antiderivative prediction becomes more pronounced with the higher noise levels.
-For the highest noise level, the performance has degraded so far that the predictions are worse than a baseline model from the mean of the target input functions.
-One must also note that despite the much worse results of the other metrics for the highest noise level, at this time we're unable to explain why sMAPE results in roughly the same performance as in the forward problem.
-
-\begin{table}[H]
-  \caption{Performance metrics of coefficient inverse prediction of derivative in scenario 1 by noise level.}\label{table:scenario_1_inv_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrrr}
-    \toprule
-    Noise level & MSE      & RMSE   & MAE    & R\textsuperscript{2}    & sMAPE \\
-    \midrule
-    5\%         & 1739.56  & 41.71  & 26.44  & 0.91  & 0.36  \\
-    10\%        & 3485.10  & 59.03  & 42.19  & 0.76  & 0.52  \\
-    50\%        & 49319.73 & 222.08 & 174.48 & -0.19 & 1.05  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-Next, we have the correlation image and p-matrix for the model of each noise level.
-The results are shown in \lccref{fig:scenario_1_interpretation}.
-Each row in the figure represent the results of a model trained on a different noise level.
-The correlation image for 5\% and 10\% noise show clear lines on the coefficient corresponding to the output coefficient that was sorted.
-We can also see that the negative wave number reflection also being sorted.
-This is because of the reflection that occurs with complex Fourier coefficients for real-valued functions.
-There are other faint vertical lines you are able to see for other input coefficients.
-These faint lines are not sorted like the corresponding coefficients we mentioned before.
-Meaning, while they don't affect the particular output coefficients that were sorted, they do show that there is information embedded in the kernel matrix for these input coefficients.
-However, if we look at the 50\% noise correlation image, even the corresponding coefficient does not show a clear line or gradient.
-The lines are more noisy compared to the other noise levels.
-But the kernel still manages to embed some information.
-The p-matrices show that The model itself is able to still learn some relationship between the input coefficients and the output coefficients.
-For the 5\% and 10\% noise levels, the p-matrices show very clearly the contributions of input coefficients to the output coefficients.
-However, looking at the p-matrix for 50\% noise level, the lower wave numbers show lower contribution of input coefficients to the output coefficients.
-\begin{figure}[H]
-  \begin{adjustwidth}{-0.05\linewidth}{-0.05\linewidth}
-    \centering
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_ci_5.pgf}
-      \end{adjustbox}
-      \caption{Correlation image 5\% noise.}\label{fig:sc1_ci_5}
-    \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_pm_5.pgf}
-      \end{adjustbox}
-      \caption{The p-matrix for 5\% noise.}\label{fig:sc1_pm_5}
-    \end{subfigure}
-    % \\[\baselineskip]
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_ci_10.pgf}
-      \end{adjustbox}
-      \caption{Correlation image 10\% noise.}\label{fig:sc1_ci_10}
-    \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_pm_10.pgf}
-      \end{adjustbox}
-      \caption{The p-matrix for 10\% noise.}\label{fig:sc1_pm_10}
-    \end{subfigure}
-    % \\[\baselineskip]
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_ci_50.pgf}
-      \end{adjustbox}
-      \caption{Correlation image 50\% noise.}\label{fig:sc1_ci_50}
-    \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_pm_50.pgf}
-      \end{adjustbox}
-      \caption{The p-matrix for 50\% noise.}\label{fig:sc1_pm_50}
-    \end{subfigure}
-  \end{adjustwidth}
-  \caption{Correlation image (left column) and p-matrix (right column) for each model trained on a different noise level (row).
-The correlation image was sorted same order the values of the real component of wave number \(k=2\) were sorted in descending order.}\label{fig:scenario_1_interpretation}
-\end{figure}
-
-The final observation we make is how for all the p-matrices the pronounced contribution of the input wave number to their corresponding output wave number.
-This means that the majority of contributions to each output coefficients come from the corresponding input coefficients of the same wave number.
-Our knowledge on how the simple derivative equation for Fourier series relate the coefficients of the derivative function and the antiderivative function is shown in \lccref{eq:derivative_coeff}.
-This aligns with the contributions shown by the p-matrices.
-This confirms that the model is indeed learning the relations that is defined by the derivative equation.
-
-In summary, the model is able to learn the linear relationship defined by the derivative equation.
-This is true even for high noise levels.
-The model also learns the actual relationship between each wave number which is shown in the p-matrix.
-Inverse prediction of the input function is also successfully done for lower noise levels.
-At high noise levels, the noise overwhelms the model.
-
-\subsection{Scenario 2}
-\noindent The second scenario results are presented in two parts which are the coefficient predictions and function value predictions.
-The functions are first preprocessed in order to format them into current and next values in time as discussed in \lccref{sec:data_transformation}.
-The sample pairs are first divided into two for the training and testing sets.
-Each function is then discretized into 200 time steps.
-Then, the features are put together as the coefficients of the solution and forcing term at the current time step.
-The labels are the solution at the next time step.
-Since there is too much data to fit into memory all at once at the end of this process, we randomly sample the feature and label pairs.
-This result in a maximum of 8000 samples for the training set and 2000 samples for the testing set.
-As mentioned in \lccref{sec:data_transformation}, the training features are used to fit a scaling function.
-And then, all features are scaled using the fitted scaling function.
-
-The coefficient value predictions are shown in \lccref{table:scenario_2_spectral_metrics}.
-The RBF kernel parameter computed from the data is once again the same for all versions of the dataset with a value of 5.66.
-The testing metrics show that the performance of the model vary with the viscosity value \(\nu \).
-Starting with the inviscid Burgers' equation, with \(\nu=0\), the model performs the best with a close second from the model for the \(\nu = 0.01 \) dataset version.
-The function value evaluated from the predictions is shown in \lccref{table:scenario_2_function_metrics}.
-The metrics across the board shows that the function value relative metrics are slightly better compared to the coefficients.
-Comparing the absolute metrics for the same table, we see the same general trend that the higher viscosity show the model performing worse.
-
-\begin{table}[H]
-  \caption{Performance metrics of coefficient prediction of next time step in scenario 2 by viscosity.}\label{table:scenario_2_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    0.0      & 3.46e-04 & 1.86e-02 & 1.24e-02 & 0.79 & 0.65  \\
-    0.01     & 3.56e-04 & 1.89e-02 & 1.27e-02 & 0.78 & 0.67  \\
-    0.1      & 9.17e-04 & 3.03e-02 & 2.32e-02 & 0.46 & 1.08  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\begin{table}[H]
-  \caption{Performance metrics of function values evaluated from coefficient prediction of next time step in scenario 2 by viscosity.}\label{table:scenario_2_function_metrics}
-  \centering
-  \begin{tabular}{lrrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    0.0      & 5.58e-05 & 7.47e-03 & 5.89e-03 & 0.82 & 0.70  \\
-    0.01     & 5.74e-05 & 7.58e-03 & 6.01e-03 & 0.81 & 0.71  \\
-    0.1      & 1.58e-04 & 1.26e-02 & 9.98e-03 & 0.51 & 1.04  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The testing results are complimented with a rollout experiment.
-The results from the rollout are shown in \lccref{fig:scenario_2_rollout}.
-The rollout starts from time \(t=0\).
-In all the plots, this is at the bottom.
-We have included this initial condition in the plots.
-From this initial condition in combination with the forcing term at the initial time step, the model predicts the first time step solution.
-The model then uses the predicted solution combined with the corresponding forcing term to predict the second time step.
-To see how well the model is performing relative to the actual target values, we compute the difference between the two as shown in \lccrefs{fig:sc2_rollout_diff_0.0,fig:sc2_rollout_diff_0.01,fig:sc2_rollout_diff_0.1}.
-Observe that errors are introduced relatively early around time \(t=1\).
-However, the model rollout stays stable until the end despite this error.
-This results in the model being able to finish the rollout for this sample.
-\begin{figure}[H]
-  \centering
-  \begin{adjustwidth}{-0.1\linewidth}{-0.1\linewidth}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_target_0.0.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.0\)}\label{fig:sc2_rollout_target_0.0}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_pred_0.0.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.0\)}\label{fig:sc2_rollout_pred_0.0}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_diff_0.0.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.0\)}\label{fig:sc2_rollout_diff_0.0}
-    \end{subfigure}
-    \\[0.7\baselineskip]
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_target_0.01.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.01\)}\label{fig:sc2_rollout_target_0.01}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_pred_0.01.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.01\)}\label{fig:sc2_rollout_pred_0.01}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_diff_0.01.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.01\)}\label{fig:sc2_rollout_diff_0.01}
-    \end{subfigure}
-    \\[0.7\baselineskip]
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_target_0.1.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.1\)}\label{fig:sc2_rollout_target_0.1}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_pred_0.1.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.1\)}\label{fig:sc2_rollout_pred_0.1}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_diff_0.1.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.1\)}\label{fig:sc2_rollout_diff_0.1}
-    \end{subfigure}
-    % \\[0.7\baselineskip]
-  \end{adjustwidth}
-  \caption{The rollout predictions for one of the test function. The difference is calculated as the targets subtracted by the predictions.}\label{fig:scenario_2_rollout}
-\end{figure}
-
-Another observation we can see is that the difference between the target and rollout predictions is much more pronounced for lower viscosity values.
-This result is aligned with metrics shown in \lccrefs{table:scenario_2_rollout_spectral_metrics,table:scenario_2_rollout_function_metrics}.
-The absolute metrics show that the models are performing several times worse in rollout compared to the single time step tests shown in \lccrefs{table:scenario_2_spectral_metrics,table:scenario_2_function_metrics}.
-This seems to be the same challenge that traditional solvers also face with the shocks that may be present with lower viscosity values.
-This means that for rollout scenarios, the model has a much harder time with lower viscosity values.
-\begin{table}[H]
-  \caption{Performance metrics of coefficient rollout in scenario 2 by viscosity.}\label{table:scenario_2_rollout_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & sMAPE \\
-    \midrule
-    0.0      & 2.91e-01 & 5.40e-01 & 4.07e-01 & 0.90  \\
-    0.01     & 1.61e-01 & 4.01e-01 & 2.86e-01 & 0.75  \\
-    0.1      & 1.70e-01 & 4.12e-01 & 3.02e-01 & 0.81  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-\begin{table}[H]
-  \caption{Performance metrics of function values evaluated from coefficient rollout in scenario 2 by viscosity.}\label{table:scenario_2_rollout_function_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & sMAPE \\
-    \midrule
-    0.0      & 5.81e-02 & 2.41e-01 & 1.89e-01 & 1.04  \\
-    0.01     & 3.17e-02 & 1.78e-01 & 1.40e-01 & 0.94  \\
-    0.1      & 2.91e-02 & 1.71e-01 & 1.33e-01 & 0.92  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The exact function \cref{eq:burgers_exact_solution} is computed for each viscosity value.
-The discrete Fourier transform of the values are then used for doing rollout with the model.
-For the forcing term, we just use a constant function with a value of zero.
-The rollout predictions are shown in \lccref{fig:scenario_2_interpretation}.
-The model is not successful in the rollout for the inviscid equation and for the viscosity of \(\nu=0.01\).
-Both of these cases, the model produces too much error that the original function is no longer recognizable in the predictions.
-For the higher viscosity value of \(\nu=0.1\) the rollout produces a recognizable prediction.
-The error stays to about half the maximum function value.
-We do see some more noticeable error in the flatter parts of the function.
-The error also take a very similar shape across the different viscosity values.
-Since we essentially used the same solutions for training the model for each viscosity, the similarity in error means that it can be alleviated with more diverse training samples.
-The error for the flatter functions may also be alleviated by including similar flatter functions during training.
-\begin{figure}[H]
-  \centering
-  \begin{adjustwidth}{-0.1\linewidth}{-0.1\linewidth}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_target_0.0.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.0\)}\label{fig:sc2_exact_target_0.0}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_pred_0.0.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.0\)}\label{fig:sc2_exact_pred_0.0}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_diff_0.0.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.0\)}\label{fig:sc2_exact_diff_0.0}
-    \end{subfigure}
-    \\[0.7\baselineskip]
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_target_0.01.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.01\)}\label{fig:sc2_exact_target_0.01}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_pred_0.01.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.01\)}\label{fig:sc2_exact_pred_0.01}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_diff_0.01.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.01\)}\label{fig:sc2_exact_diff_0.01}
-    \end{subfigure}
-    \\[0.7\baselineskip]
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_target_0.1.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.1\)}\label{fig:sc2_exact_target_0.1}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_pred_0.1.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.1\)}\label{fig:sc2_exact_pred_0.1}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_diff_0.1.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.1\)}\label{fig:sc2_exact_diff_0.1}
-    \end{subfigure}
-    % \\[0.7\baselineskip]
-  \end{adjustwidth}
-  \caption{The rollout predictions for one of the exact function in \lccref{eq:burgers_exact_solution}.
-The difference is calculated as the targets subtracted by the predictions.}\label{fig:scenario_2_exact}
-\end{figure}
-
-The metrics for the exact rollout further solidifies our observations from the plots.
-The metrics are shown in \lccrefs{table:scenario_2_exact_spectral_metrics,table:scenario_2_exact_function_metrics}.
-While the absolute metrics are low, this is mostly due to the maximum function values of the exact function also being pretty low.
-The relative metric sMAPE shows a much clearer picture.
-As expected, the inviscid prediction is pretty much just error.
-The next result, for viscosity \(\nu=0.01\), is better.
-This seems to be from the slight conformance to the target.
-The plots for this viscosity show that the prediction contains \enquote{shapes} similar to the target despite the scale not being close to the target.
-Finally, the highest viscosity level results show the best performance.
-Despite the good performance in the higher detail areas of the function, the error from the flatter areas overwhelm the metrics due to its larger portion of the function.
-\begin{table}[H]
-  \caption{Performance metrics of coefficient rollout of exact solution in scenario 2 by viscosity.}\label{table:scenario_2_exact_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & sMAPE \\
-    \midrule
-    0.0      & 2.16e-02 & 1.47e-01 & 1.08e-01 & 2.00  \\
-    0.01     & 1.32e-02 & 1.15e-01 & 6.37e-02 & 1.58  \\
-    0.1      & 2.83e-03 & 5.32e-02 & 4.00e-02 & 1.50  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-\begin{table}[H]
-  \caption{Performance metrics of function values evaluated from coefficient rollout of exact solution in scenario 2 by viscosity.}\label{table:scenario_2_exact_function_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & sMAPE \\
-    \midrule
-    0.0      & 4.16e-03 & 6.45e-02 & 4.56e-02 & 2.00  \\
-    0.01     & 3.23e-03 & 5.68e-02 & 4.94e-02 & 1.73  \\
-    0.1      & 3.86e-04 & 1.97e-02 & 1.62e-02 & 1.47  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The correlation image and p-matrix for each viscosity can be seen in \lccref{fig:scenario_2_interpretation}.
-Analyzing the correlation images first, we see that some columns are sorted in correlation to how the samples are sorted based on the real component of the 4th output wave number.
-For the inviscid equation, this correlation is the strongest with multiple columns exhibiting the correlation.
-The highest and visually most sorted values are from the forcing term portion of the inputs.
-Different wave numbers in the inputs are also sorted differently, this indicates an inverse correlation.
-For a higher viscosity of \(\nu=0.01\), a weaker correlation is still present.
-
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_ci_0.0.pgf}
-    \end{adjustbox}
-    \caption{Correlation image \(\nu=0.0\).}\label{fig:sc2_ci_0.0}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_pm_0.0.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix for \(\nu=0.0\).}\label{fig:sc2_pm_0.0}
-  \end{subfigure}
-  % \\[-0.7\baselineskip]
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_ci_0.01.pgf}
-    \end{adjustbox}
-    \caption{Correlation image \(\nu=0.01\).}\label{fig:sc2_ci_0.01}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_pm_0.01.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix for \(\nu=0.01\).}\label{fig:sc2_pm_0.01}
-  \end{subfigure}
-  % \\[-0.7\baselineskip]
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_ci_0.1.pgf}
-    \end{adjustbox}
-    \caption{Correlation image \(\nu=0.1\).}\label{fig:sc2_ci_0.1}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_pm_0.1.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix for \(\nu=0.1\).}\label{fig:sc2_pm_0.1}
-  \end{subfigure}
-  \caption{Correlation image (left column) and p-matrix (right column) for each model trained on a different viscosity (row).
-The correlation image was sorted same order the values of the real component of wave number \(k=2\) were sorted in descending order.}\label{fig:scenario_2_interpretation}
-\end{figure}
-
-Once we get to the highest viscosity, while the order is still present, we see a more random arrangement of the correlation image values.
-This observation and the lower scores can both be explained by the level of temporal discretization.
-This is the same issue we encounter when we use some traditional methods for higher viscosity values with the same time step for lower viscosity values \autocite{kassamFourthOrderTimeSteppingStiff2005,seydaogluNumericalSolutionBurgers2016}.
-The issue arises in stiff differential equations.
-Stiff differential equations refer to the presence of a rapidly varying component.
-We can see that the larger amplitudes of high frequency components in the forcing term to represent the rapidly varying components as shown in \lccrefs{fig:burgers_forcing_0.0,fig:burgers_forcing_0.01,fig:burgers_forcing_0.1}.
-Traditionally, stiff equations would require specific numerical methods purpose built to efficiently solve the problem.
-Otherwise, the using a solver like FDM would require much finer time steps than the one we are using here.
-
-The p-matrix shows the difference in contributions of both input functions.
-For the inviscid equation, the contributions mainly come from the forcing term.
-The current solution contributes a smaller amount in comparison.
-There is similarity with the antiderivative p-matrices in this case.
-The contributions to each output wave number mainly come from input coefficients with the same wave number.
-However, there is a noticeable contribution from other wave numbers too unlike the antiderivative case.
-The biggest contribution from the current solution is the constant/bias term.
-For higher viscosity values, notice that the contribution of the previous solution increases.
-The increase is more pronounced for higher frequencies.
-This aligns with the quadratic scaling from the wave number on the coefficients \autocite{canutoSpectralMethodsEvolution2007}.
-The p-matrix for lower viscosity values show more structured contribution of other wave numbers in comparison to the higher wave numbers.
-This structure comes in the form of a grid pattern.
-For the real components of the output, the contribution of other wave numbers oscillate between higher and lower values depending on whether the input component is real or not.
-The imaginary output components on the other hand have a more constant contribution across the input components.
-The contribution once again become more pronounced the higher the absolute value of the wave number.
-
-To summarize, Low viscosity values are a challenge to the model as with traditional methods.
-Despite that, this scenario confirms the model's ability to learn the nonlinear relationship defined by the Burgers' equation.
-The model is also able to stay stable with a relatively large time step.
-This concludes the synthetic data portion of the study.
-
-\subsection{Scenario 3}
-\noindent This final scenario tests the model on a much more complex dataset.
-As said previously, this dataset, which is computed using real observations of Earth's weather system, will be used to represent the model learning a very complex system with many unknown contributing variables.
-For our case, this means the data used will be limited to the 2-meter temperature.
-The anomaly is computed by subtracting the climatology from the corresponding day of years and hours of the atmospheric state.
-For example, the temperature on the 6\textsuperscript{th} of January 1998 at 18:00 UTC is subtracted with the average temperature for the 6\textsuperscript{th} day of the year at 18:00 hour UTC\@.
-For any anomaly predictions, the corresponding atmospheric state can simply be computed as the inverse process described before by adding the climatology to the predicted anomaly.
-
-The preprocessing of the data is carried out in the same manner as the Burgers' equation experiments.
-The difference being that for the features we only include the current anomaly of the atmosphere and there are no forcing terms.
-The targets are the future anomaly of the atmosphere.
-The reason for choosing to train and predict the anomaly instead of the state valued themselves is to avoid the model from just learning the obvious periodicity that exists in weather such as the day-night cycle or the seasons.
-Next, Both the current anomaly and future anomaly are Fourier transformed to their 2-dimensional coefficients.
-This process is done for both the training and testing set.
-Once the features for both are processed, we fit the standard scaling function on the training features.
-Using this fitted scaling function, both the training and testing features are scaled to a mean of 0 and standard deviation of approximately 1.
-
-The testing results are shown in \lccrefs{table:sc3_test_anomaly_metrics,table:sc3_test_state_metrics}.
-To put the absolute metrics into context, the median test state coefficient' maximum absolute value is \num{569364.25}.
-With this information, an RMSE value of 64.72 is relatively low error.
-The relative metric sMAPE also agrees with this, with a value of 0.76.
-The function values show that the model on average has an error of around 2 degrees kelvin or Celsius.
-This is again relatively small for the range of temperatures on Earth which span roughly 120 degrees kelvin across the historical maxima and minima.
-From existing knowledge of the problem, we know these values for the metrics are mainly due to the periodicity of atmospheric states.
-When we look at the anomaly metrics, the model is still able to learn some things and perform slightly better than a model of anomaly averages.
-However, since the median maximum absolute value for the state coefficients is \num{1155.14}, the error rate is not as good as the state predictions.
-\begin{table}[H]
-  \caption{Performance metrics of anomaly coefficient prediction for scenario 3.}\label{table:sc3_test_anomaly_metrics}
-  \centering
-  \begin{tabular}{lrrrrr}
-    \toprule
-                   & MSE     & RMSE  & MAE   & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    spectral       & 4189.16 & 64.72 & 32.47 & 0.35 & 1.19  \\
-    function value & 4.09    & 2.02  & 1.44  & 0.09 & 1.24  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\begin{table}[H]
-  \caption{Performance metrics of state coefficient prediction for scenario 3.}\label{table:sc3_test_state_metrics}
-  \centering
-  \begin{tabular}{lrrrrr}
-    \toprule
-                   & MSE     & RMSE  & MAE   & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    spectral       & 4189.16 & 64.72 & 32.47 & 0.56 & 0.74  \\
-    function value & 4.09    & 2.02  & 1.44  & 0.75 & 0.01  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-The p-matrix and correlation image is shown in \lccref{fig:sc3_interpretation}.
-For the correlation image, we see that most wave numbers are correlated or inversely correlated with the outputs.
-The strongest correlation is shown by the features of the same wave number as the sorted target.
-This is an indication that the equations involved may be nonlinear.
-If we look at the p-matrix however, it seems very flat save a faint diagonal line from the top left to the bottom right.
-The values of the p-matrix are also extremely high.
-With the \enquote{flatness} we see, this is indicative of strong contributions by a few inputs.
-
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_ci.pgf}
-    \end{adjustbox}
-    \caption{The correlation image.}\label{fig:sc3_ci}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_pm.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix.}\label{fig:sc3_pm}
-  \end{subfigure}
-  % \\[-0.7\baselineskip]
-  \caption{Correlation image and p-matrix for WeatherBench 2 model.
-The correlation image was sorted same order the values of the real component of wave number \((k_{longitude}=0, k_{latitude}=2)\) were sorted in descending order.}\label{fig:sc3_interpretation}
-\end{figure}
-
-To see more details of the p-matrix, we show a zoomed in version in \lccrefs{fig:sc3_pm_zoom1,fig:sc3_pm_zoom2}.
-The relationships are much more clear between features and outputs that do not share the same wave number.
-The coefficients with the same longitude wave numbers appear in the same \enquote{square} shape.
-Within the \enquote{square}, coefficients close to the same latitude wave number show much stronger contribution.
-For low wave numbers, shown in \lccref{fig:sc3_pm_zoom1}, the contribution is spread over more latitude wave numbers.
-The higher wave numbers, on the other hand, has the contributions much more concentrated on the coefficients with the same latitude wave numbers.
-In addition, the value of contribution differ by an order of magnitude with lower longitude wave numbers having higher maximum contribution.
-This observation suggests that the nonlinearity and magnitude are inversely proportional to the absolute value of the longitude wave number.
-This is in contrast to when we discussed the forcing term for our Burgers' equation scenario.
-The low frequencies in longitude may indicate that the model has learned some feature of the anomaly that is specific to different times of day.
-This is because the lowest longitudinal wave number would correspond to when different parts of the world is in nighttime or in daytime.
-Other possible explanations may be due to the fact that the earth more closely resemble a sphere compared to the toroidal shape that the 2-dimensional Fourier transform assumes.
-This would result in the representation latitude-wise being distorted.
-For this issue, the use of spherical harmonics may be a better fit to rule out the possibility of any distortions the Fourier transform may introduce.
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_pm_zoom1.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix zoomed in to \((k_{longitude}=\{0, 1, 2\}, k_{latitude}=[-16, 16))\).}\label{fig:sc3_pm_zoom1}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_pm_zoom2.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix zoomed in to \((k_{longitude}=\{\phantom{-}31,-32,\phantom{-}32\}, k_{latitude}=[-16, 16))\).}\label{fig:sc3_pm_zoom2}
-  \end{subfigure}
-  \caption{The p-matrix of the WeatherBench 2 models zoomed in to specific wave numbers.}\label{fig:sc3_pm_zoomed}
-\end{figure}
-
-The predictions from test features are processed through the Fourier inverse transform to evaluate the function values.
-The direct predictions, which is the anomaly, is shown in \lccref{fig:sc3_anomaly_predictions}.
-The model seem to be predicting less extreme values that are noticeable in the target.
-Specifically areas over North America, Central Asia, and parts of Antarctica show lower temperature anomaly than expected.
-We also loose detail in areas which should have a lower anomaly such as northern areas of Africa, Greenland, and South Asia.
-The lack of detail seems to be a problem of underestimation.
-We believe this is caused by the so-called \enquote{double penalty} issue caused by the loss function used for the LSSVR \autocite{lledoScaledependentVerificationPrecipitation2023}.
-The predictions tend to be closer to the mean of the data to avoid the extra penalty from a wrong prediction with a high value.
-One way to allow for finer details that are less accurate is to penalize the higher frequency wave numbers less compared to the lower frequency wave numbers.
-For our case this means the LSSVR for each output will have their regularization parameter decreased to allow the model to focus less on the errors for higher frequencies.
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    % \centering
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_anom_pred.pgf}
-    \end{adjustbox}
-    \caption{Predicted 2-meter temperature anomaly.}\label{fig:sc3_anomaly_pred}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    % \centering
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_anom_target.pgf}
-    \end{adjustbox}
-    \caption{Target 2-meter temperature anomaly.}\label{fig:sc3_anomaly_target}
-  \end{subfigure}
-  \caption{2-meter temperature anomaly prediction for the 1\textsuperscript{st} of January 2020 at 6:00 UTC based on the previous anomaly at 0:00 UTC.}\label{fig:sc3_anomaly_predictions}
-\end{figure}
-
-The state predictions which is obtained by adding the climatology to the predicted anomaly is shown in \lccref{fig:sc3_state_predictions}.
-This further shows areas of discrepancy between the prediction and the target.
-The area in the South Pacific show that the target has a higher difference temperature compared to the prediction.
-This smoothness in the prediction is easier to see for areas in the ocean.
-Many sharp features are lost and the state prediction start to resemble averaged view of the climatology.
-We must also take into account that the model only used temperature distribution data.
-Other pieces of information we know to be crucial to weather prediction such as wind speed or pressure was not included in the inputs.
-With this in consideration the model was still able to learn some relationships defined by governing equations of weather.
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    % \centering
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_state_pred.pgf}
-    \end{adjustbox}
-    \caption{Predicted 2-meter temperature.}\label{fig:sc3_state_pred}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    % \centering
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_state_target.pgf}
-    \end{adjustbox}
-    \caption{Target 2-meter temperature.}\label{fig:sc3_state_target}
-  \end{subfigure}
-  \caption{2-meter temperature prediction for the 1\textsuperscript{st} of January 2020 at 6:00 UTC based on the previous anomaly at 0:00 UTC.}\label{fig:sc3_state_predictions}
-\end{figure}
-
-The results of our experiments show that the proposed model has the ability to learn the relationships that PDEs and other governing equations define.
-The interpretation methods for support vector regression that we used, namely the correlation image and p-matrix developed by \textcite{ustunVisualisationInterpretationSupport2007}, allows us to confirm what the model has learned.
-In the case of the WeatherBench2 model, it has also allowed us to glean some insight into some mechanisms that the model has learned.
-This information was used to verify the learned relationships for the simple derivative equation.
-Together with the performance metrics on three different problems, we have shown the proposed model to be a viable tool for situations with limited knowledge and a need for some level of interpretability of the model.

### 2025-01-14 article/article.tex
fix labels, fix problem with graphics path and suround with curly braces, start technical document

@@
   \affiliation[upi]{organization={Department of Computer Science Education Universitas Pendidikan Indonesia},%Department and Organization
-    addressline={Jl. Dr. Setiabudi No.229},
+    addressline={Jl. Dr.\ Setiabudi No.229},
     postcode={40154},
@@
     %% keywords here, in the form: keyword \sep keyword
-    Operator Learning \sep LSSVR \sep PDE
+    Operator Learning \sep{} LSSVR \sep{} PDE
     % keyword one \sep keyword two
@@
     %% or \MSC[2008] code \sep code (2000 is the default)
-    \MSC 35-04 \sep 68T99
+    \MSC{} 35{-}04 \sep{} 68T99
   \end{keyword}
@@
 
+To test the generalization capabilities of the model, we use the sine function with a period of one shown in \lccref{eq:sine_function}.
+The derivative is simply \lccref{eq:sine_derivative}.
+The functions are discretized and noise is added.
+Finally, the values go through the same transformations to become feature and target coefficients.
+\begin{align}
+  f(t) & = 2\pi \cos\left(2\pi t\right)\label{eq:sine_derivative} \\
+  u(t) & = \sin\left(2\pi t\right)\label{eq:sine_function}
+\end{align}
+
 The predictions of the exact equation is shown in \lccref{fig:antiderivative_exact}.
@@
 
+To test the generalization capability of the model on other function families, we use an exact solution provided in the literature shown in \lccref{eq:burgers_exact_solution} \citep{woodExactSolutionBurgers2006,wazwazPartialDifferentialEquations2010,bentonTableSolutionsOnedimensional1972}.
+\begin{equation}
+  u(x,t) = \frac{2\nu\pi e^{-\pi^2\nu t}\sin(\pi x)}{a+e^{-\pi^2\nu t}\cos(\pi x)} \label{eq:burgers_exact_solution}
+\end{equation}
+
 The exact function \cref{eq:burgers_exact_solution} is computed for each viscosity value.
@@
 This is done using a model that learns in the Fourier domain with Fourier Transforms and Inverse Transform bridging the Fourier domain and the physical domain.
-  \item Interpretation of the proposed model can be done to a certain extent using two tools which are the correlation image and p-matrix developed by \citet{alisationInterpretationSupport2007}.
+  \item Interpretation of the proposed model can be done to a certain extent using two tools which are the correlation image and p-matrix developed by \citet{ustunVisualisationInterpretationSupport2007}.
 This interpretation shows that the model correctly attributes the relationship of the input coefficients to the output coefficients.
@@
 These steps will contribute to advancing computational approaches for SciML-based modelling and establish the proposed framework as a versatile tool in this domain.
+
+\input{apendix.tex}
+
 \bibliographystyle{elsarticle-harv}

### 2025-01-14 skripsi/abstrak.tex
fix labels, fix problem with graphics path and suround with curly braces, start technical document

@@
 \clearpage
-\phantomsection
+\phantomsection{}
 \addcontentsline{toc}{chapter}{ABSTRAK}
@@
 \textbf{\penulis}\\
-\textbf{NIM: \nim}\\[2em]
+\textbf{NIM:\@\nim}\\[2em]
 \end{center}
@@
 \noindent Model numerik sebuah sistem merupakan bagian penting dari ilmu pengetahuan dan \textit{engineering}.
-Penggunaan \textit{Machine Learning} (ML) dalam ruang ini untuk pembelajaran operator menyediakan alternatif sebagai \textit{data-driven surrogates}.
-\textit{Fourier Transform} menyediakan komponen kunci untuk mempelajari hubungan antara suatu fungsi dan turunannya.
+Penggunaan \textit{Machine Learning} (ML) dalam ruang ini untuk pembelajaran operator menyediakan alternatif sebagai \textit{data-driven surrogates}.\ \textit{Fourier Transform} menyediakan komponen kunci untuk mempelajari hubungan antara suatu fungsi dan turunannya.
 Berdasarkan \textit{Spectral Neural Operators (SNO)}, kami mengusulkan kerangka kerja berbasis \textit{Support Vector Machine (SVM)} untuk mempelajari persamaan dasar yang mengatur suatu sistem berdasarkan data.

### 2025-01-14 technical_doc/design.tex
fix labels, fix problem with graphics path and suround with curly braces, start technical document

--- 2025-01-06 skripsi/chapter4.tex
@@
-% !TEX root = ./skripsi.tex
-\chapter{RESULTS AND DISCUSSION}
-\noindent This chapter will elaborate on the results of the study and relevant phases for analysis.
-This chapter is organized into five sections which are the results of data generation, data retrieval, design of computational model, implementation of computational model, experimental scenarios, and the experiments themselves.
-
-\section{Data Generation}\label{sec:data_generation}
-\noindent This study uses two data acquisition approaches.
-The first approach which is discussed in this section is data generation.
-This process involves manufacturing data randomly in such a way that they obey the PDEs to be modeled.
-The generated data consists of features and labels.
-These features and labels in the context of PDEs are parameters and the solution of the PDEs, respectively.
-The PDEs enforce a relationship between parameters and the solution.
-This relationship is implicitly encoded into the features and labels, which is what machine learning models can learn.
-Because the solution and parameters to PDEs are functions and there are many kinds with different properties, generating all the different kinds of functions is a difficult task.
-This is why this study focuses on Fourier functions.
-This means that out of the space of all functions \(F \) which include categories such as polynomials \(f\left(x\right)=a_{n}x^n+\cdots+a_1x+a_0\) where \(f\in F\), and \(a_n\) are constants; we only consider the subset of functions \(U \subset F\) which are of the form \(u\left(x\right)=\sum_{k}^{m}c_k e^{2\pi i k \frac{x}{P}}\).
-
-Using the subset of Fourier functions has several benefits which has motivated the choice.
-First these functions are characterized purely by their coefficients \(c_k\), meaning there is no need to store discretized values which potentially saves space and computation.
-The second benefit is that other functions such as polynomials can be approximated by them using the Fourier transform.
-This means that despite limiting the set of functions to Fourier functions, the behavior of PDEs with other sets of functions can be approximated to a certain extent.
-The final benefit is the mature ecosystem around these functions which include fast algorithms for the Fourier transform and even numerical approaches for solving known PDEs like the previously mentioned spectral method.
-In summary the generated data consists of features and labels which are Fourier functions implicitly defining the relationship enforced by a PDE and scenario.
-After establishing the kind of functions to be used in dataset generation, the process can proceed.
-There are 4 steps involved in the data generation:% TODO: add reference to second chapter for spectral method, fourier transform, and other external concepts.
-\begin{enumerate}
-  \item Scenario and PDE Determination:
-        The first step of data generation is determining the scenario related to the PDE or governing equations.
-First, the PDE to be modeled is determined based on the goals of the dataset.
-Then, one or more of the parameters is chosen to predict the solution.
-The chosen parameters will be called the input functions and the solution will be called output functions from here on.
-The second part of the scenario is the domain or more simply the physical space occupied by the system to be modeled.
-The domain will be used to compute the function values in relation to the physical space from coefficients of Fourier functions.
-  \item Parameter Determination:
-        The second step is determining all parameters other than that input parameter based on the scenario and governing equation.
-These parameters may be coefficients such as material properties like density or viscosity, or forcing terms which model external influence on the system like a heat source in the case of the heat equation.
-Depending on the parameters, solutions of PDEs may behave very differently, such as the appearance of discontinuities in the solution to low viscosity Burgers' equation.
-Because of this, the choice of parameters is guided by what the dataset seeks to do.
-  \item Random Coefficient Generation:
-        The third step of data generation is randomly generating the solutions for the chosen equation.
-Generating random functions in the space of Fourier functions exploits the fact that the coefficients characterize the function completely.
-By randomly assigning coefficients \(c_k\), many functions can be generated randomly with very little cost.
-Since the coefficients need to be complex numbers as in \lccref{eq:complex_number}, both real and imaginary components are generated independently by assigning a random value to each component for each wave number \(k\).
-They are then put together again into complex numbers.
-
-        Since only real functions are of interest in this study, the generation cost can be approximately halved.
-This is because for real functions the coefficients for negative wave numbers \(k\) are complex conjugate of the positive wave numbers.
-This means that once the positive coefficients are generated, one only needs to compute their complex conjugate and concatenate the result with the coefficients of positive wave numbers.
-For dimensions higher than one, a simpler approach is used.
-The coefficients are generated for all wave numbers including the negative ones.
-The inverse Fourier transform is computed and this results in complex functions.
-The real components of these functions are kept and the Fourier transform is applied to get the coefficients of the real functions.
-Finally, these generated coefficients then be used with the basis functions as input functions.
-        % TODO: add diagram for generating real functions, the mirroring process too
-  \item Forcing Term Computation:
-        Finally, in order to ensure that the generated solution and chosen parameters satisfy the equation, the forcing term is computed as the residual of the equation of interest with the parameters that was previously determined.
-This computation is done using the spectral method.
-  \item Function Value and Noise Computation:
-        The generated solution and forcing functions are labeled as input and output functions.
-The values of both functions in the domain can then be computed using the scenario determined in the first step.
-Once all coefficients are generated, the function values are computed with an inverse Fourier transform.
-The real component of the function values are retained, and the imaginary component are zeroed out.
-Noise is added to the function values here as needed.
-The processed function values are then converted back into coefficients using a Fourier transform.
-This processing is necessary to ensure that the coefficients are only describing the real function.
-
-\end{enumerate}
-
-These four steps are the general processes involved in generating datasets for this study. Further specifics of the generation process of each dataset is explained in their respective subsections.
-
-\subsection{Data Generation: Anti-derivative}
-\noindent The first dataset is a simple one dimensional derivative.
-This was chosen as a simple proof of concept of the ability to solve a differential equation.
-The equation is related to many real-world problems such as acceleration and speed.
-One can imagine a train in an ideal world where acceleration is directly translated into speed.
-When the train accelerates at time \(t \) by some amount \(a \), we can expect the train to have some speed \(u \).
-In this ideal world, the relationship between speed and acceleration can be modeled with a simple differential \lccref{eq:derivative}.
-This scenario is found in many real systems albeit often with many more details such as different components of acceleration from friction, drag, gravity, and other factors.
-As previously mentioned in \lccref{sec:data_generation}, both velocity \(u \) and acceleration \(a \) are modeled with Fourier series in \lccrefs{eq:fourier_speed,eq:fourier_acceleration} respectively.
-\begin{align}
-  \dv{u\left( t \right)}{t} & = a\left( t \right) \label{eq:derivative}                         \\
-  u\left( t \right)         & = \sum_{k} \hat{u}_k e^{2\pi ikt} \label{eq:fourier_speed}        \\
-  a\left( t \right)         & = \sum_{k} \hat{a}_k e^{2\pi ikt} \label{eq:fourier_acceleration}
-\end{align}
-The domain of the scenario is a two-hour time window.
-This number was chosen because it is around the ideal length of travel time on high speed rail in comparison to air travel and car travel \autocite{givoniDevelopmentImpactModern2006,wangEfficiencySpatialEquity2019,wrro2236}.
-This is the first step in generating this dataset.
-
-In the second step, as the derivative \lccref{eq:derivative} does not contain any parameters other than the acceleration which is the input parameter, there are no other parameters to determine.
-Therefore, the data generation process proceeds to generating coefficients for the speed functions \(\hat{u} \).
-The coefficients are assigned randomly from a Gaussian distribution with a mean of zero and standard deviation of one.
-This choice was made such that most wave numbers will have a coefficient of close to zero leaving a sparse set of wave numbers to mostly affect the resulting function.
-In total, 5000 unique functions are generated with 100 complex coefficients each.
-
-In the third step, the output function coefficients are computed.
-To find the relation between \(\hat{u}_k \) and \(\hat{a}_k \), we need to find substitutes for each term in \lccref{eq:derivative}.
-To do this, we take the derivative of \lccref{eq:fourier_speed} which result in \lccref{eq:fourier_series_derivative}.
-Using this we can substitute the terms in \lccref{eq:derivative} with \lccrefs{eq:fourier_series_derivative,eq:fourier_acceleration} giving \lccref{eq:example_spectral_method_fourier_substituted}.
-Finally, after some algebraic manipulation we obtain the relationship between the input \(a^*\) and output function \(u^*\) in terms of their coefficients in \lccref{eq:derivative_coeff}.
-One also needs to choose the integration constant \(\hat{u}_{0}\) because at \(k=0\) \lccref{eq:derivative_coeff} becomes a division by zero.
-\begin{align}
-  \dv{u\left( x \right)}{x}                                    & = \sum_{k} \hat{u}_k\times \left( 2\pi ik \right) e^{2\pi ikx} \label{eq:fourier_series_derivative} \\
-  \sum_{k} \hat{u}_k\times \left( 2\pi ik \right) e^{2\pi ikx} & = \sum_{k} \hat{a}_k e^{2\pi ikx} \label{eq:example_spectral_method_fourier_substituted}            \\
-  \hat{u}_k                                                    & = \hat{a}_k / \left( 2\pi ik \right) \label{eq:derivative_coeff}
-\end{align}
-
-In the final step, using randomly generated values of \(\hat{a}_k\), the corresponding values of \(\hat{u}_k\) are computed with \lccref{eq:derivative_coeff}.
-These coefficients are then used to compute the function values inside the domain.
-The two-hour time window is represented by a grid of 500 discrete points.
-With the coefficients and evaluation points ready, the function values are computed using \lccrefs{eq:fourier_speed,eq:fourier_acceleration}.
-Next, noise is added to the function values in order to motivate models learning on the dataset to generalize on noise.
-To also allow evaluation of how well the model performs with different levels of noise, the samples are duplicated into three copies for each high, medium and low noise levels.
-The function values of each copy is perturbed with noise from a Gaussian distribution with zero mean and standard deviation of some percentage of the average function value standard deviation.
-The percentages of each high, medium, and low noise levels are 5, 10, and 50 percent.
-The perturbed function values are then transformed back into their coefficients.
-An example generated function and its different perturbed versions is shown in \lccref{fig:antiderivative_noise_levels}.
-The horizontal axis indicates time which is displayed in units of hours.
-The vertical axis indicates velocity in abstract units.
-
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/antiderivative_clean_perturbed_solution.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:antiderivative_noise_levels}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/antiderivative_clean.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:antiderivative}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/antiderivative_derivative_clean.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:derivative}
-  \end{subfigure}
-  \caption{(\subref{fig:antiderivative_noise_levels}) A generated function with no noise (clean), low noise level (5\%), medium noise level (10\%), and high noise levels (50\%).\ (\subref{fig:antiderivative}) Antiderivative function with no noise.\ (\subref{fig:derivative}) Derivative function with no noise.}
-\end{figure}
-% TODO: interesting note that model trains better on function to coefficient task when the antiderivative is computed from the randomly generated derivative than if the derivative is computed from the randomly generated antiderivative.
-THIS NEEDS A REASON AND ANALYSIS SO MIGHT NOT BE NEEDED IN THIS WRITING.
-MAYBE A GOOD IDEA FOR A SEPARATE PIECE
-
-\subsection{Data Generation: Burgers' Equation}
-\noindent The second dataset generated in this study concerns the Burgers' equation.
-This equation has been used to model a variety of cases including fluid dynamics, traffic flow, and, shock waves \autocite{bonkileSystematicLiteratureReview2018,orlandiBurgersEquation2000,becBurgersTurbulence2007,jamesonEnergyEstimatesNonlinear2007}.
-This equation is also used as a base problem for testing the effectivity of numerical methods in solving non-linear PDEs \autocite{barterShockCapturingPDEbased2008,banksNumericalErrorEstimation2012, tabatabaeiImplicitMethodsNumerical2007,bonkileSystematicLiteratureReview2018}.
-The nonlinear term in the equation creates steep gradients and even shock waves which are discontinuous with low viscosity conditions.
-These challenges test the stability of numerical solvers.
-This is the scenario and reason for the choice of this PDE\@.
-To control the viscosity and therefore the steepness of gradients, the formulation of the Burgers' equation considered in this study is the forced viscous Burgers' equation in one dimension.
-For a velocity of \(u(x, t)\), viscosity of \(\nu \), and forcing term of \(f(x, t)\), the formulation of the forced Burgers' equation is shown in \lccref{eq:forced_viscous_burgers}.
-\begin{align}
-  \pdv{u}{t}+u\pdv{u}{x}-\nu\pdv[2]{u}{x} & = f \label{eq:forced_viscous_burgers}
-\end{align}
-The domain of we consider here is based on an exact solution of the equation.
-This is done so that the learned solver model can be tested on the exact solution.
-There are a number of sources in literature on the exact solution of the Burgers' equation \autocite{bentonTableSolutionsOnedimensional1972,wazwazPartialDifferentialEquations2010,woodExactSolutionBurgers2006}.
-In this study, we use a specific solution by \textcite{woodExactSolutionBurgers2006} which can be seen in \lccref{eq:burgers_exact_solution}.
-This solution is periodic in space but not in time.
-Therefore, the domain in space will be based on the spatial periodicity of the exact solution which is two.
-As such, the space domain spans from 0 to 2.
-The time domain, on the other hand, is chosen to span from 0 to 10 such that enough details of the solution is included.
-\begin{equation}
-  u(x,t) = \frac{2\nu\pi e^{-\pi^2\nu t}\sin(\pi x)}{a+e^{-\pi^2\nu t}\cos(\pi x)} \label{eq:burgers_exact_solution}
-\end{equation}
-Continuing to the second step, the parameters involved in \lccref{eq:forced_viscous_burgers} are the viscosity \(\nu \) and the forcing term \(f \).
-Since the forcing term is dependent on the solution in this step, the only parameter to determine is the viscosity.
-We choose three constant viscosity values which are 0.1, 0.01, and 0.0.
-These values are chosen so that a variety of behaviors are represented in the dataset from viscous to inviscid flow.
-
-After this, in the third step, the solution functions \(u \) are generated with 8 modes in time and 8 in space and 500 unique function samples for each viscosity value.
-Since we don't factor the viscosity in at this point, for ease of comparison, we ensure the same solutions are generated every time by using a new instance of the generator with the same seed number each time.
-This results in the solutions being the same for all viscosity and other parameters of the equation are adapted to this.
-
-Next we account for the different viscosity values in this stage.
-The forcing term is computed using \lccref{eq:forced_viscous_burgers}.
-The solution field \(u\) and forcing term \(f\) are modeled with Fourier series in \lccrefs{eq:fourier_field,eq:fourier_force} where \(k\) is a vector of spatial and temporal wave number such that \(k_t\) is the temporal wave number and \(k_x\) is the spatial wave number.
-\begin{align}
-  u\left(x, t \right) & = \sum_{k_{x}} \sum_{k_{t}} \hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)} \label{eq:fourier_field} \\
-  f\left(x, t \right) & = \sum_{k_{x}}\sum_{k_{t}} \hat{f}_k e^{2\pi i(k_{x}x+k_{t}t)} \label{eq:fourier_force}
-\end{align}
-Substituting the terms in \lccref{eq:forced_viscous_burgers} with the respective Fourier series, we get the equation \lccref{eq:forced_viscous_burgers_fourier_substitution}.
-A problem one notices is the nonlinear term \(u\pdv{u}{x}\).
-A naive approach would multiply all wave numbers terms with each other.
-\begin{align}
-  u\pdv{u}{x} = \left(\sum_{k_{x}} \sum_{k_{t}} \hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)}\right) \times \left(\sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{x})\hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)}\right)
-\end{align}
-This is computationally expensive operation with \(N^2\) multiplications \autocite{lariosMATH934BURGERS2021,robertsDealiasedConvolutionsPseudospectral2011,shenSpectralMethodsAlgorithms2011,orszagComparisonPseudospectralSpectral1972}.
-To avoid this complexity, the term is first reformulated into \(\pdv{x}(u^2/2)\).
-Then to avoid aliasing, the coefficients are padded with 50\% zeros such that the padded coefficients are 3/2 times the size of the original \autocite{orszagEliminationAliasingFiniteDifference1971, lariosMATH934BURGERS2021}.
-Then we use the padded coefficients to compute the function values in the physical domain using the inverse transform.
-And then, the point wise squaring operation is performed and transform the results back to spectral domain.
-The resulting coefficients are then trimmed back to their original size before padding.
-Finally, we multiply the resulting coefficients \(\hat{uu}_k\) by the derivative constants.
-This operation is much more efficient with only \(1.5 N\) multiplications.
-This is still more efficient than the naive approach even after taking into account the transforms involved adds \(O(2\times 1.5Nln(1.5N))\) operations if using a Fast Fourier Transform algorithm.
-Putting all the above together, results in \lccref{eq:forced_viscous_burgers_fourier_substitution}.
-\begin{equation}
-  \begin{split}
-    \sum_{k_{x}} \sum_{k_{t}} \hat{f}_k e^{2\pi i(k_{x}x+k_{t}t)} =
-     & \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{t}) \hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)}                                                                \\
-     & + \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{x})\hat{uu}_k e^{2\pi i(k_{x}x+k_{t}t)}                                                              \\
-     & - \nu\sum_{k_{x}} \sum_{k_{t}} {(2\pi i k_{x})}^2\hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)} \label{eq:forced_viscous_burgers_fourier_substitution}
-  \end{split}
-\end{equation}
-\begin{align}
-  \sum_{k_{x}} \sum_{k_{t}} \hat{f}_k & = \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{t}) \hat{u}_k + (2\pi i k_{x})\hat{uu}_k - \nu{(2\pi i k_{x})}^2\hat{u}_k \label{eq:forced_viscous_burgers_fourier} \\
-  \hat{f}_k                           & = (2\pi i k_{t}) \hat{u}_k + (2\pi i k_{x})\hat{uu}_k - \nu{(2\pi i k_{x})}^2\hat{u}_k \label{eq:forced_viscous_burgers_coeff}
-\end{align}
-After simplifying the equation, we get the coefficients as in \lccref{eq:forced_viscous_burgers_coeff}.
-Using this equation, the exact forcing term corresponding to the randomly generated solution can be computed with relatively low cost.
-Finally, the function values of both the solutions and forcing terms are perturbed by adding Gaussian noise with a mean of zero and standard deviation of 10\% of the function value standard deviation to the values of the inverse transform.
-The perturbed coefficients are then recomputed from the sum and the final perturbed functions are obtained.
-
-An example of the solution and forcing term pairs that has been generated is shown in \lccref{fig:burgers_data}.
-Using the same seed we can see that the solution functions of the same sample are the same.
-However, with the forcing terms, we see much larger amplitudes for higher frequencies for larger viscosity values.
-This is inline with \lccref{eq:forced_viscous_burgers_coeff}.
-The squared multiplier gets large much more quickly for higher frequencies due to the squaring operation.
-The since this effect is controlled by the viscosity via multiplication, the higher the viscosity, the larger the high frequency amplitudes of the forcing term.
-This, in other words, means that more viscous fluids require a stronger forcing term to affect the solution in the same way with as fluids with a lower viscosity.
-
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_solution_0.0.pgf}
-    \end{adjustbox}
-    \caption{Solution function for \(\nu=0\).}\label{fig:burgers_solution_0.0}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_forcing_0.0.pgf}
-    \end{adjustbox}
-    \caption{Forcing function for \(\nu=0\).}\label{fig:burgers_forcing_0.0}
-  \end{subfigure}
-  % \\[-0.7\baselineskip]
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_solution_0.01.pgf}
-    \end{adjustbox}
-    \caption{Solution function for \(\nu=0.01\).}\label{fig:burgers_solution_0.01}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_forcing_0.01.pgf}
-    \end{adjustbox}
-    \caption{Forcing function for \(\nu=0.01\).}\label{fig:burgers_forcing_0.01}
-  \end{subfigure}
-  % \\[-0.7\baselineskip]
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_solution_0.1.pgf}
-    \end{adjustbox}
-    \caption{Solution function for \(\nu=0.1\).}\label{fig:burgers_solution_0.1}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_forcing_0.1.pgf}
-    \end{adjustbox}
-    \caption{Forcing function for \(\nu=0.1\).}\label{fig:burgers_forcing_0.1}
-  \end{subfigure}
-  \caption{Example sample pairs of solution and forcing terms for the Burgers' equation dataset.}\label{fig:burgers_data}
-\end{figure}
-
-\section{Data Retrieval}\label{sec:data_retrieval}
-\noindent The second data acquisition approach retrieves data of a from an external source.
-This approach downloads the external data to a local machine.
-In this study, the specific dataset that will be used is the ERA5 dataset from the European Center for Medium-range Weather Forecast (ECMWF).
-Specifically, the ERA5 dataset is a reanalysis which means it combines observational data from all over the world in order to present a more complete picture of the weather system.
-This combination process, named 4D variational data assimilation, takes into account the physics known to be involved in the system.
-As an example weather station data which take measurements such as wind speed, humidity, and temperature of the immediate surroundings of the weather station is very limited in giving a broader picture of weather over a larger area.
-Even technologies like earth observations satellites are limited to what they can observe at any single point in time as most cannot see the entirety of the earth's surface at once.
-The ERA5 dataset specifically, assimilates previous forecasts with observational data every 12 hours.
-The ERA5 reanalysis is available at the following URL (\url{https://cds.climate.copernicus.eu/datasets/reanalysis-era5-single-levels}).
-
-The original dataset made available by ECMWF has a grid size of \ang{0.25} by \ang{0.25} in latitude and longitude for atmospheric data.
-Data of oceanic waves are also available at a coarser grid size of \ang{0.5} by \ang{0.5}.
-However, we will use a cloud optimized version called WeatherBench2 that is easier to retrieve \autocite{raspWeatherBench2Benchmark2023}.
-This is because the data is available in several more grid sizes such as \ang{1.5}.
-In addition, the data can be readily downloaded to a local machine without waiting for further processing on the server.
-The guide for working with the dataset is available at (\url{https://weatherbench2.readthedocs.io/en/latest/data-guide.html}).
-In our specific case, we use the version labeled \verb|1959-2023_01_10-6h-64x32_equiangular_conservative.zarr|.
-This dataset spans from year 1959 to 2023 with a grid size of \ang{5.625} or resolution of 64 by 32 which spans from \ang{-87.19} to \ang{87.19} in latitude and \ang{0.0} to \ang{354.4} in longitude.
-The dataset is also resampled down to 6-hour intervals that starts at midnight UTC January 1959 1\textsuperscript{st} and ends at 18:00 UTC January 10\textsuperscript{th} 2023.
-
-While the original data provided by ECMWF is available in NetCDF or GRIB, the WeatherBench2 version is provided using the Zarr format in a Google Cloud Storage Bucket.
-This setup allows the use of libraries that support the Zarr format to access the dataset remotely.
-The particular library we use is called \emph{Xarray} version \verb|2024.9.0| \autocite{hoyer2017xarray,hoyerXarray2024}.
-Accessing the remote dataset is done as shown in \lccref{fig:access_remote_zarr}.
-In order to ensure access is granted, the storage option token is set to anon so that the method uses the anonymous only public access mode of authentication \autocite{GCSFSGCSFs2023122post1+1g8e500c6dirty}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-  import xarray as xr
-  ds = xr.open_zarr(
-      "DATASET_ADDRESS",
-      storage_options = {"token": "anon"},
-  )
-  \end{lstlisting}
-  \caption{Example of using Xarray to access a publicly accessible Zarr dataset hosted on Google Cloud Storage Bucket.}\label{fig:access_remote_zarr}
-\end{figure}
-
-The specific dataset resolution we use is 64 by 32 representing longitude and latitude respectively.
-The ERA5 reanalysis dataset is hosted at the following URL\@: \url{gs://weatherbench2/datasets/era5/1959-2023_01_10-6h-64x32_equiangular_conservative.zarr}.
-The corresponding climatology is hosted at \url{gs://weatherbench2/datasets/era5-hourly-climatology/1990-2019_6h_64x32_equiangular_conservative.zarr}.
-The climatology is the average for hours 0, 6, 12, and 18 for each day of the year from 1990 until 2019.
-This average helps in defining the expected state of the weather at specific points in time based on the historical averages for that time of day and year.
-
-For the reanalysis dataset, we limit the time range to the years 1995{-}2013 for training and 2020{-}2022 for testing.
-The specific time ranges for training are chosen to balance the diversity within the data and capacity of the machine the processing will be done on.
-The testing set time range was chosen to be as close to those shown on the WeatherBench 2 website.
-The filter for time and variables is shown in \lccref{fig:wb2_retrieval}.
-The reason for the different time ranges between training and testing is to reduce the risk of information leakage accross the training and testing sets.
-This ensures that the testing scores we measure will be for the most part from the generalization that model learned during training.
-The filter is an array the length of the number of samples.
-The array values are all the datetime values that the year ranges are true for.
-This results in an array of boolean values.
-Using this boolean filter we can index the data so that we get the filtered data.
-Then, the filtered data is saved locally so that we can access it in a more performant way.
-The encoding chunks may need to be removed in order to evade the Xarray library from mistakenly persisting the remote encoding after slicing data \autocite{ianZarrEncodingAttributes}.
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-  years_idx = ds['time.year']
-  data_idx = (years_idx > START_YEAR) & (years_idx < END_YEAR)
-  da_orig = ds['2m_temperature'][data_idx]
-  # save locally
-  da_orig.encoding.pop('chunks',None)
-  da_orig.to_zarr(DATA_FILENAME, mode='w')
-  # open local version
-  da = xr.open_zarr(DATA_FILENAME)
-  \end{lstlisting}
-  \caption{Example of filtering of Xarray dataset by year and variable. The data is saved and then loaded locally.}\label{fig:wb2_retrieval}
-\end{figure}
-
-The dataset includes 62 variables with some variables also spanning 13 discrete vertical levels in the atmosphere.
-For our use, we will only be using the 2-meter temperature of the atmosphere.
-This is the air temperature 2 meters above the surface be it land, sea, or inland water.
-This variable is in units of kelvin (K).
-Vertically, the values of this variable is obtained by interpolating between the model values at the surface and the lowest model vertical level.
-An example of the data that was retrieved can be seen in \lccref{fig:wb2_data}.
-The data shown is in the equiangular projection.
-This means that towards the poles, the shapes become more distorted.
-While this is not the most ideal way to represent the data, using the data in this way adds to the challenge of how the model can adapt to the use of suboptimal configurations in the data.
-To compute the anomaly, we can simply subtract the current state in \lccref{fig:wb2_train_data} by the climatology in \lccref{fig:wb2_clim_data} resulting in \lccref{fig:wb2_train_anomaly}.
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_train_data.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:wb2_train_data}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_clim_data.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:wb2_clim_data}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_train_anomaly.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:wb2_train_anomaly}
-  \end{subfigure}
-  \caption{Data retrieved:(\subref{fig:wb2_train_data}) 2-meter temperature at January 1, 1995 6:00 UTC\@.
-(\subref{fig:wb2_train_anomaly}) Anomaly for 2-meter temperature at January 1, 1995 6:00 UTC\@.
-(\subref{fig:wb2_clim_data}) 2-meter temperature climatology for the first day of the year at hour 6 UTC\@.}\label{fig:wb2_data}
-\end{figure}
-
-After filtering, our training set has the dimensions of 27760 time steps, 64 longitude, and 32 latitude.
-The testing set on the other hand has 4384 time steps and the same values for the other two dimensions.
-For uses, such as a validation set during hyperparameter optimization, one can use a subset of the training set.
-The dimensions of the climatology are 4 for hour (0, 6, 12,\& 18), 366 for day of year, 64 for longitude, and 32 for latitude.
-
-\section{Design of Computational Model}\label{sec:computational_model_design}
-\noindent In this section, we will discuss the design of the computational model that is proposed in this work. An illustration of the computational model is show in \lccref{fig:computational_model}.
-
-\begin{figure}[H]
-  \centering
-  \begin{adjustbox}{max width=\textwidth}
-    \tikzfig{figures/computational_model}
-  \end{adjustbox}
-  \caption{Computational Model of SpectralSVR.}\label{fig:computational_model}
-\end{figure}
-
-The computational model is divided into four large phases.
-The processes within these phases are based on the broad outcomes of the phase.
-The phases themselves are data preparation, data transformation, model training, and model evaluation.
-Each phase is composed of processes that together works toward the output of the larger process.
-At the end, a final process of analysis and interpretation is carried out.
-
-\subsection{Data Preparation}
-\noindent The data preparation phase starts off the computation by preparing the data that is to be used in this study.
-This phase starts with specifying the problem to be solved.
-This translates to the dataset that will be used to represent these problems.
-The first type of dataset is generated based on a known governing equation or PDE\@.
-Using said equation, the goal is to generate pairs of functions that are related to each other by the equation.
-In the next process, generally, the solution function is first generated randomly.
-This is done by generating random numbers to use as coefficients of a set of basis functions.
-Then parameters of the equation is determined, such as term coefficients.
-Using the generated solution and predetermined parameters, a forcing term can generally be computed to satisfy the equation.
-Augmentations such as noise can then be added in the final process which is evaluating the function values.
-These processes result in a generated dataset.
-To verify the generation method and any models trained on the generated data one can use exact analytical solutions of the governing equations.
-
-The second type of dataset is retrieved from an external source.
-The data source is first identified, in our case it is the WeatherBench 2 collection of datasets.
-The specific dataset from the collection of different dataset versions is first determined.
-The dataset is available in the \emph{Zarr} format.
-And then, we determine the filters for the portions of the dataset we are interested in.
-Once the dataset and filters are determined, the retrieval process starts by accessing the dataset using the \emph{Xarray} library \autocite{hoyer2017xarray,hoyerXarray2024}.
-The filters are applied as in \lccref{fig:wb2_retrieval}.
-Finally, the filtered version is stored locally.
-The local dataset is also stored in the \emph{Zarr} format.
-
-\subsection{Data Transformation}\label{sec:data_transformation}
-\noindent The second phase of the computational model transforms the data that has been prepared into a form that can be used with the proposed model.
-In this study, there are two ways a dataset can be used.
-The first and simplest way is to predict the solution function from the forcing term for a given set of PDE parameters.
-In this case, the input function is the forcing term.
-In other words, the input function is the predictor or independent variable that will be used to predict the solution function.
-As such, the output function is the solution function.
-The antiderivative dataset is used in this way.
-The derivative, which represents the acceleration function, is used to predict the velocity function.
-Which means that the input function is the acceleration function and the output function is the velocity function.
-
-The second use of a dataset depends on whether it can be interpreted as a mapping of a previous function to the next function.
-In other words, a series of functions related to the previous function as a sum of the previous function and a perturbation.
-A commonly used form of this are time series.
-Generally, a time series can be represented as \lccref{eq:time_step_function}.
-This function describes the evolution of function \(f\) as a sum of some initial state \(f^0\) and perturbation which is its rate of change \(\dv{f}{t}\) at a point in time close to the current time multiplied by the time step \(\delta t\).
-This is the first order Taylor polynomial.
-Adding more terms with higher order derivatives can be done to increase the accuracy.
-This describes the same process that is used in the finite difference method.
-\begin{equation}
-  f^{t+1} = f^{t} + \delta t \times \dv{f}{t} + \dots \label{eq:time_step_function}
-\end{equation}
-In this case the previous function and any other independent variables like the forcing term involved in the right-hand side of the equation is used to predict the difference between the future state and the current state.
-It would mean that each sample function in the data would need to at least have two dimensions.
-This is because one dimension represents the evolution of the function over time, while the other dimensions define the spatial domain where the function's values are computed at each time step.
-This condition is true for both the Burgers' equation dataset and the WeatherBench 2 collection of ERA5 datasets.
-First, the Burgers' equation dataset, while is also able to be used in the first way as a mapping between the forcing term and the solution, one of the traditional ways of solving it is using the method of lines.
-This entails solving the dimensions other that time with methods such as the finite differences method or the spectral method.
-The time dimension is then separately solved using the finite differences method such as the form shown in \lccref{eq:time_step_function} \autocite{schiesserNumericalMethodLines2012,sadikuSimpleIntroductionMethod2000}.
-This is the form that the Burgers' equation dataset will be used in.
-In this case, algebraic manipulation of \lccref{eq:forced_viscous_burgers} results in the time derivative of the solution as in \lccref{eq:forced_viscous_burgers_time_derivative}.
-\begin{align}
-  \pdv{u}{t} = f - u\pdv{u}{x} + \nu\pdv[2]{u}{x} \label{eq:forced_viscous_burgers_time_derivative}
-\end{align}
-The most important component of the right-hand side of the equation, the time derivative, is expressed in terms of the solution function, the forcing term and any other partial derivatives.
-Because of this, it means we can train the model to learn the relationship between the solution function combined with the forcing term and the time derivative.
-Putting this together with \lccref{eq:time_step_function}, it is possible to predict the solution function in a future time based on the current solution function and forcing term.
-The input functions in this case are both the value of the solution function and the forcing term at the current time step.
-The output function is the time derivative which is computed by rearranging \lccref{eq:time_step_function} resulting in \lccref{eq:time_derivative_time_step_function}.
-\begin{equation}
-  \dv{f}{t} = \frac{f^{t+1} - f^{t}}{\delta t} \label{eq:time_derivative_time_step_function}
-\end{equation}
-Perhaps in a more obvious manner, the same is also applied to the WeatherBench 2 collection of ERA5 datasets.
-The 2-meter temperature is a series of snapshots in time of the distribution of temperature all over the world at 2 meters above the surface.
-The input function in this case is the temperature distribution at the current time step.
-The output function is the time derivative of the temperature distribution computed using \lccref{eq:time_derivative_time_step_function}.
-
-The input and output functions are then transformed into basis coefficients using the Fourier transform. % TODO: add reference to fourier transform in chapter 2
-Once the coefficients are computed, the input and output sample pairs are split into train, test, and validation subsets.
-For the first type of input and output function pair, since the samples are independent of each other, a random sampling of the dataset without replacement is done to select the samples for each subset.
-For the second type of input and output function pairs, if there are multiple samples of functions as in the Burgers' equation dataset, the same process with random sampling is followed.
-On the other hand, if only one function sample is available, such as the WeatherBench 2 dataset, an issue that arises is the fact that the samples are dependent on one another.
-This is because a previous time step influences the next time step.
-This is a problem for generalizing the learned model, since random sampling would lead to the model learning information in the future of the testing subset \autocite{kapoorLeakageReproducibilityCrisis2023,kaufmanLeakageDataMining2012}.
-As such, the portioning of the dataset is done by dividing the sample into different sections of the function in time.
-
-Finally, the data is scaled.
-This is done because of how support vector machines require scaling for inputs in order to perform well with certain hyperparameters such as the RBF kernel \autocite{ben-hurUsersGuideSupport2010}.
-For our case we use standard scaling based on the inputs of the training subset.
-This approach transforms the dataset by manipulating the distribution characteristics of the dataset \autocite{ahsanEffectDataScaling2021}.
-Specifically, the standard deviation \(\sigma \) and mean \(x_0\) of the dataset values \(x\) are processed such that the resulting values have a mean of 0 and standard deviation of 1.
-The function shown in \lccref{eq:standard_scaler} represents how each sample is processed with respect to the standard deviation \(\sigma \) and mean \(x_0\) of each feature.
-\begin{equation}
-  z(x;\sigma,x_0)=\frac{x-x_0}{\sigma} \label{eq:standard_scaler}
-\end{equation}
-The scaling is important for the RBF kernel specifically due to the fact that the kernel utilize a scale parameter.
-This parameter affects how scale of values influence the kernel.
-Another and perhaps more general benefit of scaling is the uniformity it enforces across features.
-This is useful because all feature weigh the outcome equally.
-In our use case, this equality is a reflection of what the data actually represents.
-Each feature which is a discretized value or its coefficient representation has equal value to any other feature.
-No point or coefficient is any more or less value compared to another point or coefficient.
-
-The scaling is applied to input functions only because scaling of the outputs does not affect the performance of the model \autocite{ben-hurUsersGuideSupport2010}.
-To also prevent information leakage across training and testing sets, the mean and standard deviation of each feature is computed using the training subset only.
-Once the parameter values are obtained, all input function samples in the dataset are transformed into their scaled versions.
-This means that the distribution for the testing and validation sets may be outside the target standard deviation and mean.
-% TODO: add graphs and tables of the resulting preprocessed data
-
-\subsection{Model Training}
-\noindent Once the data has been preprocessed, the model is trained using pairs of training features and labels.
-The training phase is separated into four processes.
-First, the preprocessed input and output function representation need to be real numbers.
-This is because the LSSVR model was made to work with real numbers.
-Any complex values such as Fourier coefficients are represented as flattened pairs of the real and imaginary components of complex values.
-% TODO: add figure of flattened complex values
-
-The training can proceed to solve \lccref{eq:lssvr_solution}.
-As the original LSSVR equation was made for regression of a single value of \(\vb{y} \), we constructed an extended the original equation in order to train multiple regression models to predict each coefficient in an output function sample.
-The assumption of this extension is that the inputs and model hyperparameters such as kernels and the regularization constant \(C \) are the same across individual regressors.
-Therefore, it follows that the solution vector and target vector can both be transformed into their matrix form with each column representing the individual regressor which results in \lccref{eq:lssvr_solution_vectorized}.
-This vectorized version is equal to \(m \) separate instances of \lccref{eq:lssvr_solution}.
-In essence, instead of a vector of scalar sample output values and a vector of model parameters, the extended equation consists of a matrix of rows of vector output values and a matrix of model parameters with each column representing the separate model for each output and row representing the Lagrange multipliers for each sample.
-The procedure to solve \lccref{eq:lssvr_solution_vectorized} adjusts \lccref{alg:lssvr_training} for the extra dimension spanning the multiple outputs of size \(m\).
-\begin{equation} \label{eq:lssvr_solution_vectorized}
-  \begin{bmatrix}
-    0          & \vb{1}_{n}^{\intercal} \\
-    \vb{1}_{n} & \Omega + \frac{I}{C}
-  \end{bmatrix}
-  \begin{bmatrix}
-    b_0           & \cdots & b_m           \\
-    \vb{\alpha}_0 & \cdots & \vb{\alpha}_m \\
-  \end{bmatrix}
-  =
-  \begin{bmatrix}
-    0        & \cdots & 0        \\
-    \vb{y}_0 & \cdots & \vb{y}_m \\
-  \end{bmatrix}
-\end{equation}
-
-Second, as the training process of an LSSVR described in requires constructing the first matrix on the left-hand side and the matrix on the right-hand side, each component of the matrices themselves will also need to be constructed.
-The kernel matrix \(\Omega \) is first constructed by computing the kernel values between each sample input with every other sample input.
-If the training set has \(n \) samples, then the resulting kernel matrix would be of size \(n \) by \(n \).
-% Assemble lssvr optimality equation matrices
-Third, using the inputs \(\vb{X}\), outputs \(\vb{y}\), predetermined regularization constant \(C \), and the obtained kernel matrix \(\Omega \), \lccref{eq:lssvr_solution_vectorized} is assembled.
-Finally, the matrix of learned parameters \(\vb{\alpha}\) and \(\vb{b}\), which are the Lagrange multipliers and bias respectively, are solved for using a linear equation solver such as a matrix Moore-Penrose inverse or linear least squares solver.
-
-For our study, we choose to not optimize the hyperparameters to focus on the broad performance with default hyperparameter values.
-The scaling parameter of the RBF kernel is computed from the training features.
-This is computed as the square root of the sum of feature variances.
-The regularization parameter used will be a default value of 1.
-Using the same values allow for easier comparisons for comparable results.
-
-\subsection{Model Evaluation}
-\noindent The fourth phase of the computational model is the evaluation of the learned model.
-This phase starts with formatting the inputs.
-If the inputs aren't scaled yet, then it is scaled using the scaling function fitted on the training set.
-This is the case for new data such as new measurements or an analytical solution of the learned PDE\@.
-Once the inputs that is to be evaluated is scaled in the same way as the training inputs, the model can predict the corresponding outputs.
-
-The procedure to compute the predicted outputs follows \lccref{alg:lssvr_prediction}.
-This leads to the second process which is computing the kernel matrix between the training input features \(\vb{X}\) and the evaluation input features \(\vb{U}\).
-The matrix is constructed as the kernel value between each evaluation sample feature and every training sample feature.
-For \(p \) evaluation samples and \(n \) training samples, this results in a kernel matrix \(\Omega \) with a shape of \(p \) rows and \(n \) columns.
-
-In the third process, the constructed kernel matrix is then multiplied with the matrix of learned Lagrange multipliers \(\vb{\alpha}\).
-The multiplication is the matrix multiplication process.
-Then, the bias vector is added to each row to produce the final predicted outputs \(\vb{v}\).
-This process is represented by \lccref{eq:lssvr_prediction_vectorized}.
-\begin{equation}
-  \vb{v} = \Omega\vb{\alpha}+\vb{1}\vb{b} \label{eq:lssvr_prediction_vectorized}
-\end{equation}
-
-The fourth process is concerned with the fact that the predicted output \(\vb{v}\) is a matrix of real numbers.
-The LSSVR output needs to be formatted before it can be used in the proposed model.
-This is done by converting the outputs into the same format as the training labels.
-As we use the Fourier basis, the model output is converted back into a matrix of complex numbers using the inverse of the first process during training.
-Finally, these predicted Fourier basis coefficients can be used to evaluate the predicted functions themselves.
-
-\section{Implementation of Computational Model}
-\noindent This section discusses the implementation of modeling and approximation of PDEs using LSSVR\@.
-Using the computational model design in \lccref{sec:computational_model_design}, the computational model is implemented as a library using the Python programming language.
-The development process itself is based on the iterative development model as mentioned in \lccref{sec:development method}.
-In this section, the output iterative processes are consolidated and explained together.
-
-\subsection{Analysis}
-\noindent The aim of any program that is developed in this study is to model the relationship between functions defined by a partial differential equation or other operators and governing equations.
-Since the potential subject of modeling can be wide-ranging, the software product that will be developed is a library.
-This is done so that the tools and proposed model that is developed will be able to be used with a variety of PDEs.
-With this in mind, the software must also be performant and compatible with the larger machine learning and scientific computing community.
-
-To demonstrate the use and capability of the software, three case studies are chosen to represent the variety of PDEs.
-The first case study is the antiderivative equation.
-This simple case is chosen as a proof of concept to show that the proposed model works in the most simple case.
-The second case study, which is the Burgers' equation, adds a level of complexity because of the nonlinearity involved with the solution function.
-The third case study, which is the ERA5 weather dataset, was chosen to show how the model performs on data with real world observations incorporated into it.
-This dataset also presents a challenge because of the uncertainties involved with weather simulation \autocite{herreraReviewCurrentFuture2017}.
-These datasets are discussed in \lccrefs{sec:data_generation,sec:data_retrieval}.
-
-In addition, the software product is developed within certain limitations. The limitations are:
-\begin{enumerate}
-  \item The operating and implementation language of the library is Python.
-  \item The library is to be used in user code
-  \item The library depends on other libraries including the following core dependencies PyTorch, NumPy, Xarray, Zarr, Pandas, and tqdm.
-\end{enumerate}
-
-\subsection{Design}\label{sec:implementation_design}
+% !TEX root = ./technical_doc.tex
+\chapter{DESIGN}\label{sec:implementation_design}
 \noindent In this subsection, the architectural design of the software product is explained.
@@
 Throughout the iterations, the utilities were also added to alleviate the need for general tools.
-
-\subsection{Implementation}
-
-\noindent The design in \lccref{sec:implementation_design} is implemented within the same iterative loop.
-As such, the feedback from tests is immediate, and any fixes can be implemented quickly.
-The implementation is done using the Python language and a number of Python libraries.
-To facilitate the management of dependencies, the implementation makes use of the package management tool Poetry \autocite{eustacePoetryPythonPackaging2024}.
-In addition, the Python version is managed using the tool PyEnv.
-The implementation process starts with installation of the required dependencies.
-The dependencies are specified in the \verb|pyproject.toml| as shown in \lccref{fig:poetry_add_deps}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Toml]
-...
-[tool.poetry.dependencies]
-python = "^3.10.6"
-numpy = "^1.24.0"
-tqdm = "^4.65.0"
-jaxtyping = "^0.2.20"
-pandas = "^2.2.2"
-torchmetrics = "^1.4.2"
-scikit-learn = "^1.5.0"
-matplotlib = "^3.9.0"
-torch = {version = "^2.4.1+cu124", source = "pytorch-gpu"}
-torchvision = {version = "^0.19.1+cu124", source = "pytorch-gpu"}
-torchaudio = {version = "^2.4.1+cu124", source = "pytorch-gpu"}
-ray = {extras = ["tune"], version = "^2.37.0"}
-hyperopt = "^0.2.7"
-ipywidgets = "^8.1.5"
-torchdiffeq = "^0.2.4"
-xarray = "^2024.10.0"
-zarr = "^2.18.3"
-gcsfs = "^2024.10.0"
-
-[[tool.poetry.source]]
-name = "pytorch-gpu"
-url = "https://download.pytorch.org/whl/cu124"
-priority = "explicit"
-
-[build-system]
-requires = ["poetry-core"]
-build-backend = "poetry.core.masonry.api"
-  \end{lstlisting}
-  \caption{Contents of pyproject.toml configuration file that define the dependencies using Poetry.}\label{fig:poetry_add_deps}
-\end{figure}
-
-After ensuring that the correct version of python is being used with pyenv, the dependencies specified in the \verb|pyproject.toml| file can be installed using the shell command \verb|poetry install|.
-At the end of each iteration, the dependencies are subject to change depending on whether any new ones are needed or old dependencies can be removed.
-
-In the following, we will discuss the implementation of each module and how the phases of computational model relates to each implemented functionality.
-The base data structure that is used in the implementation is the PyTorch Tensor \autocite{Ansel_PyTorch_2_Faster_2024}.
-Tensors are a generalization of scalars and array-like structures such as vectors and matrices.
-This is essential since many computations that is done in the proposed model are based on matrices and higher dimensional arrays.
-PyTorch Tensors allow the elements to be of different data types such as floating point numbers of different precision or even complex numbers.
-In addition to basic operations for working with the Tensors such as matrix multiplications, PyTorch also provides many algorithms for use when working with Tensors such as linear equation solvers or the Fast Fourier Transform.
-Another reason for choosing to use PyTorch is the ability to parallelize computation using specialized processors such as GPUs.
-Lastly, PyTorch is widely used in the machine learning community which reflects on its reliability, wealth of community knowledge and support, and active development.
-
-\subsubsection{Utilities}
-
-\noindent The utilities module provide common tools that are used when working with the developed software.
-First, because the basis function used in this study is the Fourier basis, a large proportion of concern is the storage of Fourier basis coefficients.
-The Fourier series representation that is used in this study is the complex representation as show in \lccref{eq:fourier_series}.
-However, as previously mentioned, least squares support vector machines is constructed to work with real numbers.
-In order for LSSVR to learn the relationship between complex numbers, a representation of complex numbers in terms of real numbers is necessary.
-Since sample features and labels for LSSVR need to be flattened into one dimension which result in a matrix with rows of samples, the representation of complex numbers using real numbers can be done after features and labels have been flattened.
-An example of such a matrix of two samples with four features each can be seen in \lccref{eq:complex_matrix}.
-To represent the complex number features as real numbers, once can simply split a single complex number into two real numbers.
-When this is done to the entire matrix of complex numbers, the result is \lccref{eq:complex_matrix_real_rep}.
-\begin{align}
-  \begin{bmatrix}
-    -1.03+0i & -0.52+0.39i & -0.54+0i & -0.52-0.39i \\
-    -0.85+0i & -0.39+0.19i & 0.87+0i  & -0.39-0.19i
-  \end{bmatrix}\label{eq:complex_matrix} \\
-  \begin{bmatrix}
-    -1.03 & 0 & -0.52 & 0.39 & -0.54 & 0 & -0.52 & -0.39 \\
-    -0.85 & 0 & -0.39 & 0.19 & 0.87  & 0 & -0.39 & -0.19
-  \end{bmatrix}\label{eq:complex_matrix_real_rep}
-\end{align}
-There are several ways to do this in PyTorch, such as extracting the real and imaginary element components into separate matrices and then interleaving the columns to create the real representation.
-However, a more performant version can be made by using built-in functions of the library that directly allows views of complex valued tensors as real tensors and vice versa.
-The \verb|view_as_real| and \verb|view_as_complex| functions allow the conversion between real and complex representations by representing complex valued tensors by adding a dimension of size two for each component of complex numbers.
-The resulting implementation can be seen in \lccref{fig:complex_matrix_conversion_implementation}.
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-def to_real_coeff(x: torch.Tensor) -> torch.Tensor:
-    return torch.view_as_real(x).flatten(-2)
-
-def to_complex_coeff(x: torch.Tensor) -> torch.Tensor:
-  return torch.view_as_complex(
-    x.reshape((*x.shape[:-1], -1, 2))
-  )
-  \end{lstlisting}
-  \caption{Utility function to convert between complex matrices and the real representations.}\label{fig:complex_matrix_conversion_implementation}
-\end{figure}
-
-Another important utility used on inputs for the proposed SpectralSVR is a scaling function.
-This utility has been implemented in a variety of ways and using different tools.
-However, as the standard scaling is not provided by PyTorch, we have also implemented our own version.
-The scaling function accepts PyTorch tensors or tuples of tensors of real or complex elements.
-First, the scaling function is implemented as a class that is instantiated.
-The scaling function is then fitted onto the reference data to obtain the standard deviation and mean of each feature.
-This information is stored as properties of the class.
-Any complex tensors are converted into their real representations using the functions in \lccref{fig:complex_matrix_conversion_implementation}.
-Once the scaling function instance is fitted, any set of tensors with the same number of features (columns) and element type (complex or real) can be roughly transformed into a standard deviation of one and mean of zero for every feature.
-This is done by subtracting the fitted mean of each feature from the elements in the column and then dividing with the feature's standard deviation.
-The implementation also provides a method to retrieve a scaling function fitted on a subset of the original tuple of tensors.
-Serialization for saving to and loading from disk is also implemented.
-This is done simply by using the PyTorch save and load functions on the scaling function instance itself.
-For some use cases, an inverse scaling operation to the original standard deviation and mean is also essential.
-The implementation is simply the reverse of the transformation process where the elements are multiplied by the standard deviation and the mean is the added.
-
-Another group of utility in the module is concerned with managing the number of modes a tensor of coefficients has.
-First, a function called \verb|resize_modes| accepts a tensor of coefficients and the target number of modes in each dimension.
-The first dimension is always assumed to represent the different samples.
-Because of this the target modes will only affect the dimensions after the first.
-The wave numbers are also assumed to be symmetric about zero such that the highest absolute values of the wave number is in the middle of each dimension.
-The wave number decreases symmetrically as you move towards the edges of the dimension and reaching the lowest absolute wave number at the edges.
-This is done to ensure compatibility with the way existing libraries such as PyTorch works with tensors of Fourier coefficients.
-Because of this, shrinking a tensor of coefficients along a dimension means removing the center of the tensor along that dimension.
-And expanding to a target number of modes that is larger means that the tensor is padded with zeros in the center along the desired dimension.
-In addition, the remaining coefficients may be rescaled in order to balance the effect of adding or removing coefficients.
-The implementation is presented in \lccrefs{fig:coefficient_shrink_impl,fig:coefficient_expand_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-for dim, (target_mode, current_mode) in enumerate(
-    zip(target_modes, current_modes), 1
-):
-    device = x.device
-    start_range = torch.tensor(
-        range((target_mode - 1) // 2 + 1), dtype=torch.int
-    ).to(device=device)
-    end_range = torch.tensor(
-        range(current_mode - target_mode // 2,
-          current_mode
-        ),
-        dtype=torch.int,
-    ).to(device=device)
-
-    x_resized = torch.concat(
-        (
-            x_resized.index_select(dim, start_range),
-            x_resized.index_select(dim, end_range),
-        ),
-        dim,
-    )
-  \end{lstlisting}
-  \caption{Example of shrinking a tensor of samples' coefficients to a target number of modes.}\label{fig:coefficient_shrink_impl}
-\end{figure}
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-for dim, (target_mode, current_mode) in enumerate(
-    zip(target_modes, current_modes), 1
-):
-    device = x.device
-    start_range = torch.tensor(
-        range((current_mode - 1) // 2 + 1), dtype=torch.int
-    ).to(device=device)
-    # make sure that end range is empty if
-    # the coefficient is only size 1
-    end_range = torch.tensor(
-        range(current_mode // 2, current_mode)
-        if current_mode > 1
-        else range(0),
-        dtype=torch.int,
-    ).to(device=device)
-    padding_size = target_mode - current_mode
-    modes = list(x_resized.shape)
-    modes[dim] = padding_size
-    padding = torch.zeros(modes).to(x_resized)
-
-    x_resized = torch.concat(
-        (
-            x_resized.index_select(dim, start_range),
-            padding,
-            x_resized.index_select(dim, end_range),
-        ),
-        dim,
-    )
-  \end{lstlisting}
-  \caption{Example of expanding a tensor of samples' coefficients to a target number of modes.}\label{fig:coefficient_expand_impl}
-\end{figure}
-Next, the second way to manage the size of a tensor along a dimension is to interpolate the current values.
-The implementation uses simple linear interpolation.
-This is especially useful for situations such as coefficients that are themselves functions of time.
-This is a common application such as when solving the initial condition problem of a function in space and time.
-One might represent the function as a Fourier series with basis as functions of space and coefficients as functions of time.
-In this case, the coefficients for time values that are not available can be interpolated.
-The implementation of this is shown in \lccref{fig:coefficient_interpolation_impl}.
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-    index_floor = index_float.floor().to(torch.int)
-    index_ceil = index_float.ceil().to(torch.int)
-    x_ceil = x.index_select(dim, index_ceil)
-    x_floor = x.index_select(dim, index_floor)
-    # interpolate coefficients
-    index_shape = [1 for _ in range(x_floor.ndim)]
-    index_shape[1] = -1
-    index_scaler = (
-        ((index_float - index_floor) / (
-          index_ceil - index_floor
-        ))
-        .reshape(index_shape)
-        .nan_to_num()
-    )
-    # ynt + scaler * (ynt1 - ynt)
-    # (1 - scaler) * ynt + scaler * ynt1
-    x_interp = torch.lerp(x_floor, x_ceil, index_scaler.to(x))
-  \end{lstlisting}
-  \caption{Example of interpolating for indices (floating point indices) between the available ones (integer indices).}\label{fig:coefficient_interpolation_impl}
-\end{figure}
-
-Finally, this module also provides the types and reexports implementations of ordinary differential equation solvers from the torchdiffeq library \autocite{Chen_torchdiffeq_2021}.
-The implementation can be seen in \lccref{fig:solver_impl}.
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-RHSFuncType = Callable[[torch.Tensor, torch.Tensor],
-  torch.Tensor
-]
-SolverSignatureType = Callable[[
-        RHSFuncType, torch.Tensor, torch.Tensor,
-    ],
-    torch.Tensor
-]
-MixedRHSFuncType = Callable[[
-        torch.Tensor, torch.Tensor, torch.Tensor,
-    ],
-    torch.Tensor,
-]
-MixedSolverSignatureType = Callable[
-    [MixedRHSFuncType, torch.Tensor, torch.Tensor],
-    torch.Tensor,
-]
-
-def euler_solver(
-    rhs_func: RHSFuncType,
-    y0: torch.Tensor,
-    t: torch.Tensor,
-):
-    solution = torch.zeros((len(t), *y0.shape)).to(y0)
-
-    j = 1
-    solution[j - 1] = y0
-    for t0, t1 in zip(t[:-1], t[1:]):
-        dt = t1 - t0
-        y = solution[j - 1]
-        solution[j] = y + dt * rhs_func(t0, y)
-        assert (
-            solution.isnan().sum() == 0
-        ), f"solver encountered nan at timestep {j} (t={t0})"
-        j = j + 1
-    return solution
-
-implicit_adams_solver: SolverSignatureType = partial(
-    odeint, method="implicit_adams", options={"max_iters": 4}
-)  # type: ignore
-
-lsoda_solver: SolverSignatureType = partial(
-    odeint, method="scipy_solver", options={"solver": "LSODA"}
-)  # type: ignore
-  \end{lstlisting}
-  \caption{Implementation of ODE solvers and the types.}\label{fig:solver_impl}
-\end{figure}
-
-\subsubsection{Basis Functions}
-
-\noindent This module implements two classes.
-The first is the base Basis class.
-The second is a subclass implementing the Fourier basis specifically.
-These classes provide the functionality needed to have an easier time when working with basis functions and their coefficients.
-First, the core function of these classes is to provide a way to transition between the spectral domain and the physical domain.
-This is implemented in the base class by storing the coefficients of sample functions as a class property.
-The coefficients are assumed to be at least of one function.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    @staticmethod
-    def transform(
-        f: torch.Tensor,
-        res: TransformResType | None = None,
-        periodic: bool = True,
-        periods: PeriodsInputType = None,
-        allow_fft: bool = True,
-    ) -> torch.Tensor:
-        if not torch.is_complex(f):
-            f = f * (1 + 0j)
-        res = transformResType_to_tuple(res, tuple(f.shape[1:]))
-        periods = periodsInputType_to_tuple(periods, f.shape[1:])
-        # perform 1d transform over every dimension
-        F = f
-        for cdim in range(1, ndims):
-            F = FourierBasis._ndim_transform(
-                F,
-                dim=cdim,
-                func="forward",
-                res=res[cdim - 1],
-                periodic=periodic,
-                period=periods[cdim - 1],
-                allow_fft=allow_fft,
-            )
-
-        return F
-...
-  \end{lstlisting}
-  \caption{Implementation of forward Fourier transform.}\label{fig:fourier_transform_impl}
-\end{figure}
-
-The transitions between the coefficients and functions values are implemented as a function to transform function values to coefficients and an inverse transform function to compute function values from coefficients.
-The base class enforces this by defining abstract methods which any subclass will need to implement.
-The FourierBasis subclass then implements the transform and inverse transform functions specific for transitioning between function values and Fourier basis coefficients.
-As before, the implementation assumes that the first dimension indexes the samples and the rest represent the coefficient wave numbers.
-This means that the implementation must allow for multidimensional functions.
-For the Fourier transform and inverse transform, the multidimensional version is relatively simple to implement.
-The multidimensional Fourier transform essentially performs the one dimensional Fourier transform along one dimension.
-And then, using the result to perform the one dimensional Fourier transform along the next dimension.
-This process is repeated until the last dimension.
-The implementation of the forward transform is presented in \lccref{fig:fourier_transform_impl}.
-The inverse transform simply changes the \verb|func| parameter to \enquote{inverse}.
-
-The Fourier transform along each dimension is done by flattening every other dimension into the sample dimension.
-This essentially means that the function values are \enquote{sliced} along the dimension currently being transformed, and that each \enquote{slice} is its own \enquote{sample}.
-Mathematically, this is simply due to the matrix multiplication of basis functions along one dimension with every other dimension.
-The implementation of this is shown in \lccref{fig:ndim_fourier_transform_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    @staticmethod
-    def _ndim_transform(
-        f: torch.Tensor,
-        dim: int,
-        func: Literal["forward", "inverse"],
-        res: slice,
-        periodic: bool,
-        period: float,
-        allow_fft: bool,
-    ) -> torch.Tensor:
-        # flatten so that each extra dimension is
-        # treated as a separate "sample"
-        # move dimension to transform to the end
-        # so that it can stay intact after f is flatened
-        f_transposed = f.moveaxis(dim, -1)
-        # flatten so that the last dimension is intact
-        f_flatened = f_transposed.flatten(0, -2)
-
-        F_flattened = FourierBasis._raw_transform(
-            f_flatened,
-            func=func,
-            res=res,
-            periodic=periodic,
-            period=period,
-            allow_fft=allow_fft,
-        )
-        # unflatten so that the correct shape is returned
-        F_transposed = F_flattened.reshape(
-          (*f_transposed.shape[:-1], res.step)
-        )
-        F = F_transposed.moveaxis(-1, dim)
-
-        return F
-...
-  \end{lstlisting}
-  \caption{Implementation of n-dimensional Fourier transform for a specific dimension.}\label{fig:ndim_fourier_transform_impl}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    @staticmethod
-    def _raw_transform(
-        f: torch.Tensor,
-        func: Literal["forward", "inverse"],
-        res: slice,
-        periodic: bool,
-        period: float,
-        allow_fft: bool,
-    ) -> torch.Tensor:
-        match func:
-            case "forward":
-                sign = -1
-            case "inverse":
-                sign = 1
-        mode = f.shape[1]
-        domain_starts_at_0 = res.start == 0
-        domain_end_equal_to_period = res.stop == period
-        can_use_fft = (
-            domain_starts_at_0
-            and domain_end_equal_to_period
-            and periodic
-            and allow_fft
-        )
-        if can_use_fft:
-            if func == "forward":
-                F = torch.fft.fft(
-                  f, dim=1, n=res.step, norm="backward"
-                )
-            elif func == "inverse":
-                F = torch.fft.ifft(
-                  f, dim=1, n=res.step, norm="forward"
-                )
-        else:
-            if periodic:
-                n = res.start + torch.arange(res.step).to(f)
-                n = n / res.step * period
-            else:
-                n = torch.linspace(
-                    res.start, res.stop, res.step
-                ).to(f)
-            e = FourierBasis.fn(
-                n.view(-1, 1),
-                mode,
-                periods=period,
-                constant=sign * 2j * torch.pi,
-            )
-
-            F = torch.mm(f, e.T)
-        return F
-...
-  \end{lstlisting}
-  \caption{Implementation of the one dimensional Fourier Transform.}\label{fig:1d_fourier_transform_impl}
-\end{figure}
-
-The one dimensional Fourier transform itself is implemented as a raw transform function.
-This function accepts input of a matrix of values to transform, a parameter to indicate the type of transformation (inverse transform or forward transform), the evaluation boundary and number of grid points, whether the evaluation should assume the function is periodic, the size of the function domain, and if the Fast Fourier Transform is allowed to be used.
-The evaluation boundaries, actual function domain size, whether the function can be assumed to be periodic, and if FFTs is allowed to be used together determine the Discrete Fourier Transform algorithm that is used.
-The FFT algorithm is used if the following are all true: the evaluation starts at zero and ends with the same value as the period, the function can be assumed to be periodic, and FFT is allowed.
-Otherwise, the transform is computed naively using \lccrefs{eq:discrete_fourier_transform,eq:inverse_discrete_fourier_transform}.
-The naive approach allows for evaluating function values of coefficients at various grid sizes and evaluation boundaries.
-This is useful for being able to evaluate at resolutions other than that of the original discretized function or coefficients.
-One use for this is plotting the function at different parts or resolutions.
-The relationship with the physical domain means that the boundaries of the domain is important.
-This is because the function values that will be used may only be valid within certain boundaries.
-Because of this, the information of physical domain bounds must also be stored.
-This is done by storing the span of the function in each dimension.
-The implementation we have gone with doesn't store any other information than the span in each dimension.
-Because of this, the information would need to be stored outside the Basis class instance and any outputs or operations with the classes will need to take this into account.
-The implementation of the one dimensional Fourier transform is presented in \lccref{fig:1d_fourier_transform_impl}.
-
-The secondary set of functionality provided by the basis classes are mathematical operators on the functions the coefficients represent.
-There are four operators implemented, which are the addition, subtraction, derivative, and antiderivative operators.
-These four operations can be further categorized into arithmetic and calculus operations.
-The arithmetic operations, which are addition and subtraction, are implemented by following how the actual mathematical operations would be carried out on two functions which are Fourier series as shown in \lccref{eq:fourier_series_addition}.
-For subtraction, the plus sign is simply replaced with the minus sign.
-\begin{align}
-  \sum_{k} \hat{u}_k e^{2\pi ikx} + \sum_{k} \hat{f}_k e^{2\pi ikx} =
-  \sum_{k} \left(\hat{u}_k + \hat{f}_k\right) e^{2\pi ikx} \label{eq:fourier_series_addition}
-\end{align}
-The implementation leverages the operator overloading in Python classes.
-In addition, the overload should be done to the \verb|__add__| function.
-This function adds the current instance to another object which is the other basis instance for our use case.
-We also want the operation to return an independent instance without any references to the previous instances.
-To do this, all properties are copied into a new instance.
-This is then used to perform the arithmetic operation.
-The implementation in \lccref{fig:basis_addition_impl} demonstrates the addition operation.
-For subtraction, a similar implementation is done using the \verb|__sub__| function and switching the plus sign with the minus sign.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def __add__(self, other: Self):
-        if isinstance(other, self.__class__):
-            if other.coeff is None:
-                return self.copy()
-            elif self.coeff is None:
-                return other.copy()
-            else:
-                result = self.resize_modes(other)
-                result.coeff = result.coeff + other.coeff
-                return result
-        else:
-            raise TypeError(
-                f"unsupported operand type(s) for +: '{
-                    self.__class__
-                }' and '{type(other)}'"
-            )
-...
-  \end{lstlisting}
-  \caption{Implementation of basis addition function.}\label{fig:basis_addition_impl}
-\end{figure}
-
-The calculus operations for Fourier basis take advantage of the properties of the Fourier series.
-As discussed in \lccref{sec:fourier_discussion}, derivatives and integration become multiplication and division in the spectral space of Fourier series.
-Our implementation takes advantage of this as shown in \lccref{fig:basis_grad_impl}.
-Similar to how subtraction is just a modification of the addition operation, the integral or antiderivative operator is also implemented simply by changing the operation with the term multiplier from multiplication to division.
-% TODO: change the reference to specific equations for calculus in spectral domain in ch2
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def grad(self, dim: int = 0, ord: int = 1) -> Self:
-        copy = self.copy()
-        if dim == 0 and self.time_dependent:
-            # time dependent use finite differences
-            dt = self.periods[0] / (self.time_size - 1)
-            coeff = copy.coeff
-            for o in range(ord):
-                coeff = torch.gradient(coeff, spacing=dt, dim=1)[0]
-            copy.coeff = coeff
-        else:
-            if self.time_dependent:
-                # disregard time dimension
-                dim = dim - 1
-            k = copy.wave_number(copy.modes[dim])
-            multiplier_dims = [1 for _ in range(copy.ndim)]
-            multiplier_dims[dim] = copy.modes[dim]
-            if self.time_dependent:
-                multiplier_dims = (1, *multiplier_dims)
-            multiplier = (
-                2
-                * torch.pi
-                * 1j
-                * k.reshape(multiplier_dims).to(copy.coeff)
-                / self.periods[dim]
-            )
-            multiplier = multiplier.pow(ord)
-            coeff = copy.coeff.mul(multiplier)
-            coeff[:, ..., 0] = torch.tensor(0 + 0j)
-            copy.coeff = coeff
-        return copy
-...
-  \end{lstlisting}
-  \caption{Implementation of basis grad function.}\label{fig:basis_grad_impl}
-\end{figure}
-
-The last group of functionality implemented in the Basis and FourierBasis classes provides convenience and often used procedures when working with basis functions.
-First, random coefficient generation for the Fourier basis is implemented.
-This is done as discussed in step 3 of the data generation process discussed in \lccref{sec:data_generation}.
-The implemented function shown in \lccref{fig:generate_coeff_impl} is then wrapped in another function that creates a new FourierBasis instance with the generated coefficients.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    @classmethod
-    def generate_coeff(
-        cls,
-        n: int,
-        modes: int | tuple[int, ...],
-        generator: torch.Generator | None = None,
-        random_func: Callable[..., torch.Tensor] = torch.randn,
-        complex_funcs: bool = False,
-        scale: bool = True,
-    ) -> torch.Tensor:
-        if isinstance(modes, int):
-            modes = (modes,)
-        n_modes = len(modes)
-        assert n_modes > 0, "modes should have at least one element"
-        random_func = partial(random_func, generator=generator)
-        if complex_funcs:
-            coeff = random_func((n, *modes), dtype=torch.complex64)
-        else:
-            coeff = random_func((n, *modes), dtype=torch.complex64)
-
-            vals = cls.inv_transform(coeff)
-            coeff = cls.transform(vals.real + 0j)
-        if scale:
-            scaler = torch.tensor(modes).sum() * 0.2
-            coeff = coeff.mul(scaler)
-        return coeff
-...
-  \end{lstlisting}
-  \caption{Implementation of Fourier Basis coefficient generation function.}\label{fig:generate_coeff_impl}
-\end{figure}
-
-Other convenience functionality also provided include plotting, function value perturbation, and function value evaluation based on domain span information that has been stored in the class instance.
-The function value evaluation is especially useful for experimenting and for the plotting functionality itself.
-This is because, the span was given to the constructor and does not need to be composed again with the inverse transform function.
-
-\subsubsection{Model}\label{sec:impl_model}
-
-\noindent The SpectralSVR model is implemented in this module.
-There are two components in this module.
-First, there is the implementation of least-squares support vector regression (LSSVR) using PyTorch.
-This implementation is a reimplementation and modification of an LSSVR implementation using scikit-learn by \textcite{florencioLssvr2020}.
-The modifications are mainly concerned with using PyTorch in place of scikit-learn.
-Other modifications are concerned with the performance side of things, which are computing the kernel matrix in batches to avoid memory spikes and the ability to compute on hardware accelerators supported by PyTorch such as GPUs.
-The LSSVR implementation starts with the constructor which accepts model hyperparameters which include the regularization parameter, kernel function and any kernel parameters, verbosity level, kernel matrix computation batch size, and device to perform computations on.
-The received parameters are then stored as properties of the class instance.
-For the kernel specifically, it will be initialized with the correct default parameters when the fitting function is called.
-This is because if the kernel of choice is the radial basis function, the default scaling parameter needs to be computed from the training features as the square root of the sum of feature variance values.
-
-The optimization function that fits the model to the training data solves \lccref{eq:lssvr_solution}.
-This function is shown in \lccref{fig:lssvr_fit_function_impl}.
-The first half of the function sets up the left and right hand side matrices.
-The left hand side matrix is constructed in part with the kernel matrix.
-The kernel function used is batched to reduce the peak memory footprint.
-These matrices are then used in the second half to compute the solution using the least squares solver function from PyTorch called lstq.
-Finally, the result is split into the biases and Lagrange multipliers which are then returned as a tuple.
-The optimizing function is wrapped in a more user-friendly function which allows the use of NumPy arrays in addition to the PyTorch Tensor used in the optimizing function.
-The wrapper function is named fit.
-It conforms the inputs provided by the user into the expected types and matrix shapes of rows for samples and columns for input features or output targets.
-The processed inputs and outputs are also stored as support vectors for use during prediction.
-The fit function returns the class instance once training is done.
-This is for method chaining purposes for ease of use when using the fit function in a chain with other functions we will discuss next, such as the prediction function.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def _optimize_parameters(
-      self,
-      X: torch.Tensor,
-      y_values: torch.Tensor,
-    ):
-
-        A = torch.empty(
-          (X.shape[0] + 1,) * 2,
-          device=self.device,
-          dtype=self.dtype,
-        )
-        A[1:, 1:] = self._batched_K(X, X)
-        A[1:, 1:].diagonal().copy_(
-            A[1:, 1:].diagonal()
-            + torch.ones(
-                (A[1:, 1:].shape[0],),
-                device=self.device,
-                dtype=self.dtype,
-            ).to()
-            / self.C
-        )
-        A[0, 0] = 0
-        A[0, 1:] = 1
-        A[1:, 0] = 1
-        shape = np.array(y_values.shape)
-        shape[0] += 1
-        B = torch.empty(
-          list(shape), device=self.device, dtype=self.dtype
-        )
-        B[0] = 0
-        B[1:] = y_values
-
-        solution: torch.Tensor = torch.linalg.lstsq(
-            A.to(dtype=torch.float), B.to(dtype=torch.float)
-        ).solution.to(dtype=self.dtype)
-
-        b = solution[0, :]
-        alpha = solution[1:, :]
-
-        return (b, alpha)
-...
-  \end{lstlisting}
-  \caption{Implementation of Least-squares Support Vector Regression fitting function.}\label{fig:lssvr_fit_function_impl}
-\end{figure}
-
-The learned multipliers and bias parameters are then used for predicting outputs from unseen sample features.
-\Cref{eq:lssvr_prediction_vectorized} shows the computation that needs to be done to compute the predicted output.
-The prediction process first constructs both matrices on the left-hand side of the equation.
-This is done by computing the kernel matrix between the prediction features and the training features, otherwise known as support vectors.
-The prediction function therefore is very straight forward with an input of unseen features and the learned parameters.
-The function output is simply the predicted outputs.
-The implementation of this function is shown in \lccref{fig:lssvr_predict_function_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-NumpyArrayorTensor = (
-    np.ndarray[typing.Any, np.dtype[np.float_]] |
-    torch.Tensor
-)
-...
-    def predict(
-        self,
-        X: NumpyArrayorTensor,
-    ) -> NumpyArrayorTensor:
-        """Predicts the labels of data X given a trained model.
-        - X: ndarray of shape (n_samples, n_attributes)
-        """
-        is_torch = isinstance(X, torch.Tensor)
-        if is_torch:
-            if X.ndim == 1:
-                X_reshaped_torch = X.reshape(-1, 1)
-            else:
-                X_reshaped_torch = X
-            X_= X_reshaped_torch.clone().to(
-                self.device, dtype=self.dtype
-            )
-        else:
-            if X.ndim == 1:
-                X_reshaped_np = X.reshape(-1, 1)
-            else:
-                X_reshaped_np = X
-            X_ = torch.from_numpy(X_reshaped_np).to(
-                self.device, dtype=self.dtype
-            )
-
-        KxX = self._batched_K(X_, self.sv_x)
-
-        y_pred = KxX @ self.alpha + self.b
-        predictions: NumpyArrayorTensor
-        if is_torch:
-            predictions = y_pred.to(X)
-        else:
-            predictions = y_pred.cpu().numpy()
-
-        if X.ndim == 1:
-            return predictions.reshape(-1)
-        else:
-            return predictions
-...
-  \end{lstlisting}
-  \caption{Implementation of Least-squares Support Vector Regression prediction function.}\label{fig:lssvr_predict_function_impl}
-\end{figure}
-
-Aside from these core functions, interpretation of the model using the methods introduced by \textcite{ustunVisualisationInterpretationSupport2007} are also implemented in the LSSVR class.
-First, using the support vectors and the kernel matrix computed between each support vectors, the correlation image is computed.
-This image, which is a correlation matrix, is intended to visualize the importance of features within kernel functions.
-This is simply computed with matrix multiplication between the kernel matrix and the support vectors.
-The implementation is shown in \lccref{fig:lssvr_correlation_image_function_impl}.
-The batched kernel function is used in this case to mitigate the memory footprint.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def get_correlation_image(self):
-        return self._batched_K(
-            self.sv_x, self.sv_x
-        ).mm(self.sv_x)
-...
-  \end{lstlisting}
-  \caption{Implementation of Least-squares Support Vector Regression correlation image function.}\label{fig:lssvr_correlation_image_function_impl}
-\end{figure}
-
-The other interpretation method introduced by \textcite{ustunVisualisationInterpretationSupport2007} visualizes the relationship learned between the input features and the outputs.
-This visualization is computed as the matrix multiplication between the support vectors and the learned Lagrange multipliers.
-The support vector matrix is transposed so that the multiplication is done on the dimension that indexes each sample.
-This computation is implemented as shown in \lccref{fig:lssvr_p_matrix_function_impl}.
-The resulting matrix is termed the p-matrix.
-The columns of this matrix represents the outputs and the rows represents the input features.
-The p-matrix values show how each feature contribute to the output learned by the model.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def get_p_matrix(self):
-        return self.sv_x.T.mm(self.alpha)
-...
-  \end{lstlisting}
-  \caption{Implementation of Least-squares Support Vector Regression p-matrix function.}\label{fig:lssvr_p_matrix_function_impl}
-\end{figure}
-
-The second component of the model modules is the SpectralSVR implementation that uses a multi-output support vector regression (SVR) model to learn in the spectral domain, such as the LSSVR implementation in the first component.
-The SpectralSVR is implemented as a class that extends the LSSVR to be able to learn from features and labels which are complex valued, which is the case for Fourier series coefficients.
-First, the constructor used to initialize each SpectralSVR instance accepts a Basis instance, an SVR instance which is the implemented LSSVR by default, and the verbosity of the model.
-These parameters are then used when the training function shown in \lccref{fig:spectralsvr_train_impl} is called.
-Training the SpectralSVR model begins by calling the train function with parameters of the input function representation, output function representation, and an indicator of whether the output function is time dependent.
-Then, the function ensures that the features and labels are matrices.
-And then, if the input or output function representations are complex, they are transformed into the real representation.
-These formatted training data features and labels are then used to train the LSSVR model itself.
-Finally, to again allow for chaining methods, the function returns the current class instance.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def train(
-        self,
-        f: torch.Tensor,
-        u_coeff: torch.Tensor,
-        u_time_dependent: bool = False,
-    ):
-        self.basis.time_dependent = u_time_dependent
-        if self.basis.coeff_dtype.is_complex:
-            u_coeff = to_complex_coeff(u_coeff)
-
-        if f.ndim > 2:
-            f = f.flatten(1)
-        if u_coeff.ndim > 2:
-            u_coeff = u_coeff.flatten(1)
-
-        if torch.is_complex(u_coeff):
-            u_coeff = to_real_coeff(u_coeff)
-        if torch.is_complex(f):
-            f = to_real_coeff(f)
-        self.svr.fit(f, u_coeff)
-        return self
-...
-  \end{lstlisting}
-  \caption{Implementation of SpectralSVR training function.}\label{fig:spectralsvr_train_impl}
-\end{figure}
-
-Using the learned data to predict other output function representations from unseen input functions can be done by directly calling the predict function of the LSSVR\@.
-This results in the real representation which needs to be converted into the complex representation for the FourierBasis.
-Once the conversion is done, the coefficients can be used to construct a new FourerBasis instance of the predictions.
-From there, the predicted functions can be evaluated and  plotted.
-However, if one simply wants to evaluate the value of the predicted function at arbitrary points, another function is implemented to provide ease of use for this exact case.
-The implemented function is called forward as displayed in \lccref{fig:spectralsvr_forward_impl}.
-The arguments to this function are the input functions, the evaluation points, and the domain span.
-The function first predicts the output function coefficients.
-Then, the predicted coefficients are multiplied with the basis function values at each point to compute the final predicted point values.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def forward(
-        self,
-        f: torch.Tensor,
-        x: torch.Tensor,
-        periods: tuple[float, ...]
-        | None = None,
-    ) -> torch.Tensor:
-        if len(x.shape) == 1:
-            x = x.unsqueeze(-1)
-
-        # compute coefficients
-        if torch.is_complex(f):
-            f = to_real_coeff(f)
-        coeff = self.svr.predict(f)
-        # convert to complex if basis needs complex values so that the reshaping is correct
-        if self.basis.coeff_dtype.is_complex:
-            coeff = to_complex_coeff(coeff)
-
-        return self.basis.evaluate(
-            coeff=coeff.reshape((f.shape[0], *self.modes)),
-            x=x,
-            periods=periods,
-            time_dependent=self.basis.time_dependent,
-        )
-...
-  \end{lstlisting}
-  \caption{Implementation of SpectralSVR forward function (pointwise prediction).}\label{fig:spectralsvr_forward_impl}
-\end{figure}
-
-The final core piece of functionality the SpectralSVR class provides is the inverse parameter estimation.
-This is implemented to solve inverse problems such as predicting the initial conditions for the Burgers' equation or heat equation.
-This function essentially does the gradient descent on a loss function in such a way that the output function matches some expected output.
-The loss function is simply a measure of how far the outputs of the current predicted inputs are from the target outputs.
-The loss function is formulated as the mean squared error of the difference between the predicted output and expected output.
-Using some randomly initialized values as the inputs, the predicted output is then used to compute the loss.
-The gradient of the loss with respect to the inputs are then computed and then used to perform optimization of the inputs using the ADAM optimizer.
-This is implemented as the inverse function shown in \lccref{fig:spectralsvr_inverse_impl}.
-The function arguments are the expected output function coefficients, evaluation points, the loss function used, how many optimization loops are done, the random number generator, and the gain which is used in generating the random initial input functions.
-The function returns the estimated input function coefficients in the real representation.
-For Fourier coefficients this means that the predicted input coefficients need to first be converted to complex valued tensors and then used to construct a FourierBasis instance.
-For convenience, a wrapper like the forward function is also implemented for evaluating the function values of the predicted input coefficients.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def inverse_coeff(
-        self,
-        u_coeff: torch.Tensor,
-        loss_fn: Callable[
-            [torch.Tensor, torch.Tensor], torch.Tensor
-        ] = mean_squared_error,
-        epochs=100,
-        generator=torch.Generator().manual_seed(42),
-        gain=0.05,
-        **optimizer_params,
-    ):
-        f_shape = (u_coeff.shape[0], self.svr.sv_x.shape[1])
-        complex_coeff = u_coeff.is_complex()
-        original_device = u_coeff.device
-        u_coeff = to_real_coeff(u_coeff.flatten(1)).to(self.svr.device)
-
-        # inverse problem
-        f_coeff_pred = (
-            torch.randn(f_shape, generator=generator).to(self.svr.device) * gain
-        )
-        f_coeff_pred.requires_grad_()
-        optim = torch.optim.Adam([f_coeff_pred], **optimizer_params)
-
-        for epoch in range(epochs):
-            optim.zero_grad()
-            u_coeff_pred = self.svr.predict(f_coeff_pred)
-            loss = loss_fn(u_coeff_pred, u_coeff)
-            loss.backward()
-            optim.step()
-        optim.zero_grad()
-        f_coeff_pred.requires_grad_(False)
-        if complex_coeff:
-            f_coeff_pred = to_complex_coeff(f_coeff_pred)
-        return f_coeff_pred.to(original_device)
-...
-  \end{lstlisting}
-  \caption{Implementation of SpectralSVR inverse coeff function (parameter estimation).}\label{fig:spectralsvr_inverse_impl}
-\end{figure}
-
-The SpectralSVR class also provides a convenience function for testing the performance of the learned model.
-This function is shown in \lccref{fig:spectralsvr_test_impl}.
-The function arguments are the testing inputs, expected testing outputs, and a resolution for evaluation of function values.
-The first step is to convert the testing input into real representations and then predicting the output function.
-The predicted output are then compared to the testing outputs using many metrics including RMSE, MSE, MAE, R\textsuperscript{2}, SMAPE, RRSE, and the number of Nan values present in the predicted output.
-The same comparison process is carried out again for the function values which are evaluated at the specified resolution.
-Finally, the function returns the metric values as a nested tuple for both the coefficients predictions and the function value predictions.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def test(
-        self,
-        f: torch.Tensor,
-        u_coeff_targets: torch.Tensor,
-        res: ResType = 200,
-    ):
-        if torch.is_complex(f):
-            logger.debug("transform f to real")
-            f = to_real_coeff(f)
-        u_coeff_preds = self.svr.predict(f)
-        if torch.is_complex(u_coeff_targets):
-            logger.debug("transform u_coeff to real")
-            u_coeff_targets = to_real_coeff(u_coeff_targets)
-
-        grid = self.basis.grid(res).flatten(0, -2)
-        u_preds = self.basis.evaluate(
-            coeff=to_complex_coeff(u_coeff_preds),
-            x=grid,
-            time_dependent=self.basis.time_dependent,
-        ).real
-        u_targets = self.basis.evaluate(
-            coeff=to_complex_coeff(u_coeff_targets),
-            x=grid,
-            time_dependent=self.basis.time_dependent,
-        ).real
-        return {
-            "spectral": get_metrics(
-                u_coeff_preds, u_coeff_targets
-            ),
-            "function value": get_metrics(u_preds, u_targets),
-        }
-...
-  \end{lstlisting}
-  \caption{Implementation of SpectralSVR test function.}\label{fig:spectralsvr_test_impl}
-\end{figure}
-
-\subsubsection{Problems}
-
-\noindent The final module implements the PDEs that will serve as problems the proposed modules will solve.
-The implementation is mainly responsible for generating datasets from the PDEs and computing the PDE residuals.
-This implementation is focused on the two synthetic datasets which are the antiderivative problem and the Burgers' equation problem.
-The problem base class is implemented as an abstract class that the specific problems will subclass.
-The base class requires any subclass to implement three methods.
-First, the data generation method which receives specifications such as what basis functions to use, how many function samples to create, how many modes are needed for each sample, and a PyTorch generator that will be used in generating the random basis coefficients.
-Other arguments more specific to each problem will be implemented by the specific subclass.
-This function is then expected to return a tuple of Basis instances.
-The second and third functions are the spectral and function value residuals for the PDE of each subclass, respectively.
-These three functions make up the functionality that is offered by all Problem subclasses.
-The implementation of the Problem subclass can be seen in \lccref{fig:problem_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-import abc
-import torch
-from ..basis import BasisSubType
-
-class Problem(abc.ABC):
-    def __init__(self) -> None:
-        super().__init__()
-
-    @abc.abstractmethod
-    def generate(
-        self,
-        basis: type[BasisSubType],
-        n: int,
-        modes: int | tuple[int, ...],
-        *args,
-        generator: torch.Generator | None = None,
-        **kwargs,
-    ) -> tuple[BasisSubType, ...]:
-        pass
-
-    @abc.abstractmethod
-    def spectral_residual(
-        self, u: BasisSubType, *args, **kwargs
-    ) -> BasisSubType:
-        pass
-
-    @abc.abstractmethod
-    def residual(
-        self, u: BasisSubType, *args, **kwargs
-    ) -> BasisSubType:
-        pass
-  \end{lstlisting}
-  \caption{Implementation of Problem base class.}\label{fig:problem_impl}
-\end{figure}
-
-The antiderivative problem is relatively simple to implement.
-The generation function takes advantage of the gradient operation and generate function provided by the Basis subclasses.
-The arguments to this function are the same as the base class with the addition of an integration constant parameter.
-By default, the value of the integration constant is zero.
-The function then returns the tuple of basis subclass instances representing the derivative and antiderivative functions.
-This function can be seen in \lccref{fig:antiderivative_generate_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def generate(
-        self,
-        basis: Type[BasisSubType],
-        n: int,
-        modes: int | tuple[int, ...],
-        u0: float | int | complex,
-        *args,
-        generator: torch.Generator | None = None,
-        **kwargs,
-    ) -> tuple[BasisSubType, BasisSubType]:
-        if isinstance(modes, int):
-            modes = (modes,)
-        # generate solution functions
-        u = basis.generate(
-            n, modes, generator=generator, *args, **kwargs
-        )
-        # compute derivative functions
-        ut = u.grad()
-        # set the integration coefficient
-        if isinstance(u0, complex):
-            if u.coeff.is_complex():
-                u.coeff[:, 0] = torch.tensor(u0)
-            else:
-                u.coeff[:, 0] = torch.tensor(u0).real
-        elif isinstance(u0, float) or isinstance(u0, int):
-            if u.coeff.is_complex():
-                u.coeff[:, 0] = torch.tensor(u0 + 0j)
-            else:
-                u.coeff[:, 0] = torch.tensor(u0)
-        else:
-            u.coeff[:, 0] = u0
-
-        return (u, ut)
-...
-  \end{lstlisting}
-  \caption{Implementation of Antiderivative generate function.}\label{fig:antiderivative_generate_impl}
-\end{figure}
-
-The residual functions are similarly easy to implement as shown in \lccref{fig:antiderivative_residual_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def spectral_residual(
-        self, u: BasisSubType, ut: BasisSubType
-    ) -> BasisSubType:
-        residual = u.grad() - ut
-        if residual.coeff is not None:
-            residual.coeff[:, 0].mul_(0)
-
-        return residual
-
-    def residual(
-        self, u: BasisSubType, ut: BasisSubType
-    ) -> BasisSubType:
-        u_val, grid = u.get_values_and_grid()
-        ut_val = ut.get_values()
-        dt = grid[1, 0] - grid[0, 0]
-        u_grad = torch.gradient(
-            u_val, spacing=dt.item(), dim=1
-        )[0]
-        residual_val = u_grad - ut_val
-        residual = u.copy()
-        residual.coeff = u.transform(residual_val)
-        return residual
-...
-  \end{lstlisting}
-  \caption{Implementation of Antiderivative residual functions.}\label{fig:antiderivative_residual_impl}
-\end{figure}
-
-For the Burgers' equation, the problem subclass for this PDE implemented a generate function with two generation paths.
-But before discussing the specifics of the two paths, the function has some extra arguments and preprocessing of those arguments.
-This time the function asks for the kind of functions the initial condition and the forcing term needs to be, whether they are random or constant.
-The combination of the kind of functions the initial conditions and forcing terms are will determine the path of generation that the function will take.
-The function also requires the viscosity parameter nu which is 0.01 by default.
-The domain also needs to be specified with a default value of 0 to 1 with 200 grid points for both space and time.
-The solver which is used for one of the generation procedures is also an argument with a default of the implicit Adams solver from torchdiffeq \autocite{Chen_torchdiffeq_2021}.
-Finally, whether the output basis coefficients are time dependent or not is passed in as an argument alongside with the PyTorch generator.
-The implementation of this portion of the function can be seen in \lccref{fig:burgers_generate_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def generate(
-        self,
-        basis: Type[BasisSubType],
-        n: int,
-        modes: int | tuple[int, ...],
-        u0: ParamInput | BasisSubType = "random",
-        f: ParamInput | BasisSubType = 0,
-        nu: float = 0.01,
-        space_domain=slice(0, 1, 200),
-        time_domain=slice(0, 1, 200),
-        solver: SolverSignatureType = implicit_adams_solver,
-        time_dependent_coeff: bool = True,
-        *args,
-        generator: torch.Generator | None = None,
-        **kwargs,
-    ) -> tuple[BasisSubType, BasisSubType]:
-        if isinstance(modes, int):
-            modes = (modes,)
-
-        device = "cuda:0" if torch.cuda.is_available() else "cpu"
-
-        L = space_domain.stop - space_domain.start
-        x = (
-            basis.grid(slice(
-                space_domain.start, space_domain.stop, modes[0]
-            )).flatten(0, -2)
-            .to(device=device)
-        )
-        T: float = time_domain.stop - time_domain.start
-        nt = int(time_domain.step)
-        # nt = int(T / (0.01 * nu) + 2)
-        dt = T / (nt - 1)
-        t = basis.grid(time_domain).flatten().to(device=device)
-        periods = (T, L)
-...
-  \end{lstlisting}
-  \caption{Implementation of Burgers generate function.}\label{fig:burgers_generate_impl}
-\end{figure}
-
-The first generation path and most similar to the antiderivative case is when both the initial condition and forcing terms are random.
-This branch of the generate function utilizes the residual function to compute the forcing term from the randomly generated solution function.
-This method of generating the solution and forcing term is stable and relatively straightforward.
-The implementation of this branch is shown in \lccref{fig:burgers_generate_manufactured_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-        if u0 == "random" and f == "random":
-            # use method of manufactured solution
-            time_mode = modes[0]
-            if len(modes) > 1:
-                modes = modes[1:]
-            u = basis.generate(
-                n,
-                (time_mode, *modes),
-                periods=periods,
-                generator=generator,
-            )
-            res_modes = tuple(slice(0, L, mode) for mode in modes)
-            fst = self.spectral_residual(
-                u,
-                basis(
-                    basis.generate_empty(n, (time_mode, *modes))
-                ),
-                nu,
-            )
-            u_gen = u
-            f_gen = fst
-            # convert to timed dependent coeffs
-            if time_dependent_coeff:
-                u_val = u.get_values(res=(time_domain, *res_modes))
-                u_coeff = basis.transform(
-                    u_val.flatten(0, 1)
-                ).reshape((n, nt, *modes))
-                u_gen = basis(
-                    coeff=u_coeff,
-                    time_dependent=True,
-                    periods=periods
-                )
-
-                f_val = fst.get_values(
-                    res=(time_domain, *res_modes)
-                )
-                f_coeff = basis.transform(
-                    f_val.flatten(0, 1)
-                ).reshape((n, nt, *modes))
-                f_gen = basis(
-                    coeff=f_coeff,
-                    time_dependent=True,
-                    periods=periods
-                )
-...
-  \end{lstlisting}
-  \caption{Implementation of Burgers generate function manufactured method.}\label{fig:burgers_generate_manufactured_impl}
-\end{figure}
-
-The second case is when at least one of the initial condition or forcing term is not random.
-This second case requires solving the Burgers' equation using traditional numerical methods.
-The generate function calls a function that has the responsibility of setting up the constant initial conditions or constant forcing terms and then calls the ODE solver specified in the generate function arguments.
-The right-hand side function computes the time derivative based on \lccref{eq:time_derivative_time_step_function}.
-The implementation of this is show in \lccref{fig:burgers_generate_dt_impl}.
-Putting the above together gives us the implementation of the method of lines generation of Burgers' equation solution and forcing term as show in \lccref{fig:burgers_generate_mol_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    @staticmethod
-    def rhs(
-        basis: type[Basis],
-        nu: float,
-        u_hat: torch.Tensor,
-        f_hat: torch.Tensor,
-    ) -> torch.Tensor:
-        u = basis(u_hat)
-        dealias_modes = tuple(
-            int(mode * 1.5) for mode in u.modes
-        )
-        u_dealiased = u.resize_modes(
-            dealias_modes, rescale=False
-        )
-        u_val = basis.inv_transform(u_dealiased.coeff)
-        uu_x_hat_dealiased = 0.5 * basis.transform(u_val**2)
-        uu_x = basis(
-            uu_x_hat_dealiased
-        ).resize_modes(u.modes, rescale=False).grad()
-
-        u_u_x_hat = uu_x.coeff
-        u_xx_hat = u.grad().grad().coeff
-        u_t_hat = nu * u_xx_hat + f_hat - u_u_x_hat
-        return u_t_hat
-...
-  \end{lstlisting}
-  \caption{Implementation of Burgers generate function time derivative.}\label{fig:burgers_generate_dt_impl}
-\end{figure}
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-        u0.coeff = u0.coeff.to(device=device)
-        fst.coeff = fst.coeff.to(device=device)
-        print(f"generating with {len(t)} time steps")
-
-        def f_func(t: torch.Tensor, x: torch.Tensor = x):
-            x = x.tile((1, 2))
-            x[:, 0] = t
-            return basis.transform(
-                fst(x).reshape((-1, modes[0]))
-            )
-
-        def rhs_func(t: torch.Tensor, y0: torch.Tensor):
-            y0 = to_complex_coeff(y0)
-            return to_real_coeff(
-                cls.rhs(basis, nu, y0, f_func(t))
-            )
-
-        u_hat = solver(rhs_func, to_real_coeff(u0.coeff), t)
-        if basis.coeff_dtype.is_complex:
-            u_shape = u_hat.shape
-            u_hat = to_complex_coeff(
-                u_hat.flatten(0, 1)
-            ).reshape(
-                (*u_shape[:2], *u0.coeff.shape[1:])
-            )
-
-        u_hat = u_hat.movedim(0, 1)
-        if timedependent_solution:
-            u = basis(u_hat, **kwargs, time_dependent=True)
-        else:
-            u_hat = u_hat.reshape((n * nt, modes[0]))
-            u = basis(
-                basis.transform(
-                    basis.inv_transform(u_hat).reshape(
-                        (n, nt, modes[0])
-                    )
-                ),
-                **kwargs,
-            )
-        u.coeff = u.coeff.cpu()
-        fst.coeff = fst.coeff.cpu()
-        return (u, fst)
-...
-  \end{lstlisting}
-  \caption{Implementation of Burgers generate function method of lines.}\label{fig:burgers_generate_mol_impl}
-\end{figure}
-
-The spectral residual of the Burgers' equation which is used in the method of manufactured solution generation approach is implemented as shown in \lccref{fig:burgers_spectral_residual_impl}.
-As with the right-hand side function, we use the psuedospectral approach for computing the convolution term to avoid large computational expenses for higher number of modes.
-The function value residual is also implemented similarly to the antiderivative version.
-The derivatives are computed with the PyTorch gradient function.
-And then using \lccref{eq:forced_viscous_burgers}, the residual is computed by subtracting the forcing term from both sides.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def spectral_residual(
-        self, u: BasisSubType, f: BasisSubType, nu: float
-    ) -> BasisSubType:
-        u_t = u.grad(dim=0, ord=1)
-
-        dealias_modes = tuple(
-            int(mode * 1.5) for mode in u.modes
-        )
-        u_dealiased = u.resize_modes(
-            dealias_modes, rescale=False
-        )
-        u_val = u.inv_transform(u_dealiased.coeff)
-        uu_dealiased = u.copy()
-        uu_dealiased.coeff = u.transform(u_val.pow(2).mul(0.5))
-        uu_x = uu_dealiased.resize_modes(
-            u.modes, rescale=False
-        ).grad(dim=1)
-
-        u_xx = u.grad(dim=1, ord=2)
-        nu_u_xx = u_xx
-        nu_u_xx.coeff = nu_u_xx.coeff * nu
-
-        residual = u_t + uu_x - nu_u_xx - f
-        return residual
-...
-  \end{lstlisting}
-  \caption{Implementation of Burgers spectral residual function.}\label{fig:burgers_spectral_residual_impl}
-\end{figure}
-
-\subsection{Testing}
-\noindent The implementation is followed by tests of the functionality core to this study.
-The testing is done using the PyTest library.
-The testing method used is a black box approach.
-The tests are written in a separate \verb|tests| directory.
-Each module is tested by a separate file.
-The tests are done to ensure compliance of the implementation to the requirements of the software.
-The final results are presented in \lccref{table:impl_test_result}.
-Each version and iteration of the development must ensure that the tests are passed before any changes are committed to the GitHub repository.
-
-\begin{table}[H]
-  \centering
-  \begin{tabular}{lm{0.2\linewidth}m{0.5\linewidth}l}
-    % \toprule
-    \toprule
-    No & Process                         & Test Target                                                                                                   & Test Result \\
-    \midrule
-    1  & Transform                       & Transform invertible with inverse transform                                                                   & Achieved    \\\addlinespace[0.5em]
-    2  & Evaluation                      & Transform coefficient evaluation close to original values                                                     & Achieved    \\\addlinespace[0.5em]
-    3  & Plot                            & Plotting function is run successfully                                                                         & Achieved    \\\addlinespace[0.5em]
-    4  & Perturb                         & Perturb function is run successfully                                                                          & Achieved    \\\addlinespace[0.5em]
-    5  & Operations                      & Operation functions is run successfully                                                                       & Achieved    \\\addlinespace[0.5em]
-    6  & Complex Coefficients Conversion & Conversion between real and complex coefficient representation is invertible for odd and even number of modes & Achieved    \\\addlinespace[0.5em]
-    7  & SpectralSVR Train               & Training function is run successfully                                                                         & Achieved    \\\addlinespace[0.5em]
-    8  & SpectralSVR Prediction          & Coefficient prediction error within tolerable range                                                           & Achieved    \\\addlinespace[0.5em]
-    9  & SpectralSVR Prediction          & Function value prediction error within tolerable range                                                        & Achieved    \\
-    \bottomrule
-  \end{tabular}
-  \caption{Testing results of the SpectralSVR Library implementation using black box method.}\label{table:impl_test_result}
-\end{table}
-
-\section{Experimental Scenarios}\label{sec:experimental_scenarios}
-\noindent To achieve the goals of this study, as outlined in \lccref{sec:aims}, we present three experimental scenarios.
-These scenarios represent different experimental configurations that will be applied to our implementation of the SpectralSVR library.
-A table of the configurations for each scenario can be seen in \lccref{table:experimental_scenarios}.
-
-\begin{table}[H]
-  \caption{The configuration of experimental scenarios in this study.}\label{table:experimental_scenarios}
-  \centering
-  \begin{tabularx}{\textwidth}{L{0.75}*{3}{L{1.09}}} % compute these using approx barycentric coords (x + 3y = 4, x = 0.8y)
-    \toprule
-    Configuration                    & Scenario 1                                          & Scenario 2                                                          & Scenario 3                                 \\
-    \midrule
-    Data Source                      & Synthetic (computed from equations)                 & Synthetic (computed from equations) with three viscosity values     & ERA5 dataset                               \\\addlinespace[0.5em]
-    Data Augmentations               & Perturbations of three different noise levels       & Perturbation of 10\% the mean standard deviation of function values &                                            \\\addlinespace[0.5em]
-    Data Sample Size                 & 5000 unique functions for each noise level          & 500 unique functions for each viscosity value                       & 7000 time steps                            \\\addlinespace[0.5em]
-    Number of Modes                  &                                                     &                                                                     &                                            \\\addlinespace[0.5em]
-    Scaling                          & Standard scaling                                    & Standard scaling                                                    & Standard scaling                           \\\addlinespace[0.5em]
-    Dataset Split                    & 80\% Training and 20\% Testing for each noise level & 80\% Training and 20\% Testing for each viscosity value             & 80\% Training and 20\% Testing             \\\addlinespace[0.5em]
-    Regularization Parameter (\(C\)) & 1.0                                                 & 1.0                                                                 & 1.0                                        \\\addlinespace[0.5em]
-    Kernel                           & RBF (\(\sigma = features \times X.var()\))          & RBF (\(\sigma = features \times X.var()\))                          & RBF (\(\sigma = features \times X.var()\)) \\\addlinespace[0.5em]
-    Additional Tests                 & Exact solutions                                     & Exact solutions                                                     &                                            \\\addlinespace[0.5em]
-    Interpretation                   & p-matrix and correlation image                      & p-matrix and correlation image                                      & p-matrix and correlation image             \\
-    \bottomrule
-  \end{tabularx}
-\end{table}
-
-Each scenario serves a different purpose.
-The first scenario is constructed to establish whether the model can learn any relationships at all in data that implicitly defines differential equations.
-This scenario is a proof of concept of whether the model is capable of accurately learning the relationship between derivatives and their anti-derivatives.
-As the simplest case, it provides a foundation for understanding the model and its behavior.
-The 5\% noise model is then used to predict the antiderivative of a cosine function with a period of one as shown in \lccref{eq:sine_derivative}.
-The exact solution is known as \lccref{eq:sine_function} \autocite{abramowitzHandbookMathematicalFunctions1972}.
-The second goal of this scenario is to determine how noise affects the model's predictions.
-This is especially important for the inverse problem because of how sensitive the derivative is to changes in the antiderivative.
-To further solidify how the model fares for inverse problems, this scenario will also assess the performance of a trained model for a very simple inverse problem setup to determine the derivatives of the testing subset from the antiderivatives.
-This setup will utilize the model as a surrogate forward solver and optimize for a loss function using the inverse function of the SpectralSVR class as described in \lccref{sec:impl_model}.
-\begin{align}
-  f(x) & = 2\pi \cos\left(2\pi x\right)\label{eq:sine_derivative} \\
-  f(x) & = \sin\left(2\pi x\right)\label{eq:sine_function}
-\end{align}
-
-The second scenario extends the goal of the first scenario by examining the model and its behavior when learning a nonlinear PDE\@.
-The data subsets with different viscosity values are intended to allow us to learn more about how this will affect the performance on the exact solutions for lower viscosity numbers.
-The model will learn to predict future states of systems governed by the Burgers' equation from past states.
-The model for each viscosity will be used to predict \lccref{eq:burgers_exact_solution} from initial conditions at time equals zero and the corresponding forcing term of a constant value of zero.
-The exact equation prediction will be done using a rollout method.
-The initial condition along with the initial forcing term will be given to the model to predict the solution at the first time step.
-The model will then use the predicted solution with the forcing term at the first time step to predict the solution at the second time step.
-This is repeated until the stopping condition of time \(t=10\).
-The forcing term for the exact solution is a constant zero.
-Along with the rollout of the exact solution, we also perform roll out on one of the test solution.
-
-The third scenario is designed to demonstrate the modeling capability of SpectralSVR on a more practical problem of weather prediction.
-The earth weather system is a complex collection of processes.
-Using the ERA5 dataset, the model will be used to predict future states of the atmosphere from previous states.
-Specifically, the model will learn to predict the temperature 2 meters above the surface.
-That means that other than the time and spatial resolution not being the highest, the model will also learn from partial information of the relationships defined by the equation since no other variables will be included.
-This choice was made as an analog for situation with unknown PDEs and therefore unknown variables.
-With these situations, there is no guarantee that the variables measured have any relation with the system.
-These three scenarios together address the last two aims of this study.
-
-\section{Experimental Results}\label{sec:experimental_results}
-\noindent In this section, the results of each experimental scenario is presented and analyzed. The results come in the form of testing metrics mentioned in . %TODO: add reference to the metrics used.
-The model interpretations are displays of the correlation image and the p-matrix. The function values and coefficients themselves will also be plotted depending on the number of dimensions.
-
-\subsection{Scenario 1}
-\noindent The first scenario results are presented in four parts.
-The first is the coefficient prediction metrics which is shown in \lccref{table:scenario_1_spectral_metrics}.
-The table shows the noise level and the performance metrics.
-\begin{table}[H]
-  \caption{Performance metrics of coefficient prediction in scenario 1 by noise level.}\label{table:scenario_1_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrrrrrrr}
-    \toprule
-    Noise level & MSE   & RMSE & MAE  & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    5\%         & 0.86  & 0.93 & 0.57 & 0.96 & 0.31  \\
-    10\%        & 2.06  & 1.43 & 0.93 & 0.91 & 0.46  \\
-    50\%        & 15.59 & 3.95 & 3.04 & 0.50 & 1.04  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The scenario is implemented as a Jupyter notebook which imports relevant libraries and our SpectralSVR library.
-The notebook starts with creating the data with the Antiderivative problem subclass.
-All random processes use the same PyTorch Generator instance with a seed of 42.
-The data is then augmented by perturbing the function values to create three versions with the noise levels mentioned in the scenario.
-Looping through each version, the training and testing subsets are randomly sampled to result in 80\% and 20\% of the original dataset respectively.
-Then the scaling function is fitted on the training subset inputs.
-And then, both the training and testing inputs are transformed using the fitted scaling function.
-Next, an instance of SpectralSVR is trained and tested.
-Finally, the metrics are stored and the next noise level is processed.
-Next the 5\% noise model is used to predict the antiderivative of a sine function.
-
-The kernel scaling hyperparameter sigma has the same value of 10 for all noise levels.
-This is because the inputs are all scaled to approximately have a standard deviation of one.
-The value itself is from the number of features which comes out to 100 total inputs to the LSSVR\@.
-
-\Cref{table:scenario_1_spectral_metrics} shows that the model is able to generalize from the training data and learn the simple linear antiderivative operator.
-Focusing on the coefficient of determination (R\textsuperscript{2}) scores, we can see that the model is off by 0.04 to the perfect score of 1.0 for the lowest noise level.
-While increasing noise levels does degrade the performance, this is partly due to the target values also having been perturbed.
-This fact can be seen if we look at how predictions from the very same trained models on noisy inputs are compared to the noise-free versions of the antiderivative functions which is shown in \lccref{table:scenario_1_clean_spectral_metrics}.
-The metrics show that the model predictions are slightly closer to the unperturbed function coefficients compared to the perturbed versions.
-This can be seen as the influence of the independent synthetic measurement noise in the perturbed targets being removed from the testing metrics.
-
-The higher noise levels shows that the model is still relatively accurate.
-Looking at the R\textsuperscript{2} score for the 50\% noise level, the model is more accurate than a baseline mean value model.
-The R\textsuperscript{2} score of 0.5 means that the model predictions has roughly half the error the baseline would produce.
-
-\begin{table}[H]
-  \caption{Performance metrics of coefficient prediction compared to unperturbed targets in scenario 1 by noise level.}\label{table:scenario_1_clean_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrrrrrr}
-    \toprule
-    Noise level & MSE  & RMSE & MAE  & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    5\%         & 0.79 & 0.89 & 0.51 & 0.96 & 0.28  \\
-    10\%        & 1.80 & 1.34 & 0.80 & 0.92 & 0.40  \\
-    50\%        & 9.30 & 3.05 & 2.23 & 0.62 & 0.90  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The function values are also evaluated and the values of the metrics between the noisy targets and predictions are shown in \lccref{table:scenario_1_function_metrics}.
-While the relative metrics R\textsuperscript{2} and sMAPE stay close to the values we obtained for the coefficients themselves, since the metrics are now being computed in the physical domain, the scales have changed and because of that the values of the absolute metrics now reflect the change in scale.
-For reference, the scale of the target coefficient values for the 50\% noise level dataset in their real representation can range on average from -13.54 to 13.6 across the entire dataset.
-Therefore, an RMSE value of 3.94 for the predictions compared to the noisy targets mean that the error ratio is roughly 0.148 or just above 1 to 7.
-For the function values of the 50\% noise dataset the values range on average from -2.5 to 2.49.
-This was more difficult to compute since there is no direct way to compute the amplitude of the function from just the coefficients.
-Here we used the inverse transform and extracted the maximum and minimum values of each function from the discrete values.
-Since the RMSE in \lccref{table:scenario_1_function_metrics} for the 50\% noise dataset is 0.63, the error ratio comes to 0.126.
-One side note about \lccref{table:scenario_1_function_metrics} is that since the model instances are the same as the ones used in the coefficient evaluations, the hyperparameters are still the same including the kernel scaling factor sigma.
-\begin{table}[H]
-  \caption{Performance metrics of function value from evaluated coefficient prediction in scenario 1 by noise level.}\label{table:scenario_1_function_metrics}
-  \centering
-  \begin{tabular}{lrrrrrrrr}
-    \toprule
-    Noise level & MSE  & RMSE & MAE  & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    5\%         & 0.03 & 0.18 & 0.15 & 0.97 & 0.39  \\
-    10\%        & 0.08 & 0.29 & 0.23 & 0.92 & 0.55  \\
-    50\%        & 0.62 & 0.79 & 0.63 & 0.49 & 1.05  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-For the metrics between the predictions and the noise-free version of the target function values, the results parallel the outcomes of the coefficient predictions.
-The metrics show that the model performs slightly better with more pronounced differences for the higher noise levels.
-This echoes our previous statement on the effect of independent \enquote{measurement} noise in the target values on the evaluation metrics.
-\begin{table}[H]
-  \caption{Performance metrics of function value from evaluated coefficient prediction compared to unperturbed targets in scenario 1 by noise level.}\label{table:scenario_1_clean_function_metrics}
-  \centering
-  \begin{tabular}{lrrrrrrr}
-    \toprule
-    Noise level & MSE  & RMSE & MAE  & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    5\%         & 0.03 & 0.18 & 0.14 & 0.97 & 0.38  \\
-    10\%        & 0.07 & 0.27 & 0.21 & 0.93 & 0.53  \\
-    50\%        & 0.37 & 0.61 & 0.49 & 0.62 & 0.94  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The next part of this scenario is the results from predicting the exact solution of \lccref{eq:sine_derivative} which is \lccref{eq:sine_function}.
-The function values will be computed with the same discretization as the number of modes we used in the training set.
-Once the values are obtained for both functions, the coefficients are computed.
-Then instancing the FourierBasis class with the coefficients of the derivative function, we can create perturbed versions according to the noise levels of the training set.
-Finally, the derivative is used to predict the noise-free antiderivative.
-The results are presented in \lccrefs{table:scenario_1_exact_spectral_metrics,table:scenario_1_exact_function_metrics}.
-For 5\% and 10\% noise levels, the model shows that it has learned the relation.
-However, the 50\% noise level, the model has been unable to predict the results well enough.
-The marked difference in error across all metrics between the 50\% and the lower noise levels is more apparent for this specific exact problem compared to the test sets.
-A clear picture of this can be seen when we compare the sMAPE metric.
-For the test set, the predictions on average results in a value of 1, however, for this exact problem the sMAPE value is 1.4 to 1.7.
-
-\begin{table}[H]
-  \caption{Performance metrics of coefficient prediction of exact antiderivative in scenario 1 by noise level.}\label{table:scenario_1_exact_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    Noise level & MSE   & RMSE & MAE  & sMAPE \\
-    \midrule
-    5\%         & 0.09  & 0.29 & 0.16 & 1.18  \\
-    10\%        & 0.80  & 0.89 & 0.31 & 1.23  \\
-    50\%        & 10.33 & 3.21 & 0.83 & 1.44  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\begin{table}[H]
-  \caption{Performance metrics of evaluated function values of coefficient prediction of exact antiderivative in scenario 1 by noise level.}\label{table:scenario_1_exact_function_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    Noise level & MSE  & RMSE & MAE  & sMAPE \\
-    \midrule
-    5\%         & 0.00 & 0.06 & 0.05 & 0.23  \\
-    10\%        & 0.03 & 0.18 & 0.15 & 0.36  \\
-    50\%        & 0.41 & 0.64 & 0.58 & 1.65  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The predictions of the exact equation is shown in \lccref{fig:antiderivative_exact}.
-Visually, we can see that as the noise level increases, the model predictions become worse.
-Another observation is how the higher the noise level, the more the predicted functions become closer to zero.
-This is explained by the double penalty phenomenon \autocite{lledoScaledependentVerificationPrecipitation2023}.
-The loss function used for LSSVR penalizes the model for predicting a non-zero value that turns out to be wrong compared to predicting a zero value.
-This results in a model with predictions that are close to the mean of the training data.
-
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/antiderivative_exact_input.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:antiderivative_exact_input}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/antiderivative_exact_prediction.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:antiderivative_exact_prediction}
-  \end{subfigure}
-  \caption{(\subref{fig:antiderivative_exact_input}) The perturbed exact input function values from \lccref{eq:sine_derivative}.\ (\subref{fig:antiderivative_exact_prediction}) Prediction of antiderivative from the input function that was perturbed.}\label{fig:antiderivative_exact}
-\end{figure}
-
-For inverse problems, we simply use the same testing set with the labels now used to predict the features.
-The model instances are still the same as before.
-With the implementation shown in \lccref{fig:spectralsvr_inverse_impl}, we run the inverse function for predicting coefficients with 2000 epochs, a learning rate of 0.02, and randomized starting point from a normal distribution multiplied by a factor of 0.05.
-The results of inverse prediction for all three noise levels are shown in \lccref{table:scenario_1_inv_spectral_metrics}.
-These metrics were computed after both the target and predicted input functions are scaled back using the same scaling functions they were scaled down with.
-Because the scales of the input and output functions are different, the absolute metrics are much larger in these results compared to the forward problem results.
-For reference, the target input coefficients on average range from -695.65 to 694.9.
-The relative metrics show that for the lower noise levels, the accuracy is still relatively good.
-However, the values are lower than the values for the forward test.
-The difference with the antiderivative prediction becomes more pronounced with the higher noise levels.
-For the highest noise level, the performance has degraded so far that the predictions are worse than a baseline model from the mean of the target input functions.
-One must also note that despite the much worse results of the other metrics for the highest noise level, at this time we're unable to explain why sMAPE results in roughly the same performance as in the forward problem.
-
-\begin{table}[H]
-  \caption{Performance metrics of coefficient inverse prediction of derivative in scenario 1 by noise level.}\label{table:scenario_1_inv_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrrr}
-    \toprule
-    Noise level & MSE      & RMSE   & MAE    & R\textsuperscript{2}    & sMAPE \\
-    \midrule
-    5\%         & 1739.56  & 41.71  & 26.44  & 0.91  & 0.36  \\
-    10\%        & 3485.10  & 59.03  & 42.19  & 0.76  & 0.52  \\
-    50\%        & 49319.73 & 222.08 & 174.48 & -0.19 & 1.05  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-Next, we have the correlation image and p-matrix for the model of each noise level.
-The results are shown in \lccref{fig:scenario_1_interpretation}.
-Each row in the figure represent the results of a model trained on a different noise level.
-The correlation image for 5\% and 10\% noise show clear lines on the coefficient corresponding to the output coefficient that was sorted.
-We can also see that the negative wave number reflection also being sorted.
-This is because of the reflection that occurs with complex Fourier coefficients for real-valued functions.
-There are other faint vertical lines you are able to see for other input coefficients.
-These faint lines are not sorted like the corresponding coefficients we mentioned before.
-Meaning, while they don't affect the particular output coefficients that were sorted, they do show that there is information embedded in the kernel matrix for these input coefficients.
-However, if we look at the 50\% noise correlation image, even the corresponding coefficient does not show a clear line or gradient.
-The lines are more noisy compared to the other noise levels.
-But the kernel still manages to embed some information.
-The p-matrices show that The model itself is able to still learn some relationship between the input coefficients and the output coefficients.
-For the 5\% and 10\% noise levels, the p-matrices show very clearly the contributions of input coefficients to the output coefficients.
-However, looking at the p-matrix for 50\% noise level, the lower wave numbers show lower contribution of input coefficients to the output coefficients.
-\begin{figure}[H]
-  \begin{adjustwidth}{-0.05\linewidth}{-0.05\linewidth}
-    \centering
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_ci_5.pgf}
-      \end{adjustbox}
-      \caption{Correlation image 5\% noise.}\label{fig:sc1_ci_5}
-    \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_pm_5.pgf}
-      \end{adjustbox}
-      \caption{The p-matrix for 5\% noise.}\label{fig:sc1_pm_5}
-    \end{subfigure}
-    % \\[\baselineskip]
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_ci_10.pgf}
-      \end{adjustbox}
-      \caption{Correlation image 10\% noise.}\label{fig:sc1_ci_10}
-    \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_pm_10.pgf}
-      \end{adjustbox}
-      \caption{The p-matrix for 10\% noise.}\label{fig:sc1_pm_10}
-    \end{subfigure}
-    % \\[\baselineskip]
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_ci_50.pgf}
-      \end{adjustbox}
-      \caption{Correlation image 50\% noise.}\label{fig:sc1_ci_50}
-    \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_pm_50.pgf}
-      \end{adjustbox}
-      \caption{The p-matrix for 50\% noise.}\label{fig:sc1_pm_50}
-    \end{subfigure}
-  \end{adjustwidth}
-  \caption{Correlation image (left column) and p-matrix (right column) for each model trained on a different noise level (row).
-The correlation image was sorted same order the values of the real component of wave number \(k=2\) were sorted in descending order.}\label{fig:scenario_1_interpretation}
-\end{figure}
-
-The final observation we make is how for all the p-matrices the pronounced contribution of the input wave number to their corresponding output wave number.
-This means that the majority of contributions to each output coefficients come from the corresponding input coefficients of the same wave number.
-Our knowledge on how the simple derivative equation for Fourier series relate the coefficients of the derivative function and the antiderivative function is shown in \lccref{eq:derivative_coeff}.
-This aligns with the contributions shown by the p-matrices.
-This confirms that the model is indeed learning the relations that is defined by the derivative equation.
-
-In summary, the model is able to learn the linear relationship defined by the derivative equation.
-This is true even for high noise levels.
-The model also learns the actual relationship between each wave number which is shown in the p-matrix.
-Inverse prediction of the input function is also successfully done for lower noise levels.
-At high noise levels, the noise overwhelms the model.
-
-\subsection{Scenario 2}
-\noindent The second scenario results are presented in two parts which are the coefficient predictions and function value predictions.
-The functions are first preprocessed in order to format them into current and next values in time as discussed in \lccref{sec:data_transformation}.
-The sample pairs are first divided into two for the training and testing sets.
-Each function is then discretized into 200 time steps.
-Then, the features are put together as the coefficients of the solution and forcing term at the current time step.
-The labels are the solution at the next time step.
-Since there is too much data to fit into memory all at once at the end of this process, we randomly sample the feature and label pairs.
-This result in a maximum of 8000 samples for the training set and 2000 samples for the testing set.
-As mentioned in \lccref{sec:data_transformation}, the training features are used to fit a scaling function.
-And then, all features are scaled using the fitted scaling function.
-
-The coefficient value predictions are shown in \lccref{table:scenario_2_spectral_metrics}.
-The RBF kernel parameter computed from the data is once again the same for all versions of the dataset with a value of 5.66.
-The testing metrics show that the performance of the model vary with the viscosity value \(\nu \).
-Starting with the inviscid Burgers' equation, with \(\nu=0\), the model performs the best with a close second from the model for the \(\nu = 0.01 \) dataset version.
-The function value evaluated from the predictions is shown in \lccref{table:scenario_2_function_metrics}.
-The metrics across the board shows that the function value relative metrics are slightly better compared to the coefficients.
-Comparing the absolute metrics for the same table, we see the same general trend that the higher viscosity show the model performing worse.
-
-\begin{table}[H]
-  \caption{Performance metrics of coefficient prediction of next time step in scenario 2 by viscosity.}\label{table:scenario_2_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    0.0      & 3.46e-04 & 1.86e-02 & 1.24e-02 & 0.79 & 0.65  \\
-    0.01     & 3.56e-04 & 1.89e-02 & 1.27e-02 & 0.78 & 0.67  \\
-    0.1      & 9.17e-04 & 3.03e-02 & 2.32e-02 & 0.46 & 1.08  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\begin{table}[H]
-  \caption{Performance metrics of function values evaluated from coefficient prediction of next time step in scenario 2 by viscosity.}\label{table:scenario_2_function_metrics}
-  \centering
-  \begin{tabular}{lrrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    0.0      & 5.58e-05 & 7.47e-03 & 5.89e-03 & 0.82 & 0.70  \\
-    0.01     & 5.74e-05 & 7.58e-03 & 6.01e-03 & 0.81 & 0.71  \\
-    0.1      & 1.58e-04 & 1.26e-02 & 9.98e-03 & 0.51 & 1.04  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The testing results are complimented with a rollout experiment.
-The results from the rollout are shown in \lccref{fig:scenario_2_rollout}.
-The rollout starts from time \(t=0\).
-In all the plots, this is at the bottom.
-We have included this initial condition in the plots.
-From this initial condition in combination with the forcing term at the initial time step, the model predicts the first time step solution.
-The model then uses the predicted solution combined with the corresponding forcing term to predict the second time step.
-To see how well the model is performing relative to the actual target values, we compute the difference between the two as shown in \lccrefs{fig:sc2_rollout_diff_0.0,fig:sc2_rollout_diff_0.01,fig:sc2_rollout_diff_0.1}.
-Observe that errors are introduced relatively early around time \(t=1\).
-However, the model rollout stays stable until the end despite this error.
-This results in the model being able to finish the rollout for this sample.
-\begin{figure}[H]
-  \centering
-  \begin{adjustwidth}{-0.1\linewidth}{-0.1\linewidth}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_target_0.0.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.0\)}\label{fig:sc2_rollout_target_0.0}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_pred_0.0.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.0\)}\label{fig:sc2_rollout_pred_0.0}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_diff_0.0.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.0\)}\label{fig:sc2_rollout_diff_0.0}
-    \end{subfigure}
-    \\[0.7\baselineskip]
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_target_0.01.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.01\)}\label{fig:sc2_rollout_target_0.01}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_pred_0.01.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.01\)}\label{fig:sc2_rollout_pred_0.01}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_diff_0.01.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.01\)}\label{fig:sc2_rollout_diff_0.01}
-    \end{subfigure}
-    \\[0.7\baselineskip]
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_target_0.1.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.1\)}\label{fig:sc2_rollout_target_0.1}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_pred_0.1.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.1\)}\label{fig:sc2_rollout_pred_0.1}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_diff_0.1.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.1\)}\label{fig:sc2_rollout_diff_0.1}
-    \end{subfigure}
-    % \\[0.7\baselineskip]
-  \end{adjustwidth}
-  \caption{The rollout predictions for one of the test function. The difference is calculated as the targets subtracted by the predictions.}\label{fig:scenario_2_rollout}
-\end{figure}
-
-Another observation we can see is that the difference between the target and rollout predictions is much more pronounced for lower viscosity values.
-This result is aligned with metrics shown in \lccrefs{table:scenario_2_rollout_spectral_metrics,table:scenario_2_rollout_function_metrics}.
-The absolute metrics show that the models are performing several times worse in rollout compared to the single time step tests shown in \lccrefs{table:scenario_2_spectral_metrics,table:scenario_2_function_metrics}.
-This seems to be the same challenge that traditional solvers also face with the shocks that may be present with lower viscosity values.
-This means that for rollout scenarios, the model has a much harder time with lower viscosity values.
-\begin{table}[H]
-  \caption{Performance metrics of coefficient rollout in scenario 2 by viscosity.}\label{table:scenario_2_rollout_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & sMAPE \\
-    \midrule
-    0.0      & 2.91e-01 & 5.40e-01 & 4.07e-01 & 0.90  \\
-    0.01     & 1.61e-01 & 4.01e-01 & 2.86e-01 & 0.75  \\
-    0.1      & 1.70e-01 & 4.12e-01 & 3.02e-01 & 0.81  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-\begin{table}[H]
-  \caption{Performance metrics of function values evaluated from coefficient rollout in scenario 2 by viscosity.}\label{table:scenario_2_rollout_function_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & sMAPE \\
-    \midrule
-    0.0      & 5.81e-02 & 2.41e-01 & 1.89e-01 & 1.04  \\
-    0.01     & 3.17e-02 & 1.78e-01 & 1.40e-01 & 0.94  \\
-    0.1      & 2.91e-02 & 1.71e-01 & 1.33e-01 & 0.92  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The exact function \cref{eq:burgers_exact_solution} is computed for each viscosity value.
-The discrete Fourier transform of the values are then used for doing rollout with the model.
-For the forcing term, we just use a constant function with a value of zero.
-The rollout predictions are shown in \lccref{fig:scenario_2_interpretation}.
-The model is not successful in the rollout for the inviscid equation and for the viscosity of \(\nu=0.01\).
-Both of these cases, the model produces too much error that the original function is no longer recognizable in the predictions.
-For the higher viscosity value of \(\nu=0.1\) the rollout produces a recognizable prediction.
-The error stays to about half the maximum function value.
-We do see some more noticeable error in the flatter parts of the function.
-The error also take a very similar shape across the different viscosity values.
-Since we essentially used the same solutions for training the model for each viscosity, the similarity in error means that it can be alleviated with more diverse training samples.
-The error for the flatter functions may also be alleviated by including similar flatter functions during training.
-\begin{figure}[H]
-  \centering
-  \begin{adjustwidth}{-0.1\linewidth}{-0.1\linewidth}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_target_0.0.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.0\)}\label{fig:sc2_exact_target_0.0}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_pred_0.0.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.0\)}\label{fig:sc2_exact_pred_0.0}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_diff_0.0.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.0\)}\label{fig:sc2_exact_diff_0.0}
-    \end{subfigure}
-    \\[0.7\baselineskip]
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_target_0.01.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.01\)}\label{fig:sc2_exact_target_0.01}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_pred_0.01.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.01\)}\label{fig:sc2_exact_pred_0.01}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_diff_0.01.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.01\)}\label{fig:sc2_exact_diff_0.01}
-    \end{subfigure}
-    \\[0.7\baselineskip]
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_target_0.1.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.1\)}\label{fig:sc2_exact_target_0.1}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_pred_0.1.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.1\)}\label{fig:sc2_exact_pred_0.1}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_diff_0.1.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.1\)}\label{fig:sc2_exact_diff_0.1}
-    \end{subfigure}
-    % \\[0.7\baselineskip]
-  \end{adjustwidth}
-  \caption{The rollout predictions for one of the exact function in \lccref{eq:burgers_exact_solution}.
-The difference is calculated as the targets subtracted by the predictions.}\label{fig:scenario_2_exact}
-\end{figure}
-
-The metrics for the exact rollout further solidifies our observations from the plots.
-The metrics are shown in \lccrefs{table:scenario_2_exact_spectral_metrics,table:scenario_2_exact_function_metrics}.
-While the absolute metrics are low, this is mostly due to the maximum function values of the exact function also being pretty low.
-The relative metric sMAPE shows a much clearer picture.
-As expected, the inviscid prediction is pretty much just error.
-The next result, for viscosity \(\nu=0.01\), is better.
-This seems to be from the slight conformance to the target.
-The plots for this viscosity show that the prediction contains \enquote{shapes} similar to the target despite the scale not being close to the target.
-Finally, the highest viscosity level results show the best performance.
-Despite the good performance in the higher detail areas of the function, the error from the flatter areas overwhelm the metrics due to its larger portion of the function.
-\begin{table}[H]
-  \caption{Performance metrics of coefficient rollout of exact solution in scenario 2 by viscosity.}\label{table:scenario_2_exact_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & sMAPE \\
-    \midrule
-    0.0      & 2.16e-02 & 1.47e-01 & 1.08e-01 & 2.00  \\
-    0.01     & 1.32e-02 & 1.15e-01 & 6.37e-02 & 1.58  \\
-    0.1      & 2.83e-03 & 5.32e-02 & 4.00e-02 & 1.50  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-\begin{table}[H]
-  \caption{Performance metrics of function values evaluated from coefficient rollout of exact solution in scenario 2 by viscosity.}\label{table:scenario_2_exact_function_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & sMAPE \\
-    \midrule
-    0.0      & 4.16e-03 & 6.45e-02 & 4.56e-02 & 2.00  \\
-    0.01     & 3.23e-03 & 5.68e-02 & 4.94e-02 & 1.73  \\
-    0.1      & 3.86e-04 & 1.97e-02 & 1.62e-02 & 1.47  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The correlation image and p-matrix for each viscosity can be seen in \lccref{fig:scenario_2_interpretation}.
-Analyzing the correlation images first, we see that some columns are sorted in correlation to how the samples are sorted based on the real component of the 4th output wave number.
-For the inviscid equation, this correlation is the strongest with multiple columns exhibiting the correlation.
-The highest and visually most sorted values are from the forcing term portion of the inputs.
-Different wave numbers in the inputs are also sorted differently, this indicates an inverse correlation.
-For a higher viscosity of \(\nu=0.01\), a weaker correlation is still present.
-
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_ci_0.0.pgf}
-    \end{adjustbox}
-    \caption{Correlation image \(\nu=0.0\).}\label{fig:sc2_ci_0.0}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_pm_0.0.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix for \(\nu=0.0\).}\label{fig:sc2_pm_0.0}
-  \end{subfigure}
-  % \\[-0.7\baselineskip]
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_ci_0.01.pgf}
-    \end{adjustbox}
-    \caption{Correlation image \(\nu=0.01\).}\label{fig:sc2_ci_0.01}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_pm_0.01.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix for \(\nu=0.01\).}\label{fig:sc2_pm_0.01}
-  \end{subfigure}
-  % \\[-0.7\baselineskip]
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_ci_0.1.pgf}
-    \end{adjustbox}
-    \caption{Correlation image \(\nu=0.1\).}\label{fig:sc2_ci_0.1}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_pm_0.1.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix for \(\nu=0.1\).}\label{fig:sc2_pm_0.1}
-  \end{subfigure}
-  \caption{Correlation image (left column) and p-matrix (right column) for each model trained on a different viscosity (row).
-The correlation image was sorted same order the values of the real component of wave number \(k=2\) were sorted in descending order.}\label{fig:scenario_2_interpretation}
-\end{figure}
-
-Once we get to the highest viscosity, while the order is still present, we see a more random arrangement of the correlation image values.
-This observation and the lower scores can both be explained by the level of temporal discretization.
-This is the same issue we encounter when we use some traditional methods for higher viscosity values with the same time step for lower viscosity values \autocite{kassamFourthOrderTimeSteppingStiff2005,seydaogluNumericalSolutionBurgers2016}.
-The issue arises in stiff differential equations.
-Stiff differential equations refer to the presence of a rapidly varying component.
-We can see that the larger amplitudes of high frequency components in the forcing term to represent the rapidly varying components as shown in \lccrefs{fig:burgers_forcing_0.0,fig:burgers_forcing_0.01,fig:burgers_forcing_0.1}.
-Traditionally, stiff equations would require specific numerical methods purpose built to efficiently solve the problem.
-Otherwise, the using a solver like FDM would require much finer time steps than the one we are using here.
-
-The p-matrix shows the difference in contributions of both input functions.
-For the inviscid equation, the contributions mainly come from the forcing term.
-The current solution contributes a smaller amount in comparison.
-There is similarity with the antiderivative p-matrices in this case.
-The contributions to each output wave number mainly come from input coefficients with the same wave number.
-However, there is a noticeable contribution from other wave numbers too unlike the antiderivative case.
-The biggest contribution from the current solution is the constant/bias term.
-For higher viscosity values, notice that the contribution of the previous solution increases.
-The increase is more pronounced for higher frequencies.
-This aligns with the quadratic scaling from the wave number on the coefficients \autocite{canutoSpectralMethodsEvolution2007}.
-The p-matrix for lower viscosity values show more structured contribution of other wave numbers in comparison to the higher wave numbers.
-This structure comes in the form of a grid pattern.
-For the real components of the output, the contribution of other wave numbers oscillate between higher and lower values depending on whether the input component is real or not.
-The imaginary output components on the other hand have a more constant contribution across the input components.
-The contribution once again become more pronounced the higher the absolute value of the wave number.
-
-To summarize, Low viscosity values are a challenge to the model as with traditional methods.
-Despite that, this scenario confirms the model's ability to learn the nonlinear relationship defined by the Burgers' equation.
-The model is also able to stay stable with a relatively large time step.
-This concludes the synthetic data portion of the study.
-
-\subsection{Scenario 3}
-\noindent This final scenario tests the model on a much more complex dataset.
-As said previously, this dataset, which is computed using real observations of Earth's weather system, will be used to represent the model learning a very complex system with many unknown contributing variables.
-For our case, this means the data used will be limited to the 2-meter temperature.
-The anomaly is computed by subtracting the climatology from the corresponding day of years and hours of the atmospheric state.
-For example, the temperature on the 6\textsuperscript{th} of January 1998 at 18:00 UTC is subtracted with the average temperature for the 6\textsuperscript{th} day of the year at 18:00 hour UTC\@.
-For any anomaly predictions, the corresponding atmospheric state can simply be computed as the inverse process described before by adding the climatology to the predicted anomaly.
-
-The preprocessing of the data is carried out in the same manner as the Burgers' equation experiments.
-The difference being that for the features we only include the current anomaly of the atmosphere and there are no forcing terms.
-The targets are the future anomaly of the atmosphere.
-The reason for choosing to train and predict the anomaly instead of the state valued themselves is to avoid the model from just learning the obvious periodicity that exists in weather such as the day-night cycle or the seasons.
-Next, Both the current anomaly and future anomaly are Fourier transformed to their 2-dimensional coefficients.
-This process is done for both the training and testing set.
-Once the features for both are processed, we fit the standard scaling function on the training features.
-Using this fitted scaling function, both the training and testing features are scaled to a mean of 0 and standard deviation of approximately 1.
-
-The testing results are shown in \lccrefs{table:sc3_test_anomaly_metrics,table:sc3_test_state_metrics}.
-To put the absolute metrics into context, the median test state coefficient' maximum absolute value is \num{569364.25}.
-With this information, an RMSE value of 64.72 is relatively low error.
-The relative metric sMAPE also agrees with this, with a value of 0.76.
-The function values show that the model on average has an error of around 2 degrees kelvin or Celsius.
-This is again relatively small for the range of temperatures on Earth which span roughly 120 degrees kelvin across the historical maxima and minima.
-From existing knowledge of the problem, we know these values for the metrics are mainly due to the periodicity of atmospheric states.
-When we look at the anomaly metrics, the model is still able to learn some things and perform slightly better than a model of anomaly averages.
-However, since the median maximum absolute value for the state coefficients is \num{1155.14}, the error rate is not as good as the state predictions.
-\begin{table}[H]
-  \caption{Performance metrics of anomaly coefficient prediction for scenario 3.}\label{table:sc3_test_anomaly_metrics}
-  \centering
-  \begin{tabular}{lrrrrr}
-    \toprule
-                   & MSE     & RMSE  & MAE   & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    spectral       & 4189.16 & 64.72 & 32.47 & 0.35 & 1.19  \\
-    function value & 4.09    & 2.02  & 1.44  & 0.09 & 1.24  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\begin{table}[H]
-  \caption{Performance metrics of state coefficient prediction for scenario 3.}\label{table:sc3_test_state_metrics}
-  \centering
-  \begin{tabular}{lrrrrr}
-    \toprule
-                   & MSE     & RMSE  & MAE   & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    spectral       & 4189.16 & 64.72 & 32.47 & 0.56 & 0.74  \\
-    function value & 4.09    & 2.02  & 1.44  & 0.75 & 0.01  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-The p-matrix and correlation image is shown in \lccref{fig:sc3_interpretation}.
-For the correlation image, we see that most wave numbers are correlated or inversely correlated with the outputs.
-The strongest correlation is shown by the features of the same wave number as the sorted target.
-This is an indication that the equations involved may be nonlinear.
-If we look at the p-matrix however, it seems very flat save a faint diagonal line from the top left to the bottom right.
-The values of the p-matrix are also extremely high.
-With the \enquote{flatness} we see, this is indicative of strong contributions by a few inputs.
-
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_ci.pgf}
-    \end{adjustbox}
-    \caption{The correlation image.}\label{fig:sc3_ci}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_pm.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix.}\label{fig:sc3_pm}
-  \end{subfigure}
-  % \\[-0.7\baselineskip]
-  \caption{Correlation image and p-matrix for WeatherBench 2 model.
-The correlation image was sorted same order the values of the real component of wave number \((k_{longitude}=0, k_{latitude}=2)\) were sorted in descending order.}\label{fig:sc3_interpretation}
-\end{figure}
-
-To see more details of the p-matrix, we show a zoomed in version in \lccrefs{fig:sc3_pm_zoom1,fig:sc3_pm_zoom2}.
-The relationships are much more clear between features and outputs that do not share the same wave number.
-The coefficients with the same longitude wave numbers appear in the same \enquote{square} shape.
-Within the \enquote{square}, coefficients close to the same latitude wave number show much stronger contribution.
-For low wave numbers, shown in \lccref{fig:sc3_pm_zoom1}, the contribution is spread over more latitude wave numbers.
-The higher wave numbers, on the other hand, has the contributions much more concentrated on the coefficients with the same latitude wave numbers.
-In addition, the value of contribution differ by an order of magnitude with lower longitude wave numbers having higher maximum contribution.
-This observation suggests that the nonlinearity and magnitude are inversely proportional to the absolute value of the longitude wave number.
-This is in contrast to when we discussed the forcing term for our Burgers' equation scenario.
-The low frequencies in longitude may indicate that the model has learned some feature of the anomaly that is specific to different times of day.
-This is because the lowest longitudinal wave number would correspond to when different parts of the world is in nighttime or in daytime.
-Other possible explanations may be due to the fact that the earth more closely resemble a sphere compared to the toroidal shape that the 2-dimensional Fourier transform assumes.
-This would result in the representation latitude-wise being distorted.
-For this issue, the use of spherical harmonics may be a better fit to rule out the possibility of any distortions the Fourier transform may introduce.
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_pm_zoom1.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix zoomed in to \((k_{longitude}=\{0, 1, 2\}, k_{latitude}=[-16, 16))\).}\label{fig:sc3_pm_zoom1}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_pm_zoom2.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix zoomed in to \((k_{longitude}=\{\phantom{-}31,-32,\phantom{-}32\}, k_{latitude}=[-16, 16))\).}\label{fig:sc3_pm_zoom2}
-  \end{subfigure}
-  \caption{The p-matrix of the WeatherBench 2 models zoomed in to specific wave numbers.}\label{fig:sc3_pm_zoomed}
-\end{figure}
-
-The predictions from test features are processed through the Fourier inverse transform to evaluate the function values.
-The direct predictions, which is the anomaly, is shown in \lccref{fig:sc3_anomaly_predictions}.
-The model seem to be predicting less extreme values that are noticeable in the target.
-Specifically areas over North America, Central Asia, and parts of Antarctica show lower temperature anomaly than expected.
-We also loose detail in areas which should have a lower anomaly such as northern areas of Africa, Greenland, and South Asia.
-The lack of detail seems to be a problem of underestimation.
-We believe this is caused by the so-called \enquote{double penalty} issue caused by the loss function used for the LSSVR \autocite{lledoScaledependentVerificationPrecipitation2023}.
-The predictions tend to be closer to the mean of the data to avoid the extra penalty from a wrong prediction with a high value.
-One way to allow for finer details that are less accurate is to penalize the higher frequency wave numbers less compared to the lower frequency wave numbers.
-For our case this means the LSSVR for each output will have their regularization parameter decreased to allow the model to focus less on the errors for higher frequencies.
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    % \centering
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_anom_pred.pgf}
-    \end{adjustbox}
-    \caption{Predicted 2-meter temperature anomaly.}\label{fig:sc3_anomaly_pred}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    % \centering
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_anom_target.pgf}
-    \end{adjustbox}
-    \caption{Target 2-meter temperature anomaly.}\label{fig:sc3_anomaly_target}
-  \end{subfigure}
-  \caption{2-meter temperature anomaly prediction for the 1\textsuperscript{st} of January 2020 at 6:00 UTC based on the previous anomaly at 0:00 UTC.}\label{fig:sc3_anomaly_predictions}
-\end{figure}
-
-The state predictions which is obtained by adding the climatology to the predicted anomaly is shown in \lccref{fig:sc3_state_predictions}.
-This further shows areas of discrepancy between the prediction and the target.
-The area in the South Pacific show that the target has a higher difference temperature compared to the prediction.
-This smoothness in the prediction is easier to see for areas in the ocean.
-Many sharp features are lost and the state prediction start to resemble averaged view of the climatology.
-We must also take into account that the model only used temperature distribution data.
-Other pieces of information we know to be crucial to weather prediction such as wind speed or pressure was not included in the inputs.
-With this in consideration the model was still able to learn some relationships defined by governing equations of weather.
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    % \centering
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_state_pred.pgf}
-    \end{adjustbox}
-    \caption{Predicted 2-meter temperature.}\label{fig:sc3_state_pred}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    % \centering
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_state_target.pgf}
-    \end{adjustbox}
-    \caption{Target 2-meter temperature.}\label{fig:sc3_state_target}
-  \end{subfigure}
-  \caption{2-meter temperature prediction for the 1\textsuperscript{st} of January 2020 at 6:00 UTC based on the previous anomaly at 0:00 UTC.}\label{fig:sc3_state_predictions}
-\end{figure}
-
-The results of our experiments show that the proposed model has the ability to learn the relationships that PDEs and other governing equations define.
-The interpretation methods for support vector regression that we used, namely the correlation image and p-matrix developed by \textcite{ustunVisualisationInterpretationSupport2007}, allows us to confirm what the model has learned.
-In the case of the WeatherBench2 model, it has also allowed us to glean some insight into some mechanisms that the model has learned.
-This information was used to verify the learned relationships for the simple derivative equation.
-Together with the performance metrics on three different problems, we have shown the proposed model to be a viable tool for situations with limited knowledge and a need for some level of interpretability of the model.

### 2025-01-14 technical_doc/implementation.tex
fix labels, fix problem with graphics path and suround with curly braces, start technical document

--- 2025-01-13 skripsi/chapter4.tex
@@
-% !TEX root = ./skripsi.tex
-\chapter{RESULTS AND DISCUSSION}
-\noindent This chapter will elaborate on the results of the study and relevant phases for analysis.
-This chapter is organized into five sections which are the results of data generation, data retrieval, design of computational model, implementation of computational model, experimental scenarios, and the experiments themselves.
-
-\section{Data Generation}\label{sec:data_generation}
-\noindent This study uses two data acquisition approaches.
-The first approach which is discussed in this section is data generation.
-This process involves manufacturing data randomly in such a way that they obey the PDEs to be modeled.
-The generated data consists of features and labels.
-These features and labels in the context of PDEs are parameters and the solution of the PDEs, respectively.
-The PDEs enforce a relationship between parameters and the solution.
-This relationship is implicitly encoded into the features and labels, which is what machine learning models can learn.
-Because the solution and parameters to PDEs are functions and there are many kinds with different properties, generating all the different kinds of functions is a difficult task.
-This is why this study focuses on Fourier functions.
-This means that out of the space of all functions \(F \) which include categories such as polynomials \(f\left(x\right)=a_{n}x^n+\cdots+a_1x+a_0\) where \(f\in F\), and \(a_n\) are constants; we only consider the subset of functions \(U \subset F\) which are of the form \(u\left(x\right)=\sum_{k}^{m}c_k e^{2\pi i k \frac{x}{P}}\).
-
-Using the subset of Fourier functions has several benefits which has motivated the choice.
-First these functions are characterized purely by their coefficients \(c_k\), meaning there is no need to store discretized values which potentially saves space and computation.
-The second benefit is that other functions such as polynomials can be approximated by them using the Fourier transform.
-This means that despite limiting the set of functions to Fourier functions, the behavior of PDEs with other sets of functions can be approximated to a certain extent.
-The final benefit is the mature ecosystem around these functions which include fast algorithms for the Fourier transform and even numerical approaches for solving known PDEs like the previously mentioned spectral method which we discussed in \lccref{sec:fourier_discussion}.
-In summary, the generated data consists of features and labels which are Fourier coefficients implicitly defining the relationship enforced by a PDE and scenario.
-To proceed with the data generation, there are 4 steps involved:
-\begin{enumerate}
-  \item Scenario and PDE Determination:
-        The first step of data generation is determining the scenario related to the PDE or governing equations.
-First, the PDE to be modeled is determined based on the goals of the dataset.
-Then, one or more of the parameters is chosen to predict the solution.
-The chosen parameters will be called the input functions and the solution will be called output functions from here on.
-The second part of the scenario is the domain or more simply the physical space occupied by the system to be modeled.
-The domain will be used to compute the function values in relation to the physical space from coefficients of Fourier functions.
-  \item Parameter Determination:
-        The second step is determining all parameters other than that input parameter based on the scenario and governing equation.
-These parameters may be coefficients such as material properties like density or viscosity, or forcing terms which model external influence on the system like a heat source in the case of the heat equation.
-Depending on the parameters, solutions of PDEs may behave very differently, such as the appearance of discontinuities in the solution to low viscosity Burgers' equation.
-Because of this, the choice of parameters is guided by what the dataset seeks to do.
-  \item Random Coefficient Generation:
-        The third step of data generation is randomly generating the solutions for the chosen equation.
-Generating random functions in the space of Fourier functions exploits the fact that the coefficients characterize the function completely.
-By randomly assigning coefficients \(c_k\), many functions can be generated randomly with very little cost.
-Since the coefficients need to be complex numbers as in \lccref{eq:complex_number}, both real and imaginary components are generated independently by assigning a random value to each component for each wave number \(k\).
-They are then put together again into complex numbers.
-
-        Since only real functions are of interest in this study, the generation cost can be approximately halved.
-This is because for real functions the coefficients for negative wave numbers \(k\) are complex conjugate of the positive wave numbers.
-This means that once the positive coefficients are generated, one only needs to compute their complex conjugate and concatenate the result with the coefficients of positive wave numbers.
-For dimensions higher than one, a simpler approach is used.
-The coefficients are generated for all wave numbers including the negative ones.
-The inverse Fourier transform is computed and this results in complex functions.
-The real components of these functions are kept and the Fourier transform is applied to get the coefficients of the real functions.
-Finally, these generated coefficients then be used with the basis functions as input functions.
-        % TODO: add diagram for generating real functions, the mirroring process too
-  \item Forcing Term Computation:
-        Finally, in order to ensure that the generated solution and chosen parameters satisfy the equation, the forcing term is computed as the residual of the equation of interest with the parameters that was previously determined.
-This computation is done using the spectral method.
-  \item Function Value and Noise Computation:
-        The generated solution and forcing functions are labeled as input and output functions.
-The values of both functions in the domain can then be computed using the scenario determined in the first step.
-Once all coefficients are generated, the function values are computed with an inverse Fourier transform.
-The real component of the function values are retained, and the imaginary component are zeroed out.
-Noise is added to the function values here as needed.
-The processed function values are then converted back into coefficients using a Fourier transform.
-This processing is necessary to ensure that the coefficients are only describing the real function.
-
-\end{enumerate}
-
-These four steps are the general processes involved in generating datasets for this study. Further specifics of the generation process of each dataset is explained in their respective subsections.
-
-\subsection{Data Generation: Anti-derivative}
-\noindent The first dataset is a simple one dimensional derivative.
-This was chosen as a simple proof of concept of the ability to solve a differential equation.
-The equation is related to many real-world problems such as acceleration and speed.
-One can imagine a train in an ideal world where acceleration is directly translated into speed.
-When the train accelerates at time \(t \) by some amount \(a \), we can expect the train to have some speed \(u \).
-In this ideal world, the relationship between speed and acceleration can be modeled with a simple differential \lccref{eq:derivative}.
-This scenario is found in many real systems albeit often with many more details such as different components of acceleration from friction, drag, gravity, and other factors.
-As previously mentioned in \lccref{sec:data_generation}, both velocity \(u \) and acceleration \(a \) are modeled with Fourier series in \lccrefs{eq:fourier_speed,eq:fourier_acceleration} respectively, where \(T\) is the period representing the length of the domain.
-\begin{align}
-  u\left( t \right) & = \sum_{k} \hat{u}_k e^{2\pi ikt/T} \label{eq:fourier_speed}        \\
-  a\left( t \right) & = \sum_{k} \hat{a}_k e^{2\pi ikt/T} \label{eq:fourier_acceleration}
-\end{align}
-The domain of the scenario is a two-hour time window.
-This number was chosen because it is around the ideal length of travel time on high speed rail in comparison to air travel and car travel \autocite{givoniDevelopmentImpactModern2006,wangEfficiencySpatialEquity2019,wrro2236}.
-This is the first step in generating this dataset.
-
-In the second step, as the derivative \lccref{eq:derivative} does not contain any parameters other than the acceleration which is the input parameter, there are no other parameters to determine.
-Therefore, the data generation process proceeds to generating coefficients for the speed functions \(\hat{u} \).
-The coefficients are assigned randomly from a Gaussian distribution with a mean of zero and standard deviation of one.
-This choice was made such that most wave numbers will have a coefficient of close to zero leaving a sparse set of wave numbers to mostly affect the resulting function.
-In total, \num{5000} unique functions are generated with \num{50} complex coefficients each.
-
-In the third step, the output function coefficients are computed.
-To find the relation between \(\hat{u}_k \) and \(\hat{a}_k \), we need to find substitutes for each term in \lccref{eq:derivative}.
-To do this, we take the derivative of \lccref{eq:fourier_speed} which result in \lccref{eq:fourier_series_derivative}.
-Using this we can substitute the terms in \lccref{eq:derivative} with \lccrefs{eq:fourier_series_derivative,eq:fourier_acceleration} giving \lccref{eq:example_spectral_method_fourier_substituted}.
-Finally, after some algebraic manipulation we obtain the relationship between the input \(a^*\) and output function \(u^*\) in terms of their coefficients in \lccref{eq:derivative_coeff}.
-One also needs to choose the integration constant \(\hat{u}_{0}\) because at \(k=0\) \lccref{eq:derivative_coeff} becomes a division by zero.
-\begin{align}
-  \dv{u\left( t \right)}{t}                                        & = a\left(t\right) \label{eq:fourier_series_derivative}                                                             \\
-  \sum_{k} \hat{u}_k\times \left( 2\pi ik/T \right) e^{2\pi ikt/T} & = \sum_{k} \hat{a}_k e^{2\pi ikt/T} \label{eq:example_spectral_method_fourier_substituted}                         \\
-  \hat{a}_k                                                        & = \hat{u}_k\left( 2\pi ik/T \right)                                                    \label{eq:derivative_coeff}
-\end{align}
-
-In the final step, using randomly generated values of \(\hat{a}_k\), the corresponding values of \(\hat{u}_k\) are computed with \lccref{eq:derivative_coeff}.
-These coefficients are then used to compute the function values inside the domain.
-The two-hour time window is represented by a grid of \num{500} discrete points.
-With the coefficients and evaluation points ready, the function values are computed using \lccrefs{eq:fourier_speed,eq:fourier_acceleration}.
-Next, noise is added to the function values in order to motivate models learning on the dataset to generalize on noise.
-To also allow evaluation of how well the model performs with different levels of noise, the samples are duplicated into three copies for each high, medium and low noise levels.
-The function values of each copy is perturbed with noise from a Gaussian distribution with zero mean and standard deviation of some percentage of the average function value standard deviation.
-The percentages of each high, medium, and low noise levels are 5, 10, and 50 percent.
-The perturbed function values are then transformed back into their coefficients.
-An example generated function and its different perturbed versions is shown in \lccref{fig:antiderivative_noise_levels}.
-The horizontal axis indicates time which is displayed in units of hours.
-The vertical axis indicates velocity in abstract units.
-
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/antiderivative_clean_perturbed_solution.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:antiderivative_noise_levels}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/antiderivative_clean.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:antiderivative}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/antiderivative_derivative_clean.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:derivative}
-  \end{subfigure}
-  \caption{(\subref{fig:antiderivative_noise_levels}) A generated function with no noise (clean), low noise level (5\%), medium noise level (10\%), and high noise levels (50\%).\ (\subref{fig:antiderivative}) Antiderivative function with no noise.\ (\subref{fig:derivative}) Derivative function with no noise.}
-\end{figure}
-% TODO: interesting note that the model trains better on function to coefficient task when the antiderivative is computed from the randomly generated derivative than if the derivative is computed from the randomly generated antiderivative.
-THIS NEEDS A REASON AND ANALYSIS SO MIGHT NOT BE NEEDED IN THIS WRITING.
-MAYBE A GOOD IDEA FOR A SEPARATE PIECE
-
-\subsection{Data Generation: Burgers' Equation}\label{sec:data_generation_burgers}
-\noindent The second dataset generated in this study concerns the Burgers' equation.
-This equation has been used to model a variety of cases including fluid dynamics, traffic flow, and, shock waves \autocite{bonkileSystematicLiteratureReview2018,orlandiBurgersEquation2000,becBurgersTurbulence2007,jamesonEnergyEstimatesNonlinear2007}.
-This equation is also used as a base problem for testing the effectivity of numerical methods in solving non-linear PDEs \autocite{barterShockCapturingPDEbased2008,banksNumericalErrorEstimation2012, tabatabaeiImplicitMethodsNumerical2007,bonkileSystematicLiteratureReview2018}.
-The nonlinear term in the equation creates steep gradients and even shock waves which are discontinuous with low viscosity conditions.
-These challenges test the stability of numerical solvers.
-This is the scenario and reason for the choice of this PDE\@.
-To control the viscosity and therefore the steepness of gradients, the formulation of the Burgers' equation considered in this study is the forced viscous Burgers' equation in one dimension.
-For a velocity of \(u(x, t)\), viscosity of \(\nu \), and forcing term of \(f(x, t)\), the formulation of the forced Burgers' equation is shown in \lccref{eq:forced_viscous_burgers}.
-
-The domain of we consider here is based on an exact solution of the equation.
-This is done so that the learned model can be tested on an exact solution and capture enough of the details within the solution within the domain.
-In this study, we use a specific solution by \textcite{woodExactSolutionBurgers2006} which can be seen in \lccref{eq:burgers_exact_solution}.
-This solution is periodic in space but not in time.
-Therefore, the domain in space will be based on the spatial periodicity of the exact solution which is two.
-As such, the space domain spans from 0 to 2.
-The time domain, on the other hand, is chosen to span from 0 to 10 such that enough details of the solution is included.
-
-Continuing to the second step, the parameters involved in \lccref{eq:forced_viscous_burgers} are the viscosity \(\nu \) and the forcing term \(f \).
-Since the forcing term is dependent on the solution in this step, the only parameter to determine is the viscosity.
-We choose three constant viscosity values which are \num{0.1}, \num{0.01}, and \num{0.0}.
-These values are chosen so that a variety of behaviors are represented in the dataset from viscous to inviscid flow.
-
-After this, in the third step, the solution functions \(u \) are generated with 8 modes in time and 8 in space and \num{500} unique function samples for each viscosity value.
-Since we don't factor the viscosity in at this point, for ease of comparison, we ensure the same solutions are generated every time by using a new instance of the generator with the same seed number each time.
-This results in the solutions being the same for all viscosity and other parameters of the equation are adapted to this.
-
-Next we account for the different viscosity values in this stage.
-The forcing term is computed using \lccref{eq:forced_viscous_burgers}.
-The solution field \(u\) and forcing term \(f\) are modeled with Fourier series in \lccrefs{eq:fourier_field,eq:fourier_force} where \(k\) is a vector of spatial and temporal wave number such that \(k_t\) is the temporal wave number and \(k_x\) is the spatial wave number.
-The period in time is represented by \(T\) and in space it is \(L\).
-\begin{align}
-  u\left(x, t \right) & = \sum_{k_{x}} \sum_{k_{t}} \hat{u}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)} \label{eq:fourier_field} \\
-  f\left(x, t \right) & = \sum_{k_{x}}\sum_{k_{t}} \hat{f}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)} \label{eq:fourier_force}
-\end{align}
-Substituting the terms in \lccref{eq:forced_viscous_burgers} with the respective Fourier series, we get the equation \lccref{eq:forced_viscous_burgers_fourier_substitution}.
-A problem one notices is the nonlinear term \(u\pdv{u}{x}\).
-A naive approach would multiply all wave numbers terms with each other as shown in \lccref{eq:burgers_convolution}.
-\begin{align}
-  u\pdv{u}{x} = \left(\sum_{k_{x}} \sum_{k_{t}} \hat{u}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)}\right) \times \left(\sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{x}/L)\hat{u}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)}\right)\label{eq:burgers_convolution}
-\end{align}
-This is computationally expensive operation with \(N^2\) multiplications \autocite{lariosMATH934BURGERS2021,robertsDealiasedConvolutionsPseudospectral2011,shenSpectralMethodsAlgorithms2011,orszagComparisonPseudospectralSpectral1972}.
-To avoid this complexity, the term is first reformulated into \(\pdv{x}(u^2/2)\).
-Then to avoid aliasing, the coefficients are padded with 50\% zeros such that the padded coefficients are 3/2 times the size of the original \autocite{orszagEliminationAliasingFiniteDifference1971, lariosMATH934BURGERS2021}.
-Then we use the padded coefficients to compute the function values in the physical domain using the inverse transform.
-And then, the point wise squaring operation is performed and transform the results back to spectral domain.
-The resulting coefficients are then trimmed back to their original size before padding.
-Finally, we multiply the resulting coefficients \(\hat{uu}_k\) by the derivative constants.
-This operation is much more efficient with only \(1.5 N\) multiplications.
-This is still more efficient than the naive approach even after taking into account the transforms involved adds \(O(2\times 1.5Nln(1.5N))\) operations if using a Fast Fourier Transform algorithm.
-Putting all the above together, results in \lccref{eq:forced_viscous_burgers_fourier_substitution}.
-\begin{equation}
-  \begin{split}
-    \sum_{k_{x}} \sum_{k_{t}} \hat{f}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)} =
-     & \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{t}/T) \hat{u}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)}                                                                \\
-     & + \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{x}/L)\hat{uu}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)}                                                              \\
-     & - \nu\sum_{k_{x}} \sum_{k_{t}} {(2\pi i k_{x}/L)}^2\hat{u}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)} \label{eq:forced_viscous_burgers_fourier_substitution}
-  \end{split}
-\end{equation}
-\begin{align}
-  \sum_{k_{x}} \sum_{k_{t}} \hat{f}_k & = \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{t}/T) \hat{u}_k + (2\pi i k_{x}/L)\hat{uu}_k - \nu{(2\pi i k_{x}/L)}^2\hat{u}_k \label{eq:forced_viscous_burgers_fourier} \\
-  \hat{f}_k                           & = (2\pi i k_{t}/T) \hat{u}_k + (2\pi i k_{x}/L)\hat{uu}_k - \nu{(2\pi i k_{x}/L)}^2\hat{u}_k \label{eq:forced_viscous_burgers_coeff}
-\end{align}
-After simplifying the equation, we get the coefficients as in \lccref{eq:forced_viscous_burgers_coeff}.
-Using this equation, the exact forcing term corresponding to the randomly generated solution can be computed with relatively low cost.
-Finally, the function values of both the solutions and forcing terms are perturbed by adding Gaussian noise with a mean of zero and standard deviation of 10\% of the function value standard deviation to the values of the inverse transform.
-The perturbed coefficients are then recomputed from the sum and the final perturbed functions are obtained.
-
-An example of the solution and forcing term pairs that has been generated is shown in \lccref{fig:burgers_data}.
-Using the same seed we can see that the solution functions of the same sample are the same.
-However, with the forcing terms, we see much larger amplitudes for higher frequencies for larger viscosity values.
-This is inline with \lccref{eq:forced_viscous_burgers_coeff}.
-The squared multiplier gets large much more quickly for higher frequencies due to the squaring operation.
-The since this effect is controlled by the viscosity via multiplication, the higher the viscosity, the larger the high frequency amplitudes of the forcing term.
-This, in other words, means that more viscous fluids require a stronger forcing term to affect the solution in the same way with as fluids with a lower viscosity.
-
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_solution_0.0.pgf}
-    \end{adjustbox}
-    \caption{Solution function for \(\nu=0\).}\label{fig:burgers_solution_0.0}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_forcing_0.0.pgf}
-    \end{adjustbox}
-    \caption{Forcing function for \(\nu=0\).}\label{fig:burgers_forcing_0.0}
-  \end{subfigure}
-  % \\[-0.7\baselineskip]
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_solution_0.01.pgf}
-    \end{adjustbox}
-    \caption{Solution function for \(\nu=0.01\).}\label{fig:burgers_solution_0.01}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_forcing_0.01.pgf}
-    \end{adjustbox}
-    \caption{Forcing function for \(\nu=0.01\).}\label{fig:burgers_forcing_0.01}
-  \end{subfigure}
-  % \\[-0.7\baselineskip]
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_solution_0.1.pgf}
-    \end{adjustbox}
-    \caption{Solution function for \(\nu=0.1\).}\label{fig:burgers_solution_0.1}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_forcing_0.1.pgf}
-    \end{adjustbox}
-    \caption{Forcing function for \(\nu=0.1\).}\label{fig:burgers_forcing_0.1}
-  \end{subfigure}
-  \caption{Example sample pairs of solution and forcing terms for the Burgers' equation dataset.}\label{fig:burgers_data}
-\end{figure}
-
-\section{Data Retrieval}\label{sec:data_retrieval}
-\noindent The second data acquisition approach retrieves data of a from an external source.
-This approach downloads the external data to a local machine.
-In this study, the specific dataset that will be used is the ERA5 dataset from the European Center for Medium-range Weather Forecast (ECMWF).
-Specifically, the ERA5 dataset is a reanalysis which means it combines observational data from all over the world in order to present a more complete picture of the weather system.
-This combination process, named 4D variational data assimilation, takes into account the physics known to be involved in the system.
-As an example weather station data which take measurements such as wind speed, humidity, and temperature of the immediate surroundings of the weather station is very limited in giving a broader picture of weather over a larger area.
-Even technologies like earth observations satellites are limited to what they can observe at any single point in time as most cannot see the entirety of the earth's surface at once.
-The ERA5 dataset specifically, assimilates previous forecasts with observational data every 12 hours.
-The ERA5 reanalysis is available at the following URL (\url{https://cds.climate.copernicus.eu/datasets/reanalysis-era5-single-levels}).
-
-The original dataset made available by ECMWF has a grid size of \ang{0.25} by \ang{0.25} in latitude and longitude for atmospheric data.
-Data of oceanic waves are also available at a coarser grid size of \ang{0.5} by \ang{0.5}.
-However, we will use a cloud optimized version called WeatherBench2 that is easier to retrieve \autocite{raspWeatherBench2Benchmark2023}.
-This is because the data is available in several more grid sizes such as \ang{1.5}.
-In addition, the data can be readily downloaded to a local machine without waiting for further processing on the server.
-The guide for working with the dataset is available at (\url{https://weatherbench2.readthedocs.io/en/latest/data-guide.html}).
-In our specific case, we use the version labeled \verb|1959-2023_01_10-6h-64x32_equiangular_conservative.zarr|.
-This dataset spans from year 1959 to 2023 with a grid size of \ang{5.625} or resolution of 64 by 32 which spans from \ang{-87.19} to \ang{87.19} in latitude and \ang{0.0} to \ang{354.4} in longitude.
-The dataset is also resampled down to 6-hour intervals that starts at midnight UTC January 1959 1\textsuperscript{st} and ends at 18:00 UTC January 10\textsuperscript{th} 2023.
-
-While the original data provided by ECMWF is available in NetCDF or GRIB, the WeatherBench2 version is provided using the Zarr format in a Google Cloud Storage Bucket.
-This setup allows the use of libraries that support the Zarr format to access the dataset remotely.
-The particular library we use is called \emph{Xarray} version \verb|2024.9.0| \autocite{hoyer2017xarray,hoyerXarray2024}.
-Accessing the remote dataset is done as shown in \lccref{fig:access_remote_zarr}.
-In order to ensure access is granted, the storage option token is set to anon so that the method uses the anonymous only public access mode of authentication \autocite{GCSFSGCSFs2023122post1+1g8e500c6dirty}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-  import xarray as xr
-  ds = xr.open_zarr(
-      "DATASET_ADDRESS",
-      storage_options = {"token": "anon"},
-  )
-  \end{lstlisting}
-  \caption{Example of using Xarray to access a publicly accessible Zarr dataset hosted on Google Cloud Storage Bucket.}\label{fig:access_remote_zarr}
-\end{figure}
-
-The specific dataset resolution we use is 64 by 32 representing longitude and latitude respectively.
-The ERA5 reanalysis dataset is hosted at the following URL\@: \url{gs://weatherbench2/datasets/era5/1959-2023_01_10-6h-64x32_equiangular_conservative.zarr}.
-The corresponding climatology is hosted at \url{gs://weatherbench2/datasets/era5-hourly-climatology/1990-2019_6h_64x32_equiangular_conservative.zarr}.
-The climatology is the average for hours 0, 6, 12, and 18 for each day of the year from 1990 until 2019.
-This average helps in defining the expected state of the weather at specific points in time based on the historical averages for that time of day and year.
-
-For the reanalysis dataset, we limit the time range to the years 1995{-}2013 for training and 2020{-}2022 for testing.
-The specific time ranges for training are chosen to balance the diversity within the data and capacity of the machine the processing will be done on.
-The testing set time range was chosen to be as close to those shown on the WeatherBench 2 website.
-The filter for time and variables is shown in \lccref{fig:wb2_retrieval}.
-The reason for the different time ranges between training and testing is to reduce the risk of information leakage across the training and testing sets.
-This ensures that the testing scores we measure will be for the most part from the generalization that model learned during training.
-The filter is an array the length of the number of samples.
-The array values are all the datetime values that the year ranges are true for.
-This results in an array of boolean values.
-Using this boolean filter we can index the data so that we get the filtered data.
-Then, the filtered data is saved locally so that we can access it in a more performant way.
-The encoding chunks may need to be removed in order to evade the Xarray library from mistakenly persisting the remote encoding after slicing data \autocite{ianZarrEncodingAttributes}.
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-  years_idx = ds['time.year']
-  data_idx = (years_idx > START_YEAR) & (years_idx < END_YEAR)
-  da_orig = ds['2m_temperature'][data_idx]
-  # save locally
-  da_orig.encoding.pop('chunks',None)
-  da_orig.to_zarr(DATA_FILENAME, mode='w')
-  # open local version
-  da = xr.open_zarr(DATA_FILENAME)
-  \end{lstlisting}
-  \caption{Example of filtering of Xarray dataset by year and variable. The data is saved and then loaded locally.}\label{fig:wb2_retrieval}
-\end{figure}
-
-The dataset includes 62 variables with some variables also spanning 13 discrete vertical levels in the atmosphere.
-For our use, we will only be using the 2-meter temperature of the atmosphere.
-This is the air temperature 2 meters above the surface be it land, sea, or inland water.
-This variable is in units of kelvin (K).
-Vertically, the values of this variable is obtained by interpolating between the model values at the surface and the lowest model vertical level.
-An example of the data that was retrieved can be seen in \lccref{fig:wb2_data}.
-The data shown is in the equiangular projection.
-This means that towards the poles, the shapes become more distorted.
-While this is not the most ideal way to represent the data, using the data in this way adds to the challenge of how the model can adapt to the use of suboptimal configurations in the data.
-To compute the anomaly, we can simply subtract the current state in \lccref{fig:wb2_train_data} by the climatology in \lccref{fig:wb2_clim_data} resulting in \lccref{fig:wb2_train_anomaly}.
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_train_data.pgf}
-    \end{adjustbox}
-    \caption{2-meter temperature}\label{fig:wb2_train_data}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_clim_data.pgf}
-    \end{adjustbox}
-    \caption{Climatology}\label{fig:wb2_clim_data}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_train_anomaly.pgf}
-    \end{adjustbox}
-    \caption{2-meter temperature anomaly}\label{fig:wb2_train_anomaly}
-  \end{subfigure}
-  \caption{Data retrieved:(\subref{fig:wb2_train_data}) 2-meter temperature at January 1, 1995 6:00 UTC\@.
-(\subref{fig:wb2_clim_data}) 2-meter temperature climatology for the first day of the year at hour 6 UTC\@.
-(\subref{fig:wb2_train_anomaly}) Anomaly for 2-meter temperature at January 1, 1995 6:00 UTC\@.}\label{fig:wb2_data}
-\end{figure}
-
-After filtering, our training set has the dimensions of \num{27760} time steps, \num{64} longitude, and \num{32} latitude.
-The testing set on the other hand has \num{4384} time steps and the same values for the other two dimensions.
-For uses, such as a validation set during hyperparameter optimization, one can use a subset of the training set.
-The dimensions of the climatology are 4 for hour (0, 6, 12,\& 18), \num{366} for day of year, \num{64} for longitude, and 32 for latitude.
-
-\section{Design of Computational Model}\label{sec:computational_model_design}
-\noindent In this section, we will discuss the design of the computational model that is proposed in this work. An illustration of the computational model is show in \lccref{fig:computational_model}.
-
-\begin{figure}[H]
-  \centering
-  \begin{adjustbox}{max width=\textwidth}
-    \tikzfig{figures/computational_model}
-  \end{adjustbox}
-  \caption{Computational Model of SpectralSVR.}\label{fig:computational_model}
-\end{figure}
-
-The computational model is divided into four large phases.
-The processes within these phases are based on the broad outcomes of the phase.
-The phases themselves are data preparation, data transformation, model training, and model evaluation.
-Each phase is composed of processes that together works toward the output of the larger process.
-At the end, a final process of analysis and interpretation is carried out.
-
-\subsection{Data Preparation}
-\noindent The data preparation phase starts off the computation by preparing the data that is to be used in this study.
-This phase starts with specifying the problem to be solved.
-This translates to the dataset that will be used to represent these problems.
-The first type of dataset is generated based on a known governing equation or PDE\@.
-Using said equation, the goal is to generate pairs of functions that are related to each other by the equation.
-In the next process, generally, the solution function is first generated randomly.
-This is done by generating random numbers to use as coefficients of a set of basis functions.
-Then parameters of the equation is determined, such as term coefficients.
-Using the generated solution and predetermined parameters, a forcing term can generally be computed to satisfy the equation.
-Augmentations such as noise can then be added in the final process which is evaluating the function values.
-These processes result in a generated dataset.
-To verify the generation method and any models trained on the generated data one can use exact analytical solutions of the governing equations.
-
-The second type of dataset is retrieved from an external source.
-The data source is first identified, in our case it is the WeatherBench 2 collection of datasets.
-The specific dataset from the collection of different dataset versions is first determined.
-The dataset is available in the \emph{Zarr} format.
-And then, we determine the filters for the portions of the dataset we are interested in.
-Once the dataset and filters are determined, the retrieval process starts by accessing the dataset using the \emph{Xarray} library \autocite{hoyer2017xarray,hoyerXarray2024}.
-The filters are applied as in \lccref{fig:wb2_retrieval}.
-Finally, the filtered version is stored locally.
-The local dataset is also stored in the \emph{Zarr} format.
-
-\subsection{Data Transformation}\label{sec:data_transformation}
-\noindent The second phase of the computational model transforms the data that has been prepared into a form that can be used with the proposed model.
-In this study, there are two ways a dataset can be used.
-The first and simplest way is to predict the solution function from the forcing term for a given set of PDE parameters.
-In this case, the input function is the forcing term.
-In other words, the input function is the predictor or independent variable that will be used to predict the solution function.
-As such, the output function is the solution function.
-The antiderivative dataset is used in this way.
-The derivative, which represents the acceleration function, is used to predict the velocity function.
-Which means that the input function is the acceleration function and the output function is the velocity function.
-
-The second use of a dataset depends on whether it can be interpreted as a mapping of a previous function to the next function.
-In other words, a series of functions related to the previous function as a sum of the previous function and a perturbation.
-A commonly used form of this are time series.
-Generally, a time series can be represented as \lccref{eq:time_step_function}.
-This function describes the evolution of function \(f\) as a sum of some initial state \(f^0\) and perturbation which is its rate of change \(\dv{f}{t}\) at a point in time close to the current time multiplied by the time step \(\delta t\).
-This is the first order Taylor polynomial.
-Adding more terms with higher order derivatives can be done to increase the accuracy.
-This describes the same process that is used in the finite difference method.
-\begin{equation}
-  f^{t+1} = f^{t} + \delta t \times \dv{f}{t} + \dots \label{eq:time_step_function}
-\end{equation}
-In this case the previous function and any other independent variables like the forcing term involved in the right-hand side of the equation is used to predict the difference between the future state and the current state.
-It would mean that each sample function in the data would need to at least have two dimensions.
-This is because one dimension represents the evolution of the function over time, while the other dimensions define the spatial domain where the function's values are computed at each time step.
-This condition is true for both the Burgers' equation dataset and the WeatherBench 2 collection of ERA5 datasets.
-First, the Burgers' equation dataset, while is also able to be used in the first way as a mapping between the forcing term and the solution, one of the traditional ways of solving it is using the method of lines.
-This entails solving the dimensions other that time with methods such as the finite differences method or the spectral method.
-The time dimension is then separately solved using FDM such as the form shown in \lccref{eq:time_step_function} \autocite{schiesserNumericalMethodLines2012,sadikuSimpleIntroductionMethod2000}.
-This is the form that the Burgers' equation dataset will be used in.
-In this case, algebraic manipulation of \lccref{eq:forced_viscous_burgers} results in the time derivative of the solution as in \lccref{eq:forced_viscous_burgers_time_derivative}.
-\begin{align}
-  \pdv{u}{t} = f - u\pdv{u}{x} + \nu\pdv[2]{u}{x} \label{eq:forced_viscous_burgers_time_derivative}
-\end{align}
-The most important component of the right-hand side of the equation, the time derivative, is expressed in terms of the solution function, the forcing term and any other partial derivatives.
-Because of this, it means we can train the model to learn the relationship between the solution function combined with the forcing term and the time derivative.
-Putting this together with \lccref{eq:time_step_function}, it is possible to predict the solution function in a future time based on the current solution function and forcing term.
-The input functions in this case are both the value of the solution function and the forcing term at the current time step.
-The output function is the time derivative which is computed by rearranging \lccref{eq:time_step_function} resulting in \lccref{eq:time_derivative_time_step_function}.
-\begin{equation}
-  \dv{f}{t} = \frac{f^{t+1} - f^{t}}{\delta t} \label{eq:time_derivative_time_step_function}
-\end{equation}
-Perhaps in a more obvious manner, the same is also applied to the WeatherBench 2 collection of ERA5 datasets.
-The 2-meter temperature is a series of snapshots in time of the distribution of temperature all over the world at 2 meters above the surface.
-The input function in this case is the temperature distribution at the current time step.
-The output function is the time derivative of the temperature distribution computed using \lccref{eq:time_derivative_time_step_function}.
-
-The input and output functions are then transformed into basis coefficients using the Fourier transform we discussed in \lccref{sec:fourier_discussion}.
-Once the coefficients are computed, the input and output sample pairs are split into train, test, and validation subsets.
-For the first type of input and output function pair, since the samples are independent of each other, a random sampling of the dataset without replacement is done to select the samples for each subset.
-For the second type of input and output function pairs, if there are multiple samples of functions as in the Burgers' equation dataset, the same process with random sampling is followed.
-On the other hand, if only one function sample is available, such as the WeatherBench 2 dataset, an issue that arises is the fact that the samples are dependent on one another.
-This is because a previous time step influences the next time step.
-This is a problem for generalizing the learned model, since random sampling would lead to the model learning information in the future of the testing subset \autocite{kapoorLeakageReproducibilityCrisis2023,kaufmanLeakageDataMining2012}.
-As such, the portioning of the dataset is done by dividing the sample into different sections of the function in time.
-
-Finally, the data is scaled.
-This is done because of how support vector machines require scaling for inputs in order to perform well with certain hyperparameters such as the RBF kernel \autocite{ben-hurUsersGuideSupport2010}.
-For our case we use standard scaling based on the inputs of the training subset.
-This approach transforms the dataset by manipulating the distribution characteristics of the dataset \autocite{ahsanEffectDataScaling2021}.
-Specifically, the standard deviation \(\sigma \) and mean \(x_0\) of the dataset values \(x\) are processed such that the resulting values have a mean of 0 and standard deviation of 1.
-The function shown in \lccref{eq:standard_scaler} represents how each sample is processed with respect to the standard deviation \(\sigma \) and mean \(x_0\) of each feature.
-\begin{equation}
-  z(x;\sigma,x_0)=\frac{x-x_0}{\sigma} \label{eq:standard_scaler}
-\end{equation}
-The scaling is important for the RBF kernel specifically due to the fact that the kernel utilize a scale parameter.
-This parameter affects how scale of values influence the kernel.
-Another and perhaps more general benefit of scaling is the uniformity it enforces across features.
-This is useful because all feature weigh the outcome equally.
-In our use case, this equality is a reflection of what the data actually represents.
-Each feature which is a discretized value or its coefficient representation has equal value to any other feature.
-No point or coefficient is any more or less value compared to another point or coefficient.
-
-The scaling is applied to input functions only because scaling of the outputs does not affect the performance of the model \autocite{ben-hurUsersGuideSupport2010}.
-To also prevent information leakage across training and testing sets, the mean and standard deviation of each feature is computed using the training subset only.
-Once the parameter values are obtained, all input function samples in the dataset are transformed into their scaled versions.
-This means that the distribution for the testing and validation sets may be outside the target standard deviation and mean.
-% TODO: add graphs and tables of the resulting preprocessed data
-
-\subsection{Model Training}
-\noindent Once the data has been preprocessed, the model is trained using pairs of training features and labels.
-The training phase is separated into four processes.
-First, the preprocessed input and output function representation need to be real numbers.
-This is because the LSSVR model was made to work with real numbers.
-Any complex values such as Fourier coefficients are represented as flattened pairs of the real and imaginary components of complex values.
-% TODO: add figure of flattened complex values
-
-The training can proceed to solve \lccref{eq:lssvr_solution}.
-As the original LSSVR equation was made for regression of a single value of \(\vb{y} \), we constructed an extended the original equation in order to train multiple regression models to predict each coefficient in an output function sample.
-The assumption of this extension is that the inputs and model hyperparameters such as kernels and the regularization constant \(C \) are the same across individual regressors.
-Therefore, it follows that the solution vector and target vector can both be transformed into their matrix form with each column representing the individual regressor which results in \lccref{eq:lssvr_solution_vectorized}.
-This vectorized version is equal to \(m \) separate instances of \lccref{eq:lssvr_solution}.
-In essence, instead of a vector of scalar sample output values and a vector of model parameters, the extended equation consists of a matrix of rows of vector output values and a matrix of model parameters with each column representing the separate model for each output and row representing the Lagrange multipliers for each sample.
-The procedure to solve \lccref{eq:lssvr_solution_vectorized} adjusts \lccref{alg:lssvr_training} for the extra dimension spanning the multiple outputs of size \(m\).
-\begin{equation} \label{eq:lssvr_solution_vectorized}
-  \begin{bmatrix}
-    0          & \vb{1}_{n}^{\intercal} \\
-    \vb{1}_{n} & \Omega + \frac{I}{C}
-  \end{bmatrix}
-  \begin{bmatrix}
-    b_0           & \cdots & b_m           \\
-    \vb{\alpha}_0 & \cdots & \vb{\alpha}_m \\
-  \end{bmatrix}
-  =
-  \begin{bmatrix}
-    0        & \cdots & 0        \\
-    \vb{y}_0 & \cdots & \vb{y}_m \\
-  \end{bmatrix}
-\end{equation}
-
-Second, as the training process of an LSSVR described in requires constructing the first matrix on the left-hand side and the matrix on the right-hand side, each component of the matrices themselves will also need to be constructed.
-The kernel matrix \(\Omega \) is first constructed by computing the kernel values between each sample input with every other sample input.
-If the training set has \(n \) samples, then the resulting kernel matrix would be of size \(n \) by \(n \).
-% Assemble lssvr optimality equation matrices
-Third, using the inputs \(\vb{X}\), outputs \(\vb{y}\), predetermined regularization constant \(C \), and the obtained kernel matrix \(\Omega \), \lccref{eq:lssvr_solution_vectorized} is assembled.
-Finally, the matrix of learned parameters \(\vb{\alpha}\) and \(\vb{b}\), which are the Lagrange multipliers and bias respectively, are solved for using a linear equation solver such as a matrix Moore-Penrose inverse or linear least squares solver.
-
-For our study, we choose to not optimize the hyperparameters to focus on the broad performance with default hyperparameter values.
-The scaling parameter of the RBF kernel is computed from the training features.
-This is computed as the square root of the sum of feature variances.
-The regularization parameter used will be a default value of 1.
-Using the same values allow for easier comparisons for comparable results.
-
-\subsection{Model Evaluation}
-\noindent The fourth phase of the computational model is the evaluation of the learned model.
-This phase starts with formatting the inputs.
-If the inputs aren't scaled yet, then it is scaled using the scaling function fitted on the training set.
-This is the case for new data such as new measurements or an analytical solution of the learned PDE\@.
-Once the inputs that is to be evaluated is scaled in the same way as the training inputs, the model can predict the corresponding outputs.
-
-The procedure to compute the predicted outputs follows \lccref{alg:lssvr_prediction}.
-This leads to the second process which is computing the kernel matrix between the training input features \(\vb{X}\) and the evaluation input features \(\vb{U}\).
-The matrix is constructed as the kernel value between each evaluation sample feature and every training sample feature.
-For \(p \) evaluation samples and \(n \) training samples, this results in a kernel matrix \(\Omega \) with a shape of \(p \) rows and \(n \) columns.
-
-In the third process, the constructed kernel matrix is then multiplied with the matrix of learned Lagrange multipliers \(\vb{\alpha}\).
-The multiplication is the matrix multiplication process.
-Then, the bias vector is added to each row to produce the final predicted outputs \(\vb{v}\).
-This process is represented by \lccref{eq:lssvr_prediction_vectorized}.
-\begin{equation}
-  \vb{v} = \Omega\vb{\alpha}+\vb{1}\vb{b} \label{eq:lssvr_prediction_vectorized}
-\end{equation}
-
-The fourth process is concerned with the fact that the predicted output \(\vb{v}\) is a matrix of real numbers.
-The LSSVR output needs to be formatted before it can be used in the proposed model.
-This is done by converting the outputs into the same format as the training labels.
-As we use the Fourier basis, the model output is converted back into a matrix of complex numbers using the inverse of the first process during training.
-Finally, these predicted Fourier basis coefficients can be used to evaluate the predicted functions themselves.
-
-\section{Implementation of Computational Model}
-\noindent This section discusses the implementation of modeling and approximation of PDEs using LSSVR\@.
-Using the computational model design in \lccref{sec:computational_model_design}, the computational model is implemented as a library using the Python programming language.
-The development process itself is based on the iterative development model as mentioned in \lccref{sec:development_method}.
-In this section, the output iterative processes are consolidated and explained together.
-
-\subsection{Analysis}
-\noindent The aim of any program that is developed in this study is to model the relationship between functions defined by a partial differential equation or other operators and governing equations.
-Since the potential subject of modeling can be wide-ranging, the software product that will be developed is a library.
-This is done so that the tools and proposed model that is developed will be able to be used with a variety of PDEs.
-With this in mind, the software must also be performant and compatible with the larger machine learning and scientific computing community.
-
-To demonstrate the use and capability of the software, three case studies are chosen to represent the variety of PDEs.
-The first case study is the antiderivative equation.
-This simple case is chosen as a proof of concept to show that the proposed model works in the most simple case.
-The second case study, which is the Burgers' equation, adds a level of complexity because of the nonlinearity involved with the solution function.
-The third case study, which is the ERA5 weather dataset, was chosen to show how the model performs on data with real world observations incorporated into it.
-This dataset also presents a challenge because of the uncertainties involved with weather simulation \autocite{herreraReviewCurrentFuture2017}.
-These datasets are discussed in \lccrefs{sec:data_generation,sec:data_retrieval}.
-
-In addition, the software product is developed within certain limitations. The limitations are:
-\begin{enumerate}
-  \item The operating and implementation language of the library is Python.
-  \item The library is to be used in user code
-  \item The library depends on other libraries including the following core dependencies PyTorch, NumPy, Xarray, Zarr, Pandas, and tqdm.
-\end{enumerate}
-
-\subsection{Design}\label{sec:implementation_design}
-\noindent In this subsection, the architectural design of the software product is explained.
-The architecture consists of modules with similar concerns.
-This was chosen because of the intuition built by the use of other libraries with a similar architecture.
-The broad aim of modeling PDEs with LSSVR and basis functions coefficients can be separated into smaller concerns of data, model, and basis functions.
-Each of these concerns are addressed by a corresponding module.
-The explanation of each module are as follows:
-\begin{enumerate}
-  \item Utilities
-
-        \noindent This module provides basic tools that are used across the entire library.
-The utilities this module needs to provide include scaling, conversion between real and complex representations of matrices, resizing coefficient tensors, and adaptors for or the traditional ordinary differential equation solvers.
-Scaling functionality is used for inputs into the support vector machines.
-And as previously mentioned, since LSSVR only works with real numbers, the tools for converting between complex and their real number representations is also necessary.
-Another useful tool for working with basis coefficients is a way to resize the coefficients in terms of how many basis functions is desired.
-An example of the usage is downsizing Fourier coefficients from 12 to 8 modes.
-The last utility mentioned here provides the ability to solve ordinary differential equations.
-This utility is useful for generating data for certain types of PDEs such as the Burgers' equation.
-
-  \item Basis Functions
-
-        \noindent As the proposed model will learn the relationships defined by PDEs within the spectral domain, a large proportion of the computation will also concern the use of the basis functions themselves.
-The module will define the functionality and data structure that is expected to be used when working with basis functions in this library.
-First and foremost, the central function of this module is to store and facilitate the connection between the coefficients in the spectral domain and their values in the physical domain.
-This is dependent on the basis functions used.
-For the Fourier basis that we use in this study, this means that the transformations are the discrete Fourier transform and the discrete inverse Fourier transform.
-Other than this core functionality, information on the characteristics of the coefficients such as the number of modes, in other words basis functions, should also be provided by this module.
-In addition, other functionality included in this module are visualization of coefficients in physical space, generation of random functions, time dependent \& complex/real coefficients, noise perturbation of functions, and differential operators.
-
-  \item Model
-
-        \noindent The proposed SpectralSVR model is implemented in this module.
-As the proposed model essentially wraps a support vector regression model in such a way that it can process coefficients, this module will house the SpectralSVR wrapper itself and the LSSVR variant of support vector regression that is used in this study.
-The SpectralSVR wrapper must provide three core pieces of functionality.
-First, it must translate complex input and output samples into their real representations.
-This applies to both training and evaluation.
-Second, in addition to predicting the coefficients during evaluation, the wrapper should also be able to predict the function values themselves for any given set of point coordinates.
-This is important for quick evaluations of a predicted function at an arbitrary point.
-The third functionality is inverse input function search for a given output.
-This is useful for inverse problems where the parameters are unknown, but the solution is partially known.
-Aside from the core functionality, a complementary functionality is testing for the learned model.
-
-        The model module also implements the LSSVR model.
-This implementation provides two main functionalities.
-The first is training the LSSVR model with some given model hyperparameters such as the regularization constant and kernel.
-The second functionality is the evaluation of the learned model.
-Both functionalities allow for multiple output regression.
-This is required to learn the mappings for many coefficients at once.
-Other functionality provided by the implementation include interpretability functions and model serialization for saving and loading the learned model to disk.
-
-  \item Problems
-
-        \noindent This module provides the functionality concerned with generating data.
-Two out of the three datasets in this study are generated with this module.
-In general this module provides two pieces of functionality.
-The first is generation of the data itself.
-This functionality generates at least two sets of functions that are related to each other by the chosen PDE\@.
-The generation is based on at least two parameters which are the number of samples to generate and the number of modes or basis functions to generate the coefficients for.
-The second functionality provided by this module is the residual based on the chosen PDE\@.
-This is useful to verify if any set of functions comply with the PDE\@.
-For example, the residual may be used to verify the generated data.
-Another use is to grade the predictions by the learned model.
-
-\end{enumerate}
-
-The design presented here is the product of multiple iterations that started with building the core model and then the basis functions and finally the data.
-Throughout the iterations, the utilities were also added to alleviate the need for general tools.
-
-\subsection{Implementation}
-
+% !TEX root = ./technical_doc.tex
+\chapter{IMPLEMENTATION}
 \noindent The design in \lccref{sec:implementation_design} is implemented within the same iterative loop.
@@
 \end{figure}
-
-\subsection{Testing}
-\noindent The implementation is followed by tests of the functionality core to this study.
-The testing is done using the PyTest library.
-The testing method used is a black box approach.
-The tests are written in a separate \verb|tests| directory.
-Each module is tested by a separate file.
-The tests are done to ensure compliance of the implementation to the requirements of the software.
-The final results are presented in \lccref{table:impl_test_result}.
-Each version and iteration of the development must ensure that the tests are passed before any changes are committed to the GitHub repository.
-
-\begin{table}[H]
-  \centering
-  \begin{tabular}{lm{0.2\linewidth}m{0.5\linewidth}l}
-    % \toprule
-    \toprule
-    No & Process                         & Test Target                                                                                                   & Test Result \\
-    \midrule
-    1  & Transform                       & Transform invertible with inverse transform                                                                   & Achieved    \\\addlinespace[0.5em]
-    2  & Evaluation                      & Transform coefficient evaluation close to original values                                                     & Achieved    \\\addlinespace[0.5em]
-    3  & Plot                            & Plotting function is run successfully                                                                         & Achieved    \\\addlinespace[0.5em]
-    4  & Perturb                         & Perturb function is run successfully                                                                          & Achieved    \\\addlinespace[0.5em]
-    5  & Operations                      & Operation functions is run successfully                                                                       & Achieved    \\\addlinespace[0.5em]
-    6  & Complex Coefficients Conversion & Conversion between real and complex coefficient representation is invertible for odd and even number of modes & Achieved    \\\addlinespace[0.5em]
-    7  & SpectralSVR Train               & Training function is run successfully                                                                         & Achieved    \\\addlinespace[0.5em]
-    8  & SpectralSVR Prediction          & Coefficient prediction error within tolerable range                                                           & Achieved    \\\addlinespace[0.5em]
-    9  & SpectralSVR Prediction          & Function value prediction error within tolerable range                                                        & Achieved    \\
-    \bottomrule
-  \end{tabular}
-  \caption{Testing results of the SpectralSVR Library implementation using black box method.}\label{table:impl_test_result}
-\end{table}
-
-\section{Experimental Scenarios}\label{sec:experimental_scenarios}
-\noindent To achieve the goals of this study, as outlined in \lccref{sec:aims}, we present three experimental scenarios.
-These scenarios represent different experimental configurations that will be applied to our implementation of the SpectralSVR library.
-A table of the configurations for each scenario can be seen in \lccref{table:experimental_scenarios}.
-
-\begin{table}[H]
-  \caption{The configuration of experimental scenarios in this study.}\label{table:experimental_scenarios}
-  \centering
-  \begin{tabularx}{\textwidth}{L{0.75}*{3}{L{1.09}}} % compute these using approx barycentric coords (x + 3y = 4, x = 0.8y)
-    \toprule
-    Configuration                    & Scenario 1                                          & Scenario 2                                                          & Scenario 3                                 \\
-    \midrule
-    Data Source                      & Synthetic (computed from equations)                 & Synthetic (computed from equations) with three viscosity values     & ERA5 dataset                               \\\addlinespace[0.5em]
-    Data Augmentations               & Perturbations of three different noise levels       & Perturbation of 10\% the mean standard deviation of function values &                                            \\\addlinespace[0.5em]
-    Data Sample Size                 & 5000 unique functions for each noise level          & 500 unique functions for each viscosity value                       & 7000 time steps                            \\\addlinespace[0.5em]
-    Number of Modes                  &                                                     &                                                                     &                                            \\\addlinespace[0.5em]
-    Scaling                          & Standard scaling                                    & Standard scaling                                                    & Standard scaling                           \\\addlinespace[0.5em]
-    Dataset Split                    & 80\% Training and 20\% Testing for each noise level & 80\% Training and 20\% Testing for each viscosity value             & 80\% Training and 20\% Testing             \\\addlinespace[0.5em]
-    Regularization Parameter (\(C\)) & 1.0                                                 & 1.0                                                                 & 1.0                                        \\\addlinespace[0.5em]
-    Kernel                           & RBF (\(\sigma = features \times X.var()\))          & RBF (\(\sigma = features \times X.var()\))                          & RBF (\(\sigma = features \times X.var()\)) \\\addlinespace[0.5em]
-    Additional Tests                 & Exact solutions                                     & Exact solutions                                                     &                                            \\\addlinespace[0.5em]
-    Interpretation                   & p-matrix and correlation image                      & p-matrix and correlation image                                      & p-matrix and correlation image             \\
-    \bottomrule
-  \end{tabularx}
-\end{table}
-
-Each scenario serves a different purpose.
-The first scenario is constructed to establish whether the model can learn any relationships at all in data that implicitly defines differential equations.
-This scenario is a proof of concept of whether the model is capable of accurately learning the relationship between derivatives and their anti-derivatives.
-As the simplest case, it provides a foundation for understanding the model and its behavior.
-The 5\% noise model is then used to predict the antiderivative of a cosine function with a period of one as shown in \lccref{eq:sine_derivative}.
-The exact solution is known as \lccref{eq:sine_function} \autocite{abramowitzHandbookMathematicalFunctions1972}.
-The second goal of this scenario is to determine how noise affects the model's predictions.
-This is especially important for the inverse problem because of how sensitive the derivative is to changes in the antiderivative.
-To further solidify how the model fares for inverse problems, this scenario will also assess the performance of a trained model for a very simple inverse problem setup to determine the derivatives of the testing subset from the antiderivatives.
-This setup will utilize the model as a surrogate forward solver and optimize for a loss function using the inverse function of the SpectralSVR class as described in \lccref{sec:impl_model}.
-\begin{align}
-  f(x) & = 2\pi \cos\left(2\pi x\right)\label{eq:sine_derivative} \\
-  f(x) & = \sin\left(2\pi x\right)\label{eq:sine_function}
-\end{align}
-
-The second scenario extends the goal of the first scenario by examining the model and its behavior when learning a nonlinear PDE\@.
-The data subsets with different viscosity values are intended to allow us to learn more about how this will affect the performance on the exact solutions for lower viscosity numbers.
-The model will learn to predict future states of systems governed by the Burgers' equation from past states.
-The model for each viscosity will be used to predict \lccref{eq:burgers_exact_solution} from initial conditions at time equals zero and the corresponding forcing term of a constant value of zero.
-The exact equation prediction will be done using a rollout method.
-The initial condition along with the initial forcing term will be given to the model to predict the solution at the first time step.
-The model will then use the predicted solution with the forcing term at the first time step to predict the solution at the second time step.
-This is repeated until the stopping condition of time \(t=10\).
-The forcing term for the exact solution is a constant zero.
-Along with the rollout of the exact solution, we also perform roll out on one of the test solution.
-
-The third scenario is designed to demonstrate the modeling capability of SpectralSVR on a more practical problem of weather prediction.
-The earth weather system is a complex collection of processes.
-Using the ERA5 dataset, the model will be used to predict future states of the atmosphere from previous states.
-Specifically, the model will learn to predict the temperature 2 meters above the surface.
-That means that other than the time and spatial resolution not being the highest, the model will also learn from partial information of the relationships defined by the equation since no other variables will be included.
-This choice was made as an analog for situation with unknown PDEs and therefore unknown variables.
-With these situations, there is no guarantee that the variables measured have any relation with the system.
-These three scenarios together address the last two aims of this study.
-
-\section{Experimental Results}\label{sec:experimental_results}
-\noindent In this section, the results of each experimental scenario is presented and analyzed.
-The results come in the form of testing metrics mentioned in \lccref{sec:evaluation_metrics}.
-The model interpretations are displays of the correlation image and the p-matrix.
-The function values and coefficients themselves will also be plotted depending on the number of dimensions.
-
-\subsection{Scenario 1}
-\noindent The first scenario results are presented in four parts.
-The first is the coefficient prediction metrics which is shown in \lccref{table:scenario_1_spectral_metrics}.
-The table shows the noise level and the performance metrics.
-\begin{table}[H]
-  \caption{Performance metrics of coefficient prediction in scenario 1 by noise level.}\label{table:scenario_1_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrrrrrrr}
-    \toprule
-    Noise level & MSE   & RMSE & MAE  & R\textsuperscript{2} & sMAPE \\
-    \midrule
-    5\%         & 0.86  & 0.93 & 0.57 & 0.96                 & 0.31  \\
-    10\%        & 2.06  & 1.43 & 0.93 & 0.91                 & 0.46  \\
-    50\%        & 15.59 & 3.95 & 3.04 & 0.50                 & 1.04  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The scenario is implemented as a Jupyter notebook which imports relevant libraries and our SpectralSVR library.
-The notebook starts with creating the data with the Antiderivative problem subclass.
-All random processes use the same PyTorch Generator instance with a seed of 42.
-The data is then augmented by perturbing the function values to create three versions with the noise levels mentioned in the scenario.
-Looping through each version, the training and testing subsets are randomly sampled to result in 80\% and 20\% of the original dataset respectively.
-Then the scaling function is fitted on the training subset inputs.
-And then, both the training and testing inputs are transformed using the fitted scaling function.
-Next, an instance of SpectralSVR is trained and tested.
-Finally, the metrics are stored and the next noise level is processed.
-Next the 5\% noise model is used to predict the antiderivative of a sine function.
-
-The kernel scaling hyperparameter sigma has the same value of 10 for all noise levels.
-This is because the inputs are all scaled to approximately have a standard deviation of one.
-The value itself is from the number of features which comes out to 100 total inputs to the LSSVR\@.
-
-\Cref{table:scenario_1_spectral_metrics} shows that the model is able to generalize from the training data and learn the simple linear antiderivative operator.
-Focusing on the coefficient of determination (R\textsuperscript{2}) scores, we can see that the model is off by 0.04 to the perfect score of 1.0 for the lowest noise level.
-While increasing noise levels does degrade the performance, this is partly due to the target values also having been perturbed.
-This fact can be seen if we look at how predictions from the very same trained models on noisy inputs are compared to the noise-free versions of the antiderivative functions which is shown in \lccref{table:scenario_1_clean_spectral_metrics}.
-The metrics show that the model predictions are slightly closer to the unperturbed function coefficients compared to the perturbed versions.
-This can be seen as the influence of the independent synthetic measurement noise in the perturbed targets being removed from the testing metrics.
-
-The higher noise levels shows that the model is still relatively accurate.
-Looking at the R\textsuperscript{2} score for the 50\% noise level, the model is more accurate than a baseline mean value model.
-The R\textsuperscript{2} score of 0.5 means that the model predictions has roughly half the error the baseline would produce.
-
-\begin{table}[H]
-  \caption{Performance metrics of coefficient prediction compared to unperturbed targets in scenario 1 by noise level.}\label{table:scenario_1_clean_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrrrrrr}
-    \toprule
-    Noise level & MSE  & RMSE & MAE  & R\textsuperscript{2} & sMAPE \\
-    \midrule
-    5\%         & 0.79 & 0.89 & 0.51 & 0.96                 & 0.28  \\
-    10\%        & 1.80 & 1.34 & 0.80 & 0.92                 & 0.40  \\
-    50\%        & 9.30 & 3.05 & 2.23 & 0.62                 & 0.90  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The function values are also evaluated and the values of the metrics between the noisy targets and predictions are shown in \lccref{table:scenario_1_function_metrics}.
-While the relative metrics R\textsuperscript{2} and sMAPE stay close to the values we obtained for the coefficients themselves, since the metrics are now being computed in the physical domain, the scales have changed and because of that the values of the absolute metrics now reflect the change in scale.
-For reference, the scale of the target coefficient values for the 50\% noise level dataset in their real representation can range on average from -13.54 to 13.6 across the entire dataset.
-Therefore, an RMSE value of 3.94 for the predictions compared to the noisy targets mean that the error ratio is roughly 0.148 or just above 1 to 7.
-For the function values of the 50\% noise dataset the values range on average from -2.5 to 2.49.
-This was more difficult to compute since there is no direct way to compute the amplitude of the function from just the coefficients.
-Here we used the inverse transform and extracted the maximum and minimum values of each function from the discrete values.
-Since the RMSE in \lccref{table:scenario_1_function_metrics} for the 50\% noise dataset is 0.63, the error ratio comes to 0.126.
-One side note about \lccref{table:scenario_1_function_metrics} is that since the model instances are the same as the ones used in the coefficient evaluations, the hyperparameters are still the same including the kernel scaling factor sigma.
-\begin{table}[H]
-  \caption{Performance metrics of function value from evaluated coefficient prediction in scenario 1 by noise level.}\label{table:scenario_1_function_metrics}
-  \centering
-  \begin{tabular}{lrrrrrrrr}
-    \toprule
-    Noise level & MSE  & RMSE & MAE  & R\textsuperscript{2} & sMAPE \\
-    \midrule
-    5\%         & 0.03 & 0.18 & 0.15 & 0.97                 & 0.39  \\
-    10\%        & 0.08 & 0.29 & 0.23 & 0.92                 & 0.55  \\
-    50\%        & 0.62 & 0.79 & 0.63 & 0.49                 & 1.05  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-For the metrics between the predictions and the noise-free version of the target function values, the results parallel the outcomes of the coefficient predictions.
-The metrics show that the model performs slightly better with more pronounced differences for the higher noise levels.
-This echoes our previous statement on the effect of independent \enquote{measurement} noise in the target values on the evaluation metrics.
-\begin{table}[H]
-  \caption{Performance metrics of function value from evaluated coefficient prediction compared to unperturbed targets in scenario 1 by noise level.}\label{table:scenario_1_clean_function_metrics}
-  \centering
-  \begin{tabular}{lrrrrrrr}
-    \toprule
-    Noise level & MSE  & RMSE & MAE  & R\textsuperscript{2} & sMAPE \\
-    \midrule
-    5\%         & 0.03 & 0.18 & 0.14 & 0.97                 & 0.38  \\
-    10\%        & 0.07 & 0.27 & 0.21 & 0.93                 & 0.53  \\
-    50\%        & 0.37 & 0.61 & 0.49 & 0.62                 & 0.94  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The next part of this scenario is the results from predicting the exact solution of \lccref{eq:sine_derivative} which is \lccref{eq:sine_function}.
-The function values will be computed with the same discretization as the number of modes we used in the training set.
-Once the values are obtained for both functions, the coefficients are computed.
-Then instancing the FourierBasis class with the coefficients of the derivative function, we can create perturbed versions according to the noise levels of the training set.
-Finally, the derivative is used to predict the noise-free antiderivative.
-The results are presented in \lccrefs{table:scenario_1_exact_spectral_metrics,table:scenario_1_exact_function_metrics}.
-For 5\% and 10\% noise levels, the model shows that it has learned the relation.
-However, the 50\% noise level, the model has been unable to predict the results well enough.
-The marked difference in error across all metrics between the 50\% and the lower noise levels is more apparent for this specific exact problem compared to the test sets.
-A clear picture of this can be seen when we compare the sMAPE metric.
-For the test set, the predictions on average results in a value of 1, however, for this exact problem the sMAPE value is 1.4 to 1.7.
-
-\begin{table}[H]
-  \caption{Performance metrics of coefficient prediction of exact antiderivative in scenario 1 by noise level.}\label{table:scenario_1_exact_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    Noise level & MSE   & RMSE & MAE  & sMAPE \\
-    \midrule
-    5\%         & 0.09  & 0.29 & 0.16 & 1.18  \\
-    10\%        & 0.80  & 0.89 & 0.31 & 1.23  \\
-    50\%        & 10.33 & 3.21 & 0.83 & 1.44  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\begin{table}[H]
-  \caption{Performance metrics of evaluated function values of coefficient prediction of exact antiderivative in scenario 1 by noise level.}\label{table:scenario_1_exact_function_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    Noise level & MSE  & RMSE & MAE  & sMAPE \\
-    \midrule
-    5\%         & 0.00 & 0.06 & 0.05 & 0.23  \\
-    10\%        & 0.03 & 0.18 & 0.15 & 0.36  \\
-    50\%        & 0.41 & 0.64 & 0.58 & 1.65  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The predictions of the exact equation is shown in \lccref{fig:antiderivative_exact}.
-Visually, we can see that as the noise level increases, the model predictions become worse.
-Another observation is how the higher the noise level, the more the predicted functions become closer to zero.
-This is explained by the double penalty phenomenon \autocite{lledoScaledependentVerificationPrecipitation2023}.
-The loss function used for LSSVR penalizes the model for predicting a non-zero value that turns out to be wrong compared to predicting a zero value.
-This results in a model with predictions that are close to the mean of the training data.
-
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/antiderivative_exact_input.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:antiderivative_exact_input}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/antiderivative_exact_prediction.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:antiderivative_exact_prediction}
-  \end{subfigure}
-  \caption{(\subref{fig:antiderivative_exact_input}) The perturbed exact input function values from \lccref{eq:sine_derivative}.\ (\subref{fig:antiderivative_exact_prediction}) Prediction of antiderivative from the input function that was perturbed.}\label{fig:antiderivative_exact}
-\end{figure}
-
-For inverse problems, we simply use the same testing set with the labels now used to predict the features.
-The model instances are still the same as before.
-With the implementation shown in \lccref{fig:spectralsvr_inverse_impl}, we run the inverse function for predicting coefficients with 2000 epochs, a learning rate of 0.02, and randomized starting point from a normal distribution multiplied by a factor of 0.05.
-The results of inverse prediction for all three noise levels are shown in \lccref{table:scenario_1_inv_spectral_metrics}.
-These metrics were computed after both the target and predicted input functions are scaled back using the same scaling functions they were scaled down with.
-Because the scales of the input and output functions are different, the absolute metrics are much larger in these results compared to the forward problem results.
-For reference, the target input coefficients on average range from -695.65 to 694.9.
-The relative metrics show that for the lower noise levels, the accuracy is still relatively good.
-However, the values are lower than the values for the forward test.
-The difference with the antiderivative prediction becomes more pronounced with the higher noise levels.
-For the highest noise level, the performance has degraded so far that the predictions are worse than a baseline model from the mean of the target input functions.
-One must also note that despite the much worse results of the other metrics for the highest noise level, at this time we're unable to explain why sMAPE results in roughly the same performance as in the forward problem.
-
-\begin{table}[H]
-  \caption{Performance metrics of coefficient inverse prediction of derivative in scenario 1 by noise level.}\label{table:scenario_1_inv_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrrr}
-    \toprule
-    Noise level & MSE      & RMSE   & MAE    & R\textsuperscript{2} & sMAPE \\
-    \midrule
-    5\%         & 1739.56  & 41.71  & 26.44  & 0.91                 & 0.36  \\
-    10\%        & 3485.10  & 59.03  & 42.19  & 0.76                 & 0.52  \\
-    50\%        & 49319.73 & 222.08 & 174.48 & -0.19                & 1.05  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-Next, we have the correlation image and p-matrix for the model of each noise level.
-The results are shown in \lccref{fig:scenario_1_interpretation}.
-Each row in the figure represent the results of a model trained on a different noise level.
-The correlation image for 5\% and 10\% noise show clear lines on the coefficient corresponding to the output coefficient that was sorted.
-We can also see that the negative wave number reflection also being sorted.
-This is because of the reflection that occurs with complex Fourier coefficients for real-valued functions.
-There are other faint vertical lines you are able to see for other input coefficients.
-These faint lines are not sorted like the corresponding coefficients we mentioned before.
-Meaning, while they don't affect the particular output coefficients that were sorted, they do show that there is information embedded in the kernel matrix for these input coefficients.
-However, if we look at the 50\% noise correlation image, even the corresponding coefficient does not show a clear line or gradient.
-The lines are more noisy compared to the other noise levels.
-But the kernel still manages to embed some information.
-The p-matrices show that The model itself is able to still learn some relationship between the input coefficients and the output coefficients.
-For the 5\% and 10\% noise levels, the p-matrices show very clearly the contributions of input coefficients to the output coefficients.
-However, looking at the p-matrix for 50\% noise level, the lower wave numbers show lower contribution of input coefficients to the output coefficients.
-\begin{figure}[H]
-  \begin{adjustwidth}{-0.05\linewidth}{-0.05\linewidth}
-    \centering
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_ci_5.pgf}
-      \end{adjustbox}
-      \caption{Correlation image 5\% noise.}\label{fig:sc1_ci_5}
-    \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_pm_5.pgf}
-      \end{adjustbox}
-      \caption{The p-matrix for 5\% noise.}\label{fig:sc1_pm_5}
-    \end{subfigure}
-    % \\[\baselineskip]
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_ci_10.pgf}
-      \end{adjustbox}
-      \caption{Correlation image 10\% noise.}\label{fig:sc1_ci_10}
-    \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_pm_10.pgf}
-      \end{adjustbox}
-      \caption{The p-matrix for 10\% noise.}\label{fig:sc1_pm_10}
-    \end{subfigure}
-    % \\[\baselineskip]
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_ci_50.pgf}
-      \end{adjustbox}
-      \caption{Correlation image 50\% noise.}\label{fig:sc1_ci_50}
-    \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_pm_50.pgf}
-      \end{adjustbox}
-      \caption{The p-matrix for 50\% noise.}\label{fig:sc1_pm_50}
-    \end{subfigure}
-  \end{adjustwidth}
-  \caption{Correlation image (left column) and p-matrix (right column) for each model trained on a different noise level (row).
-The correlation image was sorted same order the values of the real component of wave number \(k=2\) were sorted in descending order.}\label{fig:scenario_1_interpretation}
-\end{figure}
-
-The final observation we make is how for all the p-matrices the pronounced contribution of the input wave number to their corresponding output wave number.
-This means that the majority of contributions to each output coefficients come from the corresponding input coefficients of the same wave number.
-Our knowledge on how the simple derivative equation for Fourier series relate the coefficients of the derivative function and the antiderivative function is shown in \lccref{eq:derivative_coeff}.
-This aligns with the contributions shown by the p-matrices.
-This confirms that the model is indeed learning the relations that is defined by the derivative equation.
-
-In summary, the model is able to learn the linear relationship defined by the derivative equation.
-This is true even for high noise levels.
-The model also learns the actual relationship between each wave number which is shown in the p-matrix.
-Inverse prediction of the input function is also successfully done for lower noise levels.
-At high noise levels, the noise overwhelms the model.
-
-\subsection{Scenario 2}
-\noindent The second scenario results are presented in two parts which are the coefficient predictions and function value predictions.
-The functions are first preprocessed in order to format them into current and next values in time as discussed in \lccref{sec:data_transformation}.
-The sample pairs are first divided into two for the training and testing sets.
-Each function is then discretized into 200 time steps.
-Then, the features are put together as the coefficients of the solution and forcing term at the current time step.
-The labels are the solution at the next time step.
-Since there is too much data to fit into memory all at once at the end of this process, we randomly sample the feature and label pairs.
-This result in a maximum of 8000 samples for the training set and 2000 samples for the testing set.
-As mentioned in \lccref{sec:data_transformation}, the training features are used to fit a scaling function.
-And then, all features are scaled using the fitted scaling function.
-
-The coefficient value predictions are shown in \lccref{table:scenario_2_spectral_metrics}.
-The RBF kernel parameter computed from the data is once again the same for all versions of the dataset with a value of 5.66.
-The testing metrics show that the performance of the model vary with the viscosity value \(\nu \).
-Starting with the inviscid Burgers' equation, with \(\nu=0\), the model performs the best with a close second from the model for the \(\nu = 0.01 \) dataset version.
-The function value evaluated from the predictions is shown in \lccref{table:scenario_2_function_metrics}.
-The metrics across the board shows that the function value relative metrics are slightly better compared to the coefficients.
-Comparing the absolute metrics for the same table, we see the same general trend that the higher viscosity show the model performing worse.
-For reference, the maximum amplitude of the functions on average are \num{2.56e-02}.
-This puts the error in an order of magnitude less than the average maximum amplitude.
-For the coefficients, on average, the maximum absolute value at each time step is \num{9.29e-02}.
-This means for the viscosity of 0.0 and \num{0.01}, the error is roughly 1 to 9 of the maximum absolute value.
-
-\begin{table}[H]
-  \caption{Performance metrics of coefficient prediction of next time step in scenario 2 by viscosity.}\label{table:scenario_2_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & R\textsuperscript{2} & sMAPE \\
-    \midrule
-    0.0      & 3.46e-04 & 1.86e-02 & 1.24e-02 & 0.79                 & 0.65  \\
-    0.01     & 3.56e-04 & 1.89e-02 & 1.27e-02 & 0.78                 & 0.67  \\
-    0.1      & 9.17e-04 & 3.03e-02 & 2.32e-02 & 0.46                 & 1.08  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\begin{table}[H]
-  \caption{Performance metrics of function values evaluated from coefficient prediction of next time step in scenario 2 by viscosity.}\label{table:scenario_2_function_metrics}
-  \centering
-  \begin{tabular}{lrrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & R\textsuperscript{2} & sMAPE \\
-    \midrule
-    0.0      & 5.58e-05 & 7.47e-03 & 5.89e-03 & 0.82                 & 0.70  \\
-    0.01     & 5.74e-05 & 7.58e-03 & 6.01e-03 & 0.81                 & 0.71  \\
-    0.1      & 1.58e-04 & 1.26e-02 & 9.98e-03 & 0.51                 & 1.04  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The testing results are complimented with a rollout experiment.
-The results from the rollout are shown in \lccref{fig:scenario_2_rollout}.
-The rollout starts from time \(t=0\).
-In all the plots, this is at the bottom.
-We have included this initial condition in the plots.
-From this initial condition in combination with the forcing term at the initial time step, the model predicts the first time step solution.
-The model then uses the predicted solution combined with the corresponding forcing term to predict the second time step.
-To see how well the model is performing relative to the actual target values, we compute the difference between the two as shown in \lccrefs{fig:sc2_rollout_diff_0.0,fig:sc2_rollout_diff_0.01,fig:sc2_rollout_diff_0.1}.
-Observe that errors are introduced relatively early around time \(t=1\).
-However, the model rollout stays stable until the end despite this error.
-This results in the model being able to finish the rollout for this sample.
-\begin{figure}[H]
-  \centering
-  \begin{adjustwidth}{-0.1\linewidth}{-0.1\linewidth}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_target_0.0.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.0\)}\label{fig:sc2_rollout_target_0.0}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_pred_0.0.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.0\)}\label{fig:sc2_rollout_pred_0.0}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_diff_0.0.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.0\)}\label{fig:sc2_rollout_diff_0.0}
-    \end{subfigure}
-    \\[0.7\baselineskip]
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_target_0.01.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.01\)}\label{fig:sc2_rollout_target_0.01}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_pred_0.01.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.01\)}\label{fig:sc2_rollout_pred_0.01}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_diff_0.01.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.01\)}\label{fig:sc2_rollout_diff_0.01}
-    \end{subfigure}
-    \\[0.7\baselineskip]
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_target_0.1.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.1\)}\label{fig:sc2_rollout_target_0.1}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_pred_0.1.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.1\)}\label{fig:sc2_rollout_pred_0.1}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_diff_0.1.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.1\)}\label{fig:sc2_rollout_diff_0.1}
-    \end{subfigure}
-    % \\[0.7\baselineskip]
-  \end{adjustwidth}
-  \caption{The rollout predictions for one of the test function. The difference is calculated as the targets subtracted by the predictions.}\label{fig:scenario_2_rollout}
-\end{figure}
-
-Another observation we can see is that the difference between the target and rollout predictions is much more pronounced for lower viscosity values.
-This result is aligned with metrics shown in \lccrefs{table:scenario_2_rollout_spectral_metrics,table:scenario_2_rollout_function_metrics}.
-The absolute metrics show that the models are performing several times worse in rollout compared to the single time step tests shown in \lccrefs{table:scenario_2_spectral_metrics,table:scenario_2_function_metrics}.
-This seems to be the same challenge that traditional solvers also face with the shocks that may be present with lower viscosity values.
-This means that for rollout scenarios, the model has a much harder time with lower viscosity values.
-\begin{table}[H]
-  \caption{Performance metrics of coefficient rollout in scenario 2 by viscosity.}\label{table:scenario_2_rollout_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & sMAPE \\
-    \midrule
-    0.0      & 2.91e-01 & 5.40e-01 & 4.07e-01 & 0.90  \\
-    0.01     & 1.61e-01 & 4.01e-01 & 2.86e-01 & 0.75  \\
-    0.1      & 1.70e-01 & 4.12e-01 & 3.02e-01 & 0.81  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-\begin{table}[H]
-  \caption{Performance metrics of function values evaluated from coefficient rollout in scenario 2 by viscosity.}\label{table:scenario_2_rollout_function_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & sMAPE \\
-    \midrule
-    0.0      & 5.81e-02 & 2.41e-01 & 1.89e-01 & 1.04  \\
-    0.01     & 3.17e-02 & 1.78e-01 & 1.40e-01 & 0.94  \\
-    0.1      & 2.91e-02 & 1.71e-01 & 1.33e-01 & 0.92  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The exact function \cref{eq:burgers_exact_solution} is computed for each viscosity value.
-The discrete Fourier transform of the values are then used for doing rollout with the model.
-For the forcing term, we just use a constant function with a value of zero.
-The rollout predictions are shown in \lccref{fig:scenario_2_exact}.
-The model is not successful in the rollout for the inviscid equation and for the viscosity of \(\nu=0.01\).
-Both of these cases, the model produces too much error that the original function is no longer recognizable in the predictions.
-For the higher viscosity value of \(\nu=0.1\) the rollout produces a recognizable prediction.
-The error stays to about half the maximum function value.
-We do see some more noticeable error in the flatter parts of the function.
-The error also take a very similar shape across the different viscosity values.
-Since we essentially used the same solutions for training the model for each viscosity, the similarity in error means that it can be alleviated with more diverse training samples.
-The error for the flatter functions may also be alleviated by including similar flatter functions during training.
-\begin{figure}[H]
-  \centering
-  \begin{adjustwidth}{-0.1\linewidth}{-0.1\linewidth}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_target_0.0.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.0\)}\label{fig:sc2_exact_target_0.0}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_pred_0.0.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.0\)}\label{fig:sc2_exact_pred_0.0}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_diff_0.0.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.0\)}\label{fig:sc2_exact_diff_0.0}
-    \end{subfigure}
-    \\[0.7\baselineskip]
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_target_0.01.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.01\)}\label{fig:sc2_exact_target_0.01}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_pred_0.01.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.01\)}\label{fig:sc2_exact_pred_0.01}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_diff_0.01.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.01\)}\label{fig:sc2_exact_diff_0.01}
-    \end{subfigure}
-    \\[0.7\baselineskip]
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_target_0.1.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.1\)}\label{fig:sc2_exact_target_0.1}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_pred_0.1.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.1\)}\label{fig:sc2_exact_pred_0.1}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_diff_0.1.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.1\)}\label{fig:sc2_exact_diff_0.1}
-    \end{subfigure}
-    % \\[0.7\baselineskip]
-  \end{adjustwidth}
-  \caption{The rollout predictions for one of the exact function in \lccref{eq:burgers_exact_solution}.
-The difference is calculated as the targets subtracted by the predictions.}\label{fig:scenario_2_exact}
-\end{figure}
-
-The metrics for the exact rollout further solidifies our observations from the plots.
-The metrics are shown in \lccrefs{table:scenario_2_exact_spectral_metrics,table:scenario_2_exact_function_metrics}.
-While the absolute metrics are low, this is mostly due to the maximum function values of the exact function also being pretty low.
-The relative metric sMAPE shows a much clearer picture.
-As expected, the inviscid prediction is pretty much just error.
-The next result, for viscosity \(\nu=0.01\), is better.
-This seems to be from the slight conformance to the target.
-The plots for this viscosity show that the prediction contains \enquote{shapes} similar to the target despite the scale not being close to the target.
-Finally, the highest viscosity level results show the best performance.
-Despite the good performance in the higher detail areas of the function, the error from the flatter areas overwhelm the metrics due to its larger portion of the function.
-\begin{table}[H]
-  \caption{Performance metrics of coefficient rollout of exact solution in scenario 2 by viscosity.}\label{table:scenario_2_exact_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & sMAPE \\
-    \midrule
-    0.0      & 2.16e-02 & 1.47e-01 & 1.08e-01 & 2.00  \\
-    0.01     & 1.32e-02 & 1.15e-01 & 6.37e-02 & 1.58  \\
-    0.1      & 2.83e-03 & 5.32e-02 & 4.00e-02 & 1.50  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-\begin{table}[H]
-  \caption{Performance metrics of function values evaluated from coefficient rollout of exact solution in scenario 2 by viscosity.}\label{table:scenario_2_exact_function_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & sMAPE \\
-    \midrule
-    0.0      & 4.16e-03 & 6.45e-02 & 4.56e-02 & 2.00  \\
-    0.01     & 3.23e-03 & 5.68e-02 & 4.94e-02 & 1.73  \\
-    0.1      & 3.86e-04 & 1.97e-02 & 1.62e-02 & 1.47  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The correlation image and p-matrix for each viscosity can be seen in \lccref{fig:scenario_2_interpretation}.
-Analyzing the correlation images first, we see that some columns are sorted in correlation to how the samples are sorted based on the real component of the 4th output wave number.
-For the inviscid equation, this correlation is the strongest with multiple columns exhibiting the correlation.
-The highest and visually most sorted values are from the forcing term portion of the inputs.
-Different wave numbers in the inputs are also sorted differently, this indicates an inverse correlation.
-For a higher viscosity of \(\nu=0.01\), a weaker correlation is still present.
-
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_ci_0.0.pgf}
-    \end{adjustbox}
-    \caption{Correlation image \(\nu=0.0\).}\label{fig:sc2_ci_0.0}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_pm_0.0.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix for \(\nu=0.0\).}\label{fig:sc2_pm_0.0}
-  \end{subfigure}
-  % \\[-0.7\baselineskip]
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_ci_0.01.pgf}
-    \end{adjustbox}
-    \caption{Correlation image \(\nu=0.01\).}\label{fig:sc2_ci_0.01}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_pm_0.01.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix for \(\nu=0.01\).}\label{fig:sc2_pm_0.01}
-  \end{subfigure}
-  % \\[-0.7\baselineskip]
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_ci_0.1.pgf}
-    \end{adjustbox}
-    \caption{Correlation image \(\nu=0.1\).}\label{fig:sc2_ci_0.1}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_pm_0.1.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix for \(\nu=0.1\).}\label{fig:sc2_pm_0.1}
-  \end{subfigure}
-  \caption{Correlation image (left column) and p-matrix (right column) for each model trained on a different viscosity (row).
-The correlation image was sorted same order the values of the real component of wave number \(k=2\) were sorted in descending order.}\label{fig:scenario_2_interpretation}
-\end{figure}
-
-Once we get to the highest viscosity, while the order is still present, we see a more random arrangement of the correlation image values.
-This observation and the lower scores can both be explained by the level of temporal discretization.
-This is the same issue we encounter when we use some traditional methods for higher viscosity values with the same time step for lower viscosity values \autocite{kassamFourthOrderTimeSteppingStiff2005,seydaogluNumericalSolutionBurgers2016}.
-The issue arises in stiff differential equations.
-Stiff differential equations refer to the presence of a rapidly varying component.
-We can see that the larger amplitudes of high frequency components in the forcing term to represent the rapidly varying components as shown in \lccrefs{fig:burgers_forcing_0.0,fig:burgers_forcing_0.01,fig:burgers_forcing_0.1}.
-Traditionally, stiff equations would require specific numerical methods purpose built to efficiently solve the problem.
-Otherwise, the using a solver like FDM would require much finer time steps than the one we are using here.
-
-The p-matrix shows the difference in contributions of both input functions.
-For the inviscid equation, the contributions mainly come from the forcing term.
-The current solution contributes a smaller amount in comparison.
-There is similarity with the antiderivative p-matrices in this case.
-The contributions to each output wave number mainly come from input coefficients with the same wave number.
-However, there is a noticeable contribution from other wave numbers too unlike the antiderivative case.
-The biggest contribution from the current solution is the constant/bias term.
-For higher viscosity values, notice that the contribution of the previous solution increases.
-The increase is more pronounced for higher frequencies.
-This aligns with the quadratic scaling from the wave number on the coefficients \autocite{canutoSpectralMethodsEvolution2007}.
-The p-matrix for lower viscosity values show more structured contribution of other wave numbers in comparison to the higher wave numbers.
-This structure comes in the form of a grid pattern.
-For the real components of the output, the contribution of other wave numbers oscillate between higher and lower values depending on whether the input component is real or not.
-The imaginary output components on the other hand have a more constant contribution across the input components.
-The contribution once again become more pronounced the higher the absolute value of the wave number.
-
-To summarize, Low viscosity values are a challenge to the model as with traditional methods.
-Despite that, this scenario confirms the model's ability to learn the nonlinear relationship defined by the Burgers' equation.
-The model is also able to stay stable with a relatively large time step.
-This concludes the synthetic data portion of the study.
-
-\subsection{Scenario 3}
-\noindent This final scenario tests the model on a much more complex dataset.
-As said previously, this dataset, which is computed using real observations of Earth's weather system, will be used to represent the model learning a very complex system with many unknown contributing variables.
-For our case, this means the data used will be limited to the 2-meter temperature.
-The anomaly is computed by subtracting the climatology from the corresponding day of years and hours of the atmospheric state.
-For example, the temperature on the 6\textsuperscript{th} of January 1998 at 18:00 UTC is subtracted with the average temperature for the 6\textsuperscript{th} day of the year at 18:00 hour UTC\@.
-For any anomaly predictions, the corresponding atmospheric state can simply be computed as the inverse process described before by adding the climatology to the predicted anomaly.
-
-The preprocessing of the data is carried out in the same manner as the Burgers' equation experiments.
-The difference being that for the features we only include the current anomaly of the atmosphere and there are no forcing terms.
-The targets are the future anomaly of the atmosphere.
-The reason for choosing to train and predict the anomaly instead of the state valued themselves is to avoid the model from just learning the obvious periodicity that exists in weather such as the day-night cycle or the seasons.
-Next, Both the current anomaly and future anomaly are Fourier transformed to their 2-dimensional coefficients.
-This process is done for both the training and testing set.
-Once the features for both are processed, we fit the standard scaling function on the training features.
-Using this fitted scaling function, both the training and testing features are scaled to a mean of 0 and standard deviation of approximately 1.
-
-The testing results are shown in \lccrefs{table:sc3_test_anomaly_metrics,table:sc3_test_state_metrics}.
-To put the absolute metrics into context, the median test state coefficient' maximum absolute value is \num{569364.25}.
-With this information, an RMSE value of 64.72 is relatively low error.
-The relative metric sMAPE also agrees with this, with a value of 0.76.
-The function values show that the model on average has an error of around 2 degrees kelvin or Celsius.
-This is again relatively small for the range of temperatures on Earth which span roughly 120 degrees kelvin across the historical maxima and minima.
-From existing knowledge of the problem, we know these values for the metrics are mainly due to the periodicity of atmospheric states.
-When we look at the anomaly metrics, the model is still able to learn some things and perform slightly better than a model of anomaly averages.
-However, since the median maximum absolute value for the state coefficients is \num{1155.14}, the error rate is not as good as the state predictions.
-\begin{table}[H]
-  \caption{Performance metrics of anomaly coefficient prediction for scenario 3.}\label{table:sc3_test_anomaly_metrics}
-  \centering
-  \begin{tabular}{lrrrrr}
-    \toprule
-                   & MSE     & RMSE  & MAE   & R\textsuperscript{2} & sMAPE \\
-    \midrule
-    spectral       & 4189.16 & 64.72 & 32.47 & 0.35                 & 1.19  \\
-    function value & 4.09    & 2.02  & 1.44  & 0.09                 & 1.24  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\begin{table}[H]
-  \caption{Performance metrics of state coefficient prediction for scenario 3.}\label{table:sc3_test_state_metrics}
-  \centering
-  \begin{tabular}{lrrrrr}
-    \toprule
-                   & MSE     & RMSE  & MAE   & R\textsuperscript{2} & sMAPE \\
-    \midrule
-    spectral       & 4189.16 & 64.72 & 32.47 & 0.56                 & 0.74  \\
-    function value & 4.09    & 2.02  & 1.44  & 0.75                 & 0.01  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The predictions from test features are processed through the Fourier inverse transform to evaluate the function values.
-The direct predictions, which is the anomaly, is shown in \lccref{fig:sc3_anomaly_predictions}.
-The model seem to be predicting less extreme values that are noticeable in the target.
-Specifically areas over North America, Central Asia, and parts of Antarctica show lower temperature anomaly than expected.
-We also loose detail in areas which should have a lower anomaly such as northern areas of Africa, Greenland, and South Asia.
-The lack of detail seems to be a problem of underestimation.
-We believe this is caused by the so-called \enquote{double penalty} issue caused by the loss function used for the LSSVR \autocite{lledoScaledependentVerificationPrecipitation2023}.
-The predictions tend to be closer to the mean of the data to avoid the extra penalty from a wrong prediction with a high value.
-One way to allow for finer details that are less accurate is to penalize the higher frequency wave numbers less compared to the lower frequency wave numbers.
-For our case this means the LSSVR for each output will have their regularization parameter decreased to allow the model to focus less on the errors for higher frequencies.
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    % \centering
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_anom_pred.pgf}
-    \end{adjustbox}
-    \caption{Predicted 2-meter temperature anomaly.}\label{fig:sc3_anomaly_pred}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    % \centering
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_anom_target.pgf}
-    \end{adjustbox}
-    \caption{Target 2-meter temperature anomaly.}\label{fig:sc3_anomaly_target}
-  \end{subfigure}
-  \caption{2-meter temperature anomaly prediction for the 1\textsuperscript{st} of January 2020 at 6:00 UTC based on the previous anomaly at 0:00 UTC.}\label{fig:sc3_anomaly_predictions}
-\end{figure}
-
-The state predictions which is obtained by adding the climatology to the predicted anomaly is shown in \lccref{fig:sc3_state_predictions}.
-This further shows areas of discrepancy between the prediction and the target.
-The area in the South Pacific show that the target has a higher difference temperature compared to the prediction.
-This smoothness in the prediction is easier to see for areas in the ocean.
-Many sharp features are lost and the state prediction start to resemble averaged view of the climatology.
-We must also take into account that the model only used temperature distribution data.
-Other pieces of information we know to be crucial to weather prediction such as wind speed or pressure was not included in the inputs.
-With this in consideration the model was still able to learn some relationships defined by governing equations of weather.
-%TODO: decide to mention the results of this or not (https://sites.research.google/weatherbench/deterministic-scores/)
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    % \centering
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_state_pred.pgf}
-    \end{adjustbox}
-    \caption{Predicted 2-meter temperature.}\label{fig:sc3_state_pred}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    % \centering
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_state_target.pgf}
-    \end{adjustbox}
-    \caption{Target 2-meter temperature.}\label{fig:sc3_state_target}
-  \end{subfigure}
-  \caption{2-meter temperature prediction for the 1\textsuperscript{st} of January 2020 at 6:00 UTC based on the previous anomaly at 0:00 UTC.}\label{fig:sc3_state_predictions}
-\end{figure}
-
-The p-matrix and correlation image is shown in \lccref{fig:sc3_interpretation}.
-For the correlation image, we see that most wave numbers are correlated or inversely correlated with the outputs.
-The strongest correlation is shown by the features of the same wave number as the sorted target.
-This is an indication that the equations involved may be nonlinear.
-If we look at the p-matrix however, it seems very flat save a faint diagonal line from the top left to the bottom right.
-The values of the p-matrix are also extremely high.
-With the \enquote{flatness} we see, this is indicative of strong contributions by a few inputs.
-
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_ci.pgf}
-    \end{adjustbox}
-    \caption{The correlation image.}\label{fig:sc3_ci}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_pm.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix.}\label{fig:sc3_pm}
-  \end{subfigure}
-  % \\[-0.7\baselineskip]
-  \caption{Correlation image and p-matrix for WeatherBench 2 model.
-The correlation image was sorted same order the values of the real component of wave number \((k_{longitude}=0, k_{latitude}=2)\) were sorted in descending order.}\label{fig:sc3_interpretation}
-\end{figure}
-
-To see more details of the p-matrix, we show a zoomed in version in \lccrefs{fig:sc3_pm_zoom1,fig:sc3_pm_zoom2}.
-The relationships are much more clear between features and outputs that do not share the same wave number.
-The coefficients with the same longitude wave numbers appear in the same \enquote{square} shape.
-Within the \enquote{square}, coefficients close to the same latitude wave number show much stronger contribution.
-For low wave numbers, shown in \lccref{fig:sc3_pm_zoom1}, the contribution is spread over more latitude wave numbers.
-The higher wave numbers, on the other hand, has the contributions much more concentrated on the coefficients with the same latitude wave numbers.
-In addition, the value of contribution differ by an order of magnitude with lower longitude wave numbers having higher maximum contribution.
-This observation suggests that the nonlinearity and magnitude are inversely proportional to the absolute value of the longitude wave number.
-This is in contrast to when we discussed the forcing term for our Burgers' equation scenario.
-The low frequencies in longitude may indicate that the model has learned some feature of the anomaly that is specific to different times of day.
-This is because the lowest longitudinal wave number would correspond to when different parts of the world is in nighttime or in daytime.
-Other possible explanations may be due to the fact that the earth more closely resemble a sphere compared to the toroidal shape that the 2-dimensional Fourier transform assumes.
-This would result in the representation latitude-wise being distorted.
-For this issue, the use of spherical harmonics may be a better fit to rule out the possibility of any distortions the Fourier transform may introduce.
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_pm_zoom1.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix zoomed in to \((k_{longitude}=\{0, 1, 2\}, k_{latitude}=[-16, 16))\).}\label{fig:sc3_pm_zoom1}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_pm_zoom2.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix zoomed in to \((k_{longitude}=\{\phantom{-}31,-32,\phantom{-}32\}, k_{latitude}=[-16, 16))\).}\label{fig:sc3_pm_zoom2}
-  \end{subfigure}
-  \caption{The p-matrix of the WeatherBench 2 models zoomed in to specific wave numbers.}\label{fig:sc3_pm_zoomed}
-\end{figure}
-
-The results of our experiments show that the proposed model has the ability to learn the relationships that PDEs and other governing equations define.
-The interpretation methods for support vector regression that we used, namely the correlation image and p-matrix developed by \textcite{ustunVisualisationInterpretationSupport2007}, allows us to confirm what the model has learned.
-In the case of the WeatherBench2 model, it has also allowed us to glean some insight into some mechanisms that the model has learned.
-This information was used to verify the learned relationships for the simple derivative equation.
-Together with the performance metrics on three different problems, we have shown the proposed model to be a viable tool for situations with limited knowledge and a need for some level of interpretability of the model.

### 2025-01-14 technical_doc/introduction.tex
fix labels, fix problem with graphics path and suround with curly braces, start technical document

% !TEX root = ./technical_doc.tex
\chapter{INTRODUCTION}

\section{Purpose}

This document is an example of a software manual created using \LaTeX\ and Overleaf. It provides a nice clean format for producing this type of technical document.

Simply start writing your document and use the Recompile button to view the updated PDF preview. Examples of commonly used commands and features can be found in the sections below, to help you get started.

To change the logo shown on the front page, simply upload your own logo image file (via the file-tree menu) to replace the default logo.pdf file.

Once you're familiar with the editor, you can find various project settings in the Overleaf menu, accessed via the button in the very top left of the editor. To view tutorials, user guides, and further documentation, please visit our \url{https://www.overleaf.com/learn}. If you haven't used \LaTeX\ before, our \url{https://www.overleaf.com/learn/latex/Learn_LaTeX_in_30_minutes} tutorial is an excellent place to start.

For large documents, it can be useful to split the document into multiple source files.
Double-clicking on text in Overleaf's PDF preview will take you directly to the corresponding code in the editor.

### 2025-01-14 technical_doc/requirements.tex
fix labels, fix problem with graphics path and suround with curly braces, start technical document

--- 2025-01-14 technical_doc/introduction.tex
@@
 % !TEX root = ./technical_doc.tex
-\chapter{INTRODUCTION}
-
-\section{Purpose}
-
-This document is an example of a software manual created using \LaTeX\ and Overleaf. It provides a nice clean format for producing this type of technical document.
-
-Simply start writing your document and use the Recompile button to view the updated PDF preview.
-Examples of commonly used commands and features can be found in the sections below, to help you get started.
-
-To change the logo shown on the front page, simply upload your own logo image file (via the file-tree menu) to replace the default logo.pdf file.
-
-Once you're familiar with the editor, you can find various project settings in the Overleaf menu, accessed via the button in the very top left of the editor.
-To view tutorials, user guides, and further documentation, please visit our \url{https://www.overleaf.com/learn}.
-If you haven't used \LaTeX\ before, our \url{https://www.overleaf.com/learn/latex/Learn_LaTeX_in_30_minutes} tutorial is an excellent place to start.
-
-For large documents, it can be useful to split the document into multiple source files.
-Double-clicking on text in Overleaf's PDF preview will take you directly to the corresponding code in the editor.
+\chapter{REQUIREMENTS}

### 2025-01-14 technical_doc/testing.tex
fix labels, fix problem with graphics path and suround with curly braces, start technical document

--- 2025-01-06 skripsi/chapter4.tex
@@
-% !TEX root = ./skripsi.tex
-\chapter{RESULTS AND DISCUSSION}
-\noindent This chapter will elaborate on the results of the study and relevant phases for analysis.
-This chapter is organized into five sections which are the results of data generation, data retrieval, design of computational model, implementation of computational model, experimental scenarios, and the experiments themselves.
-
-\section{Data Generation}\label{sec:data_generation}
-\noindent This study uses two data acquisition approaches.
-The first approach which is discussed in this section is data generation.
-This process involves manufacturing data randomly in such a way that they obey the PDEs to be modeled.
-The generated data consists of features and labels.
-These features and labels in the context of PDEs are parameters and the solution of the PDEs, respectively.
-The PDEs enforce a relationship between parameters and the solution.
-This relationship is implicitly encoded into the features and labels, which is what machine learning models can learn.
-Because the solution and parameters to PDEs are functions and there are many kinds with different properties, generating all the different kinds of functions is a difficult task.
-This is why this study focuses on Fourier functions.
-This means that out of the space of all functions \(F \) which include categories such as polynomials \(f\left(x\right)=a_{n}x^n+\cdots+a_1x+a_0\) where \(f\in F\), and \(a_n\) are constants; we only consider the subset of functions \(U \subset F\) which are of the form \(u\left(x\right)=\sum_{k}^{m}c_k e^{2\pi i k \frac{x}{P}}\).
-
-Using the subset of Fourier functions has several benefits which has motivated the choice.
-First these functions are characterized purely by their coefficients \(c_k\), meaning there is no need to store discretized values which potentially saves space and computation.
-The second benefit is that other functions such as polynomials can be approximated by them using the Fourier transform.
-This means that despite limiting the set of functions to Fourier functions, the behavior of PDEs with other sets of functions can be approximated to a certain extent.
-The final benefit is the mature ecosystem around these functions which include fast algorithms for the Fourier transform and even numerical approaches for solving known PDEs like the previously mentioned spectral method.
-In summary the generated data consists of features and labels which are Fourier functions implicitly defining the relationship enforced by a PDE and scenario.
-After establishing the kind of functions to be used in dataset generation, the process can proceed.
-There are 4 steps involved in the data generation:% TODO: add reference to second chapter for spectral method, fourier transform, and other external concepts.
-\begin{enumerate}
-  \item Scenario and PDE Determination:
-        The first step of data generation is determining the scenario related to the PDE or governing equations.
-First, the PDE to be modeled is determined based on the goals of the dataset.
-Then, one or more of the parameters is chosen to predict the solution.
-The chosen parameters will be called the input functions and the solution will be called output functions from here on.
-The second part of the scenario is the domain or more simply the physical space occupied by the system to be modeled.
-The domain will be used to compute the function values in relation to the physical space from coefficients of Fourier functions.
-  \item Parameter Determination:
-        The second step is determining all parameters other than that input parameter based on the scenario and governing equation.
-These parameters may be coefficients such as material properties like density or viscosity, or forcing terms which model external influence on the system like a heat source in the case of the heat equation.
-Depending on the parameters, solutions of PDEs may behave very differently, such as the appearance of discontinuities in the solution to low viscosity Burgers' equation.
-Because of this, the choice of parameters is guided by what the dataset seeks to do.
-  \item Random Coefficient Generation:
-        The third step of data generation is randomly generating the solutions for the chosen equation.
-Generating random functions in the space of Fourier functions exploits the fact that the coefficients characterize the function completely.
-By randomly assigning coefficients \(c_k\), many functions can be generated randomly with very little cost.
-Since the coefficients need to be complex numbers as in \lccref{eq:complex_number}, both real and imaginary components are generated independently by assigning a random value to each component for each wave number \(k\).
-They are then put together again into complex numbers.
-
-        Since only real functions are of interest in this study, the generation cost can be approximately halved.
-This is because for real functions the coefficients for negative wave numbers \(k\) are complex conjugate of the positive wave numbers.
-This means that once the positive coefficients are generated, one only needs to compute their complex conjugate and concatenate the result with the coefficients of positive wave numbers.
-For dimensions higher than one, a simpler approach is used.
-The coefficients are generated for all wave numbers including the negative ones.
-The inverse Fourier transform is computed and this results in complex functions.
-The real components of these functions are kept and the Fourier transform is applied to get the coefficients of the real functions.
-Finally, these generated coefficients then be used with the basis functions as input functions.
-        % TODO: add diagram for generating real functions, the mirroring process too
-  \item Forcing Term Computation:
-        Finally, in order to ensure that the generated solution and chosen parameters satisfy the equation, the forcing term is computed as the residual of the equation of interest with the parameters that was previously determined.
-This computation is done using the spectral method.
-  \item Function Value and Noise Computation:
-        The generated solution and forcing functions are labeled as input and output functions.
-The values of both functions in the domain can then be computed using the scenario determined in the first step.
-Once all coefficients are generated, the function values are computed with an inverse Fourier transform.
-The real component of the function values are retained, and the imaginary component are zeroed out.
-Noise is added to the function values here as needed.
-The processed function values are then converted back into coefficients using a Fourier transform.
-This processing is necessary to ensure that the coefficients are only describing the real function.
-
-\end{enumerate}
-
-These four steps are the general processes involved in generating datasets for this study. Further specifics of the generation process of each dataset is explained in their respective subsections.
-
-\subsection{Data Generation: Anti-derivative}
-\noindent The first dataset is a simple one dimensional derivative.
-This was chosen as a simple proof of concept of the ability to solve a differential equation.
-The equation is related to many real-world problems such as acceleration and speed.
-One can imagine a train in an ideal world where acceleration is directly translated into speed.
-When the train accelerates at time \(t \) by some amount \(a \), we can expect the train to have some speed \(u \).
-In this ideal world, the relationship between speed and acceleration can be modeled with a simple differential \lccref{eq:derivative}.
-This scenario is found in many real systems albeit often with many more details such as different components of acceleration from friction, drag, gravity, and other factors.
-As previously mentioned in \lccref{sec:data_generation}, both velocity \(u \) and acceleration \(a \) are modeled with Fourier series in \lccrefs{eq:fourier_speed,eq:fourier_acceleration} respectively.
-\begin{align}
-  \dv{u\left( t \right)}{t} & = a\left( t \right) \label{eq:derivative}                         \\
-  u\left( t \right)         & = \sum_{k} \hat{u}_k e^{2\pi ikt} \label{eq:fourier_speed}        \\
-  a\left( t \right)         & = \sum_{k} \hat{a}_k e^{2\pi ikt} \label{eq:fourier_acceleration}
-\end{align}
-The domain of the scenario is a two-hour time window.
-This number was chosen because it is around the ideal length of travel time on high speed rail in comparison to air travel and car travel \autocite{givoniDevelopmentImpactModern2006,wangEfficiencySpatialEquity2019,wrro2236}.
-This is the first step in generating this dataset.
-
-In the second step, as the derivative \lccref{eq:derivative} does not contain any parameters other than the acceleration which is the input parameter, there are no other parameters to determine.
-Therefore, the data generation process proceeds to generating coefficients for the speed functions \(\hat{u} \).
-The coefficients are assigned randomly from a Gaussian distribution with a mean of zero and standard deviation of one.
-This choice was made such that most wave numbers will have a coefficient of close to zero leaving a sparse set of wave numbers to mostly affect the resulting function.
-In total, 5000 unique functions are generated with 100 complex coefficients each.
-
-In the third step, the output function coefficients are computed.
-To find the relation between \(\hat{u}_k \) and \(\hat{a}_k \), we need to find substitutes for each term in \lccref{eq:derivative}.
-To do this, we take the derivative of \lccref{eq:fourier_speed} which result in \lccref{eq:fourier_series_derivative}.
-Using this we can substitute the terms in \lccref{eq:derivative} with \lccrefs{eq:fourier_series_derivative,eq:fourier_acceleration} giving \lccref{eq:example_spectral_method_fourier_substituted}.
-Finally, after some algebraic manipulation we obtain the relationship between the input \(a^*\) and output function \(u^*\) in terms of their coefficients in \lccref{eq:derivative_coeff}.
-One also needs to choose the integration constant \(\hat{u}_{0}\) because at \(k=0\) \lccref{eq:derivative_coeff} becomes a division by zero.
-\begin{align}
-  \dv{u\left( x \right)}{x}                                    & = \sum_{k} \hat{u}_k\times \left( 2\pi ik \right) e^{2\pi ikx} \label{eq:fourier_series_derivative} \\
-  \sum_{k} \hat{u}_k\times \left( 2\pi ik \right) e^{2\pi ikx} & = \sum_{k} \hat{a}_k e^{2\pi ikx} \label{eq:example_spectral_method_fourier_substituted}            \\
-  \hat{u}_k                                                    & = \hat{a}_k / \left( 2\pi ik \right) \label{eq:derivative_coeff}
-\end{align}
-
-In the final step, using randomly generated values of \(\hat{a}_k\), the corresponding values of \(\hat{u}_k\) are computed with \lccref{eq:derivative_coeff}.
-These coefficients are then used to compute the function values inside the domain.
-The two-hour time window is represented by a grid of 500 discrete points.
-With the coefficients and evaluation points ready, the function values are computed using \lccrefs{eq:fourier_speed,eq:fourier_acceleration}.
-Next, noise is added to the function values in order to motivate models learning on the dataset to generalize on noise.
-To also allow evaluation of how well the model performs with different levels of noise, the samples are duplicated into three copies for each high, medium and low noise levels.
-The function values of each copy is perturbed with noise from a Gaussian distribution with zero mean and standard deviation of some percentage of the average function value standard deviation.
-The percentages of each high, medium, and low noise levels are 5, 10, and 50 percent.
-The perturbed function values are then transformed back into their coefficients.
-An example generated function and its different perturbed versions is shown in \lccref{fig:antiderivative_noise_levels}.
-The horizontal axis indicates time which is displayed in units of hours.
-The vertical axis indicates velocity in abstract units.
-
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/antiderivative_clean_perturbed_solution.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:antiderivative_noise_levels}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/antiderivative_clean.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:antiderivative}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/antiderivative_derivative_clean.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:derivative}
-  \end{subfigure}
-  \caption{(\subref{fig:antiderivative_noise_levels}) A generated function with no noise (clean), low noise level (5\%), medium noise level (10\%), and high noise levels (50\%).\ (\subref{fig:antiderivative}) Antiderivative function with no noise.\ (\subref{fig:derivative}) Derivative function with no noise.}
-\end{figure}
-% TODO: interesting note that model trains better on function to coefficient task when the antiderivative is computed from the randomly generated derivative than if the derivative is computed from the randomly generated antiderivative.
-THIS NEEDS A REASON AND ANALYSIS SO MIGHT NOT BE NEEDED IN THIS WRITING.
-MAYBE A GOOD IDEA FOR A SEPARATE PIECE
-
-\subsection{Data Generation: Burgers' Equation}
-\noindent The second dataset generated in this study concerns the Burgers' equation.
-This equation has been used to model a variety of cases including fluid dynamics, traffic flow, and, shock waves \autocite{bonkileSystematicLiteratureReview2018,orlandiBurgersEquation2000,becBurgersTurbulence2007,jamesonEnergyEstimatesNonlinear2007}.
-This equation is also used as a base problem for testing the effectivity of numerical methods in solving non-linear PDEs \autocite{barterShockCapturingPDEbased2008,banksNumericalErrorEstimation2012, tabatabaeiImplicitMethodsNumerical2007,bonkileSystematicLiteratureReview2018}.
-The nonlinear term in the equation creates steep gradients and even shock waves which are discontinuous with low viscosity conditions.
-These challenges test the stability of numerical solvers.
-This is the scenario and reason for the choice of this PDE\@.
-To control the viscosity and therefore the steepness of gradients, the formulation of the Burgers' equation considered in this study is the forced viscous Burgers' equation in one dimension.
-For a velocity of \(u(x, t)\), viscosity of \(\nu \), and forcing term of \(f(x, t)\), the formulation of the forced Burgers' equation is shown in \lccref{eq:forced_viscous_burgers}.
-\begin{align}
-  \pdv{u}{t}+u\pdv{u}{x}-\nu\pdv[2]{u}{x} & = f \label{eq:forced_viscous_burgers}
-\end{align}
-The domain of we consider here is based on an exact solution of the equation.
-This is done so that the learned solver model can be tested on the exact solution.
-There are a number of sources in literature on the exact solution of the Burgers' equation \autocite{bentonTableSolutionsOnedimensional1972,wazwazPartialDifferentialEquations2010,woodExactSolutionBurgers2006}.
-In this study, we use a specific solution by \textcite{woodExactSolutionBurgers2006} which can be seen in \lccref{eq:burgers_exact_solution}.
-This solution is periodic in space but not in time.
-Therefore, the domain in space will be based on the spatial periodicity of the exact solution which is two.
-As such, the space domain spans from 0 to 2.
-The time domain, on the other hand, is chosen to span from 0 to 10 such that enough details of the solution is included.
-\begin{equation}
-  u(x,t) = \frac{2\nu\pi e^{-\pi^2\nu t}\sin(\pi x)}{a+e^{-\pi^2\nu t}\cos(\pi x)} \label{eq:burgers_exact_solution}
-\end{equation}
-Continuing to the second step, the parameters involved in \lccref{eq:forced_viscous_burgers} are the viscosity \(\nu \) and the forcing term \(f \).
-Since the forcing term is dependent on the solution in this step, the only parameter to determine is the viscosity.
-We choose three constant viscosity values which are 0.1, 0.01, and 0.0.
-These values are chosen so that a variety of behaviors are represented in the dataset from viscous to inviscid flow.
-
-After this, in the third step, the solution functions \(u \) are generated with 8 modes in time and 8 in space and 500 unique function samples for each viscosity value.
-Since we don't factor the viscosity in at this point, for ease of comparison, we ensure the same solutions are generated every time by using a new instance of the generator with the same seed number each time.
-This results in the solutions being the same for all viscosity and other parameters of the equation are adapted to this.
-
-Next we account for the different viscosity values in this stage.
-The forcing term is computed using \lccref{eq:forced_viscous_burgers}.
-The solution field \(u\) and forcing term \(f\) are modeled with Fourier series in \lccrefs{eq:fourier_field,eq:fourier_force} where \(k\) is a vector of spatial and temporal wave number such that \(k_t\) is the temporal wave number and \(k_x\) is the spatial wave number.
-\begin{align}
-  u\left(x, t \right) & = \sum_{k_{x}} \sum_{k_{t}} \hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)} \label{eq:fourier_field} \\
-  f\left(x, t \right) & = \sum_{k_{x}}\sum_{k_{t}} \hat{f}_k e^{2\pi i(k_{x}x+k_{t}t)} \label{eq:fourier_force}
-\end{align}
-Substituting the terms in \lccref{eq:forced_viscous_burgers} with the respective Fourier series, we get the equation \lccref{eq:forced_viscous_burgers_fourier_substitution}.
-A problem one notices is the nonlinear term \(u\pdv{u}{x}\).
-A naive approach would multiply all wave numbers terms with each other.
-\begin{align}
-  u\pdv{u}{x} = \left(\sum_{k_{x}} \sum_{k_{t}} \hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)}\right) \times \left(\sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{x})\hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)}\right)
-\end{align}
-This is computationally expensive operation with \(N^2\) multiplications \autocite{lariosMATH934BURGERS2021,robertsDealiasedConvolutionsPseudospectral2011,shenSpectralMethodsAlgorithms2011,orszagComparisonPseudospectralSpectral1972}.
-To avoid this complexity, the term is first reformulated into \(\pdv{x}(u^2/2)\).
-Then to avoid aliasing, the coefficients are padded with 50\% zeros such that the padded coefficients are 3/2 times the size of the original \autocite{orszagEliminationAliasingFiniteDifference1971, lariosMATH934BURGERS2021}.
-Then we use the padded coefficients to compute the function values in the physical domain using the inverse transform.
-And then, the point wise squaring operation is performed and transform the results back to spectral domain.
-The resulting coefficients are then trimmed back to their original size before padding.
-Finally, we multiply the resulting coefficients \(\hat{uu}_k\) by the derivative constants.
-This operation is much more efficient with only \(1.5 N\) multiplications.
-This is still more efficient than the naive approach even after taking into account the transforms involved adds \(O(2\times 1.5Nln(1.5N))\) operations if using a Fast Fourier Transform algorithm.
-Putting all the above together, results in \lccref{eq:forced_viscous_burgers_fourier_substitution}.
-\begin{equation}
-  \begin{split}
-    \sum_{k_{x}} \sum_{k_{t}} \hat{f}_k e^{2\pi i(k_{x}x+k_{t}t)} =
-     & \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{t}) \hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)}                                                                \\
-     & + \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{x})\hat{uu}_k e^{2\pi i(k_{x}x+k_{t}t)}                                                              \\
-     & - \nu\sum_{k_{x}} \sum_{k_{t}} {(2\pi i k_{x})}^2\hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)} \label{eq:forced_viscous_burgers_fourier_substitution}
-  \end{split}
-\end{equation}
-\begin{align}
-  \sum_{k_{x}} \sum_{k_{t}} \hat{f}_k & = \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{t}) \hat{u}_k + (2\pi i k_{x})\hat{uu}_k - \nu{(2\pi i k_{x})}^2\hat{u}_k \label{eq:forced_viscous_burgers_fourier} \\
-  \hat{f}_k                           & = (2\pi i k_{t}) \hat{u}_k + (2\pi i k_{x})\hat{uu}_k - \nu{(2\pi i k_{x})}^2\hat{u}_k \label{eq:forced_viscous_burgers_coeff}
-\end{align}
-After simplifying the equation, we get the coefficients as in \lccref{eq:forced_viscous_burgers_coeff}.
-Using this equation, the exact forcing term corresponding to the randomly generated solution can be computed with relatively low cost.
-Finally, the function values of both the solutions and forcing terms are perturbed by adding Gaussian noise with a mean of zero and standard deviation of 10\% of the function value standard deviation to the values of the inverse transform.
-The perturbed coefficients are then recomputed from the sum and the final perturbed functions are obtained.
-
-An example of the solution and forcing term pairs that has been generated is shown in \lccref{fig:burgers_data}.
-Using the same seed we can see that the solution functions of the same sample are the same.
-However, with the forcing terms, we see much larger amplitudes for higher frequencies for larger viscosity values.
-This is inline with \lccref{eq:forced_viscous_burgers_coeff}.
-The squared multiplier gets large much more quickly for higher frequencies due to the squaring operation.
-The since this effect is controlled by the viscosity via multiplication, the higher the viscosity, the larger the high frequency amplitudes of the forcing term.
-This, in other words, means that more viscous fluids require a stronger forcing term to affect the solution in the same way with as fluids with a lower viscosity.
-
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_solution_0.0.pgf}
-    \end{adjustbox}
-    \caption{Solution function for \(\nu=0\).}\label{fig:burgers_solution_0.0}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_forcing_0.0.pgf}
-    \end{adjustbox}
-    \caption{Forcing function for \(\nu=0\).}\label{fig:burgers_forcing_0.0}
-  \end{subfigure}
-  % \\[-0.7\baselineskip]
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_solution_0.01.pgf}
-    \end{adjustbox}
-    \caption{Solution function for \(\nu=0.01\).}\label{fig:burgers_solution_0.01}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_forcing_0.01.pgf}
-    \end{adjustbox}
-    \caption{Forcing function for \(\nu=0.01\).}\label{fig:burgers_forcing_0.01}
-  \end{subfigure}
-  % \\[-0.7\baselineskip]
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_solution_0.1.pgf}
-    \end{adjustbox}
-    \caption{Solution function for \(\nu=0.1\).}\label{fig:burgers_solution_0.1}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_forcing_0.1.pgf}
-    \end{adjustbox}
-    \caption{Forcing function for \(\nu=0.1\).}\label{fig:burgers_forcing_0.1}
-  \end{subfigure}
-  \caption{Example sample pairs of solution and forcing terms for the Burgers' equation dataset.}\label{fig:burgers_data}
-\end{figure}
-
-\section{Data Retrieval}\label{sec:data_retrieval}
-\noindent The second data acquisition approach retrieves data of a from an external source.
-This approach downloads the external data to a local machine.
-In this study, the specific dataset that will be used is the ERA5 dataset from the European Center for Medium-range Weather Forecast (ECMWF).
-Specifically, the ERA5 dataset is a reanalysis which means it combines observational data from all over the world in order to present a more complete picture of the weather system.
-This combination process, named 4D variational data assimilation, takes into account the physics known to be involved in the system.
-As an example weather station data which take measurements such as wind speed, humidity, and temperature of the immediate surroundings of the weather station is very limited in giving a broader picture of weather over a larger area.
-Even technologies like earth observations satellites are limited to what they can observe at any single point in time as most cannot see the entirety of the earth's surface at once.
-The ERA5 dataset specifically, assimilates previous forecasts with observational data every 12 hours.
-The ERA5 reanalysis is available at the following URL (\url{https://cds.climate.copernicus.eu/datasets/reanalysis-era5-single-levels}).
-
-The original dataset made available by ECMWF has a grid size of \ang{0.25} by \ang{0.25} in latitude and longitude for atmospheric data.
-Data of oceanic waves are also available at a coarser grid size of \ang{0.5} by \ang{0.5}.
-However, we will use a cloud optimized version called WeatherBench2 that is easier to retrieve \autocite{raspWeatherBench2Benchmark2023}.
-This is because the data is available in several more grid sizes such as \ang{1.5}.
-In addition, the data can be readily downloaded to a local machine without waiting for further processing on the server.
-The guide for working with the dataset is available at (\url{https://weatherbench2.readthedocs.io/en/latest/data-guide.html}).
-In our specific case, we use the version labeled \verb|1959-2023_01_10-6h-64x32_equiangular_conservative.zarr|.
-This dataset spans from year 1959 to 2023 with a grid size of \ang{5.625} or resolution of 64 by 32 which spans from \ang{-87.19} to \ang{87.19} in latitude and \ang{0.0} to \ang{354.4} in longitude.
-The dataset is also resampled down to 6-hour intervals that starts at midnight UTC January 1959 1\textsuperscript{st} and ends at 18:00 UTC January 10\textsuperscript{th} 2023.
-
-While the original data provided by ECMWF is available in NetCDF or GRIB, the WeatherBench2 version is provided using the Zarr format in a Google Cloud Storage Bucket.
-This setup allows the use of libraries that support the Zarr format to access the dataset remotely.
-The particular library we use is called \emph{Xarray} version \verb|2024.9.0| \autocite{hoyer2017xarray,hoyerXarray2024}.
-Accessing the remote dataset is done as shown in \lccref{fig:access_remote_zarr}.
-In order to ensure access is granted, the storage option token is set to anon so that the method uses the anonymous only public access mode of authentication \autocite{GCSFSGCSFs2023122post1+1g8e500c6dirty}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-  import xarray as xr
-  ds = xr.open_zarr(
-      "DATASET_ADDRESS",
-      storage_options = {"token": "anon"},
-  )
-  \end{lstlisting}
-  \caption{Example of using Xarray to access a publicly accessible Zarr dataset hosted on Google Cloud Storage Bucket.}\label{fig:access_remote_zarr}
-\end{figure}
-
-The specific dataset resolution we use is 64 by 32 representing longitude and latitude respectively.
-The ERA5 reanalysis dataset is hosted at the following URL\@: \url{gs://weatherbench2/datasets/era5/1959-2023_01_10-6h-64x32_equiangular_conservative.zarr}.
-The corresponding climatology is hosted at \url{gs://weatherbench2/datasets/era5-hourly-climatology/1990-2019_6h_64x32_equiangular_conservative.zarr}.
-The climatology is the average for hours 0, 6, 12, and 18 for each day of the year from 1990 until 2019.
-This average helps in defining the expected state of the weather at specific points in time based on the historical averages for that time of day and year.
-
-For the reanalysis dataset, we limit the time range to the years 1995{-}2013 for training and 2020{-}2022 for testing.
-The specific time ranges for training are chosen to balance the diversity within the data and capacity of the machine the processing will be done on.
-The testing set time range was chosen to be as close to those shown on the WeatherBench 2 website.
-The filter for time and variables is shown in \lccref{fig:wb2_retrieval}.
-The reason for the different time ranges between training and testing is to reduce the risk of information leakage accross the training and testing sets.
-This ensures that the testing scores we measure will be for the most part from the generalization that model learned during training.
-The filter is an array the length of the number of samples.
-The array values are all the datetime values that the year ranges are true for.
-This results in an array of boolean values.
-Using this boolean filter we can index the data so that we get the filtered data.
-Then, the filtered data is saved locally so that we can access it in a more performant way.
-The encoding chunks may need to be removed in order to evade the Xarray library from mistakenly persisting the remote encoding after slicing data \autocite{ianZarrEncodingAttributes}.
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-  years_idx = ds['time.year']
-  data_idx = (years_idx > START_YEAR) & (years_idx < END_YEAR)
-  da_orig = ds['2m_temperature'][data_idx]
-  # save locally
-  da_orig.encoding.pop('chunks',None)
-  da_orig.to_zarr(DATA_FILENAME, mode='w')
-  # open local version
-  da = xr.open_zarr(DATA_FILENAME)
-  \end{lstlisting}
-  \caption{Example of filtering of Xarray dataset by year and variable. The data is saved and then loaded locally.}\label{fig:wb2_retrieval}
-\end{figure}
-
-The dataset includes 62 variables with some variables also spanning 13 discrete vertical levels in the atmosphere.
-For our use, we will only be using the 2-meter temperature of the atmosphere.
-This is the air temperature 2 meters above the surface be it land, sea, or inland water.
-This variable is in units of kelvin (K).
-Vertically, the values of this variable is obtained by interpolating between the model values at the surface and the lowest model vertical level.
-An example of the data that was retrieved can be seen in \lccref{fig:wb2_data}.
-The data shown is in the equiangular projection.
-This means that towards the poles, the shapes become more distorted.
-While this is not the most ideal way to represent the data, using the data in this way adds to the challenge of how the model can adapt to the use of suboptimal configurations in the data.
-To compute the anomaly, we can simply subtract the current state in \lccref{fig:wb2_train_data} by the climatology in \lccref{fig:wb2_clim_data} resulting in \lccref{fig:wb2_train_anomaly}.
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_train_data.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:wb2_train_data}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_clim_data.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:wb2_clim_data}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_train_anomaly.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:wb2_train_anomaly}
-  \end{subfigure}
-  \caption{Data retrieved:(\subref{fig:wb2_train_data}) 2-meter temperature at January 1, 1995 6:00 UTC\@.
-(\subref{fig:wb2_train_anomaly}) Anomaly for 2-meter temperature at January 1, 1995 6:00 UTC\@.
-(\subref{fig:wb2_clim_data}) 2-meter temperature climatology for the first day of the year at hour 6 UTC\@.}\label{fig:wb2_data}
-\end{figure}
-
-After filtering, our training set has the dimensions of 27760 time steps, 64 longitude, and 32 latitude.
-The testing set on the other hand has 4384 time steps and the same values for the other two dimensions.
-For uses, such as a validation set during hyperparameter optimization, one can use a subset of the training set.
-The dimensions of the climatology are 4 for hour (0, 6, 12,\& 18), 366 for day of year, 64 for longitude, and 32 for latitude.
-
-\section{Design of Computational Model}\label{sec:computational_model_design}
-\noindent In this section, we will discuss the design of the computational model that is proposed in this work. An illustration of the computational model is show in \lccref{fig:computational_model}.
-
-\begin{figure}[H]
-  \centering
-  \begin{adjustbox}{max width=\textwidth}
-    \tikzfig{figures/computational_model}
-  \end{adjustbox}
-  \caption{Computational Model of SpectralSVR.}\label{fig:computational_model}
-\end{figure}
-
-The computational model is divided into four large phases.
-The processes within these phases are based on the broad outcomes of the phase.
-The phases themselves are data preparation, data transformation, model training, and model evaluation.
-Each phase is composed of processes that together works toward the output of the larger process.
-At the end, a final process of analysis and interpretation is carried out.
-
-\subsection{Data Preparation}
-\noindent The data preparation phase starts off the computation by preparing the data that is to be used in this study.
-This phase starts with specifying the problem to be solved.
-This translates to the dataset that will be used to represent these problems.
-The first type of dataset is generated based on a known governing equation or PDE\@.
-Using said equation, the goal is to generate pairs of functions that are related to each other by the equation.
-In the next process, generally, the solution function is first generated randomly.
-This is done by generating random numbers to use as coefficients of a set of basis functions.
-Then parameters of the equation is determined, such as term coefficients.
-Using the generated solution and predetermined parameters, a forcing term can generally be computed to satisfy the equation.
-Augmentations such as noise can then be added in the final process which is evaluating the function values.
-These processes result in a generated dataset.
-To verify the generation method and any models trained on the generated data one can use exact analytical solutions of the governing equations.
-
-The second type of dataset is retrieved from an external source.
-The data source is first identified, in our case it is the WeatherBench 2 collection of datasets.
-The specific dataset from the collection of different dataset versions is first determined.
-The dataset is available in the \emph{Zarr} format.
-And then, we determine the filters for the portions of the dataset we are interested in.
-Once the dataset and filters are determined, the retrieval process starts by accessing the dataset using the \emph{Xarray} library \autocite{hoyer2017xarray,hoyerXarray2024}.
-The filters are applied as in \lccref{fig:wb2_retrieval}.
-Finally, the filtered version is stored locally.
-The local dataset is also stored in the \emph{Zarr} format.
-
-\subsection{Data Transformation}\label{sec:data_transformation}
-\noindent The second phase of the computational model transforms the data that has been prepared into a form that can be used with the proposed model.
-In this study, there are two ways a dataset can be used.
-The first and simplest way is to predict the solution function from the forcing term for a given set of PDE parameters.
-In this case, the input function is the forcing term.
-In other words, the input function is the predictor or independent variable that will be used to predict the solution function.
-As such, the output function is the solution function.
-The antiderivative dataset is used in this way.
-The derivative, which represents the acceleration function, is used to predict the velocity function.
-Which means that the input function is the acceleration function and the output function is the velocity function.
-
-The second use of a dataset depends on whether it can be interpreted as a mapping of a previous function to the next function.
-In other words, a series of functions related to the previous function as a sum of the previous function and a perturbation.
-A commonly used form of this are time series.
-Generally, a time series can be represented as \lccref{eq:time_step_function}.
-This function describes the evolution of function \(f\) as a sum of some initial state \(f^0\) and perturbation which is its rate of change \(\dv{f}{t}\) at a point in time close to the current time multiplied by the time step \(\delta t\).
-This is the first order Taylor polynomial.
-Adding more terms with higher order derivatives can be done to increase the accuracy.
-This describes the same process that is used in the finite difference method.
-\begin{equation}
-  f^{t+1} = f^{t} + \delta t \times \dv{f}{t} + \dots \label{eq:time_step_function}
-\end{equation}
-In this case the previous function and any other independent variables like the forcing term involved in the right-hand side of the equation is used to predict the difference between the future state and the current state.
-It would mean that each sample function in the data would need to at least have two dimensions.
-This is because one dimension represents the evolution of the function over time, while the other dimensions define the spatial domain where the function's values are computed at each time step.
-This condition is true for both the Burgers' equation dataset and the WeatherBench 2 collection of ERA5 datasets.
-First, the Burgers' equation dataset, while is also able to be used in the first way as a mapping between the forcing term and the solution, one of the traditional ways of solving it is using the method of lines.
-This entails solving the dimensions other that time with methods such as the finite differences method or the spectral method.
-The time dimension is then separately solved using the finite differences method such as the form shown in \lccref{eq:time_step_function} \autocite{schiesserNumericalMethodLines2012,sadikuSimpleIntroductionMethod2000}.
-This is the form that the Burgers' equation dataset will be used in.
-In this case, algebraic manipulation of \lccref{eq:forced_viscous_burgers} results in the time derivative of the solution as in \lccref{eq:forced_viscous_burgers_time_derivative}.
-\begin{align}
-  \pdv{u}{t} = f - u\pdv{u}{x} + \nu\pdv[2]{u}{x} \label{eq:forced_viscous_burgers_time_derivative}
-\end{align}
-The most important component of the right-hand side of the equation, the time derivative, is expressed in terms of the solution function, the forcing term and any other partial derivatives.
-Because of this, it means we can train the model to learn the relationship between the solution function combined with the forcing term and the time derivative.
-Putting this together with \lccref{eq:time_step_function}, it is possible to predict the solution function in a future time based on the current solution function and forcing term.
-The input functions in this case are both the value of the solution function and the forcing term at the current time step.
-The output function is the time derivative which is computed by rearranging \lccref{eq:time_step_function} resulting in \lccref{eq:time_derivative_time_step_function}.
-\begin{equation}
-  \dv{f}{t} = \frac{f^{t+1} - f^{t}}{\delta t} \label{eq:time_derivative_time_step_function}
-\end{equation}
-Perhaps in a more obvious manner, the same is also applied to the WeatherBench 2 collection of ERA5 datasets.
-The 2-meter temperature is a series of snapshots in time of the distribution of temperature all over the world at 2 meters above the surface.
-The input function in this case is the temperature distribution at the current time step.
-The output function is the time derivative of the temperature distribution computed using \lccref{eq:time_derivative_time_step_function}.
-
-The input and output functions are then transformed into basis coefficients using the Fourier transform. % TODO: add reference to fourier transform in chapter 2
-Once the coefficients are computed, the input and output sample pairs are split into train, test, and validation subsets.
-For the first type of input and output function pair, since the samples are independent of each other, a random sampling of the dataset without replacement is done to select the samples for each subset.
-For the second type of input and output function pairs, if there are multiple samples of functions as in the Burgers' equation dataset, the same process with random sampling is followed.
-On the other hand, if only one function sample is available, such as the WeatherBench 2 dataset, an issue that arises is the fact that the samples are dependent on one another.
-This is because a previous time step influences the next time step.
-This is a problem for generalizing the learned model, since random sampling would lead to the model learning information in the future of the testing subset \autocite{kapoorLeakageReproducibilityCrisis2023,kaufmanLeakageDataMining2012}.
-As such, the portioning of the dataset is done by dividing the sample into different sections of the function in time.
-
-Finally, the data is scaled.
-This is done because of how support vector machines require scaling for inputs in order to perform well with certain hyperparameters such as the RBF kernel \autocite{ben-hurUsersGuideSupport2010}.
-For our case we use standard scaling based on the inputs of the training subset.
-This approach transforms the dataset by manipulating the distribution characteristics of the dataset \autocite{ahsanEffectDataScaling2021}.
-Specifically, the standard deviation \(\sigma \) and mean \(x_0\) of the dataset values \(x\) are processed such that the resulting values have a mean of 0 and standard deviation of 1.
-The function shown in \lccref{eq:standard_scaler} represents how each sample is processed with respect to the standard deviation \(\sigma \) and mean \(x_0\) of each feature.
-\begin{equation}
-  z(x;\sigma,x_0)=\frac{x-x_0}{\sigma} \label{eq:standard_scaler}
-\end{equation}
-The scaling is important for the RBF kernel specifically due to the fact that the kernel utilize a scale parameter.
-This parameter affects how scale of values influence the kernel.
-Another and perhaps more general benefit of scaling is the uniformity it enforces across features.
-This is useful because all feature weigh the outcome equally.
-In our use case, this equality is a reflection of what the data actually represents.
-Each feature which is a discretized value or its coefficient representation has equal value to any other feature.
-No point or coefficient is any more or less value compared to another point or coefficient.
-
-The scaling is applied to input functions only because scaling of the outputs does not affect the performance of the model \autocite{ben-hurUsersGuideSupport2010}.
-To also prevent information leakage across training and testing sets, the mean and standard deviation of each feature is computed using the training subset only.
-Once the parameter values are obtained, all input function samples in the dataset are transformed into their scaled versions.
-This means that the distribution for the testing and validation sets may be outside the target standard deviation and mean.
-% TODO: add graphs and tables of the resulting preprocessed data
-
-\subsection{Model Training}
-\noindent Once the data has been preprocessed, the model is trained using pairs of training features and labels.
-The training phase is separated into four processes.
-First, the preprocessed input and output function representation need to be real numbers.
-This is because the LSSVR model was made to work with real numbers.
-Any complex values such as Fourier coefficients are represented as flattened pairs of the real and imaginary components of complex values.
-% TODO: add figure of flattened complex values
-
-The training can proceed to solve \lccref{eq:lssvr_solution}.
-As the original LSSVR equation was made for regression of a single value of \(\vb{y} \), we constructed an extended the original equation in order to train multiple regression models to predict each coefficient in an output function sample.
-The assumption of this extension is that the inputs and model hyperparameters such as kernels and the regularization constant \(C \) are the same across individual regressors.
-Therefore, it follows that the solution vector and target vector can both be transformed into their matrix form with each column representing the individual regressor which results in \lccref{eq:lssvr_solution_vectorized}.
-This vectorized version is equal to \(m \) separate instances of \lccref{eq:lssvr_solution}.
-In essence, instead of a vector of scalar sample output values and a vector of model parameters, the extended equation consists of a matrix of rows of vector output values and a matrix of model parameters with each column representing the separate model for each output and row representing the Lagrange multipliers for each sample.
-The procedure to solve \lccref{eq:lssvr_solution_vectorized} adjusts \lccref{alg:lssvr_training} for the extra dimension spanning the multiple outputs of size \(m\).
-\begin{equation} \label{eq:lssvr_solution_vectorized}
-  \begin{bmatrix}
-    0          & \vb{1}_{n}^{\intercal} \\
-    \vb{1}_{n} & \Omega + \frac{I}{C}
-  \end{bmatrix}
-  \begin{bmatrix}
-    b_0           & \cdots & b_m           \\
-    \vb{\alpha}_0 & \cdots & \vb{\alpha}_m \\
-  \end{bmatrix}
-  =
-  \begin{bmatrix}
-    0        & \cdots & 0        \\
-    \vb{y}_0 & \cdots & \vb{y}_m \\
-  \end{bmatrix}
-\end{equation}
-
-Second, as the training process of an LSSVR described in requires constructing the first matrix on the left-hand side and the matrix on the right-hand side, each component of the matrices themselves will also need to be constructed.
-The kernel matrix \(\Omega \) is first constructed by computing the kernel values between each sample input with every other sample input.
-If the training set has \(n \) samples, then the resulting kernel matrix would be of size \(n \) by \(n \).
-% Assemble lssvr optimality equation matrices
-Third, using the inputs \(\vb{X}\), outputs \(\vb{y}\), predetermined regularization constant \(C \), and the obtained kernel matrix \(\Omega \), \lccref{eq:lssvr_solution_vectorized} is assembled.
-Finally, the matrix of learned parameters \(\vb{\alpha}\) and \(\vb{b}\), which are the Lagrange multipliers and bias respectively, are solved for using a linear equation solver such as a matrix Moore-Penrose inverse or linear least squares solver.
-
-For our study, we choose to not optimize the hyperparameters to focus on the broad performance with default hyperparameter values.
-The scaling parameter of the RBF kernel is computed from the training features.
-This is computed as the square root of the sum of feature variances.
-The regularization parameter used will be a default value of 1.
-Using the same values allow for easier comparisons for comparable results.
-
-\subsection{Model Evaluation}
-\noindent The fourth phase of the computational model is the evaluation of the learned model.
-This phase starts with formatting the inputs.
-If the inputs aren't scaled yet, then it is scaled using the scaling function fitted on the training set.
-This is the case for new data such as new measurements or an analytical solution of the learned PDE\@.
-Once the inputs that is to be evaluated is scaled in the same way as the training inputs, the model can predict the corresponding outputs.
-
-The procedure to compute the predicted outputs follows \lccref{alg:lssvr_prediction}.
-This leads to the second process which is computing the kernel matrix between the training input features \(\vb{X}\) and the evaluation input features \(\vb{U}\).
-The matrix is constructed as the kernel value between each evaluation sample feature and every training sample feature.
-For \(p \) evaluation samples and \(n \) training samples, this results in a kernel matrix \(\Omega \) with a shape of \(p \) rows and \(n \) columns.
-
-In the third process, the constructed kernel matrix is then multiplied with the matrix of learned Lagrange multipliers \(\vb{\alpha}\).
-The multiplication is the matrix multiplication process.
-Then, the bias vector is added to each row to produce the final predicted outputs \(\vb{v}\).
-This process is represented by \lccref{eq:lssvr_prediction_vectorized}.
-\begin{equation}
-  \vb{v} = \Omega\vb{\alpha}+\vb{1}\vb{b} \label{eq:lssvr_prediction_vectorized}
-\end{equation}
-
-The fourth process is concerned with the fact that the predicted output \(\vb{v}\) is a matrix of real numbers.
-The LSSVR output needs to be formatted before it can be used in the proposed model.
-This is done by converting the outputs into the same format as the training labels.
-As we use the Fourier basis, the model output is converted back into a matrix of complex numbers using the inverse of the first process during training.
-Finally, these predicted Fourier basis coefficients can be used to evaluate the predicted functions themselves.
-
-\section{Implementation of Computational Model}
-\noindent This section discusses the implementation of modeling and approximation of PDEs using LSSVR\@.
-Using the computational model design in \lccref{sec:computational_model_design}, the computational model is implemented as a library using the Python programming language.
-The development process itself is based on the iterative development model as mentioned in \lccref{sec:development method}.
-In this section, the output iterative processes are consolidated and explained together.
-
-\subsection{Analysis}
-\noindent The aim of any program that is developed in this study is to model the relationship between functions defined by a partial differential equation or other operators and governing equations.
-Since the potential subject of modeling can be wide-ranging, the software product that will be developed is a library.
-This is done so that the tools and proposed model that is developed will be able to be used with a variety of PDEs.
-With this in mind, the software must also be performant and compatible with the larger machine learning and scientific computing community.
-
-To demonstrate the use and capability of the software, three case studies are chosen to represent the variety of PDEs.
-The first case study is the antiderivative equation.
-This simple case is chosen as a proof of concept to show that the proposed model works in the most simple case.
-The second case study, which is the Burgers' equation, adds a level of complexity because of the nonlinearity involved with the solution function.
-The third case study, which is the ERA5 weather dataset, was chosen to show how the model performs on data with real world observations incorporated into it.
-This dataset also presents a challenge because of the uncertainties involved with weather simulation \autocite{herreraReviewCurrentFuture2017}.
-These datasets are discussed in \lccrefs{sec:data_generation,sec:data_retrieval}.
-
-In addition, the software product is developed within certain limitations. The limitations are:
-\begin{enumerate}
-  \item The operating and implementation language of the library is Python.
-  \item The library is to be used in user code
-  \item The library depends on other libraries including the following core dependencies PyTorch, NumPy, Xarray, Zarr, Pandas, and tqdm.
-\end{enumerate}
-
-\subsection{Design}\label{sec:implementation_design}
-\noindent In this subsection, the architectural design of the software product is explained.
-The architecture consists of modules with similar concerns.
-This was chosen because of the intuition built by the use of other libraries with a similar architecture.
-The broad aim of modeling PDEs with LSSVR and basis functions coefficients can be separated into smaller concerns of data, model, and basis functions.
-Each of these concerns are addressed by a corresponding module.
-The explanation of each module are as follows:
-\begin{enumerate}
-  \item Utilities
-
-        \noindent This module provides basic tools that are used across the entire library.
-The utilities this module needs to provide include scaling, conversion between real and complex representations of matrices, resizing coefficient tensors, and adaptors for or the traditional ordinary differential equation solvers.
-Scaling functionality is used for inputs into the support vector machines.
-And as previously mentioned, since LSSVR only works with real numbers, the tools for converting between complex and their real number representations is also necessary.
-Another useful tool for working with basis coefficients is a way to resize the coefficients in terms of how many basis functions is desired.
-An example of the usage is downsizing Fourier coefficients from 12 to 8 modes.
-The last utility mentioned here provides the ability to solve ordinary differential equations.
-This utility is useful for generating data for certain types of PDEs such as the Burgers' equation.
-
-  \item Basis Functions
-
-        \noindent As the proposed model will learn the relationships defined by PDEs within the spectral domain, a large proportion of the computation will also concern the use of the basis functions themselves.
-The module will define the functionality and data structure that is expected to be used when working with basis functions in this library.
-First and foremost, the central function of this module is to store and facilitate the connection between the coefficients in the spectral domain and their values in the physical domain.
-This is dependent on the basis functions used.
-For the Fourier basis that we use in this study, this means that the transformations are the discrete Fourier transform and the discrete inverse Fourier transform.
-Other than this core functionality, information on the characteristics of the coefficients such as the number of modes, in other words basis functions, should also be provided by this module.
-In addition, other functionality included in this module are visualization of coefficients in physical space, generation of random functions, time dependent \& complex/real coefficients, noise perturbation of functions, and differential operators.
-
-  \item Model
-
-        \noindent The proposed SpectralSVR model is implemented in this module.
-As the proposed model essentially wraps a support vector regression model in such a way that it can process coefficients, this module will house the SpectralSVR wrapper itself and the LSSVR variant of support vector regression that is used in this study.
-The SpectralSVR wrapper must provide three core pieces of functionality.
-First, it must translate complex input and output samples into their real representations.
-This applies to both training and evaluation.
-Second, in addition to predicting the coefficients during evaluation, the wrapper should also be able to predict the function values themselves for any given set of point coordinates.
-This is important for quick evaluations of a predicted function at an arbitrary point.
-The third functionality is inverse input function search for a given output.
-This is useful for inverse problems where the parameters are unknown, but the solution is partially known.
-Aside from the core functionality, a complementary functionality is testing for the learned model.
-
-        The model module also implements the LSSVR model.
-This implementation provides two main functionalities.
-The first is training the LSSVR model with some given model hyperparameters such as the regularization constant and kernel.
-The second functionality is the evaluation of the learned model.
-Both functionalities allow for multiple output regression.
-This is required to learn the mappings for many coefficients at once.
-Other functionality provided by the implementation include interpretability functions and model serialization for saving and loading the learned model to disk.
-
-  \item Problems
-
-        \noindent This module provides the functionality concerned with generating data.
-Two out of the three datasets in this study are generated with this module.
-In general this module provides two pieces of functionality.
-The first is generation of the data itself.
-This functionality generates at least two sets of functions that are related to each other by the chosen PDE\@.
-The generation is based on at least two parameters which are the number of samples to generate and the number of modes or basis functions to generate the coefficients for.
-The second functionality provided by this module is the residual based on the chosen PDE\@.
-This is useful to verify if any set of functions comply with the PDE\@.
-For example, the residual may be used to verify the generated data.
-Another use is to grade the predictions by the learned model.
-
-\end{enumerate}
-
-The design presented here is the product of multiple iterations that started with building the core model and then the basis functions and finally the data.
-Throughout the iterations, the utilities were also added to alleviate the need for general tools.
-
-\subsection{Implementation}
-
-\noindent The design in \lccref{sec:implementation_design} is implemented within the same iterative loop.
-As such, the feedback from tests is immediate, and any fixes can be implemented quickly.
-The implementation is done using the Python language and a number of Python libraries.
-To facilitate the management of dependencies, the implementation makes use of the package management tool Poetry \autocite{eustacePoetryPythonPackaging2024}.
-In addition, the Python version is managed using the tool PyEnv.
-The implementation process starts with installation of the required dependencies.
-The dependencies are specified in the \verb|pyproject.toml| as shown in \lccref{fig:poetry_add_deps}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Toml]
-...
-[tool.poetry.dependencies]
-python = "^3.10.6"
-numpy = "^1.24.0"
-tqdm = "^4.65.0"
-jaxtyping = "^0.2.20"
-pandas = "^2.2.2"
-torchmetrics = "^1.4.2"
-scikit-learn = "^1.5.0"
-matplotlib = "^3.9.0"
-torch = {version = "^2.4.1+cu124", source = "pytorch-gpu"}
-torchvision = {version = "^0.19.1+cu124", source = "pytorch-gpu"}
-torchaudio = {version = "^2.4.1+cu124", source = "pytorch-gpu"}
-ray = {extras = ["tune"], version = "^2.37.0"}
-hyperopt = "^0.2.7"
-ipywidgets = "^8.1.5"
-torchdiffeq = "^0.2.4"
-xarray = "^2024.10.0"
-zarr = "^2.18.3"
-gcsfs = "^2024.10.0"
-
-[[tool.poetry.source]]
-name = "pytorch-gpu"
-url = "https://download.pytorch.org/whl/cu124"
-priority = "explicit"
-
-[build-system]
-requires = ["poetry-core"]
-build-backend = "poetry.core.masonry.api"
-  \end{lstlisting}
-  \caption{Contents of pyproject.toml configuration file that define the dependencies using Poetry.}\label{fig:poetry_add_deps}
-\end{figure}
-
-After ensuring that the correct version of python is being used with pyenv, the dependencies specified in the \verb|pyproject.toml| file can be installed using the shell command \verb|poetry install|.
-At the end of each iteration, the dependencies are subject to change depending on whether any new ones are needed or old dependencies can be removed.
-
-In the following, we will discuss the implementation of each module and how the phases of computational model relates to each implemented functionality.
-The base data structure that is used in the implementation is the PyTorch Tensor \autocite{Ansel_PyTorch_2_Faster_2024}.
-Tensors are a generalization of scalars and array-like structures such as vectors and matrices.
-This is essential since many computations that is done in the proposed model are based on matrices and higher dimensional arrays.
-PyTorch Tensors allow the elements to be of different data types such as floating point numbers of different precision or even complex numbers.
-In addition to basic operations for working with the Tensors such as matrix multiplications, PyTorch also provides many algorithms for use when working with Tensors such as linear equation solvers or the Fast Fourier Transform.
-Another reason for choosing to use PyTorch is the ability to parallelize computation using specialized processors such as GPUs.
-Lastly, PyTorch is widely used in the machine learning community which reflects on its reliability, wealth of community knowledge and support, and active development.
-
-\subsubsection{Utilities}
-
-\noindent The utilities module provide common tools that are used when working with the developed software.
-First, because the basis function used in this study is the Fourier basis, a large proportion of concern is the storage of Fourier basis coefficients.
-The Fourier series representation that is used in this study is the complex representation as show in \lccref{eq:fourier_series}.
-However, as previously mentioned, least squares support vector machines is constructed to work with real numbers.
-In order for LSSVR to learn the relationship between complex numbers, a representation of complex numbers in terms of real numbers is necessary.
-Since sample features and labels for LSSVR need to be flattened into one dimension which result in a matrix with rows of samples, the representation of complex numbers using real numbers can be done after features and labels have been flattened.
-An example of such a matrix of two samples with four features each can be seen in \lccref{eq:complex_matrix}.
-To represent the complex number features as real numbers, once can simply split a single complex number into two real numbers.
-When this is done to the entire matrix of complex numbers, the result is \lccref{eq:complex_matrix_real_rep}.
-\begin{align}
-  \begin{bmatrix}
-    -1.03+0i & -0.52+0.39i & -0.54+0i & -0.52-0.39i \\
-    -0.85+0i & -0.39+0.19i & 0.87+0i  & -0.39-0.19i
-  \end{bmatrix}\label{eq:complex_matrix} \\
-  \begin{bmatrix}
-    -1.03 & 0 & -0.52 & 0.39 & -0.54 & 0 & -0.52 & -0.39 \\
-    -0.85 & 0 & -0.39 & 0.19 & 0.87  & 0 & -0.39 & -0.19
-  \end{bmatrix}\label{eq:complex_matrix_real_rep}
-\end{align}
-There are several ways to do this in PyTorch, such as extracting the real and imaginary element components into separate matrices and then interleaving the columns to create the real representation.
-However, a more performant version can be made by using built-in functions of the library that directly allows views of complex valued tensors as real tensors and vice versa.
-The \verb|view_as_real| and \verb|view_as_complex| functions allow the conversion between real and complex representations by representing complex valued tensors by adding a dimension of size two for each component of complex numbers.
-The resulting implementation can be seen in \lccref{fig:complex_matrix_conversion_implementation}.
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-def to_real_coeff(x: torch.Tensor) -> torch.Tensor:
-    return torch.view_as_real(x).flatten(-2)
-
-def to_complex_coeff(x: torch.Tensor) -> torch.Tensor:
-  return torch.view_as_complex(
-    x.reshape((*x.shape[:-1], -1, 2))
-  )
-  \end{lstlisting}
-  \caption{Utility function to convert between complex matrices and the real representations.}\label{fig:complex_matrix_conversion_implementation}
-\end{figure}
-
-Another important utility used on inputs for the proposed SpectralSVR is a scaling function.
-This utility has been implemented in a variety of ways and using different tools.
-However, as the standard scaling is not provided by PyTorch, we have also implemented our own version.
-The scaling function accepts PyTorch tensors or tuples of tensors of real or complex elements.
-First, the scaling function is implemented as a class that is instantiated.
-The scaling function is then fitted onto the reference data to obtain the standard deviation and mean of each feature.
-This information is stored as properties of the class.
-Any complex tensors are converted into their real representations using the functions in \lccref{fig:complex_matrix_conversion_implementation}.
-Once the scaling function instance is fitted, any set of tensors with the same number of features (columns) and element type (complex or real) can be roughly transformed into a standard deviation of one and mean of zero for every feature.
-This is done by subtracting the fitted mean of each feature from the elements in the column and then dividing with the feature's standard deviation.
-The implementation also provides a method to retrieve a scaling function fitted on a subset of the original tuple of tensors.
-Serialization for saving to and loading from disk is also implemented.
-This is done simply by using the PyTorch save and load functions on the scaling function instance itself.
-For some use cases, an inverse scaling operation to the original standard deviation and mean is also essential.
-The implementation is simply the reverse of the transformation process where the elements are multiplied by the standard deviation and the mean is the added.
-
-Another group of utility in the module is concerned with managing the number of modes a tensor of coefficients has.
-First, a function called \verb|resize_modes| accepts a tensor of coefficients and the target number of modes in each dimension.
-The first dimension is always assumed to represent the different samples.
-Because of this the target modes will only affect the dimensions after the first.
-The wave numbers are also assumed to be symmetric about zero such that the highest absolute values of the wave number is in the middle of each dimension.
-The wave number decreases symmetrically as you move towards the edges of the dimension and reaching the lowest absolute wave number at the edges.
-This is done to ensure compatibility with the way existing libraries such as PyTorch works with tensors of Fourier coefficients.
-Because of this, shrinking a tensor of coefficients along a dimension means removing the center of the tensor along that dimension.
-And expanding to a target number of modes that is larger means that the tensor is padded with zeros in the center along the desired dimension.
-In addition, the remaining coefficients may be rescaled in order to balance the effect of adding or removing coefficients.
-The implementation is presented in \lccrefs{fig:coefficient_shrink_impl,fig:coefficient_expand_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-for dim, (target_mode, current_mode) in enumerate(
-    zip(target_modes, current_modes), 1
-):
-    device = x.device
-    start_range = torch.tensor(
-        range((target_mode - 1) // 2 + 1), dtype=torch.int
-    ).to(device=device)
-    end_range = torch.tensor(
-        range(current_mode - target_mode // 2,
-          current_mode
-        ),
-        dtype=torch.int,
-    ).to(device=device)
-
-    x_resized = torch.concat(
-        (
-            x_resized.index_select(dim, start_range),
-            x_resized.index_select(dim, end_range),
-        ),
-        dim,
-    )
-  \end{lstlisting}
-  \caption{Example of shrinking a tensor of samples' coefficients to a target number of modes.}\label{fig:coefficient_shrink_impl}
-\end{figure}
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-for dim, (target_mode, current_mode) in enumerate(
-    zip(target_modes, current_modes), 1
-):
-    device = x.device
-    start_range = torch.tensor(
-        range((current_mode - 1) // 2 + 1), dtype=torch.int
-    ).to(device=device)
-    # make sure that end range is empty if
-    # the coefficient is only size 1
-    end_range = torch.tensor(
-        range(current_mode // 2, current_mode)
-        if current_mode > 1
-        else range(0),
-        dtype=torch.int,
-    ).to(device=device)
-    padding_size = target_mode - current_mode
-    modes = list(x_resized.shape)
-    modes[dim] = padding_size
-    padding = torch.zeros(modes).to(x_resized)
-
-    x_resized = torch.concat(
-        (
-            x_resized.index_select(dim, start_range),
-            padding,
-            x_resized.index_select(dim, end_range),
-        ),
-        dim,
-    )
-  \end{lstlisting}
-  \caption{Example of expanding a tensor of samples' coefficients to a target number of modes.}\label{fig:coefficient_expand_impl}
-\end{figure}
-Next, the second way to manage the size of a tensor along a dimension is to interpolate the current values.
-The implementation uses simple linear interpolation.
-This is especially useful for situations such as coefficients that are themselves functions of time.
-This is a common application such as when solving the initial condition problem of a function in space and time.
-One might represent the function as a Fourier series with basis as functions of space and coefficients as functions of time.
-In this case, the coefficients for time values that are not available can be interpolated.
-The implementation of this is shown in \lccref{fig:coefficient_interpolation_impl}.
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-    index_floor = index_float.floor().to(torch.int)
-    index_ceil = index_float.ceil().to(torch.int)
-    x_ceil = x.index_select(dim, index_ceil)
-    x_floor = x.index_select(dim, index_floor)
-    # interpolate coefficients
-    index_shape = [1 for _ in range(x_floor.ndim)]
-    index_shape[1] = -1
-    index_scaler = (
-        ((index_float - index_floor) / (
-          index_ceil - index_floor
-        ))
-        .reshape(index_shape)
-        .nan_to_num()
-    )
-    # ynt + scaler * (ynt1 - ynt)
-    # (1 - scaler) * ynt + scaler * ynt1
-    x_interp = torch.lerp(x_floor, x_ceil, index_scaler.to(x))
-  \end{lstlisting}
-  \caption{Example of interpolating for indices (floating point indices) between the available ones (integer indices).}\label{fig:coefficient_interpolation_impl}
-\end{figure}
-
-Finally, this module also provides the types and reexports implementations of ordinary differential equation solvers from the torchdiffeq library \autocite{Chen_torchdiffeq_2021}.
-The implementation can be seen in \lccref{fig:solver_impl}.
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-RHSFuncType = Callable[[torch.Tensor, torch.Tensor],
-  torch.Tensor
-]
-SolverSignatureType = Callable[[
-        RHSFuncType, torch.Tensor, torch.Tensor,
-    ],
-    torch.Tensor
-]
-MixedRHSFuncType = Callable[[
-        torch.Tensor, torch.Tensor, torch.Tensor,
-    ],
-    torch.Tensor,
-]
-MixedSolverSignatureType = Callable[
-    [MixedRHSFuncType, torch.Tensor, torch.Tensor],
-    torch.Tensor,
-]
-
-def euler_solver(
-    rhs_func: RHSFuncType,
-    y0: torch.Tensor,
-    t: torch.Tensor,
-):
-    solution = torch.zeros((len(t), *y0.shape)).to(y0)
-
-    j = 1
-    solution[j - 1] = y0
-    for t0, t1 in zip(t[:-1], t[1:]):
-        dt = t1 - t0
-        y = solution[j - 1]
-        solution[j] = y + dt * rhs_func(t0, y)
-        assert (
-            solution.isnan().sum() == 0
-        ), f"solver encountered nan at timestep {j} (t={t0})"
-        j = j + 1
-    return solution
-
-implicit_adams_solver: SolverSignatureType = partial(
-    odeint, method="implicit_adams", options={"max_iters": 4}
-)  # type: ignore
-
-lsoda_solver: SolverSignatureType = partial(
-    odeint, method="scipy_solver", options={"solver": "LSODA"}
-)  # type: ignore
-  \end{lstlisting}
-  \caption{Implementation of ODE solvers and the types.}\label{fig:solver_impl}
-\end{figure}
-
-\subsubsection{Basis Functions}
-
-\noindent This module implements two classes.
-The first is the base Basis class.
-The second is a subclass implementing the Fourier basis specifically.
-These classes provide the functionality needed to have an easier time when working with basis functions and their coefficients.
-First, the core function of these classes is to provide a way to transition between the spectral domain and the physical domain.
-This is implemented in the base class by storing the coefficients of sample functions as a class property.
-The coefficients are assumed to be at least of one function.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    @staticmethod
-    def transform(
-        f: torch.Tensor,
-        res: TransformResType | None = None,
-        periodic: bool = True,
-        periods: PeriodsInputType = None,
-        allow_fft: bool = True,
-    ) -> torch.Tensor:
-        if not torch.is_complex(f):
-            f = f * (1 + 0j)
-        res = transformResType_to_tuple(res, tuple(f.shape[1:]))
-        periods = periodsInputType_to_tuple(periods, f.shape[1:])
-        # perform 1d transform over every dimension
-        F = f
-        for cdim in range(1, ndims):
-            F = FourierBasis._ndim_transform(
-                F,
-                dim=cdim,
-                func="forward",
-                res=res[cdim - 1],
-                periodic=periodic,
-                period=periods[cdim - 1],
-                allow_fft=allow_fft,
-            )
-
-        return F
-...
-  \end{lstlisting}
-  \caption{Implementation of forward Fourier transform.}\label{fig:fourier_transform_impl}
-\end{figure}
-
-The transitions between the coefficients and functions values are implemented as a function to transform function values to coefficients and an inverse transform function to compute function values from coefficients.
-The base class enforces this by defining abstract methods which any subclass will need to implement.
-The FourierBasis subclass then implements the transform and inverse transform functions specific for transitioning between function values and Fourier basis coefficients.
-As before, the implementation assumes that the first dimension indexes the samples and the rest represent the coefficient wave numbers.
-This means that the implementation must allow for multidimensional functions.
-For the Fourier transform and inverse transform, the multidimensional version is relatively simple to implement.
-The multidimensional Fourier transform essentially performs the one dimensional Fourier transform along one dimension.
-And then, using the result to perform the one dimensional Fourier transform along the next dimension.
-This process is repeated until the last dimension.
-The implementation of the forward transform is presented in \lccref{fig:fourier_transform_impl}.
-The inverse transform simply changes the \verb|func| parameter to \enquote{inverse}.
-
-The Fourier transform along each dimension is done by flattening every other dimension into the sample dimension.
-This essentially means that the function values are \enquote{sliced} along the dimension currently being transformed, and that each \enquote{slice} is its own \enquote{sample}.
-Mathematically, this is simply due to the matrix multiplication of basis functions along one dimension with every other dimension.
-The implementation of this is shown in \lccref{fig:ndim_fourier_transform_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    @staticmethod
-    def _ndim_transform(
-        f: torch.Tensor,
-        dim: int,
-        func: Literal["forward", "inverse"],
-        res: slice,
-        periodic: bool,
-        period: float,
-        allow_fft: bool,
-    ) -> torch.Tensor:
-        # flatten so that each extra dimension is
-        # treated as a separate "sample"
-        # move dimension to transform to the end
-        # so that it can stay intact after f is flatened
-        f_transposed = f.moveaxis(dim, -1)
-        # flatten so that the last dimension is intact
-        f_flatened = f_transposed.flatten(0, -2)
-
-        F_flattened = FourierBasis._raw_transform(
-            f_flatened,
-            func=func,
-            res=res,
-            periodic=periodic,
-            period=period,
-            allow_fft=allow_fft,
-        )
-        # unflatten so that the correct shape is returned
-        F_transposed = F_flattened.reshape(
-          (*f_transposed.shape[:-1], res.step)
-        )
-        F = F_transposed.moveaxis(-1, dim)
-
-        return F
-...
-  \end{lstlisting}
-  \caption{Implementation of n-dimensional Fourier transform for a specific dimension.}\label{fig:ndim_fourier_transform_impl}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    @staticmethod
-    def _raw_transform(
-        f: torch.Tensor,
-        func: Literal["forward", "inverse"],
-        res: slice,
-        periodic: bool,
-        period: float,
-        allow_fft: bool,
-    ) -> torch.Tensor:
-        match func:
-            case "forward":
-                sign = -1
-            case "inverse":
-                sign = 1
-        mode = f.shape[1]
-        domain_starts_at_0 = res.start == 0
-        domain_end_equal_to_period = res.stop == period
-        can_use_fft = (
-            domain_starts_at_0
-            and domain_end_equal_to_period
-            and periodic
-            and allow_fft
-        )
-        if can_use_fft:
-            if func == "forward":
-                F = torch.fft.fft(
-                  f, dim=1, n=res.step, norm="backward"
-                )
-            elif func == "inverse":
-                F = torch.fft.ifft(
-                  f, dim=1, n=res.step, norm="forward"
-                )
-        else:
-            if periodic:
-                n = res.start + torch.arange(res.step).to(f)
-                n = n / res.step * period
-            else:
-                n = torch.linspace(
-                    res.start, res.stop, res.step
-                ).to(f)
-            e = FourierBasis.fn(
-                n.view(-1, 1),
-                mode,
-                periods=period,
-                constant=sign * 2j * torch.pi,
-            )
-
-            F = torch.mm(f, e.T)
-        return F
-...
-  \end{lstlisting}
-  \caption{Implementation of the one dimensional Fourier Transform.}\label{fig:1d_fourier_transform_impl}
-\end{figure}
-
-The one dimensional Fourier transform itself is implemented as a raw transform function.
-This function accepts input of a matrix of values to transform, a parameter to indicate the type of transformation (inverse transform or forward transform), the evaluation boundary and number of grid points, whether the evaluation should assume the function is periodic, the size of the function domain, and if the Fast Fourier Transform is allowed to be used.
-The evaluation boundaries, actual function domain size, whether the function can be assumed to be periodic, and if FFTs is allowed to be used together determine the Discrete Fourier Transform algorithm that is used.
-The FFT algorithm is used if the following are all true: the evaluation starts at zero and ends with the same value as the period, the function can be assumed to be periodic, and FFT is allowed.
-Otherwise, the transform is computed naively using \lccrefs{eq:discrete_fourier_transform,eq:inverse_discrete_fourier_transform}.
-The naive approach allows for evaluating function values of coefficients at various grid sizes and evaluation boundaries.
-This is useful for being able to evaluate at resolutions other than that of the original discretized function or coefficients.
-One use for this is plotting the function at different parts or resolutions.
-The relationship with the physical domain means that the boundaries of the domain is important.
-This is because the function values that will be used may only be valid within certain boundaries.
-Because of this, the information of physical domain bounds must also be stored.
-This is done by storing the span of the function in each dimension.
-The implementation we have gone with doesn't store any other information than the span in each dimension.
-Because of this, the information would need to be stored outside the Basis class instance and any outputs or operations with the classes will need to take this into account.
-The implementation of the one dimensional Fourier transform is presented in \lccref{fig:1d_fourier_transform_impl}.
-
-The secondary set of functionality provided by the basis classes are mathematical operators on the functions the coefficients represent.
-There are four operators implemented, which are the addition, subtraction, derivative, and antiderivative operators.
-These four operations can be further categorized into arithmetic and calculus operations.
-The arithmetic operations, which are addition and subtraction, are implemented by following how the actual mathematical operations would be carried out on two functions which are Fourier series as shown in \lccref{eq:fourier_series_addition}.
-For subtraction, the plus sign is simply replaced with the minus sign.
-\begin{align}
-  \sum_{k} \hat{u}_k e^{2\pi ikx} + \sum_{k} \hat{f}_k e^{2\pi ikx} =
-  \sum_{k} \left(\hat{u}_k + \hat{f}_k\right) e^{2\pi ikx} \label{eq:fourier_series_addition}
-\end{align}
-The implementation leverages the operator overloading in Python classes.
-In addition, the overload should be done to the \verb|__add__| function.
-This function adds the current instance to another object which is the other basis instance for our use case.
-We also want the operation to return an independent instance without any references to the previous instances.
-To do this, all properties are copied into a new instance.
-This is then used to perform the arithmetic operation.
-The implementation in \lccref{fig:basis_addition_impl} demonstrates the addition operation.
-For subtraction, a similar implementation is done using the \verb|__sub__| function and switching the plus sign with the minus sign.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def __add__(self, other: Self):
-        if isinstance(other, self.__class__):
-            if other.coeff is None:
-                return self.copy()
-            elif self.coeff is None:
-                return other.copy()
-            else:
-                result = self.resize_modes(other)
-                result.coeff = result.coeff + other.coeff
-                return result
-        else:
-            raise TypeError(
-                f"unsupported operand type(s) for +: '{
-                    self.__class__
-                }' and '{type(other)}'"
-            )
-...
-  \end{lstlisting}
-  \caption{Implementation of basis addition function.}\label{fig:basis_addition_impl}
-\end{figure}
-
-The calculus operations for Fourier basis take advantage of the properties of the Fourier series.
-As discussed in \lccref{sec:fourier_discussion}, derivatives and integration become multiplication and division in the spectral space of Fourier series.
-Our implementation takes advantage of this as shown in \lccref{fig:basis_grad_impl}.
-Similar to how subtraction is just a modification of the addition operation, the integral or antiderivative operator is also implemented simply by changing the operation with the term multiplier from multiplication to division.
-% TODO: change the reference to specific equations for calculus in spectral domain in ch2
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def grad(self, dim: int = 0, ord: int = 1) -> Self:
-        copy = self.copy()
-        if dim == 0 and self.time_dependent:
-            # time dependent use finite differences
-            dt = self.periods[0] / (self.time_size - 1)
-            coeff = copy.coeff
-            for o in range(ord):
-                coeff = torch.gradient(coeff, spacing=dt, dim=1)[0]
-            copy.coeff = coeff
-        else:
-            if self.time_dependent:
-                # disregard time dimension
-                dim = dim - 1
-            k = copy.wave_number(copy.modes[dim])
-            multiplier_dims = [1 for _ in range(copy.ndim)]
-            multiplier_dims[dim] = copy.modes[dim]
-            if self.time_dependent:
-                multiplier_dims = (1, *multiplier_dims)
-            multiplier = (
-                2
-                * torch.pi
-                * 1j
-                * k.reshape(multiplier_dims).to(copy.coeff)
-                / self.periods[dim]
-            )
-            multiplier = multiplier.pow(ord)
-            coeff = copy.coeff.mul(multiplier)
-            coeff[:, ..., 0] = torch.tensor(0 + 0j)
-            copy.coeff = coeff
-        return copy
-...
-  \end{lstlisting}
-  \caption{Implementation of basis grad function.}\label{fig:basis_grad_impl}
-\end{figure}
-
-The last group of functionality implemented in the Basis and FourierBasis classes provides convenience and often used procedures when working with basis functions.
-First, random coefficient generation for the Fourier basis is implemented.
-This is done as discussed in step 3 of the data generation process discussed in \lccref{sec:data_generation}.
-The implemented function shown in \lccref{fig:generate_coeff_impl} is then wrapped in another function that creates a new FourierBasis instance with the generated coefficients.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    @classmethod
-    def generate_coeff(
-        cls,
-        n: int,
-        modes: int | tuple[int, ...],
-        generator: torch.Generator | None = None,
-        random_func: Callable[..., torch.Tensor] = torch.randn,
-        complex_funcs: bool = False,
-        scale: bool = True,
-    ) -> torch.Tensor:
-        if isinstance(modes, int):
-            modes = (modes,)
-        n_modes = len(modes)
-        assert n_modes > 0, "modes should have at least one element"
-        random_func = partial(random_func, generator=generator)
-        if complex_funcs:
-            coeff = random_func((n, *modes), dtype=torch.complex64)
-        else:
-            coeff = random_func((n, *modes), dtype=torch.complex64)
-
-            vals = cls.inv_transform(coeff)
-            coeff = cls.transform(vals.real + 0j)
-        if scale:
-            scaler = torch.tensor(modes).sum() * 0.2
-            coeff = coeff.mul(scaler)
-        return coeff
-...
-  \end{lstlisting}
-  \caption{Implementation of Fourier Basis coefficient generation function.}\label{fig:generate_coeff_impl}
-\end{figure}
-
-Other convenience functionality also provided include plotting, function value perturbation, and function value evaluation based on domain span information that has been stored in the class instance.
-The function value evaluation is especially useful for experimenting and for the plotting functionality itself.
-This is because, the span was given to the constructor and does not need to be composed again with the inverse transform function.
-
-\subsubsection{Model}\label{sec:impl_model}
-
-\noindent The SpectralSVR model is implemented in this module.
-There are two components in this module.
-First, there is the implementation of least-squares support vector regression (LSSVR) using PyTorch.
-This implementation is a reimplementation and modification of an LSSVR implementation using scikit-learn by \textcite{florencioLssvr2020}.
-The modifications are mainly concerned with using PyTorch in place of scikit-learn.
-Other modifications are concerned with the performance side of things, which are computing the kernel matrix in batches to avoid memory spikes and the ability to compute on hardware accelerators supported by PyTorch such as GPUs.
-The LSSVR implementation starts with the constructor which accepts model hyperparameters which include the regularization parameter, kernel function and any kernel parameters, verbosity level, kernel matrix computation batch size, and device to perform computations on.
-The received parameters are then stored as properties of the class instance.
-For the kernel specifically, it will be initialized with the correct default parameters when the fitting function is called.
-This is because if the kernel of choice is the radial basis function, the default scaling parameter needs to be computed from the training features as the square root of the sum of feature variance values.
-
-The optimization function that fits the model to the training data solves \lccref{eq:lssvr_solution}.
-This function is shown in \lccref{fig:lssvr_fit_function_impl}.
-The first half of the function sets up the left and right hand side matrices.
-The left hand side matrix is constructed in part with the kernel matrix.
-The kernel function used is batched to reduce the peak memory footprint.
-These matrices are then used in the second half to compute the solution using the least squares solver function from PyTorch called lstq.
-Finally, the result is split into the biases and Lagrange multipliers which are then returned as a tuple.
-The optimizing function is wrapped in a more user-friendly function which allows the use of NumPy arrays in addition to the PyTorch Tensor used in the optimizing function.
-The wrapper function is named fit.
-It conforms the inputs provided by the user into the expected types and matrix shapes of rows for samples and columns for input features or output targets.
-The processed inputs and outputs are also stored as support vectors for use during prediction.
-The fit function returns the class instance once training is done.
-This is for method chaining purposes for ease of use when using the fit function in a chain with other functions we will discuss next, such as the prediction function.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def _optimize_parameters(
-      self,
-      X: torch.Tensor,
-      y_values: torch.Tensor,
-    ):
-
-        A = torch.empty(
-          (X.shape[0] + 1,) * 2,
-          device=self.device,
-          dtype=self.dtype,
-        )
-        A[1:, 1:] = self._batched_K(X, X)
-        A[1:, 1:].diagonal().copy_(
-            A[1:, 1:].diagonal()
-            + torch.ones(
-                (A[1:, 1:].shape[0],),
-                device=self.device,
-                dtype=self.dtype,
-            ).to()
-            / self.C
-        )
-        A[0, 0] = 0
-        A[0, 1:] = 1
-        A[1:, 0] = 1
-        shape = np.array(y_values.shape)
-        shape[0] += 1
-        B = torch.empty(
-          list(shape), device=self.device, dtype=self.dtype
-        )
-        B[0] = 0
-        B[1:] = y_values
-
-        solution: torch.Tensor = torch.linalg.lstsq(
-            A.to(dtype=torch.float), B.to(dtype=torch.float)
-        ).solution.to(dtype=self.dtype)
-
-        b = solution[0, :]
-        alpha = solution[1:, :]
-
-        return (b, alpha)
-...
-  \end{lstlisting}
-  \caption{Implementation of Least-squares Support Vector Regression fitting function.}\label{fig:lssvr_fit_function_impl}
-\end{figure}
-
-The learned multipliers and bias parameters are then used for predicting outputs from unseen sample features.
-\Cref{eq:lssvr_prediction_vectorized} shows the computation that needs to be done to compute the predicted output.
-The prediction process first constructs both matrices on the left-hand side of the equation.
-This is done by computing the kernel matrix between the prediction features and the training features, otherwise known as support vectors.
-The prediction function therefore is very straight forward with an input of unseen features and the learned parameters.
-The function output is simply the predicted outputs.
-The implementation of this function is shown in \lccref{fig:lssvr_predict_function_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-NumpyArrayorTensor = (
-    np.ndarray[typing.Any, np.dtype[np.float_]] |
-    torch.Tensor
-)
-...
-    def predict(
-        self,
-        X: NumpyArrayorTensor,
-    ) -> NumpyArrayorTensor:
-        """Predicts the labels of data X given a trained model.
-        - X: ndarray of shape (n_samples, n_attributes)
-        """
-        is_torch = isinstance(X, torch.Tensor)
-        if is_torch:
-            if X.ndim == 1:
-                X_reshaped_torch = X.reshape(-1, 1)
-            else:
-                X_reshaped_torch = X
-            X_= X_reshaped_torch.clone().to(
-                self.device, dtype=self.dtype
-            )
-        else:
-            if X.ndim == 1:
-                X_reshaped_np = X.reshape(-1, 1)
-            else:
-                X_reshaped_np = X
-            X_ = torch.from_numpy(X_reshaped_np).to(
-                self.device, dtype=self.dtype
-            )
-
-        KxX = self._batched_K(X_, self.sv_x)
-
-        y_pred = KxX @ self.alpha + self.b
-        predictions: NumpyArrayorTensor
-        if is_torch:
-            predictions = y_pred.to(X)
-        else:
-            predictions = y_pred.cpu().numpy()
-
-        if X.ndim == 1:
-            return predictions.reshape(-1)
-        else:
-            return predictions
-...
-  \end{lstlisting}
-  \caption{Implementation of Least-squares Support Vector Regression prediction function.}\label{fig:lssvr_predict_function_impl}
-\end{figure}
-
-Aside from these core functions, interpretation of the model using the methods introduced by \textcite{ustunVisualisationInterpretationSupport2007} are also implemented in the LSSVR class.
-First, using the support vectors and the kernel matrix computed between each support vectors, the correlation image is computed.
-This image, which is a correlation matrix, is intended to visualize the importance of features within kernel functions.
-This is simply computed with matrix multiplication between the kernel matrix and the support vectors.
-The implementation is shown in \lccref{fig:lssvr_correlation_image_function_impl}.
-The batched kernel function is used in this case to mitigate the memory footprint.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def get_correlation_image(self):
-        return self._batched_K(
-            self.sv_x, self.sv_x
-        ).mm(self.sv_x)
-...
-  \end{lstlisting}
-  \caption{Implementation of Least-squares Support Vector Regression correlation image function.}\label{fig:lssvr_correlation_image_function_impl}
-\end{figure}
-
-The other interpretation method introduced by \textcite{ustunVisualisationInterpretationSupport2007} visualizes the relationship learned between the input features and the outputs.
-This visualization is computed as the matrix multiplication between the support vectors and the learned Lagrange multipliers.
-The support vector matrix is transposed so that the multiplication is done on the dimension that indexes each sample.
-This computation is implemented as shown in \lccref{fig:lssvr_p_matrix_function_impl}.
-The resulting matrix is termed the p-matrix.
-The columns of this matrix represents the outputs and the rows represents the input features.
-The p-matrix values show how each feature contribute to the output learned by the model.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def get_p_matrix(self):
-        return self.sv_x.T.mm(self.alpha)
-...
-  \end{lstlisting}
-  \caption{Implementation of Least-squares Support Vector Regression p-matrix function.}\label{fig:lssvr_p_matrix_function_impl}
-\end{figure}
-
-The second component of the model modules is the SpectralSVR implementation that uses a multi-output support vector regression (SVR) model to learn in the spectral domain, such as the LSSVR implementation in the first component.
-The SpectralSVR is implemented as a class that extends the LSSVR to be able to learn from features and labels which are complex valued, which is the case for Fourier series coefficients.
-First, the constructor used to initialize each SpectralSVR instance accepts a Basis instance, an SVR instance which is the implemented LSSVR by default, and the verbosity of the model.
-These parameters are then used when the training function shown in \lccref{fig:spectralsvr_train_impl} is called.
-Training the SpectralSVR model begins by calling the train function with parameters of the input function representation, output function representation, and an indicator of whether the output function is time dependent.
-Then, the function ensures that the features and labels are matrices.
-And then, if the input or output function representations are complex, they are transformed into the real representation.
-These formatted training data features and labels are then used to train the LSSVR model itself.
-Finally, to again allow for chaining methods, the function returns the current class instance.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def train(
-        self,
-        f: torch.Tensor,
-        u_coeff: torch.Tensor,
-        u_time_dependent: bool = False,
-    ):
-        self.basis.time_dependent = u_time_dependent
-        if self.basis.coeff_dtype.is_complex:
-            u_coeff = to_complex_coeff(u_coeff)
-
-        if f.ndim > 2:
-            f = f.flatten(1)
-        if u_coeff.ndim > 2:
-            u_coeff = u_coeff.flatten(1)
-
-        if torch.is_complex(u_coeff):
-            u_coeff = to_real_coeff(u_coeff)
-        if torch.is_complex(f):
-            f = to_real_coeff(f)
-        self.svr.fit(f, u_coeff)
-        return self
-...
-  \end{lstlisting}
-  \caption{Implementation of SpectralSVR training function.}\label{fig:spectralsvr_train_impl}
-\end{figure}
-
-Using the learned data to predict other output function representations from unseen input functions can be done by directly calling the predict function of the LSSVR\@.
-This results in the real representation which needs to be converted into the complex representation for the FourierBasis.
-Once the conversion is done, the coefficients can be used to construct a new FourerBasis instance of the predictions.
-From there, the predicted functions can be evaluated and  plotted.
-However, if one simply wants to evaluate the value of the predicted function at arbitrary points, another function is implemented to provide ease of use for this exact case.
-The implemented function is called forward as displayed in \lccref{fig:spectralsvr_forward_impl}.
-The arguments to this function are the input functions, the evaluation points, and the domain span.
-The function first predicts the output function coefficients.
-Then, the predicted coefficients are multiplied with the basis function values at each point to compute the final predicted point values.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def forward(
-        self,
-        f: torch.Tensor,
-        x: torch.Tensor,
-        periods: tuple[float, ...]
-        | None = None,
-    ) -> torch.Tensor:
-        if len(x.shape) == 1:
-            x = x.unsqueeze(-1)
-
-        # compute coefficients
-        if torch.is_complex(f):
-            f = to_real_coeff(f)
-        coeff = self.svr.predict(f)
-        # convert to complex if basis needs complex values so that the reshaping is correct
-        if self.basis.coeff_dtype.is_complex:
-            coeff = to_complex_coeff(coeff)
-
-        return self.basis.evaluate(
-            coeff=coeff.reshape((f.shape[0], *self.modes)),
-            x=x,
-            periods=periods,
-            time_dependent=self.basis.time_dependent,
-        )
-...
-  \end{lstlisting}
-  \caption{Implementation of SpectralSVR forward function (pointwise prediction).}\label{fig:spectralsvr_forward_impl}
-\end{figure}
-
-The final core piece of functionality the SpectralSVR class provides is the inverse parameter estimation.
-This is implemented to solve inverse problems such as predicting the initial conditions for the Burgers' equation or heat equation.
-This function essentially does the gradient descent on a loss function in such a way that the output function matches some expected output.
-The loss function is simply a measure of how far the outputs of the current predicted inputs are from the target outputs.
-The loss function is formulated as the mean squared error of the difference between the predicted output and expected output.
-Using some randomly initialized values as the inputs, the predicted output is then used to compute the loss.
-The gradient of the loss with respect to the inputs are then computed and then used to perform optimization of the inputs using the ADAM optimizer.
-This is implemented as the inverse function shown in \lccref{fig:spectralsvr_inverse_impl}.
-The function arguments are the expected output function coefficients, evaluation points, the loss function used, how many optimization loops are done, the random number generator, and the gain which is used in generating the random initial input functions.
-The function returns the estimated input function coefficients in the real representation.
-For Fourier coefficients this means that the predicted input coefficients need to first be converted to complex valued tensors and then used to construct a FourierBasis instance.
-For convenience, a wrapper like the forward function is also implemented for evaluating the function values of the predicted input coefficients.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def inverse_coeff(
-        self,
-        u_coeff: torch.Tensor,
-        loss_fn: Callable[
-            [torch.Tensor, torch.Tensor], torch.Tensor
-        ] = mean_squared_error,
-        epochs=100,
-        generator=torch.Generator().manual_seed(42),
-        gain=0.05,
-        **optimizer_params,
-    ):
-        f_shape = (u_coeff.shape[0], self.svr.sv_x.shape[1])
-        complex_coeff = u_coeff.is_complex()
-        original_device = u_coeff.device
-        u_coeff = to_real_coeff(u_coeff.flatten(1)).to(self.svr.device)
-
-        # inverse problem
-        f_coeff_pred = (
-            torch.randn(f_shape, generator=generator).to(self.svr.device) * gain
-        )
-        f_coeff_pred.requires_grad_()
-        optim = torch.optim.Adam([f_coeff_pred], **optimizer_params)
-
-        for epoch in range(epochs):
-            optim.zero_grad()
-            u_coeff_pred = self.svr.predict(f_coeff_pred)
-            loss = loss_fn(u_coeff_pred, u_coeff)
-            loss.backward()
-            optim.step()
-        optim.zero_grad()
-        f_coeff_pred.requires_grad_(False)
-        if complex_coeff:
-            f_coeff_pred = to_complex_coeff(f_coeff_pred)
-        return f_coeff_pred.to(original_device)
-...
-  \end{lstlisting}
-  \caption{Implementation of SpectralSVR inverse coeff function (parameter estimation).}\label{fig:spectralsvr_inverse_impl}
-\end{figure}
-
-The SpectralSVR class also provides a convenience function for testing the performance of the learned model.
-This function is shown in \lccref{fig:spectralsvr_test_impl}.
-The function arguments are the testing inputs, expected testing outputs, and a resolution for evaluation of function values.
-The first step is to convert the testing input into real representations and then predicting the output function.
-The predicted output are then compared to the testing outputs using many metrics including RMSE, MSE, MAE, R\textsuperscript{2}, SMAPE, RRSE, and the number of Nan values present in the predicted output.
-The same comparison process is carried out again for the function values which are evaluated at the specified resolution.
-Finally, the function returns the metric values as a nested tuple for both the coefficients predictions and the function value predictions.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def test(
-        self,
-        f: torch.Tensor,
-        u_coeff_targets: torch.Tensor,
-        res: ResType = 200,
-    ):
-        if torch.is_complex(f):
-            logger.debug("transform f to real")
-            f = to_real_coeff(f)
-        u_coeff_preds = self.svr.predict(f)
-        if torch.is_complex(u_coeff_targets):
-            logger.debug("transform u_coeff to real")
-            u_coeff_targets = to_real_coeff(u_coeff_targets)
-
-        grid = self.basis.grid(res).flatten(0, -2)
-        u_preds = self.basis.evaluate(
-            coeff=to_complex_coeff(u_coeff_preds),
-            x=grid,
-            time_dependent=self.basis.time_dependent,
-        ).real
-        u_targets = self.basis.evaluate(
-            coeff=to_complex_coeff(u_coeff_targets),
-            x=grid,
-            time_dependent=self.basis.time_dependent,
-        ).real
-        return {
-            "spectral": get_metrics(
-                u_coeff_preds, u_coeff_targets
-            ),
-            "function value": get_metrics(u_preds, u_targets),
-        }
-...
-  \end{lstlisting}
-  \caption{Implementation of SpectralSVR test function.}\label{fig:spectralsvr_test_impl}
-\end{figure}
-
-\subsubsection{Problems}
-
-\noindent The final module implements the PDEs that will serve as problems the proposed modules will solve.
-The implementation is mainly responsible for generating datasets from the PDEs and computing the PDE residuals.
-This implementation is focused on the two synthetic datasets which are the antiderivative problem and the Burgers' equation problem.
-The problem base class is implemented as an abstract class that the specific problems will subclass.
-The base class requires any subclass to implement three methods.
-First, the data generation method which receives specifications such as what basis functions to use, how many function samples to create, how many modes are needed for each sample, and a PyTorch generator that will be used in generating the random basis coefficients.
-Other arguments more specific to each problem will be implemented by the specific subclass.
-This function is then expected to return a tuple of Basis instances.
-The second and third functions are the spectral and function value residuals for the PDE of each subclass, respectively.
-These three functions make up the functionality that is offered by all Problem subclasses.
-The implementation of the Problem subclass can be seen in \lccref{fig:problem_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-import abc
-import torch
-from ..basis import BasisSubType
-
-class Problem(abc.ABC):
-    def __init__(self) -> None:
-        super().__init__()
-
-    @abc.abstractmethod
-    def generate(
-        self,
-        basis: type[BasisSubType],
-        n: int,
-        modes: int | tuple[int, ...],
-        *args,
-        generator: torch.Generator | None = None,
-        **kwargs,
-    ) -> tuple[BasisSubType, ...]:
-        pass
-
-    @abc.abstractmethod
-    def spectral_residual(
-        self, u: BasisSubType, *args, **kwargs
-    ) -> BasisSubType:
-        pass
-
-    @abc.abstractmethod
-    def residual(
-        self, u: BasisSubType, *args, **kwargs
-    ) -> BasisSubType:
-        pass
-  \end{lstlisting}
-  \caption{Implementation of Problem base class.}\label{fig:problem_impl}
-\end{figure}
-
-The antiderivative problem is relatively simple to implement.
-The generation function takes advantage of the gradient operation and generate function provided by the Basis subclasses.
-The arguments to this function are the same as the base class with the addition of an integration constant parameter.
-By default, the value of the integration constant is zero.
-The function then returns the tuple of basis subclass instances representing the derivative and antiderivative functions.
-This function can be seen in \lccref{fig:antiderivative_generate_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def generate(
-        self,
-        basis: Type[BasisSubType],
-        n: int,
-        modes: int | tuple[int, ...],
-        u0: float | int | complex,
-        *args,
-        generator: torch.Generator | None = None,
-        **kwargs,
-    ) -> tuple[BasisSubType, BasisSubType]:
-        if isinstance(modes, int):
-            modes = (modes,)
-        # generate solution functions
-        u = basis.generate(
-            n, modes, generator=generator, *args, **kwargs
-        )
-        # compute derivative functions
-        ut = u.grad()
-        # set the integration coefficient
-        if isinstance(u0, complex):
-            if u.coeff.is_complex():
-                u.coeff[:, 0] = torch.tensor(u0)
-            else:
-                u.coeff[:, 0] = torch.tensor(u0).real
-        elif isinstance(u0, float) or isinstance(u0, int):
-            if u.coeff.is_complex():
-                u.coeff[:, 0] = torch.tensor(u0 + 0j)
-            else:
-                u.coeff[:, 0] = torch.tensor(u0)
-        else:
-            u.coeff[:, 0] = u0
-
-        return (u, ut)
-...
-  \end{lstlisting}
-  \caption{Implementation of Antiderivative generate function.}\label{fig:antiderivative_generate_impl}
-\end{figure}
-
-The residual functions are similarly easy to implement as shown in \lccref{fig:antiderivative_residual_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def spectral_residual(
-        self, u: BasisSubType, ut: BasisSubType
-    ) -> BasisSubType:
-        residual = u.grad() - ut
-        if residual.coeff is not None:
-            residual.coeff[:, 0].mul_(0)
-
-        return residual
-
-    def residual(
-        self, u: BasisSubType, ut: BasisSubType
-    ) -> BasisSubType:
-        u_val, grid = u.get_values_and_grid()
-        ut_val = ut.get_values()
-        dt = grid[1, 0] - grid[0, 0]
-        u_grad = torch.gradient(
-            u_val, spacing=dt.item(), dim=1
-        )[0]
-        residual_val = u_grad - ut_val
-        residual = u.copy()
-        residual.coeff = u.transform(residual_val)
-        return residual
-...
-  \end{lstlisting}
-  \caption{Implementation of Antiderivative residual functions.}\label{fig:antiderivative_residual_impl}
-\end{figure}
-
-For the Burgers' equation, the problem subclass for this PDE implemented a generate function with two generation paths.
-But before discussing the specifics of the two paths, the function has some extra arguments and preprocessing of those arguments.
-This time the function asks for the kind of functions the initial condition and the forcing term needs to be, whether they are random or constant.
-The combination of the kind of functions the initial conditions and forcing terms are will determine the path of generation that the function will take.
-The function also requires the viscosity parameter nu which is 0.01 by default.
-The domain also needs to be specified with a default value of 0 to 1 with 200 grid points for both space and time.
-The solver which is used for one of the generation procedures is also an argument with a default of the implicit Adams solver from torchdiffeq \autocite{Chen_torchdiffeq_2021}.
-Finally, whether the output basis coefficients are time dependent or not is passed in as an argument alongside with the PyTorch generator.
-The implementation of this portion of the function can be seen in \lccref{fig:burgers_generate_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def generate(
-        self,
-        basis: Type[BasisSubType],
-        n: int,
-        modes: int | tuple[int, ...],
-        u0: ParamInput | BasisSubType = "random",
-        f: ParamInput | BasisSubType = 0,
-        nu: float = 0.01,
-        space_domain=slice(0, 1, 200),
-        time_domain=slice(0, 1, 200),
-        solver: SolverSignatureType = implicit_adams_solver,
-        time_dependent_coeff: bool = True,
-        *args,
-        generator: torch.Generator | None = None,
-        **kwargs,
-    ) -> tuple[BasisSubType, BasisSubType]:
-        if isinstance(modes, int):
-            modes = (modes,)
-
-        device = "cuda:0" if torch.cuda.is_available() else "cpu"
-
-        L = space_domain.stop - space_domain.start
-        x = (
-            basis.grid(slice(
-                space_domain.start, space_domain.stop, modes[0]
-            )).flatten(0, -2)
-            .to(device=device)
-        )
-        T: float = time_domain.stop - time_domain.start
-        nt = int(time_domain.step)
-        # nt = int(T / (0.01 * nu) + 2)
-        dt = T / (nt - 1)
-        t = basis.grid(time_domain).flatten().to(device=device)
-        periods = (T, L)
-...
-  \end{lstlisting}
-  \caption{Implementation of Burgers generate function.}\label{fig:burgers_generate_impl}
-\end{figure}
-
-The first generation path and most similar to the antiderivative case is when both the initial condition and forcing terms are random.
-This branch of the generate function utilizes the residual function to compute the forcing term from the randomly generated solution function.
-This method of generating the solution and forcing term is stable and relatively straightforward.
-The implementation of this branch is shown in \lccref{fig:burgers_generate_manufactured_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-        if u0 == "random" and f == "random":
-            # use method of manufactured solution
-            time_mode = modes[0]
-            if len(modes) > 1:
-                modes = modes[1:]
-            u = basis.generate(
-                n,
-                (time_mode, *modes),
-                periods=periods,
-                generator=generator,
-            )
-            res_modes = tuple(slice(0, L, mode) for mode in modes)
-            fst = self.spectral_residual(
-                u,
-                basis(
-                    basis.generate_empty(n, (time_mode, *modes))
-                ),
-                nu,
-            )
-            u_gen = u
-            f_gen = fst
-            # convert to timed dependent coeffs
-            if time_dependent_coeff:
-                u_val = u.get_values(res=(time_domain, *res_modes))
-                u_coeff = basis.transform(
-                    u_val.flatten(0, 1)
-                ).reshape((n, nt, *modes))
-                u_gen = basis(
-                    coeff=u_coeff,
-                    time_dependent=True,
-                    periods=periods
-                )
-
-                f_val = fst.get_values(
-                    res=(time_domain, *res_modes)
-                )
-                f_coeff = basis.transform(
-                    f_val.flatten(0, 1)
-                ).reshape((n, nt, *modes))
-                f_gen = basis(
-                    coeff=f_coeff,
-                    time_dependent=True,
-                    periods=periods
-                )
-...
-  \end{lstlisting}
-  \caption{Implementation of Burgers generate function manufactured method.}\label{fig:burgers_generate_manufactured_impl}
-\end{figure}
-
-The second case is when at least one of the initial condition or forcing term is not random.
-This second case requires solving the Burgers' equation using traditional numerical methods.
-The generate function calls a function that has the responsibility of setting up the constant initial conditions or constant forcing terms and then calls the ODE solver specified in the generate function arguments.
-The right-hand side function computes the time derivative based on \lccref{eq:time_derivative_time_step_function}.
-The implementation of this is show in \lccref{fig:burgers_generate_dt_impl}.
-Putting the above together gives us the implementation of the method of lines generation of Burgers' equation solution and forcing term as show in \lccref{fig:burgers_generate_mol_impl}.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    @staticmethod
-    def rhs(
-        basis: type[Basis],
-        nu: float,
-        u_hat: torch.Tensor,
-        f_hat: torch.Tensor,
-    ) -> torch.Tensor:
-        u = basis(u_hat)
-        dealias_modes = tuple(
-            int(mode * 1.5) for mode in u.modes
-        )
-        u_dealiased = u.resize_modes(
-            dealias_modes, rescale=False
-        )
-        u_val = basis.inv_transform(u_dealiased.coeff)
-        uu_x_hat_dealiased = 0.5 * basis.transform(u_val**2)
-        uu_x = basis(
-            uu_x_hat_dealiased
-        ).resize_modes(u.modes, rescale=False).grad()
-
-        u_u_x_hat = uu_x.coeff
-        u_xx_hat = u.grad().grad().coeff
-        u_t_hat = nu * u_xx_hat + f_hat - u_u_x_hat
-        return u_t_hat
-...
-  \end{lstlisting}
-  \caption{Implementation of Burgers generate function time derivative.}\label{fig:burgers_generate_dt_impl}
-\end{figure}
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-        u0.coeff = u0.coeff.to(device=device)
-        fst.coeff = fst.coeff.to(device=device)
-        print(f"generating with {len(t)} time steps")
-
-        def f_func(t: torch.Tensor, x: torch.Tensor = x):
-            x = x.tile((1, 2))
-            x[:, 0] = t
-            return basis.transform(
-                fst(x).reshape((-1, modes[0]))
-            )
-
-        def rhs_func(t: torch.Tensor, y0: torch.Tensor):
-            y0 = to_complex_coeff(y0)
-            return to_real_coeff(
-                cls.rhs(basis, nu, y0, f_func(t))
-            )
-
-        u_hat = solver(rhs_func, to_real_coeff(u0.coeff), t)
-        if basis.coeff_dtype.is_complex:
-            u_shape = u_hat.shape
-            u_hat = to_complex_coeff(
-                u_hat.flatten(0, 1)
-            ).reshape(
-                (*u_shape[:2], *u0.coeff.shape[1:])
-            )
-
-        u_hat = u_hat.movedim(0, 1)
-        if timedependent_solution:
-            u = basis(u_hat, **kwargs, time_dependent=True)
-        else:
-            u_hat = u_hat.reshape((n * nt, modes[0]))
-            u = basis(
-                basis.transform(
-                    basis.inv_transform(u_hat).reshape(
-                        (n, nt, modes[0])
-                    )
-                ),
-                **kwargs,
-            )
-        u.coeff = u.coeff.cpu()
-        fst.coeff = fst.coeff.cpu()
-        return (u, fst)
-...
-  \end{lstlisting}
-  \caption{Implementation of Burgers generate function method of lines.}\label{fig:burgers_generate_mol_impl}
-\end{figure}
-
-The spectral residual of the Burgers' equation which is used in the method of manufactured solution generation approach is implemented as shown in \lccref{fig:burgers_spectral_residual_impl}.
-As with the right-hand side function, we use the psuedospectral approach for computing the convolution term to avoid large computational expenses for higher number of modes.
-The function value residual is also implemented similarly to the antiderivative version.
-The derivatives are computed with the PyTorch gradient function.
-And then using \lccref{eq:forced_viscous_burgers}, the residual is computed by subtracting the forcing term from both sides.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def spectral_residual(
-        self, u: BasisSubType, f: BasisSubType, nu: float
-    ) -> BasisSubType:
-        u_t = u.grad(dim=0, ord=1)
-
-        dealias_modes = tuple(
-            int(mode * 1.5) for mode in u.modes
-        )
-        u_dealiased = u.resize_modes(
-            dealias_modes, rescale=False
-        )
-        u_val = u.inv_transform(u_dealiased.coeff)
-        uu_dealiased = u.copy()
-        uu_dealiased.coeff = u.transform(u_val.pow(2).mul(0.5))
-        uu_x = uu_dealiased.resize_modes(
-            u.modes, rescale=False
-        ).grad(dim=1)
-
-        u_xx = u.grad(dim=1, ord=2)
-        nu_u_xx = u_xx
-        nu_u_xx.coeff = nu_u_xx.coeff * nu
-
-        residual = u_t + uu_x - nu_u_xx - f
-        return residual
-...
-  \end{lstlisting}
-  \caption{Implementation of Burgers spectral residual function.}\label{fig:burgers_spectral_residual_impl}
-\end{figure}
-
-\subsection{Testing}
+% !TEX root = ./technical_doc.tex
+\chapter{TESTING}
 \noindent The implementation is followed by tests of the functionality core to this study.
@@
 \end{table}
-
-\section{Experimental Scenarios}\label{sec:experimental_scenarios}
-\noindent To achieve the goals of this study, as outlined in \lccref{sec:aims}, we present three experimental scenarios.
-These scenarios represent different experimental configurations that will be applied to our implementation of the SpectralSVR library.
-A table of the configurations for each scenario can be seen in \lccref{table:experimental_scenarios}.
-
-\begin{table}[H]
-  \caption{The configuration of experimental scenarios in this study.}\label{table:experimental_scenarios}
-  \centering
-  \begin{tabularx}{\textwidth}{L{0.75}*{3}{L{1.09}}} % compute these using approx barycentric coords (x + 3y = 4, x = 0.8y)
-    \toprule
-    Configuration                    & Scenario 1                                          & Scenario 2                                                          & Scenario 3                                 \\
-    \midrule
-    Data Source                      & Synthetic (computed from equations)                 & Synthetic (computed from equations) with three viscosity values     & ERA5 dataset                               \\\addlinespace[0.5em]
-    Data Augmentations               & Perturbations of three different noise levels       & Perturbation of 10\% the mean standard deviation of function values &                                            \\\addlinespace[0.5em]
-    Data Sample Size                 & 5000 unique functions for each noise level          & 500 unique functions for each viscosity value                       & 7000 time steps                            \\\addlinespace[0.5em]
-    Number of Modes                  &                                                     &                                                                     &                                            \\\addlinespace[0.5em]
-    Scaling                          & Standard scaling                                    & Standard scaling                                                    & Standard scaling                           \\\addlinespace[0.5em]
-    Dataset Split                    & 80\% Training and 20\% Testing for each noise level & 80\% Training and 20\% Testing for each viscosity value             & 80\% Training and 20\% Testing             \\\addlinespace[0.5em]
-    Regularization Parameter (\(C\)) & 1.0                                                 & 1.0                                                                 & 1.0                                        \\\addlinespace[0.5em]
-    Kernel                           & RBF (\(\sigma = features \times X.var()\))          & RBF (\(\sigma = features \times X.var()\))                          & RBF (\(\sigma = features \times X.var()\)) \\\addlinespace[0.5em]
-    Additional Tests                 & Exact solutions                                     & Exact solutions                                                     &                                            \\\addlinespace[0.5em]
-    Interpretation                   & p-matrix and correlation image                      & p-matrix and correlation image                                      & p-matrix and correlation image             \\
-    \bottomrule
-  \end{tabularx}
-\end{table}
-
-Each scenario serves a different purpose.
-The first scenario is constructed to establish whether the model can learn any relationships at all in data that implicitly defines differential equations.
-This scenario is a proof of concept of whether the model is capable of accurately learning the relationship between derivatives and their anti-derivatives.
-As the simplest case, it provides a foundation for understanding the model and its behavior.
-The 5\% noise model is then used to predict the antiderivative of a cosine function with a period of one as shown in \lccref{eq:sine_derivative}.
-The exact solution is known as \lccref{eq:sine_function} \autocite{abramowitzHandbookMathematicalFunctions1972}.
-The second goal of this scenario is to determine how noise affects the model's predictions.
-This is especially important for the inverse problem because of how sensitive the derivative is to changes in the antiderivative.
-To further solidify how the model fares for inverse problems, this scenario will also assess the performance of a trained model for a very simple inverse problem setup to determine the derivatives of the testing subset from the antiderivatives.
-This setup will utilize the model as a surrogate forward solver and optimize for a loss function using the inverse function of the SpectralSVR class as described in \lccref{sec:impl_model}.
-\begin{align}
-  f(x) & = 2\pi \cos\left(2\pi x\right)\label{eq:sine_derivative} \\
-  f(x) & = \sin\left(2\pi x\right)\label{eq:sine_function}
-\end{align}
-
-The second scenario extends the goal of the first scenario by examining the model and its behavior when learning a nonlinear PDE\@.
-The data subsets with different viscosity values are intended to allow us to learn more about how this will affect the performance on the exact solutions for lower viscosity numbers.
-The model will learn to predict future states of systems governed by the Burgers' equation from past states.
-The model for each viscosity will be used to predict \lccref{eq:burgers_exact_solution} from initial conditions at time equals zero and the corresponding forcing term of a constant value of zero.
-The exact equation prediction will be done using a rollout method.
-The initial condition along with the initial forcing term will be given to the model to predict the solution at the first time step.
-The model will then use the predicted solution with the forcing term at the first time step to predict the solution at the second time step.
-This is repeated until the stopping condition of time \(t=10\).
-The forcing term for the exact solution is a constant zero.
-Along with the rollout of the exact solution, we also perform roll out on one of the test solution.
-
-The third scenario is designed to demonstrate the modeling capability of SpectralSVR on a more practical problem of weather prediction.
-The earth weather system is a complex collection of processes.
-Using the ERA5 dataset, the model will be used to predict future states of the atmosphere from previous states.
-Specifically, the model will learn to predict the temperature 2 meters above the surface.
-That means that other than the time and spatial resolution not being the highest, the model will also learn from partial information of the relationships defined by the equation since no other variables will be included.
-This choice was made as an analog for situation with unknown PDEs and therefore unknown variables.
-With these situations, there is no guarantee that the variables measured have any relation with the system.
-These three scenarios together address the last two aims of this study.
-
-\section{Experimental Results}\label{sec:experimental_results}
-\noindent In this section, the results of each experimental scenario is presented and analyzed. The results come in the form of testing metrics mentioned in . %TODO: add reference to the metrics used.
-The model interpretations are displays of the correlation image and the p-matrix. The function values and coefficients themselves will also be plotted depending on the number of dimensions.
-
-\subsection{Scenario 1}
-\noindent The first scenario results are presented in four parts.
-The first is the coefficient prediction metrics which is shown in \lccref{table:scenario_1_spectral_metrics}.
-The table shows the noise level and the performance metrics.
-\begin{table}[H]
-  \caption{Performance metrics of coefficient prediction in scenario 1 by noise level.}\label{table:scenario_1_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrrrrrrr}
-    \toprule
-    Noise level & MSE   & RMSE & MAE  & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    5\%         & 0.86  & 0.93 & 0.57 & 0.96 & 0.31  \\
-    10\%        & 2.06  & 1.43 & 0.93 & 0.91 & 0.46  \\
-    50\%        & 15.59 & 3.95 & 3.04 & 0.50 & 1.04  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The scenario is implemented as a Jupyter notebook which imports relevant libraries and our SpectralSVR library.
-The notebook starts with creating the data with the Antiderivative problem subclass.
-All random processes use the same PyTorch Generator instance with a seed of 42.
-The data is then augmented by perturbing the function values to create three versions with the noise levels mentioned in the scenario.
-Looping through each version, the training and testing subsets are randomly sampled to result in 80\% and 20\% of the original dataset respectively.
-Then the scaling function is fitted on the training subset inputs.
-And then, both the training and testing inputs are transformed using the fitted scaling function.
-Next, an instance of SpectralSVR is trained and tested.
-Finally, the metrics are stored and the next noise level is processed.
-Next the 5\% noise model is used to predict the antiderivative of a sine function.
-
-The kernel scaling hyperparameter sigma has the same value of 10 for all noise levels.
-This is because the inputs are all scaled to approximately have a standard deviation of one.
-The value itself is from the number of features which comes out to 100 total inputs to the LSSVR\@.
-
-\Cref{table:scenario_1_spectral_metrics} shows that the model is able to generalize from the training data and learn the simple linear antiderivative operator.
-Focusing on the coefficient of determination (R\textsuperscript{2}) scores, we can see that the model is off by 0.04 to the perfect score of 1.0 for the lowest noise level.
-While increasing noise levels does degrade the performance, this is partly due to the target values also having been perturbed.
-This fact can be seen if we look at how predictions from the very same trained models on noisy inputs are compared to the noise-free versions of the antiderivative functions which is shown in \lccref{table:scenario_1_clean_spectral_metrics}.
-The metrics show that the model predictions are slightly closer to the unperturbed function coefficients compared to the perturbed versions.
-This can be seen as the influence of the independent synthetic measurement noise in the perturbed targets being removed from the testing metrics.
-
-The higher noise levels shows that the model is still relatively accurate.
-Looking at the R\textsuperscript{2} score for the 50\% noise level, the model is more accurate than a baseline mean value model.
-The R\textsuperscript{2} score of 0.5 means that the model predictions has roughly half the error the baseline would produce.
-
-\begin{table}[H]
-  \caption{Performance metrics of coefficient prediction compared to unperturbed targets in scenario 1 by noise level.}\label{table:scenario_1_clean_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrrrrrr}
-    \toprule
-    Noise level & MSE  & RMSE & MAE  & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    5\%         & 0.79 & 0.89 & 0.51 & 0.96 & 0.28  \\
-    10\%        & 1.80 & 1.34 & 0.80 & 0.92 & 0.40  \\
-    50\%        & 9.30 & 3.05 & 2.23 & 0.62 & 0.90  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The function values are also evaluated and the values of the metrics between the noisy targets and predictions are shown in \lccref{table:scenario_1_function_metrics}.
-While the relative metrics R\textsuperscript{2} and sMAPE stay close to the values we obtained for the coefficients themselves, since the metrics are now being computed in the physical domain, the scales have changed and because of that the values of the absolute metrics now reflect the change in scale.
-For reference, the scale of the target coefficient values for the 50\% noise level dataset in their real representation can range on average from -13.54 to 13.6 across the entire dataset.
-Therefore, an RMSE value of 3.94 for the predictions compared to the noisy targets mean that the error ratio is roughly 0.148 or just above 1 to 7.
-For the function values of the 50\% noise dataset the values range on average from -2.5 to 2.49.
-This was more difficult to compute since there is no direct way to compute the amplitude of the function from just the coefficients.
-Here we used the inverse transform and extracted the maximum and minimum values of each function from the discrete values.
-Since the RMSE in \lccref{table:scenario_1_function_metrics} for the 50\% noise dataset is 0.63, the error ratio comes to 0.126.
-One side note about \lccref{table:scenario_1_function_metrics} is that since the model instances are the same as the ones used in the coefficient evaluations, the hyperparameters are still the same including the kernel scaling factor sigma.
-\begin{table}[H]
-  \caption{Performance metrics of function value from evaluated coefficient prediction in scenario 1 by noise level.}\label{table:scenario_1_function_metrics}
-  \centering
-  \begin{tabular}{lrrrrrrrr}
-    \toprule
-    Noise level & MSE  & RMSE & MAE  & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    5\%         & 0.03 & 0.18 & 0.15 & 0.97 & 0.39  \\
-    10\%        & 0.08 & 0.29 & 0.23 & 0.92 & 0.55  \\
-    50\%        & 0.62 & 0.79 & 0.63 & 0.49 & 1.05  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-For the metrics between the predictions and the noise-free version of the target function values, the results parallel the outcomes of the coefficient predictions.
-The metrics show that the model performs slightly better with more pronounced differences for the higher noise levels.
-This echoes our previous statement on the effect of independent \enquote{measurement} noise in the target values on the evaluation metrics.
-\begin{table}[H]
-  \caption{Performance metrics of function value from evaluated coefficient prediction compared to unperturbed targets in scenario 1 by noise level.}\label{table:scenario_1_clean_function_metrics}
-  \centering
-  \begin{tabular}{lrrrrrrr}
-    \toprule
-    Noise level & MSE  & RMSE & MAE  & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    5\%         & 0.03 & 0.18 & 0.14 & 0.97 & 0.38  \\
-    10\%        & 0.07 & 0.27 & 0.21 & 0.93 & 0.53  \\
-    50\%        & 0.37 & 0.61 & 0.49 & 0.62 & 0.94  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The next part of this scenario is the results from predicting the exact solution of \lccref{eq:sine_derivative} which is \lccref{eq:sine_function}.
-The function values will be computed with the same discretization as the number of modes we used in the training set.
-Once the values are obtained for both functions, the coefficients are computed.
-Then instancing the FourierBasis class with the coefficients of the derivative function, we can create perturbed versions according to the noise levels of the training set.
-Finally, the derivative is used to predict the noise-free antiderivative.
-The results are presented in \lccrefs{table:scenario_1_exact_spectral_metrics,table:scenario_1_exact_function_metrics}.
-For 5\% and 10\% noise levels, the model shows that it has learned the relation.
-However, the 50\% noise level, the model has been unable to predict the results well enough.
-The marked difference in error across all metrics between the 50\% and the lower noise levels is more apparent for this specific exact problem compared to the test sets.
-A clear picture of this can be seen when we compare the sMAPE metric.
-For the test set, the predictions on average results in a value of 1, however, for this exact problem the sMAPE value is 1.4 to 1.7.
-
-\begin{table}[H]
-  \caption{Performance metrics of coefficient prediction of exact antiderivative in scenario 1 by noise level.}\label{table:scenario_1_exact_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    Noise level & MSE   & RMSE & MAE  & sMAPE \\
-    \midrule
-    5\%         & 0.09  & 0.29 & 0.16 & 1.18  \\
-    10\%        & 0.80  & 0.89 & 0.31 & 1.23  \\
-    50\%        & 10.33 & 3.21 & 0.83 & 1.44  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\begin{table}[H]
-  \caption{Performance metrics of evaluated function values of coefficient prediction of exact antiderivative in scenario 1 by noise level.}\label{table:scenario_1_exact_function_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    Noise level & MSE  & RMSE & MAE  & sMAPE \\
-    \midrule
-    5\%         & 0.00 & 0.06 & 0.05 & 0.23  \\
-    10\%        & 0.03 & 0.18 & 0.15 & 0.36  \\
-    50\%        & 0.41 & 0.64 & 0.58 & 1.65  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The predictions of the exact equation is shown in \lccref{fig:antiderivative_exact}.
-Visually, we can see that as the noise level increases, the model predictions become worse.
-Another observation is how the higher the noise level, the more the predicted functions become closer to zero.
-This is explained by the double penalty phenomenon \autocite{lledoScaledependentVerificationPrecipitation2023}.
-The loss function used for LSSVR penalizes the model for predicting a non-zero value that turns out to be wrong compared to predicting a zero value.
-This results in a model with predictions that are close to the mean of the training data.
-
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/antiderivative_exact_input.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:antiderivative_exact_input}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/antiderivative_exact_prediction.pgf}
-    \end{adjustbox}
-    \caption{}\label{fig:antiderivative_exact_prediction}
-  \end{subfigure}
-  \caption{(\subref{fig:antiderivative_exact_input}) The perturbed exact input function values from \lccref{eq:sine_derivative}.\ (\subref{fig:antiderivative_exact_prediction}) Prediction of antiderivative from the input function that was perturbed.}\label{fig:antiderivative_exact}
-\end{figure}
-
-For inverse problems, we simply use the same testing set with the labels now used to predict the features.
-The model instances are still the same as before.
-With the implementation shown in \lccref{fig:spectralsvr_inverse_impl}, we run the inverse function for predicting coefficients with 2000 epochs, a learning rate of 0.02, and randomized starting point from a normal distribution multiplied by a factor of 0.05.
-The results of inverse prediction for all three noise levels are shown in \lccref{table:scenario_1_inv_spectral_metrics}.
-These metrics were computed after both the target and predicted input functions are scaled back using the same scaling functions they were scaled down with.
-Because the scales of the input and output functions are different, the absolute metrics are much larger in these results compared to the forward problem results.
-For reference, the target input coefficients on average range from -695.65 to 694.9.
-The relative metrics show that for the lower noise levels, the accuracy is still relatively good.
-However, the values are lower than the values for the forward test.
-The difference with the antiderivative prediction becomes more pronounced with the higher noise levels.
-For the highest noise level, the performance has degraded so far that the predictions are worse than a baseline model from the mean of the target input functions.
-One must also note that despite the much worse results of the other metrics for the highest noise level, at this time we're unable to explain why sMAPE results in roughly the same performance as in the forward problem.
-
-\begin{table}[H]
-  \caption{Performance metrics of coefficient inverse prediction of derivative in scenario 1 by noise level.}\label{table:scenario_1_inv_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrrr}
-    \toprule
-    Noise level & MSE      & RMSE   & MAE    & R\textsuperscript{2}    & sMAPE \\
-    \midrule
-    5\%         & 1739.56  & 41.71  & 26.44  & 0.91  & 0.36  \\
-    10\%        & 3485.10  & 59.03  & 42.19  & 0.76  & 0.52  \\
-    50\%        & 49319.73 & 222.08 & 174.48 & -0.19 & 1.05  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-Next, we have the correlation image and p-matrix for the model of each noise level.
-The results are shown in \lccref{fig:scenario_1_interpretation}.
-Each row in the figure represent the results of a model trained on a different noise level.
-The correlation image for 5\% and 10\% noise show clear lines on the coefficient corresponding to the output coefficient that was sorted.
-We can also see that the negative wave number reflection also being sorted.
-This is because of the reflection that occurs with complex Fourier coefficients for real-valued functions.
-There are other faint vertical lines you are able to see for other input coefficients.
-These faint lines are not sorted like the corresponding coefficients we mentioned before.
-Meaning, while they don't affect the particular output coefficients that were sorted, they do show that there is information embedded in the kernel matrix for these input coefficients.
-However, if we look at the 50\% noise correlation image, even the corresponding coefficient does not show a clear line or gradient.
-The lines are more noisy compared to the other noise levels.
-But the kernel still manages to embed some information.
-The p-matrices show that The model itself is able to still learn some relationship between the input coefficients and the output coefficients.
-For the 5\% and 10\% noise levels, the p-matrices show very clearly the contributions of input coefficients to the output coefficients.
-However, looking at the p-matrix for 50\% noise level, the lower wave numbers show lower contribution of input coefficients to the output coefficients.
-\begin{figure}[H]
-  \begin{adjustwidth}{-0.05\linewidth}{-0.05\linewidth}
-    \centering
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_ci_5.pgf}
-      \end{adjustbox}
-      \caption{Correlation image 5\% noise.}\label{fig:sc1_ci_5}
-    \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_pm_5.pgf}
-      \end{adjustbox}
-      \caption{The p-matrix for 5\% noise.}\label{fig:sc1_pm_5}
-    \end{subfigure}
-    % \\[\baselineskip]
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_ci_10.pgf}
-      \end{adjustbox}
-      \caption{Correlation image 10\% noise.}\label{fig:sc1_ci_10}
-    \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_pm_10.pgf}
-      \end{adjustbox}
-      \caption{The p-matrix for 10\% noise.}\label{fig:sc1_pm_10}
-    \end{subfigure}
-    % \\[\baselineskip]
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_ci_50.pgf}
-      \end{adjustbox}
-      \caption{Correlation image 50\% noise.}\label{fig:sc1_ci_50}
-    \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/antiderivative_pm_50.pgf}
-      \end{adjustbox}
-      \caption{The p-matrix for 50\% noise.}\label{fig:sc1_pm_50}
-    \end{subfigure}
-  \end{adjustwidth}
-  \caption{Correlation image (left column) and p-matrix (right column) for each model trained on a different noise level (row).
-The correlation image was sorted same order the values of the real component of wave number \(k=2\) were sorted in descending order.}\label{fig:scenario_1_interpretation}
-\end{figure}
-
-The final observation we make is how for all the p-matrices the pronounced contribution of the input wave number to their corresponding output wave number.
-This means that the majority of contributions to each output coefficients come from the corresponding input coefficients of the same wave number.
-Our knowledge on how the simple derivative equation for Fourier series relate the coefficients of the derivative function and the antiderivative function is shown in \lccref{eq:derivative_coeff}.
-This aligns with the contributions shown by the p-matrices.
-This confirms that the model is indeed learning the relations that is defined by the derivative equation.
-
-In summary, the model is able to learn the linear relationship defined by the derivative equation.
-This is true even for high noise levels.
-The model also learns the actual relationship between each wave number which is shown in the p-matrix.
-Inverse prediction of the input function is also successfully done for lower noise levels.
-At high noise levels, the noise overwhelms the model.
-
-\subsection{Scenario 2}
-\noindent The second scenario results are presented in two parts which are the coefficient predictions and function value predictions.
-The functions are first preprocessed in order to format them into current and next values in time as discussed in \lccref{sec:data_transformation}.
-The sample pairs are first divided into two for the training and testing sets.
-Each function is then discretized into 200 time steps.
-Then, the features are put together as the coefficients of the solution and forcing term at the current time step.
-The labels are the solution at the next time step.
-Since there is too much data to fit into memory all at once at the end of this process, we randomly sample the feature and label pairs.
-This result in a maximum of 8000 samples for the training set and 2000 samples for the testing set.
-As mentioned in \lccref{sec:data_transformation}, the training features are used to fit a scaling function.
-And then, all features are scaled using the fitted scaling function.
-
-The coefficient value predictions are shown in \lccref{table:scenario_2_spectral_metrics}.
-The RBF kernel parameter computed from the data is once again the same for all versions of the dataset with a value of 5.66.
-The testing metrics show that the performance of the model vary with the viscosity value \(\nu \).
-Starting with the inviscid Burgers' equation, with \(\nu=0\), the model performs the best with a close second from the model for the \(\nu = 0.01 \) dataset version.
-The function value evaluated from the predictions is shown in \lccref{table:scenario_2_function_metrics}.
-The metrics across the board shows that the function value relative metrics are slightly better compared to the coefficients.
-Comparing the absolute metrics for the same table, we see the same general trend that the higher viscosity show the model performing worse.
-
-\begin{table}[H]
-  \caption{Performance metrics of coefficient prediction of next time step in scenario 2 by viscosity.}\label{table:scenario_2_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    0.0      & 3.46e-04 & 1.86e-02 & 1.24e-02 & 0.79 & 0.65  \\
-    0.01     & 3.56e-04 & 1.89e-02 & 1.27e-02 & 0.78 & 0.67  \\
-    0.1      & 9.17e-04 & 3.03e-02 & 2.32e-02 & 0.46 & 1.08  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\begin{table}[H]
-  \caption{Performance metrics of function values evaluated from coefficient prediction of next time step in scenario 2 by viscosity.}\label{table:scenario_2_function_metrics}
-  \centering
-  \begin{tabular}{lrrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    0.0      & 5.58e-05 & 7.47e-03 & 5.89e-03 & 0.82 & 0.70  \\
-    0.01     & 5.74e-05 & 7.58e-03 & 6.01e-03 & 0.81 & 0.71  \\
-    0.1      & 1.58e-04 & 1.26e-02 & 9.98e-03 & 0.51 & 1.04  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The testing results are complimented with a rollout experiment.
-The results from the rollout are shown in \lccref{fig:scenario_2_rollout}.
-The rollout starts from time \(t=0\).
-In all the plots, this is at the bottom.
-We have included this initial condition in the plots.
-From this initial condition in combination with the forcing term at the initial time step, the model predicts the first time step solution.
-The model then uses the predicted solution combined with the corresponding forcing term to predict the second time step.
-To see how well the model is performing relative to the actual target values, we compute the difference between the two as shown in \lccrefs{fig:sc2_rollout_diff_0.0,fig:sc2_rollout_diff_0.01,fig:sc2_rollout_diff_0.1}.
-Observe that errors are introduced relatively early around time \(t=1\).
-However, the model rollout stays stable until the end despite this error.
-This results in the model being able to finish the rollout for this sample.
-\begin{figure}[H]
-  \centering
-  \begin{adjustwidth}{-0.1\linewidth}{-0.1\linewidth}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_target_0.0.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.0\)}\label{fig:sc2_rollout_target_0.0}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_pred_0.0.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.0\)}\label{fig:sc2_rollout_pred_0.0}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_diff_0.0.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.0\)}\label{fig:sc2_rollout_diff_0.0}
-    \end{subfigure}
-    \\[0.7\baselineskip]
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_target_0.01.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.01\)}\label{fig:sc2_rollout_target_0.01}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_pred_0.01.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.01\)}\label{fig:sc2_rollout_pred_0.01}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_diff_0.01.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.01\)}\label{fig:sc2_rollout_diff_0.01}
-    \end{subfigure}
-    \\[0.7\baselineskip]
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_target_0.1.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.1\)}\label{fig:sc2_rollout_target_0.1}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_pred_0.1.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.1\)}\label{fig:sc2_rollout_pred_0.1}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_rollout_diff_0.1.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.1\)}\label{fig:sc2_rollout_diff_0.1}
-    \end{subfigure}
-    % \\[0.7\baselineskip]
-  \end{adjustwidth}
-  \caption{The rollout predictions for one of the test function. The difference is calculated as the targets subtracted by the predictions.}\label{fig:scenario_2_rollout}
-\end{figure}
-
-Another observation we can see is that the difference between the target and rollout predictions is much more pronounced for lower viscosity values.
-This result is aligned with metrics shown in \lccrefs{table:scenario_2_rollout_spectral_metrics,table:scenario_2_rollout_function_metrics}.
-The absolute metrics show that the models are performing several times worse in rollout compared to the single time step tests shown in \lccrefs{table:scenario_2_spectral_metrics,table:scenario_2_function_metrics}.
-This seems to be the same challenge that traditional solvers also face with the shocks that may be present with lower viscosity values.
-This means that for rollout scenarios, the model has a much harder time with lower viscosity values.
-\begin{table}[H]
-  \caption{Performance metrics of coefficient rollout in scenario 2 by viscosity.}\label{table:scenario_2_rollout_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & sMAPE \\
-    \midrule
-    0.0      & 2.91e-01 & 5.40e-01 & 4.07e-01 & 0.90  \\
-    0.01     & 1.61e-01 & 4.01e-01 & 2.86e-01 & 0.75  \\
-    0.1      & 1.70e-01 & 4.12e-01 & 3.02e-01 & 0.81  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-\begin{table}[H]
-  \caption{Performance metrics of function values evaluated from coefficient rollout in scenario 2 by viscosity.}\label{table:scenario_2_rollout_function_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & sMAPE \\
-    \midrule
-    0.0      & 5.81e-02 & 2.41e-01 & 1.89e-01 & 1.04  \\
-    0.01     & 3.17e-02 & 1.78e-01 & 1.40e-01 & 0.94  \\
-    0.1      & 2.91e-02 & 1.71e-01 & 1.33e-01 & 0.92  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The exact function \cref{eq:burgers_exact_solution} is computed for each viscosity value.
-The discrete Fourier transform of the values are then used for doing rollout with the model.
-For the forcing term, we just use a constant function with a value of zero.
-The rollout predictions are shown in \lccref{fig:scenario_2_interpretation}.
-The model is not successful in the rollout for the inviscid equation and for the viscosity of \(\nu=0.01\).
-Both of these cases, the model produces too much error that the original function is no longer recognizable in the predictions.
-For the higher viscosity value of \(\nu=0.1\) the rollout produces a recognizable prediction.
-The error stays to about half the maximum function value.
-We do see some more noticeable error in the flatter parts of the function.
-The error also take a very similar shape across the different viscosity values.
-Since we essentially used the same solutions for training the model for each viscosity, the similarity in error means that it can be alleviated with more diverse training samples.
-The error for the flatter functions may also be alleviated by including similar flatter functions during training.
-\begin{figure}[H]
-  \centering
-  \begin{adjustwidth}{-0.1\linewidth}{-0.1\linewidth}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_target_0.0.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.0\)}\label{fig:sc2_exact_target_0.0}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_pred_0.0.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.0\)}\label{fig:sc2_exact_pred_0.0}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_diff_0.0.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.0\)}\label{fig:sc2_exact_diff_0.0}
-    \end{subfigure}
-    \\[0.7\baselineskip]
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_target_0.01.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.01\)}\label{fig:sc2_exact_target_0.01}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_pred_0.01.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.01\)}\label{fig:sc2_exact_pred_0.01}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_diff_0.01.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.01\)}\label{fig:sc2_exact_diff_0.01}
-    \end{subfigure}
-    \\[0.7\baselineskip]
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_target_0.1.pgf}
-      \end{adjustbox}
-      \caption{The target for \(\nu=0.1\)}\label{fig:sc2_exact_target_0.1}
-    \end{subfigure}
-    \begin{subfigure}{0.33\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_pred_0.1.pgf}
-      \end{adjustbox}
-      \caption{The prediction for \(\nu=0.1\)}\label{fig:sc2_exact_pred_0.1}
-    \end{subfigure}
-    \begin{subfigure}{0.32\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/burgers_exact_diff_0.1.pgf}
-      \end{adjustbox}
-      \caption{The difference for \(\nu=0.1\)}\label{fig:sc2_exact_diff_0.1}
-    \end{subfigure}
-    % \\[0.7\baselineskip]
-  \end{adjustwidth}
-  \caption{The rollout predictions for one of the exact function in \lccref{eq:burgers_exact_solution}.
-The difference is calculated as the targets subtracted by the predictions.}\label{fig:scenario_2_exact}
-\end{figure}
-
-The metrics for the exact rollout further solidifies our observations from the plots.
-The metrics are shown in \lccrefs{table:scenario_2_exact_spectral_metrics,table:scenario_2_exact_function_metrics}.
-While the absolute metrics are low, this is mostly due to the maximum function values of the exact function also being pretty low.
-The relative metric sMAPE shows a much clearer picture.
-As expected, the inviscid prediction is pretty much just error.
-The next result, for viscosity \(\nu=0.01\), is better.
-This seems to be from the slight conformance to the target.
-The plots for this viscosity show that the prediction contains \enquote{shapes} similar to the target despite the scale not being close to the target.
-Finally, the highest viscosity level results show the best performance.
-Despite the good performance in the higher detail areas of the function, the error from the flatter areas overwhelm the metrics due to its larger portion of the function.
-\begin{table}[H]
-  \caption{Performance metrics of coefficient rollout of exact solution in scenario 2 by viscosity.}\label{table:scenario_2_exact_spectral_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & sMAPE \\
-    \midrule
-    0.0      & 2.16e-02 & 1.47e-01 & 1.08e-01 & 2.00  \\
-    0.01     & 1.32e-02 & 1.15e-01 & 6.37e-02 & 1.58  \\
-    0.1      & 2.83e-03 & 5.32e-02 & 4.00e-02 & 1.50  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-\begin{table}[H]
-  \caption{Performance metrics of function values evaluated from coefficient rollout of exact solution in scenario 2 by viscosity.}\label{table:scenario_2_exact_function_metrics}
-  \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    \(\nu \) & MSE      & RMSE     & MAE      & sMAPE \\
-    \midrule
-    0.0      & 4.16e-03 & 6.45e-02 & 4.56e-02 & 2.00  \\
-    0.01     & 3.23e-03 & 5.68e-02 & 4.94e-02 & 1.73  \\
-    0.1      & 3.86e-04 & 1.97e-02 & 1.62e-02 & 1.47  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The correlation image and p-matrix for each viscosity can be seen in \lccref{fig:scenario_2_interpretation}.
-Analyzing the correlation images first, we see that some columns are sorted in correlation to how the samples are sorted based on the real component of the 4th output wave number.
-For the inviscid equation, this correlation is the strongest with multiple columns exhibiting the correlation.
-The highest and visually most sorted values are from the forcing term portion of the inputs.
-Different wave numbers in the inputs are also sorted differently, this indicates an inverse correlation.
-For a higher viscosity of \(\nu=0.01\), a weaker correlation is still present.
-
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_ci_0.0.pgf}
-    \end{adjustbox}
-    \caption{Correlation image \(\nu=0.0\).}\label{fig:sc2_ci_0.0}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_pm_0.0.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix for \(\nu=0.0\).}\label{fig:sc2_pm_0.0}
-  \end{subfigure}
-  % \\[-0.7\baselineskip]
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_ci_0.01.pgf}
-    \end{adjustbox}
-    \caption{Correlation image \(\nu=0.01\).}\label{fig:sc2_ci_0.01}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_pm_0.01.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix for \(\nu=0.01\).}\label{fig:sc2_pm_0.01}
-  \end{subfigure}
-  % \\[-0.7\baselineskip]
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_ci_0.1.pgf}
-    \end{adjustbox}
-    \caption{Correlation image \(\nu=0.1\).}\label{fig:sc2_ci_0.1}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/burgers_pm_0.1.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix for \(\nu=0.1\).}\label{fig:sc2_pm_0.1}
-  \end{subfigure}
-  \caption{Correlation image (left column) and p-matrix (right column) for each model trained on a different viscosity (row).
-The correlation image was sorted same order the values of the real component of wave number \(k=2\) were sorted in descending order.}\label{fig:scenario_2_interpretation}
-\end{figure}
-
-Once we get to the highest viscosity, while the order is still present, we see a more random arrangement of the correlation image values.
-This observation and the lower scores can both be explained by the level of temporal discretization.
-This is the same issue we encounter when we use some traditional methods for higher viscosity values with the same time step for lower viscosity values \autocite{kassamFourthOrderTimeSteppingStiff2005,seydaogluNumericalSolutionBurgers2016}.
-The issue arises in stiff differential equations.
-Stiff differential equations refer to the presence of a rapidly varying component.
-We can see that the larger amplitudes of high frequency components in the forcing term to represent the rapidly varying components as shown in \lccrefs{fig:burgers_forcing_0.0,fig:burgers_forcing_0.01,fig:burgers_forcing_0.1}.
-Traditionally, stiff equations would require specific numerical methods purpose built to efficiently solve the problem.
-Otherwise, the using a solver like FDM would require much finer time steps than the one we are using here.
-
-The p-matrix shows the difference in contributions of both input functions.
-For the inviscid equation, the contributions mainly come from the forcing term.
-The current solution contributes a smaller amount in comparison.
-There is similarity with the antiderivative p-matrices in this case.
-The contributions to each output wave number mainly come from input coefficients with the same wave number.
-However, there is a noticeable contribution from other wave numbers too unlike the antiderivative case.
-The biggest contribution from the current solution is the constant/bias term.
-For higher viscosity values, notice that the contribution of the previous solution increases.
-The increase is more pronounced for higher frequencies.
-This aligns with the quadratic scaling from the wave number on the coefficients \autocite{canutoSpectralMethodsEvolution2007}.
-The p-matrix for lower viscosity values show more structured contribution of other wave numbers in comparison to the higher wave numbers.
-This structure comes in the form of a grid pattern.
-For the real components of the output, the contribution of other wave numbers oscillate between higher and lower values depending on whether the input component is real or not.
-The imaginary output components on the other hand have a more constant contribution across the input components.
-The contribution once again become more pronounced the higher the absolute value of the wave number.
-
-To summarize, Low viscosity values are a challenge to the model as with traditional methods.
-Despite that, this scenario confirms the model's ability to learn the nonlinear relationship defined by the Burgers' equation.
-The model is also able to stay stable with a relatively large time step.
-This concludes the synthetic data portion of the study.
-
-\subsection{Scenario 3}
-\noindent This final scenario tests the model on a much more complex dataset.
-As said previously, this dataset, which is computed using real observations of Earth's weather system, will be used to represent the model learning a very complex system with many unknown contributing variables.
-For our case, this means the data used will be limited to the 2-meter temperature.
-The anomaly is computed by subtracting the climatology from the corresponding day of years and hours of the atmospheric state.
-For example, the temperature on the 6\textsuperscript{th} of January 1998 at 18:00 UTC is subtracted with the average temperature for the 6\textsuperscript{th} day of the year at 18:00 hour UTC\@.
-For any anomaly predictions, the corresponding atmospheric state can simply be computed as the inverse process described before by adding the climatology to the predicted anomaly.
-
-The preprocessing of the data is carried out in the same manner as the Burgers' equation experiments.
-The difference being that for the features we only include the current anomaly of the atmosphere and there are no forcing terms.
-The targets are the future anomaly of the atmosphere.
-The reason for choosing to train and predict the anomaly instead of the state valued themselves is to avoid the model from just learning the obvious periodicity that exists in weather such as the day-night cycle or the seasons.
-Next, Both the current anomaly and future anomaly are Fourier transformed to their 2-dimensional coefficients.
-This process is done for both the training and testing set.
-Once the features for both are processed, we fit the standard scaling function on the training features.
-Using this fitted scaling function, both the training and testing features are scaled to a mean of 0 and standard deviation of approximately 1.
-
-The testing results are shown in \lccrefs{table:sc3_test_anomaly_metrics,table:sc3_test_state_metrics}.
-To put the absolute metrics into context, the median test state coefficient' maximum absolute value is \num{569364.25}.
-With this information, an RMSE value of 64.72 is relatively low error.
-The relative metric sMAPE also agrees with this, with a value of 0.76.
-The function values show that the model on average has an error of around 2 degrees kelvin or Celsius.
-This is again relatively small for the range of temperatures on Earth which span roughly 120 degrees kelvin across the historical maxima and minima.
-From existing knowledge of the problem, we know these values for the metrics are mainly due to the periodicity of atmospheric states.
-When we look at the anomaly metrics, the model is still able to learn some things and perform slightly better than a model of anomaly averages.
-However, since the median maximum absolute value for the state coefficients is \num{1155.14}, the error rate is not as good as the state predictions.
-\begin{table}[H]
-  \caption{Performance metrics of anomaly coefficient prediction for scenario 3.}\label{table:sc3_test_anomaly_metrics}
-  \centering
-  \begin{tabular}{lrrrrr}
-    \toprule
-                   & MSE     & RMSE  & MAE   & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    spectral       & 4189.16 & 64.72 & 32.47 & 0.35 & 1.19  \\
-    function value & 4.09    & 2.02  & 1.44  & 0.09 & 1.24  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\begin{table}[H]
-  \caption{Performance metrics of state coefficient prediction for scenario 3.}\label{table:sc3_test_state_metrics}
-  \centering
-  \begin{tabular}{lrrrrr}
-    \toprule
-                   & MSE     & RMSE  & MAE   & R\textsuperscript{2}   & sMAPE \\
-    \midrule
-    spectral       & 4189.16 & 64.72 & 32.47 & 0.56 & 0.74  \\
-    function value & 4.09    & 2.02  & 1.44  & 0.75 & 0.01  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-The p-matrix and correlation image is shown in \lccref{fig:sc3_interpretation}.
-For the correlation image, we see that most wave numbers are correlated or inversely correlated with the outputs.
-The strongest correlation is shown by the features of the same wave number as the sorted target.
-This is an indication that the equations involved may be nonlinear.
-If we look at the p-matrix however, it seems very flat save a faint diagonal line from the top left to the bottom right.
-The values of the p-matrix are also extremely high.
-With the \enquote{flatness} we see, this is indicative of strong contributions by a few inputs.
-
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_ci.pgf}
-    \end{adjustbox}
-    \caption{The correlation image.}\label{fig:sc3_ci}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_pm.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix.}\label{fig:sc3_pm}
-  \end{subfigure}
-  % \\[-0.7\baselineskip]
-  \caption{Correlation image and p-matrix for WeatherBench 2 model.
-The correlation image was sorted same order the values of the real component of wave number \((k_{longitude}=0, k_{latitude}=2)\) were sorted in descending order.}\label{fig:sc3_interpretation}
-\end{figure}
-
-To see more details of the p-matrix, we show a zoomed in version in \lccrefs{fig:sc3_pm_zoom1,fig:sc3_pm_zoom2}.
-The relationships are much more clear between features and outputs that do not share the same wave number.
-The coefficients with the same longitude wave numbers appear in the same \enquote{square} shape.
-Within the \enquote{square}, coefficients close to the same latitude wave number show much stronger contribution.
-For low wave numbers, shown in \lccref{fig:sc3_pm_zoom1}, the contribution is spread over more latitude wave numbers.
-The higher wave numbers, on the other hand, has the contributions much more concentrated on the coefficients with the same latitude wave numbers.
-In addition, the value of contribution differ by an order of magnitude with lower longitude wave numbers having higher maximum contribution.
-This observation suggests that the nonlinearity and magnitude are inversely proportional to the absolute value of the longitude wave number.
-This is in contrast to when we discussed the forcing term for our Burgers' equation scenario.
-The low frequencies in longitude may indicate that the model has learned some feature of the anomaly that is specific to different times of day.
-This is because the lowest longitudinal wave number would correspond to when different parts of the world is in nighttime or in daytime.
-Other possible explanations may be due to the fact that the earth more closely resemble a sphere compared to the toroidal shape that the 2-dimensional Fourier transform assumes.
-This would result in the representation latitude-wise being distorted.
-For this issue, the use of spherical harmonics may be a better fit to rule out the possibility of any distortions the Fourier transform may introduce.
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_pm_zoom1.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix zoomed in to \((k_{longitude}=\{0, 1, 2\}, k_{latitude}=[-16, 16))\).}\label{fig:sc3_pm_zoom1}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_pm_zoom2.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix zoomed in to \((k_{longitude}=\{\phantom{-}31,-32,\phantom{-}32\}, k_{latitude}=[-16, 16))\).}\label{fig:sc3_pm_zoom2}
-  \end{subfigure}
-  \caption{The p-matrix of the WeatherBench 2 models zoomed in to specific wave numbers.}\label{fig:sc3_pm_zoomed}
-\end{figure}
-
-The predictions from test features are processed through the Fourier inverse transform to evaluate the function values.
-The direct predictions, which is the anomaly, is shown in \lccref{fig:sc3_anomaly_predictions}.
-The model seem to be predicting less extreme values that are noticeable in the target.
-Specifically areas over North America, Central Asia, and parts of Antarctica show lower temperature anomaly than expected.
-We also loose detail in areas which should have a lower anomaly such as northern areas of Africa, Greenland, and South Asia.
-The lack of detail seems to be a problem of underestimation.
-We believe this is caused by the so-called \enquote{double penalty} issue caused by the loss function used for the LSSVR \autocite{lledoScaledependentVerificationPrecipitation2023}.
-The predictions tend to be closer to the mean of the data to avoid the extra penalty from a wrong prediction with a high value.
-One way to allow for finer details that are less accurate is to penalize the higher frequency wave numbers less compared to the lower frequency wave numbers.
-For our case this means the LSSVR for each output will have their regularization parameter decreased to allow the model to focus less on the errors for higher frequencies.
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    % \centering
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_anom_pred.pgf}
-    \end{adjustbox}
-    \caption{Predicted 2-meter temperature anomaly.}\label{fig:sc3_anomaly_pred}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    % \centering
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_anom_target.pgf}
-    \end{adjustbox}
-    \caption{Target 2-meter temperature anomaly.}\label{fig:sc3_anomaly_target}
-  \end{subfigure}
-  \caption{2-meter temperature anomaly prediction for the 1\textsuperscript{st} of January 2020 at 6:00 UTC based on the previous anomaly at 0:00 UTC.}\label{fig:sc3_anomaly_predictions}
-\end{figure}
-
-The state predictions which is obtained by adding the climatology to the predicted anomaly is shown in \lccref{fig:sc3_state_predictions}.
-This further shows areas of discrepancy between the prediction and the target.
-The area in the South Pacific show that the target has a higher difference temperature compared to the prediction.
-This smoothness in the prediction is easier to see for areas in the ocean.
-Many sharp features are lost and the state prediction start to resemble averaged view of the climatology.
-We must also take into account that the model only used temperature distribution data.
-Other pieces of information we know to be crucial to weather prediction such as wind speed or pressure was not included in the inputs.
-With this in consideration the model was still able to learn some relationships defined by governing equations of weather.
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    % \centering
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_state_pred.pgf}
-    \end{adjustbox}
-    \caption{Predicted 2-meter temperature.}\label{fig:sc3_state_pred}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    % \centering
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_state_target.pgf}
-    \end{adjustbox}
-    \caption{Target 2-meter temperature.}\label{fig:sc3_state_target}
-  \end{subfigure}
-  \caption{2-meter temperature prediction for the 1\textsuperscript{st} of January 2020 at 6:00 UTC based on the previous anomaly at 0:00 UTC.}\label{fig:sc3_state_predictions}
-\end{figure}
-
-The results of our experiments show that the proposed model has the ability to learn the relationships that PDEs and other governing equations define.
-The interpretation methods for support vector regression that we used, namely the correlation image and p-matrix developed by \textcite{ustunVisualisationInterpretationSupport2007}, allows us to confirm what the model has learned.
-In the case of the WeatherBench2 model, it has also allowed us to glean some insight into some mechanisms that the model has learned.
-This information was used to verify the learned relationships for the simple derivative equation.
-Together with the performance metrics on three different problems, we have shown the proposed model to be a viable tool for situations with limited knowledge and a need for some level of interpretability of the model.

### 2025-01-14 technical_doc/usecase.tex
fix labels, fix problem with graphics path and suround with curly braces, start technical document

--- 2025-01-14 technical_doc/testing.tex
@@
 % !TEX root = ./technical_doc.tex
-\chapter{TESTING}
-\noindent The implementation is followed by tests of the functionality core to this study.
-The testing is done using the PyTest library.
-The testing method used is a black box approach.
-The tests are written in a separate \verb|tests| directory.
-Each module is tested by a separate file.
-The tests are done to ensure compliance of the implementation to the requirements of the software.
-The final results are presented in \lccref{table:impl_test_result}.
-Each version and iteration of the development must ensure that the tests are passed before any changes are committed to the GitHub repository.
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{lm{0.2\linewidth}m{0.5\linewidth}l}
-        % \toprule
-        \toprule
-        No & Process                         & Test Target                                                                                                   & Test Result \\
-        \midrule
-        1  & Transform                       & Transform invertible with inverse transform                                                                   & Achieved    \\\addlinespace[0.5em]
-        2  & Evaluation                      & Transform coefficient evaluation close to original values                                                     & Achieved    \\\addlinespace[0.5em]
-        3  & Plot                            & Plotting function is run successfully                                                                         & Achieved    \\\addlinespace[0.5em]
-        4  & Perturb                         & Perturb function is run successfully                                                                          & Achieved    \\\addlinespace[0.5em]
-        5  & Operations                      & Operation functions is run successfully                                                                       & Achieved    \\\addlinespace[0.5em]
-        6  & Complex Coefficients Conversion & Conversion between real and complex coefficient representation is invertible for odd and even number of modes & Achieved    \\\addlinespace[0.5em]
-        7  & SpectralSVR Train               & Training function is run successfully                                                                         & Achieved    \\\addlinespace[0.5em]
-        8  & SpectralSVR Prediction          & Coefficient prediction error within tolerable range                                                           & Achieved    \\\addlinespace[0.5em]
-        9  & SpectralSVR Prediction          & Function value prediction error within tolerable range                                                        & Achieved    \\
-        \bottomrule
-    \end{tabular}
-    \caption{Testing results of the SpectralSVR Library implementation using black box method.}\label{table:impl_test_result}
-\end{table}
+\chapter{USE CASE}

### 2025-01-16 skripsi/chapter2.tex
fix labels, fix problem with graphics path and suround with curly braces, start technical document
add revisions file, fix chapter headings, fix numbered enumerate lists bodyless heading like on the explanation of the research design, fix reasonable chktex and lacheck complaints

@@
     \EndFor{}
-    \State{\textbf{return}\(\vb{\alpha}, b\)}
+    \State{\textbf{return} \(\vb{\alpha}, b\)}
     \EndProcedure{}
@@
   \begin{algorithmic}[1]
-    \Require{\(\vb{U}, \vb{\alpha}, \vb{X}, b\)}
-    \Ensure{\(\vb{v}\)}
+    \Procedure{PredictionLSSVR}{$\vb{U}, \vb{\alpha}, \vb{X}, b $}
     \State{\(\Omega \gets [[]]\)} \Comment{Construct matrix of inner products in high dimensional space}
@@
     \State{\(\vb{v} \gets \Omega\vb{\alpha} + \vb{1}_{m}b\)}
+    \State{\textbf{return} \(\vb{v}\)}
+    \EndProcedure{}
   \end{algorithmic}
@@
 The choice of kernel used to construct the kernel matrix is problem specific. Three kernels are most commonly used in SVMs. These kernels are:
-\begin{enumerate}
-  \item Linear Kernel
-
+\begin{numdesc}
+  \item[Linear Kernel]
   This kernel is the simplest with it being the dot product.
@@
   \end{equation}
-  \item Polynomial Kernel
+  \item[Polynomial Kernel]
 
@@
   \begin{equation}
-          K\left(\vb{x}_k,\vb{x}_l\right) = \left(\vb{x}_k\cdot\vb{x}_l+c\right)^{d} \label{eq:poly_kernel}
+    K\left(\vb{x}_k,\vb{x}_l\right) = {\left(\vb{x}_k\cdot\vb{x}_l+c\right)}^{d} \label{eq:poly_kernel}
   \end{equation}
-  \item Radial Basis Function Kernel
+  \item[Radial Basis Function Kernel]
 
@@
   \end{equation}
-\end{enumerate}
+\end{numdesc}
 
@@
 The metrics we discuss here are:
-\begin{enumerate}
-  \item MSE and RMSE
-
+\begin{numdesc}
+  \item[MSE and RMSE]
   The Mean Squared Error (MSE) and its root RMSE, are both very popular metrics.
@@
 This makes the MSE and RMSE very useful.
-  \item MAE
-
+  \item[MAE]
   The second metric is the MAE\@. This metric is calculated as the mean of the absolute differences between the prediction and the target. The MAE is calculated as shown in \lccref{eq:mae}.
@@
 Due to the use of the absolute value, the minimum value of the metric is also zero.
-  \item R\textsuperscript{2}
-
+  \item[R\textsuperscript{2}]
   The third metric is the coefficient of determination.
@@
   \begin{equation}
-          r2 = 1 - \frac{\sum_{i=1}^{n}(y_{i} - y'_{i})^{2}}{\sum_{i=1}^{n}(y_{i} - \bar{y})^{2}}\label{eq:r2}
+    {R}^{2} = 1 - \frac{\sum_{i=1}^{n}{(y_{i} - y'_{i})}^{2}}{\sum_{i=1}^{n}{(y_{i} - \bar{y})}^{2}}\label{eq:r2}
   \end{equation}
@@
 Scores below zero mean that the predictions are worse than the average value.
-  \item sMAPE
-
+  \item[sMAPE]
   The final metric is the symmetric Mean Absolute Percentage Error.
@@
   \begin{equation}
-          sMAPE = \frac{2}{N} \sum_{i=1}^{N}\frac{\abs{e_{i}}}{\max(\abs{y_{i}} + \abs{y'_{i}},\epsilon)}
+    sMAPE = \frac{2}{N} \sum_{i=1}^{N}\frac{\abs{e_{i}}}{\max(\abs{y_{i}} + \abs{y'_{i}},\epsilon)}\label{eq:smape}
   \end{equation}
@@
 
-\end{enumerate}
+\end{numdesc}
 

### 2025-01-16 skripsi/chapter3.tex
fix fourier derivatives with periods, fix typos in cover, change judul to lower case and add title case variant, add toc, tof, tot, toa to table of contents, fix font issue with mathptmx, add statement of originality, remove list of notation (for now), fix incorrect statement about burgers eq in ch2, fix sattelite coverage image caption too long, move burgers eq exact solution to ch2, fix figure positioning H not h, reword future work
add revisions file, fix chapter headings, fix numbered enumerate lists bodyless heading like on the explanation of the research design, fix reasonable chktex and

@@
 
-\begin{figure}[h]
+\begin{figure}[H]
       \centering
@@
 The study is carried out in 9 main phases. Each phase has a specific aim to accomplish such that the subsequent phases are able to proceed. Each phase is explained as follows:
-
-\begin{enumerate}
-      \item Problem Specification
-
+\begin{numdesc}
+      \item[Problem Specification]
       In this phase, relevant literature of related works and other supporting materials will be reviewed to lay the groundwork of this study.
@@
 
-      \item Design of Computational Model
-
+      \item[Design of Computational Model]
       This phase of the study is allocated to the design of the computational model based on the literature that has been reviewed.
@@
 
-      \item Implementation of Computational Model
-
+      \item[Implementation of Computational Model]
       After the computational model design is completed, the model is implemented in the Python Language using the PyTorch library as a core component.
@@
 
-      \item Planning of Experimental Scenarios
-
+      \item[Planning of Experimental Scenarios]
       To properly gauge the performance of the proposed method at approximating operators, specifically the solution operator of partial differential equations, experimental scenarios are developed in this phase.
@@
 
-      \item Data Generation and Retrieval
-
+      \item[Data Generation and Retrieval]
       This phase of the study is tied to the experimental scenarios that have been developed.
@@
 
-      \item Data Preprocessing
-
+      \item[Data Preprocessing]
       The next phase after data generation or retrieval is preprocessing.
@@
 
-      \item Experiments
-
+      \item[Experiments]
       This phase of the study executes the experimental scenarios that was determined previously. The preprocessed data will be used in accordance to the preplanned scenarios.
 
-      \item Analysis and Discussion
-
+      \item[Analysis and Discussion]
       The final phase of the study is the analysis and discussion of the results.
@@
 This will show how the model performs differently compared to the baseline.
-\end{enumerate}
+\end{numdesc}
 
@@
 This development model was adapted from \textcite{bittnerManagingIterativeSoftware2006}. Each process in the model is explained as follows:
-\begin{enumerate}
-      \item Initial Planning
-
+\begin{numdesc}
+      \item[Initial Planning]
       The first process of the iterative development model sets up the parameters for the iterative development.
@@
 
-      \item Requirements
-
+      \item[Requirements]
       This process separates out the backlog of requirements into those that will be worked on in the current iteration.
@@
 
-      \item Analysis and Design
-
+      \item[Analysis and Design]
       This process an analysis of the requirements of the current iteration is performed.
@@
 
-      \item Implementation
-
+      \item[Implementation]
       The implementation process applies the design that has been produced.
@@
 
-      \item Testing and Evaluation
-
+      \item[Testing and Evaluation]
       Once the design is implemented, tests that have been created are run.
@@
 
-      \item Release
-
+      \item[Release]
       After an iteration, the current version of the software is released.
 The iterative nature of this development model necessitates the use of a versioning system.
-As such each release can be identified by a version number loosely based on semantic versioning \autocite{preston-wernerSemanticVersioning200}.
+As such each release can be identified by a version number loosely based on semantic versioning \autocite{preston-wernerSemanticVersioning2002023}.
 This version numbering system consists of major number that indicates breaking changes, minor numbers which indicate features and non-breaking changes, and lastly patch numbers are used for fixes.

### 2025-01-16 skripsi/chapter4.tex
fix labels, fix problem with graphics path and suround with curly braces, start technical document
add revisions file, fix chapter headings, fix numbered enumerate lists bodyless heading like on the explanation of the research design, fix reasonable chktex and lacheck complaints

@@
 \end{figure}
-
+% ignore chktex warnings about the URLs
 The specific dataset resolution we use is 64 by 32 representing longitude and latitude respectively.
@@
   \end{subfigure}
-  \caption{Data retrieved:(\subref{fig:wb2_train_data}) 2-meter temperature at January 1, 1995 6:00 UTC\@.
+  \caption{Data retrieved: (\subref{fig:wb2_train_data}) 2-meter temperature at January 1, 1995 6:00 UTC\@.
 (\subref{fig:wb2_clim_data}) 2-meter temperature climatology for the first day of the year at hour 6 UTC\@.
@@
 The explanation of each module are as follows:
-\begin{enumerate}
-  \item Utilities
-
-        \noindent This module provides basic tools that are used across the entire library.
+\begin{numdesc}
+  \item[Utilities]
+  This module provides basic tools that are used across the entire library.
 The utilities this module needs to provide include scaling, conversion between real and complex representations of matrices, resizing coefficient tensors, and adaptors for or the traditional ordinary differential equation solvers.
@@
 
-  \item Basis Functions
-
-        \noindent As the proposed model will learn the relationships defined by PDEs within the spectral domain, a large proportion of the computation will also concern the use of the basis functions themselves.
+  \item[Basis Functions]
+  As the proposed model will learn the relationships defined by PDEs within the spectral domain, a large proportion of the computation will also concern the use of the basis functions themselves.
 The module will define the functionality and data structure that is expected to be used when working with basis functions in this library.
@@
 
-  \item Model
-
-        \noindent The proposed SpectralSVR model is implemented in this module.
+  \item[Model]
+  The proposed SpectralSVR model is implemented in this module.
 As the proposed model essentially wraps a support vector regression model in such a way that it can process coefficients, this module will house the SpectralSVR wrapper itself and the LSSVR variant of support vector regression that is used in this study.
@@
 
-  \item Problems
-
-        \noindent This module provides the functionality concerned with generating data.
+  \item[Problems]
+  This module provides the functionality concerned with generating data.
 Two out of the three datasets in this study are generated with this module.

### 2025-01-16 skripsi/chapter5.tex
fix labels, fix problem with graphics path and suround with curly braces, start technical document
add revisions file, fix chapter headings, fix numbered enumerate lists bodyless heading like on the explanation of the research design, fix reasonable chktex and lacheck complaints

@@
 This is done with a computational model that with four phases which are data preparation, data transformation, model training, and finally model evaluation.
-    \item Interpretation of the proposed model can be done to a certain extent using two tools which are the correlation image and p-matrix developed by \textcite{ustunVisualisationInterpretationSupport2007}.
-    \item The proposed model is also capable in dealing with noise and partial data as shown in scenario 1 and 3.
+    \item Interpretation of the proposed model can be done to a certain extent using two tools which are the correlation image and p-matrix developed by \textcite{ustunVisualisationInterpretationSupport2007}.\@\item The proposed model is also capable in dealing with noise and partial data as shown in scenario 1 and 3.
     \item The model's capabilities are also verified using exact solution. This revealed that for some configurations the model is able to successfully generalize to exact solutions.

### 2025-01-16 skripsi/chapter1.tex
add outline to ch1

@@
 
-% \section{Sistematika Penulisan}
+\section{Outline}
+\noindent This thesis will be structured into five chapters with this chapter being the first.
+For further detail, \lccref{sec:literature_review} will discuss and summarize the literature related to this study.
+The context of the study will be explained in terms of the state of the art (SoTA), the literature involved, and how this problem fits within the larger computing and physical sciences field.
+In \lccref{sec:research_methodology}, we discuss the methodology that is used in this study to achieve the aims that were set in the first chapter.
+And then, the results of applying the research methodology are presented in \lccref{sec:results_and_discussion}.
+In this section, the results are also analyzed and discussed.
+Finally, in \lccref{sec:conclusions_and_future_work} we draw conclusions from the results and future directions of research for the use of SVMs in operator learning with basis functions.
 % \noindent Bagian ini adalah penutup Bab I yang menyampaikan  secara ringkas isi setiap  bab.

### 2025-01-16 skripsi/chapter4.tex
add outline to ch1

@@
 % !TEX root = ./skripsi.tex
-\chapter{RESULTS AND DISCUSSION}
-\noindent This chapter will elaborate on the results of the study and relevant phases for analysis.
-This chapter is organized into five sections which are the results of data generation, data retrieval, design of computational model, implementation of computational model, experimental scenarios, and the experiments themselves.
+\chapter{RESULTS AND DISCUSSION}\label{sec:results_and_discussion}
+\noindent This chapter is organized into five sections which are the results of data generation, data retrieval, design of computational model, implementation of computational model, experimental scenarios, and the experiments themselves.
 

### 2025-01-18 skripsi/chapter2.tex
add outline to ch1
add literature map

@@
 % !TEX root = ./skripsi.tex
-\chapter{LITERATURE REVIEW}
-\noindent This chapter will discuss and summarize the literature related to this study.
-The context of the study will be explained in terms of the state of the art (SoTA), the literature involved, and how this problem fits within the larger computing and physical sciences field.
+\chapter{LITERATURE REVIEW}\label{sec:literature_review}
 % \noindent Bab ini mengulas secara rinci konsep-konsep dasar yang berkaitan dengn pekerjaan penelitian TA dan deskripsi studi pustaka yang dilakukan.
@@
 Demikian halnya dengan judul sub bab.
-
+\begin{figure}[H]
+  \begin{adjustwidth}{-0.1\linewidth}{-0.1\linewidth}
+  \centering
+    \tikzfig{figures/literature_map}
+  \end{adjustwidth}
+  \caption{Literature Map}\label{fig:literature_map}
+\end{figure}
+The topics this literature review will cover in this chapter is shown in \lccref{fig:literature_map}.
+There are four main topics which are governing equations, Fourier transform and series, machine learning regression, and relevant works to this study.
+These topics will be discussed in the following sections.
 \section{Governing Equations}
@@
 The features and all other benefits of both Python and PyTorch, allow for rapid prototyping and is conducive to research projects.
-The community means help is also not far away.
-% Mean Squared Error (MSE & RMSE)
-% Mean Absolute Error (MAE)
-% Coefficient of Determination (R\textsuperscript{2})
-% Symmetric Mean Absolute Percentage Error (sMAPE)
 

### 2025-01-23 skripsi/apendix.tex
fix fourier derivatives with periods, fix typos in cover, change judul to lower case and add title case variant, add toc, tof, tot, toa to table of contents, fix font issue with mathptmx, add statement of originality, remove list of notation (for now), fix incorrect statement about burgers eq in ch2, fix sattelite coverage image caption too long, move burgers eq exact solution to ch2, fix figure positioning H not h, reword future work
fix labels, fix problem with graphics path and suround with curly braces, start technical document
add revisions file, fix chapter headings, fix numbered enumera

@@
 % Example computation
-In this example we will be using the function \(2x^2+4\). The values of this function can be seen in \lccref{table:1}.
+In this example we will be using the function \(2x^2+4\). The values of this function can be seen in \lccref{table:lssvr_example_function_values}.
 
@@
 \end{table}
-For \(\Omega_{i,j}=K(x_i,x_j)=exp \left(-\frac{\norm*{x_i-x_j}^2}{2\sigma^2}\right)\)
+For \(\Omega_{i,j}=K(x_i,x_j)=\exp\left(-\frac{\norm*{x_i-x_j}^2}{2\sigma^2}\right)\)
 
-For example, with \(\sigma=1\), \(x_i=0.0\), \& \(x_j = 0.33\dots\)
+For example, with \(\sigma=1\), \(x_i=0.0\), \& \(x_j = 0.33\dots \)
 \begin{equation}
   \begin{split}
-    K(0.0,0.33) & = \exp\left(-\frac{\norm*{0.0-0.33}^2}{2(1)^2}\right) \\
+    K(0.0,0.33) & = \exp\left(-\frac{\norm*{0.0-0.33}^2}{2{(1)}^2}\right) \\
                 & = \exp\left(-\frac{0.33^2}{2}\right)                  \\
@@
 
+\chapter{BURGERS' EQUATION COMPARISON}\label{sec:burgers_comparison}
+Comparison of SpectralSVR against the Method of Lines with finite differences. The numerical methods used for comparison are lsoda and Implicit Adams-Bashforth-Moulton methods.
+\begin{figure}[H]
+  \centering
+  \begin{adjustwidth}{-0.05\linewidth}{-0.05\linewidth}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_model_pred_0.0.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR prediction.}\label{fig:comp_model_pred_0.0}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_model_diff_0.0.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR difference with target.}\label{fig:comp_model_diff_0.0}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_spo_pred_0.0.pgf}
+      \end{adjustbox}
+      \caption{SciPy \& NumPy prediction.}\label{fig:comp_spo_pred_0.0}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_spo_diff_0.0.pgf}
+      \end{adjustbox}
+      \caption{SciPy \& NumPy difference with target.}\label{fig:comp_spo_diff_0.0}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_tdo_pred_0.0.pgf}
+      \end{adjustbox}
+      \caption{torchdiffeq \& PyTorch prediction.}\label{fig:comp_tdo_pred_0.0}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_tdo_diff_0.0.pgf}
+      \end{adjustbox}
+      \caption{torchdiffeq \& PyTorch difference with target.}\label{fig:comp_tdo_diff_0.0}
+    \end{subfigure}
+  \end{adjustwidth}
+  \caption{Comparison of our model (SpectralSVR) and numerical methods for the Forced Burgers equation with viscosity \(\nu=0.0\).}\label{fig:comparison_burgers_0.0}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \begin{adjustwidth}{-0.05\linewidth}{-0.05\linewidth}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_model_pred_0.01.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR prediction.}\label{fig:comp_model_pred_0.01}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_model_diff_0.01.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR difference with target.}\label{fig:comp_model_diff_0.01}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_spo_pred_0.01.pgf}
+      \end{adjustbox}
+      \caption{SciPy \& NumPy prediction.}\label{fig:comp_spo_pred_0.01}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_spo_diff_0.01.pgf}
+      \end{adjustbox}
+      \caption{SciPy \& NumPy difference with target.}\label{fig:comp_spo_diff_0.01}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_tdo_pred_0.01.pgf}
+      \end{adjustbox}
+      \caption{torchdiffeq \& PyTorch prediction.}\label{fig:comp_tdo_pred_0.01}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_tdo_diff_0.01.pgf}
+      \end{adjustbox}
+      \caption{torchdiffeq \& PyTorch difference with target.}\label{fig:comp_tdo_diff_0.01}
+    \end{subfigure}
+  \end{adjustwidth}
+  \caption{Comparison of our model (SpectralSVR) and numerical methods for the Forced Burgers equation with viscosity \(\nu=0.01\).}\label{fig:comparison_burgers_0.01}
+\end{figure}
+\begin{table}
+  \caption{Metrics for predicting the exact solution for SpectralSVR (Ours) method}\label{table:comparison_exact_metrics_model}
+  \centering
+  \begin{tabular}{lcccc}
+    \toprule
+    \(\nu \) & MSE  & RMSE & MAE  & sMAPE \\
+    \midrule
+    0.0      & 0.01 & 0.07 & 0.06 & 1.99  \\
+    0.01     & 0.00 & 0.07 & 0.06 & 1.61  \\
+    0.1      & 0.00 & 0.02 & 0.02 & 1.47  \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+\begin{table}
+  \caption{Metrics for predicting the exact solution for the lsoda method}\label{table:comparison_exact_metrics_lsoda}
+  \centering
+  \begin{tabular}{lcccc}
+    \toprule
+    \(\nu \) & MSE  & RMSE & MAE  & sMAPE \\
+    \midrule
+    0.0      & 0.00 & 0.00 & 0.00 & 0.00  \\
+    0.01     & 0.00 & 0.00 & 0.00 & 0.09  \\
+    0.1      & 0.00 & 0.03 & 0.02 & 1.56  \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+\begin{table}
+  \caption{Metrics for predicting the exact solution for the IABM method}\label{table:comparison_exact_metrics_iabm}
+  \centering
+  \begin{tabular}{lcccc}
+    \toprule
+    \(\nu \) & MSE  & RMSE & MAE  & sMAPE \\
+    \midrule
+    0.0      & 0.00 & 0.00 & 0.00 & 0.00  \\
+    0.01     & nan  & nan  & nan  & nan   \\
+    0.1      & nan  & nan  & nan  & nan   \\
+    \bottomrule
+  \end{tabular}
+\end{table}
 % \section{PROGRAM SATU}

### 2025-01-23 skripsi/chapter1.tex
add literature map
add discussion, add comparison, change conclusion, revise future work

@@
     \item A novel use LSSVR which has a convex objective to learn solution operators of partial differential equations and operators in general.
-    \item Interpretation of machine learning model trained on operator data.
+    \item Faster time to solution compared to conventional methods provided by widely used libraries like SciPy.
+    \item Interpretable machine learning model trained on operator data.
 \end{enumerate}
@@
 \noindent This thesis will be structured into five chapters with this chapter being the first.
-For further detail, \lccref{sec:literature_review} will discuss and summarize the literature related to this study.
+For further detail on the topics relevant to this study, \lccref{sec:literature_review} will discuss and summarize the related literature.
 The context of the study will be explained in terms of the state of the art (SoTA), the literature involved, and how this problem fits within the larger computing and physical sciences field.

### 2025-01-23 skripsi/chapter4.tex
add discussion, add comparison, change conclusion, revise future work

@@
     Scaling                          & Standard scaling                                    & Standard scaling                                                                                      & Standard scaling                             \\\addlinespace[0.5em]
-    Dataset Split                    & 80\% Training and 20\% Testing for each noise level & 80\% Training and 20\% Testing for each viscosity value             & 80\% Training and 20\% Testing             \\\addlinespace[0.5em]
+    Dataset Split                    & 80\% Training and 20\% Testing for each noise level & 80\% Training and 20\% Testing for each viscosity value                                               & 1995{-}2013 Training and 2020{-}2022 Testing \\\addlinespace[0.5em]
     Regularization Parameter (\(C\)) & 1.0                                                 & 1.0                                                                                                   & 1.0                                          \\\addlinespace[0.5em]
     Kernel                           & RBF (\(\sigma = features \times X.var()\))          & RBF (\(\sigma = features \times X.var()\))                                                            & RBF (\(\sigma = features \times X.var()\))   \\\addlinespace[0.5em]
-    Additional Tests                 & Exact solutions                                     & Exact solutions                                                     &                                            \\\addlinespace[0.5em]
+    Additional Tests                 & Exact solutions and Inverse Problem                 & Exact solution in \cref{eq:burgers_exact_solution} and in initial value problem formulation (rollout) &                                              \\\addlinespace[0.5em]
+    Comparisons                      &                                                     & Method of Lines with FDM in space                                                                     &                                              \\\addlinespace[0.5em]
+    Machine                          & Local CPU                                           & Local CPU                                                                                             & Kaggle CPU                                   \\\addlinespace[0.5em]
     Interpretation                   & p-matrix and correlation image                      & p-matrix and correlation image                                                                        & p-matrix and correlation image               \\
@@
 The model for each viscosity will be used to predict \lccref{eq:burgers_exact_solution} from initial conditions at time equals zero and the corresponding forcing term of a constant value of zero.
-The exact equation prediction will be done using a rollout method.
-The initial condition along with the initial forcing term will be given to the model to predict the solution at the first time step.
-The model will then use the predicted solution with the forcing term at the first time step to predict the solution at the second time step.
+The exact equation prediction will be done using a initial value problem formulation, also described as a rollout.
+The initial solution value along with the forcing term will be given to the model to predict the solution at the first time step.
+The model will then use the predicted solution with the forcing term to predict the solution at the second time step.
 This is repeated until the stopping condition of time \(t=10\).
 The forcing term for the exact solution is a constant zero.
-Along with the rollout of the exact solution, we also perform roll out on one of the test solution.
+In addition to the rollout of the exact solution, we also perform rollout on of the test set.
+This will be done in comparison to traditional numerical methods, namely the commonly used method of lines in time using SciPy and torchdiffeq and finite differences in space with NumPy gradient and PyTorch gradient respectively.
+Specifically, the SciPy odeint function uses lsoda from the FORTRAN library odepack.
+And, the torchdiffeq version will use Implicit Adams-Bashforth-Moulton (IABM) method.
+Both of these were chosen for their availability for use in Python and therefore the kind of numerical solver one could set up with relative reliability.
 
@@
 \subsection{Scenario 1}
-\noindent The first scenario results are presented in four parts.
+\noindent The scenario is implemented as a Jupyter notebook which imports relevant libraries and our SpectralSVR library.
+The notebook starts with creating the data with the Antiderivative problem subclass.
+All random processes use the same PyTorch Generator instance with a seed of 42.
+The data is then augmented by perturbing the function values to create three versions with the noise levels mentioned in the scenario.
+Looping through each version, the training and testing subsets are randomly sampled to result in 80\% and 20\% of the original dataset respectively.
+Then the scaling function is fitted on the training subset inputs.
+And then, both the training and testing inputs are transformed using the fitted scaling function.
+Next, an instance of SpectralSVR is trained and tested.
+Finally, the metrics are stored and the next noise level is processed.
+
+The kernel scaling hyperparameter sigma has the same value of 10 for all noise levels.
+This is because the inputs are all scaled to approximately have a standard deviation of one.
+The value itself is from the number of features which comes out to 100 total inputs to the LSSVR\@.
+This was multiplied with the average standard deviation of all features across samples of 1 and then squared to get our current scaling hyperparameter value of 10.
+
+The first scenario results are presented in four parts.
 The first is the coefficient prediction metrics which is shown in \lccref{table:scenario_1_spectral_metrics}.
 The table shows the noise level and the performance metrics.
+Focusing on the coefficient of determination (R\textsuperscript{2}) scores, we can see that the model is off by 0.04 to the perfect score of 1.0 for the lowest noise level.
+For higher noise levels, the model performance gets worse with the R\textsuperscript{2} score of 0.5 for the highest noise level.
 \begin{table}[H]
@@
 
-The scenario is implemented as a Jupyter notebook which imports relevant libraries and our SpectralSVR library.
-The notebook starts with creating the data with the Antiderivative problem subclass.
-All random processes use the same PyTorch Generator instance with a seed of 42.
-The data is then augmented by perturbing the function values to create three versions with the noise levels mentioned in the scenario.
-Looping through each version, the training and testing subsets are randomly sampled to result in 80\% and 20\% of the original dataset respectively.
-Then the scaling function is fitted on the training subset inputs.
-And then, both the training and testing inputs are transformed using the fitted scaling function.
-Next, an instance of SpectralSVR is trained and tested.
-Finally, the metrics are stored and the next noise level is processed.
-Next the 5\% noise model is used to predict the antiderivative of a sine function.
-
-The kernel scaling hyperparameter sigma has the same value of 10 for all noise levels.
-This is because the inputs are all scaled to approximately have a standard deviation of one.
-The value itself is from the number of features which comes out to 100 total inputs to the LSSVR\@.
-
-\Cref{table:scenario_1_spectral_metrics} shows that the model is able to generalize from the training data and learn the simple linear antiderivative operator.
-Focusing on the coefficient of determination (R\textsuperscript{2}) scores, we can see that the model is off by 0.04 to the perfect score of 1.0 for the lowest noise level.
-While increasing noise levels does degrade the performance, this is partly due to the target values also having been perturbed.
-This fact can be seen if we look at how predictions from the very same trained models on noisy inputs are compared to the noise-free versions of the antiderivative functions which is shown in \lccref{table:scenario_1_clean_spectral_metrics}.
-The metrics show that the model predictions are slightly closer to the unperturbed function coefficients compared to the perturbed versions.
-This can be seen as the influence of the independent synthetic measurement noise in the perturbed targets being removed from the testing metrics.
-
-The higher noise levels shows that the model is still relatively accurate.
-Looking at the R\textsuperscript{2} score for the 50\% noise level, the model is more accurate than a baseline mean value model.
-The R\textsuperscript{2} score of 0.5 means that the model predictions has roughly half the error the baseline would produce.
+The metrics against the non perturbed values are shown in \lccref{table:scenario_1_clean_spectral_metrics}.
+The results show that the model performs best with lower noise levels, with the highest R\textsuperscript{2} value of 0.96 achieved at noise of 5\% average function value standard deviation.
+Higher noise levels sees the model performing worse with an R\textsuperscript{2} value of 0.62 at the highest noise level.
 
@@
 
-For the metrics between the predictions and the noise-free version of the target function values, the results parallel the outcomes of the coefficient predictions.
+For the metrics between the predictions and the noise-free version of the target function values shown in \lccref{table:scenario_1_clean_function_metrics}, the results parallel the outcomes of the coefficient predictions.
 The metrics show that the model performs slightly better with more pronounced differences for the higher noise levels.
-This echoes our previous statement on the effect of independent \enquote{measurement} noise in the target values on the evaluation metrics.
 \begin{table}[H]
@@
 Another observation is how the higher the noise level, the more the predicted functions become closer to zero.
-This is explained by the double penalty phenomenon \autocite{lledoScaledependentVerificationPrecipitation2023}.
-The loss function used for LSSVR penalizes the model for predicting a non-zero value that turns out to be wrong compared to predicting a zero value.
-This results in a model with predictions that are close to the mean of the training data.
 
@@
 For the highest noise level, the performance has degraded so far that the predictions are worse than a baseline model from the mean of the target input functions.
-One must also note that despite the much worse results of the other metrics for the highest noise level, at this time we're unable to explain why sMAPE results in roughly the same performance as in the forward problem.
 
@@
 
-The final observation we make is how for all the p-matrices the pronounced contribution of the input wave number to their corresponding output wave number.
-This means that the majority of contributions to each output coefficients come from the corresponding input coefficients of the same wave number.
-Our knowledge on how the simple derivative equation for Fourier series relate the coefficients of the derivative function and the antiderivative function is shown in \lccref{eq:derivative_coeff}.
-This aligns with the contributions shown by the p-matrices.
-This confirms that the model is indeed learning the relations that is defined by the derivative equation.
-
-In summary, the model is able to learn the linear relationship defined by the derivative equation.
-This is true even for high noise levels.
-The model also learns the actual relationship between each wave number which is shown in the p-matrix.
-Inverse prediction of the input function is also successfully done for lower noise levels.
-At high noise levels, the noise overwhelms the model.
-
 \subsection{Scenario 2}
@@
 Since there is too much data to fit into memory all at once at the end of this process, we randomly sample the feature and label pairs.
-This result in a maximum of 8000 samples for the training set and 2000 samples for the testing set.
+This result in a maximum of 8000 features and labels for the training set and 2000 features and labels from the testing set.
 As mentioned in \lccref{sec:data_transformation}, the training features are used to fit a scaling function.
@@
 The absolute metrics show that the models are performing several times worse in rollout compared to the single time step tests shown in \lccrefs{table:scenario_2_spectral_metrics,table:scenario_2_function_metrics}.
-This seems to be the same challenge that traditional solvers also face with the shocks that may be present with lower viscosity values.
-This means that for rollout scenarios, the model has a much harder time with lower viscosity values.
 \begin{table}[H]
@@
 \end{table}
-
 The exact function \cref{eq:burgers_exact_solution} is computed for each viscosity value.
@@
 The error stays to about half the maximum function value.
-We do see some more noticeable error in the flatter parts of the function.
-The error also take a very similar shape across the different viscosity values.
-Since we essentially used the same solutions for training the model for each viscosity, the similarity in error means that it can be alleviated with more diverse training samples.
-The error for the flatter functions may also be alleviated by including similar flatter functions during training.
 \begin{figure}[H]
@@
 For a higher viscosity of \(\nu=0.01\), a weaker correlation is still present.
+Once we get to the highest viscosity, while the order is still present, we see a more random arrangement of the correlation image values.
 
@@
 \end{figure}
-
-Once we get to the highest viscosity, while the order is still present, we see a more random arrangement of the correlation image values.
-This observation and the lower scores can both be explained by the level of temporal discretization.
-This is the same issue we encounter when we use some traditional methods for higher viscosity values with the same time step for lower viscosity values \autocite{kassamFourthOrderTimeSteppingStiff2005,seydaogluNumericalSolutionBurgers2016}.
-The issue arises in stiff differential equations.
-Stiff differential equations refer to the presence of a rapidly varying component.
-We can see that the larger amplitudes of high frequency components in the forcing term to represent the rapidly varying components as shown in \lccrefs{fig:burgers_forcing_0.0,fig:burgers_forcing_0.01,fig:burgers_forcing_0.1}.
-Traditionally, stiff equations would require specific numerical methods purpose built to efficiently solve the problem.
-Otherwise, the using a solver like FDM would require much finer time steps than the one we are using here.
 
@@
 For higher viscosity values, notice that the contribution of the previous solution increases.
-The increase is more pronounced for higher frequencies.
-This aligns with the quadratic scaling from the wave number on the coefficients \autocite{canutoSpectralMethodsEvolution2007}.
-The p-matrix for lower viscosity values show more structured contribution of other wave numbers in comparison to the higher wave numbers.
-This structure comes in the form of a grid pattern.
-For the real components of the output, the contribution of other wave numbers oscillate between higher and lower values depending on whether the input component is real or not.
-The imaginary output components on the other hand have a more constant contribution across the input components.
-The contribution once again become more pronounced the higher the absolute value of the wave number.
-
-To summarize, Low viscosity values are a challenge to the model as with traditional methods.
-Despite that, this scenario confirms the model's ability to learn the nonlinear relationship defined by the Burgers' equation.
-The model is also able to stay stable with a relatively large time step.
-This concludes the synthetic data portion of the study.
 
@@
 We also loose detail in areas which should have a lower anomaly such as northern areas of Africa, Greenland, and South Asia.
-The lack of detail seems to be a problem of underestimation.
-We believe this is caused by the so-called \enquote{double penalty} issue caused by the loss function used for the LSSVR \autocite{lledoScaledependentVerificationPrecipitation2023}.
-The predictions tend to be closer to the mean of the data to avoid the extra penalty from a wrong prediction with a high value.
-One way to allow for finer details that are less accurate is to penalize the higher frequency wave numbers less compared to the lower frequency wave numbers.
-For our case this means the LSSVR for each output will have their regularization parameter decreased to allow the model to focus less on the errors for higher frequencies.
 \begin{figure}[H]
@@
 Many sharp features are lost and the state prediction start to resemble averaged view of the climatology.
-We must also take into account that the model only used temperature distribution data.
-Other pieces of information we know to be crucial to weather prediction such as wind speed or pressure was not included in the inputs.
-With this in consideration the model was still able to learn some relationships defined by governing equations of weather.
-%TODO: decide to mention the results of this or not (https://sites.research.google/weatherbench/deterministic-scores/)
 \begin{figure}[H]
@@
 With the \enquote{flatness} we see, this is indicative of strong contributions by a few inputs.
-
 \begin{figure}[H]
@@
 In addition, the value of contribution differ by an order of magnitude with lower longitude wave numbers having higher maximum contribution.
-This observation suggests that the nonlinearity and magnitude are inversely proportional to the absolute value of the longitude wave number.
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/wb2_pm_zoom1.pgf}
+    \end{adjustbox}
+    \caption{The p-matrix zoomed in to \((k_{longitude}=\{0, 1, 2\}, k_{latitude}=[-16, 16))\).}\label{fig:sc3_pm_zoom1}
+  \end{subfigure}
+  \begin{subfigure}{\linewidth}
+    \begin{adjustbox}{width=\linewidth}
+      \input{figures/wb2_pm_zoom2.pgf}
+    \end{adjustbox}
+    \caption{The p-matrix zoomed in to \((k_{longitude}=\{\phantom{-}31,-32,\phantom{-}32\}, k_{latitude}=[-16, 16))\).}\label{fig:sc3_pm_zoom2}
+  \end{subfigure}
+  \caption{The p-matrix of the WeatherBench 2 models zoomed in to specific wave numbers.}\label{fig:sc3_pm_zoomed}
+\end{figure}
+
+\subsection{Comparisons}
+
+Next we present the results of comparing our model in for solving the IVP for the Burgers' Equation against the method of lines and finite differences using SciPy odeint, torchdiffeq odeint, NumPy gradient, and PyTorch gradient.
+First, we present the results of solving \lccref{eq:burgers_exact_solution} as an IVP as shown in \lccref{table:comparison_exact_metrics_0.1} for viscosity \(\nu=0.1\).
+For the forcing term, we use a constant value of zero.
+The functions are also unperturbed.
+The metrics measure the performace of the predicted solutions compared against the exact solution.
+We see that our model has slightly better performance compared to the lsoda method.
+We do want to note that for lower viscosity values the lsoda method performs much better compared to ours as shown in \lccref{sec:burgers_comparison}.
+And for the viscosity of \(\nu=0.0\), even the IABM method performs much better due to the fact that the solution is a constant value of zero.
+\begin{table}[H]
+  \caption{Metrics for predicting the exact solution for each method with viscosity \(\nu=0.1\)}\label{table:comparison_exact_metrics_0.1}
+  \centering
+  \begin{tabular}{lcccc}
+    \toprule
+    Method      & MSE  & RMSE & MAE  & sMAPE \\
+    \midrule
+    SpectralSVR & 0.00 & 0.02 & 0.02 & 1.47  \\
+    lsoda       & 0.00 & 0.03 & 0.02 & 1.56  \\
+    IABM        & nan  & nan  & nan  & nan   \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+For better visualization, the predictions and the difference against the exact solution is shown in \lccref{fig:comparison_burgers_exact_0.1}.
+We show that for our method and the lsoda method, the exact solution is achieved to a recognizable form.
+However, using the IABM method with torchdiffeq is ineffective and the solution \enquote{blows up} and results in many not a number values.
+Our method has errors characterized by lines which stems form our use of only eight basis functions to represent solution.
+This is in contrast to the error of the lsoda method, which is spread over larger areas.
+\begin{figure}[H]
+  \centering
+  \begin{adjustwidth}{-0.05\linewidth}{-0.05\linewidth}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_exact_model_pred_0.1.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR prediction.}\label{fig:comp_exact_model_pred_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_exact_model_diff_0.1.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR difference with target.}\label{fig:comp_exact_model_diff_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_exact_spo_pred_0.1.pgf}
+      \end{adjustbox}
+      \caption{SciPy \& NumPy prediction.}\label{fig:comp_exact_spo_pred_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_exact_spo_diff_0.1.pgf}
+      \end{adjustbox}
+      \caption{SciPy \& NumPy difference with target.}\label{fig:comp_exact_spo_diff_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_exact_tdo_pred_0.1.pgf}
+      \end{adjustbox}
+      \caption{torchdiffeq \& PyTorch prediction.}\label{fig:comp_exact_tdo_pred_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_exact_tdo_diff_0.1.pgf}
+      \end{adjustbox}
+      \caption{torchdiffeq \& PyTorch difference with target.}\label{fig:comp_exact_tdo_diff_0.1}
+    \end{subfigure}
+  \end{adjustwidth}
+  \caption{Comparison of our model (SpectralSVR) and numerical methods for the exact solution in \cref{eq:burgers_exact_solution} of the Forced Burgers equation with viscosity \(\nu=0.1\).}\label{fig:comparison_burgers_exact_0.1}
+\end{figure}
+
+The predictions for IVP rollout of the functions in the test set is shown in \lccrefs{fig:comparison_burgers_0.1} for viscosity \(\nu=0.1\).
+Other viscosity values were also compared and presented in \lccrefs{fig:comparison_burgers_0.0,fig:comparison_burgers_0.01}.
+An obvious observation is the fact that the numerical methods fail to solve the entire solution.
+The SciPy odeint version is able to solve up until the 13th iteration or time \(t=0.6533\).
+The torchdiffeq version on the other hand only solves up until the second iteration.
+Even at this early step, the solution is already unstable with many values having an order of larger than \num{10e10}.
+\begin{figure}[H]
+  \centering
+  \begin{adjustwidth}{-0.05\linewidth}{-0.05\linewidth}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_model_pred_0.1.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR prediction.}\label{fig:comp_model_pred_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_model_diff_0.1.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR difference with target.}\label{fig:comp_model_diff_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_spo_pred_0.1.pgf}
+      \end{adjustbox}
+      \caption{SciPy \& NumPy prediction.}\label{fig:comp_spo_pred_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_spo_diff_0.1.pgf}
+      \end{adjustbox}
+      \caption{SciPy \& NumPy difference with target.}\label{fig:comp_spo_diff_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_tdo_pred_0.1.pgf}
+      \end{adjustbox}
+      \caption{torchdiffeq \& PyTorch prediction.}\label{fig:comp_tdo_pred_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_tdo_diff_0.1.pgf}
+      \end{adjustbox}
+      \caption{torchdiffeq \& PyTorch difference with target.}\label{fig:comp_tdo_diff_0.1}
+    \end{subfigure}
+  \end{adjustwidth}
+  \caption{Comparison of our model (SpectralSVR) and numerical methods for a manufactured solution of the Forced Burgers equation with viscosity \(\nu=0.1\).}\label{fig:comparison_burgers_0.1}
+\end{figure}
+
+In terms of efficiency, we also present our measurements of the time it took for each method to solve the exact solution IVP using the \verb|%timit| macro in Jupyter Notebook.
+This was done on our machine without any hardware accelerators such as GPUs.
+The time was averaged over 7 measurements.
+The results are shown in \lccref{table:comparison_efficiency}.
+Our method solves this problem the fastest by around 33 times faster than the lsoda method.
+\begin{table}[H]
+  \caption{Average time elapsed in solving for \lccref{eq:burgers_exact_solution} by method.}\label{table:comparison_efficiency}
+  \centering
+  \begin{tabular}{lc}
+    \toprule
+    Method      & Time Elapsed               \\
+    \midrule
+    SpectralSVR & \textbf{0.431 s ± 0.122 s} \\
+    lsoda       & 12.1 s ± 2.62 s            \\
+    IABM        & 15.7 s ± 1.85 s            \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\section{Discussion}\label{sec:discussion}
+
+\noindent Here we will discuss the results of the three scenarios.
+The first goal of the three scenarios is to show that the model is capable of predicting the correct outputs given challenges of the data such as noise, nonlinearity, stiffness, and incomplete data.
+The results show that the model is able to learn effectively the relationships of equations in our scenarios embedded in data.
+On the question of noise, \lccref{table:scenario_1_spectral_metrics} shows that the model is able to generalize from the training data and learn the simple linear antiderivative operator.
+While increasing noise levels does degrade the performance, this is partly due to the target values also having been perturbed.
+This fact can be seen if we look at how predictions from the very same trained models on noisy inputs are compared to the noise-free versions of the antiderivative functions as shown in \lccrefs{table:scenario_1_spectral_metrics,table:scenario_1_clean_spectral_metrics}.
+The metrics show that the model predictions are slightly closer to the unperturbed function coefficients compared to the perturbed versions.
+This can be seen as the influence of the independent synthetic measurement noise in the perturbed targets being removed from the testing metrics.
+
+The higher noise levels shows that the model is still relatively accurate.
+Looking at the R\textsuperscript{2} score for the 50\% noise level, the model is more accurate than a baseline mean value model.
+The R\textsuperscript{2} score of 0.5 means that the model predictions has roughly half the error the baseline would produce.
+This is explained by the double penalty phenomenon \autocite{lledoScaledependentVerificationPrecipitation2023}.
+The loss function used for LSSVR penalizes the model for predicting a non-zero value that turns out to be wrong compared to predicting a zero value.
+This results in a model with predictions that are close to the mean of the training data.
+This is exemplified by \lccref{fig:antiderivative_exact} and our previous observation of the flatter solutions of higher noise levels.
+
+We also touch on the effectivity of the learned model as a surrogate in inverse problems in noisy conditions.
+Our results show that the model is capable of being a surrogate for parameter determination in lower noise levels.
+Higher noise levels show the model performing worse with the inverse predictions being worse than a mean value model.
+We believe the main contributing factor is the uneven contribution of input to output coefficients across wave numbers.
+This may exaggerate the gradients evaluated for different coefficients.
+Because of the difference in gradient sizes the optimizer we used could have more difficulty in higher noise levels \autocite{griffithsAchievingRobustnessAleatoric2022, ozbayramHeteroscedasticGaussianProcess2024,zhangImprovedAdamOptimizer2018}.
+To alleviate this, scaling the outputs to a similar standard deviation may be needed.
+This would balance the influence of the outputs and allow for easier optimization.
+
+On the topic of nonlinearity and stiffness, the results show that the model is also capable of learning nonlinear operators as shown in \lccrefs{table:scenario_2_spectral_metrics,table:scenario_2_function_metrics}.
+The increase of the viscosity, which corresponds to the stiffness or the high variability of a component in an equation, shows that the model's performance decrease with increasing stiffness.
+This problem is similar what one encounters in solving stiff equations using traditional methods like FDM\@.
+Stiff differential equations refer to the presence of a rapidly varying component.
+We can see that the larger amplitudes of high frequency components in the forcing term to represent the rapidly varying components as shown in \lccrefs{fig:burgers_forcing_0.0,fig:burgers_forcing_0.01,fig:burgers_forcing_0.1}.
+In those cases, specialized methods were developed to address the issue \autocite{kassamFourthOrderTimeSteppingStiff2005,seydaogluNumericalSolutionBurgers2016}.
+Otherwise, the using a solver like FDM would require much finer time steps such that it could become impractical.
+However, the stiffness does not affect our approach as bad as traditional approaches as it is still able to solve the Burgers' equation initial value problem at a relatively coarse time resolution as shown in \lccref{fig:scenario_2_rollout} and \lccref{table:scenario_2_rollout_function_metrics}.
+The initial value problem formulation actually highlights the fact that for this use case, the nonlinear term actually presents more of a problem compared to the stiffness.
+This seems to be the same challenge that traditional solvers also face with the shocks that may be present with lower viscosity values.
+
+If we look at the case for the initial value problem formulation of the exact equation shown in \lccref{fig:scenario_2_exact} and \lccref{table:scenario_2_exact_function_metrics}, another factor for better generalization of the model may be identified.
+If we focus on the flatter parts of the predicted solution, the error take a very similar shape across the different viscosity values.
+Since we essentially used the same solutions for training the model for each viscosity, the similarity in error means that it can be alleviated with more diverse training samples.
+Specifically for the error int the flatter functions may be reduced by including similar functions with flat areas during training.
+This would allow the model to avoid making similar errors.
+
+For the ERA 5 WeatherBench 2 dataset, our model is able to learn to predict the 2-meter temperature anomaly distribution for 6 hours in the future with only the current 2-meter temperature anomaly distribution as shown in \lccref{table:sc3_test_anomaly_metrics}.
+If we look at the predicted values, there is a lack of detail which seems to be a problem of underestimation.
+We believe this is caused by the so-called \enquote{double penalty} issue caused by the loss function used for the LSSVR \autocite{lledoScaledependentVerificationPrecipitation2023}.
+The predictions tend to be closer to the mean of the data.
+This is motivated to avoid the extra penalty from a wrong prediction with a high value.
+One way to allow for finer details that are less accurate is to penalize the higher frequency wave numbers less compared to the lower frequency wave numbers.
+For our case this means the LSSVR for each output will have their regularization parameter decreased to allow the model to focus less on the errors for higher frequencies.
+Another factor is the purposeful lack of other information that are crucial to higher detail such as wind speed.
+With this in consideration, the model is able to learn from partial data.
+
+For the second goal, which is whether the model is learning the correct relationships, we use the visualization tools by \textcite{ustunVisualisationInterpretationSupport2007} which are the correlation image and p-matrix.
+For the derivative equation, an observation we make is how for all the p-matrices shown in \lccref{fig:scenario_1_interpretation}, the contribution of the input wave number is pronounced for the corresponding output wave number.
+This means that the majority of contributions to each output coefficients come from the corresponding input coefficients of the same wave number or it's negative wave number counterpart as the complex conjugate.
+Our knowledge on how the simple derivative equation for Fourier series relate the coefficients of the derivative function and the antiderivative function is shown in \lccref{eq:derivative_coeff}.
+Our observations align with this knowledge.
+This confirms that the model is indeed learning the relations that is defined by the derivative equation.
+
+The p-matrix for the Burgers' equation on the other hand does not have the same straightforward relationship visualized as shown in \lccref{fig:scenario_2_interpretation}.
+Instead, the contribution of for each output coefficient is from multiple input coefficients.
+The contribution is more pronounced for higher frequencies.
+This aligns with the quadratic scaling from the wave number on the coefficients \autocite{canutoSpectralMethodsEvolution2007}.
+The p-matrix for lower viscosity values show more structured contribution of other wave numbers in comparison to the higher wave numbers.
+This structure comes in the form of a grid pattern.
+For the real components of the output, the contribution of other wave numbers alternate between higher and lower values depending on whether the input component is real or not.
+The imaginary output components on the other hand have a more constant contribution across the input components.
+The contribution once again become more pronounced the higher the absolute value of the wave number.
+
+Input coefficients of other wave numbers also significantly contribute to each output coefficient.
+If we take a look back to the relationship shown in \lccref{eq:burgers_convolution}, the nonlinear term corresponds to a convolution that sums the multiplication of each wave number against all wave numbers.
+This means that the contribution of multiple input wave numbers is the model trying to do something like the convolution.
+With this in contrast to the linear contribution we see for the derivative equation, we believe that the model has learned the nonlinear term correctly.
+However, because of the multiple terms in the Burgers' equation, and p-matrix representing the total of those terms, it is not possible to separate the contributions into each term.
+
+A different way these multiple inputs can contribute to the same output coefficient is demonstrated in scenario 3 with the 2-meter temperature data.
+The p-matrix shown in \lccrefs{fig:sc3_interpretation,fig:sc3_pm_zoomed} displays similar behavior to the p-matrix from the Burgers' equation.
+Here we see that largest contributor to each output coefficient, is the input coefficient of the same wave number.
+We also see contribution from other wave numbers.
+However, we can see that the pattern is very different.
+There are two possible reasons for this.
+First, similar to the Burgers' equation, there is a term in the governing equation that does convolution scaled by the closeness of each wave number to each other.
+Our observation of how higher longitude frequencies spread the contribution to more latitude frequencies compared to higher longitude frequency suggests that the nonlinearity and magnitude of contribution are inversely proportional to the absolute value of the longitude wave number.
 This is in contrast to when we discussed the forcing term for our Burgers' equation scenario.
-The low frequencies in longitude may indicate that the model has learned some feature of the anomaly that is specific to different times of day.
+The low frequencies in longitude may indicate that the model has learned some nonlinear feature of the anomaly that is specific to different times of day.
 This is because the lowest longitudinal wave number would correspond to when different parts of the world is in nighttime or in daytime.
-Other possible explanations may be due to the fact that the earth more closely resemble a sphere compared to the toroidal shape that the 2-dimensional Fourier transform assumes.
+The second plausible reason is the fact that our choice of basis functions are suboptimal \autocite{bonevSphericalFourierNeural2023,shenSpectralMethodsAlgorithms2011}.
+The earth more closely resemble a sphere compared to the toroidal shape that the 2-dimensional Fourier transform assumes.
 This would result in the representation latitude-wise being distorted.
 For this issue, the use of spherical harmonics may be a better fit to rule out the possibility of any distortions the Fourier transform may introduce.
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_pm_zoom1.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix zoomed in to \((k_{longitude}=\{0, 1, 2\}, k_{latitude}=[-16, 16))\).}\label{fig:sc3_pm_zoom1}
-  \end{subfigure}
-  \begin{subfigure}{\linewidth}
-    \begin{adjustbox}{width=\linewidth}
-      \input{figures/wb2_pm_zoom2.pgf}
-    \end{adjustbox}
-    \caption{The p-matrix zoomed in to \((k_{longitude}=\{\phantom{-}31,-32,\phantom{-}32\}, k_{latitude}=[-16, 16))\).}\label{fig:sc3_pm_zoom2}
-  \end{subfigure}
-  \caption{The p-matrix of the WeatherBench 2 models zoomed in to specific wave numbers.}\label{fig:sc3_pm_zoomed}
-\end{figure}
-
-The results of our experiments show that the proposed model has the ability to learn the relationships that PDEs and other governing equations define.
+
+In summary, the model is able to learn the linear relationship defined by the derivative equation and the nonlinear relationships characteristic of systems such as the weather and systems described by the Burgers' equation.
+This is true even for some levels of noise levels and stiffness.
+Interpreting the p-matrix, we explain how the model has learned the correct contribution of the input coefficients to each output coefficient based on the equations obtained using the spectral method.
 The interpretation methods for support vector regression that we used, namely the correlation image and p-matrix developed by \textcite{ustunVisualisationInterpretationSupport2007}, allows us to confirm what the model has learned.
 In the case of the WeatherBench2 model, it has also allowed us to glean some insight into some mechanisms that the model has learned.
-This information was used to verify the learned relationships for the simple derivative equation.
+This information was used to verify the learned relationships for the simple derivative equation and partially for the Burgers' equation.
 Together with the performance metrics on three different problems, we have shown the proposed model to be a viable tool for situations with limited knowledge and a need for some level of interpretability of the model.
+Our comparisons with the lsoda and IABM methods with FDM in space, also show how our model as being relatively stable and efficient for quickly computing solutions in comparison with grid-based traditional methods.
+This shows how the model can be used for many-query problems.
+As an example, inverse prediction of the function is done relatively well for lower noise levels.

### 2025-01-23 skripsi/chapter5.tex
add outline to ch1
add discussion, add comparison, change conclusion, revise future work

--- 2025-01-13 skripsi/chapter5.tex
@@
 % !TEX root = ./skripsi.tex
-\chapter{CONCLUSIONS AND FUTURE WORK}
+\chapter{CONCLUSIONS AND FUTURE WORK}\label{sec:conclusions_and_future_work}
 
 \section{Conclusion}
-\noindent Based on the results of the research into \MakeLowercase{\judul}, several conclusions can be drawn.
+\noindent Based on the results of the research into \MakeLowercase{\judul}, the following conclusions can be drawn:
 \begin{enumerate}
-    \item The proposed SpectralSVR model is able to learn the relationships defined by PDEs.
-This is done with a computational model that with four phases which are data preparation, data transformation, model training, and finally model evaluation.
+    \item The proposed SpectralSVR model is able to learn the relationships defined by PDEs in the spectral domain as an operator regression model.
+This is done with a computational model that with four phases which are data preparation, data transformation into the spectral domain and appropriate scale, model training of the LSSVR, and finally model evaluation by transforming the spectral results into the physical domain.
+    \item The proposed model's capabilities are verified using the derivative equation, the Burgers' equation, and the 2-meter temperature data from the ERA5 dataset.
+For more concrete verification, the model was tasked with and successfully solved problems based on exact analytical solutions to the derivative equation and the Burgers' equation.
+This revealed that for some configurations the model is able to successfully generalize to exact solutions.
+The model is able to work with some level of noise, with performance deteriorating with high levels of noise.
+Stiffness and nonlinearity can also be handled to an extent.
+And when solving IVPs, the model's solution converge and stays stable.
+The model's performance does suffer when the solution is a type of function that was not part of the training set.
     \item Interpretation of the proposed model can be done to a certain extent using two tools which are the correlation image and p-matrix developed by \textcite{ustunVisualisationInterpretationSupport2007}.
-    \item The proposed model is also capable in dealing with noise and partial data as shown in scenario 1 and 3.
-    \item The model's capabilities are also verified using exact solution. This revealed that for some configurations the model is able to successfully generalize to exact solutions.
+The p-matrix specifically can be used to reveal how the input coefficients contribute to the output coefficients.
+This allows the user to see the learned relationship similar to the spectral method with its equations of the solution in terms of the coefficients of parameters.
 \end{enumerate}
@@
 \begin{itemize}
-    % TODO: reword these points
     \item The synthetic data used in scenarios 1 and 2 were generated using MMS\@.
@@
 Incorporating more realistic data from traditional numerical methods or other sources could enhance the model's ability to predict more realistic solutions.
-    \item Test how the auto-regression of weather compares to the target data.
-    \item Compare inverse prediction results with traditional derivatives, such as the spectral method or FDM\@.
-    \item Compare the proposed method with other methods in comparable situations.
-    \item Measure and compare the efficiency (time) of computing solutions against traditional and machine learning-based methods.
-    \item Add more basis functions, such as spherical harmonics or wavelet bases.
-    \item Incorporate more regression models, specifically more support vector regression models, to continue utilizing the correlation image and p-matrix.
-    \item Use better metrics for measuring performance, such as the \enquote{standard error of regression}.
-    \item Analyze the performance with different hyperparameters or data sizes and present the results in charts.
-    \item Perform an analysis of the error by wave number.
-    \item Solve the problem of double penalties that cause the model to favor smooth solutions \autocite{brownForecastsSpatialFields2011,NIPS2017_44a2e080}.
-Try using stronger regularization (a higher regularization parameter) for higher wave numbers.
-    \item Add support for sparse data by employing data assimilation techniques, such as the Lomb-Scargle periodogram \autocite{vanderplasUnderstandingLombScargle2018}, and 4D-Var data assimilation \autocite{puNumericalWeatherPrediction2018,parkDataAssimilationAtmospheric2013}.
-    \item Study the contribution patterns for different terms in a PDE using the p-matrix or other methods.
+In addition, a more diverse set of training data would allow the model to better avoid errors like the prediction of the exact solution for the inviscid Burgers' equation.
+    \item For the 2-meter temperature data, we only measured how well the model performed in predicting the temperature for six hours in the future.
+Other works may be interested in measuring how well auto-regression of weather using this model compares to the target data.
+    \item Comparison of inverse prediction results with traditional methods, such as the Method of Regularization or iterative methods \autocite{groetschInverseProblemsMathematical1993,vogelComputationalMethodsInverse2002}.
+    \item Measure and compare the proposed model against other machine learning-based methods.
+    \item Different problems require other kinds of basis functions to be able to represent them well.
+For example, global weather prediction would benefit from using spherical harmonics \autocite{bonevSphericalFourierNeural2023}.
+Other problems such as seismic data would be better represented using wavelet bases \autocite{chakrabortyFrequencytimeDecompositionSeismic1995}.
+    \item The use better metrics for measuring performance, such as the \enquote{standard error of regression} as it may be inadequate for nonlinear cases \autocite{spiessEvaluationR2Inadequate2010}.
+    \item Our study focused on what the model learned and whether it is capable of doing operator regression.
+Further study into optimizing the model would be useful for problems like overcoming noise or stiffness.
+    \item Further insight into how the model performs, specifically in conditions that may induce the double penalty phenomenon would need to be undertaken for optimizing the model.
+This would include analyzing the error by wave number.
+Based on the information of error by wave number, the model can be tuned accordingly.
+For example, using stronger regularization (a higher regularization parameter) for higher wave numbers.
+    \item The current work is limited to smooth and dense functions.
+However, many data sources do not provide data with this property.
+Because of this, expanding the model's capability would require support for sparse data by employing data assimilation techniques, such as the Lomb-Scargle periodogram \autocite{vanderplasUnderstandingLombScargle2018}, and 4D-Var data assimilation \autocite{puNumericalWeatherPrediction2018,parkDataAssimilationAtmospheric2013}.
+    \item Deeper understanding of the relationship learned by the model would need separation of terms in how the input coefficients contribute to the output coefficients.
+This would require better visualization and interpretation tool than what is provided by the p-matrix.
+Another way to extend understanding is research into the relationship between the contribution values of the p-matrix and the equations from the spectral method.
 \end{itemize}

### 2025-01-24 skripsi/chapter1.tex
move operator learning to related works, update revision list, mention mathematical  guarantee of conventional numerical methods in comparison scenario

@@
     \item A novel use LSSVR which has a convex objective to learn solution operators of partial differential equations and operators in general.
-    \item Faster time to solution compared to conventional methods provided by widely used libraries like SciPy.
-    \item Interpretable machine learning model trained on operator data.
+    \item Faster time from parameter to solution compared to conventional methods provided by widely used libraries like SciPy.
+    \item Interpretable data-driven model for the mapping between spectral coefficients.
 \end{enumerate}

### 2025-01-24 skripsi/chapter2.tex
add discussion, add comparison, change conclusion, revise future work
move operator learning to related works, update revision list, mention mathematical  guarantee of conventional numerical methods in comparison scenario

@@
 
-\section{Operator Learning}
+\section{Related Works}
 \noindent Machine learning, as with many other fields, has found its foothold in scientific computing.
@@
 This allows the NN to be trained in a self-supervised setting.
-Another major model is the so called DeepONet architecture proposed by \textcite{luLearningNonlinearOperators2021}.
+
+Another paradigm is the so called DeepONet architecture proposed by \textcite{luLearningNonlinearOperators2021}.
 This model can be seen as foregoing the basis function the Fourier Transform enforces and instead learns the basis functions from the data \autocite{meurisMachinelearningbasedSpectralMethods2023}.
-Because of this, the model has two components.
+Because of this, the model has two component networks.
 The first, named the trunk network acts as the learned basis functions.
-This network is given evaluation coordinates and computes the values of the \enquote{basis functions}.
+This network is given evaluation coordinates and computes the values of the \enquote{basis functions} at said coordinates.
 The second network, called the branch network, learns the mapping between the input function representation and the coefficients for the output function.
@@
 This model enjoys the advantage of using one of the simplest forms of machine learning.
+
+The literature also further into the learned basis functions of DeepONet.
+In their study, \textcite{meurisMachinelearningbasedSpectralMethods2023} utilize the trained trunk network to extract custom basis functions.
+These can then be used in a spectral procedure like Fourier basis functions.
+These have been found to be more accurate than the DeepONet by itself.
+Building on a two-stage training process that was originally done to improve performance of DeepONets \autocite{leeTrainingGeneralizationDeep2024}, \textcite{peyvanRiemannONetsInterpretableNeural2024} uses the two-stage method to obtain the basis functions for their proposed RiemannONet.
+The basis functions that are obtained are also investigated.
+The authors also reveal the contribution of the hidden layers towards the final shape of the basis functions using Singular Value Decomposition (SVD).
+This interpretation allows the authors to see how different layer compositions affect the contributions toward the basis functions.
+These works extend the understanding of learned basis functions.
+However, to our knowledge at the time of writing, there has been no discussion on interpreting the learned mapping between spectral coefficients.
+The interpretability of this is crucial to better understand what the model actually learned in terms of the operator between solution and parameter functions.
 
@@
 This is called the Karush-Khun-Tucker optimality condition.
-Computing this for our Lagrangian results in \lccref{eq:lssvr_KKT}.
-\begin{equation}
-  \begin{split}
-    \pdv{L}{W} = 0 \rightarrow          & W           = & \sum_{k=1}^{n}\alpha_{k}\vb{x}_{k}                      \\
-    \pdv{L}{b} = 0 \rightarrow          & 0           = & \sum_{k=1}^{n}\alpha_{k}                                \\
-    \pdv{L}{e_{k}} = 0 \rightarrow      & \alpha_{k}  = & C e_{k}                            & \qquad k=1,\dots,n \\
-    \pdv{L}{\alpha_{k}} = 0 \rightarrow & y_{k}       = & W^{\intercal}\vb{x}_{k}+b+e_{k}    & \qquad k=1,\dots,n \\
-  \end{split}\label{eq:lssvr_KKT}
-\end{equation}
+Computing this for our Lagrangian results in \lccref{eq:lssvr_kkt}.
+\begin{subequations}
+  \begin{align}
+    \pdv{L}{W} = 0 \rightarrow          & W           = & \sum_{k=1}^{n}\alpha_{k}\vb{x}_{k}                      \label{eq:lssvr_kkt_w}                                             \\
+    \pdv{L}{b} = 0 \rightarrow          & 0           = & \sum_{k=1}^{n}\alpha_{k}                                \label{eq:lssvr_kkt_b}                                             \\
+    \pdv{L}{e_{k}} = 0 \rightarrow      & \alpha_{k}  = & C e_{k}                                                                        & \qquad k=1,\dots,n \label{eq:lssvr_kkt_e} \\
+    \pdv{L}{\alpha_{k}} = 0 \rightarrow & y_{k}       = & W^{\intercal}\vb{x}_{k}+b+e_{k}                                                & \qquad k=1,\dots,n \label{eq:lssvr_kkt_a}
+  \end{align}\label{eq:lssvr_kkt}
+\end{subequations}
 
@@
 If we generalize to multiple outputs, the result is a matrix with the rows representing input features and columns representing each output.
+For the linear kernel, this would essentially be the weight vector as shown in \lccref{eq:lssvr_kkt_w}.
+However, the relationship is more abstract when we apply to nonlinear kernels because the weight vector is then the Lagrangian multipliers multiplied by the inputs in feature space (higher dimension).
+This means if we multiply the Lagrangian multipliers with the inputs in its original form, the result we get a projection of the contributions of each feature on the output.
 
@@
 A simple mitigation can be done by filtering training samples with small absolute values of Lagrangian multipliers \autocite{haifengwangComparisonSVMLSSVM2005}.
-However, the benefits of simple matrix operations outweigh the disadvantages.
-This is because of the parallelization benefits of algorithms for simple matrix operations.
+Larger training sets would also mean that the model would need to compute through the kernel matrix which scales as \(n^2\).
+This means that for larger datasets, optimization strategies such as only computing relevant parts of the kernel matrix would become necessary.
+
+However, the benefits of using the LSSVM, such as simple matrix operations, outweigh the disadvantages.
+Specifically for the LSSVM compared to SVM with SMO, the model benefits from parallelization of algorithms for simple matrix operations.
 With access to parallel hardware accelerators, the speedup for both training and inference can be very large.
+Another benefit is the clear role of the parameters of the model \autocite{suykensLeastSquaresSupport2005}.
+The Lagrangian multiplier represents the influence of each sample on the model output.
+The bias term on the other hand represents the offset of the model output.
+This is in contrast to the weight parameters of deep neural networks which can represent any number of influence on the output.
+This fact makes SVMs much more clear to interpret in comparison to NNs \autocite{zhouInterpretingDeepVisual2019}.
+Against methods like kernel regression, SVMs enjoy the benefit of the training process being able to figure out which variables matter.
+In contrast, kernel regression would be less optimal since the regularization term in SVMs penalizes it for undue complexity.
 

### 2025-01-24 skripsi/chapter4.tex
move operator learning to related works, update revision list, mention mathematical  guarantee of conventional numerical methods in comparison scenario

@@
 In addition to the rollout of the exact solution, we also perform rollout on of the test set.
-This will be done in comparison to traditional numerical methods, namely the commonly used method of lines in time using SciPy and torchdiffeq and finite differences in space with NumPy gradient and PyTorch gradient respectively.
-Specifically, the SciPy odeint function uses lsoda from the FORTRAN library odepack.
-And, the torchdiffeq version will use Implicit Adams-Bashforth-Moulton (IABM) method.
+This will be done in comparison to traditional numerical methods, namely the commonly used method of lines in time using SciPy \autocite{virtanenSciPy10Fundamental2020} and torchdiffeq \autocite{Chen_torchdiffeq_2021} with finite differences in space using NumPy gradient and PyTorch gradient respectively.
+Specifically, the SciPy odeint function uses lsoda from the FORTRAN library ODEPACK \autocite{osti_145724}.
+And, the torchdiffeq version will use Implicit Adams-Bashforth-Moulton (IABM) method \autocite{bashforth1883attempt,moulton1926new}.
 Both of these were chosen for their availability for use in Python and therefore the kind of numerical solver one could set up with relative reliability.
+The choice of conventional physics based numerical methods is due to its mathematical guarantee that machine learning models do not possess \autocite{schiesserNumericalMethodLines2012,karniadakisPhysicsinformedMachineLearning2021}.
 

### 2025-01-24 skripsi/chapter1.tex
update outline to be like the UPI format with chapter abstracts

@@
 % !TEX root = ./skripsi.tex
-\chapter{INTRODUCTION}
+\chapter{INTRODUCTION}\label{ch:introduction}
 \section{Background}\label{sec:background}
@@
 \section{Outline}
-\noindent This thesis will be structured into five chapters with this chapter being the first.
-For further detail on the topics relevant to this study, \lccref{sec:literature_review} will discuss and summarize the related literature.
+\noindent This thesis will be structured into five chapters with this chapter being the first. This outline will provide a summary of each chapter. The outline is as follows:
+
+\noindent\chref{ch:introduction}\\
+\noindent This chapter begins with the background and relevant context of the problem of governing equations and their solutions.
+Their importance and the methods that are used to solve them are also discussed.
+This leads to the problem statement and goals based on said problems.
+The limitations and contribution are also derived from the background and context.
+Finally, the chapter ends with the outline that discusses structure of this thesis.
+
+\noindent\chref{ch:literature_review}\\
+\noindent For further detail on the topics relevant to this study, the second chapter will discuss and summarize the related literature.
 The context of the study will be explained in terms of the state of the art (SoTA), the literature involved, and how this problem fits within the larger computing and physical sciences field.
-In \lccref{sec:research_methodology}, we discuss the methodology that is used in this study to achieve the aims that were set in the first chapter.
-And then, the results of applying the research methodology are presented in \lccref{sec:results_and_discussion}.
-In this section, the results are also analyzed and discussed.
-Finally, in \lccref{sec:conclusions_and_future_work} we draw conclusions from the results and future directions of research for the use of SVMs in operator learning with basis functions.
+The specific components that will be covered are the Fourier transform, governing equations, and machine learning regression.
+
+\noindent\chref{ch:research_methodology}\\
+\noindent In this chapter we discuss the methodology that is used in this study to achieve the aims that were set in the first chapter.
+The chapter starts by explaining the steps within the research process from the problem specification to the analysis and discussion.
+Then the specific approach to data acquisition, literature study, and the computational model implementation are discussed.
+The last section of this chapter list the hardware and software tools that will be used in this study.
+
+\noindent\chref{ch:results_and_discussion}\\
+\noindent The results of applying the research methodology are presented in this chapter.
+This chapter starts with the data generation and retrieval results.
+Then, the SpectralSVR software library is development discussed from the design to the implementation and testing.
+The chapter then continues to the experimental scenarios the proposed model will be used.
+The experimental results are then presented and then discussed.
+
+\noindent\chref{ch:conclusions_and_future_work}\\
+\noindent Finally, in this chapter we draw conclusions from the results and analysis that was done in the previous chapter.
+Based on the analysis of weaknesses and unexplored questions, the future directions of research are also explored.
 % \noindent Bagian ini adalah penutup Bab I yang menyampaikan  secara ringkas isi setiap  bab.

### 2025-01-24 skripsi/chapter4.tex
update outline to be like the UPI format with chapter abstracts

@@
 % !TEX root = ./skripsi.tex
-\chapter{RESULTS AND DISCUSSION}\label{sec:results_and_discussion}
+\chapter{RESULTS AND DISCUSSION}\label{ch:results_and_discussion}
 \noindent This chapter is organized into five sections which are the results of data generation, data retrieval, design of computational model, implementation of computational model, experimental scenarios, and the experiments themselves.
@@
         coeff = self.svr.predict(f)
-        # convert to complex if basis needs complex values so that the reshaping is correct
+        # convert to complex if basis needs complex
+        # values so that the reshaping is correct
         if self.basis.coeff_dtype.is_complex:
@@
         original_device = u_coeff.device
-        u_coeff = to_real_coeff(u_coeff.flatten(1)).to(self.svr.device)
+        u_coeff = to_real_coeff(
+          u_coeff.flatten(1)
+        ).to(self.svr.device)
 
@@
         f_coeff_pred = (
-            torch.randn(f_shape, generator=generator).to(self.svr.device) * gain
+            torch.randn(
+              f_shape, generator=generator
+            ).to(self.svr.device) * gain
         )

### 2025-01-24 skripsi/apendix.tex
add example tensors for pre and post processing, add SoTA section

@@
 \appendix
+
+\chapter{EXAMPLE GENERATION AND PROCESSING OF DATA BEFORE AND AFTER THE LSSVR}\label{ch:example_prepostprocessing_basis}
+First we will start with how a function can be generated randomly.
+The random solution and parameter pair generation process starts by randomly sampling from a normal distribution coefficients of Fourier basis functions which result in tensors as shown in \lccref{fig:example_generated_coefficients}.
+The dimensions of this tensor of coefficients is the number of unique functions \(N\) by the number of basis functions representing each dimension \(m_1, m_2, \ldots, m_d\).
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+tensor([[ 0.0000+0.0000j,  5.9584-7.5454j, -6.4740-6.0901j,  ...,
+          4.5666+7.3829j, -6.4740+6.0901j,  5.9584+7.5454j],
+        [ 0.0000+0.0000j,  5.4649-6.3776j, -4.8105+1.3955j,  ...,
+          4.8338-1.8225j, -4.8105-1.3955j,  5.4649+6.3776j],
+        [ 0.0000+0.0000j,  1.4697-5.8133j,  7.7991+2.8807j,  ...,
+          2.0915-1.7939j,  7.7991-2.8807j,  1.4697+5.8133j],
+        ...,
+        [ 0.0000+0.0000j, -0.7932+4.6427j,  6.5799+1.1859j,  ...,
+         -0.1577-9.3086j,  6.5799-1.1859j, -0.7932-4.6427j],
+        [ 0.0000+0.0000j,  5.2905-6.0955j, -5.6544+3.8172j,  ...,
+          5.8754-1.5761j, -5.6544-3.8172j,  5.2905+6.0955j],
+        [ 0.0000+0.0000j,  3.2358+6.8016j, -8.0814+3.5778j,  ...,
+         -5.1760+1.9684j, -8.0814-3.5778j,  3.2358-6.8016j]])
+\end{lstlisting}
+  \caption{Example of coefficients randomly generated as the solution of the 1D derivative equation.}\label{fig:example_generated_coefficients}
+\end{figure}
+
+Noise is then added to the generated coefficients by transforming the coefficients to their function values using the function shown in \lccref{fig:fourier_transform_impl}.
+For our previous tensor of randomly generated coefficients the inverse transform results in the tensor shown in \lccref{fig:example_clean_inv_transform}.
+This tensor has the shape of \(N\) unique functions by the number of points in each dimension \(n_1,n_2,\ldots,n_d\).
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+  tensor([[-1.4411-4.4703e-08j,  0.3935-2.2054e-08j, -1.4868-8.9565e-09j,
+          ..., -0.7727-4.2093e-08j, -0.3239+2.0381e-08j,
+          1.1053-8.6315e-08j],
+        [-0.9293-5.7220e-08j, -0.0500-4.7684e-08j, -0.2628+2.8610e-08j,
+          ...,  1.4031-5.8692e-08j,  0.1245-6.1988e-08j,
+          2.1139+2.9045e-08j],
+        [-0.7640-2.8610e-08j,  1.0191+6.1989e-08j,  0.8502+2.7388e-08j,
+          ..., -1.1099-5.4252e-08j,  0.3513+2.3798e-08j,
+          1.0349-1.5378e-07j],
+        ...,
+        [ 0.3640+1.7881e-09j, -0.6330+5.5432e-08j, -1.6459-1.1356e-07j,
+          ...,  1.9432+7.8670e-08j,  0.1409+1.5608e-08j,
+          1.9429-1.1898e-07j],
+        [ 1.4188-5.7220e-08j, -0.0971-1.9073e-08j,  1.2511-6.4455e-09j,
+          ..., -0.2919+8.5157e-08j, -0.2904+1.2012e-08j,
+          0.4568-1.1858e-07j],
+        [-1.1443-9.5367e-09j, -1.6120+9.0599e-08j,  0.7427-3.5344e-08j,
+          ..., -0.6559+4.0621e-08j,  0.6636+2.1595e-08j,
+          0.7892-6.0481e-08j]])
+\end{lstlisting}
+  \caption{Example of the inverse Fourier transform of the randomly generated coefficients.}\label{fig:example_clean_inv_transform}
+\end{figure}
+
+The values we have obtained are perturbed using random values sampled from a normal distribution and then scaled to the requested noise ratio based on the standard deviation of the computed function values.
+Once perturbed, the values are transformed back to the Fourier domain.
+
+For data that starts as function values, like measurements or the ERA5 dataset, this is where the computational process would start.
+The function values transformed into the coefficient representation is shown in \lccref{fig:example_data_fourier_transformed}.
+This tensor has the same shape as \lccref{fig:example_generated_coefficients}.
+For data that started as function values, the number of modes would be by default the same as the discretization in each dimension.
+This can be altered according to the problem.
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+tensor([[ 7.1488e-01-1.0658e-14j,  6.4083e+00-7.7222e+00j,
+         -6.8440e+00-6.9812e+00j,  ...,
+          4.9350e+00+6.8183e+00j, -6.8440e+00+6.9812e+00j,
+          6.4083e+00+7.7222e+00j],
+        [ 1.4488e-01-9.5923e-14j,  5.7198e+00-6.4293e+00j,
+         -5.0511e+00+1.5238e+00j,  ...,
+          4.6795e+00-1.7510e+00j, -5.0511e+00-1.5238e+00j,
+          5.7198e+00+6.4293e+00j],
+        [-9.2841e-01+6.3949e-14j,  2.2419e+00-5.2065e+00j,
+          7.8745e+00+2.6073e+00j,  ...,
+          1.3050e+00-8.7435e-01j,  7.8745e+00-2.6073e+00j,
+          2.2419e+00+5.2065e+00j],
+        ...,
+        [-1.1377e-03+1.4211e-14j,  2.9627e-01+4.8204e+00j,
+          7.0653e+00+7.0965e-01j,  ...,
+         -1.1042e-01-9.8381e+00j,  7.0653e+00-7.0965e-01j,
+          2.9627e-01-4.8204e+00j],
+        [-8.5599e-01-6.0396e-14j,  4.9924e+00-5.7394e+00j,
+         -6.8187e+00+3.7167e+00j,  ...,
+          5.8396e+00-1.1584e+00j, -6.8187e+00-3.7167e+00j,
+          4.9924e+00+5.7394e+00j],
+        [ 7.6012e-01-2.1316e-14j,  3.6402e+00+5.9960e+00j,
+         -7.6304e+00+3.8345e+00j,  ...,
+         -4.6177e+00+2.4993e+00j, -7.6304e+00-3.8345e+00j,
+          3.6402e+00-5.9960e+00j]])
+\end{lstlisting}
+  \caption{Example of the coefficients from the Fourier transform of the data which was either generated and perturbed or from external sources as function values like ERA5 2-meter temperature.}\label{fig:example_data_fourier_transformed}
+\end{figure}
+
+For the generated data, the entire process of adding noise and getting the coefficients of the perturbed function values is done using the perturb function of the base Basis class as shown in \lccref{fig:basis_perturb_impl}.
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+...
+    def perturb(
+        self,
+        std_ratio: float = 0.1,
+        rand_func=torch.randn,
+        generator: torch.Generator | None = None,
+    ) -> Self:
+        values = self.inv_transform(self.coeff)
+        perturbed_values = (
+            values
+            + rand_func(
+                values.shape,
+                generator=generator,
+                dtype=self.coeff.dtype
+                if self._complex_funcs
+                else self.coeff.real.dtype,
+            )
+            * std_ratio
+            * values.std()
+        )
+        copy = self.copy()
+        copy.coeff = self.transform(perturbed_values)
+        return copy
+...
+\end{lstlisting}
+  \caption{Example of the inverse Fourier transform of the randomly generated coefficients.}\label{fig:basis_perturb_impl}
+\end{figure}
+
+Finally, the tensor of noisy generated functions or function values from other sources are preprocessed to be able to be used with the LSSVR\@.
+First, since LSSVR only works with one dimensional feature vectors, we flatten the tensors so that they become matrices.
+The coefficients are complex types, we represent them as two elements of the float type in the tensor as shown in \lccref{fig:example_coeff_flat_real}.
+Notice that the values are just the components of the complex number in \lccref{fig:example_data_fourier_transformed} as their own elements side by side.
+This would have the shape of \(N\) unique functions by the product of the number of modes in each dimension \(m_1\times m_2 \times\cdots\times m_d\) and multiplied by two because of the representation of complex number components as real elements.
+The final shape is \(N\) by \(2\times m_1\times m_2 \times\cdots\times m_d\).
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+tensor([[ 7.1488e-01, -1.0658e-14,  6.4083e+00,  ...,  6.9812e+00,
+          6.4083e+00,  7.7222e+00],
+        [ 1.4488e-01, -9.5923e-14,  5.7198e+00,  ..., -1.5238e+00,
+          5.7198e+00,  6.4293e+00],
+        [-9.2841e-01,  6.3949e-14,  2.2419e+00,  ..., -2.6073e+00,
+          2.2419e+00,  5.2065e+00],
+        ...,
+        [-1.1377e-03,  1.4211e-14,  2.9627e-01,  ..., -7.0965e-01,
+          2.9627e-01, -4.8204e+00],
+        [-8.5599e-01, -6.0396e-14,  4.9924e+00,  ..., -3.7167e+00,
+          4.9924e+00,  5.7394e+00],
+        [ 7.6012e-01, -2.1316e-14,  3.6402e+00,  ..., -3.8345e+00,
+          3.6402e+00, -5.9960e+00]])
+\end{lstlisting}
+  \caption{Example of the flattened coefficients represented as real numbers side by side.}\label{fig:example_coeff_flat_real}
+\end{figure}
+
+For the real representation of the parameter functions which will act as features, the data is scaled to have a distribution with a mean of zero and standard deviation of zero.
+This is the standard scaling of the data to achieve better and more consistent performance with the LSSVR\@.
+To achieve this, the current mean and standard deviation of the data is computed for each feature column (coefficient component).
+By subtracting the current data by the computed mean and then dividing by the standard deviation, the data should now have a mean of roughly zero and standard deviation of one.
+For our example data the scaled version is shown in \lccref{fig:example_scaled_data}.
+\begin{figure}[H]
+  \centering
+  \begin{lstlisting}[language=Python]
+tensor([[ 1.0025, -0.0103,  1.2830,  ...,  1.4096,  1.2830,  1.5487],
+        [ 0.1999, -0.0955,  1.1464,  ..., -0.3085,  1.1464,  1.2894],
+        [-1.3114,  0.0643,  0.4562,  ..., -0.5274,  0.4562,  1.0442],
+        ...,
+        [-0.0057,  0.0146,  0.0701,  ..., -0.1440,  0.0701, -0.9666],
+        [-1.2095, -0.0600,  1.0020,  ..., -0.7515,  1.0020,  1.1511],
+        [ 1.0662, -0.0209,  0.7337,  ..., -0.7753,  0.7337, -1.2024]])
+  \end{lstlisting}
+  \caption{Example of the scaled parameter function coefficients real representation.}\label{fig:example_scaled_data}
+\end{figure}
+
+The scaled parameter function coefficients which will act as the features along with the labels of the solution function coefficients are then used to get the trained parameters of the LSSVR\@.
+Since the predictions will be in the same format as shown in \lccref{fig:example_coeff_flat_real}, to obtain the predicted function values, we simply do the reverse process until we get to the function values.
+First the coefficients are changed to their complex number representation and then the dimensions are unflattened which results in a similar format to \lccref{fig:example_data_fourier_transformed}.
+So for labels that were originally two-dimensional, this means the predictions need to be reshaped from the flattened state into the same two-dimensional form.
+So the flattened dimension with size \(2\times m_1\times m_2 \times\cdots\times m_d\) would become \(d\) dimensions with shape \(m_1, m_2, \ldots, m_d\).
+Once the coefficients are formatted correctly, we use the inverse Fourier transform to obtain the function values with the implementation of \lccref{eq:inverse_discrete_fourier_transform}.
+The resulting function values should have the same format as the example shown in \lccref{fig:example_clean_inv_transform}.
+Since for the most part we are only interested in real-valued functions, we can discard the imaginary component.
+This results in the final predicted solution function values.
 

### 2025-01-24 skripsi/chapter2.tex
update outline to be like the UPI format with chapter abstracts
add example tensors for pre and post processing, add SoTA section

@@
 % !TEX root = ./skripsi.tex
-\chapter{LITERATURE REVIEW}\label{sec:literature_review}
+\chapter{LITERATURE REVIEW}\label{ch:literature_review}
 % \noindent Bab ini mengulas secara rinci konsep-konsep dasar yang berkaitan dengn pekerjaan penelitian TA dan deskripsi studi pustaka yang dilakukan.
@@
 Adding multiple of these blocks allow for learning more complex relationships.
-Another approach called Spectral Neural Operators, instead maps the coefficients of inputs to the coefficients of output functions \autocite{fanaskovSpectralNeuralOperators2023}.
+Another study extends this to spherical harmonics which reduce artifacts when modeling spherical domains like the weather \autocite{bonevSphericalFourierNeural2023}.
+% TODO: add more and maybe move some of the text in the introduction here.
+
+\section{State of The Art}
+\noindent Within the State of The Art (SoTA), our proposed method falls within a group of operator learning approach that utilize the advantageous properties of basis functions.
+This group of methods exploit the same properties of basis functions and their coefficients that the more conventional spectral method also utilize.
+One of the earliest works in this group of methods is the Deep Operator Network (DeepONet) \textcite{luLearningNonlinearOperators2021}.
+This paradigm is different from later methods since it uses a neural network as a learned basis function.
+This model can be seen as foregoing the basis function the Fourier transform enforces and instead learns the basis functions from the data \autocite{meurisMachinelearningbasedSpectralMethods2023}.
+Because of this, the model has two component networks.
+The first, named the trunk network acts as the learned basis functions.
+This network is given evaluation coordinates and computes the values of the \enquote{basis functions} at said coordinates.
+The second network, called the branch network, learns the mapping between the input function representation and the coefficients for the output function.
+The dot product of the outputs of both trunk and branch networks are evaluated to obtain the value of the predicted function at the specified coordinate.
+
+Another approach called Spectral Neural Operators, instead maps the coefficients of more common basis functions like the Fourier or Chebyshev basis functions \autocite{fanaskovSpectralNeuralOperators2023}.
 For coefficients obtained from Fourier transforms, the model is approximating the standard spectral method by taking advantage of the properties of the Fourier coefficients we discuss in \lccref{sec:fourier_discussion}.
@@
 This allows the NN to be trained in a self-supervised setting.
-
-Another paradigm is the so called DeepONet architecture proposed by \textcite{luLearningNonlinearOperators2021}.
-This model can be seen as foregoing the basis function the Fourier Transform enforces and instead learns the basis functions from the data \autocite{meurisMachinelearningbasedSpectralMethods2023}.
-Because of this, the model has two component networks.
-The first, named the trunk network acts as the learned basis functions.
-This network is given evaluation coordinates and computes the values of the \enquote{basis functions} at said coordinates.
-The second network, called the branch network, learns the mapping between the input function representation and the coefficients for the output function.
-The dot product of the outputs of both trunk and branch networks are evaluated to obtain the value of the predicted function at the specified coordinate.
 The final proposed approach we will discuss here doesn't use Deep Learning.

### 2025-01-24 skripsi/chapter4.tex
add example tensors for pre and post processing, add SoTA section

@@
 The implementation is simply the reverse of the transformation process where the elements are multiplied by the standard deviation and the mean is the added.
+This functionality is demonstrated for processing the data for use in SpectralSVR in \lccref{ch:example_prepostprocessing_basis}.
 
@@
 These classes provide the functionality needed to have an easier time when working with basis functions and their coefficients.
+An example of the use of these functions for pre-processing and post-processing the function data into and out of the Fourier domain is presented in \lccref{ch:example_prepostprocessing_basis}.
 First, the core function of these classes is to provide a way to transition between the spectral domain and the physical domain.

### 2025-01-26 technical_doc/implementation.tex
finish converting some code to diagrams

@@
 First, because the basis function used in this study is the Fourier basis, a large proportion of concern is the storage of Fourier basis coefficients.
-The Fourier series representation that is used in this study is the complex representation as show in \lccref{eq:fourier_series}.
-However, as previously mentioned, least squares support vector machines is constructed to work with real numbers.
+However, as previously mentioned, least-squares support vector machines is constructed to work with real numbers.
 In order for LSSVR to learn the relationship between complex numbers, a representation of complex numbers in terms of real numbers is necessary.
@@
 The \verb|view_as_real| and \verb|view_as_complex| functions allow the conversion between real and complex representations by representing complex valued tensors by adding a dimension of size two for each component of complex numbers.
-The resulting implementation can be seen in \lccref{fig:complex_matrix_conversion_implementation}.
+The resulting implementation can be seen in \lccref{fig:complex_matrix_format}.
 \begin{figure}[H]
     \centering
-  \begin{lstlisting}[language=Python]
-def to_real_coeff(x: torch.Tensor) -> torch.Tensor:
-    return torch.view_as_real(x).flatten(-2)
-
-def to_complex_coeff(x: torch.Tensor) -> torch.Tensor:
-  return torch.view_as_complex(
-    x.reshape((*x.shape[:-1], -1, 2))
-  )
-  \end{lstlisting}
-  \caption{Utility function to convert between complex matrices and the real representations.}\label{fig:complex_matrix_conversion_implementation}
+    \tikzfig{figures/complex_number_real_format}
+    \caption{Utility function to convert between complex matrices and the real representations.}\label{fig:complex_matrix_format}
 \end{figure}
@@
 This information is stored as properties of the class.
-Any complex tensors are converted into their real representations using the functions in \lccref{fig:complex_matrix_conversion_implementation}.
+Any complex tensors are converted into their real representations.
 Once the scaling function instance is fitted, any set of tensors with the same number of features (columns) and element type (complex or real) can be roughly transformed into a standard deviation of one and mean of zero for every feature.
@@
 In addition, the remaining coefficients may be rescaled in order to balance the effect of adding or removing coefficients.
-The implementation is presented in \lccrefs{fig:coefficient_shrink_impl,fig:coefficient_expand_impl}.
+The implementation is presented in \lccrefs{fig:resize_modes_process}.
 
 \begin{figure}[H]
+    \begin{subfigure}{0.45\textwidth}
     \centering
-  \begin{lstlisting}[language=Python]
-for dim, (target_mode, current_mode) in enumerate(
-    zip(target_modes, current_modes), 1
-):
-    device = x.device
-    start_range = torch.tensor(
-        range((target_mode - 1) // 2 + 1), dtype=torch.int
-    ).to(device=device)
-    end_range = torch.tensor(
-        range(current_mode - target_mode // 2,
-          current_mode
-        ),
-        dtype=torch.int,
-    ).to(device=device)
+        \tikzfig{figures/reduce_modes}
+        \caption{}\label{fig:reduce_modes}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+    \centering
+        \tikzfig{figures/expand_modes}
+        \caption{}\label{fig:expand_modes}
+    \end{subfigure}
+    \caption{The two ways to resize coefficient tensors: (\subref{fig:reduce_modes}) Reduce coefficient modes, (\subref{fig:expand_modes}) Expand coefficient modes.}\label{fig:resize_modes_process}
+\end{figure}
 
-    x_resized = torch.concat(
-        (
-            x_resized.index_select(dim, start_range),
-            x_resized.index_select(dim, end_range),
-        ),
-        dim,
-    )
-  \end{lstlisting}
-  \caption{Example of shrinking a tensor of samples' coefficients to a target number of modes.}\label{fig:coefficient_shrink_impl}
-\end{figure}
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-for dim, (target_mode, current_mode) in enumerate(
-    zip(target_modes, current_modes), 1
-):
-    device = x.device
-    start_range = torch.tensor(
-        range((current_mode - 1) // 2 + 1), dtype=torch.int
-    ).to(device=device)
-    # make sure that end range is empty if
-    # the coefficient is only size 1
-    end_range = torch.tensor(
-        range(current_mode // 2, current_mode)
-        if current_mode > 1
-        else range(0),
-        dtype=torch.int,
-    ).to(device=device)
-    padding_size = target_mode - current_mode
-    modes = list(x_resized.shape)
-    modes[dim] = padding_size
-    padding = torch.zeros(modes).to(x_resized)
-
-    x_resized = torch.concat(
-        (
-            x_resized.index_select(dim, start_range),
-            padding,
-            x_resized.index_select(dim, end_range),
-        ),
-        dim,
-    )
-  \end{lstlisting}
-  \caption{Example of expanding a tensor of samples' coefficients to a target number of modes.}\label{fig:coefficient_expand_impl}
-\end{figure}
 Next, the second way to manage the size of a tensor along a dimension is to interpolate the current values.
@@
 In this case, the coefficients for time values that are not available can be interpolated.
-The implementation of this is shown in \lccref{fig:coefficient_interpolation_impl}.
+The visualization of this is shown in \lccref{fig:linear_interpolation}.
 \begin{figure}[H]
     \centering
-  \begin{lstlisting}[language=Python]
-    index_floor = index_float.floor().to(torch.int)
-    index_ceil = index_float.ceil().to(torch.int)
-    x_ceil = x.index_select(dim, index_ceil)
-    x_floor = x.index_select(dim, index_floor)
-    # interpolate coefficients
-    index_shape = [1 for _ in range(x_floor.ndim)]
-    index_shape[1] = -1
-    index_scaler = (
-        ((index_float - index_floor) / (
-          index_ceil - index_floor
-        ))
-        .reshape(index_shape)
-        .nan_to_num()
-    )
-    # ynt + scaler * (ynt1 - ynt)
-    # (1 - scaler) * ynt + scaler * ynt1
-    x_interp = torch.lerp(x_floor, x_ceil, index_scaler.to(x))
-  \end{lstlisting}
-  \caption{Example of interpolating for indices (floating point indices) between the available ones (integer indices).}\label{fig:coefficient_interpolation_impl}
+    \tikzfig{figures/linear_interpolation}
+    \caption{Linear interpolation process}\label{fig:linear_interpolation}
 \end{figure}
@@
 Finally, this module also provides the types and reexports implementations of ordinary differential equation solvers from the torchdiffeq library \autocite{Chen_torchdiffeq_2021}.
-The implementation can be seen in \lccref{fig:solver_impl}.
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-RHSFuncType = Callable[[torch.Tensor, torch.Tensor],
-  torch.Tensor
-]
-SolverSignatureType = Callable[[
-        RHSFuncType, torch.Tensor, torch.Tensor,
-    ],
-    torch.Tensor
-]
-MixedRHSFuncType = Callable[[
-        torch.Tensor, torch.Tensor, torch.Tensor,
-    ],
-    torch.Tensor,
-]
-MixedSolverSignatureType = Callable[
-    [MixedRHSFuncType, torch.Tensor, torch.Tensor],
-    torch.Tensor,
-]
-
-def euler_solver(
-    rhs_func: RHSFuncType,
-    y0: torch.Tensor,
-    t: torch.Tensor,
-):
-    solution = torch.zeros((len(t), *y0.shape)).to(y0)
-
-    j = 1
-    solution[j - 1] = y0
-    for t0, t1 in zip(t[:-1], t[1:]):
-        dt = t1 - t0
-        y = solution[j - 1]
-        solution[j] = y + dt * rhs_func(t0, y)
-        assert (
-            solution.isnan().sum() == 0
-        ), f"solver encountered nan at timestep {j} (t={t0})"
-        j = j + 1
-    return solution
-
-implicit_adams_solver: SolverSignatureType = partial(
-    odeint, method="implicit_adams", options={"max_iters": 4}
-)  # type: ignore
-
-lsoda_solver: SolverSignatureType = partial(
-    odeint, method="scipy_solver", options={"solver": "LSODA"}
-)  # type: ignore
-  \end{lstlisting}
-  \caption{Implementation of ODE solvers and the types.}\label{fig:solver_impl}
-\end{figure}
+This portion of the module provide a uniform interface to use for the rest of the library.
+This is needed because of the extensibility requirement and the possibility of using other numerical method implementations.
 
@@
 The coefficients are assumed to be at least of one function.
-
 \begin{figure}[H]
     \centering
-  \begin{lstlisting}[language=Python]
-...
-    @staticmethod
-    def transform(
-        f: torch.Tensor,
-        res: TransformResType | None = None,
-        periodic: bool = True,
-        periods: PeriodsInputType = None,
-        allow_fft: bool = True,
-    ) -> torch.Tensor:
-        if not torch.is_complex(f):
-            f = f * (1 + 0j)
-        res = transformResType_to_tuple(res, tuple(f.shape[1:]))
-        periods = periodsInputType_to_tuple(periods, f.shape[1:])
-        # perform 1d transform over every dimension
-        F = f
-        for cdim in range(1, ndims):
-            F = FourierBasis._ndim_transform(
-                F,
-                dim=cdim,
-                func="forward",
-                res=res[cdim - 1],
-                periodic=periodic,
-                period=periods[cdim - 1],
-                allow_fft=allow_fft,
-            )
-
-        return F
-...
-  \end{lstlisting}
-  \caption{Implementation of forward Fourier transform.}\label{fig:fourier_transform_impl}
+    \tikzfig{figures/fourier_transform_process}
+    \caption{Fourier transforms for multiple dimensions.}\label{fig:fourier_transform_multidim}
 \end{figure}
@@
 This process is repeated until the last dimension.
-The implementation of the forward transform is presented in \lccref{fig:fourier_transform_impl}.
+The visualization of the forward transform for multiple dimensions is presented in \lccref{fig:fourier_transform_multidim}.
 The inverse transform simply changes the \verb|func| parameter to \enquote{inverse}.
@@
 Mathematically, this is simply due to the matrix multiplication of basis functions along one dimension with every other dimension.
-The implementation of this is shown in \lccref{fig:ndim_fourier_transform_impl}.
-
+The visualization of this process is shown in \lccref{fig:fourier_transform_along_one_dim}.
 \begin{figure}[H]
     \centering
-  \begin{lstlisting}[language=Python]
-...
-    @staticmethod
-    def _ndim_transform(
-        f: torch.Tensor,
-        dim: int,
-        func: Literal["forward", "inverse"],
-        res: slice,
-        periodic: bool,
-        period: float,
-        allow_fft: bool,
-    ) -> torch.Tensor:
-        # flatten so that each extra dimension is
-        # treated as a separate "sample"
-        # move dimension to transform to the end
-        # so that it can stay intact after f is flatened
-        f_transposed = f.moveaxis(dim, -1)
-        # flatten so that the last dimension is intact
-        f_flatened = f_transposed.flatten(0, -2)
-
-        F_flattened = FourierBasis._raw_transform(
-            f_flatened,
-            func=func,
-            res=res,
-            periodic=periodic,
-            period=period,
-            allow_fft=allow_fft,
-        )
-        # unflatten so that the correct shape is returned
-        F_transposed = F_flattened.reshape(
-          (*f_transposed.shape[:-1], res.step)
-        )
-        F = F_transposed.moveaxis(-1, dim)
-
-        return F
-...
-  \end{lstlisting}
-  \caption{Implementation of n-dimensional Fourier transform for a specific dimension.}\label{fig:ndim_fourier_transform_impl}
+    \tikzfig{figures/fourier_transform_along_one_dim}
+    \caption{The application of the one dimension Fourier transform on multiple dimensions.}\label{fig:fourier_transform_along_one_dim}
 \end{figure}
-
 \begin{figure}[H]
     \centering
-  \begin{lstlisting}[language=Python]
-...
-    @staticmethod
-    def _raw_transform(
-        f: torch.Tensor,
-        func: Literal["forward", "inverse"],
-        res: slice,
-        periodic: bool,
-        period: float,
-        allow_fft: bool,
-    ) -> torch.Tensor:
-        match func:
-            case "forward":
-                sign = -1
-            case "inverse":
-                sign = 1
-        mode = f.shape[1]
-        domain_starts_at_0 = res.start == 0
-        domain_end_equal_to_period = res.stop == period
-        can_use_fft = (
-            domain_starts_at_0
-            and domain_end_equal_to_period
-            and periodic
-            and allow_fft
-        )
-        if can_use_fft:
-            if func == "forward":
-                F = torch.fft.fft(
-                  f, dim=1, n=res.step, norm="backward"
-                )
-            elif func == "inverse":
-                F = torch.fft.ifft(
-                  f, dim=1, n=res.step, norm="forward"
-                )
-        else:
-            if periodic:
-                n = res.start + torch.arange(res.step).to(f)
-                n = n / res.step * period
-            else:
-                n = torch.linspace(
-                    res.start, res.stop, res.step
-                ).to(f)
-            e = FourierBasis.fn(
-                n.view(-1, 1),
-                mode,
-                periods=period,
-                constant=sign * 2j * torch.pi,
-            )
-
-            F = torch.mm(f, e.T)
-        return F
-...
-  \end{lstlisting}
-  \caption{Implementation of the one dimensional Fourier Transform.}\label{fig:1d_fourier_transform_impl}
+    \tikzfig{figures/fourier_transform_one_dim}
+    \caption{The application of the one dimension Fourier transform on multiple samples.}\label{fig:fourier_transform_one_dim}
 \end{figure}
@@
 The FFT algorithm is used if the following are all true: the evaluation starts at zero and ends with the same value as the period, the function can be assumed to be periodic, and FFT is allowed.
-Otherwise, the transform is computed naively using \lccrefs{eq:discrete_fourier_transform,eq:inverse_discrete_fourier_transform}.
+Otherwise, the transform is computed naively using the Discrete Fourier Transform (DFT) and Inverse Discrete Fourier Transform (IDFT).
 The naive approach allows for evaluating function values of coefficients at various grid sizes and evaluation boundaries.
@@
 Because of this, the information would need to be stored outside the Basis class instance and any outputs or operations with the classes will need to take this into account.
-The implementation of the one dimensional Fourier transform is presented in \lccref{fig:1d_fourier_transform_impl}.
+The implementation of the one dimensional Fourier transform is presented in \lccref{fig:fourier_transform_one_dim}.
 
@@
 This is then used to perform the arithmetic operation.
-The implementation in \lccref{fig:basis_addition_impl} demonstrates the addition operation.
 For subtraction, a similar implementation is done using the \verb|__sub__| function and switching the plus sign with the minus sign.
 
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def __add__(self, other: Self):
-        if isinstance(other, self.__class__):
-            if other.coeff is None:
-                return self.copy()
-            elif self.coeff is None:
-                return other.copy()
-            else:
-                result = self.resize_modes(other)
-                result.coeff = result.coeff + other.coeff
-                return result
-        else:
-            raise TypeError(
-                f"unsupported operand type(s) for +: '{
-                    self.__class__
-                }' and '{type(other)}'"
-            )
-...
-  \end{lstlisting}
-  \caption{Implementation of basis addition function.}\label{fig:basis_addition_impl}
-\end{figure}
-
 The calculus operations for Fourier basis take advantage of the properties of the Fourier series.
-As discussed in \lccref{sec:fourier_discussion}, derivatives and integration become multiplication and division in the spectral space of Fourier series.
-Our implementation takes advantage of this as shown in \lccref{fig:basis_grad_impl}.
+Derivatives and integration become multiplication and division in the spectral space of Fourier series.
 Similar to how subtraction is just a modification of the addition operation, the integral or antiderivative operator is also implemented simply by changing the operation with the term multiplier from multiplication to division.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def grad(self, dim: int = 0, ord: int = 1) -> Self:
-        copy = self.copy()
-        if dim == 0 and self.time_dependent:
-            # time dependent use finite differences
-            dt = self.periods[0] / (self.time_size - 1)
-            coeff = copy.coeff
-            for o in range(ord):
-                coeff = torch.gradient(coeff, spacing=dt, dim=1)[0]
-            copy.coeff = coeff
-        else:
-            if self.time_dependent:
-                # disregard time dimension
-                dim = dim - 1
-            k = copy.wave_number(copy.modes[dim])
-            multiplier_dims = [1 for _ in range(copy.ndim)]
-            multiplier_dims[dim] = copy.modes[dim]
-            if self.time_dependent:
-                multiplier_dims = (1, *multiplier_dims)
-            multiplier = (
-                2
-                * torch.pi
-                * 1j
-                * k.reshape(multiplier_dims).to(copy.coeff)
-                / self.periods[dim]
-            )
-            multiplier = multiplier.pow(ord)
-            coeff = copy.coeff.mul(multiplier)
-            coeff[:, ..., 0] = torch.tensor(0 + 0j)
-            copy.coeff = coeff
-        return copy
-...
-  \end{lstlisting}
-  \caption{Implementation of basis grad function.}\label{fig:basis_grad_impl}
-\end{figure}
 
@@
 First, random coefficient generation for the Fourier basis is implemented.
-This is done as discussed in step 3 of the data generation process discussed in \lccref{sec:data_generation}.
-The implemented function shown in \lccref{fig:generate_coeff_impl} is then wrapped in another function that creates a new FourierBasis instance with the generated coefficients.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    @classmethod
-    def generate_coeff(
-        cls,
-        n: int,
-        modes: int | tuple[int, ...],
-        generator: torch.Generator | None = None,
-        random_func: Callable[..., torch.Tensor] = torch.randn,
-        complex_funcs: bool = False,
-        scale: bool = True,
-    ) -> torch.Tensor:
-        if isinstance(modes, int):
-            modes = (modes,)
-        n_modes = len(modes)
-        assert n_modes > 0, "modes should have at least one element"
-        random_func = partial(random_func, generator=generator)
-        if complex_funcs:
-            coeff = random_func((n, *modes), dtype=torch.complex64)
-        else:
-            coeff = random_func((n, *modes), dtype=torch.complex64)
-
-            vals = cls.inv_transform(coeff)
-            coeff = cls.transform(vals.real + 0j)
-        if scale:
-            scaler = torch.tensor(modes).sum() * 0.2
-            coeff = coeff.mul(scaler)
-        return coeff
-...
-  \end{lstlisting}
-  \caption{Implementation of Fourier Basis coefficient generation function.}\label{fig:generate_coeff_impl}
-\end{figure}
+The function is then wrapped in another function that creates a new FourierBasis instance with the generated coefficients.
 
@@
 
-The optimization function that fits the model to the training data solves \lccref{eq:lssvr_solution}.
-This function is shown in \lccref{fig:lssvr_fit_function_impl}.
+The optimization function that fits the model to the training data solves the linear optimization problem of the LSSVR\@.
+This process is shown in \lccref{fig:lssvr_optimization}.
 The first half of the function sets up the left and right hand side matrices.
@@
 This is for method chaining purposes for ease of use when using the fit function in a chain with other functions we will discuss next, such as the prediction function.
-
 \begin{figure}[H]
     \centering
-  \begin{lstlisting}[language=Python]
-...
-    def _optimize_parameters(
-      self,
-      X: torch.Tensor,
-      y_values: torch.Tensor,
-    ):
-
-        A = torch.empty(
-          (X.shape[0] + 1,) * 2,
-          device=self.device,
-          dtype=self.dtype,
-        )
-        A[1:, 1:] = self._batched_K(X, X)
-        A[1:, 1:].diagonal().copy_(
-            A[1:, 1:].diagonal()
-            + torch.ones(
-                (A[1:, 1:].shape[0],),
-                device=self.device,
-                dtype=self.dtype,
-            ).to()
-            / self.C
-        )
-        A[0, 0] = 0
-        A[0, 1:] = 1
-        A[1:, 0] = 1
-        shape = np.array(y_values.shape)
-        shape[0] += 1
-        B = torch.empty(
-          list(shape), device=self.device, dtype=self.dtype
-        )
-        B[0] = 0
-        B[1:] = y_values
-
-        solution: torch.Tensor = torch.linalg.lstsq(
-            A.to(dtype=torch.float), B.to(dtype=torch.float)
-        ).solution.to(dtype=self.dtype)
-
-        b = solution[0, :]
-        alpha = solution[1:, :]
-
-        return (b, alpha)
-...
-  \end{lstlisting}
-  \caption{Implementation of Least-squares Support Vector Regression fitting function.}\label{fig:lssvr_fit_function_impl}
+    \tikzfig{figures/lssvr_optimization}
+    \caption{Optimization process of LSSVR}\label{fig:lssvr_optimization}
 \end{figure}
@@
 The learned multipliers and bias parameters are then used for predicting outputs from unseen sample features.
-\Cref{eq:lssvr_prediction_vectorized} shows the computation that needs to be done to compute the predicted output.
 The prediction process first constructs both matrices on the left-hand side of the equation.
@@
 The function output is simply the predicted outputs.
-The implementation of this function is shown in \lccref{fig:lssvr_predict_function_impl}.
-
+The implementation of this function is shown in \lccref{fig:lssvr_optimization}.
 \begin{figure}[H]
     \centering
-  \begin{lstlisting}[language=Python]
-...
-NumpyArrayorTensor = (
-    np.ndarray[typing.Any, np.dtype[np.float_]] |
-    torch.Tensor
-)
-...
-    def predict(
-        self,
-        X: NumpyArrayorTensor,
-    ) -> NumpyArrayorTensor:
-        """Predicts the labels of data X given a trained model.
-        - X: ndarray of shape (n_samples, n_attributes)
-        """
-        is_torch = isinstance(X, torch.Tensor)
-        if is_torch:
-            if X.ndim == 1:
-                X_reshaped_torch = X.reshape(-1, 1)
-            else:
-                X_reshaped_torch = X
-            X_= X_reshaped_torch.clone().to(
-                self.device, dtype=self.dtype
-            )
-        else:
-            if X.ndim == 1:
-                X_reshaped_np = X.reshape(-1, 1)
-            else:
-                X_reshaped_np = X
-            X_ = torch.from_numpy(X_reshaped_np).to(
-                self.device, dtype=self.dtype
-            )
-
-        KxX = self._batched_K(X_, self.sv_x)
-
-        y_pred = KxX @ self.alpha + self.b
-        predictions: NumpyArrayorTensor
-        if is_torch:
-            predictions = y_pred.to(X)
-        else:
-            predictions = y_pred.cpu().numpy()
-
-        if X.ndim == 1:
-            return predictions.reshape(-1)
-        else:
-            return predictions
-...
-  \end{lstlisting}
-  \caption{Implementation of Least-squares Support Vector Regression prediction function.}\label{fig:lssvr_predict_function_impl}
+    \tikzfig{figures/lssvr_prediction}
+    \caption{Prediction process of LSSVR}\label{fig:lssvr_prediction}
 \end{figure}
@@
 This is simply computed with matrix multiplication between the kernel matrix and the support vectors.
-The implementation is shown in \lccref{fig:lssvr_correlation_image_function_impl}.
 The batched kernel function is used in this case to mitigate the memory footprint.
-
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def get_correlation_image(self):
-        return self._batched_K(
-            self.sv_x, self.sv_x
-        ).mm(self.sv_x)
-...
-  \end{lstlisting}
-  \caption{Implementation of Least-squares Support Vector Regression correlation image function.}\label{fig:lssvr_correlation_image_function_impl}
-\end{figure}
 
@@
 The support vector matrix is transposed so that the multiplication is done on the dimension that indexes each sample.
-This computation is implemented as shown in \lccref{fig:lssvr_p_matrix_function_impl}.
 The resulting matrix is termed the p-matrix.
@@
 
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def get_p_matrix(self):
-        return self.sv_x.T.mm(self.alpha)
-...
-  \end{lstlisting}
-  \caption{Implementation of Least-squares Support Vector Regression p-matrix function.}\label{fig:lssvr_p_matrix_function_impl}
-\end{figure}
-
 The second component of the model modules is the SpectralSVR implementation that uses a multi-output support vector regression (SVR) model to learn in the spectral domain, such as the LSSVR implementation in the first component.
@@
 First, the constructor used to initialize each SpectralSVR instance accepts a Basis instance, an SVR instance which is the implemented LSSVR by default, and the verbosity of the model.
-These parameters are then used when the training function shown in \lccref{fig:spectralsvr_train_impl} is called.
-Training the SpectralSVR model begins by calling the train function with parameters of the input function representation, output function representation, and an indicator of whether the output function is time dependent.
+These parameters are then in the training process shown in \lccref{fig:spectralsvr_training}.
+Training the SpectralSVR model begins with parameters of the input function representation, output function representation, and an indicator of whether the output function is time dependent.
 Then, the function ensures that the features and labels are matrices.
@@
 Finally, to again allow for chaining methods, the function returns the current class instance.
-
 \begin{figure}[H]
     \centering
-  \begin{lstlisting}[language=Python]
-...
-    def train(
-        self,
-        f: torch.Tensor,
-        u_coeff: torch.Tensor,
-        u_time_dependent: bool = False,
-    ):
-        self.basis.time_dependent = u_time_dependent
-        if self.basis.coeff_dtype.is_complex:
-            u_coeff = to_complex_coeff(u_coeff)
-
-        if f.ndim > 2:
-            f = f.flatten(1)
-        if u_coeff.ndim > 2:
-            u_coeff = u_coeff.flatten(1)
-
-        if torch.is_complex(u_coeff):
-            u_coeff = to_real_coeff(u_coeff)
-        if torch.is_complex(f):
-            f = to_real_coeff(f)
-        self.svr.fit(f, u_coeff)
-        return self
-...
-  \end{lstlisting}
-  \caption{Implementation of SpectralSVR training function.}\label{fig:spectralsvr_train_impl}
+    \tikzfig{figures/training_spectralsvr}
+    \caption{SpectralSVR training diagram}\label{fig:spectralsvr_training}
 \end{figure}
@@
 From there, the predicted functions can be evaluated and  plotted.
-However, if one simply wants to evaluate the value of the predicted function at arbitrary points, another function is implemented to provide ease of use for this exact case.
-The implemented function is called forward as displayed in \lccref{fig:spectralsvr_forward_impl}.
-The arguments to this function are the input functions, the evaluation points, and the domain span.
-The function first predicts the output function coefficients.
-Then, the predicted coefficients are multiplied with the basis function values at each point to compute the final predicted point values.
-
+The flow of this entire process is displayed in \lccref{fig:spectralsvr_prediction}.
 \begin{figure}[H]
     \centering
-  \begin{lstlisting}[language=Python]
-...
-    def forward(
-        self,
-        f: torch.Tensor,
-        x: torch.Tensor,
-        periods: tuple[float, ...]
-        | None = None,
-    ) -> torch.Tensor:
-        if len(x.shape) == 1:
-            x = x.unsqueeze(-1)
-
-        # compute coefficients
-        if torch.is_complex(f):
-            f = to_real_coeff(f)
-        coeff = self.svr.predict(f)
-        # convert to complex if basis needs complex values so that the reshaping is correct
-        if self.basis.coeff_dtype.is_complex:
-            coeff = to_complex_coeff(coeff)
-
-        return self.basis.evaluate(
-            coeff=coeff.reshape((f.shape[0], *self.modes)),
-            x=x,
-            periods=periods,
-            time_dependent=self.basis.time_dependent,
-        )
-...
-  \end{lstlisting}
-  \caption{Implementation of SpectralSVR forward function (pointwise prediction).}\label{fig:spectralsvr_forward_impl}
+    \tikzfig{figures/prediction_spectralsvr}
+    \caption{SpectralSVR prediction diagram}\label{fig:spectralsvr_prediction}
 \end{figure}
@@
 The gradient of the loss with respect to the inputs are then computed and then used to perform optimization of the inputs using the ADAM optimizer.
-This is implemented as the inverse function shown in \lccref{fig:spectralsvr_inverse_impl}.
 The function arguments are the expected output function coefficients, evaluation points, the loss function used, how many optimization loops are done, the random number generator, and the gain which is used in generating the random initial input functions.
@@
 
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def inverse_coeff(
-        self,
-        u_coeff: torch.Tensor,
-        loss_fn: Callable[
-            [torch.Tensor, torch.Tensor], torch.Tensor
-        ] = mean_squared_error,
-        epochs=100,
-        generator=torch.Generator().manual_seed(42),
-        gain=0.05,
-        **optimizer_params,
-    ):
-        f_shape = (u_coeff.shape[0], self.svr.sv_x.shape[1])
-        complex_coeff = u_coeff.is_complex()
-        original_device = u_coeff.device
-        u_coeff = to_real_coeff(u_coeff.flatten(1)).to(self.svr.device)
-
-        # inverse problem
-        f_coeff_pred = (
-            torch.randn(f_shape, generator=generator).to(self.svr.device) * gain
-        )
-        f_coeff_pred.requires_grad_()
-        optim = torch.optim.Adam([f_coeff_pred], **optimizer_params)
-
-        for epoch in range(epochs):
-            optim.zero_grad()
-            u_coeff_pred = self.svr.predict(f_coeff_pred)
-            loss = loss_fn(u_coeff_pred, u_coeff)
-            loss.backward()
-            optim.step()
-        optim.zero_grad()
-        f_coeff_pred.requires_grad_(False)
-        if complex_coeff:
-            f_coeff_pred = to_complex_coeff(f_coeff_pred)
-        return f_coeff_pred.to(original_device)
-...
-  \end{lstlisting}
-  \caption{Implementation of SpectralSVR inverse coeff function (parameter estimation).}\label{fig:spectralsvr_inverse_impl}
-\end{figure}
-
 The SpectralSVR class also provides a convenience function for testing the performance of the learned model.
-This function is shown in \lccref{fig:spectralsvr_test_impl}.
 The function arguments are the testing inputs, expected testing outputs, and a resolution for evaluation of function values.
@@
 
-\begin{figure}[H]
-  \centering
-  \begin{lstlisting}[language=Python]
-...
-    def test(
-        self,
-        f: torch.Tensor,
-        u_coeff_targets: torch.Tensor,
-        res: ResType = 200,
-    ):
-        if torch.is_complex(f):
-            logger.debug("transform f to real")
-            f = to_real_coeff(f)
-        u_coeff_preds = self.svr.predict(f)
-        if torch.is_complex(u_coeff_targets):
-            logger.debug("transform u_coeff to real")
-            u_coeff_targets = to_real_coeff(u_coeff_targets)
-
-        grid = self.basis.grid(res).flatten(0, -2)
-        u_preds = self.basis.evaluate(
-            coeff=to_complex_coeff(u_coeff_preds),
-            x=grid,
-            time_dependent=self.basis.time_dependent,
-        ).real
-        u_targets = self.basis.evaluate(
-            coeff=to_complex_coeff(u_coeff_targets),
-            x=grid,
-            time_dependent=self.basis.time_dependent,
-        ).real
-        return {
-            "spectral": get_metrics(
-                u_coeff_preds, u_coeff_targets
-            ),
-            "function value": get_metrics(u_preds, u_targets),
-        }
-...
-  \end{lstlisting}
-  \caption{Implementation of SpectralSVR test function.}\label{fig:spectralsvr_test_impl}
-\end{figure}
-
 \subsubsection{Problems}
-
 \noindent The final module implements the PDEs that will serve as problems the proposed modules will solve.
@@
 The generate function calls a function that has the responsibility of setting up the constant initial conditions or constant forcing terms and then calls the ODE solver specified in the generate function arguments.
-The right-hand side function computes the time derivative based on \lccref{eq:time_derivative_time_step_function}.
+The right-hand side function computes the time derivative.
 The implementation of this is show in \lccref{fig:burgers_generate_dt_impl}.
@@
 The derivatives are computed with the PyTorch gradient function.
-And then using \lccref{eq:forced_viscous_burgers}, the residual is computed by subtracting the forcing term from both sides.
+And then using the forced burgers equation, the residual is computed by subtracting the forcing term from both sides.
 

### 2025-01-26 technical_doc/introduction.tex
finish converting some code to diagrams

@@
 
-This document is an example of a software manual created using \LaTeX\ and Overleaf. It provides a nice clean format for producing this type of technical document.
+The purpose of this technical document is to provide a comprehensive, interpretable guide for all stakeholders to understand the library.
+The requirements that were gathered will first be presented.
+Then there will be an explanation of the architecture and designs that will go towards fulfilling the requirements and constraints.
+This includes the different modules and their roles in performing operator learning in the Fourier domain using LSSVR\@.
+The designs will also discuss the way the modules will interface with external stimuli.
+From the designs, the implementation will be tested on its adherence to restrictions and the designs as a whole.
 
-Simply start writing your document and use the Recompile button to view the updated PDF preview.
-Examples of commonly used commands and features can be found in the sections below, to help you get started.
+\section{Scope}
+This document will cover the requirements, design and analysis, implementation, and testing of the library.
+The library is a software product developed with the purpose of providing functionality relevant to our proposed SpectralSVR operator learning approach.
 
-To change the logo shown on the front page, simply upload your own logo image file (via the file-tree menu) to replace the default logo.pdf file.
-
-Once you're familiar with the editor, you can find various project settings in the Overleaf menu, accessed via the button in the very top left of the editor.
-To view tutorials, user guides, and further documentation, please visit our \url{https://www.overleaf.com/learn}.
-If you haven't used \LaTeX\ before, our \url{https://www.overleaf.com/learn/latex/Learn_LaTeX_in_30_minutes} tutorial is an excellent place to start.
-
-For large documents, it can be useful to split the document into multiple source files.
-Double-clicking on text in Overleaf's PDF preview will take you directly to the corresponding code in the editor.
+\section{Outline}
+This document will be organized as follows:
+\begin{enumerate}
+    \item Introduction: This chapter provides context to the purpose of this document. This chapter also describes the scope and structure of this document.
+    \item Requirements: This chapter explains the software requirements, including functional requirements, non-functional requirements, information requirements, user characteristics, and external interface requirements.
+    \item Use Case: This chapter explains the model used based on the results of the software requirements analysis.
+The model created consists of a rich picture diagram that visualize the use case for the software product.
+    \item Design: This chapter explains the software design using Sequence Diagram and module descriptions.
+    \item Implementation: This chapter explains the implementation of the software in a specific programming language.
+    \item Testing: This chapter contains the process of testing the software using specific test cases. The current results of said test cases are also presented.
+\end{enumerate}

### 2025-01-26 technical_doc/requirements.tex
finish converting some code to diagrams

@@
 \chapter{REQUIREMENTS}
+The requirements of the software can be divided into two main categories of functional and non-functional requirements. The functional requirements of the software are:\nopagebreak
+\begin{itemize}
+    \item The ability to transform between discrete function values and the coefficients of their Fourier series approximation.
+    \item The ability to visualize functions in their coefficient representation
+    \item The ability to represent differential equations using Fourier series and the coefficient relation between parameters and solution.
+    \item Generation of random functions.
+    \item Generate parameters and solutions for the derivative equation and Burgers' equation.
+    \item A way to represent complex numbers as a pair of real numbers.
+    \item An LSSVR model for regressing the coefficient relationship of parameter and solutions.
+    \item A way to normalize inputs to the LSSVR.
+    \item A way to measure the accuracy and efficiency of the model.
+    \item A way to interpret the coefficient relationship learned by the model.
+    \item The ability to use the tools in a Jupyter Notebooks or Python scripts.
+\end{itemize}
+
+\noindent The non-functional requirements for the software are:\nopagebreak
+\begin{itemize}
+    \item Working memory footprint that fits within 16 GB\@.
+    \item Efficient and fast performance.
+    \item Reliability and the consistency.
+    \item Extendable to other problems.
+\end{itemize}
+\filbreak
+\noindent The information requirements of the software are:
+\begin{itemize}
+    \item Reference of derivative and Burgers' equations.
+    \item Mathematical formulation of LSSVR.
+    \item Mathematical formulation of the Discrete Fourier Transform (DFT) and properties of the basis and its coefficients.
+\end{itemize}
+
+\noindent The external interface requirements are:\nopagebreak
+\begin{itemize}
+    \item Data compatibility with Zarr or other data formats.
+\end{itemize}

### 2025-01-26 technical_doc/usecase.tex
finish converting some code to diagrams

@@
 \chapter{USE CASE}
+The model that will be used based on the requirements is shown in \lccref{fig:rich_picture}.
+The systems one would like to model using this library may or may not have governing equations that are defined to describe its behavior.
+In both cases, the measurements of said systems are typically discrete values representing some state of the systems such as temperature distribution.
+Other measurements may include the thermal conductivity distribution of systems or heat source distribution.
+Together these form the effect and causes of said system.
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=1.0\linewidth]{figures/rich_picture.png}
+    \caption{Rich picture diagram illustrating the environment and use case for the library.}\label{fig:rich_picture}
+\end{figure}
+
+Functions from measurements or synthetically generated using known governing equations can be represented as the Fourier coefficients of their approximating Fourier series.
+As the computation must be able to switch between the physical and Fourier domain, other utilities to change the data format will also be essential.
+Because the relationship between solutions and the parameters can be learned as the relationship between the coefficients of their parameters, the Least-Squares Support Vector Regression is used to learn this from data.
+Evaluation of how well the model performs will also be required to understand areas of improvement.

### 2025-02-09 skripsi/apendix.tex
fix table caption position
add FNN baseline

@@
 \begin{table}[H]
+  \caption{Example data of function \(2x^2+4\)}\label{table:lssvr_example_function_values}
   \centering
@@
   \end{tabular}
-  \caption{Example data of function \(2x^2+4\)}\label{table:lssvr_example_function_values}
 \end{table}
@@
       \begin{adjustbox}{width=\linewidth}
-        \input{figures/comparisons/burgers_rollout_model_pred_0.0.pgf}
+        \input{figures/comparisons/burgers_rollout_lssvr_pred_0.0.pgf}
       \end{adjustbox}
-      \caption{SpectralSVR prediction.}\label{fig:comp_model_pred_0.0}
+      \caption{SpectralSVR prediction.}\label{fig:comp_lssvr_pred_0.0}
     \end{subfigure}
@@
       \begin{adjustbox}{width=\linewidth}
-        \input{figures/comparisons/burgers_rollout_model_diff_0.0.pgf}
+        \input{figures/comparisons/burgers_rollout_lssvr_diff_0.0.pgf}
       \end{adjustbox}
-      \caption{SpectralSVR difference with target.}\label{fig:comp_model_diff_0.0}
+      \caption{SpectralSVR difference with target.}\label{fig:comp_lssvr_diff_0.0}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_fnn_pred_0.0.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR prediction.}\label{fig:comp_fnn_pred_0.0}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_fnn_diff_0.0.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR difference with target.}\label{fig:comp_fnn_diff_0.0}
     \end{subfigure}
@@
     \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/comparisons/burgers_rollout_tdo_pred_0.0.pgf}
-      \end{adjustbox}
-      \caption{torchdiffeq \& PyTorch prediction.}\label{fig:comp_tdo_pred_0.0}
-    \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/comparisons/burgers_rollout_tdo_diff_0.0.pgf}
-      \end{adjustbox}
-      \caption{torchdiffeq \& PyTorch difference with target.}\label{fig:comp_tdo_diff_0.0}
-    \end{subfigure}
   \end{adjustwidth}
@@
       \begin{adjustbox}{width=\linewidth}
-        \input{figures/comparisons/burgers_rollout_model_pred_0.01.pgf}
+        \input{figures/comparisons/burgers_rollout_lssvr_pred_0.01.pgf}
       \end{adjustbox}
-      \caption{SpectralSVR prediction.}\label{fig:comp_model_pred_0.01}
+      \caption{SpectralSVR prediction.}\label{fig:comp_lssvr_pred_0.01}
     \end{subfigure}
@@
       \begin{adjustbox}{width=\linewidth}
-        \input{figures/comparisons/burgers_rollout_model_diff_0.01.pgf}
+        \input{figures/comparisons/burgers_rollout_lssvr_diff_0.01.pgf}
       \end{adjustbox}
-      \caption{SpectralSVR difference with target.}\label{fig:comp_model_diff_0.01}
+      \caption{SpectralSVR difference with target.}\label{fig:comp_lssvr_diff_0.01}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_fnn_pred_0.01.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR prediction.}\label{fig:comp_fnn_pred_0.01}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_fnn_diff_0.01.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR difference with target.}\label{fig:comp_fnn_diff_0.01}
     \end{subfigure}
@@
     \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/comparisons/burgers_rollout_tdo_pred_0.01.pgf}
-      \end{adjustbox}
-      \caption{torchdiffeq \& PyTorch prediction.}\label{fig:comp_tdo_pred_0.01}
-    \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/comparisons/burgers_rollout_tdo_diff_0.01.pgf}
-      \end{adjustbox}
-      \caption{torchdiffeq \& PyTorch difference with target.}\label{fig:comp_tdo_diff_0.01}
-    \end{subfigure}
   \end{adjustwidth}
@@
 \end{figure}
-\begin{table}
-  \caption{Metrics for predicting the exact solution for SpectralSVR (Ours) method}\label{table:comparison_exact_metrics_model}
+\begin{table}[H]
+  \caption{Metrics for predicting the exact solution for SpectralSVR (Ours) method}\label{table:comparison_exact_metrics_lssvr}
   \centering
@@
 \end{table}
-\begin{table}
+\begin{table}[H]
+  \caption{Metrics for predicting the exact solution for SpectralSVR (FNN) baseline method}\label{table:comparison_exact_metrics_fnn}
+  \centering
+  \begin{tabular}{lcccc}
+    \toprule
+    \(\nu \) & MSE & RMSE & MAE & sMAPE \\
+    \midrule
+    0.0      & inf & inf  & inf & 1.99  \\
+    0.01     & inf & inf  & inf & 1.98  \\
+    0.1      & inf & inf  & inf & 1.98  \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+\begin{table}[H]
   \caption{Metrics for predicting the exact solution for the lsoda method}\label{table:comparison_exact_metrics_lsoda}
@@
 \end{table}
-\begin{table}
+\begin{table}[H]
   \caption{Metrics for predicting the exact solution for the IABM method}\label{table:comparison_exact_metrics_iabm}

### 2025-02-09 skripsi/chapter4.tex
fix table caption position
add FNN baseline

@@
 \begin{table}[H]
+  \caption{Testing results of the SpectralSVR Library implementation using black box method.}\label{table:impl_test_result}
   \centering
@@
   \end{tabular}
-  \caption{Testing results of the SpectralSVR Library implementation using black box method.}\label{table:impl_test_result}
 \end{table}
@@
 The choice of conventional physics based numerical methods is due to its mathematical guarantee that machine learning models do not possess \autocite{schiesserNumericalMethodLines2012,karniadakisPhysicsinformedMachineLearning2021}.
+However, for the sake of completeness, a comparison with as simple neural network to replace the LSSVR will also be done.
+This is by no means an attempt to replicate the SNO \autocite{fanaskovSpectralNeuralOperators2023} or NSM \autocite{du2024neural} approaches.
+The neural network will have 4 hidden layers with a width of 64 neurons each.
+The activation function we will use is the softplus function.
+And after some rough estimation of the number of epochs that will be required to avoid overfitting by comparing against a validation set, the model will be trained over 7 epochs using the same data as the LSSVR version.
 
@@
 And for the viscosity of \(\nu=0.0\), even the IABM method performs much better due to the fact that the solution is a constant value of zero.
+The baseline FNN method, however, does not perform well on any of the viscosities with the solution becoming unstable after several time steps.
 \begin{table}[H]
@@
     SpectralSVR       & 0.00 & 0.02 & 0.02 & 1.47  \\
+    SpectralSVR (FNN) & inf  & inf  & inf  & 1.98  \\
     lsoda             & 0.00 & 0.03 & 0.02 & 1.56  \\
@@
 We show that for our method and the lsoda method, the exact solution is achieved to a recognizable form.
-However, using the IABM method with torchdiffeq is ineffective and the solution \enquote{blows up} and results in many not a number values.
+However, using the IABM method with torchdiffeq is ineffective and the solution \enquote{blows up} and results in many not a number values, which is why we chose not to display them.
 Our method has errors characterized by lines which stems form our use of only eight basis functions to represent solution.
@@
       \begin{adjustbox}{width=\linewidth}
-        \input{figures/comparisons/burgers_exact_model_pred_0.1.pgf}
-      \end{adjustbox}
-      \caption{SpectralSVR prediction.}\label{fig:comp_exact_model_pred_0.1}
-    \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/comparisons/burgers_exact_model_diff_0.1.pgf}
-      \end{adjustbox}
-      \caption{SpectralSVR difference with target.}\label{fig:comp_exact_model_diff_0.1}
+        \input{figures/comparisons/burgers_exact_lssvr_pred_0.1.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR prediction.}\label{fig:comp_exact_lssvr_pred_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_exact_lssvr_diff_0.1.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR difference with target.}\label{fig:comp_exact_lssvr_diff_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_exact_fnn_pred_0.1.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR (FNN) prediction.}\label{fig:comp_exact_fnn_pred_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_exact_fnn_diff_0.1.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR (FNN) difference with target.}\label{fig:comp_exact_fnn_diff_0.1}
     \end{subfigure}
@@
     \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/comparisons/burgers_exact_tdo_pred_0.1.pgf}
-      \end{adjustbox}
-      \caption{torchdiffeq \& PyTorch prediction.}\label{fig:comp_exact_tdo_pred_0.1}
-    \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/comparisons/burgers_exact_tdo_diff_0.1.pgf}
-      \end{adjustbox}
-      \caption{torchdiffeq \& PyTorch difference with target.}\label{fig:comp_exact_tdo_diff_0.1}
-    \end{subfigure}
   \end{adjustwidth}
-  \caption{Comparison of our model (SpectralSVR) and numerical methods for the exact solution in \cref{eq:burgers_exact_solution} of the Forced Burgers equation with viscosity \(\nu=0.1\).}\label{fig:comparison_burgers_exact_0.1}
+  \caption{Comparison of our model (SpectralSVR), baseline FNN model, and numerical methods for the exact solution in \cref{eq:burgers_exact_solution} of the Forced Burgers equation with viscosity \(\nu=0.1\).}\label{fig:comparison_burgers_exact_0.1}
 \end{figure}
@@
 An obvious observation is the fact that the numerical methods fail to solve the entire solution.
-The SciPy odeint version is able to solve up until the 13th iteration or time \(t=0.6533\).
-The torchdiffeq version on the other hand only solves up until the second iteration.
+The SciPy odeint (lsoda) version is able to solve up until the 13th iteration or time \(t=0.6533\).
+The torchdiffeq (IABM) version on the other hand only solves up until the second iteration.
 Even at this early step, the solution is already unstable with many values having an order of larger than \num{10e10}.
@@
       \begin{adjustbox}{width=\linewidth}
-        \input{figures/comparisons/burgers_rollout_model_pred_0.1.pgf}
-      \end{adjustbox}
-      \caption{SpectralSVR prediction.}\label{fig:comp_model_pred_0.1}
-    \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/comparisons/burgers_rollout_model_diff_0.1.pgf}
-      \end{adjustbox}
-      \caption{SpectralSVR difference with target.}\label{fig:comp_model_diff_0.1}
+        \input{figures/comparisons/burgers_rollout_lssvr_pred_0.1.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR prediction.}\label{fig:comp_lssvr_pred_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_lssvr_diff_0.1.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR difference with target.}\label{fig:comp_lssvr_diff_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_fnn_pred_0.1.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR (FNN) prediction.}\label{fig:comp_fnn_pred_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_fnn_diff_0.1.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR (FNN) difference with target.}\label{fig:comp_fnn_diff_0.1}
     \end{subfigure}
@@
     \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/comparisons/burgers_rollout_tdo_pred_0.1.pgf}
-      \end{adjustbox}
-      \caption{torchdiffeq \& PyTorch prediction.}\label{fig:comp_tdo_pred_0.1}
-    \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \begin{adjustbox}{width=\linewidth}
-        \input{figures/comparisons/burgers_rollout_tdo_diff_0.1.pgf}
-      \end{adjustbox}
-      \caption{torchdiffeq \& PyTorch difference with target.}\label{fig:comp_tdo_diff_0.1}
-    \end{subfigure}
   \end{adjustwidth}
-  \caption{Comparison of our model (SpectralSVR) and numerical methods for a manufactured solution of the Forced Burgers equation with viscosity \(\nu=0.1\).}\label{fig:comparison_burgers_0.1}
+  \caption{Comparison of our model (SpectralSVR), baseline FNN model, and numerical methods for a manufactured solution of the Forced Burgers equation with viscosity \(\nu=0.1\).}\label{fig:comparison_burgers_0.1}
 \end{figure}
@@
 The results are shown in \lccref{table:comparison_efficiency}.
-Our method solves this problem the fastest by around 33 times faster than the lsoda method.
+Our method solves this problem around 33 times faster than the lsoda method.
+However, the kernel computation required does slow the LSSVR in comparison to the neural network version by around 140 milliseconds.
 \begin{table}[H]
@@
     \midrule
-    SpectralSVR & \textbf{0.431 s ± 0.122 s} \\
-    lsoda       & 12.1 s ± 2.62 s            \\
-    IABM        & 15.7 s ± 1.85 s            \\
+    SpectralSVR       & 0.438 s ± 0.075 s          \\
+    SpectralSVR (FNN) & \textbf{0.298 s ± 0.054 s} \\
+    lsoda             & 15.1 s ± 2.85 s            \\
+    IABM              & 20.9 s ± 2.98 s            \\
     \bottomrule
@@
 \end{table}
+
+In terms of training, the FNN baseline model with 7 epochs and a batch size of 16, training takes on average 14.6 seconds ± 0.86 seconds. The LSSVR version takes on average 8 seconds ± 2.47 seconds.
 

### 2025-02-10 skripsi/abstrak.tex
add discussion, add comparison, change conclusion, revise future work
fix typo in indonesian abstract title

@@
 \textbf{\large  ABSTRAK}\\[0.5cm]
-\textbf{\large Aproksimasi Solusi \textit{Govering Equations} dengan \emph{Fourier Transform} dan \textit{Support Vector Machine}}\\[0.5cm]
+\textbf{\large Aproksimasi Solusi \textit{Governing Equations} dengan \emph{Fourier Transform} dan \textit{Support Vector Machine}}\\[0.5cm]
 \textbf{Oleh}\\
@@
 Model yang dipelajari diinterpretasikan dan diverifikasi untuk mempelajari kontribusi yang benar dari koefisien fungsi masukan terhadap koefisien fungsi keluaran.
+Model yang diajukan menyelesaikan solusi \textit{Burgers' equation} hingga 33 kali lebih cepat daripada metode numerik tradisional lsoda.
 % \noindent Abstrak merupakan penjelasan singkat dan padat tentang pekerjaan dan hasil penelitian TA, yang dituliskan secara teknis.

### 2025-02-10 skripsi/acknowledgments.tex
update title to using instead of with, add more to acknowledgements

@@
 \noindent I would like to take the time to acknowledge my friends, family, and everyone who have taken the time to support and encourage me through the completion process of my degree.
+Through this work, I hope to be able to contribute to our understanding of the world.
+I also would like to thank all the professors and academic staff who have helped me to achieve this goal.
+At some points, parts of this work seemed endless and insurmountable.
+However, the support everyone has given me has been instrumental in surpassing those obstacles.
+
+On a more academic note, this work takes our knowledge of how the spectral method works and uses that as a basis for cases for when the systems are too complex, or not fully modeled mathematically.
+This means that, akin to how one would manually derive the solution coefficients from parameter coefficients in the spectral method, the proposed SpectralSVR would model the  relationship between solution coefficients and parameter coefficients from data.
+Building on previous work, our contribution also include interpretation of the learned relationship between coefficients.
+The proposed method exposes the learned relationship as the contributions of each parameter coefficient towards each solution coefficient.
+More specifically, I would like to acknowledge the works of \textcite{fanaskovSpectralNeuralOperators2023,du2024neural,ustunVisualisationInterpretationSupport2007} which have been the inspiration for the proposed approach.
+
 % \noindent Kata pengantar berperan sebagai gerbang masuk bagi pembaca dan mendapat sajian ringkas tentang hal-hal terkait paparan pada buku Tugas Akhir (TA).

### 2025-02-10 skripsi/identitas.tex
update title to using instead of with, add more to acknowledgements

@@
 %JUDUL: 
-\providecommand{\judul}{approximating solutions of governing equations with Fourier transform and support vector machine}
-\providecommand{\judulcapitalized}{Approximating Solutions of Governing Equations With Fourier Transform and Support Vector Machine}
+\providecommand{\judul}{approximating solutions of governing equations using Fourier transform and support vector machine}
+\providecommand{\judulcapitalized}{Approximating Solutions of Governing Equations Using Fourier Transform and Support Vector Machine}
 %PENULIS:

### 2025-04-01 article/apendix.tex
add comparisons in apendix & discussion, shorten conclusion, change order of authors,

@@
 \end{figure}
+
+\section{Burgers' Equation Comparison}\label{sec:burgers_comparison}
+\begin{figure}[H]
+  \centering
+  \begin{adjustwidth}{-0.05\linewidth}{-0.05\linewidth}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_lssvr_pred_0.0.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR prediction.}\label{fig:comp_lssvr_pred_0.0}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_lssvr_diff_0.0.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR difference with target.}\label{fig:comp_lssvr_diff_0.0}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_fnn_pred_0.0.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR prediction.}\label{fig:comp_fnn_pred_0.0}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_fnn_diff_0.0.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR difference with target.}\label{fig:comp_fnn_diff_0.0}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_spo_pred_0.0.pgf}
+      \end{adjustbox}
+      \caption{SciPy \& NumPy prediction.}\label{fig:comp_spo_pred_0.0}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_spo_diff_0.0.pgf}
+      \end{adjustbox}
+      \caption{SciPy \& NumPy difference with target.}\label{fig:comp_spo_diff_0.0}
+    \end{subfigure}
+  \end{adjustwidth}
+  \caption{Comparison of our model (SpectralSVR) and numerical methods for the Forced Burgers equation with viscosity \(\nu=0.0\).}\label{fig:comparison_burgers_0.0}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \begin{adjustwidth}{-0.05\linewidth}{-0.05\linewidth}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_lssvr_pred_0.01.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR prediction.}\label{fig:comp_lssvr_pred_0.01}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_lssvr_diff_0.01.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR difference with target.}\label{fig:comp_lssvr_diff_0.01}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_fnn_pred_0.01.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR prediction.}\label{fig:comp_fnn_pred_0.01}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_fnn_diff_0.01.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR difference with target.}\label{fig:comp_fnn_diff_0.01}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_spo_pred_0.01.pgf}
+      \end{adjustbox}
+      \caption{SciPy \& NumPy prediction.}\label{fig:comp_spo_pred_0.01}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_spo_diff_0.01.pgf}
+      \end{adjustbox}
+      \caption{SciPy \& NumPy difference with target.}\label{fig:comp_spo_diff_0.01}
+    \end{subfigure}
+  \end{adjustwidth}
+  \caption{Comparison of our model (SpectralSVR) and numerical methods for the Forced Burgers equation with viscosity \(\nu=0.01\).}\label{fig:comparison_burgers_0.01}
+\end{figure}
+\begin{table}[H]
+  \caption{Metrics for predicting the exact solution for SpectralSVR (Ours) method}\label{table:comparison_exact_metrics_lssvr}
+  \centering
+  \begin{tabular}{lcccc}
+    \toprule
+    \(\nu \) & MSE  & RMSE & MAE  & sMAPE \\
+    \midrule
+    0.0      & 0.01 & 0.07 & 0.06 & 1.99  \\
+    0.01     & 0.00 & 0.07 & 0.06 & 1.61  \\
+    0.1      & 0.00 & 0.02 & 0.02 & 1.47  \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+\begin{table}[H]
+  \caption{Metrics for predicting the exact solution for SpectralSVR (FNN) baseline method}\label{table:comparison_exact_metrics_fnn}
+  \centering
+  \begin{tabular}{lcccc}
+    \toprule
+    \(\nu \) & MSE & RMSE & MAE & sMAPE \\
+    \midrule
+    0.0      & inf & inf  & inf & 1.99  \\
+    0.01     & inf & inf  & inf & 1.98  \\
+    0.1      & inf & inf  & inf & 1.98  \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+\begin{table}[H]
+  \caption{Metrics for predicting the exact solution for the lsoda method}\label{table:comparison_exact_metrics_lsoda}
+  \centering
+  \begin{tabular}{lcccc}
+    \toprule
+    \(\nu \) & MSE  & RMSE & MAE  & sMAPE \\
+    \midrule
+    0.0      & 0.00 & 0.00 & 0.00 & 0.00  \\
+    0.01     & 0.00 & 0.00 & 0.00 & 0.08  \\
+    0.1      & 0.00 & 0.04 & 0.04 & 1.52  \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+\begin{table}[H]
+  \caption{Metrics for predicting the exact solution for the IABM method}\label{table:comparison_exact_metrics_iabm}
+  \centering
+  \begin{tabular}{lcccc}
+    \toprule
+    \(\nu \) & MSE  & RMSE & MAE  & sMAPE \\
+    \midrule
+    0.0      & 0.00 & 0.00 & 0.00 & 0.00  \\
+    0.01     & nan  & nan  & nan  & nan   \\
+    0.1      & nan  & nan  & nan  & nan   \\
+    \bottomrule
+  \end{tabular}
+\end{table}

### 2025-04-01 article/article.tex
change flowcharts to use start and stop
add comparisons in apendix & discussion, shorten conclusion, change order of authors,

@@
   \title{\judul}
-  % \author{
-  %   Lala Septem Riza\\
-  %   \texttt{lala.s.riza@upi.edu}
-  %   \and
-  %   Ahmad Izzuddin\\
-  %   \texttt{ahmadizzuddin@upi.edu}
+  \author[upi]{Ahmad Izzuddin}
+  \ead{ahmadizzuddin@upi.edu}
+  \author[upi]{Muhammad Nursalman}
+  \ead{mnursalman@upi.edu}
+  \author[ku]{Hadi Susanto}
+  \ead{hadi.susanto@ku.ac.ae}
   \author[upi]{Lala Septem Riza}
   \ead{lala.s.riza@upi.edu}
-  \author[upi]{Ahmad Izzuddin}
-  \ead{ahmadizzuddin@upi.edu}
 
-  \affiliation[upi]{organization={Department of Computer Science Education Universitas Pendidikan Indonesia},%Department and Organization
+  \affiliation[upi]{organization={Department of Computer Science Universitas Pendidikan Indonesia},%Department and Organization
     addressline={Jl. Dr.\ Setiabudi No.229},
@@
     country={Indonesia}}
+  \affiliation[ku]{organization={Department of Mathematics Khalifa University},%Department and Organization
+    addressline={Shakhbout Bin Sultan St - Hadbat Al Za`Faranah},
+    postcode={127788},
+    city={Abu Dhabi},
+    country={United Arab Emirates}}
   \begin{abstract}
@@
 \end{figure}
+% TODO: add psuedocode for training the model
+% TODO: add figures of how a dataset of 1D functions is represented and the transformed coefficient representation
 
@@
 \section{Results and Discussion}
-In this section, we will present the results of the experiments on each equation and the ERA5 dataset.
+In this section, we will present the results of the experiments on the derivative equation and the Burgers' equation.
 The metrics we will show in this section are evaluated between the function values evaluated from the predicted coefficients and the function values of the test label coefficients.
@@
 But the kernel still manages to embed some information.
-The p-matrices show that The model itself is able to still learn some relationship between the input coefficients and the output coefficients.
+The p-matrices show that the model itself is able to still learn some relationship between the input coefficients and the output coefficients.
 For the 5\% and 10\% noise levels, the p-matrices show very clearly the contributions of input coefficients to the output coefficients.
@@
 The contribution once again become more pronounced the higher the absolute value of the wave number.
+
+\subsection{Comparisons}
+
+\noindent As a point of reference, the comparisons of our method against three other methods will be discussed for solving the Burger's equation as an initial value problem.
+The methods we compare against are the lsoda program using the SciPy library, the Implicit Adams-Bashforth-Moulton (IABM) method using the torchdiffeq library, and using a Fully-connected Neural Network (FNN) in place of the LSSVR to directly model the coefficient relationships.
+Both the lsoda and IABM approaches discretize the solution in space into 400 points and the periodicity is enforced using a ghost cell at one end that has the same value as the other end.
+First, we present the results of solving \lccref{eq:burgers_exact_solution} as an IVP as shown in \lccref{table:comparison_exact_metrics_0.1} for viscosity \(\nu=0.1\).
+For the forcing term, we use a constant value of zero.
+The functions are also unperturbed.
+The metrics measure the performance of the predicted solutions compared against the exact solution.
+We see that our model has slightly better performance compared to the lsoda method.
+However, for lower viscosity values the lsoda method performs much better compared to ours as shown in~\ref{sec:burgers_comparison}.
+And for the viscosity of \(\nu=0.0\), even the IABM method performs much better due to the fact that the solution is a constant value of zero.
+The baseline FNN method, however, does not perform well on any of the viscosity values with the solution becoming unstable after several time steps.
+\begin{table}[H]
+  \caption{Metrics for predicting the exact solution for each method with viscosity \(\nu=0.1\)}\label{table:comparison_exact_metrics_0.1}
+  \centering
+  \begin{tabular}{lcccc}
+    \toprule
+    Method            & MSE  & RMSE & MAE  & sMAPE \\
+    \midrule
+
+    SpectralSVR       & 0.00 & 0.02 & 0.02 & 1.47  \\
+    SpectralSVR (FNN) & inf  & inf  & inf  & 1.98  \\
+    lsoda             & 0.00 & 0.04 & 0.04 & 1.52  \\
+    IABM              & nan  & nan  & nan  & nan   \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+For better visualization, the predictions and the difference against the exact solution is shown in \lccref{fig:comparison_burgers_exact_0.1}.
+We show that for our method and the lsoda method, the exact solution is achieved to a recognizable form.
+However, using the IABM method with torchdiffeq is ineffective, and the solution \enquote{blows up} and results in many not a number values, which is why we chose not to display them.
+Our method has errors characterized by \enquote{lines} which stems form our use of only eight basis functions to represent solution.
+This is in contrast to the error of the lsoda method, which is spread over larger areas.
+\begin{figure}[H]
+  \centering
+  \begin{adjustwidth}{-0.05\linewidth}{-0.05\linewidth}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_exact_lssvr_pred_0.1.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR prediction.}\label{fig:comp_exact_lssvr_pred_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_exact_lssvr_diff_0.1.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR difference with target.}\label{fig:comp_exact_lssvr_diff_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_exact_fnn_pred_0.1.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR (FNN) prediction.}\label{fig:comp_exact_fnn_pred_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_exact_fnn_diff_0.1.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR (FNN) difference with target.}\label{fig:comp_exact_fnn_diff_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_exact_spo_pred_0.1.pgf}
+      \end{adjustbox}
+      \caption{SciPy \& NumPy prediction.}\label{fig:comp_exact_spo_pred_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_exact_spo_diff_0.1.pgf}
+      \end{adjustbox}
+      \caption{SciPy \& NumPy difference with target.}\label{fig:comp_exact_spo_diff_0.1}
+    \end{subfigure}
+  \end{adjustwidth}
+  \caption{Comparison of our model (SpectralSVR), baseline FNN model, and numerical methods for the exact solution in \cref{eq:burgers_exact_solution} of the Forced Burgers equation with viscosity \(\nu=0.1\).}\label{fig:comparison_burgers_exact_0.1}
+\end{figure}
+
+The predictions for IVP rollout of the functions in the test set is shown in \lccrefs{fig:comparison_burgers_0.1} for viscosity \(\nu=0.1\).
+Other viscosity values were also compared and presented in \lccrefs{fig:comparison_burgers_0.0,fig:comparison_burgers_0.01}.
+An obvious observation is the fact that the numerical methods fail to solve the entire solution.
+The SciPy odeint (lsoda) version is able to solve up until the 13th iteration or time \(t=0.6533\).
+The torchdiffeq (IABM) version on the other hand only solves up until the second iteration.
+Even at this early step, the solution is already unstable with many values having an order of larger than \num{10e10}.
+\begin{figure}[H]
+  \centering
+  \begin{adjustwidth}{-0.05\linewidth}{-0.05\linewidth}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_lssvr_pred_0.1.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR prediction.}\label{fig:comp_lssvr_pred_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_lssvr_diff_0.1.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR difference with target.}\label{fig:comp_lssvr_diff_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_fnn_pred_0.1.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR (FNN) prediction.}\label{fig:comp_fnn_pred_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_fnn_diff_0.1.pgf}
+      \end{adjustbox}
+      \caption{SpectralSVR (FNN) difference with target.}\label{fig:comp_fnn_diff_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_spo_pred_0.1.pgf}
+      \end{adjustbox}
+      \caption{SciPy \& NumPy prediction.}\label{fig:comp_spo_pred_0.1}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \begin{adjustbox}{width=\linewidth}
+        \input{figures/comparisons/burgers_rollout_spo_diff_0.1.pgf}
+      \end{adjustbox}
+      \caption{SciPy \& NumPy difference with target.}\label{fig:comp_spo_diff_0.1}
+    \end{subfigure}
+  \end{adjustwidth}
+  \caption{Comparison of our model (SpectralSVR), baseline FNN model, and numerical methods for a manufactured solution of the Forced Burgers equation with viscosity \(\nu=0.1\).}\label{fig:comparison_burgers_0.1}
+\end{figure}
+
+In terms of efficiency, we also present our measurements of the time it took for each method to solve the exact solution IVP using the \verb|%timit| macro in Jupyter Notebook.
+This was done on our machine without any hardware accelerators such as GPUs.
+The time was averaged over 7 measurements.
+The results are shown in \lccref{table:comparison_efficiency}.
+Our method solves this problem around 33 times faster than the lsoda method.
+However, the kernel computation required does slow the LSSVR in comparison to the neural network version by around 140 milliseconds.
+\begin{table}[H]
+  \caption{Average time elapsed in solving for \lccref{eq:burgers_exact_solution} by method.}\label{table:comparison_efficiency}
+  \centering
+  \begin{tabular}{lc}
+    \toprule
+    Method            & Time Elapsed               \\
+    \midrule
+    SpectralSVR       & 0.438 s \pm{} 0.075 s          \\
+    SpectralSVR (FNN) & \textbf{0.298 s \pm{} 0.054 s} \\
+    lsoda             & 15.1 s \pm{} 2.85 s            \\
+    IABM              & 20.9 s \pm{} 2.98 s            \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+In terms of training, the FNN baseline model with 7 epochs and a batch size of 16, training takes on average 14.6 seconds \pm{} 0.86 seconds.
+The LSSVR version takes on average 8 seconds \pm{} 2.47 seconds.
+
 \section{Conclusion}
-\noindent Based on the results of the research into \MakeLowercase{\judul}, several conclusions can be drawn.
-\begin{enumerate}
-  \item The proposed SpectralSVR model is able to learn the relationships defined by PDEs.
-This is done using a model that learns in the Fourier domain with Fourier Transforms and Inverse Transform bridging the Fourier domain and the physical domain.
-  \item Interpretation of the proposed model can be done to a certain extent using two tools which are the correlation image and p-matrix developed by \citet{ustunVisualisationInterpretationSupport2007}.
-This interpretation shows that the model correctly attributes the relationship of the input coefficients to the output coefficients.
-  \item The proposed model is also capable in dealing with noise and partial data as shown in scenario 1.
-        % \item The model's capabilities are also verified using exact solution. This revealed that for some configurations the model is able to successfully generalize to exact solutions.
-\end{enumerate}
+\noindent Using the LSSVR to predict the Fourier coefficients of approximate solutions to PDEs, we demonstrate the advantages of this approach in terms of efficiency and interpretability.
+Because of the potential this approach has shown, it is a promising candidate for further research.
 
-To improve the model's predictive capabilities, several key areas of enhancement have been identified for future works.
-First, the synthetic data used in scenarios 1 and 2 lack realism, even though they are mathematically correct when generated using the method of manufactured solutions.
-Incorporating data derived from traditional numerical methods or other reliable sources could help the model produce more accurate and realistic predictions.
-Evaluating the performance of auto-regression in weather data compared to target data is another critical step.
-Additionally, the inverse prediction results should be compared with traditional methods, such as the spectral method or finite difference method (FDM), to assess accuracy and reliability.
-
-Further improvements include benchmarking the proposed method against comparable approaches and measuring computational efficiency in terms of time, relative to both traditional and machine learning-based methods.
-Expanding the range of basis functions, such as spherical harmonics or wavelet bases, and incorporating additional regression models, specifically support vector regression models, could enhance the utility of tools like the correlation image and p-matrix.
-The use of better performance metrics, such as the standard error of regression, is recommended, along with a detailed analysis of performance across varying hyperparameters, data sizes, and error trends by wave number.
-Addressing the issue of double penalties, which lead to overly smooth solutions \citep{brownForecastsSpatialFields2011,NIPS2017_44a2e080}, requires exploring stronger regularization for higher wave numbers.
-Finally, incorporating data assimilation techniques, such as the Lomb-Scargle periodogram \citep{vanderplasUnderstandingLombScargle2018} and 4D-Var assimilation \citep{puNumericalWeatherPrediction2018,parkDataAssimilationAtmospheric2013}, could enable support for sparse data.
-Finally, a study of contribution patterns for different terms in partial differential equations (PDEs) using methods like the p-matrix would provide deeper insights into model dynamics.
-
-These future directions build on the strengths of the proposed SpectralSVR model, which has demonstrated its ability to learn relationships defined by PDEs, interpret results using tools like the correlation image and p-matrix, and handle noise and partial data effectively.
-By addressing these identified areas of improvement, the model's robustness, accuracy, and applicability could be further enhanced, especially in real-world scenarios.
-
-Through these developments, the SpectralSVR model has the potential to not only refine its generalization capabilities, as evidenced by its partial success with exact solutions, but also to expand its utility across diverse and complex problems.
-These steps will contribute to advancing computational approaches for SciML-based modelling and establish the proposed framework as a versatile tool in this domain.
+Based on the limitations of this work, we highlight three areas of interest for future research.
+First, our focus on the use of the Fourier basis means that it is much more suited for certain geometries.
+This may cause aberrations when used with unsuitable geometries such as a sphere \citep{bonevSphericalFourierNeural2023}.
+Which is why other kinds of basis functions such as spherical harmonics or even learned basis functions is of great interest in a variety of applications.
+Second, our configuration for generating the training data means that it is mathematically correct \citep{roacheCodeVerificationMethod2002,salariCodeVerificationMethod2000,vedovotoApplicationMethodManufactured2011} but not representative of the desired distribution of function types; in addition to lacking realism.
+Because of this, an investigation into different distributions of function types like using more realistic solutions from traditional solvers would allow the model to handle challenges like flatness.
+Last but not least, improving the interpretability of the model such as gaining insight into the contributions of each term in a governing equation will build upon the visualization provided by the p-matrix.
 

### 2025-04-24 article/apendix.tex
shrink matplotlib pgf to graph size, change library name for comparison method to computational method used, add full stop to captions, add psuedocode for training, change figure placement to hbp to reduce dead whitespace.

@@
       \end{adjustbox}
-      \caption{SciPy \& NumPy prediction.}\label{fig:comp_spo_pred_0.0}
+      \caption{lsoda prediction.}\label{fig:comp_spo_pred_0.0}
     \end{subfigure}
@@
       \end{adjustbox}
-      \caption{SciPy \& NumPy difference with target.}\label{fig:comp_spo_diff_0.0}
+      \caption{lsoda difference with target.}\label{fig:comp_spo_diff_0.0}
     \end{subfigure}
@@
       \end{adjustbox}
-      \caption{SciPy \& NumPy prediction.}\label{fig:comp_spo_pred_0.01}
+      \caption{lsoda prediction.}\label{fig:comp_spo_pred_0.01}
     \end{subfigure}
@@
       \end{adjustbox}
-      \caption{SciPy \& NumPy difference with target.}\label{fig:comp_spo_diff_0.01}
+      \caption{lsoda difference with target.}\label{fig:comp_spo_diff_0.01}
     \end{subfigure}
@@
 \begin{table}[H]
-  \caption{Metrics for predicting the exact solution for SpectralSVR (Ours) method}\label{table:comparison_exact_metrics_lssvr}
+  \caption{Metrics for predicting the exact solution for SpectralSVR (Ours) method.}\label{table:comparison_exact_metrics_lssvr}
   \centering
@@
 \begin{table}[H]
-  \caption{Metrics for predicting the exact solution for SpectralSVR (FNN) baseline method}\label{table:comparison_exact_metrics_fnn}
+  \caption{Metrics for predicting the exact solution for SpectralSVR (FNN) baseline method.}\label{table:comparison_exact_metrics_fnn}
   \centering
@@
 \begin{table}[H]
-  \caption{Metrics for predicting the exact solution for the lsoda method}\label{table:comparison_exact_metrics_lsoda}
+  \caption{Metrics for predicting the exact solution for the lsoda method.}\label{table:comparison_exact_metrics_lsoda}
   \centering
@@
 \begin{table}[H]
-  \caption{Metrics for predicting the exact solution for the IABM method}\label{table:comparison_exact_metrics_iabm}
+  \caption{Metrics for predicting the exact solution for the IABM method.}\label{table:comparison_exact_metrics_iabm}
   \centering

### 2025-04-24 article/article.tex
shrink matplotlib pgf to graph size, change library name for comparison method to computational method used, add full stop to captions, add psuedocode for training, change figure placement to hbp to reduce dead whitespace.

@@
 And, any predictions from the model, which are coefficients, should be transformed back into function values.
-The training process is shown in \lccref{fig:spectralsvr_training}.
-The process starts with determining the feature and label functions.
-Typically, the feature functions would include the forcing term and other parameter functions such as the solution at the current time step.
-The label functions typically is the solution function or the solution function at the next time step.
-The Fourier coefficients are then computed using the DFT\@.
-The coefficients are then flattened for each sample.
-A scaling function is fitted on the flattened feature coefficients and the feature coefficients are then scaled using the fitted scaling function.
-Finally, Using the scaled feature and label coefficients, the training function computes the parameters of the model.
-
-\begin{figure}[H]
+\begin{figure}[hbp]
   \centering
   \tikzfig{figures/training_spectralsvr}
-  \caption{SpectralSVR training diagram}\label{fig:spectralsvr_training}
+  \caption{SpectralSVR training diagram.}\label{fig:spectralsvr_training}
 \end{figure}
-% TODO: add psuedocode for training the model
+
+The training process is shown in \lccref{fig:spectralsvr_training}.
+The process in psuedocode is also shown in \lccref{alg:spectralsvr_training_psuedocode}.
+The process starts with determining the parameter and solution functions.
+Typically, the parameter functions would include the forcing term and others such as the initial solution function values.
+The solution function typically is the state variable that the PDE constraints using its derivatives, such as the displacement of a membrane for the wave equation.
+Next, the features and labels are constructed.
+Generally, the Fourier coefficients for both functions are computed using the DFT\@.
+And then, the parameter and solution coefficients are used as the feature and labels respectively.
+To finalize the construction, the coefficients are flattened into one dimension for each sample.
+And then, the features are scaled for training the LSSVR\@.
+Finally, after the feature and label construction, we train the LSSVR by computing the parameters of the model.
+In the psuedocode this starts by computing the kernel matrix from the features.
+And then the two matrices, \(\vb{A}\) and \(\vb{B}\), are put together to compute the model parameters via least-squares, which marks the end of the training process.
+\begin{algorithm}[hbp]
+  \caption{SpectralSVR Training Psuedocode.}\label{alg:spectralsvr_training_psuedocode}
+  \begin{algorithmic}[1]
+    \Procedure{TrainSpectralSVR}{$\vb{U}, \vb{F}, C $}
+    \State{\(\vb{\hat{U}} \gets DFT(\vb{U})\)}
+    \State{\(\vb{\hat{F}} \gets DFT(\vb{F})\)}
+    \Comment{Compute Fourier coefficients of training functions}
+    \State{\(\vb{X} \gets finalizeFeatures(\vb{\hat{U}},\vb{\hat{F}})\)}
+    \State{\(\vb{y} \gets finalizeLabels(\vb{\hat{U}},\vb{\hat{F}})\)}
+    \State{\(\Omega \gets K(\vb{X})\)}
+    \Comment{Construct matrix of inner products}
+    \State{\(\vb{A} \gets [[]]\)}
+    \State{\(\vb{B} \gets [[]]\)}
+    \State{\(\vb{A}[1:,1:] \gets \Omega+\frac{\vb{I}}{C}, \vb{A}[0,:] \gets 0,\vb{A}[:,0] \gets 0\)}
+    \State{\(\vb{B}[0] \gets 0, \vb{B}[1:] \gets \vb{y}\)}
+    \State{\(\vb{S} \gets leastSquares(\vb{A},\vb{B})\)}
+    \State{\(\vb{\alpha} \gets \vb{S}[1:],\vb{b} \gets \vb{S}[0]\)}
+    \Comment{Learned model parameters}
+    \State{\textbf{return} \(\vb{\alpha}, \vb{b}\)}
+    \EndProcedure{}
+  \end{algorithmic}
+\end{algorithm}
+
 % TODO: add figures of how a dataset of 1D functions is represented and the transformed coefficient representation
+% The data transformations are visualized in \lccref{fig:spectralsvr_training_data}.
+% \begin{figure}[hbp]
+%   \centering
+%   \tikzfig{figures/training_spectralsvr_data}
+%   \caption{SpectralSVR training data transformations.}\label{fig:spectralsvr_training_data}
+% \end{figure}
 
@@
 Finally, the inverse DFT is computed on the predicted coefficients to obtain the predicted function value.
-\begin{figure}[H]
+\begin{figure}[hbp]
   \centering
   \tikzfig{figures/prediction_spectralsvr}
-  \caption{SpectralSVR prediction diagram}\label{fig:spectralsvr_prediction}
+  \caption{SpectralSVR prediction diagram.}\label{fig:spectralsvr_prediction}
 \end{figure}
-
-To interpret the relationship learned by the LSSVR between the feature and label coefficients, we use two tools called the correlation image and p-matrix introduced by \citet{ustunVisualisationInterpretationSupport2007}.
 
@@
 However, looking at the p-matrix for 50\% noise level, the lower wave numbers show lower contribution of input coefficients to the output coefficients.
-\begin{figure}[H]
+\begin{figure}[hbp]
   \begin{adjustwidth}{-0.05\linewidth}{-0.05\linewidth}
@@
 This results in the model being able to finish the rollout for this sample.
-\begin{figure}[H]
+\begin{figure}[hbp]
   \centering
@@
       \end{adjustbox}
-      \caption{The target for \(\nu=0.0\)}\label{fig:sc2_rollout_target_0.0}
+      \caption{The target for \(\nu=0.0\).}\label{fig:sc2_rollout_target_0.0}
     \end{subfigure}
@@
       \end{adjustbox}
-      \caption{The prediction for \(\nu=0.0\)}\label{fig:sc2_rollout_pred_0.0}
+      \caption{The prediction for \(\nu=0.0\).}\label{fig:sc2_rollout_pred_0.0}
     \end{subfigure}
@@
       \end{adjustbox}
-      \caption{The difference for \(\nu=0.0\)}\label{fig:sc2_rollout_diff_0.0}
+      \caption{The difference for \(\nu=0.0\).}\label{fig:sc2_rollout_diff_0.0}
     \end{subfigure}
@@
       \end{adjustbox}
-      \caption{The target for \(\nu=0.01\)}\label{fig:sc2_rollout_target_0.01}
+      \caption{The target for \(\nu=0.01\).}\label{fig:sc2_rollout_target_0.01}
     \end{subfigure}
@@
       \end{adjustbox}
-      \caption{The prediction for \(\nu=0.01\)}\label{fig:sc2_rollout_pred_0.01}
+      \caption{The prediction for \(\nu=0.01\).}\label{fig:sc2_rollout_pred_0.01}
     \end{subfigure}
@@
       \end{adjustbox}
-      \caption{The difference for \(\nu=0.01\)}\label{fig:sc2_rollout_diff_0.01}
+      \caption{The difference for \(\nu=0.01\).}\label{fig:sc2_rollout_diff_0.01}
     \end{subfigure}
@@
       \end{adjustbox}
-      \caption{The target for \(\nu=0.1\)}\label{fig:sc2_rollout_target_0.1}
+      \caption{The target for \(\nu=0.1\).}\label{fig:sc2_rollout_target_0.1}
     \end{subfigure}
@@
       \end{adjustbox}
-      \caption{The prediction for \(\nu=0.1\)}\label{fig:sc2_rollout_pred_0.1}
+      \caption{The prediction for \(\nu=0.1\).}\label{fig:sc2_rollout_pred_0.1}
     \end{subfigure}
@@
       \end{adjustbox}
-      \caption{The difference for \(\nu=0.1\)}\label{fig:sc2_rollout_diff_0.1}
+      \caption{The difference for \(\nu=0.1\).}\label{fig:sc2_rollout_diff_0.1}
     \end{subfigure}
@@
 The error for the flatter functions may also be alleviated by including similar flatter functions during training.
-\begin{figure}[H]
+\begin{figure}[hbp]
   \centering
@@
       \end{adjustbox}
-      \caption{The target for \(\nu=0.0\)}\label{fig:sc2_exact_target_0.0}
+      \caption{The target for \(\nu=0.0\).}\label{fig:sc2_exact_target_0.0}
     \end{subfigure}
@@
       \end{adjustbox}
-      \caption{The prediction for \(\nu=0.0\)}\label{fig:sc2_exact_pred_0.0}
+      \caption{The prediction for \(\nu=0.0\).}\label{fig:sc2_exact_pred_0.0}
     \end{subfigure}
@@
       \end{adjustbox}
-      \caption{The difference for \(\nu=0.0\)}\label{fig:sc2_exact_diff_0.0}
+      \caption{The difference for \(\nu=0.0\).}\label{fig:sc2_exact_diff_0.0}
     \end{subfigure}
@@
       \end{adjustbox}
-      \caption{The target for \(\nu=0.01\)}\label{fig:sc2_exact_target_0.01}
+      \caption{The target for \(\nu=0.01\).}\label{fig:sc2_exact_target_0.01}
     \end{subfigure}
@@
       \end{adjustbox}
-      \caption{The prediction for \(\nu=0.01\)}\label{fig:sc2_exact_pred_0.01}
+      \caption{The prediction for \(\nu=0.01\).}\label{fig:sc2_exact_pred_0.01}
     \end{subfigure}
@@
       \end{adjustbox}
-      \caption{The difference for \(\nu=0.01\)}\label{fig:sc2_exact_diff_0.01}
+      \caption{The difference for \(\nu=0.01\).}\label{fig:sc2_exact_diff_0.01}
     \end{subfigure}
@@
       \end{adjustbox}
-      \caption{The target for \(\nu=0.1\)}\label{fig:sc2_exact_target_0.1}
+      \caption{The target for \(\nu=0.1\).}\label{fig:sc2_exact_target_0.1}
     \end{subfigure}
@@
       \end{adjustbox}
-      \caption{The prediction for \(\nu=0.1\)}\label{fig:sc2_exact_pred_0.1}
+      \caption{The prediction for \(\nu=0.1\).}\label{fig:sc2_exact_pred_0.1}
     \end{subfigure}
@@
       \end{adjustbox}
-      \caption{The difference for \(\nu=0.1\)}\label{fig:sc2_exact_diff_0.1}
+      \caption{The difference for \(\nu=0.1\).}\label{fig:sc2_exact_diff_0.1}
     \end{subfigure}
@@
 For a higher viscosity of \(\nu=0.01\), a weaker correlation is still present.
-\begin{figure}[H]
+\begin{figure}[hbp]
   \centering
   \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
+    \centering
+    \begin{adjustbox}{height=5.5cm}
       \input{figures/burgers_ci_0.0.pgf}
@@
   \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
+    \centering
+    \begin{adjustbox}{height=5.5cm}
       \input{figures/burgers_pm_0.0.pgf}
@@
   \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
+    \centering
+    \begin{adjustbox}{height=5.5cm}
       \input{figures/burgers_ci_0.01.pgf}
@@
   \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
+    \centering
+    \begin{adjustbox}{height=5.5cm}
       \input{figures/burgers_pm_0.01.pgf}
@@
   \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
+    \centering
+    \begin{adjustbox}{height=5.5cm}
       \input{figures/burgers_ci_0.1.pgf}
@@
   \begin{subfigure}{0.49\linewidth}
-    \begin{adjustbox}{width=\linewidth}
+    \centering
+    \begin{adjustbox}{height=5.5cm}
       \input{figures/burgers_pm_0.1.pgf}
@@
 The baseline FNN method, however, does not perform well on any of the viscosity values with the solution becoming unstable after several time steps.
-\begin{table}[H]
-  \caption{Metrics for predicting the exact solution for each method with viscosity \(\nu=0.1\)}\label{table:comparison_exact_metrics_0.1}
+\begin{table}[htp]
+  \caption{Metrics for predicting the exact solution for each method with viscosity \(\nu=0.1\).}\label{table:comparison_exact_metrics_0.1}
   \centering
@@
 This is in contrast to the error of the lsoda method, which is spread over larger areas.
-\begin{figure}[H]
+\begin{figure}[hbp]
   \centering
@@
       \end{adjustbox}
-      \caption{SciPy \& NumPy prediction.}\label{fig:comp_exact_spo_pred_0.1}
+      \caption{lsoda prediction.}\label{fig:comp_exact_spo_pred_0.1}
     \end{subfigure}
@@
       \end{adjustbox}
-      \caption{SciPy \& NumPy difference with target.}\label{fig:comp_exact_spo_diff_0.1}
+      \caption{lsoda difference with target.}\label{fig:comp_exact_spo_diff_0.1}
     \end{subfigure}
@@
 Even at this early step, the solution is already unstable with many values having an order of larger than \num{10e10}.
-\begin{figure}[H]
+\begin{figure}[hbp]
   \centering
@@
       \end{adjustbox}
-      \caption{SciPy \& NumPy prediction.}\label{fig:comp_spo_pred_0.1}
+      \caption{lsoda prediction.}\label{fig:comp_spo_pred_0.1}
     \end{subfigure}
@@
       \end{adjustbox}
-      \caption{SciPy \& NumPy difference with target.}\label{fig:comp_spo_diff_0.1}
+      \caption{lsoda difference with target.}\label{fig:comp_spo_diff_0.1}
     \end{subfigure}
@@
 However, the kernel computation required does slow the LSSVR in comparison to the neural network version by around 140 milliseconds.
-\begin{table}[H]
+\begin{table}[hbp]
   \caption{Average time elapsed in solving for \lccref{eq:burgers_exact_solution} by method.}\label{table:comparison_efficiency}
@@
 
-\input{apendix.tex}
-
 \bibliographystyle{elsarticle-harv}
 \bibliography{references.bib}
+
+\input{apendix.tex}
 \end{document}

### 2025-05-22 skripsi/chapter4.tex
fix dagger in pseudocode for lssvr training since we just do least squares and not psuedoinverse, add footer, add signatures

@@
 The functions are also unperturbed.
-The metrics measure the performace of the predicted solutions compared against the exact solution.
+The metrics measure the performance of the predicted solutions compared against the exact solution.
 We see that our model has slightly better performance compared to the lsoda method.
@@
 And for the viscosity of \(\nu=0.0\), even the IABM method performs much better due to the fact that the solution is a constant value of zero.
-The baseline FNN method, however, does not perform well on any of the viscosities with the solution becoming unstable after several time steps.
+The baseline FNN method, however, does not perform well on any of the viscosity values with the solution becoming unstable after several time steps.
 \begin{table}[H]

### 2025-05-22 skripsi/copyright.tex
fix dagger in pseudocode for lssvr training since we just do least squares and not psuedoinverse, add footer, add signatures

% !TEX root = ./skripsi.tex
% lembar hak cipta
\newpage
\phantomsection{}
\addcontentsline{toc}{chapter}{COPYRIGHT}

\begin{center}
    \doublespacing
    \textbf{\MakeUppercase{\judul}}
\end{center}

\begin{center}
    Oleh\\
    \penulis\\[6em]
\end{center}
\begin{center}
    Sebuah skripsi yang diajukan untuk memenuhi salah satu syarat memperoleh gelar Sarjana Komputer pada Fakultas Pendidikan Matematika dan Ilmu Pengetahuan Alam\\
\end{center}
\vfill
\begin{center}
    \textcopyright{} \penulis{} 2025\\
    Universitas Pendidikan Indonesia\\
    Mei 2025\\
\end{center}
\vfill 
\begin{center}
    Hak Cipta dilindungi undang-undang.\\
    Skripsi ini tidak boleh diperbanyak seluruhya atau sebagian, dengan dicetak ulang, difoto kopi, atau cara lainnya tanpa ijin dari penulis.\\
\end{center}
